---
title: "CRH PC Engagement Metrics"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(cowplot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
```

```{r reading-in}
analytic_df = dbGetQuery(oabi_con,
                         "select *
                         from [OABI_myVAAccess].[pccrh_eng].Z_analytic_df") %>%
  filter(always_missing_gap == F & always_missing_pf == F) %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_cat = factor(case_when(
           gap_metric < 1.0 ~ "< 1.0",
           gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
           gap_metric > 1.2 ~ "> 1.2",
           TRUE ~ "Missing"
         ), 
         ordered = TRUE,
         levels = c("< 1.0", "1.0 - 1.2", "> 1.2", "Missing")),
         pf_cat = factor(case_when(
           panel_fullness > 1.0 ~ "> 100%",
           panel_fullness >= 0.8 & panel_fullness <= 1.0 ~ "80% - 100%",
           panel_fullness < 0.8 ~ "< 80%",
           TRUE ~ "Missing"
         ),
         ordered = TRUE,
         levels = c("< 80%", "80% - 100%", "> 100%", "Missing")),
         period_initiating_crh = factor(period_initiating_crh,
                                        ordered = TRUE,
                                        levels = c("Before March 2020", 
                                                   "March to September 2020",
                                                   "After September 2020")))
#
vast = DBI::dbGetQuery(oabi_con,
                  "--
select distinct sta5a = stationno, parent_station = par_sta_no, visn = newvisn, city, st, stationname, s_abbr
from [PACT_CC].[Dim].VAST
where extractdate = '8-16-2022'
	AND s_abbr IN('HCC', 'VAMC', 'MSCBOC', 'PCCBOC', 'OOS')
	AND stationname NOT LIKE '%Mobile Clinic%'
	AND stationno IN(select distinct sta6aid from PACT_CC.Dim.VAST_Historic where snapshotDate = '2022-07-01')") %>%
  filter(sta5a %in% analytic_df$sta5a) %>%
  mutate(visn = str_pad(visn, width = 2, side = "left", pad = "0"))
```


# Timeframe  

* The first month of observation is `r min(analytic_df$vssc_month)`
* The last month of observation is `r max(analytic_df$vssc_month)`

# Sta5as  

* There are `r n_distinct(analytic_df$sta5a) %>% comma()` unique sta5as  
* I have excluded:
    + Sites with < 450 uniques all 4 years
    + Sites that are not HCC, VAMC, CBOC, or OOS
    + Sites with the phrase "Mobile Clinic" in their name
    + Sites that are missing Gap Metric or Panel Fullness for all 48 months

## Period Initiating PC CRH  

```{r}
analytic_df %>%
  select(sta5a, period_initiating_crh) %>%
  distinct() %>%
  filter(is.na(period_initiating_crh) == F) %>%
  tabyl(period_initiating_crh) %>%
  adorn_totals() %>%
  mutate(percent = percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Period Initiating PC CRH", "Sta5a", "%"),
      full_width = F,
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) 
```

# Site Type  

```{r}
analytic_df %>%
  select(sta5a, s_abbr) %>%
  distinct() %>%
  tabyl(s_abbr) %>%
  adorn_totals() %>%
  mutate(percent = percent(percent, accuracy = 0.1),
         n = comma(n)) %>%
  kbl(col.names = c("Site Type", "n", "%"),
      full_width = F,
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F)
```

# Outcomes  

## Established Patient Wait Time  

```{r}
outcome_fxn = function(outcome, ymax, label){
  bp = ggplot(data = analytic_df,
              aes(x = "a", y = {{outcome}})) +
    geom_boxplot(fill = "skyblue") +
    theme(axis.title.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    scale_y_continuous(limits = c(0, {{ymax}})) +
    labs(y = label)
  #--
  lp = analytic_df %>%
    group_by(sta5a) %>%
    slice_sample(., prop = 0.25) %>%
    ggplot(data = .,
           aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_line(alpha = 0.4) +
    scale_y_continuous(limits = c(0, {{ymax}})) +
    scale_x_date(breaks = "4 months") +
    labs(y = label) +
    theme(axis.text.x = element_text(angle = 270, vjust = 0.3))
  #
  if(str_detect({{label}}, 'Timely|Fullness')){
    plot_grid(bp + scale_y_continuous(labels = percent_format(),
              limits = c(0, {{ymax}})), lp + scale_y_continuous(labels = percent_format(), limits = c(0, {{ymax}})))}
  else {plot_grid(bp, lp)}
}
outcome_fxn(est_pt_wt_pid, 30, "Established Pt Wt (PID)")
```

## New Patient Wait Time  

```{r}
outcome_fxn(new_pt_wt, 50, "New Pt Wt")
```

## Third Next Available  

```{r}
outcome_fxn(tna, 40, "3rd Next Available")
```

## Timely Care  

```{r}
outcome_fxn(tc_pc_success_prop, NA, "Timely Care Success")
```

# Engagement Measures  

## Gap   
### Continuous    
```{r}
outcome_fxn(gap_metric, 2.5, "Gap Metric")
```

### Categorical Sta5a-month  
```{r}
analytic_df %>%
  tabyl(gap_cat) %>%
  adorn_totals() %>%
  mutate(n = comma(n),
         percent = percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Gap Category", "Sta5a-Months", "%"),
      full_width = F,
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F)
```

### Categorical Average  
```{r}
analytic_df %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T)) %>%
  mutate(mean_gap_cat = factor(case_when(
    mean_gap < 1.0 ~ "< 1.0",
    mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0 - 1.2",
    mean_gap > 1.2 ~ "> 1.2",
    TRUE ~ "Missing all Gap Obs."
  ), ordered = TRUE,
  levels = c("< 1.0", "1.0 - 1.2", "> 1.2", "Missing all Gap Obs.")),
  mean_gap_cat = fct_drop(mean_gap_cat)) %>%
  tabyl(mean_gap_cat) %>%
  adorn_totals() %>%
  mutate(n = comma(n),
         percent = percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Gap Category", "Sta5a", "%"),
      full_width = F,
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) 
```

## Panel Fullness  
### Continuous  
```{r}
outcome_fxn(panel_fullness, 1.5, "Panel Fullness")
```

### Categorical Sta5a-month  
```{r}
analytic_df %>%
  tabyl(pf_cat) %>%
  adorn_totals() %>%
  mutate(n = comma(n),
         percent = percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Panel Fullness Category", "Sta5a-Months", "%"),
      full_width = F,
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) 
```

### Categorical Average  
```{r}
analytic_df %>%
  group_by(sta5a) %>%
  summarise(pf_mean = mean(panel_fullness, na.rm = T),
            pf_cat = factor(case_when(
              pf_mean > 1.0 ~ "> 100%",
              pf_mean >= 0.8 & pf_mean <= 1.0 ~ "80% - 100%",
              pf_mean < 0.8 ~ "< 80%",
              TRUE ~ "Missing"
            ),
            ordered = TRUE,
            levels = c("< 80%", "80% - 100%", "> 100%", "Missing"))) %>%
  mutate(pf_cat = fct_drop(pf_cat))%>%
  tabyl(pf_cat) %>%
  adorn_totals() %>%
  mutate(n = comma(n),
         percent = percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Panel Fullness Category", "Sta5a", "%"),
      full_width = F,
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) 
```


## Joint Definition  
### Sta5a-Months  
```{r}
analytic_df %>%
  mutate(joint_def = fct_drop(factor(
    case_when(pf_cat == "> 100%" | gap_cat == "< 1.0" ~ 
                "PF > 100% OR Gap < 1.0",
              pf_cat == "< 80%" | gap_cat == "> 1.2" ~
                "PF < 80% OR Gap > 1.2",
              pf_cat == "80% - 100%" | gap_cat == "1.0 - 1.2" ~
                "PF 80%-100% OR Gap 1.0-1.2",
              TRUE ~ "Missing"),
    ordered = TRUE,
    levels = c("PF > 100% OR Gap < 1.0", "PF 80%-100% OR Gap 1.0-1.2",
               "PF < 80% OR Gap > 1.2", "Missing")
  ))) %>%
  tabyl(joint_def) %>%
  mutate(n = comma(n),
         percent = percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Joint Definition", "Obs.", "%"),
      align = c("l", rep("r", 2))) %>%
  kable_classic("striped")
```

### Average  

```{r}
analytic_df %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            pf_mean = mean(panel_fullness, na.rm = T)) %>%
  mutate(joint_def = fct_drop(factor(
    case_when(pf_mean > 1.0 | mean_gap < 1.0 ~ 
                "PF > 100% OR Gap < 1.0",
              pf_mean < 0.8 | mean_gap > 1.2 ~
                "PF < 80% OR Gap > 1.2",
              (pf_mean >= 0.8 & pf_mean <= 1.0) | 
                (mean_gap <= 1.2 & mean_gap >= 1.0) ~
                "PF 80%-100% OR Gap 1.0-1.2",
              TRUE ~ "Missing"),
    ordered = TRUE,
    levels = c("PF > 100% OR Gap < 1.0", "PF 80%-100% OR Gap 1.0-1.2",
               "PF < 80% OR Gap > 1.2", "Missing")
  ))) %>%
  tabyl(joint_def) %>%
  adorn_totals() %>%
  mutate(percent = percent(percent, accuracy = 0.1),
         n = comma(n)) %>%
  kbl(col.names = c("Joint Definition", "Obs.", "%"),
      align = c("l", rep("r", 2))) %>%
  kable_classic("striped")
```

## Meaningful CRH Use 
### Sta5a-Months  
```{r}
crh_sta5as = analytic_df %>%
  filter(crh_flag == 1) %>%
  select(sta5a) %>%
  distinct() %>%
  pull
#
analytic_df %>%
  filter(sta5a %in% crh_sta5as) %>%
  mutate(joint_def = fct_drop(factor(
    case_when(pf_cat == "> 100%" | gap_cat == "< 1.0" ~ 
                "PF > 100% OR Gap < 1.0",
              pf_cat == "< 80%" | gap_cat == "> 1.2" ~
                "PF < 80% OR Gap > 1.2",
              pf_cat == "80% - 100%" | gap_cat == "1.0 - 1.2" ~
                "PF 80%-100% OR Gap 1.0-1.2",
              TRUE ~ "Missing"),
    ordered = TRUE,
    levels = c("PF > 100% OR Gap < 1.0", "PF 80%-100% OR Gap 1.0-1.2",
               "PF < 80% OR Gap > 1.2", "Missing")
  ))) %>%
  tabyl(joint_def) %>%
  mutate(n = comma(n),
         percent = percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Joint Definition", "Obs.", "%"),
      align = c("l", rep("r", 2))) %>%
  kable_classic("striped")
```

### Average  

```{r}
analytic_df %>%
  filter(sta5a %in% crh_sta5as) %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            pf_mean = mean(panel_fullness, na.rm = T)) %>%
  mutate(joint_def = fct_drop(factor(
    case_when(pf_mean > 1.0 | mean_gap < 1.0 ~ 
                "PF > 100% OR Gap < 1.0",
              pf_mean < 0.8 | mean_gap > 1.2 ~
                "PF < 80% OR Gap > 1.2",
              (pf_mean >= 0.8 & pf_mean <= 1.0) | 
                (mean_gap <= 1.2 & mean_gap >= 1.0) ~
                "PF 80%-100% OR Gap 1.0-1.2",
              TRUE ~ "Missing"),
    ordered = TRUE,
    levels = c("PF > 100% OR Gap < 1.0", "PF 80%-100% OR Gap 1.0-1.2",
               "PF < 80% OR Gap > 1.2", "Missing")
  ))) %>%
  tabyl(joint_def) %>%
  adorn_totals() %>%
  mutate(percent = percent(percent, accuracy = 0.1),
         n = comma(n)) %>%
  kbl(col.names = c("Joint Definition", "Obs.", "%"),
      align = c("l", rep("r", 2))) %>%
  kable_classic("striped")
```

# Confounders  

## Nosos  

* Nosos is measured at the sta5a-month  

```{r}
outcome_fxn(nosos, 2, "Average Nosos")
```

### ADI  

```{r}
covar_fxn = function(covar, label, time, maxval){
  
  hp = analytic_df %>%
    select(sta5a, {{time}}, {{covar}}) %>%
    distinct() %>%
    ggplot(data = .,
           aes(x = {{covar}})) +
    geom_histogram(color = "black") +
    labs(y = "Observations",
         x = label)
  #--
  bp = analytic_df %>%
    select(sta5a, {{time}}, {{covar}}) %>%
    distinct() %>%
    ggplot(data = .,
           aes(y = {{covar}}, x = "a")) +
    geom_boxplot(fill = "darkorchid") +
    theme(axis.title.x = element_blank(),
          axis.ticks.x = element_blank(),
          axis.text.x = element_blank()) +
    labs(y = label)
  #--
  lp = if(time == "fy"){analytic_df %>%
      group_by(sta5a) %>%
      slice_sample(., prop = 0.25) %>%
      mutate(timevar = fy) %>%
      ggplot(data = .,
             aes(x = timevar, y = {{covar}}, group = sta5a)) +
      geom_line(alpha = 0.4) +
      scale_y_continuous(limits = c(0, {{maxval}})) +
      labs(y = label) +
      theme(axis.title.x = element_blank())}
    else{analytic_df %>%
        group_by(sta5a) %>%
        slice_sample(., prop = 0.25) %>%
        mutate(timevar = vssc_month) %>%
        ggplot(data = .,
               aes(x = timevar, y = {{covar}}, group = sta5a)) +
        geom_line(alpha = 0.4) +
        scale_y_continuous(limits = c(0, {{maxval}})) +
        labs(y = label) +
        theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
        scale_x_date(breaks = "4 months")}
  #--
  if(str_detect(label, "Urban|Rural|Prop")){
    plot_grid(
      hp + scale_x_continuous(labels = percent_format(),
                              limits = c(NA, {{maxval}})) +
        scale_y_continuous(labels = comma_format()), 
      bp + scale_y_continuous(labels = percent_format(), 
                              limits = c(NA, {{maxval}})), 
      lp + scale_y_continuous(labels = percent_format(), 
                              limits = c(NA, {{maxval}})))}
  else{plot_grid(
    hp + scale_x_continuous(limits = c(NA, {{maxval}}),
                            labels = comma_format()) +
      scale_y_continuous(labels = comma_format()), 
    bp + scale_y_continuous(limits = c(NA, {{maxval}}),
                            labels = comma_format()), 
    lp + scale_y_continuous(limits = c(NA, {{maxval}}),
                            labels = comma_format()))}
}
#
covar_fxn(adi_natrank_mean, "ADI","fy", NA)
```

### Gender  

```{r}
covar_fxn(prop_male, "Proportion Male", "fy", NA)
```

### Age    

```{r}
covar_fxn(age_jan1_mean, "Average Age", "fy", NA)
```

### URH  

```{r}
covar_fxn(urban_prop, "Urban", "fy", NA)
covar_fxn(rural_prop, "Rural", "fy", NA)
```

### Observed to Expected PC Panel Size Ratio  

```{r}
covar_fxn(obs_exp, "Observed:Expected", "vssc_month", 3)
```

### Uniques in PCMM  

```{r}
covar_fxn(scrssn_count, "Uniques in PCMM", "fy", NA)
```

### Total Primary Care Provider FTE  

```{r}
covar_fxn(pcp_fte_tot, "PCP FTE", "vssc_month", NA)
```

### CRH Primary Care Provider FTE  

```{r}
covar_fxn(pcp_fte_crh, "CRH PCP FTE", "vssc_month", NA)
```

### CRH-Corrected Primary Care Provider FTE  

```{r}
covar_fxn(crh_corr_pcp_fte, "CRH-Corrected PCP FTE", "vssc_month", NA)
```

### Primary Care CC Referral Rate  

* This metric is calculated as $\frac{\text{PC CC Referrals}}{\text{Total PC Encounters}}\times 1,000$
* There are `r sum(analytic_df$pc_cc_refs_per_1k_tot_pc > 1000, na.rm = TRUE)` observations with a value > 1,000

```{r}
covar_fxn(pc_cc_refs_per_1k_tot_pc, "PC CC Referrals per 1,000 Total PC Encounters", "vssc_month", 1000)
```

### Primary Care Staffing Ratio  

* There are `r sum(analytic_df$teamlet_staff_ratio > 10, na.rm = T)` observations with a value > 10

```{r}
covar_fxn(teamlet_staff_ratio, "Core Teamlet Staffing Ratio", "vssc_month",
          10)
```

## CAN  

* Below is the sta5a-month average CAN score of sta5a-fy-specific PCMM ScrSSNs


```{r}
covar_fxn(cHosp_90d_mean, "Mean 90-Day Hospitalization Percentile", "vssc_month", NA)
```

```{r}
covar_fxn(cMort_90d_mean, "Mean 90-Day Mortality Percentile", "vssc_month", NA)
```



## Proportion of patients with a CAN > 95  

```{r}
analytic_df %>%
  select(sta5a, vssc_month, contains("gt95")) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  ggplot(data = .,
         aes(x = value, fill = name)) +
  geom_histogram(color = "black") +
  facet_wrap(~name) +
  theme(legend.position = "none") +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(labels = percent_format(),
                     limits = c(0, 0.2)) +
  labs(y = "Observations",
       x = "Proportion of Patients")
```

## Proportion of patients with a CAN > 90  

```{r}
analytic_df %>%
  select(sta5a, vssc_month, contains("gt90")) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  ggplot(data = .,
         aes(x = value, fill = name)) +
  geom_histogram(color = "black") +
  facet_wrap(~name) +
  theme(legend.position = "none") +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(labels = percent_format(),
                     limits = c(0, 0.4)) +
  labs(y = "Observations",
       x = "Proportion of Patients")
```

## Proportion of patients with a CAN > 80  

```{r}
analytic_df %>%
  select(sta5a, vssc_month, contains("gt80")) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  ggplot(data = .,
         aes(x = value, fill = name)) +
  geom_histogram(color = "black") +
  facet_wrap(~name) +
  theme(legend.position = "none") +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(labels = percent_format(),
                     limits = c(0, 0.6)) +
  labs(y = "Observations",
       x = "Proportion of Patients")
```