---
title: "Modeling PC CRH Engagement"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(cowplot)
library(stargazer)
library(starpolishr)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
```

```{r reading-in}
starting_df = dbGetQuery(oabi_con,
                         "select *
                         from [OABI_myVAAccess].[pccrh_eng].Z_analytic_df") %>%
  filter(always_missing_gap == F & always_missing_pf == F) %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_cat = factor(case_when(
           gap_metric < 1.0 ~ "< 1.0",
           gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
           gap_metric > 1.2 ~ "> 1.2",
           TRUE ~ NA
         )),
         pf_cat = factor(case_when(
           panel_fullness > 1.0 ~ "> 100%",
           panel_fullness >= 0.8 & panel_fullness <= 1.0 ~ "80% - 100%",
           panel_fullness < 0.8 ~ "< 80%",
           TRUE ~ NA
         )),
         pf_cat_85 = factor(case_when(
           panel_fullness > 1.05 ~ "> 105%",
           panel_fullness >= 0.85 & panel_fullness <= 1.05 ~ "85% - 105%",
           panel_fullness < 0.85 ~ "< 85%",
           TRUE ~ NA
         )),
         joint_def = fct_drop(factor(
           case_when(panel_fullness > 1.0 | gap_metric < 1.0 ~ 
                       "Worst Group",
                     panel_fullness < 0.8 | gap_metric > 1.2 ~
                       "Best Group",
                     (panel_fullness >= 0.8 & panel_fullness <= 1.0) | 
                       (gap_metric <= 1.2 & gap_metric >= 1.0) ~
                       "Middle Group",
                     TRUE ~ NA)
         )),
         joint_def2 = fct_drop(factor(
           case_when(panel_fullness > 1.05 | gap_metric < 1.0 ~ 
                       "Worst Group",
                     panel_fullness < 0.85 | gap_metric > 1.2 ~
                       "Best Group",
                     (panel_fullness >= 0.85 & panel_fullness <= 1.05) | 
                       (gap_metric <= 1.2 & gap_metric >= 1.0) ~
                       "Middle Group",
                     TRUE ~ NA)
         )),
         period_initiating_crh = relevel(factor(period_initiating_crh,
                                                ordered = FALSE,
                                                levels = c("Before March 2020", 
                                                           "March to September 2020",
                                                           "After September 2020")),
                                         ref = "Before March 2020"))
#============
pen_rate = dbGetQuery(oabi_con,
                      "select a.* 
                      from [OABI_MyVAAccess].[crh_eval].[B1_crh_penRate] as a
                      left join [OABI_MyVAAccess].pccrh_eng.G_crh_flag as b
                      	on a.sta5a = b.sta5a
                      where crh_encounter_count > 9
                      	and a.crh_month >= b.first_mo_w_mt9_pc_crh") %>%
  mutate(this_month_crh = 1,
         vssc_month = ymd(crh_month)) %>%
  select(sta5a, vssc_month, this_month_crh)
#============
tot_crh_fte_visn = starting_df %>%
  group_by(vssc_month, visn) %>%
  summarise(tot_crh_fte = sum(pcp_fte_crh, na.rm = T))
#
tot_crh_fte_nat = starting_df %>%
  group_by(vssc_month) %>%
  summarise(tot_crh_fte = sum(pcp_fte_crh, na.rm = T))
#------------
prop_crh_fte_in_worst_pf = starting_df %>% 
  filter(is.na(pf_cat_85) == F) %>%
  group_by(vssc_month, visn, pf_cat_85) %>%
  summarise(crh_fte_in_group = sum(pcp_fte_crh, na.rm = T)) %>%
  left_join(., tot_crh_fte_visn) %>%
  mutate(prop_crh_fte_in_worst_pf = crh_fte_in_group / tot_crh_fte) %>%
  filter(pf_cat_85 == "> 105%") %>%
  select(vssc_month, visn, prop_crh_fte_in_worst_pf)
#------------
prop_crh_fte_in_worst_gap = starting_df %>% 
  filter(is.na(gap_cat) == F) %>%
  group_by(vssc_month, visn, gap_cat) %>%
  summarise(crh_fte_in_group = sum(pcp_fte_crh, na.rm = T)) %>%
  left_join(., tot_crh_fte_visn) %>%
  mutate(prop_crh_fte_in_worst_gap = crh_fte_in_group / tot_crh_fte) %>%
  filter(gap_cat == "< 1.0") %>%
  select(vssc_month, visn, prop_crh_fte_in_worst_gap)
#------------
prop_crh_fte_in_worst_joint = starting_df %>% 
  filter(is.na(joint_def2) == F) %>%
  group_by(vssc_month, visn, joint_def2) %>%
  summarise(crh_fte_in_group = sum(pcp_fte_crh, na.rm = T)) %>%
  left_join(., tot_crh_fte_visn) %>%
  mutate(prop_crh_fte_in_worst_joint = crh_fte_in_group / tot_crh_fte) %>%
  filter(joint_def2 == "Worst Group") %>%
  select(vssc_month, visn, prop_crh_fte_in_worst_joint)
#============
treated_after_sep2020 <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month),
         treated_month = if_else(crh_encounter_count > 9, 1, 0)) %>%
  filter(vssc_month > ymd("2020-09-01")) %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    ((last_mo_mt9_pc_crh == 1 | is.na(last_mo_mt9_pc_crh)) 
                                     | (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh))),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit_both = meets_inc_crit,
         meets_inc_crit_fwd = if_else(this_mo_mt9_pc_crh == TRUE & (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh)), 1, 0)
  ) %>%
  filter(meets_inc_crit == 1) %>%
  select(sta5a) %>%
  distinct
#=====

vast = DBI::dbGetQuery(oabi_con,
                       "--
select distinct sta5a = stationno, parent_station = par_sta_no, visn = newvisn, city, st, stationname, urh, s_abbr
from [PACT_CC].[Dim].VAST
where extractdate = '8-16-2022'
	AND s_abbr IN('HCC', 'VAMC', 'MSCBOC', 'PCCBOC', 'OOS')
	AND stationname NOT LIKE '%Mobile Clinic%'
	AND stationno IN(select distinct sta6aid from PACT_CC.Dim.VAST_Historic where snapshotDate = '2022-07-01')") %>%
  mutate(visn = str_pad(visn, width = 2, side = "left", pad = "0"),
         urh_vast = factor(if_else(urh %in% c("R", "H", "I"), "R", "U"),
                           levels = c("R", "U")))
#------------
analytic_df = starting_df %>%
  left_join(., pen_rate) %>%
  left_join(., tot_crh_fte_visn) %>%
  left_join(., prop_crh_fte_in_worst_gap) %>%
  left_join(., prop_crh_fte_in_worst_pf) %>%
  left_join(., prop_crh_fte_in_worst_joint) %>%
  left_join(., vast %>%
              select(sta5a, urh_vast)) %>%
  mutate(pc_cc_refs_per_1k_tot_pc = replace_na(pc_cc_refs_per_1k_tot_pc, 0),
         joint_def2 = relevel(joint_def, ref = "Best Group"),
         pf_cat = relevel(pf_cat, ref = "< 80%"),
         gap_cat = relevel(gap_cat, ref = "> 1.2"),
         tc_pc_success_pct = tc_pc_success_prop * 100,
         crh_flag = relevel(factor(crh_flag), ref = "0"),
         scrssn_count_cat = relevel(factor(scrssn_count_cat, ordered = FALSE), ref = "450-2,399"),
         male_pct = prop_male * 100,
         visn = relevel(factor(visn), ref = "06"),
         cHosp_90d_gt90_pct = cHosp_90d_gt90_prop * 100,
         this_month_crh = replace_na(this_month_crh, 0),
         this_month_crh = relevel(factor(this_month_crh), ref = "0"),
         period_initiating_crh = relevel(factor(
           if_else(is.na(period_initiating_crh), "Never Initiated CRH", period_initiating_crh)),
           ref = "Never Initiated CRH"),
         crh_fte_prop = pcp_fte_crh / tot_crh_fte,
         crh_fte_pct = crh_fte_prop * 100,
         treated_ever = if_else(sta5a %in% treated_after_sep2020$sta5a, 1, 0))
#
est_75 = quantile(analytic_df$est_pt_wt_pid, 0.75, na.rm = T)
est_95 = quantile(analytic_df$est_pt_wt_pid, 0.95, na.rm = T)
est_99 = quantile(analytic_df$est_pt_wt_pid, 0.99, na.rm = T)
new_95 = quantile(analytic_df$new_pt_wt, 0.95, na.rm = T)
new_99 = quantile(analytic_df$new_pt_wt, 0.99, na.rm = T)
tna_99 = quantile(analytic_df$tna, 0.99, na.rm = T)
```


# Front Matter  

* This is an iteration of modeling access metrics as a function of:
    + PC CRH (binary)
    + Rurality
    + PC CRH Engagement metric
      + VISN-level
      + Percent of PC CRH FTE in worst category
* This model allows:
    + A correlated random intercept and slope for sta5a
    + A random intercept for VISN
* I log-transformed the outcomes. All of the regression summary table estimates have been exponentiated back to the appropriate scale

```{r}
lm_df = analytic_df %>%
  mutate(est_pt_wt_lim = if_else(est_pt_wt_pid > est_99, est_99, est_pt_wt_pid),
         new_pt_wt_lim = if_else(new_pt_wt > new_99, new_99, new_pt_wt),
         tna_lim = if_else(tna > tna_99, tna_99, tna),
         est_pt_wt_log = log(est_pt_wt_pid),
         est_pt_wt_exp = exp(est_pt_wt_pid),
         new_pt_wt_log = log(new_pt_wt),
         tna_log = log(tna),
         pct_crh_fte_in_worst_gap = prop_crh_fte_in_worst_gap * 100,
         pct_crh_fte_in_worst_pf = prop_crh_fte_in_worst_pf * 100,
         pct_crh_fte_in_worst_joint = prop_crh_fte_in_worst_joint * 100) %>%
  filter(is.infinite(est_pt_wt_log) == F)
  
#
lmer_fxn = function(outcome, exposure){
  exposure_visn = if(exposure == "gap_cat"){"pct_crh_fte_in_worst_gap"}
    else if(exposure == "pf_cat"){"pct_crh_fte_in_worst_pf"}
    else{"pct_crh_fte_in_worst_joint"}
  #
  fmla = as.formula(
    paste0({{outcome}}, " ~ this_month_crh + urh_vast + ",
           {{exposure_visn}},
           " + (1 + ", {{exposure_visn}}, " | sta5a)",#correlated random intercept and slope 
           " + (1 | visn)")#random intercept for visn
  )
  lmerTest::lmer(fmla,
       data = lm_df)
}
```


# Established Patient Wait Time  

## Distribution  

* Below are the original established patient wait time and the log-transformed established patient wait time  

```{r}
p1 = analytic_df %>%
  ggplot(data = .,
       aes(x = est_pt_wt_pid)) +
  geom_histogram(bins = 100,
                 color = "black") +
  scale_y_continuous(labels = comma_format())+
  labs(x = "Established Patient Wait Time",
       y = "Observations")

p2 = lm_df %>%
  ggplot(data = .,
       aes(x = est_pt_wt_log)) +
  geom_histogram(bins = 100,
                 color = "black") +
  scale_y_continuous(labels = comma_format())+
  labs(x = "log(Established Patient Wait Time)",
       y = "Observations")
#--
cowplot::plot_grid(p1, p2)
```

## Gap Category  

```{r}
est_gap = lmer_fxn("est_pt_wt_log", "gap_cat")
#
predictmeans::residplot(est_gap)
#
tab_model(est_gap, transform = "exp", digits = 4)
```

## Panel Fullness Category  

```{r}
est_pf = lmer_fxn("est_pt_wt_log", "pf_cat_85")
#
predictmeans::residplot(est_pf)
#
tab_model(est_pf, transform = "exp", digits = 4)
```

## Joint Definition Category  

```{r}
est_joint = lmer_fxn("est_pt_wt_log", "joint_def2")
#
predictmeans::residplot(est_joint)
#
tab_model(est_joint, transform = "exp", digits = 4)
```