---
title: "Outcomes X Exposure & Covariates"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(cowplot)
library(stargazer)
library(starpolishr)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
```

```{r reading-in}
starting_df = dbGetQuery(oabi_con,
                         "select *
                         from [OABI_myVAAccess].[pccrh_eng].Z_analytic_df") %>%
  filter(always_missing_gap == F & always_missing_pf == F) %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_cat = factor(case_when(
           gap_metric < 1.0 ~ "< 1.0",
           gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
           gap_metric > 1.2 ~ "> 1.2",
           TRUE ~ "Missing"
         )),
         pf_cat = factor(case_when(
           panel_fullness > 1.0 ~ "> 100%",
           panel_fullness >= 0.8 & panel_fullness <= 1.0 ~ "80% - 100%",
           panel_fullness < 0.8 ~ "< 80%",
           TRUE ~ "Missing"
         )),
         joint_def = fct_drop(factor(
           case_when(panel_fullness > 1.0 | gap_metric < 1.0 ~ 
                       "PF > 100% OR Gap < 1.0",
                     panel_fullness < 0.8 | gap_metric > 1.2 ~
                       "PF < 80% OR Gap > 1.2",
                     (panel_fullness >= 0.8 & panel_fullness <= 1.0) | 
                       (gap_metric <= 1.2 & gap_metric >= 1.0) ~
                       "PF 80%-100% OR Gap 1.0-1.2",
                     TRUE ~ "Missing")
         )),
         period_initiating_crh = factor(period_initiating_crh,
                                        ordered = TRUE,
                                        levels = c("Before March 2020", 
                                                   "March to September 2020",
                                                   "After September 2020")))
#===========
pf_avg = starting_df %>%
  group_by(sta5a) %>%
  summarise(pf_mean = mean(panel_fullness, na.rm = T),
            pf_cat_mean = factor(case_when(
              pf_mean > 1.0 ~ "> 100%",
              pf_mean >= 0.8 & pf_mean <= 1.0 ~ "80% - 100%",
              pf_mean < 0.8 ~ "< 80%",
              TRUE ~ "Missing"
            ))) %>%
  select(sta5a, pf_cat_mean)
#===========
gap_avg = starting_df %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T)) %>%
  mutate(gap_cat_mean = factor(case_when(
    mean_gap < 1.0 ~ "< 1.0",
    mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0 - 1.2",
    mean_gap > 1.2 ~ "> 1.2",
    TRUE ~ "Missing all Gap Obs."
  )),
  gap_cat_mean = fct_drop(gap_cat_mean)) %>%
  select(sta5a, gap_cat_mean)
#===========
joint_def_avg = starting_df %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            pf_mean = mean(panel_fullness, na.rm = T)) %>%
  mutate(joint_def_mean = fct_drop(factor(
    case_when(pf_mean > 1.0 | mean_gap < 1.0 ~ 
                "PF > 100% OR Gap < 1.0",
              pf_mean < 0.8 | mean_gap > 1.2 ~
                "PF < 80% OR Gap > 1.2",
              (pf_mean >= 0.8 & pf_mean <= 1.0) | 
                (mean_gap <= 1.2 & mean_gap >= 1.0) ~
                "PF 80%-100% OR Gap 1.0-1.2",
              TRUE ~ "Missing")
  ))) %>%
  select(sta5a, joint_def_mean)
#------------
analytic_df = starting_df %>%
  left_join(., gap_avg) %>%
  left_join(., pf_avg) %>%
  left_join(., joint_def_avg)
#
analytic_df = analytic_df %>%
  mutate(joint_def_mean = relevel(joint_def_mean, ref = "PF < 80% OR Gap > 1.2"),
         pf_cat_mean = relevel(pf_cat_mean, ref = "< 80%"),
         gap_cat_mean = relevel(gap_cat_mean, ref = "> 1.2"),
         joint_def = relevel(joint_def, ref = "PF < 80% OR Gap > 1.2"),
         pf_cat = relevel(pf_cat, ref = "< 80%"),
         gap_cat = relevel(gap_cat, ref = "> 1.2"),
         tc_pc_success_pct = tc_pc_success_prop * 100)
#
vast = DBI::dbGetQuery(oabi_con,
                       "--
select distinct sta5a = stationno, parent_station = par_sta_no, visn = newvisn, city, st, stationname, s_abbr
from [PACT_CC].[Dim].VAST
where extractdate = '8-16-2022'
	AND s_abbr IN('HCC', 'VAMC', 'MSCBOC', 'PCCBOC', 'OOS')
	AND stationname NOT LIKE '%Mobile Clinic%'
	AND stationno IN(select distinct sta6aid from PACT_CC.Dim.VAST_Historic where snapshotDate = '2022-07-01')") %>%
  filter(sta5a %in% analytic_df$sta5a) %>%
  mutate(visn = str_pad(visn, width = 2, side = "left", pad = "0"))
```

# Exposure(s) X Outcomes  

```{r}
corr = cor(analytic_df[c("panel_fullness", "gap_metric", "est_pt_wt_pid", "new_pt_wt", "tna", "tc_pc_success_pct")],
           use = "pairwise.complete.obs")
corr_p = corr %>% rstatix::cor_get_pval()
#
ggcorrplot::ggcorrplot(corr,
                       hc.order = FALSE,
                       type = "lower",
                       show.legend = FALSE,
                       lab = TRUE,
                       lab_size = 8,
                       tl.cex = 25,
                       p.mat = corr_p)

```

## Exposure allowed to vary   
<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### Established Patient Wait Time  
</div>

```{r, results = 'asis'}
outcome_fxn = function(outcome, label){
  pf_fmla = as.formula(paste0({{outcome}}, " ~ pf_cat"))
  gap_fmla = as.formula(paste0({{outcome}}, " ~ gap_cat"))
  joint_fmla = as.formula(paste0({{outcome}}, " ~ joint_def"))
  #--
  pf_lm = analytic_df %>%
    filter(pf_cat != "Missing") %>%
    lm(pf_fmla, data = .)
  gap_lm = analytic_df %>%
    filter(gap_cat != "Missing") %>%
    lm(gap_fmla, data = .)
  joint_lm = analytic_df %>%
    filter(joint_def != "Missing") %>%
    lm(joint_fmla, data = .)
  #
  stargazer::stargazer(pf_lm, gap_lm, joint_lm,
                       type = "html",
                       intercept.top = TRUE,
                       intercept.bottom = FALSE,
                       digits = 2,
                       single.row = TRUE,
                       dep.var.caption = "",
                       covariate.labels = c(
                         "<strong>Intercept</strong>",
                         "<strong>Panel Fullness</strong> > 100%",
                         "<strong>Panel Fullness</strong> 80% - 100%",
                         "<strong>Gap</strong> < 1.0",
                         "<strong>Gap</strong> 1.0-1.2",
                         "<strong>Panel Fullness</strong> > 100% OR <strong>Gap</strong> < 1.0",
                         "<strong>Panel Fullness</strong> 80%-100% OR <strong>Gap</strong> 1.0-1.2"
                       ), 
                       dep.var.labels = {{label}})
}
#
outcome_fxn("est_pt_wt_pid", "Established Patient Wait Time")
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### New Patient Wait Time  
</div>

```{r, results = 'asis'}
outcome_fxn("new_pt_wt", "New Patient Wait Time")
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### Third Next Available  
</div>

```{r, results = 'asis'}
outcome_fxn("tna", "Third Next Available")
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### Timely Care    
</div>

```{r, results = 'asis'}
outcome_fxn("tc_pc_success_pct", "Timely Care Success %")
```

## Sta5a-Average Exposure   
<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### Established Patient Wait Time 
</div>

```{r, results = 'asis'}
outcome_X_mean_fxn = function(outcome, label){
  pf_fmla = as.formula(paste0({{outcome}}, " ~ pf_cat_mean"))
  gap_fmla = as.formula(paste0({{outcome}}, " ~ gap_cat_mean"))
  joint_fmla = as.formula(paste0({{outcome}}, " ~ joint_def_mean"))
  #--
  pf_lm = lm(pf_fmla, data = analytic_df)
  gap_lm = lm(gap_fmla, data = analytic_df)
  joint_lm = lm(joint_fmla, data = analytic_df)
  #
  stargazer::stargazer(pf_lm, gap_lm, joint_lm,
                       type = "html",
                       intercept.top = TRUE,
                       intercept.bottom = FALSE,
                       single.row = TRUE,
                       dep.var.caption = "",
                       digits = 2,
                       covariate.labels = c(
                         "<strong>Intercept</strong>",
                         "<strong>Panel Fullness</strong> > 100%",
                         "<strong>Panel Fullness</strong> 80% - 100%",
                         "<strong>Gap</strong> < 1.0",
                         "<strong>Gap</strong> 1.0-1.2",
                         "<strong>Panel Fullness</strong> > 100% OR <strong>Gap</strong> < 1.0",
                         "<strong>Panel Fullness</strong> 80%-100% OR <strong>Gap</strong> 1.0-1.2"
                       ), 
                       dep.var.labels = {{label}})
}
#
outcome_X_mean_fxn("est_pt_wt_pid", "Established Patient Wait Time")
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### New Patient Wait Time  
</div>

```{r, results = 'asis'}
outcome_X_mean_fxn("new_pt_wt", "New Patient Wait Time")
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### Third Next Available 
</div>

```{r, results = 'asis'}
outcome_X_mean_fxn("tna", "Third Next Available")
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 3px;}
</style>
<div class = "blue">
### Timely Care    
</div>

```{r, results = 'asis'}
outcome_X_mean_fxn("tc_pc_success_pct", "Timely Care Success %")
```


# Outcome(s) X Covariates   

```{r}
corr_df = analytic_df %>%
  select(est_pt_wt_pid, new_pt_wt, tna, tc_pc_success_pct, pcp_fte_crh, crh_corr_pcp_fte, gap_metric, nosos,
         cMort_90d_mean, cHosp_90d_mean, adi_natrank_mean, 
         panel_fullness, teamlet_staff_ratio, scrssn_count_mean, 
         pc_crh_per_1k_total_pc, pc_cc_refs_per_1k_tot_pc, age_jan1_mean,
         prop_male, urban_prop)
#
corr1 = corr_df %>% rstatix::cor_mat()
corr1_p = corr1 %>% rstatix::cor_get_pval()
#
ggcorrplot::ggcorrplot(corr1,
                       type = "lower",
                       lab = TRUE,
                       lab_size = 5,
                       tl.cex = 15,
                       show.legend = FALSE,
                       digits = 1,
                       p.mat = corr1_p,
                       sig.level = 0.01)
```