---
title: "PC CRH Engagement: Linear Models"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(cowplot)
library(stargazer)
library(starpolishr)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
```

```{r reading-in}
starting_df = dbGetQuery(oabi_con,
                         "select *
                         from [OABI_myVAAccess].[pccrh_eng].Z_analytic_df") %>%
  filter(always_missing_gap == F & always_missing_pf == F) %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_cat = factor(case_when(
           gap_metric < 1.0 ~ "< 1.0",
           gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
           gap_metric > 1.2 ~ "> 1.2",
           TRUE ~ NA
         )),
         pf_cat = factor(case_when(
           panel_fullness > 1.0 ~ "> 100%",
           panel_fullness >= 0.8 & panel_fullness <= 1.0 ~ "80% - 100%",
           panel_fullness < 0.8 ~ "< 80%",
           TRUE ~ NA
         )),
         joint_def = fct_drop(factor(
           case_when(panel_fullness > 1.0 | gap_metric < 1.0 ~ 
                       "PF > 100% OR Gap < 1.0",
                     panel_fullness < 0.8 | gap_metric > 1.2 ~
                       "PF < 80% OR Gap > 1.2",
                     (panel_fullness >= 0.8 & panel_fullness <= 1.0) | 
                       (gap_metric <= 1.2 & gap_metric >= 1.0) ~
                       "PF 80%-100% OR Gap 1.0-1.2",
                     TRUE ~ NA)
         )),
         period_initiating_crh = relevel(factor(period_initiating_crh,
                                                ordered = FALSE,
                                                levels = c("Before March 2020", 
                                                           "March to September 2020",
                                                           "After September 2020")),
                                         ref = "Before March 2020"))
#===========
pf_avg = starting_df %>%
  group_by(sta5a) %>%
  summarise(pf_mean = mean(panel_fullness, na.rm = T),
            pf_cat_mean = factor(case_when(
              pf_mean > 1.0 ~ "> 100%",
              pf_mean >= 0.8 & pf_mean <= 1.0 ~ "80% - 100%",
              pf_mean < 0.8 ~ "< 80%",
              TRUE ~ "Missing"
            ))) %>%
  select(sta5a, pf_cat_mean)
#===========
gap_avg = starting_df %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T)) %>%
  mutate(gap_cat_mean = factor(case_when(
    mean_gap < 1.0 ~ "< 1.0",
    mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0 - 1.2",
    mean_gap > 1.2 ~ "> 1.2",
    TRUE ~ "Missing all Gap Obs."
  )),
  gap_cat_mean = fct_drop(gap_cat_mean)) %>%
  select(sta5a, gap_cat_mean)
#===========
joint_def_avg = starting_df %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            pf_mean = mean(panel_fullness, na.rm = T)) %>%
  mutate(joint_def_mean = fct_drop(factor(
    case_when(pf_mean > 1.0 | mean_gap < 1.0 ~ 
                "PF > 100% OR Gap < 1.0",
              pf_mean < 0.8 | mean_gap > 1.2 ~
                "PF < 80% OR Gap > 1.2",
              (pf_mean >= 0.8 & pf_mean <= 1.0) | 
                (mean_gap <= 1.2 & mean_gap >= 1.0) ~
                "PF 80%-100% OR Gap 1.0-1.2",
              TRUE ~ "Missing")
  ))) %>%
  select(sta5a, joint_def_mean)
#============
pen_rate = dbGetQuery(oabi_con,
                      "select a.* 
                      from [OABI_MyVAAccess].[crh_eval].[B1_crh_penRate] as a
                      left join [OABI_MyVAAccess].pccrh_eng.G_crh_flag as b
                      	on a.sta5a = b.sta5a
                      where crh_encounter_count > 9
                      	and a.crh_month >= b.first_mo_w_mt9_pc_crh") %>%
  mutate(this_month_crh = 1,
         vssc_month = ymd(crh_month)) %>%
  select(sta5a, vssc_month, this_month_crh)
#============
tot_crh_fte_visn = starting_df %>%
  group_by(vssc_month, visn) %>%
  summarise(tot_crh_fte = sum(pcp_fte_crh, na.rm = T))
#------------
analytic_df = starting_df %>%
  left_join(., gap_avg) %>%
  left_join(., pf_avg) %>%
  left_join(., joint_def_avg) %>%
  left_join(., pen_rate) %>%
  left_join(., tot_crh_fte_visn) %>%
  mutate(pc_cc_refs_per_1k_tot_pc = replace_na(pc_cc_refs_per_1k_tot_pc, 0),
         joint_def_mean = relevel(joint_def_mean, ref = "PF < 80% OR Gap > 1.2"),
         pf_cat_mean = relevel(pf_cat_mean, ref = "< 80%"),
         gap_cat_mean = relevel(gap_cat_mean, ref = "> 1.2"),
         joint_def = relevel(joint_def, ref = "PF < 80% OR Gap > 1.2"),
         pf_cat = relevel(pf_cat, ref = "< 80%"),
         gap_cat = relevel(gap_cat, ref = "> 1.2"),
         tc_pc_success_pct = tc_pc_success_prop * 100,
         crh_flag = relevel(factor(crh_flag), ref = "0"),
         scrssn_count_cat = relevel(factor(scrssn_count_cat, ordered = FALSE), ref = "450-2,399"),
         male_pct = prop_male * 100,
         visn = relevel(factor(visn), ref = "06"),
         cHosp_90d_gt90_pct = cHosp_90d_gt90_prop * 100,
         this_month_crh = replace_na(this_month_crh, 0),
         this_month_crh = relevel(factor(this_month_crh), ref = "0"),
         period_initiating_crh = relevel(factor(
           if_else(is.na(period_initiating_crh), "Never Initiated CRH", period_initiating_crh)),
           ref = "Never Initiated CRH"),
         crh_fte_prop = pcp_fte_crh / tot_crh_fte,
         crh_fte_pct = crh_fte_prop * 100)
#
vast = DBI::dbGetQuery(oabi_con,
                       "--
select distinct sta5a = stationno, parent_station = par_sta_no, visn = newvisn, city, st, stationname, s_abbr
from [PACT_CC].[Dim].VAST
where extractdate = '8-16-2022'
	AND s_abbr IN('HCC', 'VAMC', 'MSCBOC', 'PCCBOC', 'OOS')
	AND stationname NOT LIKE '%Mobile Clinic%'
	AND stationno IN(select distinct sta6aid from PACT_CC.Dim.VAST_Historic where snapshotDate = '2022-07-01')") %>%
  filter(sta5a %in% analytic_df$sta5a) %>%
  mutate(visn = str_pad(visn, width = 2, side = "left", pad = "0"))
```

# Tables  
## Gap  
```{r}
analytic_df %>%
  filter(is.na(gap_cat) == F) %>%
  mutate(gap_cat = factor(gap_cat,
                          ordered = TRUE,
                          levels = c("< 1.0", "1.0 - 1.2", "> 1.2"))) %>%
  group_by(gap_cat) %>%
  tally() %>%
  adorn_percentages("col") %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  adorn_ns("front") %>%
  kbl(col.names = c("Gap Category", "N (%)"),
      align = c("l", "r")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(c(0, 4), bold = TRUE)
```

## Panel Fullness    
```{r}
analytic_df %>%
  filter(is.na(pf_cat) == F) %>%
  mutate(pf_cat = factor(pf_cat,
                          ordered = TRUE,
                          levels = c("< 80%", "80% - 100%", "> 100%"))) %>%
  group_by(pf_cat) %>%
  tally() %>%
  adorn_percentages("col") %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  adorn_ns("front") %>%
  kbl(col.names = c("Panel Fullness Category", "N (%)"),
      align = c("l", "r")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(c(0, 4), bold = TRUE)
```

# Linear Regression Models    

```{r}
lm_fxn2 = function(outcome, label){
  covar_list = " + nosos + adi_natrank_mean + scrssn_count_cat + pc_cc_refs_per_1k_tot_pc + age_jan1_mean + male_pct + urban_prop + visn + (1 | sta5a)"
  #
  gap_fmla = as.formula(paste0({{outcome}}, " ~ gap_cat + this_month_crh", covar_list))
  #
  pf_fmla = as.formula(paste0({{outcome}}, " ~ pf_cat + this_month_crh", covar_list))
  #
  joint_fmla = as.formula(paste0({{outcome}}, " ~ joint_def + this_month_crh", covar_list))
  #making both have the same number of observations for comparing by AIC/BIC
  analytic_df = analytic_df %>%
    filter(is.na(gap_cat) == F & is.na(pf_cat) == F)
  #
  gap_lm = lmer(gap_fmla,
                  data = analytic_df)
  #
  pf_lm = lmer(pf_fmla,
                  data = analytic_df)
  #
  joint_lm = lmer(joint_fmla,
                  data = analytic_df)
  #
  stargazer(gap_lm, pf_lm, joint_lm,
                       type = "html",
                       intercept.top = TRUE,
                       intercept.bottom = FALSE,
                       digits = 2,
                       single.row = TRUE,
                       dep.var.caption = "",
                       covariate.labels = c(
                         "<strong>Intercept</strong>",
                         "<strong>Gap Category</strong> < 1.0",
                         "<strong>Gap Category</strong> 1.0 - 1.2",
                         "<strong>Panel Fullness Category</strong> > 100%",
                         "<strong>Panel Fullness Category</strong> 80% - 100%",
                         "<strong>Panel Fullness</strong> > 100% OR <strong>Gap</strong> < 1.0",
                         "<strong>Panel Fullness</strong> 80%-100% OR <strong>Gap</strong> 1.0-1.2",
                         "This Month Met PC CRH Criteria (vs. Didn't)",
                         "Nosos",
                         "ADI",
                         "Uniques: 10,000+",
                         "Uniques: 2,400-9,999",
                         "PC CC Referral Rate",
                         "Age",
                         "Male %",
                         "Urban %"
                       ), 
                       dep.var.labels = {{label}})
}
#--


#
```

## Time-Varying CRH Indicator  
* The analyses below use an indicator for whether each month: 
    + Met the 10-or-more PC CRH criterion
    + Occurred on or after the first month meeting that criterion 

<style>
div.green { background-color:#6aff00; border-radius: 3px;}
</style>
<div class = "green">
### Established Patient Wait Time  
</div>

```{r, results = 'asis'}
lm_fxn2("est_pt_wt_pid", "Established Patient Wait Time")
```

<style>
div.green { background-color:#6aff00; border-radius: 3px;}
</style>
<div class = "green">
### New Patient Wait Time  
</div>

```{r, results = 'asis'}
lm_fxn2("new_pt_wt", "New Patient Wait Time")
```

<style>
div.green { background-color:#6aff00; border-radius: 3px;}
</style>
<div class = "green">
### Third Next Available    
</div>

```{r, results = 'asis'}
lm_fxn2("tna", "Third Next Available")
```

<style>
div.green { background-color:#6aff00; border-radius: 3px;}
</style>
<div class = "green">
### Timely Care      
</div>

```{r, results = 'asis'}
lm_fxn2("tc_pc_success_pct", "Timely Care Success %")
```