---
title: "VISN 23 - CRH Encounters Over Time"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = TRUE,
                      fig.width = 12, fig.height = 12)

library(tidyverse)
library(readxl)
library(ggplot2)
library(ggthemes)
library(kableExtra)
library(lubridate)
library(scales)
library(grid)
library(DT)
library(RODBC)
library(DBI)
library(janitor)
library(here)
#
source(here("Input", "Functions", "customFacetWrap.R"))
#
options(scipen = 999)
###
`%ni%` <- negate(`%in%`)
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Truested_Connection = "true")
#=============
theme_update(
  strip.text = element_text(size = 20),
  axis.text = element_text(size = 15),
  axis.title.y = element_text(size = 18),
  axis.title.x = element_blank(),
  axis.text.x = element_text(angle = 270, hjust = 0, vjust = 0.3),
  legend.text = element_text(size = 14),
  plot.title = element_text(size = 20),
  legend.title = element_blank()
)
```

```{r reading-in}
access_metrics_sta5a <- read_csv(here("Input", "Data", "pc_access_metrics.csv")) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop)
#
access_metrics_parent <- read_csv(here("Input", "Data", "pc_access_metrics_parent.csv")) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop)
#
access_metrics_visn <- read_csv(here("Input", "Data", "pc_access_metrics_visn.csv")) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop)
#
access_metrics_nat <- read_csv(here("Input", "Data", "pc_access_metrics_nat.csv")) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop)
#
vast <- read_csv(here("Input","Data","VAST_from_A06_11jan21.csv"))
#
crh_encounters <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].crh_encounters_deDup") %>%
  mutate(crh_month = ymd(crh_month)) %>%
  filter(crh_month > ymd("2019-09-01"))
#
stopCodes <- crh_encounters %>% 
  select(stopCode = location_primary_sc, stopCodeName = primarystopcodelocationname) %>% 
  distinct %>%
  bind_rows(., crh_encounters %>% 
              select(stopCode = location_secondary_sc, stopCodeName = secondarystopcodelocationname) %>% distinct) %>%
  distinct
```

# Access Metrics  
## National  
```{r}
access_metrics_nat %>%
  pivot_longer(-vssc_month) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(2,3))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```


---

## VISN 23     
```{r}
access_metrics_visn %>% filter(visn == "23") %>%
  pivot_longer(-c(vssc_month, visn)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(2,3))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (618) Minneapolis, MN           
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "618") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(2,4))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (568) Fort Meade, SD         
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "568") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(2,4))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (438) Sioux Falls, SD         
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "438") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(1.5, 3))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (636) Omaha, NE         
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "636") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(1.5, 3))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (636A6) Des Moines, IA          
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "636A6") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(1.5, 3))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (636A8) Iowa City, IA          
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "636A8") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0, 65))),
                      scale_override(2, scale_y_continuous(limits = c(0, 65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(3, 3.5), breaks = c(3, 3.25, 3.5))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0, 1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (656) St. Cloud, MN            
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "656") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1))),
                      scale_override(4, scale_y_continuous(limits = c(2,3.5))),
                      scale_override(5, scale_y_continuous(limits = c(0.25, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```

---

## VISN 23 - Parent Station (437) Fargo, ND            
```{r}
#vast %>% filter(visn == 23) %>% select(parent_station_sta5a) %>% distinct()
#
access_metrics_parent %>% filter(sta5a == "437") %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name_lab = case_when(name == "established_pt_waitTime" ~ "Est. Patient Wait Time",
                              name == "new_pt_waitTime" ~ "New Patient Wait Time",
                              name == "obs_expected_panel_size_ratio" ~ "Obs:Exp Panel Ratio",
                              name == "pc_staff_ratio" ~ "PC Staff Ratio",
                              name == "same_day_appts_wPC_provider_ratio" ~ "Same-day Appts. w/PC",
                              name == "tc_pc_success_prop" ~ "PC TimelyCare Success %")) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap_custom(~name_lab, scales = "free",
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0,65))),
                      scale_override(2, scale_y_continuous(limits = c(0,65))),
                      scale_override(3, scale_y_continuous(limits = c(0.5, 1.1))),
                      scale_override(4, scale_y_continuous(limits = c(2, 3.5))),
                      scale_override(5, scale_y_continuous(limits = c(0.5, 1), labels = scales::percent_format())),
                      scale_override(6, scale_y_continuous(limits = c(0,1)))
                    )) +
  theme(legend.position = "none", 
        axis.title.y = element_blank())
```


# CRH Encounters  
## National  
```{r}
crh_encounters_nat <- crh_encounters %>%
  filter(care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n())
#
crh_encounters %>%
  filter(care_type %ni% c("Missing crh")) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  group_by(fy_qtr) %>%
  summarise(count = n()) %>%
  adorn_totals() %>%
  kbl(col.names = c("FY-Qtr", "CRH Encounters")) %>%
  kable_classic()
#--
ggplot(data = crh_encounters_nat,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#--==
crh_encounters_type_nat <- crh_encounters %>%
  filter(care_type %ni% c("Missing crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  mutate(care_type = str_remove(care_type, " crh"))
#
crh_encounters %>%
  filter(care_type %ni% c("Missing crh")) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  group_by(fy_qtr, care_type) %>%
  summarise(count = n()) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  pivot_wider(names_from = care_type, values_from = count) %>%
  adorn_totals() %>%
  kbl(col.names = c("FY-Qtr", "Mental Health", "PCMHI", "Pharmacy", "Primary Care", "Specialty")) %>%
  kable_classic()
#
ggplot(data = crh_encounters_type_nat,
       aes(x = crh_month, y = count, group = care_type, color = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  facet_wrap(~care_type) +
  theme(legend.position = "none")
  
```

## VISN 23  
```{r}
crh_v23_tot <- crh_encounters %>%
  filter(parent_visn == 23 & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n())
#
ggplot(data = crh_v23_tot,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#--
crh_v23_type <- crh_encounters %>%
  filter(parent_visn == 23 & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  mutate(care_type = str_remove(care_type, " crh"))
#
crh_encounters %>%
  filter(parent_visn == 23 & care_type == "Specialty crh") %>%
  group_by(psc_joined) %>%
  summarise(count = n()) %>%
  left_join(., stopCodes, by = c("psc_joined" = "stopCode")) %>%
  select(psc_joined, stopCodeName, count) %>%
  arrange(desc(count)) %>%
  slice_head(n = 7) %>%
  kbl(col.names = c("Primary Stop Code", "Stop Code Name", "Count")) %>%
  kable_classic()
#
ggplot(data = crh_v23_type,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  facet_wrap(~care_type) +
  theme(legend.position = "none")
```

## VISN 23 - Parent Station (618) Minneapolis, MN  
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "618" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "618" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month, care_type) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```

## VISN 23 - Parent Station (568) Fort Meade, SD    
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "568" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "568" & care_type %ni% c("Missing crh")) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```

## VISN 23 - Parent Station (438) Sioux Falls, SD     
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "438" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "438" & care_type %ni% c("Missing crh")) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```

## VISN 23 - Parent Station (636) Omaha, NE      
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "636" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "636" & care_type %ni% c("Missing crh")) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```

## VISN 23 - Parent Station (636A6) Des Moines, IA      
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "636A6" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "636A6" & care_type %ni% c("Missing crh")) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```

## VISN 23 - Parent Station (636A8) Iowa City, IA      
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "636A8" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "636A8" & care_type %ni% c("Missing crh")) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```

## VISN 23 - Parent Station (656) St. Cloud, MN      
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "656" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "656" & care_type %ni% c("Missing crh")) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```

## VISN 23 - Parent Station (437) Fargo, ND      
```{r}
crh_encounters %>%
  filter(parent_station_sta5a == "437" & care_type %ni% c("Missing crh")) %>%
  group_by(crh_month) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count)) +
  geom_line(size = 1, color = "red") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month")
#---
crh_encounters %>%
  filter(parent_station_sta5a == "437" & care_type %ni% c("Missing crh")) %>%
  mutate(care_type = str_remove(care_type, " crh")) %>%
  group_by(crh_month, care_type) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
       aes(x = crh_month, y = count, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), 
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per Month") +
  theme(legend.position = "none") +
  facet_wrap(~care_type)

```