---
title: "\"New\" PC CRH Inclusion Criteria"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 12, fig.height = 12)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
##---------- Connection to PACT_CC
pactcc_con <- dbConnect(odbc::odbc(),
                        Driver = "SQL Server",
                        Server = "vhacdwsql13.vha.med.va.gov",
                        Database = "PACT_CC",
                        Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#---
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#=========================
# VAST
vast <- read_csv(here("Input", "Data", "vast_from_a06.csv")) %>%
  filter(is.na(s_abbr) == F) %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count < 450 ~ "< 450",
    scrssn_count >= 450 & scrssn_count < 2500 ~ "450 - 2,499",
    scrssn_count >= 2500 & scrssn_count < 10000 ~ "2,500 - 9,999",
    scrssn_count >= 10000 ~ "10,000+",
    TRUE ~ "Missing"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,499", "2,500 - 9,999", "10,000+", "Missing")))
#----
# crh flags
crh_flags <- dbGetQuery(oabi_con,
                        "select * from [crh_eval].yoon_flag")
#
pen_rate_subset <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].crh_penRate_month") %>%
  inner_join(., vast) %>%
  inner_join(., crh_flags %>% filter(yoon_10_flag == 0 & yoon_5_flag == 1)) %>%
  group_by(sta5a) %>%
  summarise(total_pc_crh = sum(crh_encounter_count, na.rm = T))
```

# What Changed?  
* Under the original inclusion criteria of at least 2 consecutive months with 6 or more PC CRH encounters `r crh_flags %>% filter(yoon_5_flag == 1) %>% nrow()` sta5as were categorized as __CRH__
* Under the "new" criteria of at least 2 consecutive months with 10 or more PC CRH encounters `r crh_flags %>% filter(yoon_10_flag == 1) %>% nrow()` (`r ((crh_flags %>% filter(yoon_10_flag == 1) %>% nrow()) / (crh_flags %>% filter(yoon_5_flag == 1) %>% nrow())) %>% percent(accuracy = 0.1)`) sta5as are categorized as __CRH__
* Below is a table of those `r crh_flags %>% filter(yoon_10_flag == 0 & yoon_5_flag == 1) %>% nrow()` sta5as that are not included under the "new" definition

```{r}

crh_flags %>% 
  filter(yoon_10_flag == 0 & yoon_5_flag == 1) %>%
  select(sta5a) %>%
  left_join(., vast) %>%
  select(sta5a, short_name, state, visn, s_abbr, urh_vast, scrssn_count_cat) %>%
  left_join(., pen_rate_subset) %>%
  kbl(col.names = c("Sta5a", "Facility Name", "State", "VISN", "Site Type", "URH", "Uniques", "Total PC CRH Encounters")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```

# While we're here let's talk about PCMM exclusion criteria:  

## Any PC CRH  
```{r}
vast %>% inner_join(crh_flags) %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n()) %>%
  adorn_totals() %>%
  kbl(col.names = c("Uniques in PCMM", "Sta5as")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```

## Meeting > 9 PC CRH Inclusion Criteria  
```{r}
vast %>% inner_join(crh_flags) %>%
  filter(yoon_10_flag == 1) %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n()) %>%
  adorn_totals() %>%
  kbl(col.names = c("Uniques in PCMM", "Sta5as")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```

## Not Meeting > 9 PC CRH Inclusion Criteria  
```{r}
vast %>% inner_join(crh_flags) %>%
  filter(yoon_10_flag == 0) %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n()) %>%
  adorn_totals() %>%
  kbl(col.names = c("Uniques in PCMM", "Sta5as")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```