---
title: "CRH Encounters"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = '-')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 15),
             strip.text = element_text(size = 15),
             legend.text = element_text(size = 14),
             legend.title = element_text(size = 16),
             plot.caption = element_text(size = 12))
#
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
institution_lookup <- dbGetQuery(oabi_con,
                                 "select distinct a.InstitutionName, b.Sta6a
                                  from [CDWWork].[Dim].Institution as a
                                  left join [CDWWork].[Dim].Division as b
                                  	on a.InstitutionSID = b.InstitutionSID
                                  where b.Sta6a IS NOT NULL and a.InstitutionName <> '*Missing*'") %>%
  rename_all(tolower)
#--
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#==
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working") %>%
  left_join(., vast, by = c("spoke_sta5a" = "sta5a"))
#===========
hubs <- dbGetQuery(oabi_con,
                   "select distinct hub_sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY20]
                    UNION 
                    select distinct Hub_Sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY21_working]") %>%
  pull
#--
v23_dina_check <- read_xlsx("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/CRH_PCAT_Check.xlsx") %>%
  rename_all(tolower) %>%
  left_join(., institution_lookup) %>%
  mutate(psc = str_sub(stopcodename, start = 2, end = 4),
         ssc = str_sub(creditstopname, start = 2, end = 4),
         care_type = 
           case_when(
             (psc %in% c(156, 176, 177, 178, 301, 322, 323, 338, 348) 
              & (ssc != 160 | is.na(ssc) == T)) 
             | (psc != 160 
                & ssc %in% c(156, 176, 177, 178, 301, 322, 323, 338, 348))    ~ "Primary Care",
             (psc %in% c(502, 509, 510, 513, 516, 527, 538, 545, 550, 562, 576, 579, 586, 587) 
              & (ssc %ni% c(160, 534) | is.na(ssc) == T)) 
             | (psc %ni% c(160, 534)
                & ssc %in% c(502, 509, 510, 513, 516, 527, 538, 545, 550, 
                                    562, 576, 579, 586, 587))                  ~ "Mental Health",
             (psc %in% c(534, 539) 
              & (ssc != 160 | is.na(ssc) == T)) 
             | (psc != 160 & ssc %in% c(534, 539)) ~ "PCMHI",
             psc == 160 | ssc == 160  ~ "Pharmacy",
             is.na(psc) == T ~ "Missing",
             TRUE                                                                          ~ "Specialty"),
         visitdate = as_date(visitdatetime),
         hub_flag = if_else(sta6a %in% hubs, 2, 1),
         visit_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(visitdate) > 9, year(visitdate) + 1, year(visitdate)),
         qtr = case_when(month(visitdate) %in% c(10, 11, 12) ~ 1,
                         month(visitdate) %in% c(1, 2, 3) ~ 2,
                         month(visitdate) %in% c(4, 5, 6) ~ 3,
                         month(visitdate) %in% c(7, 8, 9) ~ 4)) %>%
  arrange(`pat id`, visitdatetime, hub_flag) %>%
  group_by(`pat id`, visitdatetime, care_type) %>%
  mutate(rowNum = row_number()) %>%
  ungroup
#--
bjarni_crh <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].crh_encounters_deDup
                         where fy in(2020, 2021)") %>%
  rename_all(tolower)
#--
chelle_crh <- dbGetQuery(oabi_con,
                         "select * from  [PACT_CC].[CRH].[crh_full_utilization_CLEAN]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         fy = if_else(month(visitdate) > 9, year(visitdate) + 1, year(visitdate)),
         qtr = case_when(month(visitdate) %in% c(10, 11, 12) ~ 1,
                         month(visitdate) %in% c(1, 2, 3) ~ 2,
                         month(visitdate) %in% c(4, 5, 6) ~ 3,
                         month(visitdate) %in% c(7, 8, 9) ~ 4)) %>%
  left_join(., vast, by = c("spoke_sta5a" = "sta5a")) %>%
  filter(fy %in% c(2020, 2021))
```

# National  
```{r}
bjarni_nat <- bjarni_crh %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Bjarni")
#
chelle_nat <- chelle_crh %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Chelle")
#
bjarni_nat %>%
  bind_rows(., chelle_nat) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_")) %>%
  ungroup %>%
  select(-c(fy, qtr)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = care_type_source, lty = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~care_type)
```

## Differences as a Table  
```{r}
b_nat_table <- bjarni_nat %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_")) %>%
  ungroup %>%
  select(-c(fy, qtr)) %>%
  pivot_wider(., names_from = c(source, fy_qtr), values_from = count)
#
c_nat_table <- chelle_nat %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_")) %>%
  ungroup %>%
  select(-c(fy, qtr)) %>%
  pivot_wider(., names_from = c(source, fy_qtr), values_from = count)
#--
b_nat_table %>%
  left_join(., c_nat_table) %>%
  mutate(b_c_diff_2020_1 = Bjarni_2020_1 - Chelle_2020_1,
         b_c_diff_2020_2 = Bjarni_2020_2 - Chelle_2020_2,
         b_c_diff_2020_3 = Bjarni_2020_3 - Chelle_2020_3,
         b_c_diff_2020_4 = Bjarni_2020_4 - Chelle_2020_4,
         b_c_diff_2021_1 = Bjarni_2021_1 - Chelle_2021_1,
         b_c_diff_2021_2 = Bjarni_2021_2 - Chelle_2021_2,
         b_c_diff_2021_3 = Bjarni_2021_3 - Chelle_2021_3,
         b_c_diff_2021_4 = Bjarni_2021_4 - Chelle_2021_4) %>%
  select(care_type, contains("diff_2020_1"), contains("diff_2020_2"), contains("diff_2020_3"),
         contains("diff_2020_4"), contains("diff_2021_1"), contains("diff_2021_2"), contains("diff_2021_3"),
         contains("diff_2021_4")) %>%
  janitor::adorn_totals() %>%
  kbl(col.names = c("Care Type", "B - C, 2020_1", "B - C, 2020_2", "B - C, 2020_3", "B - C, 2020_4",
                    "B - C, 2021_1", "B - C, 2021_2", "B - C, 2021_3", "B - C, 2021_4"),
      format.args = list(big.mark = ",")) %>%
  kable_classic("striped")
```

<!-- ## What's up with Specialty in Chelle's?   -->
<!-- ```{r} -->
<!-- chelle_crh %>% -->
<!--   filter(care_type == "Specialty") %>% -->
<!--   group_by(location_primary_sc, primarystopcodelocationname) %>% -->
<!--   summarise(count = n()) %>% -->
<!--   arrange(desc(count)) %>% -->
<!--   mutate(prop = paste0(round(count / 63449 * 100, 1), "%")) %>% -->
<!--   ungroup %>% -->
<!--   slice_head(., n = 12) %>% -->
<!--   kbl(col.names = c("Primary SC", "Primary SC Name", "Count", "Proportion of \"Specialty\""), -->
<!--       caption = "Top 12", -->
<!--       format.args = list(big.mark = ","), -->
<!--       align = c("c", "l", "r", "r")) %>% -->
<!--   kable_classic("striped") -->
<!-- ``` -->



# VISN 20  
```{r}
bjarni_crh_visn20 <- bjarni_crh %>%
  filter(parent_visn == 20 & care_type != "Missing")
#
chelle_crh_visn20 <- chelle_crh %>%
  filter(parent_visn == 20)
#----
b_crh_visn20_summ_qtr <- bjarni_crh_visn20 %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Bjarni")
#
c_crh_visn20_summ_qtr <- chelle_crh_visn20 %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Chelle")
#---
b_crh_visn20_summ_qtr %>%
  bind_rows(., c_crh_visn20_summ_qtr) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_")) %>%
  select(-c(fy, qtr)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = care_type_source, lty = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~care_type)
```

## Differences as a Table  
```{r}
bjarni_v20 <- bjarni_crh_visn20 %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Bjarni")
#
chelle_v20 <- chelle_crh_visn20 %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Chelle")
#==
b_v20_table <- bjarni_v20 %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_")) %>%
  ungroup %>%
  select(-c(fy, qtr)) %>%
  pivot_wider(., names_from = c(source, fy_qtr), values_from = count)
#
c_v20_table <- chelle_v20 %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_")) %>%
  ungroup %>%
  select(-c(fy, qtr)) %>%
  pivot_wider(., names_from = c(source, fy_qtr), values_from = count)
#--
b_v20_table %>%
  left_join(., c_v20_table) %>%
  mutate(b_c_diff_2020_1 = Bjarni_2020_1 - Chelle_2020_1,
         b_c_diff_2020_2 = Bjarni_2020_2 - Chelle_2020_2,
         b_c_diff_2020_3 = Bjarni_2020_3 - Chelle_2020_3,
         b_c_diff_2020_4 = Bjarni_2020_4 - Chelle_2020_4,
         b_c_diff_2021_1 = Bjarni_2021_1 - Chelle_2021_1,
         b_c_diff_2021_2 = Bjarni_2021_2 - Chelle_2021_2,
         b_c_diff_2021_3 = Bjarni_2021_3 - Chelle_2021_3,
         b_c_diff_2021_4 = Bjarni_2021_4 - Chelle_2021_4) %>%
  select(care_type, contains("diff_2020_1"), contains("diff_2020_2"), contains("diff_2020_3"),
         contains("diff_2020_4"), contains("diff_2021_1"), contains("diff_2021_2"), contains("diff_2021_3"),
         contains("diff_2021_4")) %>%
  janitor::adorn_totals() %>%
  kbl(col.names = c("Care Type", "B - C, 2020_1", "B - C, 2020_2", "B - C, 2020_3", "B - C, 2020_4",
                    "B - C, 2021_1", "B - C, 2021_2", "B - C, 2021_3", "B - C, 2021_4"),
      format.args = list(big.mark = ",")) %>%
  kable_classic("striped")
```

## What Sta5a's are there in both?  
```{r}
visn20_spokes <- spokes %>% filter(parent_visn == 20) %>% select(spoke_sta5a) %>% distinct %>% pull
#======
v20_sta5a_in_both <- bjarni_crh_visn20 %>%
  select(spoke_sta5a) %>% distinct %>%
  inner_join(., chelle_crh_visn20 %>% select(spoke_sta5a) %>% distinct) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(is_spoke = if_else(spoke_sta5a %in% visn20_spokes, TRUE, FALSE))
# 
v20_spokes_no_crh <- spokes %>% filter(parent_visn == 20) %>% 
  select(spoke_sta5a) %>% distinct %>% 
  filter(spoke_sta5a %ni% v20_sta5a_in_both$spoke_sta5a) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name))
```
* According to _[PACT_CC].[CRH].CRH_sites_fy20_working_ and _[PACT_CC].[CRH].CRH_sites_fy21_working_ there are `r nrow(table(visn20_spokes))` spoke sta5a in VISN 20
* Bjarni and Chelle both have the same `r nrow(v20_sta5a_in_both)` sta5a in their datasets
* The 2 sta5a that are not in either are:
    + `r v20_spokes_no_crh[1,3]`
    + `r v20_spokes_no_crh[2,3]`

```{r}
foo <- chelle_crh_visn20 %>%
  mutate(care_type = factor(care_type, ordered = T, levels = c("Mental Health", "Primary Care",
                                                               "Pharmacy", "PCMHI", "Specialty"))) %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(Count = n()) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(Sta5a = paste0("(", spoke_sta5a, ") ", short_name)) %>% ungroup %>%
  select(-c(spoke_sta5a, short_name)) %>%
  pivot_wider(names_from = care_type, values_from = Count) %>%
  janitor::adorn_totals() %>%
  rename(c_mh = `Mental Health`,
         c_pc = `Primary Care`,
         c_pharmacy = `Pharmacy`,
         c_pcmhi = `PCMHI`,
         c_spec = `Specialty`)
#
bar <- bjarni_crh_visn20 %>%
  mutate(care_type = factor(care_type, ordered = T, levels = c("Mental Health", "Primary Care",
                                                               "Pharmacy", "PCMHI", "Specialty"))) %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(Count = n()) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(Sta5a = paste0("(", spoke_sta5a, ") ", short_name)) %>% ungroup %>%
  select(-c(spoke_sta5a, short_name)) %>%
  pivot_wider(names_from = care_type, values_from = Count) %>%
  janitor::adorn_totals() %>%
  rename(b_mh = `Mental Health`,
         b_pc = `Primary Care`,
         b_pharmacy = `Pharmacy`,
         b_pcmhi = `PCMHI`,
         b_spec = `Specialty`)
#--
both <- foo %>%
  left_join(., bar) %>%
  mutate(drop_flag = if_else(is.na(b_mh) & is.na(c_mh) & is.na(b_pc) & is.na(c_pc)
                             & is.na(b_pharmacy) & is.na(c_pharmacy) & is.na(b_pcmhi) & is.na(c_pcmhi), T, F)) %>%
  filter(drop_flag == F) %>%
  mutate(across(where(is.numeric), ~ replace_na(.x, 0))) %>%
  mutate(mh_diff = b_mh - c_mh,
         pc_diff = b_pc - c_pc,
         pharm_diff = b_pharmacy - c_pharmacy,
         pcmhi_diff = b_pcmhi - c_pcmhi) %>%
  select(Sta5a, b_mh, c_mh, mh_diff, b_pc, c_pc, pc_diff, b_pharmacy, c_pharmacy, pharm_diff, b_pcmhi, c_pcmhi, pcmhi_diff)
#
kbl(both,
    col.names = c("Sta5a", rep(c("Bjarni", "Chelle", "Bjarni - Chelle"),4)),
    format.args = list(big.mark = ","),
    align = c("l", rep("r", 12))) %>%
  column_spec(c(2, 5, 8, 11), border_left = T) %>%
  kable_classic("striped") %>%
  add_header_above(c(" " = 1, "Mental Health" = 3, "Primary Care" = 3, "Pharmacy" = 3, "PCMHI" = 3))
```

### Mental Health: A subset of Sta5a's in VISN 20 (that are ever-spokes)  
```{r}
visn20_spokes <- spokes %>% filter(parent_visn == 20) %>% select(spoke_sta5a) %>% distinct %>% pull
#======
b_crh_visn20_summ_qtr_sta5a <- bjarni_crh_visn20 %>%
  group_by(care_type, spoke_sta5a, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Bjarni") %>%
  filter(spoke_sta5a %in% visn20_spokes)
#
b_sta5a_w_MT_100_crh <- b_crh_visn20_summ_qtr_sta5a %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(tot_crh = sum(count, na.rm = T)) %>%
  filter(tot_crh > 100)
#
b_mh_sta5a <- b_sta5a_w_MT_100_crh %>% filter(care_type == "Mental Health") %>% select(spoke_sta5a) %>% pull
#--
c_crh_visn20_summ_qtr_sta5a <- chelle_crh_visn20 %>%
  group_by(care_type, spoke_sta5a, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Chelle") %>%
  filter(spoke_sta5a %in% visn20_spokes)
#---
b_crh_visn20_summ_qtr_sta5a %>%
  bind_rows(., c_crh_visn20_summ_qtr_sta5a) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  select(-c(fy, qtr)) %>% ungroup %>%
  filter(care_type == "Mental Health" & spoke_sta5a %in% c("463", "531", "648", "653GA", "663",
                                                           "663GC", "687", "687HA")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = source, lty = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~sta5a_lab)
```


### Primary Care: A subset of Sta5a's in VISN 20 (that are ever-spokes)  
```{r}
b_crh_visn20_summ_qtr_sta5a %>%
  bind_rows(., c_crh_visn20_summ_qtr_sta5a) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  select(-c(fy, qtr)) %>% ungroup %>%
  filter(care_type == "Primary Care" & spoke_sta5a %in% c("463", "531", "531GI", "648GD", "653",
                                                           "653BY", "663A4", "692")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = source, lty = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~sta5a_lab)
```


# VISN 23  
```{r}
bjarni_crh_visn23 <- bjarni_crh %>%
  filter(parent_visn == 23 & care_type != "Missing")
#
chelle_crh_visn23 <- chelle_crh %>%
  filter(parent_visn == 23 & care_type != "Missing")
#
dina_nat_wDupes <- v23_dina_check %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "V23")
#
dina_nat_noDupes <- v23_dina_check %>%
  filter(rowNum == 1) %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "V23")
#----
b_crh_visn23_summ_qtr <- bjarni_crh_visn23 %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Bjarni")
#
c_crh_visn23_summ_qtr <- chelle_crh_visn23 %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Chelle")
#---
wDupes <- b_crh_visn23_summ_qtr %>%
  bind_rows(., c_crh_visn23_summ_qtr) %>%
  bind_rows(., dina_nat_wDupes) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_")) %>%
  select(-c(fy, qtr)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = care_type_source, color = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter",
       title = "With Duplicates") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~care_type)
#
noDupes <- b_crh_visn23_summ_qtr %>%
  bind_rows(., c_crh_visn23_summ_qtr) %>%
  bind_rows(., dina_nat_noDupes) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_")) %>%
  select(-c(fy, qtr)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = care_type_source, color = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter",
       title = "Without Duplicates") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~care_type)
#
multiplot(wDupes, noDupes, cols = 2)
```


## Differences as a Table  
```{r}
bjarni_v23 <- bjarni_crh_visn23 %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Bjarni")
#
chelle_v23 <- chelle_crh_visn23 %>%
  filter(care_type != "Missing") %>%
  group_by(care_type, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Chelle")
#==
b_v23_table <- bjarni_v23 %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_")) %>%
  ungroup %>%
  select(-c(fy, qtr)) %>%
  pivot_wider(., names_from = c(source, fy_qtr), values_from = count)
#
c_v23_table <- chelle_v23 %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_")) %>%
  ungroup %>%
  select(-c(fy, qtr)) %>%
  pivot_wider(., names_from = c(source, fy_qtr), values_from = count)
#--
b_v23_table %>%
  left_join(., c_v23_table) %>%
  mutate(b_c_diff_2020_1 = Bjarni_2020_1 - Chelle_2020_1,
         b_c_diff_2020_2 = Bjarni_2020_2 - Chelle_2020_2,
         b_c_diff_2020_3 = Bjarni_2020_3 - Chelle_2020_3,
         b_c_diff_2020_4 = Bjarni_2020_4 - Chelle_2020_4,
         b_c_diff_2021_1 = Bjarni_2021_1 - Chelle_2021_1,
         b_c_diff_2021_2 = Bjarni_2021_2 - Chelle_2021_2,
         b_c_diff_2021_3 = Bjarni_2021_3 - Chelle_2021_3,
         b_c_diff_2021_4 = Bjarni_2021_4 - Chelle_2021_4) %>%
  select(care_type, contains("diff_2020_1"), contains("diff_2020_2"), contains("diff_2020_3"),
         contains("diff_2020_4"), contains("diff_2021_1"), contains("diff_2021_2"), contains("diff_2021_3"),
         contains("diff_2021_4")) %>%
  janitor::adorn_totals() %>%
  kbl(col.names = c("Care Type", "B - C, 2020_1", "B - C, 2020_2", "B - C, 2020_3", "B - C, 2020_4",
                    "B - C, 2021_1", "B - C, 2021_2", "B - C, 2021_3", "B - C, 2021_4"),
      format.args = list(big.mark = ",")) %>%
  kable_classic("striped")
```

## What Sta5a's are there in both?  
```{r}
visn23_spokes <- spokes %>% filter(parent_visn == 23) %>% select(spoke_sta5a) %>% distinct %>% pull
#======
v23_sta5a_in_both <- bjarni_crh_visn23 %>%
  select(spoke_sta5a) %>% distinct %>%
  inner_join(., chelle_crh_visn23 %>% select(spoke_sta5a) %>% distinct) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(is_spoke = if_else(spoke_sta5a %in% visn23_spokes, TRUE, FALSE))
#
v23_sta5a_in_bjarni <- bjarni_crh_visn23 %>%
  select(spoke_sta5a) %>% distinct %>%
  anti_join(., chelle_crh_visn23 %>% select(spoke_sta5a)) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name))
# 
v23_spokes_no_crh <- spokes %>% filter(parent_visn == 23) %>% 
  select(spoke_sta5a) %>% distinct %>% 
  filter(spoke_sta5a %ni% v23_sta5a_in_both$spoke_sta5a & spoke_sta5a %ni% v23_sta5a_in_bjarni$spoke_sta5a) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name))
```

* According to _[PACT_CC].[CRH].CRH_sites_fy23_working_ and _[PACT_CC].[CRH].CRH_sites_fy21_working_ there are `r nrow(table(visn23_spokes))` spoke sta5a in VISN 23
* Bjarni and Chelle have the same `r nrow(v23_sta5a_in_both)` sta5a in their datasets
* Bjarni has `r nrow(v23_sta5a_in_bjarni)` sta5a that Chelle does not:
    + `r v23_sta5a_in_bjarni[1, 3]`
    + `r v23_sta5a_in_bjarni[2, 3]`
    + `r v23_sta5a_in_bjarni[3, 3]`
* The 2 sta5a that are not in either are:
    + `r v23_spokes_no_crh[1, 3]`
    + `r v23_spokes_no_crh[2, 3]`


```{r}
foo <- chelle_crh_visn23 %>%
  mutate(care_type = factor(care_type, ordered = T, levels = c("Mental Health", "Primary Care",
                                                               "Pharmacy", "PCMHI", "Specialty"))) %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(Count = n()) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(Sta5a = paste0("(", spoke_sta5a, ") ", short_name)) %>% ungroup %>%
  select(-c(spoke_sta5a, short_name)) %>%
  pivot_wider(names_from = care_type, values_from = Count) %>%
  janitor::adorn_totals() %>%
  rename(c_mh = `Mental Health`,
         c_pc = `Primary Care`,
         c_pharmacy = `Pharmacy`,
         c_pcmhi = `PCMHI`,
         c_spec = `Specialty`)
#
bar <- bjarni_crh_visn23 %>%
  mutate(care_type = factor(care_type, ordered = T, levels = c("Mental Health", "Primary Care",
                                                               "Pharmacy", "PCMHI", "Specialty"))) %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(Count = n()) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(Sta5a = paste0("(", spoke_sta5a, ") ", short_name)) %>% ungroup %>%
  select(-c(spoke_sta5a, short_name)) %>%
  pivot_wider(names_from = care_type, values_from = Count) %>%
  janitor::adorn_totals() %>%
  rename(b_mh = `Mental Health`,
         b_pc = `Primary Care`,
         b_pharmacy = `Pharmacy`,
         b_pcmhi = `PCMHI`,
         b_spec = `Specialty`)
#--
both <- bar %>%
  left_join(., foo) %>%
  mutate(drop_flag = if_else(is.na(b_mh) & is.na(c_mh) & is.na(b_pc) & is.na(c_pc)
                             & is.na(b_pharmacy) & is.na(c_pharmacy) & is.na(b_pcmhi) & is.na(c_pcmhi), T, F)) %>%
  filter(drop_flag == F) %>%
  mutate(across(where(is.numeric), ~ replace_na(.x, 0))) %>%
  mutate(mh_diff = b_mh - c_mh,
         pc_diff = b_pc - c_pc,
         pharm_diff = b_pharmacy - c_pharmacy,
         pcmhi_diff = b_pcmhi - c_pcmhi) %>%
  select(Sta5a, b_mh, c_mh, mh_diff, b_pc, c_pc, pc_diff, b_pharmacy, c_pharmacy, pharm_diff, b_pcmhi, c_pcmhi, pcmhi_diff)
#
kbl(both,
    col.names = c("Sta5a", rep(c("Bjarni", "Chelle", "Bjarni - Chelle"),4)),
    format.args = list(big.mark = ","),
    align = c("l", rep("r", 12))) %>%
  column_spec(c(2, 5, 8, 11), border_left = T) %>%
  kable_classic("striped") %>%
  add_header_above(c(" " = 1, "Mental Health" = 3, "Primary Care" = 3, "Pharmacy" = 3, "PCMHI" = 3))
```

### Mental Health: A subset of Sta5a's in VISN 23 (that are ever-spokes)  
```{r}
visn23_spokes <- spokes %>% filter(parent_visn == 23) %>% select(spoke_sta5a) %>% distinct %>% pull
#======
b_crh_visn23_summ_qtr_sta5a <- bjarni_crh_visn23 %>%
  group_by(care_type, spoke_sta5a, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Bjarni") %>%
  filter(spoke_sta5a %in% visn23_spokes)
#
b_sta5a_w_MT_100_crh <- b_crh_visn23_summ_qtr_sta5a %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(tot_crh = sum(count, na.rm = T)) %>%
  filter(tot_crh > 100)
#
b_mh_sta5a <- b_sta5a_w_MT_100_crh %>% filter(care_type == "Mental Health") %>% select(spoke_sta5a) %>% pull
#--
c_crh_visn23_summ_qtr_sta5a <- chelle_crh_visn23 %>%
  group_by(care_type, spoke_sta5a, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "Chelle") %>%
  filter(spoke_sta5a %in% visn23_spokes)
#--
dina_crh_visn23_summ_qtr_sta5a <- v23_dina_check %>%
  filter(rowNum == 1) %>%
  rename(spoke_sta5a = sta6a) %>%
  group_by(care_type, spoke_sta5a, fy, qtr) %>%
  summarise(count = n()) %>%
  mutate(source = "V23")
#---
b_crh_visn23_summ_qtr_sta5a %>%
  bind_rows(., c_crh_visn23_summ_qtr_sta5a) %>%
  bind_rows(., dina_crh_visn23_summ_qtr_sta5a) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  select(-c(fy, qtr)) %>% ungroup %>%
  filter(care_type == "Mental Health" & spoke_sta5a %in% c("437", "636", "636A4", "618",
                                                           "636GD", "656", "656GA", "656GC")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = source, color = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~sta5a_lab)
```


### Primary Care: A subset of Sta5a's in VISN 23 (that are ever-spokes)  
```{r}
b_crh_visn23_summ_qtr_sta5a %>%
  bind_rows(., c_crh_visn23_summ_qtr_sta5a) %>%
  bind_rows(., dina_crh_visn23_summ_qtr_sta5a) %>%
  left_join(., vast %>% select(spoke_sta5a = sta5a, short_name)) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "_"),
         care_type_source = str_c(care_type, source, sep = "_"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  select(-c(fy, qtr)) %>% ungroup %>%
  filter(care_type == "Primary Care" & spoke_sta5a %in% c("437", "568A4", "618", "636A6",
                                                          "636GG", "636GR", "656")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = count, group = source, color = source)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  labs(x = "FY_Qtr",
       y = "Encounters per Quarter") +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.3),
        legend.title = element_blank()) +
  facet_wrap(~sta5a_lab)
```