---
title: "Denominator for Penetration Rate"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#--
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```


```{r}
# dbExecute(oabi_con, "drop table if exists #pcat_sc_encounters")
#
# dbExecute(oabi_con,
#           "select cast(op.visitDateTime as date) as visitDate
#           	, psc.StopCode as pStopCode
#       			, pSCName = case 
#       				when psc.StopCode = 323 then 'PRIMARY CARE/MEDICINE'
#       				else psc.stopcodename end
#           	, ssc.StopCode as sStopCode
#       			, sSCName = case 
#       				when ssc.StopCode = 185 then 'NURSE PRACTITIONER'
#       				when ssc.StopCode = 323 then 'PRIMARY CARE/MEDICINE'
#       				when ssc.StopCode IS NULL then '*Missing*'
#       				else ssc.stopcodename end
#           into #pcat_sc_encounters
#           from [CDWWork].[Outpat].Workload as op
#           left join [CDWWork].[Dim].StopCode as psc
#           	on op.PrimaryStopCodeSID = psc.StopCodeSID
#           left join [CDWWork].[Dim].StopCode as ssc
#           	on op.SecondaryStopCodeSID = ssc.StopCodeSID
#           where psc.StopCode in(322, 323, 348, 350, 704)
#           	AND psc.StopCode not in(107, 115, 152, 311, 321, 328, 329, 333, 334, 430, 435, 474, 999) 
#           	OR ssc.StopCode in(322, 323, 348, 350, 704)
#           	AND VisitDateTime >= cast('2019-10-01' as datetime2) and VisitDateTime <= cast('2021-09-30' as datetime2);",
#           immediate = TRUE)
#==
# pcat_sc_count <- dbGetQuery(oabi_con,
#                             "select count(*) as pcat_stopCode_count
#                             	, pStopCode
#                             	, sStopCode, sSCName
#                             from #pcat_sc_encounters
#                             group by pStopCode
#                             	, sStopCode, sSCName")
#-----
# write_csv(pcat_sc_count,
#           here("Input", "Data", "pcat_pc_sc_counts.csv"))
#
pcat_sc_count <- read_csv(here("Input", "Data", "pcat_pc_sc_counts.csv"))
#--------------------------------

sc_names <- dbGetQuery(oabi_con,
                       "select distinct stopcode
                        	, stopCodeName = case 
                        		when stopcode = 185 then 'NURSE PRACTITIONER'
                        		when stopcode = 188 then 'FELLOW/RESIDENT'
                        		when stopcode = 301 then 'GENERAL INTERNAL MEDICINE'
                        		when stopcode = 323 then 'PRIMARY CARE/MEDICINE'
                        		when stopcode = 674 then 'ADMIN PAT ACTIVTIES (MASNONCT)'
                        		else StopCodeName end
                        from [CDWWork].[Dim].StopCode
                        where StopCode in(156,176,177,178,301,338,179 ,697,205,206,510,534,185,690,692,693,117    
                        ,125,130,184,186,188,301,673,322, 323, 348, 674)")
#
#---------------
pc_crh_stopCode_count <- dbGetQuery(oabi_con,
                                    "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr),
         ssc_117_flag = if_else(secondarystopcode == 117, T, F)) %>%
  rename(sta5a = spoke_sta5a_combined_cdw) %>%
  filter(fy %in% c(2020, 2021) 
         & care_type == "Primary Care") %>%
  mutate(secondarystopcode = if_else(is.na(secondarystopcode) == T, "Missing", as.character(secondarystopcode))) %>%
  group_by(primarystopcode, secondarystopcode) %>%
  summarise(crh_sc_count = n())
#-----------------------------------------------------------------------------------------------------------
crh_vs_pcat <- pc_crh_stopCode_count %>%
  left_join(., pcat_sc_count %>% mutate(sStopCode = as.character(sStopCode)), 
            by = c("primarystopcode" = "pStopCode", "secondarystopcode" = "sStopCode")) %>%
  left_join(., sc_names, by = c("primarystopcode" = "stopcode")) %>%
  rename(pSCName = stopCodeName) %>%
  left_join(., sc_names %>% mutate(stopcode = as.character(stopcode)), by = c("secondarystopcode" = "stopcode")) %>%
  mutate(sSCName = if_else(is.na(sSCName), stopCodeName, sSCName)) %>%
  mutate(crh_prop = round(crh_sc_count / 306855 * 100, 1),
         pcat_prop = round(pcat_stopCode_count / 287176114 * 100, 1)) %>%
  select(primarystopcode, pSCName, secondarystopcode, sSCName, crh_sc_count, crh_prop, pcat_stopCode_count, pcat_prop) %>%
  arrange(desc(crh_sc_count)) %>% 
  janitor::adorn_totals() %>%
  mutate(crh_prop = paste0(crh_prop, "%"),
         pcat_prop = if_else(is.na(pcat_prop), "-", as.character(pcat_prop)),
         pcat_prop = paste0(pcat_prop, "%"),
         crh_sc_count = scales::comma(crh_sc_count, accuracy = 1),
         pcat_stopCode_count = scales::comma(pcat_stopCode_count, accuracy = 1))
#+++++++++++++++++++++++++++++++++++++++++++++++++
cdw_crh <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].stopCode_combos
                         where careType = 'PC'") %>%
  arrange(desc(sc_count))
```

# PCAT Approach  
* These are the encounters included as Primary Care Encounters in the _[PACT_CC].[econ].[Outp_PCMM_SSN_Summary]_ table
    + This is the "official" PCAT denominator table
    + Code for table written by Phillip Sylling, maintained now by Jorge Rojas
    + `r colorize("PrimaryStopCode in (322, 323, 348, 350, 704) AND PrimaryStopCode not in(107, 115, 152, 311, 321, 328, 329, 333, 334, 430, 435, 474, 999)", "red")`
    + `r colorize("OR SecondaryStopCode in(322, 323, 348, 350, 704)", "red")`
* This method yields `r sum(pcat_sc_count$pcat_stopCode_count)` encounters for FY 20 & FY21 
* There are `r nrow(pcat_sc_count)` unique primary and secondary stop code combinations using this method for selecting the denominator                                               


## Top 25 for PCAT  

```{r}
pcat_sc_count %>%
  arrange(desc(pcat_stopCode_count)) %>%
  slice_head(., n = 25) %>%
  left_join(., sc_names, by = c("pStopCode" = "stopcode")) %>%
  select(pStopCode, stopCodeName, sStopCode, sSCName, pcat_stopCode_count) %>%
  mutate(prop = paste0(round(pcat_stopCode_count / 287176114 * 100, 1), "%"),
         pcat_stopCode_count = scales::comma(pcat_stopCode_count, accuracy = 1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "PCAT Count", "PCAT %")) %>%
  kable_classic("striped") %>% 
  row_spec(0,bold=TRUE)
```

## CRH vs. PCAT  
* Out of the `r sum(pc_crh_stopCode_count$crh_sc_count)` Primary Care CRH encounters in FY20 and FY21 there are `r nrow(pc_crh_stopCode_count)` unique primary and secondary stop code combinations

```{r}
crh_vs_pcat %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "CRH Count", "CRH %", "PCAT Count", "PCAT %")) %>%
  kable_classic("striped") %>% 
  row_spec(0,bold=TRUE)
```

# Previous Approach  

* Below are the top 25 Primary & Secondary stop code combinations using the following criteria to pull PC encounters from CDW:
    + `r colorize("PrimaryStopCode in (156, 176, 177, 178, 301, 322, 323, 338, 348) AND (SecondaryStopCode not in(160, 534, 539) OR SecondaryStopCode IS NULL)", "red")`
    + `r colorize("OR (PrimaryStopCode not in(160, 534, 539) AND SecondaryStopCode in (156, 176, 177, 178, 301, 322, 323, 338, 348))", "red")` 
* This yields `r sum(cdw_crh$sc_count)` encounters in FY20 & FY21
* There are a total of `r nrow(cdw_crh)` stop code combinations 


## Top 25  

```{r}
cdw_crh %>%
  select(pStopCode_, pStopCodeName_,
         sStopCode_, sStopCodeName_, sc_count) %>%
  slice_head(., n = 25) %>%
  mutate(prop = round(sc_count / sum(cdw_crh$sc_count) * 100, 1),
         pStopCode_ = as.character(pStopCode_),
         sStopCode_ = as.character(sStopCode_),
         sc_count = as.character(scales::comma(sc_count))) %>%
  janitor::adorn_totals() %>%
  mutate(prop = paste0(prop, "%")) %>%
  kbl(align = c("c", "l", "c", "l", "r", "r"),
      col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Total Encounters", "Proportion of total")) %>%
  kable_classic("striped") %>% 
  row_spec(0,bold=TRUE)
```

## CRH vs. Previous  
```{r}
pc_crh_stopCode_count %>%
  left_join(., cdw_crh %>% mutate(sStopCode_ = as.character(sStopCode_)), 
            by = c("primarystopcode" = "pStopCode_", "secondarystopcode" = "sStopCode_")) %>%
  mutate(crh_prop = crh_sc_count / sum(pc_crh_stopCode_count$crh_sc_count) * 100,
         cdw_prop = sc_count / sum(cdw_crh$sc_count) * 100) %>%
  arrange(desc(crh_sc_count)) %>%
  select(primarystopcode, pStopCodeName_, secondarystopcode, sStopCodeName_, crh_sc_count, crh_prop, sc_count, cdw_prop) %>%
  janitor::adorn_totals() %>%
  mutate(crh_prop = paste0(round(crh_prop, 1), "%"),
         cdw_prop = if_else(cdw_prop < 0.1, "< 0.1%", paste0(round(cdw_prop, 1), "%")),
         crh_sc_count = scales::comma(crh_sc_count, accuracy = 1),
         sc_count = scales::comma(sc_count, accuracy = 1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "CRH Count", "CRH %", "CDW Count", "CDW %"),
      align = c(rep(c("c", "l"), 2), rep("r", 4))) %>%
  kable_classic("striped") %>% 
  row_spec(0,bold=TRUE)

```