---
title: "VISN 20 - CRH Encounters Over Time"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    toc_depth: 3
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = '-')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(ggrepel)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 24),
             axis.text = element_text(size = 20),
             strip.text = element_text(size = 22),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 15))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes_v <- spokes %>% pull
#
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#
vast_spokes <- vast %>%
  inner_join(., spokes, by = c("sta5a" = "spoke_sta5a"))
#==
all_months <- seq.Date(ymd('2019-10-01'),ymd('2021-09-01'), by = 'month')
#--
all_encounters <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].encounter_counts") %>%
  select(-contains("Vax")) %>%
  mutate(vizMonth = ymd(vizMonth)) %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", sta6a, ") ", short_name),
         spoke_flag = if_else(sta6a %in% spokes_v, TRUE, FALSE),
         fy = if_else(month(vizMonth) > 9, year(vizMonth) + 1, year(vizMonth)),
         qtr = case_when(month(vizMonth) %in% c(10, 11, 12) ~ 1,
                         month(vizMonth) %in% c(1, 2, 3) ~ 2,
                         month(vizMonth) %in% c(4, 5, 6) ~ 3,
                         month(vizMonth) %in% c(7, 8, 9) ~ 4)) %>%
  filter(is.na(parent_visn) == F & fy %in% c(2020, 2021)) %>%
  rename("Primary Care" = pc_encounters,
         "Mental Health" = mh_encounters,
         "Pharmacy" = pharmacy_encounters,
         "PCMHI" = pcmhi_encounters)
#
spoke_encounters <- all_encounters %>% filter(spoke_flag == T)
#==
crh_encounters <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].crh_encounters_deDup") %>%
  rename_all(tolower) %>%
  filter(fy %in% c(2020, 2021) & care_type %ni% c("Specialty", "Missing")) %>%
  mutate(crh_month = ymd(crh_month))
```

```{r visn_creating_data_frames}
#--TOTAL
crh_visn_total <- crh_encounters %>%
  group_by(crh_month, parent_visn) %>%
  summarise(crh_encounters = n())
#
all_visn_total <- spoke_encounters %>%
  select(2:6, parent_visn) %>%
  pivot_longer(-c(vizMonth, parent_visn)) %>%
  group_by(vizMonth, parent_visn) %>%
  summarise(total = sum(value, na.rm = T))
#
total_visn_df <- crh_visn_total %>%
  left_join(., all_visn_total, by = c("crh_month" = "vizMonth", "parent_visn" = "parent_visn")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(parent_visn) == F) %>%
  ungroup %>%
  complete(crh_month = all_months, nesting(parent_visn))
#==BY CARE TYPE
crh_visn_type <- crh_encounters %>%
  group_by(crh_month, parent_visn, care_type) %>%
  summarise(crh_encounters = n())
#
all_visn_type <- spoke_encounters %>%
  select(2:6, parent_visn) %>%
  pivot_longer(-c(vizMonth, parent_visn)) %>%
  group_by(vizMonth, parent_visn, name) %>%
  summarise(total = sum(value, na.rm = T))
#
type_visn_df <- crh_visn_type %>%
  left_join(., all_visn_type, by = c("crh_month" = "vizMonth", "care_type" = "name", "parent_visn" = "parent_visn")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(parent_visn) == F) %>%
  ungroup %>%
  complete(crh_month = all_months, nesting(parent_visn, care_type))
```

```{r sta5a_creating_data_frames}
#--TOTAL
crh_sta5a_total <- crh_encounters %>%
  group_by(crh_month, spoke_sta5a) %>%
  summarise(crh_encounters = n())
#
all_sta5a_total <- spoke_encounters %>%
  select(2:6, sta6a) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(vizMonth, sta6a) %>%
  summarise(total = sum(value, na.rm = T))
#
total_sta5a_df_1 <- crh_sta5a_total %>%
  left_join(., all_sta5a_total, by = c("crh_month" = "vizMonth", "spoke_sta5a" = "sta6a")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(spoke_sta5a) == F) %>%
  ungroup %>%
  complete(crh_month = all_months, nesting(spoke_sta5a))
#
avg_tot_crh_sta5a <- total_sta5a_df_1 %>%
  filter(is.na(crh_encounters) == F) %>%
  group_by(spoke_sta5a) %>%
  summarise(number_of_crh_months = n(),
            avg_crh_per_month = mean(crh_encounters, na.rm = T),
            avg_crh_per_1k = mean(crh_per_1k_total, na.rm = T),
            avg_tot = mean(total, na.rm = T),
            sum_tot = sum(total)) %>%
  left_join(., vast, by = c("spoke_sta5a" = "sta5a"))
#--
total_sta5a_df <- total_sta5a_df_1 %>% left_join(., avg_tot_crh_sta5a) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name))
#==BY CARE TYPE
crh_sta5a_type <- crh_encounters %>%
  group_by(crh_month, spoke_sta5a, care_type) %>%
  summarise(crh_encounters = n())
#
all_sta5a_type <- spoke_encounters %>%
  select(2:6, sta6a) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(vizMonth, sta6a, name) %>%
  summarise(total = sum(value, na.rm = T))
#
type_sta5a_df_1 <- crh_sta5a_type %>%
  left_join(., all_sta5a_type, by = c("crh_month" = "vizMonth", "care_type" = "name", "spoke_sta5a" = "sta6a")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(spoke_sta5a) == F) %>%
  ungroup %>%
  complete(crh_month = all_months, nesting(spoke_sta5a, care_type))
#
avg_type_sta5a <- type_sta5a_df_1 %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(number_of_crh_months = n(),
            avg_crh_per_month = mean(crh_encounters),
            avg_crh_per_1k = mean(crh_per_1k_total),
            sum_tot = sum(total)) %>%
  left_join(., vast, by = c("spoke_sta5a" = "sta5a"))
#==
type_sta5a_df <- type_sta5a_df_1 %>% left_join(., avg_type_sta5a) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name))
```

\newpage

```{r visn-functions}
total_plot_fxn <- function(visn_var){
  p <- ggplot(data = subset(total_visn_df, parent_visn == visn_var),
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn, color = "1")) +
    geom_line(size = 1) +
    scale_y_continuous(limits = c(0, 100),
                       labels = scales::comma_format(accuracy = 1)) +
    ggsci::scale_color_aaas() +
    guides(color = guide_legend(override.aes = list(size = 1.25))) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    labs(x = "Month",
         y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
    geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2)
  #
  return(p)
}
#----
total_table_fxn <- function(visn_var){
  total_visn_df %>% filter(parent_visn == visn_var) %>%
    select(-parent_visn) %>%
    mutate(crh_per_1k_total = round(crh_per_1k_total, 1)) %>%
    rename("CRH Encounters" = crh_encounters,
           "Total" = total,
           "CRH/1,000 total" = crh_per_1k_total) %>%
    kbl(col.names = c("Month", "CRH Encounters", "Total Encounters", "CRH/1,000 Total"),
        format.args = list(big.mark = ","),
        align = c("l", rep("r", 4))) %>%
    kable_classic(latex_options = c("striped", "hold_position"))
}
#----
type_plot_fxn <- function(visn_var){
  ggplot(data = subset(type_visn_df, care_type != "PCMHI" & parent_visn == visn_var),
         aes(x = crh_month, y = crh_per_1k_total, group = care_type, color = care_type)) +
    geom_line(size = 1) +
    scale_y_continuous(limits = c(0, 100),
                       labels = scales::comma_format(accuracy = 1)) +
    ggsci::scale_color_aaas() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 270, vjust = 0.5)) +
    labs(x = "Month",
         y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
    geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
    facet_wrap(~care_type)
}
#----
type_plot_fxn2 <- function(visn_var){
  ggplot(data = subset(type_visn_df, care_type == "PCMHI" & parent_visn == visn_var),
         aes(x = crh_month, y = crh_per_1k_total, group = care_type, color = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  ggsci::scale_color_aaas() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.5)) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~care_type)
}
#----
type_table_fxn <- function(visn_var){
  type_visn_df %>%
  filter(parent_visn == visn_var) %>%
  ungroup %>%
  select(-parent_visn) %>%
  mutate(crh_per_1k_total = round(crh_per_1k_total, 1)) %>%
  pivot_longer(-c(crh_month, care_type)) %>%
  pivot_wider(names_from = c(care_type, name), values_from = value) %>%
  select(crh_month, contains("Mental"), contains("Primary")) %>%
  kbl(col.names = c("Month",
                    rep(c("CRH", "Total", "CRH/1,000"), 2)),
      align = c("l", rep("r", 6)),
      format.args = list(big.mark = ",")) %>%
  column_spec(c(4), border_right = T) %>%
  kable_classic(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c(" " = 1, "Mental Health" = 3, "Primary Care" = 3))
}
#----
type_table_fxn2 <- function(visn_var){
  type_visn_df %>%
  filter(parent_visn == visn_var) %>%
  ungroup %>%
  select(-parent_visn) %>%
  mutate(crh_per_1k_total = round(crh_per_1k_total, 1)) %>%
  pivot_longer(-c(crh_month, care_type)) %>%
  pivot_wider(names_from = c(care_type, name), values_from = value) %>%
  select(crh_month, contains("Pharmacy"), contains("PCMHI")) %>%
  kbl(col.names = c("Month",
                    rep(c("CRH", "Total", "CRH/1,000"), 2)),
      align = c("l", rep("r", 6)),
      format.args = list(big.mark = ",")) %>%
  column_spec(c(4), border_right = T) %>%
  kable_classic(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c(" " = 1, "Pharmacy" = 3, "PCMHI" = 3))
}
```

```{r sta5a_functions}
crh_months_fxn <- function(visn_var){
  ggplot(data = subset(avg_tot_crh_sta5a, parent_visn == visn_var),
       aes(x = number_of_crh_months)) +
  geom_histogram(bins = 24, fill = "royalblue", color = "black") +
  scale_x_continuous(breaks = seq(0, 24, 3),
                     limits = c(0, 25)) +
  labs(x = "Months with > 0 CRH Encounters",
       y = "Count of Sta5as")
}
#
avg_crh_tot_fxn <- function(visn_var){
  ggplot(data = subset(avg_tot_crh_sta5a, parent_visn == visn_var & avg_crh_per_month < 1000),
                      aes(x = avg_crh_per_month)) +
  geom_histogram(fill = "red", color = "black") +
  labs(x = "Average CRH Encounters per Month",
       y = "Count of Sta5as")
}
#
avg_crh_1k_fxn <- function(visn_var){
  ggplot(data = subset(avg_tot_crh_sta5a, parent_visn == visn_var & avg_crh_per_1k < 1000),
                     aes(x = avg_crh_per_1k)) +
  geom_histogram(fill = "forestgreen", color = "black") +
  labs(x = "Average CRH Encounters/1,000 per Month",
       y = "Count of Sta5as")
}
#
avg_tot_fxn <- function(visn_var){
  ggplot(data = subset(avg_tot_crh_sta5a, parent_visn == visn_var),
                     aes(x = avg_tot)) +
  geom_histogram(fill = "goldenrod", color = "black") +
  scale_y_continuous(labels = scales::comma_format(accuracy = 1)) +
  labs(x = "Average Total Encounters per Month",
       y = "Count of Sta5as") +
  scale_x_continuous(labels = scales::comma_format())
}
```
\newpage

# VISN 20   
## Total  
```{r}
total_plot_fxn(20)
```

\newpage

### As a Table  

```{r}
total_table_fxn(20)
```

\newpage

## By Care Type - I    

```{r}
type_plot_fxn(20)
```

\newpage


## By Care Type - II  
```{r}
type_plot_fxn2(20)
```

\newpage

### As a Table - I    

```{r}
type_table_fxn(20)
```

\newpage

### As a Table - II     
```{r}
type_table_fxn2(20)
```

\newpage

# Distribution of CRH Encounters   
* There are `r total_sta5a_df %>% filter(parent_visn == 20) %>% select(spoke_sta5a) %>% n_distinct %>% toString` Sta5as in this VISN with at least 1 CRH encounter from October, 2019 through September, 2021   

## Months with at least 1 CRH Encounter  
```{r}
crh_months_fxn(20)
```

\newpage

## Average CRH Encounters per Month  
* Removed `r avg_tot_crh_sta5a %>% filter(avg_crh_per_month > 1000) %>% n_distinct %>% toString` observations with values > 1,000   

```{r}
avg_crh_tot_fxn(20)
```

\newpage

## Average CRH Encounters/1,000 Total Encounters  
* Removed `r avg_tot_crh_sta5a %>% filter(avg_crh_per_1k > 1000) %>% n_distinct %>% toString` observations with values > 1,000   

```{r}
avg_crh_1k_fxn(20)
```

\newpage

## Average Total Encounters   
```{r}
avg_tot_fxn(20)
```



