---
title: "VISN 6"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```



```{r reading-in}
hubs <- dbGetQuery(oabi_con,
                   "select distinct hub_sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY20]
                    UNION 
                    select distinct Hub_Sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY21_working]") %>%
  pull
#--
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes_v <- spokes %>% pull
#
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#
vast_spokes <- vast %>%
  inner_join(., spokes, by = c("sta5a" = "spoke_sta5a"))
#==
all_encounters <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].all_encounters_E_counts") %>%
  select(-contains("Vax")) %>%
  mutate(vizMonth = ymd(vizMonth)) %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", sta6a, ") ", short_name),
         spoke_flag = if_else(sta6a %in% spokes_v, TRUE, FALSE),
         fy = if_else(month(vizMonth) > 9, year(vizMonth) + 1, year(vizMonth)),
         qtr = case_when(month(vizMonth) %in% c(10, 11, 12) ~ 1,
                         month(vizMonth) %in% c(1, 2, 3) ~ 2,
                         month(vizMonth) %in% c(4, 5, 6) ~ 3,
                         month(vizMonth) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  filter(is.na(parent_visn) == F & fy %in% c(2020, 2021)) %>%
  rename("Primary Care" = pc_encounters,
         "Mental Health" = mh_encounters,
         "Pharmacy" = pharmacy_encounters,
         "PCMHI" = pcmhi_encounters)
#
all_qtrs <- all_encounters %>% select(fyqtr) %>% distinct
#
spoke_encounters <- all_encounters %>% filter(spoke_flag == T) %>%
  rename(sta5a = sta6a)
#-----
crh_encounters <- dbGetQuery(oabi_con,
                         "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  filter(fy %in% c(2020, 2021) & care_type %in% c("Primary Care", "Pharmacy")) %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a")) %>%
  rename(sta5a = spoke_sta5a_combined_cdw)
#--==================
access_metrics_sta5a <- read_csv(here("Input", "Data", "pc_access_metrics_sta5a_qtr.csv")) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop) %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  rename(sta5a = sta6a) %>%
  mutate(sta5a_lab = paste0("(", sta5a, ") ", short_name),
         fy_qtr = str_replace(fy_qtr, "_", "-"))
```

```{r creating_sta5a_data_frames}
#--TOTAL
crh_sta5a_total <- all_qtrs %>% left_join(., crh_encounters) %>%
  group_by(fyqtr, sta5a) %>%
  summarise(crh_encounters = n()) %>%
  ungroup
#
all_sta5a_total <- all_qtrs %>% left_join(., spoke_encounters) %>%
  select(4:7, sta5a, fyqtr) %>%
  pivot_longer(-c(fyqtr, sta5a)) %>%
  group_by(fyqtr, sta5a) %>%
  summarise(total = sum(value, na.rm = T)) %>%
  ungroup
#
total_avg <- crh_sta5a_total %>% 
  group_by(sta5a) %>%
  summarise(avg_crh_per_qtr = mean(crh_encounters, na.rm = T))
#
total_sta5a_df <- all_qtrs %>% 
  full_join(., crh_sta5a_total) %>%
  full_join(., all_sta5a_total, by = c("fyqtr" = "fyqtr", "sta5a" = "sta5a")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  ungroup %>%
  left_join(., vast %>% select(sta5a, parent_visn, short_name)) %>%
  mutate(sta5a_lab = paste0("(", sta5a, ") ", short_name)) %>%
  left_join(., total_avg) %>%
  filter(sta5a %in% spokes_v)
#==BY CARE TYPE
crh_sta5a_type <- all_qtrs %>% left_join(., crh_encounters) %>%
  group_by(fyqtr, sta5a, care_type) %>%
  summarise(crh_encounters = n()) %>%
  ungroup
#
all_sta5a_type <- all_qtrs %>% left_join(., spoke_encounters) %>%
  select(4:7, sta5a, fyqtr) %>%
  pivot_longer(-c(fyqtr, sta5a)) %>%
  group_by(fyqtr, sta5a, name) %>%
  summarise(total = sum(value, na.rm = T)) %>%
  ungroup
#
type_avg <- crh_sta5a_type %>% 
  group_by(sta5a, care_type) %>%
  summarise(avg_crh_per_qtr = mean(crh_encounters, na.rm = T))
#
type_sta5a_df <- all_qtrs %>% 
  full_join(., crh_sta5a_type) %>%
  full_join(., all_sta5a_type, by = c("fyqtr" = "fyqtr", "care_type" = "name", "sta5a" = "sta5a")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  ungroup %>%
  left_join(., vast %>% select(sta5a, parent_visn, short_name)) %>%
  mutate(sta5a_lab = paste0("(", sta5a, ") ", short_name)) %>%
  left_join(., type_avg) %>%
  filter(sta5a %in% spokes_v)
#-------
access_metrics_sta5a <- access_metrics_sta5a %>%
  inner_join(., type_avg %>% filter(care_type == "Primary Care")) %>%
  filter(sta5a %in% spokes_v)
```

```{r sta5a_functions}
crh_plot_fxn_1 <- function(visn_var, care_type_var, metric){
  if (metric == "total"){
    y_axis <- paste0("Total ", care_type_var, " Encounters")
  }
  else if (metric == "crh_encounters"){
    y_axis <- paste0(care_type_var, " CRH Encounters")
  }
  else {
    y_axis <- paste0(care_type_var, " CRH Encounters per 1,000 ", care_type_var, " Encounters")
  }
  type_sta5a_df %>%
    filter(parent_visn == visn_var & avg_crh_per_qtr > 100 & care_type == care_type_var) %>% 
    select(-care_type) %>%
    mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                           fyqtr, crh_encounters)) %>%
    select(-c(sta5a, parent_visn, short_name)) %>%
    pivot_longer(-c(fyqtr, sta5a_lab)) %>%
    filter(name == metric) %>%
    ggplot(data = .,
           aes(y = value, x = fyqtr, group = sta5a_lab, color = sta5a_lab)) +
    geom_line(size = 1) +
    geom_point(size = 1) +
    scale_y_continuous(limits = c(0, NA),
                       labels = scales::comma_format(accuracy = 1)) +
    theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    labs(color = "Sta5a",
         x = "FY-Quarter",
         y = y_axis,
         caption = "*Legend is ordered by the last datapoint") +
    guides(color = guide_legend(override.aes = list(size = 1.25)))
}
#-------
crh_plot_fxn_2 <- function(visn_var, care_type_var, metric){
  if (metric == "total"){
    y_axis <- paste0("Total ", care_type_var, " Encounters")
  }
  else if (metric == "crh_encounters"){
    y_axis <- paste0(care_type_var, " CRH Encounters")
  }
  else {
    y_axis <- paste0(care_type_var, " CRH Encounters per 1,000 ", care_type_var, " Encounters")
  }
  type_sta5a_df %>%
    filter(parent_visn == visn_var & avg_crh_per_qtr <= 100 & care_type == care_type_var) %>% 
    select(-care_type) %>%
    mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                           fyqtr, crh_encounters)) %>%
    select(-c(sta5a, parent_visn, short_name)) %>%
    pivot_longer(-c(fyqtr, sta5a_lab)) %>%
    filter(name == metric) %>%
    ggplot(data = .,
           aes(y = value, x = fyqtr, group = sta5a_lab, color = sta5a_lab)) +
    geom_line(size = 1) +
    geom_point(size = 1) +
    scale_y_continuous(limits = c(0, NA),
                       labels = scales::comma_format(accuracy = 1)) +
    theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    labs(color = "Sta5a",
         x = "FY-Quarter",
         y = y_axis,
         caption = "*Legend is ordered by the last datapoint") +
    guides(color = guide_legend(override.aes = list(size = 1.25)))
}
#=====
crh_table_fxn <- function(visn_var, care_type_var){
  type_sta5a_df %>% 
    filter(parent_visn == visn_var & care_type == care_type_var) %>%
    select(fyqtr, sta5a_lab, crh_encounters, total, crh_per_1k_total) %>%
    mutate(crh_encounters = format(crh_encounters, digits = 0, big.mark = ","),
           total = format(total, digits = 0, big.mark = ","),
           crh_per_1k_total = format(round(crh_per_1k_total, 1), digits = 1)) %>%
    pivot_longer(-c(fyqtr, sta5a_lab)) %>%
    mutate(
      name_lab = case_when(
        name == "total" ~ "Total",
        name == "crh_per_1k_total" ~ "CRH per 1,000",
        name == "crh_encounters" ~ "CRH"),
      value = if_else(str_trim(value) == "NA", NA_character_, value)
    ) %>%
    select(-name) %>%
    pivot_wider(names_from = c(name_lab, fyqtr), values_from = value) %>%
    select(sta5a_lab, contains("20-1"), contains("20-2"), contains("20-3"), contains("20-4"),
           contains("21-1"), contains("21-2"), contains("21-3"), contains("21-4")) %>%
    kbl(col.names = c("Sta5a", rep(c("CRH Encounters", "Total", "CRH per 1,000"), 8)),
        align = c("l", rep("r", 24))) %>%
    kable_classic("striped") %>%
    add_header_above(bold = TRUE,
                     c(" ",
                       "2020-1" = 3, "2020-2" = 3, "2020-3" = 3, "2020-4" = 3,
                       "2021-1" = 3, "2021-2" = 3, "2021-3" = 3, "2021-4" = 3)) %>%
    column_spec(c(1, 4, 7, 10, 13, 16, 19, 22, 25), border_right = TRUE)
}
#========================
access_plot_1 <- function(visn_var, visn_var_quote, metric_var, metric_var_quote){
  if ({{metric_var_quote}} == "established_pt_waitTime"){
    y_axis <- "Established Patient Wait Time (days)"
  }
  else if ({{metric_var_quote}} == "new_pt_waitTime"){
    y_axis <- "New Patient Wait Time (days)"
  }
  else if ({{metric_var_quote}} == "obs_exp_panelSize_ratio"){
    y_axis <- "Observed:Expected Panel Size Ratio"
  }
  else {
    y_axis <- "Timely Care Success Rate"
  }
  #-
  if({{metric_var_quote}} == "established_pt_waitTime"){
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, established_pt_waitTime)) %>%
      ungroup
  }
  else if({{metric_var_quote}} == "new_pt_waitTime"){
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, new_pt_waitTime)) %>%
      ungroup
  }
  else if({{metric_var_quote}} == "obs_exp_panelSize_ratio"){
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, obs_exp_panelSize_ratio)) %>%
      ungroup
  }
  else {
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, tc_pc_success_prop)) %>%
      ungroup
  }
  #-
  if ({{metric_var_quote}} == "tc_pc_success_prop"){
  access_metrics_sta5a %>%
    filter(parent_visn == {{visn_var}}) %>%
    select(fy_qtr, sta5a_lab, {{metric_var_quote}}, avg_crh_per_qtr) %>%
    filter(avg_crh_per_qtr > 100) %>%
    ggplot(data = .,
           aes(x = fy_qtr, y = {{metric_var}}, color = sta5a_lab, group = sta5a_lab)) +
    geom_line(size = 1) +
    scale_y_continuous(limits = c(0, 1),
                       labels = scales::percent_format(accuracy = 1)) +
    theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    labs(color = "Sta5a",
         x = "FY-Quarter",
         y = y_axis,
         caption = "*Legend is ordered by the last datapoint") +
    guides(color = guide_legend(override.aes = list(size = 1.25)))
  }
  else {
    access_metrics_sta5a %>%
      filter(parent_visn == {{visn_var}}) %>%
      select(fy_qtr, sta5a_lab, {{metric_var_quote}}, avg_crh_per_qtr) %>%
      filter(avg_crh_per_qtr > 100) %>%
      ggplot(data = .,
             aes(x = fy_qtr, y = {{metric_var}}, color = sta5a_lab, group = sta5a_lab)) +
      geom_line(size = 1) +
      scale_y_continuous(limits = c(0, NA),
                         labels = scales::comma_format(accuracy = 1)) +
      theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
      labs(color = "Sta5a",
           x = "FY-Quarter",
           y = y_axis,
           caption = "*Legend is ordered by the last datapoint") +
      guides(color = guide_legend(override.aes = list(size = 1.25)))
  }
}
#----
access_plot_2 <- function(visn_var, visn_var_quote, metric_var, metric_var_quote){
  if ({{metric_var_quote}} == "established_pt_waitTime"){
    y_axis <- "Established Patient Wait Time (days)"
  }
  else if ({{metric_var_quote}} == "new_pt_waitTime"){
    y_axis <- "New Patient Wait Time (days)"
  }
  else if ({{metric_var_quote}} == "obs_exp_panelSize_ratio"){
    y_axis <- "Observed:Expected Panel Size Ratio"
  }
  else {
    y_axis <- "Timely Care Success Rate"
  }
  #-
  if({{metric_var_quote}} == "established_pt_waitTime"){
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, established_pt_waitTime)) %>%
      ungroup
  }
  else if({{metric_var_quote}} == "new_pt_waitTime"){
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, new_pt_waitTime)) %>%
      ungroup
  }
  else if({{metric_var_quote}} == "obs_exp_panelSize_ratio"){
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, obs_exp_panelSize_ratio)) %>%
      ungroup
  }
  else {
    access_metrics_sta5a <- access_metrics_sta5a %>%
      group_by({{visn_var_quote}}) %>%
      mutate(sta5a_lab = fct_reorder2(factor(sta5a_lab),
                                      fy_qtr, tc_pc_success_prop)) %>%
      ungroup
  }
  #-
  if ({{metric_var_quote}} == "tc_pc_success_prop"){
  access_metrics_sta5a %>%
    filter(parent_visn == {{visn_var}}) %>%
    select(fy_qtr, sta5a_lab, {{metric_var_quote}}, avg_crh_per_qtr) %>%
    filter(avg_crh_per_qtr <= 100) %>%
    ggplot(data = .,
           aes(x = fy_qtr, y = {{metric_var}}, color = sta5a_lab, group = sta5a_lab)) +
    geom_line(size = 1) +
    scale_y_continuous(limits = c(0, 1),
                       labels = scales::percent_format(accuracy = 1)) +
    theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    labs(color = "Sta5a",
         x = "FY-Quarter",
         y = y_axis,
         caption = "*Legend is ordered by the last datapoint") +
    guides(color = guide_legend(override.aes = list(size = 1.25)))
  }
  else {
    access_metrics_sta5a %>%
      filter(parent_visn == {{visn_var}}) %>%
      select(fy_qtr, sta5a_lab, {{metric_var_quote}}, avg_crh_per_qtr) %>%
      filter(avg_crh_per_qtr <= 100) %>%
      ggplot(data = .,
             aes(x = fy_qtr, y = {{metric_var}}, color = sta5a_lab, group = sta5a_lab)) +
      geom_line(size = 1) +
      scale_y_continuous(limits = c(0, NA),
                         labels = scales::comma_format(accuracy = 1)) +
      theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
      labs(color = "Sta5a",
           x = "FY-Quarter",
           y = y_axis,
           caption = "*Legend is ordered by the last datapoint") +
      guides(color = guide_legend(override.aes = list(size = 1.25)))
  }
}
#=================
access_table_fxn <- function(visn_var, metric_var_quote){
  access_metrics_sta5a %>%
    filter(parent_visn == visn_var) %>%
    select(fy_qtr, sta5a_lab, established_pt_waitTime, new_pt_waitTime,
           obs_exp_panelSize_ratio, tc_pc_success_prop) %>%
    mutate(established_pt_waitTime = format(established_pt_waitTime, 
                                            big.mark = ",", digits = 2),
           new_pt_waitTime = format(round(new_pt_waitTime, 1), 
                                    big.mark = ",", digits = 2),
           obs_exp_panelSize_ratio = format(obs_exp_panelSize_ratio, 
                                            big.mark = ",", digits = 1),
           tc_pc_success_prop = paste0(format(round(tc_pc_success_prop * 100, 1), nsmall = 2), "%")) %>%
    pivot_longer(-c(fy_qtr, sta5a_lab)) %>%
    filter(name == metric_var_quote) %>%
    pivot_wider(names_from = c(fy_qtr, name), values_from = value) %>%
    kbl(col.names = c("Sta5a", "2020-1", "2020-2", "2020-3", "2020-4",
                      "2021-1", "2021-2", "2021-3", "2021-4"),
        align = c("l", rep("r", 8))) %>%
    kable_classic("striped")
}
```

## Primary Care   
### PC CRH Encounters - I    
```{r}
crh_plot_fxn_1(visn_var = 6, "Primary Care", "crh_encounters")
```

### PC CRH Encounters - II    
```{r}
crh_plot_fxn_2(visn_var = 6, "Primary Care", "crh_encounters")
```

### Total PC Encounters - I    
```{r}
crh_plot_fxn_1(visn_var = 6, "Primary Care", "total")
```

### Total PC Encounters - II    
```{r}
crh_plot_fxn_2(visn_var = 6, "Primary Care", "crh_encounters")
```

### PC CRH Encounters per 1,000 Total PC Encounters - I    
```{r}
crh_plot_fxn_1(visn_var = 6, "Primary Care", "crh_per_1k_total")
```

### PC CRH Encounters per 1,000 Total PC Encounters - II    
```{r}
crh_plot_fxn_2(visn_var = 6, "Primary Care", "crh_per_1k_total")
```

### As a Table  
```{r}
crh_table_fxn(visn_var = 6, "Primary Care")
```

## Primary Care Access Metrics  
### Established Patient Wait Time - I  
```{r}
access_plot_1(visn_var = 6, visn_var_quote = "6", established_pt_waitTime, "established_pt_waitTime")
```
  
### Established Patient Wait Time - II  
```{r}
access_plot_2(visn_var = 6, visn_var_quote = "6", established_pt_waitTime, "established_pt_waitTime")
```

### As a Table  
```{r}
access_table_fxn(visn_var = 6, "established_pt_waitTime")
```
 
### New Patient Wait Time - I  
```{r}
access_plot_1(visn_var = 6, visn_var_quote = "6", new_pt_waitTime, "new_pt_waitTime")
```
  
### New Patient Wait Time - II  
```{r}
access_plot_2(visn_var = 6, visn_var_quote = "6", new_pt_waitTime, "new_pt_waitTime")
```

### As a Table  
```{r}
access_table_fxn(visn_var = 6, "new_pt_waitTime")
```
 
### Observed:Expected Panel Size Ratio - I  
```{r}
access_plot_1(visn_var = 6, visn_var_quote = "6", obs_exp_panelSize_ratio, "obs_exp_panelSize_ratio")
```
  
### Observed:Expected Panel Size Ratio - II  
```{r}
access_plot_2(visn_var = 6, visn_var_quote = "6", obs_exp_panelSize_ratio, "obs_exp_panelSize_ratio")
```
 
### As a Table  
```{r}
access_table_fxn(visn_var = 6, "obs_exp_panelSize_ratio")
```

### Timely Care Success Rate - I  
```{r}
access_plot_1(visn_var = 6, visn_var_quote = "6", tc_pc_success_prop, "tc_pc_success_prop")
```
  
### Timely Care Success Rate - II  
```{r}
access_plot_2(visn_var = 6, visn_var_quote = "6", tc_pc_success_prop, "tc_pc_success_prop")
```

### As a Table  
```{r}
access_table_fxn(visn_var = 6, "tc_pc_success_prop")
``` 


## Pharmacy   
### CPS CRH Encounters - I    
```{r}
crh_plot_fxn_1(visn_var = 6, "Pharmacy", "crh_encounters")
```

### CPS CRH Encounters - II    
```{r}
crh_plot_fxn_2(visn_var = 6, "Pharmacy", "crh_encounters")
```

### Total CPS Encounters - I    
```{r}
crh_plot_fxn_1(visn_var = 6, "Pharmacy", "total")
```

### Total CPS Encounters - II    
```{r}
crh_plot_fxn_2(visn_var = 6, "Pharmacy", "crh_encounters")
```

### CPS CRH Encounters per 1,000 Total CPS Encounters - I    
```{r}
crh_plot_fxn_1(visn_var = 6, "Pharmacy", "crh_per_1k_total")
```

### CPS CRH Encounters per 1,000 Total CPS Encounters - II    
```{r}
crh_plot_fxn_2(visn_var = 6, "Pharmacy", "crh_per_1k_total")
```

### As a Table  
```{r}
crh_table_fxn(visn_var = 6, "Pharmacy")
```