---
title: "CRH Encounters per 1,000 Total Encounters - VISN"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = '')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(ggrepel)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 24),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
hubs <- dbGetQuery(oabi_con,
                     "select hub_sta3n from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select hub_sta3n from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes_v <- spokes %>% pull
#
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#
vast_spokes <- vast %>%
  inner_join(., spokes, by = c("sta5a" = "spoke_sta5a"))
#==
all_months <- seq.Date(ymd('2019-10-01'),ymd('2021-09-01'), by = 'month')
#--
all_encounters <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].all_encounters_E_counts") %>%
  select(-contains("Vax")) %>%
  mutate(vizMonth = ymd(vizMonth)) %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", sta6a, ") ", short_name),
         spoke_flag = if_else(sta6a %in% spokes_v, TRUE, FALSE),
         fy = if_else(month(vizMonth) > 9, year(vizMonth) + 1, year(vizMonth)),
         qtr = case_when(month(vizMonth) %in% c(10, 11, 12) ~ 1,
                         month(vizMonth) %in% c(1, 2, 3) ~ 2,
                         month(vizMonth) %in% c(4, 5, 6) ~ 3,
                         month(vizMonth) %in% c(7, 8, 9) ~ 4)) %>%
  filter(is.na(parent_visn) == F & fy %in% c(2020, 2021)) %>%
  rename("Primary Care" = pc_encounters,
         "Mental Health" = mh_encounters,
         "Pharmacy" = pharmacy_encounters,
         "PCMHI" = pcmhi_encounters)
#
spoke_encounters <- all_encounters %>% filter(spoke_flag == T)
#==
crh_encounters <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].encounters_D_deDup") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(visitdate) > 9, year(visitdate) + 1, year(visitdate)),
         sta5a_to_use = if_else(spoke_sta5a %in% hubs$hub_sta3n | is.na(spoke_sta5a) == T, sta5a_most_freq, spoke_sta5a)) %>%
  filter(fy %in% c(2020, 2021) & care_type %ni% c("Specialty", "Missing")) %>%
  left_join(., vast, by = c("sta5a_to_use" = "sta5a")) %>%
  filter(is.na(parent_visn) == FALSE)
```

```{r creating_data_frames}
#--TOTAL
crh_visn_total <- crh_encounters %>%
  group_by(crh_month, parent_visn) %>%
  summarise(crh_encounters = n())
#
all_visn_total <- spoke_encounters %>%
  select(2:6, parent_visn) %>%
  pivot_longer(-c(vizMonth, parent_visn)) %>%
  group_by(vizMonth, parent_visn) %>%
  summarise(total = sum(value, na.rm = T))
#
total_visn_df <- crh_visn_total %>%
  left_join(., all_visn_total, by = c("crh_month" = "vizMonth", "parent_visn" = "parent_visn")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(parent_visn) == F) %>%
  ungroup %>%
  complete(crh_month = all_months, nesting(parent_visn))
#==BY CARE TYPE
crh_visn_type <- crh_encounters %>%
  group_by(crh_month, parent_visn, care_type) %>%
  summarise(crh_encounters = n())
#
all_visn_type <- spoke_encounters %>%
  select(2:6, parent_visn) %>%
  pivot_longer(-c(vizMonth, parent_visn)) %>%
  group_by(vizMonth, parent_visn, name) %>%
  summarise(total = sum(value, na.rm = T))
#
type_visn_df <- crh_visn_type %>%
  left_join(., all_visn_type, by = c("crh_month" = "vizMonth", "care_type" = "name", "parent_visn" = "parent_visn")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(parent_visn) == F) %>%
  ungroup %>%
  complete(crh_month = all_months, nesting(parent_visn, care_type))
```


# All VISNs  
## Total - I    
```{r total_1}
ggplot(data = total_visn_df,
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn, color = "1")) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 50),
                     labels = scales::comma_format(accuracy = 1)) +
  ggsci::scale_color_aaas() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  facet_wrap(~parent_visn) +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

\newpage

## Total - II  
```{r total_2}
total_visn_df %>% 
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         crh_month, crh_per_1k_total)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn_char, 
             color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 50),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(color = "VISN",
       x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

\newpage

## By Care Type - I   
### No PCMHI  
```{r type_no_pcmhi}
ggplot(data = subset(type_visn_df, care_type != "PCMHI"),
         aes(x = crh_month, y = crh_per_1k_total, group = care_type, color = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 80),
                     labels = scales::comma_format(accuracy = 1)) +
  ggsci::scale_color_aaas() +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  facet_wrap(~parent_visn) +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

\newpage

### PCMHI  
```{r type_pcmhi}
ggplot(data = subset(type_visn_df, care_type == "PCMHI"),
         aes(x = crh_month, y = crh_per_1k_total, group = care_type, color = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  ggsci::scale_color_aaas() +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  facet_wrap(~parent_visn) +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```


\newpage
## By Care Type - II  
### Mental Health  
```{r mental_health} 
type_visn_df %>% filter(care_type == "Mental Health") %>%
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         crh_month, crh_per_1k_total)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn_char, color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 80),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "Month",
       y = "CRH Mental Health Encounters/1,000 Mental Health Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2)
```

\newpage
### Primary Care  
```{r primary_care} 
type_visn_df %>% filter(care_type == "Primary Care") %>%
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         crh_month, crh_per_1k_total)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn_char, color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 40),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "Month",
       y = "CRH Primary Care Encounters/1,000 Primary Care Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2)
```

\newpage
### Pharmacy    
```{r pharmacy} 
type_visn_df %>% filter(care_type == "Pharmacy") %>%
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         crh_month, crh_per_1k_total)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn_char, color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 10),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "Month",
       y = "CRH Pharmacy Encounters/1,000 Pharmacy Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2)
```


\newpage
### PCMHI    
```{r pcmhi} 
type_visn_df %>% filter(care_type == "PCMHI") %>%
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         crh_month, crh_per_1k_total)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn_char, color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.title = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "Month",
       y = "CRH PCMHI Encounters/1,000 PCMHI Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2)
```


\newpage

```{r functions}
total_plot_fxn <- function(visn_var){
  ggplot(data = subset(total_visn_df, parent_visn == visn_var),
         aes(x = crh_month, y = crh_per_1k_total, group = parent_visn, color = "1")) +
    geom_line(size = 1) +
    geom_point() +
    scale_y_continuous(limits = c(0, 50),
                       labels = scales::comma_format(accuracy = 1)) +
    ggsci::scale_color_aaas() +
    guides(color = guide_legend(override.aes = list(size = 1.25))) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    labs(x = "Month",
         y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
    geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2)
}
#----
total_table_fxn <- function(visn_var){
  total_visn_df %>% filter(parent_visn == visn_var) %>%
    select(-parent_visn) %>%
    mutate(crh_per_1k_total = round(crh_per_1k_total, 1)) %>%
    rename("CRH Encounters" = crh_encounters,
           "Total" = total,
           "CRH/1,000 total" = crh_per_1k_total) %>%
    kbl(col.names = c("Month", "CRH Encounters", "Total Encounters", "CRH/1,000 Total"),
        format.args = list(big.mark = ","),
        align = c("l", rep("r", 4))) %>%
    kable_classic(latex_options = c("striped", "hold_position"))
}
#----
type_plot_fxn <- function(visn_var){
  ggplot(data = subset(type_visn_df, care_type != "PCMHI" & parent_visn == visn_var),
         aes(x = crh_month, y = crh_per_1k_total, group = care_type, color = care_type)) +
    geom_line(size = 1) +
    geom_point() +
    scale_y_continuous(limits = c(0, 80),
                       labels = scales::comma_format(accuracy = 1)) +
    ggsci::scale_color_aaas() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 270, vjust = 0.5)) +
    labs(x = "Month",
         y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
    geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
    facet_wrap(~care_type)
}
#----
type_plot_fxn2 <- function(visn_var){
  ggplot(data = subset(type_visn_df, care_type == "PCMHI" & parent_visn == visn_var),
         aes(x = crh_month, y = crh_per_1k_total, group = care_type, color = care_type)) +
  geom_line(size = 1) +
  geom_point() +
  scale_y_continuous(limits = c(0, 275),
                     labels = scales::comma_format(accuracy = 1)) +
  ggsci::scale_color_aaas() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.5)) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Vertical line at March 1st, 2020") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~care_type)
}
#----
type_table_fxn <- function(visn_var){
  type_visn_df %>%
  filter(parent_visn == visn_var) %>%
  ungroup %>%
  select(-parent_visn) %>%
  mutate(crh_per_1k_total = round(crh_per_1k_total, 1)) %>%
  pivot_longer(-c(crh_month, care_type)) %>%
  pivot_wider(names_from = c(care_type, name), values_from = value) %>%
  select(crh_month, contains("Mental"), contains("Primary")) %>%
  kbl(col.names = c("Month",
                    rep(c("CRH", "Total", "CRH/1,000"), 2)),
      align = c("l", rep("r", 6)),
      format.args = list(big.mark = ",")) %>%
  column_spec(c(4), border_right = T) %>%
  kable_classic(latex_options = c("striped", "hold_position")) %>%
  add_header_above(c(" " = 1, "Mental Health" = 3, "Primary Care" = 3))
}
#----
type_table_fxn2 <- function(visn_var){
    type_visn_df %>%
    filter(parent_visn == visn_var) %>%
    ungroup %>%
    select(-parent_visn) %>%
    mutate(crh_per_1k_total = round(crh_per_1k_total, 1)) %>%
    pivot_longer(-c(crh_month, care_type)) %>%
    pivot_wider(names_from = c(care_type, name), values_from = value) %>%
    select(crh_month, contains("Pharmacy"), contains("PCMHI")) %>%
    kbl(col.names = c("Month",
                      rep(c("CRH", "Total", "CRH/1,000"), 2)),
        align = c("l", rep("r", 6)),
        format.args = list(big.mark = ",")) %>%
    column_spec(c(4), border_right = T) %>%
    kable_classic(latex_options = c("striped", "hold_position")) %>%
    add_header_above(c(" " = 1, "Pharmacy" = 3, "PCMHI" = 3))
}
```

# VISN 1   
## Total  
```{r}
total_plot_fxn(1)
```

\newpage

### As a Table  

```{r}
total_table_fxn(1)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(1)
```

\newpage


```{r}
type_plot_fxn2(1)
```

\newpage

### As a Table  

```{r}
type_table_fxn(1)
```

\newpage

```{r}
type_table_fxn2(1)
```

\newpage

# VISN 2   
## Total  
```{r}
total_plot_fxn(2)
```

\newpage

### As a Table  

```{r}
total_table_fxn(2)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(2)
```

\newpage


```{r}
type_plot_fxn2(2)
```

\newpage

### As a Table  

```{r}
type_table_fxn(2)
```

\newpage

```{r}
type_table_fxn2(2)
```

\newpage

# VISN 4   
## Total  
```{r}
total_plot_fxn(4)
```

\newpage

### As a Table  

```{r}
total_table_fxn(4)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(4)
```

\newpage


```{r}
type_plot_fxn2(4)
```

\newpage

### As a Table  

```{r}
type_table_fxn(4)
```

\newpage

```{r}
type_table_fxn2(4)
```

# VISN 5   
## Total  
```{r}
total_plot_fxn(5)
```

\newpage

### As a Table  

```{r}
total_table_fxn(5)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(5)
```

\newpage


```{r}
type_plot_fxn2(5)
```

\newpage

### As a Table  

```{r}
type_table_fxn(5)
```

\newpage

```{r}
type_table_fxn2(5)
```

# VISN 6   
## Total  
```{r}
total_plot_fxn(6)
```

\newpage

### As a Table  

```{r}
total_table_fxn(6)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(6)
```

\newpage


```{r}
type_plot_fxn2(6)
```

\newpage

### As a Table  

```{r}
type_table_fxn(6)
```

\newpage

```{r}
type_table_fxn2(6)
```

\newpage

# VISN 7   
## Total  
```{r}
total_plot_fxn(7)
```

\newpage

### As a Table  

```{r}
total_table_fxn(7)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(7)
```

\newpage


```{r}
type_plot_fxn2(7)
```

\newpage

### As a Table  

```{r}
type_table_fxn(1)
```

\newpage

```{r}
type_table_fxn2(7)
```

\newpage

# VISN 8   
## Total  
```{r}
total_plot_fxn(8)
```

\newpage

### As a Table  

```{r}
total_table_fxn(8)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(8)
```

\newpage


```{r}
type_plot_fxn2(8)
```

\newpage

### As a Table  

```{r}
type_table_fxn(8)
```

\newpage

```{r}
type_table_fxn(8)
```

\newpage

# VISN 9   
## Total  
```{r}
total_plot_fxn(9)
```

\newpage

### As a Table  

```{r}
total_table_fxn(9)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(9)
```

\newpage


```{r}
type_plot_fxn2(9)
```

\newpage

### As a Table  

```{r}
type_table_fxn(9)
```

\newpage

```{r}
type_table_fxn2(9)
```

\newpage

# VISN 10   
## Total  
```{r}
total_plot_fxn(10)
```

\newpage

### As a Table  

```{r}
total_table_fxn(10)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(10)
```

\newpage


```{r}
type_plot_fxn2(10)
```

\newpage

### As a Table  

```{r}
type_table_fxn(10)
```

\newpage

```{r}
type_table_fxn2(10)
```

\newpage

# VISN 12   
## Total  
```{r}
total_plot_fxn(12)
```

\newpage

### As a Table  

```{r}
total_table_fxn(12)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(12)
```

\newpage


```{r}
type_plot_fxn2(12)
```

\newpage

### As a Table  

```{r}
type_table_fxn(12)
```

\newpage

```{r}
type_table_fxn2(12)
```

\newpage

# VISN 15   
## Total  
```{r}
total_plot_fxn(15)
```

\newpage

### As a Table  

```{r}
total_table_fxn(15)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(15)
```

\newpage


```{r}
type_plot_fxn2(15)
```

\newpage

### As a Table  

```{r}
type_table_fxn(15)
```

\newpage

```{r}
type_table_fxn2(15)
```

\newpage


# VISN 16   
## Total  
```{r}
total_plot_fxn(16)
```

\newpage

### As a Table  

```{r}
total_table_fxn(16)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(16)
```

\newpage


```{r}
type_plot_fxn2(16)
```

\newpage

### As a Table  

```{r}
type_table_fxn(16)
```

\newpage

```{r}
type_table_fxn2(16)
```

\newpage

# VISN 17   
## Total  
```{r}
total_plot_fxn(17)
```

\newpage

### As a Table  

```{r}
total_table_fxn(17)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(17)
```

\newpage


```{r}
type_plot_fxn2(17)
```

\newpage

### As a Table  

```{r}
type_table_fxn(17)
```

\newpage

```{r}
type_table_fxn2(17)
```

\newpage


# VISN 19   
## Total  
```{r}
total_plot_fxn(19)
```

\newpage

### As a Table  

```{r}
total_table_fxn(19)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(19)
```

\newpage


```{r}
type_plot_fxn2(19)
```

\newpage

### As a Table  

```{r}
type_table_fxn(19)
```

\newpage

```{r}
type_table_fxn2(19)
```

\newpage

# VISN 20   
## Total  
```{r}
total_plot_fxn(20)
```

\newpage

### As a Table  

```{r}
total_table_fxn(20)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(20)
```

\newpage


```{r}
type_plot_fxn2(20)
```

\newpage

### As a Table  

```{r}
type_table_fxn(20)
```

\newpage

```{r}
type_table_fxn2(20)
```

\newpage


# VISN 21   
## Total  
```{r}
total_plot_fxn(21)
```

\newpage

### As a Table  

```{r}
total_table_fxn(21)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(21)
```

\newpage


```{r}
type_plot_fxn2(21)
```

\newpage

### As a Table  

```{r}
type_table_fxn(21)
```

\newpage

```{r}
type_table_fxn2(21)
```

\newpage

# VISN 22   
## Total  
```{r}
total_plot_fxn(22)
```

\newpage

### As a Table  

```{r}
total_table_fxn(22)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(22)
```

\newpage


```{r}
type_plot_fxn2(22)
```

\newpage

### As a Table  

```{r}
type_table_fxn(22)
```

\newpage

```{r}
type_table_fxn2(22)
```

\newpage

# VISN 23   
## Total  
```{r}
total_plot_fxn(23)
```

\newpage

### As a Table  

```{r}
total_table_fxn(23)
```

\newpage

## By Care Type  

```{r}
type_plot_fxn(23)
```

\newpage


```{r}
type_plot_fxn2(23)
```

\newpage

### As a Table  

```{r}
type_table_fxn(23)
```

\newpage

```{r}
type_table_fxn2(23)
```