---
title: "Primary Care CRH Encounters & Primary Care Access Metrics"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```



```{r reading-in}
hubs <- dbGetQuery(oabi_con,
                   "select distinct hub_sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY20]
                    UNION 
                    select distinct Hub_Sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY21_working]") %>%
  pull
#--
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes_v <- spokes %>% pull
#
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#
vast_spokes <- vast %>%
  inner_join(., spokes, by = c("sta5a" = "spoke_sta5a"))
#==
all_encounters <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].all_encounters_E_counts") %>%
  select(-contains("Vax")) %>%
  mutate(vizMonth = ymd(vizMonth)) %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", sta6a, ") ", short_name),
         spoke_flag = if_else(sta6a %in% spokes_v, TRUE, FALSE),
         fy = if_else(month(vizMonth) > 9, year(vizMonth) + 1, year(vizMonth)),
         qtr = case_when(month(vizMonth) %in% c(10, 11, 12) ~ 1,
                         month(vizMonth) %in% c(1, 2, 3) ~ 2,
                         month(vizMonth) %in% c(4, 5, 6) ~ 3,
                         month(vizMonth) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  filter(is.na(parent_visn) == F & fy %in% c(2020, 2021)) %>%
  rename("Primary Care" = pc_encounters,
         "Mental Health" = mh_encounters,
         "Pharmacy" = pharmacy_encounters,
         "PCMHI" = pcmhi_encounters)
#
all_qtrs <- all_encounters %>% select(fyqtr) %>% distinct
#
spoke_encounters <- all_encounters %>% filter(spoke_flag == T)
#-----
crh_encounters <- dbGetQuery(oabi_con,
                         "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  filter(fy %in% c(2020, 2021) & care_type %in% c("Primary Care", "Pharmacy")) %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a"))
#--==================
access_metrics_sta5a <- read_csv(here("Input", "Data", "pc_access_metrics_sta5a_qtr.csv")) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop)
#
access_metrics_visn <- read_csv(here("Input", "Data", "pc_access_metrics_visn_qtr.csv")) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop)
#
access_metrics_nat <- read_csv(here("Input", "Data", "pc_access_metrics_nat_qtr.csv")) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop)
```

```{r creating_nat_data_frames}
#--TOTAL
crh_nat_total <- crh_encounters %>%
  group_by(fyqtr) %>%
  summarise(crh_encounters = n()) %>%
  ungroup
#
all_nat_total <- spoke_encounters %>%
  select(3:6, 23) %>%
  pivot_longer(-c(fyqtr)) %>%
  group_by(fyqtr) %>%
  summarise(total = sum(value, na.rm = T)) %>%
  ungroup
#
total_nat_df <- all_qtrs %>%
  full_join(., crh_nat_total) %>%
  full_join(., all_nat_total, by = c("fyqtr" = "fyqtr")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  ungroup
#==BY CARE TYPE
crh_nat_type <- crh_encounters %>%
  group_by(fyqtr, care_type) %>%
  summarise(crh_encounters = n()) %>%
  ungroup
#
all_nat_type <- spoke_encounters %>%
  select(3:6, fyqtr) %>%
  pivot_longer(-c(fyqtr)) %>%
  group_by(fyqtr, name) %>%
  summarise(total = sum(value, na.rm = T)) %>%
  ungroup
#
type_nat_df <- all_qtrs %>%
  full_join(., crh_nat_type) %>%
  full_join(., all_nat_type, by = c("fyqtr" = "fyqtr", "care_type" = "name")) %>%
  mutate(crh_per_1k_total = round(crh_encounters / total * 1000, 1)) %>%
  ungroup
```

```{r creating_visn_data_frames}
#--TOTAL
crh_visn_total <- crh_encounters %>%
  group_by(fyqtr, parent_visn) %>%
  summarise(crh_encounters = n()) %>%
  ungroup
#
all_visn_total <- all_qtrs %>% left_join(., spoke_encounters) %>%
  select(4:7, parent_visn, fyqtr) %>%
  pivot_longer(-c(fyqtr, parent_visn)) %>%
  group_by(fyqtr, parent_visn) %>%
  summarise(total = sum(value, na.rm = T)) %>%
  ungroup
#
total_visn_df <- all_qtrs %>%
  full_join(., crh_visn_total) %>%
  full_join(., all_visn_total, by = c("fyqtr" = "fyqtr", "parent_visn" = "parent_visn")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(parent_visn) == F) %>%
  ungroup
#==BY CARE TYPE
crh_visn_type <- crh_encounters %>%
  group_by(fyqtr, parent_visn, care_type) %>%
  summarise(crh_encounters = n()) %>%
  ungroup
#
all_visn_type <- all_qtrs %>% left_join(., spoke_encounters) %>%
  select(4:7, parent_visn, fyqtr) %>%
  pivot_longer(-c(fyqtr, parent_visn)) %>%
  group_by(fyqtr, parent_visn, name) %>%
  summarise(total = sum(value, na.rm = T)) %>%
  ungroup
#
type_visn_df <- all_qtrs %>%
  full_join(., crh_visn_type) %>%
  full_join(., all_visn_type, by = c("fyqtr" = "fyqtr", "care_type" = "name", 
                                     "parent_visn" = "parent_visn")) %>%
  mutate(crh_per_1k_total = crh_encounters / total * 1000) %>%
  filter(is.na(parent_visn) == F) %>%
  ungroup
```

# National  
## Primary Care CRH    
```{r}
type_nat_df %>%
  filter(care_type == "Primary Care") %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  ggsci::scale_color_lancet()+
  theme(axis.title.y = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  facet_wrap_custom(~name_lab, scales = 'free', ncol = 2,
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0, 60000), 
                                                           labels = scales::comma_format())),
                      scale_override(2, scale_y_continuous(limits = c(0, 16), 
                                                           labels = scales::comma_format(accuracy = 1))),
                      scale_override(3, scale_y_continuous(limits = c(0, 4000000), 
                                                           labels = scales::comma_format()))
                    )) +
  labs(x = "FY-Qtr")
```

## CRH Per 1,000 Total  

```{r}
type_nat_df %>%
  filter(care_type == "Primary Care") %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  filter(name == "crh_per_1k_total") %>%
  ggplot(data = .,
         aes(x = fyqtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1, color = "blue") +
  ggsci::scale_color_lancet()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(x = "FY-Qtr",
       y = "PC CRH Encounters per 1,000 Total PC Encounters") +
  scale_y_continuous(limits = c(0, 15))
```

## CRH PC Encounters    

```{r}
type_nat_df %>%
  filter(care_type == "Primary Care") %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  filter(name == "crh_encounters") %>%
  ggplot(data = .,
         aes(x = fyqtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1, color = "forestgreen") +
  ggsci::scale_color_lancet()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(x = "FY-Qtr",
       y = "PC CRH Encounters") +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1))
```

### As a Table  

```{r}
type_nat_df %>% filter(care_type == "Primary Care") %>%
  mutate(crh_encounters = format(crh_encounters, digits = 0, big.mark = ","),
         total = format(total, digits = 0, big.mark = ","),
         crh_per_1k_total = format(crh_per_1k_total, digits = 2)) %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  select(-name) %>%
  pivot_wider(names_from = fyqtr, values_from = value) %>%
  kbl(col.names = c(" ", "2020-1", "2020-2", "2020-3", "2020-4",
                              "2021-1", "2021-2", "2021-3", "2021-4"),
      align = c("l", rep("r", 8))) %>%
  kable_classic("striped")
```

## Primary Care Access Metrics  
```{r}
access_metrics_nat %>%
  pivot_longer(-fy_qtr) %>%
  mutate(name_lab = case_when(
    name == "established_pt_waitTime" ~ "Established Pt WT",
    name == "new_pt_waitTime" ~ "New Pt WT",
    name == "obs_exp_panelSize_ratio" ~ "Obs:Exp Panel Size",
    name == "tc_pc_success_prop" ~ "Timely Care Success"
  )) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  ggsci::scale_color_uchicago() +
  theme(axis.title.y = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  facet_wrap_custom(~name_lab, scales = 'free', ncol = 2,
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0, 60), 
                                                           labels = scales::comma_format())),
                      scale_override(2, scale_y_continuous(limits = c(0, 60), 
                                                           labels = scales::comma_format(accuracy = 1))),
                      scale_override(3, scale_y_continuous(limits = c(0, 1), 
                                                           labels = scales::comma_format())),
                      scale_override(4, scale_y_continuous(limits = c(0, 1), 
                                                           labels = scales::percent_format(accuracy = 1)))
                    ))
```

### As a Table  
```{r}
access_metrics_nat %>%
  mutate(obs_exp_panelSize_ratio = round(obs_exp_panelSize_ratio, 2),
         tc_pc_success_prop = round(tc_pc_success_prop * 100, 1)) %>%
  pivot_longer(-fy_qtr) %>%
  mutate(name_lab = case_when(
    name == "established_pt_waitTime" ~ "Established Patient WT",
    name == "new_pt_waitTime" ~ "New Patient WT",
    name == "obs_exp_panelSize_ratio" ~ "Obs:Exp Panel Size Ratio",
    name == "tc_pc_success_prop" ~ "Timely Care Success (%)"
  )) %>%
  select(-name) %>%
  mutate(value = round(value, 1)) %>%
  pivot_wider(names_from = fy_qtr, values_from = value) %>%
  kbl(col.names = c(" ", "2020-1", "2020-2", "2020-3", "2020-4",
                              "2021-1", "2021-2", "2021-3", "2021-4")) %>%
  kable_classic("striped")
```

## Pharmacy CRH    
```{r}
type_nat_df %>%
  filter(care_type == "Pharmacy") %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  ggsci::scale_color_lancet()+
  theme(axis.title.y = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  facet_wrap_custom(~name_lab, scales = 'free', ncol = 2,
                    scale_overrides = list(
                      scale_override(1, scale_y_continuous(limits = c(0, 25000), 
                                                           labels = scales::comma_format())),
                      scale_override(2, scale_y_continuous(limits = c(0, 20), 
                                                           labels = scales::comma_format(accuracy = 1))),
                      scale_override(3, scale_y_continuous(limits = c(0, 1500000), 
                                                           labels = scales::comma_format()))
                    )) +
  labs(x = "FY-Qtr")
```

### CRH Per 1,000 Total  

```{r}
type_nat_df %>%
  filter(care_type == "Pharmacy") %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  filter(name == "crh_per_1k_total") %>%
  ggplot(data = .,
         aes(x = fyqtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1, color = "blue") +
  ggsci::scale_color_lancet()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(x = "FY-Qtr",
       y = "CPS CRH Encounters per 1,000 Total CPS Encounters") +
  scale_y_continuous(limits = c(0, 20))
```

### CRH CPS Encounters    

```{r}
type_nat_df %>%
  filter(care_type == "Pharmacy") %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  filter(name == "crh_encounters") %>%
  ggplot(data = .,
         aes(x = fyqtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1, color = "forestgreen") +
  ggsci::scale_color_lancet()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(x = "FY-Qtr",
       y = "CPS CRH Encounters") +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1))
```

### As a Table  

```{r}
type_nat_df %>% filter(care_type == "Pharmacy") %>%
  mutate(crh_encounters = format(crh_encounters, digits = 0, big.mark = ","),
         total = format(total, digits = 0, big.mark = ","),
         crh_per_1k_total = format(crh_per_1k_total, digits = 2)) %>%
  select(-care_type) %>%
  pivot_longer(-fyqtr) %>%
  mutate(name_lab = case_when(
    name == "total" ~ "Total",
    name == "crh_per_1k_total" ~ "CRH/1,000",
    name == "crh_encounters" ~ "CRH"
  )) %>%
  select(-name) %>%
  pivot_wider(names_from = fyqtr, values_from = value) %>%
  kbl(col.names = c(" ", "2020-1", "2020-2", "2020-3", "2020-4",
                              "2021-1", "2021-2", "2021-3", "2021-4"),
      align = c("l", rep("r", 8))) %>%
  kable_classic("striped")
```




# VISN  
## Primary Care CRH  
### CRH per 1,000 Total          
```{r}
type_visn_df %>% 
  filter(care_type == "Primary Care") %>%
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         fyqtr, crh_per_1k_total)) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = crh_per_1k_total, group = parent_visn_char, 
             color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 35),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(color = "VISN",
       x = "FY-Quarter",
       y = "CRH PC Encounters per 1,000 Total PC Encounters",
       caption = "*Legend is ordered by the last datapoint") +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

### CRH Encounters    
```{r}
type_visn_df %>% 
  filter(care_type == "Primary Care") %>% 
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         fyqtr, crh_encounters)) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = crh_encounters, group = parent_visn_char, 
             color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(color = "VISN",
       x = "FY-Quarter",
       y = "CRH PC Encounters",
       caption = "*Legend is ordered by the last datapoint") +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

### Total Encounters    
```{r}
type_visn_df %>% 
  filter(care_type == "Primary Care") %>% 
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         fyqtr, total)) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = total, group = parent_visn_char, 
             color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(color = "VISN",
       x = "FY-Quarter",
       y = "Total PC Encounters",
       caption = "*Legend is ordered by the last datapoint") +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

### As a Table  
```{r}
type_visn_df %>% 
  filter(care_type == "Primary Care") %>%
  select(-care_type) %>%
  mutate(parent_visn = str_pad(parent_visn, side = "left", width = 2, pad = "0"),
         crh_encounters = format(crh_encounters, digits = 0, big.mark = ","),
         total = format(total, digits = 0, big.mark = ","),
         crh_per_1k_total = format(crh_per_1k_total, digits = 1)) %>%
  pivot_longer(-c(parent_visn, fyqtr)) %>%
  pivot_wider(names_from = c(fyqtr, name), values_from = value) %>%
  arrange(parent_visn) %>%
  kbl(col.names = c("VISN", rep(c("CRH Encounters", "Total", "CRH per 1,000"), 8)),
      align = c("l", rep("r", 24))) %>%
  kable_classic("striped") %>%
  add_header_above(c(" ",
                     "2020-1" = 3, "2020-2" = 3, "2020-3" = 3, "2020-4" = 3,
                     "2021-1" = 3, "2021-2" = 3, "2021-3" = 3, "2021-4" = 3)) %>%
  column_spec(c(1, 4, 7, 10, 13, 16, 19, 22, 25), border_right = TRUE)
```

## Primary Care Access Metrics  

### Established Patient Wait Time - I    
```{r}
access_metrics_visn %>%
  mutate(visn = fct_reorder2(factor(visn),
                                         fy_qtr, established_pt_waitTime),
         fy_qtr = str_replace(fy_qtr, "_", "-")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = established_pt_waitTime, group = visn,
             color = visn)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "Established Patient Wait Time (days)",
       caption = "*Legend is ordered by the last datapoint",
       color = "VISN")

```

### Established Patient Wait Time - II    
```{r}
access_metrics_visn %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = established_pt_waitTime, group = visn)) +
  geom_line(size = 1, color = "blue3") +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "Established Patient Wait Time (days)") +
  facet_wrap(~visn)
```

### As a Table  
```{r}
access_metrics_visn %>%
  select(-parent_visn) %>%
  mutate(established_pt_waitTime = format(established_pt_waitTime, digits = 3),
         new_pt_waitTime = format(new_pt_waitTime, digits = 2),
         obs_exp_panelSize_ratio = format(obs_exp_panelSize_ratio, digits = 2),
         tc_pc_success_prop = paste0(format(round(tc_pc_success_prop * 100, 1), nsmall = 1), "%")) %>%
  select(visn, fy_qtr, established_pt_waitTime) %>%
  pivot_longer(-c(visn, fy_qtr)) %>%
  pivot_wider(names_from = c(fy_qtr, name), values_from = value) %>%
  arrange(visn) %>%
  kbl(col.names = c("VISN", "2020-1", "2020-2", "2020-3", "2020-4",
                              "2021-1", "2021-2", "2021-3", "2021-4"),
      align = c("l", rep("r", 8))) %>%
  kable_classic("striped")

```


### New Patient Wait Time - I    
```{r}
access_metrics_visn %>%
  mutate(visn = fct_reorder2(factor(visn),
                                         fy_qtr, new_pt_waitTime),
         fy_qtr = str_replace(fy_qtr, "_", "-")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = new_pt_waitTime, group = visn,
             color = visn)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "New Patient Wait Time (days)",
       caption = "*Legend is ordered by the last datapoint",
       color = "VISN")

```

### New Patient Wait Time - II    
```{r}
access_metrics_visn %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = new_pt_waitTime, group = visn)) +
  geom_line(size = 1, color = "blue3") +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "New Patient Wait Time (days)") +
  facet_wrap(~visn)
```

### As a Table  
```{r}
access_metrics_visn %>%
  select(-parent_visn) %>%
  mutate(established_pt_waitTime = format(established_pt_waitTime, digits = 2),
         new_pt_waitTime = format(new_pt_waitTime, digits = 2),
         obs_exp_panelSize_ratio = format(obs_exp_panelSize_ratio, digits = 2),
         tc_pc_success_prop = paste0(format(round(tc_pc_success_prop * 100, 1), nsmall = 1), "%")) %>%
  select(visn, fy_qtr, new_pt_waitTime) %>%
  pivot_longer(-c(visn, fy_qtr)) %>%
  pivot_wider(names_from = c(fy_qtr, name), values_from = value) %>%
  arrange(visn) %>%
  kbl(col.names = c("VISN", "2020-1", "2020-2", "2020-3", "2020-4",
                              "2021-1", "2021-2", "2021-3", "2021-4"),
      align = c("l", rep("r", 8))) %>%
  kable_classic("striped")

```

### Observed:Expected Panel Size Ratio - I    
```{r}
access_metrics_visn %>%
  mutate(visn = fct_reorder2(factor(visn),
                                         fy_qtr, obs_exp_panelSize_ratio),
         fy_qtr = str_replace(fy_qtr, "_", "-")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = obs_exp_panelSize_ratio, group = visn,
             color = visn)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0.5, 1),
                     labels = scales::comma_format(accuracy = 0.1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "Observed:Expected Panel Size Ratio",
       caption = "*Legend is ordered by the last datapoint",
       color = "VISN")

```

### Observed:Expected Panel Size Ratio - II    
```{r}
access_metrics_visn %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = obs_exp_panelSize_ratio, group = visn)) +
  geom_line(size = 1, color = "blue3") +
  scale_y_continuous(limits = c(0.5, 1),
                     labels = scales::comma_format(accuracy = 0.1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "Observed:Expected Panel Size Ratio") +
  facet_wrap(~visn)
```

### As a Table  
```{r}
access_metrics_visn %>%
  select(-parent_visn) %>%
  mutate(established_pt_waitTime = format(established_pt_waitTime, digits = 2),
         new_pt_waitTime = format(new_pt_waitTime, digits = 2),
         obs_exp_panelSize_ratio = format(obs_exp_panelSize_ratio, digits = 2),
         tc_pc_success_prop = paste0(format(round(tc_pc_success_prop * 100, 1), nsmall = 1), "%")) %>%
  select(visn, fy_qtr, obs_exp_panelSize_ratio) %>%
  pivot_longer(-c(visn, fy_qtr)) %>%
  pivot_wider(names_from = c(fy_qtr, name), values_from = value) %>%
  arrange(visn) %>%
  kbl(col.names = c("VISN", "2020-1", "2020-2", "2020-3", "2020-4",
                              "2021-1", "2021-2", "2021-3", "2021-4"),
      align = c("l", rep("r", 8))) %>%
  kable_classic("striped")

```

### Timely Care Success Rate - I    
```{r}
access_metrics_visn %>%
  mutate(visn = fct_reorder2(factor(visn),
                                         fy_qtr, tc_pc_success_prop),
         fy_qtr = str_replace(fy_qtr, "_", "-")) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = tc_pc_success_prop, group = visn,
             color = visn)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0.5, 1),
                     labels = scales::percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "Timely Care Success Rate",
       caption = "*Legend is ordered by the last datapoint",
       color = "VISN")

```

### Timely Care Success Rate - II    
```{r}
access_metrics_visn %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = tc_pc_success_prop, group = visn)) +
  geom_line(size = 1, color = "blue3") +
  scale_y_continuous(limits = c(0.5, 1),
                     labels = scales::percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  guides(color = guide_legend(override.aes = list(size = 1.25))) +
  labs(x = "FY-Quarter",
       y = "Timely Care Success Rate") +
  facet_wrap(~visn)
```

### As a Table  
```{r}
access_metrics_visn %>%
  select(-parent_visn) %>%
  mutate(established_pt_waitTime = format(established_pt_waitTime, digits = 2),
         new_pt_waitTime = format(new_pt_waitTime, digits = 2),
         obs_exp_panelSize_ratio = format(obs_exp_panelSize_ratio, digits = 2),
         tc_pc_success_prop = paste0(format(round(tc_pc_success_prop * 100, 1), nsmall = 1), "%")) %>%
  select(visn, fy_qtr, tc_pc_success_prop) %>%
  pivot_longer(-c(visn, fy_qtr)) %>%
  pivot_wider(names_from = c(fy_qtr, name), values_from = value) %>%
  arrange(visn) %>%
  kbl(col.names = c("VISN", "2020-1", "2020-2", "2020-3", "2020-4",
                              "2021-1", "2021-2", "2021-3", "2021-4"),
      align = c("l", rep("r", 8))) %>%
  kable_classic("striped")

```

## Pharmacy CRH  
### CRH per 1,000 Total          
```{r}
type_visn_df %>% 
  filter(care_type == "Pharmacy") %>%
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         fyqtr, crh_per_1k_total)) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = crh_per_1k_total, group = parent_visn_char, 
             color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, 35),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(color = "VISN",
       x = "FY-Quarter",
       y = "CRH CPS Encounters per 1,000 Total Encounters",
       caption = "*Legend is ordered by the last datapoint") +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

### CRH Encounters    
```{r}
type_visn_df %>% 
  filter(care_type == "Pharmacy") %>% 
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         fyqtr, crh_encounters)) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = crh_encounters, group = parent_visn_char, 
             color = parent_visn_char)) +
  geom_line(size = 1) +
  geom_point() +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(color = "VISN",
       x = "FY-Quarter",
       y = "CRH CPS Encounters",
       caption = "*Legend is ordered by the last datapoint") +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

### Total Encounters    
```{r}
type_visn_df %>% 
  filter(care_type == "Pharmacy") %>% 
  mutate(parent_visn_char = fct_reorder2(factor(str_pad(parent_visn, side = "left", width = 2, pad = 0)),
                                         fyqtr, total)) %>%
  ggplot(data = .,
         aes(x = fyqtr, y = total, group = parent_visn_char, 
             color = parent_visn_char)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  labs(color = "VISN",
       x = "FY-Quarter",
       y = "Total CPS Encounters",
       caption = "*Legend is ordered by the last datapoint") +
  guides(color = guide_legend(override.aes = list(size = 1.25)))
```

### As a Table  
```{r}
type_visn_df %>% 
  filter(care_type == "Pharmacy") %>%
  select(-care_type) %>%
  mutate(parent_visn = str_pad(parent_visn, side = "left", width = 2, pad = "0"),
         crh_encounters = format(crh_encounters, digits = 0, big.mark = ","),
         total = format(total, digits = 0, big.mark = ","),
         crh_per_1k_total = format(crh_per_1k_total, digits = 1)) %>%
  pivot_longer(-c(parent_visn, fyqtr)) %>%
  pivot_wider(names_from = c(fyqtr, name), values_from = value) %>%
  arrange(parent_visn) %>%
  kbl(col.names = c("VISN", rep(c("CRH Encounters", "Total", "CRH per 1,000"), 8)),
      align = c("l", rep("r", 24))) %>%
  kable_classic("striped") %>%
  add_header_above(c(" ",
                     "2020-1" = 3, "2020-2" = 3, "2020-3" = 3, "2020-4" = 3,
                     "2021-1" = 3, "2021-2" = 3, "2021-3" = 3, "2021-4" = 3)) %>%
  column_spec(c(1, 4, 7, 10, 13, 16, 19, 22, 25), border_right = TRUE)
```