---
title: "Primary Care CRH: OOS Sites & Access Metrics (Outcomes)"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 8, fig.height = 8)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
##---------- Connection to PACT_CC
pactcc_con <- dbConnect(odbc::odbc(),
                        Driver = "SQL Server",
                        Server = "vhacdwsql13.vha.med.va.gov",
                        Database = "PACT_CC",
                        Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
```

```{r reading-in}
#=========================
# VAST
vast <- read_csv(here("Input", "Data", "vast_from_a06_17mar22.csv"))
#----
# crh flags
crh_flags <- dbGetQuery(oabi_con,
                        "select * from [crh_eval].yoon_flag")
#=============================
# access metrics
access_metrics_sta5a <- read_csv(here("Input", "Data", "pc_access_metrics.csv")) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop) %>%
  left_join(., crh_flags) %>%
  mutate(table_1_columns = factor(case_when(yoon_flag == 1 ~ "CRH",
                                            crh_flag == 1 & yoon_flag == 0 ~ "Not Enough CRH",
                                            is.na(crh_flag) == T ~ "No CRH",
                                            TRUE ~ "Uh-oh"), 
                                  ordered = TRUE,
                                  levels = c("CRH", "Not Enough CRH", "No CRH")))
```

# 1: Do All OOS Sites Have Wait Times?  
```{r}
crh_flags_w_sAbbr <- crh_flags %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%
  distinct %>%
  mutate(table_1_columns = factor(case_when(yoon_flag == 1 ~ "CRH",
                                            crh_flag == 1 & yoon_flag == 0 ~ "Not Enough CRH",
                                            is.na(crh_flag) == T ~ "No CRH",
                                            TRUE ~ "Uh-oh"), 
                                  ordered = TRUE,
                                  levels = c("CRH", "Not Enough CRH", "No CRH")))
```

* There are `r crh_flags_w_sAbbr %>% filter(s_abbr == "OOS" & table_1_columns == "CRH") %>% select(sta5a) %>% n_distinct` sta5as that have at least 2 consecutive months with > 5 PC CRH encounters __AND__ that are classified as __OOS__
* Out of those, `r crh_flags_w_sAbbr %>% filter(s_abbr == "OOS" & table_1_columns == "CRH" & sta5a %in% access_metrics_sta5a$sta5a) %>% select(sta5a) %>% n_distinct` sta5as have __New Patient Wait Time:__

```{r}
access_metrics_sta5a %>% 
  select(sta5a, vssc_month, new_pt_waitTime) %>%
  inner_join(crh_flags_w_sAbbr) %>%
  filter(table_1_columns == "CRH"
         & s_abbr == "OOS") %>%
  left_join(., vast %>% select(sta5a, parent_visn, short_name)) %>%
  mutate(name_lab = paste0("V", parent_visn, ", ", sta5a)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = new_pt_waitTime, group = sta5a)) +
  geom_line() +
  facet_wrap(~name_lab) +
  labs(y = "New Patient Wait Time (days)") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.4))
```

* The `r crh_flags_w_sAbbr %>% filter(s_abbr == "OOS" & table_1_columns == "CRH" & sta5a %ni% access_metrics_sta5a$sta5a) %>% select(sta5a) %>% n_distinct` sta5a that does not have __New Patient Wait Time__ is __618QA__, the Fort Snelling VA Clinic 
    + In fact, __618QA__ does not contribute any PC Access Metrics
    
## 1a: What proportion of _all_ CRH sites contribute PC Access Metrics?  
* There are `r crh_flags_w_sAbbr %>% filter(table_1_columns == "CRH") %>% select(sta5a) %>% n_distinct` sta5as that have at least 2 consecutive months with > 5 PC CRH encounters
* Out of those, `r crh_flags_w_sAbbr %>% filter(table_1_columns == "CRH" & sta5a %in% access_metrics_sta5a$sta5a) %>% select(sta5a) %>% n_distinct` sta5as have __New Patient Wait Time__
* The `r crh_flags_w_sAbbr %>% filter(table_1_columns == "CRH" & sta5a %ni% access_metrics_sta5a$sta5a) %>% select(sta5a) %>% n_distinct` sta5a that does not have __New Patient Wait Time__ is __618QA__, the Fort Snelling VA Clinic   

# 2: New Patient Wait Time  
## 2a: New Patient Wait Time X CRH Status  
```{r}
access_metrics_sta5a %>%
  select(sta5a, new_pt_waitTime) %>%
  group_by(sta5a) %>%
  summarise(mean_new_pt_wt = mean(new_pt_waitTime, na.rm = T)) %>%
  left_join(., crh_flags)  %>%
  mutate(table_1_columns = factor(case_when(yoon_flag == 1 ~ "CRH",
                                            crh_flag == 1 & yoon_flag == 0 ~ "Not Enough CRH",
                                            is.na(crh_flag) == T ~ "No CRH",
                                            TRUE ~ "Uh-oh"), 
                                  ordered = TRUE,
                                  levels = c("CRH", "Not Enough CRH", "No CRH"))) %>%
  ggplot(data = .,
         aes(x = table_1_columns, y = mean_new_pt_wt, fill = table_1_columns)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Mean New Patient Wait Time")
```

## 2b: New Patient Wait Time X Site Type  
```{r}
access_metrics_sta5a %>%
  select(sta5a, new_pt_waitTime) %>%
  group_by(sta5a) %>%
  summarise(mean_new_pt_wt = mean(new_pt_waitTime, na.rm = T)) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  filter(is.na(s_abbr) == F) %>%
  ggplot(data = .,
         aes(x = s_abbr, y = mean_new_pt_wt, fill = s_abbr)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Mean New Patient Wait Time")
```


## 2c: New Patient Wait Time X URH  
```{r}
access_metrics_sta5a %>%
  select(sta5a, new_pt_waitTime) %>%
  group_by(sta5a) %>%
  summarise(mean_new_pt_wt = mean(new_pt_waitTime, na.rm = T)) %>%
  left_join(., vast %>% select(sta5a, urh_vast)) %>%
  filter(is.na(urh_vast) == F) %>%
  mutate(urh2 = if_else(urh_vast == "U", "Urban", "Rural")) %>%
  ggplot(data = .,
         aes(x = urh2, y = mean_new_pt_wt, fill = urh2)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Mean New Patient Wait Time")
```

# 3: Timely Care    
## 3a: Timely Car X CRH Status  
```{r}
access_metrics_sta5a %>%
  select(sta5a, tc_pc_success_prop) %>%
  group_by(sta5a) %>%
  summarise(mean_pc_tc = mean(tc_pc_success_prop, na.rm = T)) %>%
  left_join(., crh_flags)  %>%
  mutate(table_1_columns = factor(case_when(yoon_flag == 1 ~ "CRH",
                                            crh_flag == 1 & yoon_flag == 0 ~ "Not Enough CRH",
                                            is.na(crh_flag) == T ~ "No CRH",
                                            TRUE ~ "Uh-oh"), 
                                  ordered = TRUE,
                                  levels = c("CRH", "Not Enough CRH", "No CRH"))) %>%
  ggplot(data = .,
         aes(x = table_1_columns, y = mean_pc_tc, fill = table_1_columns)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::percent_format()) +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Mean Timely Care")
```

## 3b: Timely Care X Site Type  
```{r}
access_metrics_sta5a %>%
  select(sta5a, tc_pc_success_prop) %>%
  group_by(sta5a) %>%
  summarise(mean_pc_tc = mean(tc_pc_success_prop, na.rm = T)) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  filter(is.na(s_abbr) == F) %>%
  ggplot(data = .,
         aes(x = s_abbr, y = mean_pc_tc, fill = s_abbr)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::percent_format()) +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Mean Timely Care")
```


## 3c: Timely Care X URH  
```{r}
access_metrics_sta5a %>%
  select(sta5a, tc_pc_success_prop) %>%
  group_by(sta5a) %>%
  summarise(mean_pc_tc = mean(tc_pc_success_prop, na.rm = T)) %>%
  left_join(., vast %>% select(sta5a, urh_vast)) %>%
  filter(is.na(urh_vast) == F) %>%
  mutate(urh2 = if_else(urh_vast == "U", "Urban", "Rural")) %>%
  ggplot(data = .,
         aes(x = urh2, y = mean_pc_tc, fill = urh2)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::percent_format()) +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Mean Timely Care")
```
