---
title: "PC CRH Matching"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r}
sta5a_demog <- dbGetQuery(oabi_con,
                          "select vast.sta5a
	, at_least_10_pc_crh_flag = case	
		when crh_flag.crh_10_flag <> 1 then 0
		else 1 end
	, vast.parent_visn
	, urh = case 
		when vast.urh_vast = 'U' then 'U'
		when vast.urh_vast <> 'U' then 'R'
		end
	, vast.census_division
	, vast.s_abbr
	, vssc.nosos_3mo_avg
	, vssc.obs_exp_panel_ratio_3mo_avg
	, vssc.team_pcp_ap_fte_total_3mo_avg
	, pcmm.pcmm_scrssn_count
	, access.est_pc_pt_wt_3mo_avg
	, access.new_pc_pt_wt_3mo_avg
	, access.third_next_avail_3mo_avg
	, adi.adi_natRnk_avg
	, age.avg_age_oct1_2020
	, prop_male = cast(demog.male_count as float) / cast(demog.scrssn_count as float)
	, prop_white = cast(demog.race_white_count as float) / cast(demog.scrssn_count as float)
	, prop_rural = cast(demog.urh_rural_count as float) / cast(demog.scrssn_count as float)
from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as vast
left join [OABI_MyVAAccess].[crh_eval].C1_crh_flag as crh_flag
	on vast.sta5a = crh_flag.sta5a
left join [OABI_MyVAAccess].[crh_eval].F1_3_vssc_3mo_avg as vssc
	on vast.sta5a = vssc.sta5a
left join [OABI_MyVAAccess].[crh_eval].F2_pcmm_scrssn_count_avg as pcmm
	on vast.sta5a = pcmm.sta5a
left join [OABI_MyVAAccess].[crh_eval].F3_access_metrics_3mo_avg as access
	on vast.sta5a = access.sta5a
left join [OABI_MyVAAccess].[crh_eval].F4_adi_avg as adi
	on vast.sta5a = adi.sta5a
left join [OABI_MyVAAccess].[crh_eval].D1_age_sta5a_qtr as age
	on vast.sta5a = age.Sta5a
left join [OABI_MyVAAccess].[crh_eval].D2_race_gender_urh_count as demog
	on vast.sta5a = demog.Sta5a
where age.FY = 2020 AND age.QTR = 1
	AND demog.fy = 2020 AND demog.qtr = 1") %>%
  mutate(parent_visn = factor(parent_visn),
         adi_cat = case_when(adi_natRnk_avg < 25 ~ "0-24",
                             adi_natRnk_avg >= 25 & adi_natRnk_avg < 50 ~ "25-49",
                             adi_natRnk_avg >= 50 & adi_natRnk_avg < 75 ~ "50-74",
                             adi_natRnk_avg >= 75 ~ "75-100"),
         treat = if_else(at_least_10_pc_crh_flag == 1, 0, 1),
         s_abbr2 = case_when(s_abbr %in% c("MSCBOC", "PCCBOC") ~ "CBOC",
                             s_abbr %in% c("HCC", "VAMC") ~ "VAMC/HCC",
                             TRUE ~ s_abbr))
#
sta5a_demog_no_missing <- sta5a_demog %>%
  drop_na()
#
#sta5a_demog %>% filter(sta5a %ni% sta5a_demog_no_missing$sta5a)
```

# Nearest Neighbor (1:1) Matching  
* Model: Treatment = 
    + Parent VISN (Exact)
    + Census Division
    + NOSOS (3 month average)
    + Observed:Expected PC Panel Size (3 month average)
    + Team PCP/AP FTE (3 month average)
    + Uniques in PCMM (2 quarter average)
    + Established patient wait time (3 month average)
    + New patient wait time (3 month average)
    + Third next available (3 month average)
    + ADI (3 month average)
    + Average age October 1st, 2020
    + Proportion male
    + Proportion white
    + Proportion rural

* Out of `r nrow(sta5a_demog) %>% comma(accuracy = 1)` sta5as included, `r nrow(sta5a_demog_no_missing) %>% comma(accuracy = 1)` have complete data for all of these covariates

```{r}
#-- nearest neighbor (1:1) matching
nn_match <- matchit(treat ~ 
                        parent_visn 
                      + census_division 
                      + s_abbr2
                      + nosos_3mo_avg
                      + obs_exp_panel_ratio_3mo_avg
                      + team_pcp_ap_fte_total_3mo_avg
                      + pcmm_scrssn_count
                      + est_pc_pt_wt_3mo_avg
                      + new_pc_pt_wt_3mo_avg
                      + third_next_avail_3mo_avg
                      + adi_natRnk_avg
                      + avg_age_oct1_2020
                      + prop_male 
                      + prop_white
                      + prop_rural,
                      data = sta5a_demog_no_missing,
                      method = "nearest",
                      distance = "glm",
                      link = "logit",
                      exact = ~parent_visn)
#
nn_get_matches <- get_matches(nn_match)
#
print(nn_match)
```

* This yields `r nrow(nn_get_matches) / 2` pairs 

```{r}
plot(nn_match, type = "jitter", interactive = FALSE)
```

```{r}
plot(summary(nn_match), position = NULL)
```

# Optimal Matching  
* Model: Treatment = 
    + Parent VISN (Exact)
    + Census Division
    + NOSOS (3 month average)
    + Observed:Expected PC Panel Size (3 month average)
    + Team PCP/AP FTE (3 month average)
    + Uniques in PCMM (2 quarter average)
    + Established patient wait time (3 month average)
    + New patient wait time (3 month average)
    + Third next available (3 month average)
    + ADI (3 month average)
    + Average age October 1st, 2020
    + Proportion male
    + Proportion white
    + Proportion rural

* Out of `r nrow(sta5a_demog) %>% comma(accuracy = 1)` sta5as included, `r nrow(sta5a_demog_no_missing) %>% comma(accuracy = 1)` have complete data for all of these covariates

```{r}
#-- optimal matching
opt_match <- matchit(treat ~ 
                        parent_visn 
                      + census_division 
                      + s_abbr2
                      + nosos_3mo_avg
                      + obs_exp_panel_ratio_3mo_avg
                      + team_pcp_ap_fte_total_3mo_avg
                      + pcmm_scrssn_count
                      + est_pc_pt_wt_3mo_avg
                      + new_pc_pt_wt_3mo_avg
                      + third_next_avail_3mo_avg
                      + adi_natRnk_avg
                      + avg_age_oct1_2020
                      + prop_male 
                      + prop_white
                      + prop_rural,
                      data = sta5a_demog_no_missing,
                      method = "optimal",
                      distance = "glm",
                      link = "logit",
                      exact = ~parent_visn)
#
opt_get_matches <- get_matches(opt_match)
#
print(opt_match)
```


* This yields `r nrow(opt_get_matches) / 2` pairs 


```{r}
plot(opt_match, type = "jitter", interactive = FALSE)
```

```{r}
plot(summary(opt_match), position = NULL)
```


# Full Matching  
* Model: Treatment = 
    + Parent VISN (Exact)
    + Census Division
    + NOSOS (3 month average)
    + Observed:Expected PC Panel Size (3 month average)
    + Team PCP/AP FTE (3 month average)
    + Uniques in PCMM (2 quarter average)
    + Established patient wait time (3 month average)
    + New patient wait time (3 month average)
    + Third next available (3 month average)
    + ADI (3 month average)
    + Average age October 1st, 2020
    + Proportion male
    + Proportion white
    + Proportion rural

* Out of `r nrow(sta5a_demog) %>% comma(accuracy = 1)` sta5as included, `r nrow(sta5a_demog_no_missing) %>% comma(accuracy = 1)` have complete data for all of these covariates

```{r}
#-- full matching
full_match <- matchit(treat ~ 
                        parent_visn 
                      + census_division 
                      + s_abbr2
                      + nosos_3mo_avg
                      + obs_exp_panel_ratio_3mo_avg
                      + team_pcp_ap_fte_total_3mo_avg
                      + pcmm_scrssn_count
                      + est_pc_pt_wt_3mo_avg
                      + new_pc_pt_wt_3mo_avg
                      + third_next_avail_3mo_avg
                      + adi_natRnk_avg
                      + avg_age_oct1_2020
                      + prop_male 
                      + prop_white
                      + prop_rural,
                      data = sta5a_demog_no_missing,
                      method = "full",
                      distance = "glm",
                      link = "logit",
                      exact = ~parent_visn)
#
full_get_matches <- match.data(full_match)
#
print(full_match)
```

* This yields a match between all `r sum(1-sta5a_demog_no_missing$at_least_10_pc_crh_flag)` treated sta5as and at least 1 control sta5a, for a total of `r max(as.integer(full_get_matches$subclass))` groups

```{r}
full_get_matches %>% 
  filter(treat == 1) %>%
  group_by(subclass) %>% 
  summarise(count = n()) %>%
  ggplot(data = .,
         aes(x = count)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Number of Treated Matched",
       y = "Sta5a Count in Bin")
```

```{r}
full_get_matches %>% 
  filter(treat == 0) %>%
  group_by(subclass) %>% 
  summarise(count = n()) %>%
  ggplot(data = .,
         aes(x = count)) +
  geom_histogram(binwidth = 1) +
  labs(x = "Number of Controls Matched",
       y = "Sta5a Count in Bin")
```


```{r}
plot(full_match, type = "jitter", interactive = FALSE)
```

```{r}
plot(summary(full_match), position = NULL)
```

# Distribution of PC CRH Start Month  

```{r}
start_month <- dbGetQuery(oabi_con,
                          "select * from [OABI_MyVAAccess].[crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh)) %>%
  filter(is.na(first_mo_w_mt9_pc_crh) == F)
#--
ggplot(data = start_month,
       aes(x = first_mo_w_mt9_pc_crh)) +
  geom_histogram(bins = 26, color = "black", fill = "red") +
  scale_x_date(breaks=  "2 months") +
  theme(axis.text.x = element_text(angle = 270, hjust = 0.3, vjust = 0.3)) +
  labs(x = "First Month (of dyad) w/>9 PC CRH Encounters",
       y = "Number of Sta5as")
```