---
title: "PC CRH: PCMM Count & Covariates"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_connect <- dbConnect(odbc::odbc(), Driver = "SQL Server", 
                          Server = "vhacdwsql13.vha.med.va.gov",
                          Database = "OABI_MyVAAccess", 
                          Trusted_Connection = "true"
)
# VAST
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv")) %>%
  mutate(parent_visn = str_pad(parent_visn, side = 'left', width = 2, pad = "0"))
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#==========================================
# PC CRH Encounters
pc_crh_encounters <- dbGetQuery(oabi_connect,
                                "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a")) %>%
  rename(sta5a = spoke_sta5a_combined_cdw) %>%
  filter(fy %in% c(2020, 2021) 
         & care_type == "Primary Care")
#
pc_crh_sta5a_qtr <- pc_crh_encounters %>%
  group_by(sta5a, fyqtr, fy) %>%
  summarise(pc_crh_encounters = n())
#
pc_crh_sta5as <- pc_crh_sta5a_qtr %>%
  select(sta5a) %>% distinct %>% pull
#==============================
# Unique ScrSSNs, Race, gender, and URH
race_gender_urh <- dbGetQuery(oabi_connect,
                              "select * from [OABI_MyVAAccess].[crh_eval].[pcmm_pssg_race_gender_count]") %>%
  mutate(male_prop = male_count / scrssn_count,
         female_prop = female_count / scrssn_count,
         race_white_prop = race_white_count / scrssn_count,
         race_black_prop = race_black_count / scrssn_count,
         race_other_prop = race_other_count / scrssn_count,
         race_missing_prop = race_missing / scrssn_count,
         urh_urban_prop = urh_urban_count / scrssn_count,
         urh_rural_prop = urh_rural_count / scrssn_count,
         fy_qtr = str_c(FY, QTR, sep = "-"),
         scrssn_count_cat = factor(case_when(
           scrssn_count < 1750 ~ "< 1,750",
           scrssn_count >= 1750 & scrssn_count < 4500 ~ "1,750 - 4,499",
           scrssn_count >= 4500 & scrssn_count < 7250 ~ "4,500 - 7,249",
           scrssn_count >= 7250 & scrssn_count < 15000 ~ "7,250 - 14,999",
           scrssn_count >= 15000 ~ "15,000+"
         ),
         ordered = T, levels = c("< 1,750","1,750 - 4,499","4,500 - 7,249","7,250 - 14,999","15,000+"))) %>%
  rename_all(tolower) %>%
  left_join(., vast) %>%
  mutate(pc_crh_flag = if_else(sta5a %in% pc_crh_sta5as, "PC CRH Site", "Not a PC CRH Site"))
#====================================
# ADI
adi <- dbGetQuery(oabi_connect,
                  "select * from [OABI_MyVAAccess].[crh_eval].[adi_sta5a_qtr]") %>%
  left_join(., vast, by = c("Sta5a" = "sta5a")) %>%
  filter(is.na(parent_visn) == F & state %in% state.abb) %>%
  mutate(fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  rename(sta5a = Sta5a)
```


# Review   
## PC CRH Encounters per Quarter (total)      
```{r}
p1_crh <- pc_crh_sta5a_qtr %>%
  ggplot(data = .,
         aes(x = pc_crh_encounters)) +
  geom_histogram(color = "black", fill = "red") +
  scale_x_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters", 
       y = "Sta5a-Quarters")
#
p2_crh <- pc_crh_sta5a_qtr %>%
  ggplot(data = .,
         aes(x = "x", y = pc_crh_encounters)) +
  geom_boxplot(color = "black", fill = "darkorchid3") +
  labs(y = "PC CRH Encounters per Quarter") +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())
#--
multiplot(p1_crh, p2_crh, cols = 2)
```

## Maximum Number of PC CRH Encounters per Quarter - Everything          
```{r}
p1_crh <- pc_crh_sta5a_qtr %>%
  group_by(sta5a) %>%
  summarise(pc_crh_encounters = max(pc_crh_encounters)) %>%
  ggplot(data = .,
         aes(x = pc_crh_encounters)) +
  geom_histogram(color = "black", fill = "blue") +
  scale_x_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters", 
       y = "Sta5a-Quarters")
#
p2_crh <- pc_crh_sta5a_qtr %>%
  group_by(sta5a) %>%
  summarise(pc_crh_encounters = max(pc_crh_encounters)) %>%
  ggplot(data = .,
         aes(x = "x", y = pc_crh_encounters)) +
  geom_boxplot(color = "black", fill = "firebrick") +
  labs(y = "PC CRH Encounters per Quarter") +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())
#--
multiplot(p1_crh, p2_crh, cols = 2)
```

## Maximum Number of PC CRH Encounters per Quarter - 1-50          
```{r}
p1_crh <- pc_crh_sta5a_qtr %>%
  filter(pc_crh_encounters < 51) %>%
  group_by(sta5a) %>%
  summarise(pc_crh_encounters = max(pc_crh_encounters)) %>%
  ggplot(data = .,
         aes(x = pc_crh_encounters)) +
  geom_histogram(color = "black", fill = "seagreen2", bins = 50) +
  scale_x_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters", 
       y = "Sta5a-Quarters")
#
p2_crh <- pc_crh_sta5a_qtr %>%
  filter(pc_crh_encounters < 51) %>%
  group_by(sta5a) %>%
  summarise(pc_crh_encounters = max(pc_crh_encounters)) %>%
  ggplot(data = .,
         aes(x = "x", y = pc_crh_encounters)) +
  geom_boxplot(color = "black", fill = "forestgreen") +
  labs(y = "PC CRH Encounters per Quarter") +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())
#--
multiplot(p1_crh, p2_crh, cols = 2)
```


## Unique ScrSSNs in PCMM FY2021, Q4           
```{r}
p1_scrssn_count <- race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = scrssn_count)) +
  geom_histogram(color = "black", fill = "darkorange2") +
  scale_y_continuous(labels = scales::comma_format()) +
  scale_x_continuous(labels = scales::comma_format()) +
  labs(x = "Unique ScrSSNs", 
       y = "Sta5as")
#
p2_scrssn_count <- race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = "x", y = scrssn_count)) +
  geom_boxplot(color = "black", fill = "seagreen") +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "Unique ScrSSNs")
#==
multiplot(p1_scrssn_count, p2_scrssn_count, cols = 2)
```

## Unique ScrSSNs in PCMM FY2021, Q4 - by CRH Site yes/no       
```{r}
p1_scrssn_count <- race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = scrssn_count, color = "black", fill = pc_crh_flag)) +
  geom_histogram(color = "black") +
  scale_y_continuous(labels = scales::comma_format()) +
  scale_x_continuous(labels = scales::comma_format()) +
  labs(y = "Sta5as") +
  facet_wrap(~pc_crh_flag) +
  theme(axis.title.x = element_blank(),
        legend.position = "none")
#
p2_scrssn_count <- race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = pc_crh_flag, y = scrssn_count, fill = pc_crh_flag)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "Unique ScrSSNs")
#==
multiplot(p1_scrssn_count, p2_scrssn_count, cols = 2)
```

# Proposing Categories of Unique ScrSSNs FY2021, Q4    
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n()) %>%
  kbl(col.names = c("Unique ScrSSNs", "Sta5as")) %>%
  kable_classic("striped", full_width = F)
#
race_gender_urh %>%
  filter(fy_qtr == "2021-4" & is.na(s_abbr) == F) %>%
  janitor::tabyl(scrssn_count_cat, s_abbr) %>%
  janitor::adorn_totals(where = c("row", "col")) %>%
  kbl(col.names = c("Unique ScrSSNs", "HCC", "MSCBOC", "OOS", "PCCBOC", "VAMC", "Total")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = TRUE)
#
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  janitor::tabyl(scrssn_count_cat, pc_crh_flag) %>%
  janitor::adorn_totals(where = c("row", "col")) %>%
  kbl(col.names = c("Unique ScrSSNs", "Not a PC CRH Site", "PC CRH Site", "Total")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = TRUE)
#
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(.,
         aes(y = scrssn_count, x = "x", fill = scrssn_count_cat)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Unique ScrSSNs",
       fill = "Unique ScrSSNs")
```

## PC CRH Site, yes/no    
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(.,
         aes(y = scrssn_count, x = pc_crh_flag, fill = scrssn_count_cat)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Unique ScrSSNs",
       fill = "Unique ScrSSNs")
```

## PC CRH Encounters by Categorical ScrSSN  
```{r}
pc_crh_sta5a_qtr %>%
  left_join(., race_gender_urh %>% filter(fy_qtr == "2021-4"), by = c("sta5a" = "sta5a")) %>%
  filter(is.na(scrssn_count_cat) == F) %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n()) %>%
  janitor::adorn_totals() %>%
  mutate(count = scales::comma(count, accuracy = 1)) %>%
  kbl(col.names = c("Unique ScrSSNs", "Sta5a-Quarters"),
      align = c("l", "r")) %>%
  kable_classic("striped",
                full_width = F)
#
pc_crh_sta5a_qtr %>%
  left_join(., race_gender_urh %>% filter(fy_qtr == "2021-4")) %>%
  filter(is.na(scrssn_count_cat) == F) %>%
  ggplot(data = .,
         aes(x = scrssn_count_cat, y = pc_crh_encounters, fill = scrssn_count_cat)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "Unique ScrSSNs",
       y = "PC CRH Encounters per Quarter") +
  theme(legend.position = "none")
  
```

# Other Covariates  

## Average ADI FY2021, Q4    
```{r}
adi_p1 <- adi %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = adi_natRnk_avg)) +
  geom_histogram(color = "black", fill = "dodgerblue3") +
  labs(x = "Average ADI of Patient's Home Address",
       y = "Sta5as")
#
adi_p2 <- adi %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(y = adi_natRnk_avg)) +
  geom_boxplot(fill = "red", color = "black") +
  scale_y_continuous(limits = c(0, 100)) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Average ADI of Patient's Home Address")
#--
multiplot(adi_p1, adi_p2, cols = 2)
```

## Average ADI FY2021, Q4 by PC CRH Site yes/no    
```{r}
adi %>%
  filter(fy_qtr == "2021-4") %>% mutate(crh_flag = if_else(sta5a %in% pc_crh_sta5as, "PC CRH Site", "Not a PC CRH Site")) %>%
  ggplot(data = .,
         aes(y = adi_natRnk_avg, x = crh_flag, fill = crh_flag)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = "Average ADI of Patient's Home Address") +
  theme(axis.title.x = element_blank(),
        legend.position = "none")
```

## Average ADI FY2021, Q4 by ScrSSN Count Category      
```{r}
adi %>%
  filter(fy_qtr == "2021-4") %>%
  left_join(., race_gender_urh %>% filter(fy_qtr == "2021-4") %>% select(sta5a, scrssn_count_cat)) %>%
  ggplot(data = .,
         aes(y = adi_natRnk_avg, x = scrssn_count_cat, fill = scrssn_count_cat)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = "Average ADI of Patient's Home Address") +
  theme(axis.title.x = element_blank(),
        legend.position = "none")
```

## Proportion Male  
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = "x", y = male_prop)) +
  geom_boxplot(color = "black",
               fill = "darkseagreen") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = "Proportion Male") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())
```

## Proportion Male, by Categorical ScrSSN Count    
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = "x", y = male_prop, fill = scrssn_count_cat)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(y = "Proportion Male") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none") +
  facet_wrap(~scrssn_count_cat) +
  ggsci::scale_fill_jco()
```

  
## Proportion White    
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = "x", y = race_white_prop)) +
  geom_boxplot(color = "black",
               fill = "cyan3") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0,1)) +
  labs(y = "Proportion White") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())
```

## Proportion White, by Categorical ScrSSN Count    
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = "x", y = race_white_prop, fill = scrssn_count_cat)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0, 1)) +
  labs(y = "Proportion White") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none") +
  facet_wrap(~scrssn_count_cat) +
  ggsci::scale_fill_aaas()
```

  
## Proportion Urban    
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = "x", y = urh_urban_prop)) +
  geom_boxplot(color = "black",
               fill = "cadetblue3") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0,1)) +
  labs(y = "Proportion Urban") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())
```

## Proportion Urban, by Categorical ScrSSN Count    
```{r}
race_gender_urh %>%
  filter(fy_qtr == "2021-4") %>%
  ggplot(data = .,
         aes(x = "x", y = urh_urban_prop, fill = scrssn_count_cat)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0, 1)) +
  labs(y = "Proportion Urban") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none") +
  facet_wrap(~scrssn_count_cat) +
  ggsci::scale_fill_d3()
```
