---
title: "CRH"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r}
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#===================
hubs <- dbGetQuery(oabi_con,
                   "select distinct hub_sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY20]
                    UNION 
                    select distinct Hub_Sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY21_working]") %>%
  pull
#--
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes_v <- spokes %>% pull
#
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#
vast_spokes <- vast %>%
  inner_join(., spokes, by = c("sta5a" = "spoke_sta5a"))
#-----
crh_encounters <- dbGetQuery(oabi_con,
                             "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  filter(fy %in% c(2020, 2021) & care_type == "Primary Care") %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a")) %>%
  rename(sta5a = spoke_sta5a_combined_cdw)
#====================================================================================
crh_sta5a_month <- crh_encounters %>%
  group_by(sta5a, crh_month) %>%
  summarise(pc_crh_encounters = n()) %>%
  left_join(., vast %>% select(sta5a, short_name, s_abbr)) %>%
  filter(is.na(s_abbr) == FALSE)
# ======--------
sta5a_month_summary <- crh_sta5a_month %>%
  mutate(mnth_w_lt6 = if_else(pc_crh_encounters < 6, 1, 0),
         mnth_w_gt5 = if_else(pc_crh_encounters > 5, 1, 0)) %>%
  group_by(sta5a) %>%
  summarise(lt6 = sum(mnth_w_lt6),
            gt5 = sum(mnth_w_gt5),
            both_lt6_and_gt5 = if_else(lt6 > 0 & gt5 > 0, TRUE, FALSE),
            only_lt6 = if_else(lt6 > 0 & gt5 == 0, 1, 0),
            only_gt5 = if_else(lt6 == 0 & gt5 > 0, 1, 0),
            has_both = sum(both_lt6_and_gt5),
            only_lt6 = sum(only_lt6),
            only_gt5 = sum(only_gt5))
#  
crh_sta5a_month <- crh_sta5a_month %>%
  left_join(., sta5a_month_summary)
```

* There are a total of `r nrow(crh_sta5a_month)` sta5a-months with __> 0__ PC CRH encounters
* `r crh_sta5a_month %>% filter(pc_crh_encounters < 6) %>% select(sta5a, crh_month) %>% n_distinct` out of those `r nrow(crh_sta5a_month)` (`r round((crh_sta5a_month %>% filter(pc_crh_encounters < 6) %>% select(sta5a, crh_month) %>% n_distinct) / nrow(crh_sta5a_month) * 100, 1)`%) have __< 6__ PC CRH encounters


---

* There are a total of `r nrow(sta5a_month_summary)` unique sta5as
* Out of those:
    + `r sum(sta5a_month_summary$has_both)` (`r round(sum(sta5a_month_summary$has_both) / nrow(sta5a_month_summary) * 100, 1)`%) have at least one month with __< 6__ and one month with __> 5__ PC CRH encounters
    + `r sum(sta5a_month_summary$only_lt6)` (`r round(sum(sta5a_month_summary$only_lt6) / nrow(sta5a_month_summary) * 100, 1)`%) only have months with __< 6__ PC CRH encounters
    + `r sum(sta5a_month_summary$only_gt5)` (`r round(sum(sta5a_month_summary$only_gt5) / nrow(sta5a_month_summary) * 100, 1)`%) only have months with __> 5__ PC CRH encounters
    
---

## Distribution of PC CRH Encounters per Month  
### All Together  

```{r}
ggplot(data = crh_sta5a_month,
       aes(x = pc_crh_encounters)) +
  geom_histogram(bins = 100, color = "black", fill = "red") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters",
       y = "Sta5a-Months")
```

### Sta5a with both < 6 and > 5 months   
```{r}
ggplot(data = subset(crh_sta5a_month, has_both == T),
       aes(x = pc_crh_encounters)) +
  geom_histogram(bins = 100, color = "black", fill = "forestgreen") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters",
       y = "Sta5a-Months")
```

### Sta5a with only < 6 months     
```{r}
ggplot(data = subset(crh_sta5a_month, only_lt6 == T),
       aes(x = pc_crh_encounters)) +
  geom_histogram(bins = 5, color = "black", fill = "royalblue") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters",
       y = "Sta5a-Months")
```

### Sta5a with only > 5 months      
```{r}
ggplot(data = subset(crh_sta5a_month, only_gt5 == T),
       aes(x = pc_crh_encounters)) +
  geom_histogram(bins = 100, color = "black", fill = "darkorchid3") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters",
       y = "Sta5a-Months")
```

### No sta5a with only < 6 months      
```{r}
ggplot(data = subset(crh_sta5a_month, only_lt6 == F),
       aes(x = pc_crh_encounters)) +
  geom_histogram(bins = 100, color = "black", fill = "grey") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters",
       y = "Sta5a-Months")
```

---

### Only Sta5a-months with > 20        
```{r}
ggplot(data = subset(crh_sta5a_month, pc_crh_encounters > 20),
       aes(x = pc_crh_encounters)) +
  geom_histogram(bins = 100, color = "black", fill = "seagreen3") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Encounters",
       y = "Sta5a-Months")
```  

---

## Primary Care CRH - Nursing?  
* `r crh_encounters %>% filter(secondarystopcode == 117) %>% nrow` out of the total `r nrow(crh_encounters)` PC CRH Encounters(`r round((crh_encounters %>% filter(secondarystopcode == 117) %>% nrow) /  nrow(crh_encounters) * 100, 1)`%) use the secondary stop code __117__ "NURSING (2ND ONLY)"  

---

```{r}
crh_sta5a_month %>%
  group_by(sta5a) %>%
  summarise(count = n()) %>%
  ggplot(data = .,
         aes(x = "A", y = count)) +
  geom_jitter() +
  geom_boxplot(color = "black", fill = "slateblue", alpha = 0.75) +
  labs(y = "Number of months with > 0 PC CRH Encounters") +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank())
```