---
title: "Denominator for Penetration Rate"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#--
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```

```{r}
psc_ssc_provType <- dbGetQuery(oabi_con,
                                "select * from [OABI_MyVAAccess].[crh_eval].psc_ssc_provType_counts")
```

# Primary Care Encounters  
* The starting dataset aimed to pull as many potential Primary Care Encounters as possible
* Towards that end I started by pulling all `r sum(psc_ssc_provType$psc_ssc_provType_count) %>% scales::comma(accuracy = 1)` encounters that met the following criteria:
    + Primary Stop Code > 299 AND Primary Stop Code < 400 AND Secondary Stop Code != 710 ("PREVENTIVE IMMUNIZATION")
    + OR Secondary Stop Code > 299 AND Secondary Stop Code < 400

# Stop Codes  
## All 300-series Stop Codes    

```{r}
#==========================
psc_ssc_provType %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## Primary Stop Code in(323, 338, 348) Only    
* Using all 300-series primary stop codes is pulling-in a lot of garbage
* Let's instead use the 3 primary stop codes that have the words "PRIMARY CARE" in their official name:
    + 323 PRIMARY CARE/MEDICINE
    + 338 TELEPHONE PRIMARY CARE
    + 348 PRIMARY CARE SHARED APPT
* These account for `r psc_ssc_provType %>% filter(primaryStopCode %in% c(323, 338, 348)) %>% summarise(tot = sum(psc_ssc_provType_count)) %>% pull %>% scales::comma()` out of all `r sum(psc_ssc_provType$psc_ssc_provType_count) %>% scales::comma(accuracy = 1)` (`r round((psc_ssc_provType %>% filter(primaryStopCode %in% c(323, 338, 348)) %>% summarise(tot = sum(psc_ssc_provType_count)) %>% pull) / (sum(psc_ssc_provType$psc_ssc_provType_count)) * 100, 1)`%) encounters with 300-series stop codes
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)) %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)

```

# Provider Type  
* This based on a [HSR&D ListServ](https://vaww.listserv.va.gov/scripts/wa.exe?A2=HSRDATA-L;fcf74357.2111&S=) thread from November, 2021  

## All 300-series Stop Codes  
```{r}
psc_ssc_provType %>%
  group_by(provTypeCat) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1))  %>%
  kbl(col.names = c("Provider Type", "Encounters", "Proportion of Total"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


## Primary Stop Code in(323, 338, 348) Only 
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)) %>%
  group_by(provTypeCat) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Provider Type", "Encounters", "Proportion of Total"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

# Provider Type X PSC/SSC - Primary Stop Code in(323, 338, 348) Only    

## Nurse  
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)
         & provTypeCat == "Nurse") %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


## MD    
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)
         & provTypeCat == "MD") %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## PA/APN    
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)
         & provTypeCat == "PA/APN") %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## Psychologist    
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)
         & provTypeCat == "Psychologist") %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## Pharmacist      
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)
         & provTypeCat == "Pharmacist") %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


## Other        
```{r}
psc_ssc_provType %>%
  filter(primaryStopCode %in% c(323, 338, 348)
         & provTypeCat == "Other") %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(total = sum(psc_ssc_provType_count)) %>%
  ungroup %>%
  mutate(sum_total = sum(total),
         prop = total / sum_total,
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  arrange(desc(total)) %>%
  slice_head(., n = 25) %>%
  select(-sum_total) %>%
  janitor::adorn_totals() %>%
  mutate(total = scales::comma(total, accuracy = 1),
         prop = scales::percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Encounters", "Proportion of Total"),
      align = c("c", "l", "c", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```
