---
title: "Primary Care CRH, FY 2021 - PCAT vs. MCAA in VISN 23"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = TRUE, fig.width = 25, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 26, face = "bold"),
             axis.text = element_text(size = 22),
             strip.text = element_text(size = 22),
             legend.text = element_text(size = 22),
             legend.title = element_text(size = 26, face = "bold"),
             plot.caption = element_text(size = 18))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```



```{r reading-in}
hubs <- dbGetQuery(oabi_con,
                   "select distinct hub_sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY20]
                    UNION 
                    select distinct Hub_Sta3n as hub_sta5a
                    FROM [PACT_CC].[CRH].[CRH_sites_FY21_working]") %>%
  pull
#--
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes_v <- spokes %>% pull
#
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#
vast_spokes <- vast %>%
  inner_join(., spokes, by = c("sta5a" = "spoke_sta5a"))
#--
institution_lookup <- dbGetQuery(oabi_con,
                                 "select distinct a.InstitutionName, b.Sta6a
                                  from [CDWWork].[Dim].Institution as a
                                  left join [CDWWork].[Dim].Division as b
                                  	on a.InstitutionSID = b.InstitutionSID
                                  where b.Sta6a IS NOT NULL and a.InstitutionName <> '*Missing*'") %>%
  rename_all(tolower)
#-----
crh_encounters_v23_01 <- dbGetQuery(oabi_con,
                         "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr),
         ccc_flag = if_else(str_detect(locationname, "CCC") == T, TRUE, FALSE)) %>%
  filter(fy %in% c(2020, 2021) & care_type %ni% c("Specialty", "Missing")) %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a")) %>%
  filter(parent_visn == 23) %>%
  mutate(source = "PCAT")
#
crh_encounters_v23 <- crh_encounters_v23_01 %>%
  filter(ccc_flag == FALSE)
#--==================
v23_mcaa <- read_csv(here("Input", "Data", "CRH_PCAT_Check_11302021.csv")) %>%
  rename_all(tolower) %>%
  left_join(., institution_lookup) %>%
  mutate(psc = as.numeric(str_sub(stopcodename, start = 2, end = 4)),
         ssc = if_else(creditstopname == "NULL", NA_real_, as.numeric(str_sub(creditstopname, start = 2, end = 4))),
         care_type = 
           case_when(
             (psc %in% c(156, 176, 177, 178, 301, 322, 323, 338, 348) 
              & (ssc != 160 | is.na(ssc) == T)) 
             | (psc != 160 
                & ssc %in% c(156, 176, 177, 178, 301, 322, 323, 338, 348))    ~ "Primary Care",
             (psc %in% c(502, 509, 510, 513, 516, 527, 538, 545, 550, 562, 576, 579, 586, 587) 
              & (ssc %ni% c(160, 534) | is.na(ssc) == T)) 
             | (psc %ni% c(160, 534)
                & ssc %in% c(502, 509, 510, 513, 516, 527, 538, 545, 550, 
                                    562, 576, 579, 586, 587))                  ~ "Mental Health",
             (psc %in% c(534, 539) 
              & (ssc != 160 | is.na(ssc) == T)) 
             | (psc != 160 & ssc %in% c(534, 539)) ~ "PCMHI",
             psc == 160 | ssc == 160  ~ "Pharmacy",
             is.na(psc) == T ~ "Missing",
             TRUE                                                                          ~ "Specialty"),
         visitdatetime = mdy_hm(visitdatetime),
         visitdate = as_date(visitdatetime),
         hub_flag = if_else(sta6a %in% hubs, 2, 1),
         visit_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(visitdate) > 9, year(visitdate) + 1, year(visitdate)),
         qtr = case_when(month(visitdate) %in% c(10, 11, 12) ~ 1,
                         month(visitdate) %in% c(1, 2, 3) ~ 2,
                         month(visitdate) %in% c(4, 5, 6) ~ 3,
                         month(visitdate) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  arrange(scrssn, visitdatetime, hub_flag) %>%
  group_by(scrssn, visitdatetime, care_type) %>%
  mutate(rowNum = row_number()) %>%
  filter(rowNum == 1 & care_type %ni% c("Specialty", "Missing")) %>%
  mutate(source = "V23 MCAA")
```


```{r}
pcat_primary_care <- crh_encounters_v23 %>%
  filter(care_type == "Primary Care" & fy == 2021)
#7,112
mcaa_primary_care <- v23_mcaa %>%
  filter(care_type == "Primary Care") %>%
  ungroup %>%
  group_by(scrssn, visitdate) %>%
  mutate(rn = row_number()) %>%
  filter(rn == 1)
#2,237
#
pcat_innerJoin_mcaa <- pcat_primary_care %>% 
  inner_join(., mcaa_primary_care %>% ungroup %>% select(scrssn, visitdate))
#
mcaa_anti_join_pcat <- mcaa_primary_care %>%
  anti_join(., pcat_primary_care %>% select(scrssn, visitdate))
```

# Comparison  
* There are `r nrow(pcat_primary_care)` Primary Care encounters in the __PCAT__ dataset
* There are `r nrow(mcaa_primary_care)` Primary Care Encounters in the __MCAA__ dataset
* This means that __PCAT__ has `r nrow(pcat_primary_care) - nrow(mcaa_primary_care)` more Primary Care CRH encounters than __MCAA__

## Inner Join  
* If I inner_join __PCAT__ with __MCAA__ on ScrSSN and VisitDate we get `r nrow(pcat_innerJoin_mcaa)` rows (i.e., all but `r nrow(mcaa_primary_care) - nrow(pcat_innerJoin_mcaa)` of the encounters in __PCAT__ are also in __MCAA__)

## Unique ScrSSNs  
```{r}
pcat_distinct_scrssn <- pcat_primary_care %>%
  select(scrssn) %>%
  distinct() %>% pull
#
mcaa_distinct_scrssn <- mcaa_primary_care %>%
  ungroup %>%
  select(scrssn) %>%
  distinct() %>% pull
#-
scrssn_intersect <- intersect(pcat_distinct_scrssn, mcaa_distinct_scrssn)
#1,797
scrssn_in_pcat_not_mcaa <- setdiff(pcat_distinct_scrssn, mcaa_distinct_scrssn)
#713
scrssn_in_mcaa_not_pcat <- setdiff(mcaa_distinct_scrssn, pcat_distinct_scrssn)
#
scrssn_encounters_in_pcat_not_mcaa <- pcat_primary_care %>% filter(scrssn %in% scrssn_in_pcat_not_mcaa)
```

* There are `r length(pcat_distinct_scrssn)` unique ScrSSNs with Primary Care encounters in the __PCAT__ dataset

* There are `r length(mcaa_distinct_scrssn)` unique ScrSSNs with Primary Care Encounters in the __MCAA__ dataset

* Out of the `r length(pcat_distinct_scrssn)` unique ScrSSNs with Primary Care encounters in the __PCAT__ dataset, `r length(scrssn_intersect)` (`r round(length(scrssn_intersect) / length(pcat_distinct_scrssn) * 100, 1)`%) are also in the __MCAA__ dataset
    + The remaining `r length(scrssn_in_pcat_not_mcaa)` ScrSSNs are responsible for `r nrow(scrssn_encounters_in_pcat_not_mcaa)` Primary Care CRH encounters in the PCAT dataset and not the MCAA dataset (this is `r round(nrow(scrssn_encounters_in_pcat_not_mcaa) / (nrow(pcat_primary_care) - nrow(mcaa_primary_care)) * 100, 1)`% of the difference between PCAT and MCAA)

* Out of the `r length(mcaa_distinct_scrssn)` unique ScrSSNs with Primary Care encounters in the __MCAA__ dataset, `r length(scrssn_intersect)` (`r round(length(scrssn_intersect) / length(mcaa_distinct_scrssn) * 100, 1)`%) are also in the __PCAT__ dataset (i.e., all but `r length(mcaa_distinct_scrssn) - length(scrssn_intersect)` ScrSSNs)

## Unique LocationName  
```{r}
pcat_distinct_locationname <- pcat_primary_care %>%
  select(locationname) %>% distinct
#
mcaa_distinct_locationname <- mcaa_primary_care %>%
  ungroup %>%
  select(locationname) %>%
  distinct
#
locationname_in_pcat_not_mcaa <- setdiff(pcat_distinct_locationname, mcaa_distinct_locationname)
#
locName_encounters_in_pcat_not_mcaa <- pcat_primary_care %>% 
  filter(locationname %in% locationname_in_pcat_not_mcaa$locationname)
```

* In the __PCAT__ dataset there are `r nrow(pcat_distinct_locationname)` unique LocationNames
* In the __MCAA__ dataset there are `r nrow(mcaa_distinct_locationname)` unique LocationNames

* The `r nrow(locationname_in_pcat_not_mcaa)` unique LocationNames that are in __PCAT__ and not in __MCAA__ account for `r nrow(locName_encounters_in_pcat_not_mcaa)` of the difference in encounter counts between the two datasets:
```{r}
locName_encounters_in_pcat_not_mcaa %>% group_by(locationname) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  slice_head(., n = 10) %>%
  kbl(col.names = c("LocationName", "Encounters"),
      position = "left") %>%
  kable_classic("striped")
```

# What do we know so far?  
```{r}
locName_and_scrssn_visitDate <- locName_encounters_in_pcat_not_mcaa %>%
  bind_rows(., scrssn_encounters_in_pcat_not_mcaa) %>%
  distinct
#2,954
in_pcat_not_mcaa <- pcat_primary_care %>%#foo
  anti_join(., mcaa_primary_care %>% select(scrssn, visitdate))
#--
unaccountedFor_by_locName_or_scrSSN_visitDate <- in_pcat_not_mcaa %>%#bar
  anti_join(., locName_and_scrssn_visitDate %>% select(scrssn, visitdate))
#===---
extra_pcat_encounters <- locName_and_scrssn_visitDate %>%
  bind_rows(., unaccountedFor_by_locName_or_scrSSN_visitDate) %>%
  distinct
#---
unaccounted_for_1 <- nrow(pcat_primary_care) - nrow(mcaa_primary_care)
```

* If I UNION the ScrSSN dataset (i.e., ScrSSNs in PCAT, not in MCAA) with the LocationName dataset (i.e., locationNames in PCAT, not in MCAA) I get `r nrow(locName_and_scrssn_visitDate)` encounters
    + This is `r round(nrow(locName_and_scrssn_visitDate) / (nrow(pcat_primary_care) - nrow(mcaa_primary_care)) * 100, 1)`% of the PCAT vs. MCAA difference (i.e., `r nrow(locName_and_scrssn_visitDate)` out of `r nrow(pcat_primary_care) - nrow(mcaa_primary_care)`) 
    + This means that there are still `r nrow(pcat_primary_care) - nrow(mcaa_primary_care) - nrow(locName_and_scrssn_visitDate)` encounters unaccounted for by the ScrSSN and LocationName method
    + At the time of writing this I don't know why there are an extra `r nrow(extra_pcat_encounters) - unaccounted_for_1` encounters in this dataset  ¯\\\_(ツ)_/¯

## All Together  
* Below are all `r nrow(extra_pcat_encounters)` presented together:
* Quarterly distribution:
```{r}
extra_pcat_encounters %>%
  group_by(fyqtr) %>%
  summarise(count = n()) %>%
  kbl(col.names = c("FY-Qtr", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Top 10 LocationNames by encounter count:
```{r}
extra_pcat_encounters %>%
  group_by(locationname) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  slice_head(., n = 10) %>%
  kbl(col.names = c("LocationName", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Sta5as by encounter count:
```{r}
extra_pcat_encounters %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a_combined_cdw, ") ", short_name)) %>%
  group_by(sta5a_lab) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  kbl(col.names = c("Sta5a", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

## Unaccounted-For Encounters    
* Below are all `r nrow(unaccountedFor_by_locName_or_scrSSN_visitDate)` encounters not identified by ScrSSN/VisitDate or LocationName presented together:
* Quarterly distribution:
```{r}
unaccountedFor_by_locName_or_scrSSN_visitDate %>%
  group_by(fyqtr) %>%
  summarise(count = n()) %>%
  kbl(col.names = c("FY-Qtr", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Top 10 LocationNames by encounter count:
```{r}
unaccountedFor_by_locName_or_scrSSN_visitDate %>%
  group_by(locationname) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  slice_head(., n = 10) %>%
  kbl(col.names = c("LocationName", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Sta5as by encounter count:
```{r}
unaccountedFor_by_locName_or_scrSSN_visitDate %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a_combined_cdw, ") ", short_name)) %>%
  group_by(sta5a_lab) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  kbl(col.names = c("Sta5a", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Spoke_sta5as by encounter count:
```{r}
unaccountedFor_by_locName_or_scrSSN_visitDate %>%
  select(spoke_sta5a_crh) %>%
  left_join(., vast, by = c("spoke_sta5a_crh" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a_crh, ") ", short_name)) %>%
  group_by(sta5a_lab) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  kbl(col.names = c("Spoke_Sta5a_CRH", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* A sample of 10 of these encounters:
```{r}
unaccountedFor_by_locName_or_scrSSN_visitDate %>%
  mutate(sta5a = as.character(spoke_sta5a_combined_cdw),
         sta5a_lab = paste0("(", sta5a, ") ", short_name)) %>%
  select(sta5a_lab, visitdate, char4, locationname, primarystopcode, secondarystopcode) %>%
  slice_sample(., n = 10) %>%
  kbl(col.names = c("Sta5a", "VisitDate", "CHAR-4", "LocationName", "PSC", "SSC")) %>%
  kable_classic("striped",
      position = "left")
```

## Accounted-For Encounters    
* Below are all `r nrow(locName_and_scrssn_visitDate)` encounters identified by ScrSSN/VisitDate or LocationName presented together:
* Quarterly distribution:
```{r}
locName_and_scrssn_visitDate %>%
  group_by(fyqtr) %>%
  summarise(count = n()) %>%
  kbl(col.names = c("FY-Qtr", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Top 10 LocationNames by encounter count:
```{r}
locName_and_scrssn_visitDate %>%
  group_by(locationname) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  slice_head(., n = 10) %>%
  kbl(col.names = c("LocationName", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Sta5as by encounter count:
```{r}
locName_and_scrssn_visitDate %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a_combined_cdw, ") ", short_name)) %>%
  group_by(sta5a_lab) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  kbl(col.names = c("Sta5a", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
```

* Spoke_sta5as by encounter count:
```{r}
locName_and_scrssn_visitDate %>%
  select(spoke_sta5a_crh) %>%
  left_join(., vast, by = c("spoke_sta5a_crh" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a_crh, ") ", short_name)) %>%
  group_by(sta5a_lab) %>%
  summarise(count = n()) %>%
  arrange(desc(count)) %>%
  kbl(col.names = c("Spoke_Sta5a_CRH", "Encounters")) %>%
  kable_classic("striped", full_width = F,
      position = "left")
=======
foo <- pcat_primary_care %>%
  anti_join(., mcaa_primary_care %>% select(scrssn, visitdate))
#--
bar <- foo %>%
  anti_join(., extra_pcat_encounters_1 %>% select(scrssn, visitdate))
#===---
extra_pcat_encounters <- extra_pcat_encounters_1 %>%
  bind_rows(., bar) %>%
  distinct
#--
extra_pcat_encounters %>%
  group_by(fyqtr) %>%
  summarise(count = n())
#
extra_pcat_encounters %>%
  group_by(locationname) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
#
extra_pcat_encounters %>%
  group_by(spoke_sta5a_combined_cdw, short_name) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

* A sample of 10 of these encounters:
```{r results='asis'}
locName_and_scrssn_visitDate %>%
  mutate(sta5a = as.character(spoke_sta5a_combined_cdw),
         sta5a_lab = paste0("(", sta5a, ") ", short_name)) %>%
  select(sta5a_lab, visitdate, char4, locationname, primarystopcode, secondarystopcode) %>%
  slice_sample(., n = 10) %>%
  kbl(col.names = c("Sta5a", "VisitDate", "CHAR-4", "LocationName", "PSC", "SSC")) %>%
  kable_classic("striped",
      position = "left")
```