---
title: "PC Access Metrics Pre-Post First PC CRH Month"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r}
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#===================
# PC CRH Encounters
pc_crh_encounters <- dbGetQuery(oabi_con,
                             "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a")) %>%
  rename(sta5a = spoke_sta5a_combined_cdw) %>%
  filter(fy %in% c(2020, 2021) 
         & care_type == "Primary Care")
#====================================================================================
pc_crh_sta5a_month <- pc_crh_encounters %>%
  group_by(sta5a, crh_month) %>%
  summarise(pc_crh_encounters = n())
#==
#vector of pc crh sta5as
pc_crh_sta5a <- pc_crh_sta5a_month %>%
  select(sta5a) %>% distinct %>% pull
#------------------
# first PC CRH encounter-month
first_pc_crh_month <- pc_crh_sta5a_month %>%
  group_by(sta5a) %>%
  summarise(first_pc_crh_month = first(crh_month))
#-----
# first month with > 5 PC CRH encounters
first_gt5_pc_crh_month <- pc_crh_sta5a_month %>%
  filter(pc_crh_encounters > 5) %>%
  group_by(sta5a) %>%
  summarise(first_gt5_pc_crh_month = first(crh_month))
#-----
# first month with > 25 PC CRH encounters
first_gt25_pc_crh_month <- pc_crh_sta5a_month %>%
  filter(pc_crh_encounters > 25) %>%
  group_by(sta5a) %>%
  summarise(first_gt25_pc_crh_month = first(crh_month))
#----
first_dates <- as_tibble(pc_crh_sta5a) %>%
  rename(sta5a = value) %>%
  left_join(., first_pc_crh_month) %>%
  left_join(., first_gt5_pc_crh_month) %>%
  left_join(., first_gt25_pc_crh_month)
# ======--------
sta5a_month_summary <- pc_crh_sta5a_month %>%
  mutate(month_w_lt6 = if_else(pc_crh_encounters < 6, 1, 0),
         month_w_gt5 = if_else(pc_crh_encounters > 5, 1, 0),
         month_w_lt20 = if_else(pc_crh_encounters < 20, 1, 0),
         month_w_gt19 = if_else(pc_crh_encounters > 19, 1, 0),
         month_w_lt50 = if_else(pc_crh_encounters < 50, 1, 0),
         month_w_gt49 = if_else(pc_crh_encounters > 49, 1, 0)) %>%
  group_by(sta5a) %>%
  summarise(lt6 = sum(month_w_lt6),
            gt5 = sum(month_w_gt5),
            both_lt6_and_gt5 = if_else(lt6 > 0 & gt5 > 0, 1, 0),
            only_lt6 = if_else(lt6 > 0 & gt5 == 0, 1, 0),
            only_gt5 = if_else(lt6 == 0 & gt5 > 0, 1, 0),
            has_both = sum(both_lt6_and_gt5),
            only_lt6 = sum(only_lt6),
            only_gt5 = sum(only_gt5),
            #
            lt20 = sum(month_w_lt20),
            gt19 = sum(month_w_gt19),
            both_lt20_and_gt19 = if_else(lt20 > 0 & gt19 > 0, 1, 0),
            only_lt20 = if_else(lt20 > 0 & gt19 == 0, 1, 0),
            only_gt19 = if_else(lt20 == 0 & gt19 > 0, 1, 0),
            has_both_19_20 = sum(both_lt20_and_gt19),
            only_lt20 = sum(only_lt20),
            only_gt19 = sum(only_gt19),
            #
            lt50 = sum(month_w_lt50),
            gt49 = sum(month_w_gt49),
            both_lt50_and_gt49 = if_else(lt50 > 0 & gt49 > 0, 1, 0),
            only_lt50 = if_else(lt50 > 0 & gt49 == 0, 1, 0),
            only_gt49 = if_else(lt50 == 0 & gt49 > 0, 1, 0),
            has_both_49_50 = sum(both_lt50_and_gt49),
            only_lt50 = sum(only_lt50),
            only_gt49 = sum(only_gt49))
#  
pc_crh_sta5a_month_1 <- pc_crh_sta5a_month %>%
  left_join(., sta5a_month_summary) %>%
  left_join(., vast) %>%
  left_join(., first_dates)
#=============================
# access metrics
access_metrics_sta5a <- read_csv(here("Input", "Data", "pc_access_metrics.csv")) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop) %>%
  filter(sta5a %in% pc_crh_sta5a)
```

```{r}
only_gt5_sta5a <- pc_crh_sta5a_month_1 %>%
  filter(only_gt5 == T) %>%
  select(sta5a, first_pc_crh_month) %>%
  distinct
#
only_gt5_df <- access_metrics_sta5a %>%
  left_join(., only_gt5_sta5a) %>%
  filter(vssc_month <= c(first_pc_crh_month %m+% months(6)) & vssc_month >= c(first_pc_crh_month %m-% months(6))) %>%
  group_by(sta5a) %>%
  mutate(rowNum = row_number())
#--
only_gt19_sta5a <- pc_crh_sta5a_month_1 %>%
  filter(only_gt19 == T) %>%
  select(sta5a, first_pc_crh_month) %>%
  distinct
#
only_gt19_df <- access_metrics_sta5a %>%
  left_join(., only_gt19_sta5a) %>%
  filter(vssc_month <= c(first_pc_crh_month %m+% months(6)) & vssc_month >= c(first_pc_crh_month %m-% months(6))) %>%
  group_by(sta5a) %>%
  mutate(rowNum = row_number())
```

# Sta5as Having Only Months With > 5 PC CRH Encounters per Month  

* There are `r nrow(only_gt5_sta5a)` unique sta5as having only months with > 5 PC CRH Encounters per month
* The vertical line is plotted on the first month with any PC CRH encounters (in this case > 5)
* I plotted 6 months on either side of this month, for a total of 13 months plotted

## Established Patient Wait Time  

```{r}
ggplot(data = only_gt5_df,
       aes(x = rowNum, y = established_pt_waitTime, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Established Patient Wait Time (days)")
```


## New Patient Wait Time  

```{r}
ggplot(data = only_gt5_df,
       aes(x = rowNum, y = new_pt_waitTime, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "New Patient Wait Time (days)")
```

## Observed to Expected Panel Size Ratio    

```{r}
ggplot(data = only_gt5_df,
       aes(x = rowNum, y = obs_expected_panel_size_ratio, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Observed to Expected Panel Size Ratio")
```

## Core Teamlet PC Staff Ratio    

```{r}
ggplot(data = only_gt5_df,
       aes(x = rowNum, y = pc_staff_ratio, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Core Teamlet PC Staff Ratio")
```


## Same Day Appointments with PC Provider Ratio      

```{r}
ggplot(data = only_gt5_df,
       aes(x = rowNum, y = same_day_appts_wPC_provider_ratio, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Same Day Appointments with PC Provider Ratio")
```

## Timely Care Success Rate          

```{r}
ggplot(data = only_gt5_df,
       aes(x = rowNum, y = tc_pc_success_prop, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Timely Care Success Rate")
```

---


# Sta5as Having Only Months With > 19 PC CRH Encounters per Month  

* There are `r nrow(only_gt19_sta5a)` unique sta5as having only months with > 19 PC CRH Encounters per month
* The vertical line is plotted on the first month with any PC CRH encounters (in this case > 19)
* I plotted 6 months on either side of this month, for a total of 13 months plotted

## Established Patient Wait Time  

```{r}
ggplot(data = only_gt19_df,
       aes(x = rowNum, y = established_pt_waitTime, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Established Patient Wait Time (days)")
```


## New Patient Wait Time  

```{r}
ggplot(data = only_gt19_df,
       aes(x = rowNum, y = new_pt_waitTime, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "New Patient Wait Time (days)")
```

## Observed to Expected Panel Size Ratio    

```{r}
ggplot(data = only_gt19_df,
       aes(x = rowNum, y = obs_expected_panel_size_ratio, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Observed to Expected Panel Size Ratio")
```

## Core Teamlet PC Staff Ratio    

```{r}
ggplot(data = only_gt19_df,
       aes(x = rowNum, y = pc_staff_ratio, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Core Teamlet PC Staff Ratio")
```


## Same Day Appointments with PC Provider Ratio      

```{r}
ggplot(data = only_gt19_df,
       aes(x = rowNum, y = same_day_appts_wPC_provider_ratio, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Same Day Appointments with PC Provider Ratio")
```

## Timely Care Success Rate          

```{r}
ggplot(data = only_gt19_df,
       aes(x = rowNum, y = tc_pc_success_prop, group = sta5a, color = sta5a)) +
 geom_line(size = 1) +
  theme(legend.position = "none") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  geom_vline(xintercept = 7,
             lty = 2) +
  labs(x = "Month",
       y = "Timely Care Success Rate")
```