---
title: "PC Access Metrics Pre-Post First PC CRH Month"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r}
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#===================
# PC CRH Encounters - VISNs 2 & 23
pc_crh_encounters <- dbGetQuery(oabi_con,
                             "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr)) %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a")) %>%
  rename(sta5a = spoke_sta5a_combined_cdw) %>%
  filter(fy %in% c(2020, 2021) 
         & care_type == "Primary Care")
#===---
#count encounters by sta5a-month
pc_crh_sta5a_month <- pc_crh_encounters %>%
  group_by(sta5a, crh_month) %>%
  summarise(pc_crh_encounters = n())
#---
# vector of sta5as
pc_crh_sta5a <- pc_crh_sta5a_month %>%
  select(sta5a) %>%
  distinct %>% pull
#------------------
# first PC CRH encounter-month
first_pc_crh_month <- pc_crh_sta5a_month %>%
  group_by(sta5a) %>%
  summarise(first_pc_crh_month = first(crh_month))
#-----
# first month with > 5 PC CRH encounters
first_gt5_pc_crh_month <- pc_crh_sta5a_month %>%
  filter(pc_crh_encounters > 5) %>%
  group_by(sta5a) %>%
  summarise(first_gt5_pc_crh_month = first(crh_month))
#-----
# first month with > 25 PC CRH encounters
first_gt25_pc_crh_month <- pc_crh_sta5a_month %>%
  filter(pc_crh_encounters > 25) %>%
  group_by(sta5a) %>%
  summarise(first_gt25_pc_crh_month = first(crh_month))
#----
first_dates <- as_tibble(pc_crh_sta5a) %>%
  rename(sta5a = value) %>%
  left_join(., first_pc_crh_month) %>%
  left_join(., first_gt5_pc_crh_month) %>%
  left_join(., first_gt25_pc_crh_month)
#=============================
# access metrics
access_metrics_sta5a <- read_csv(here("Input", "Data", "pc_access_metrics.csv")) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop) %>%
  filter(sta5a %in% pc_crh_sta5a)
#==========================
#taking 6-month mean before first date
avg_access_b4_first_date <- access_metrics_sta5a %>%
  left_join(., first_pc_crh_month) %>%
  filter(vssc_month <= first_pc_crh_month) %>%
  select(-first_pc_crh_month) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  arrange(sta5a, name, vssc_month) %>%
  summarise(avg_b4_first_month = mean(lag(value, 6), na.rm = T))
#taking 6-month mean before first date
avg_access_after_first_date <- access_metrics_sta5a %>%
  left_join(., first_pc_crh_month) %>%
  filter(vssc_month > first_pc_crh_month) %>%
  select(-first_pc_crh_month) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  arrange(sta5a, name, vssc_month) %>%
  summarise(avg_after_first_month = mean(lead(value, 6), na.rm = T))
#==========================
#taking 6-month mean before first > 5 date
avg_access_b4_first_gt5_date <- access_metrics_sta5a %>%
  left_join(., first_gt5_pc_crh_month) %>%
  filter(vssc_month <= first_gt5_pc_crh_month) %>%
  select(-first_gt5_pc_crh_month) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  arrange(sta5a, name, vssc_month) %>%
  summarise(avg_b4_first_gt5_month = mean(lag(value, 6), na.rm = T))
#taking 6-month mean before first > 5 date
avg_access_after_first_gt5_date <- access_metrics_sta5a %>%
  left_join(., first_gt5_pc_crh_month) %>%
  filter(vssc_month > first_gt5_pc_crh_month) %>%
  select(-first_gt5_pc_crh_month) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  arrange(sta5a, name, vssc_month) %>%
  summarise(avg_after_first_gt5_month = mean(lead(value, 6), na.rm = T))
#==========================
#taking 6-month mean before first > 5 date
avg_access_b4_first_gt25_date <- access_metrics_sta5a %>%
  left_join(., first_gt25_pc_crh_month) %>%
  filter(vssc_month <= first_gt25_pc_crh_month) %>%
  select(-first_gt25_pc_crh_month) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  arrange(sta5a, name, vssc_month) %>%
  summarise(avg_b4_first_gt25_month = mean(lag(value, 6), na.rm = T))
#taking 6-month mean before first > 5 date
avg_access_after_first_gt25_date <- access_metrics_sta5a %>%
  left_join(., first_gt25_pc_crh_month) %>%
  filter(vssc_month > first_gt25_pc_crh_month) %>%
  select(-first_gt25_pc_crh_month) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  arrange(sta5a, name, vssc_month) %>%
  summarise(avg_after_first_gt25_month = mean(lead(value, 6), na.rm = T))
#******************************************************
# all access metric names so i din't drop any
metric_names <- access_metrics_sta5a %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  select(name) %>% distinct
#
access_metrics_pre_post <- as_tibble(pc_crh_sta5a) %>%
  rename(sta5a = value) %>%
  full_join(., metric_names, by = character()) %>%
  left_join(., avg_access_b4_first_date)  %>%
  left_join(., avg_access_after_first_date) %>%
  left_join(., avg_access_b4_first_gt5_date)  %>%
  left_join(., avg_access_after_first_gt5_date) %>%
  left_join(., avg_access_b4_first_gt25_date)  %>%
  left_join(., avg_access_after_first_gt25_date)
```

# Before and After 1st PC CRH Month  

* There are `r nrow(first_pc_crh_month)` unique sta5as in this dataset  

## Established Patient Wait Time  
```{r}
access_metrics_pre_post %>%
  filter(name == "established_pt_waitTime") %>%
  select(1, 3, 4) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st Month", "6 mos. After 1st Month"),
                           ordered = T, levels = c("6 mos. Before 1st Month", "6 mos. After 1st Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time") +
  ggsci::scale_fill_jco()

```  

## New Patient Wait Time  
```{r}
access_metrics_pre_post %>%
  filter(name == "new_pt_waitTime") %>%
  select(1, 3, 4) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st Month", "6 mos. After 1st Month"),
                           ordered = T, levels = c("6 mos. Before 1st Month", "6 mos. After 1st Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time") +
  ggsci::scale_fill_jco()
```

## Observed:Expected Panel Size Ratio    
```{r}
access_metrics_pre_post %>%
  filter(name == "obs_expected_panel_size_ratio") %>%
  select(1, 3, 4) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st Month", "6 mos. After 1st Month"),
                           ordered = T, levels = c("6 mos. Before 1st Month", "6 mos. After 1st Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Observed:Expected Panel Size Ratio") +
  ggsci::scale_fill_jco()
```

## PC Staffing Ratio      
```{r}
access_metrics_pre_post %>%
  filter(name == "pc_staff_ratio") %>%
  select(1, 3, 4) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st Month", "6 mos. After 1st Month"),
                           ordered = T, levels = c("6 mos. Before 1st Month", "6 mos. After 1st Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "PC Staff Ratio") +
  ggsci::scale_fill_jco()
```

## Same-Day Appointment With PC Provider Ratio        
```{r}
access_metrics_pre_post %>%
  filter(name == "same_day_appts_wPC_provider_ratio") %>%
  select(1, 3, 4) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st Month", "6 mos. After 1st Month"),
                           ordered = T, levels = c("6 mos. Before 1st Month", "6 mos. After 1st Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Same-Day Appointment With PC Provider Ratio") +
  ggsci::scale_fill_jco()
```

## Timely Care Success Rate          
```{r}
access_metrics_pre_post %>%
  filter(name == "tc_pc_success_prop") %>%
  select(1, 3, 4) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st Month", "6 mos. After 1st Month"),
                           ordered = T, levels = c("6 mos. Before 1st Month", "6 mos. After 1st Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Timely Care Success Rate") +
  scale_y_continuous(labels = scales::percent_format()) +
  ggsci::scale_fill_jco()
```

# Before and After 1st > 5 PC CRH Month 

* There are `r nrow(first_gt5_pc_crh_month)` unique sta5as in this dataset

## Established Patient Wait Time  
```{r}
access_metrics_pre_post %>%
  filter(name == "established_pt_waitTime") %>%
  select(1, 5, 6) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time") +
  ggsci::scale_fill_jco()

```  

## New Patient Wait Time  
```{r}
access_metrics_pre_post %>%
  filter(name == "new_pt_waitTime") %>%
  select(1, 5, 6) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time") +
  ggsci::scale_fill_jco()
```

## Observed:Expected Panel Size Ratio    
```{r}
access_metrics_pre_post %>%
  filter(name == "obs_expected_panel_size_ratio") %>%
  select(1, 5, 6) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Observed:Expected Panel Size Ratio") +
  ggsci::scale_fill_jco()
```

## PC Staffing Ratio      
```{r}
access_metrics_pre_post %>%
  filter(name == "pc_staff_ratio") %>%
  select(1, 5, 6) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "PC Staff Ratio") +
  ggsci::scale_fill_jco()
```

## Same-Day Appointment With PC Provider Ratio        
```{r}
access_metrics_pre_post %>%
  filter(name == "same_day_appts_wPC_provider_ratio") %>%
  select(1, 5, 6) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Same-Day Appointment With PC Provider Ratio") +
  ggsci::scale_fill_jco()
```

## Timely Care Success Rate          
```{r}
access_metrics_pre_post %>%
  filter(name == "tc_pc_success_prop") %>%
  select(1, 5, 6) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 5 Month", "6 mos. After 1st > 5 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Timely Care Success Rate") +
  scale_y_continuous(labels = scales::percent_format()) +
  ggsci::scale_fill_jco()
```


# Before and After 1st > 25 PC CRH Month  

* There are `r nrow(first_gt25_pc_crh_month)` unique sta5as in this dataset

## Established Patient Wait Time  
```{r}
access_metrics_pre_post %>%
  filter(name == "established_pt_waitTime") %>%
  select(1, 7, 8) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time") +
  ggsci::scale_fill_jco()

```  

## New Patient Wait Time  
```{r}
access_metrics_pre_post %>%
  filter(name == "new_pt_waitTime") %>%
  select(1, 7, 8) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time") +
  ggsci::scale_fill_jco()
```

## Observed:Expected Panel Size Ratio    
```{r}
access_metrics_pre_post %>%
  filter(name == "obs_expected_panel_size_ratio") %>%
  select(1, 7, 8) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Observed:Expected Panel Size Ratio") +
  ggsci::scale_fill_jco()
```

## PC Staffing Ratio      
```{r}
access_metrics_pre_post %>%
  filter(name == "pc_staff_ratio") %>%
  select(1, 7, 8) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "PC Staff Ratio") +
  ggsci::scale_fill_jco()
```

## Same-Day Appointment With PC Provider Ratio        
```{r}
access_metrics_pre_post %>%
  filter(name == "same_day_appts_wPC_provider_ratio") %>%
  select(1, 7, 8) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Same-Day Appointment With PC Provider Ratio") +
  ggsci::scale_fill_jco()
```

## Timely Care Success Rate          
```{r}
access_metrics_pre_post %>%
  filter(name == "tc_pc_success_prop") %>%
  select(1, 7, 8) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = factor(if_else(str_detect(name, "b4") == T, "6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"),
                           ordered = T, levels = c("6 mos. Before 1st > 25 Month", "6 mos. After 1st > 25 Month"))) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Timely Care Success Rate") +
  scale_y_continuous(labels = scales::percent_format()) +
  ggsci::scale_fill_jco()
```