---
title: "PCAT Primary Care: Primary and Secondary Stop Codes & Provider Type"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#--
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```

```{r}
psc_ssc_count <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].psc_ssc")
#
psc_ssc_sum <- sum(psc_ssc_count$psc_ssc_count, na.rm = T)
#--
psc_count <- psc_ssc_count %>%
  group_by(primaryStopCode, pStopCodeName) %>%
  summarise(psc_count = sum(psc_ssc_count, na.rm = T)) %>%
  arrange(desc(psc_count))
#--
provType_psc_ssc_count <- dbGetQuery(oabi_con,
                                     "select * from [OABI_MyVAAccess].[crh_eval].provType_psc_ssc")
#--
provType_psc_ssc_sum <- sum(provType_psc_ssc_count$provType_psc_ssc_count, na.rm = T)
```

# PCAT/ECON Primary Care Inclusion Criteria  

* The PCAT/ECON Primary Care inclusion criteria is a workload outpatient encounter in CDW where:
    + PrimaryStopCode IN(322, 323, 338, 348, 350, 704) 
        + AND SecondaryStopCode NOT IN(107, 115, 152, 311, 321, 328, 329, 333, 334, 430, 435, 474, 999)
        
    + OR SecondaryStopCode IN(322, 323, 348, 350, 704)
    
* This yields `r psc_ssc_sum %>% comma(accuracy = 1)` encounters with `r nrow(psc_count)` Primary Stop Codes in FYs 19, 20 and 21. Below are the first 25:

```{r}
psc_count %>%
  ungroup %>%
  slice_head(., n = 25) %>%
  mutate(prop = psc_count / psc_ssc_sum,
         primaryStopCode = as.character(primaryStopCode)) %>%
  adorn_totals() %>%
  mutate(psc_count = comma(psc_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.01)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Count", "Proportion"),
      align = c("l", "l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


* This yields `r nrow(psc_ssc_count)` Primary and Secondary Stop Code combinations. Below are the top 40:
```{r}
psc_ssc_count %>%
  arrange(desc(psc_ssc_count)) %>%
  ungroup %>%
  slice_head(., n = 40) %>%
  mutate(prop = psc_ssc_count / psc_ssc_sum,
         primaryStopCode = as.character(primaryStopCode),
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  select(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName, psc_ssc_count, prop) %>%
  adorn_totals() %>%
  mutate(psc_ssc_count = comma(psc_ssc_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.01)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Count", "Proportion"),
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

* And for funsies, here are the bottom 25:
```{r}
psc_ssc_count %>%
  arrange(desc(psc_ssc_count)) %>%
  ungroup %>%
  slice_tail(., n = 25) %>%
  mutate(prop = psc_ssc_count / psc_ssc_sum,
         primaryStopCode = as.character(primaryStopCode),
         secondaryStopCode = as.character(secondaryStopCode)) %>%
  select(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName, psc_ssc_count, prop) %>%
  adorn_totals() %>%
  mutate(psc_ssc_count = comma(psc_ssc_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.01)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Count", "Proportion"),
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

# By Provider Type  

```{r}
provType_psc_ssc_count %>%
  group_by(provTypeCat) %>%
  summarise(provType_count = sum(provType_psc_ssc_count, na.rm = T)) %>%
  arrange(desc(provType_count)) %>%
  mutate(prop = provType_count / psc_ssc_sum) %>%
  adorn_totals() %>%
  mutate(provType_count = comma(provType_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Provider Type", "Count", "Proportion"),
      full_width = F,
      align = c("l", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## Nursing Primary and Secondary Stop Codes  
```{r}
nursing_sum <- provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Nursing") == T) %>%
  summarise(total = sum(provType_psc_ssc_count)) %>%
  pull
#
provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Nursing") == T) %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(provType_count = sum(provType_psc_ssc_count, na.rm = T)) %>%
  ungroup %>%
  arrange(desc(provType_count)) %>%
  mutate(prop = provType_count / nursing_sum) %>%
  slice_head(., n = 25) %>%
  adorn_totals() %>%
  mutate(provType_count = comma(provType_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary Stop Code", "SSC Name", "Count", "Proportion"),
      full_width = F,
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## MD/DO Primary and Secondary Stop Codes  
```{r}
md_do_sum <- provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "MD/DO") == T) %>%
  summarise(total = sum(provType_psc_ssc_count)) %>%
  pull
#
provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "MD/DO") == T) %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(provType_count = sum(provType_psc_ssc_count, na.rm = T)) %>%
  ungroup %>%
  arrange(desc(provType_count)) %>%
  mutate(prop = provType_count / md_do_sum) %>%
  slice_head(., n = 25) %>%
  adorn_totals() %>%
  mutate(provType_count = comma(provType_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary Stop Code", "SSC Name", "Count", "Proportion"),
      full_width = F,
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


## PA/APN Primary and Secondary Stop Codes  
```{r}
pa_apn_sum <- provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "PA/APN") == T) %>%
  summarise(total = sum(provType_psc_ssc_count)) %>%
  pull
#
provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "PA/APN") == T) %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(provType_count = sum(provType_psc_ssc_count, na.rm = T)) %>%
  ungroup %>%
  arrange(desc(provType_count)) %>%
  mutate(prop = provType_count / pa_apn_sum) %>%
  slice_head(., n = 25) %>%
  adorn_totals() %>%
  mutate(provType_count = comma(provType_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary Stop Code", "SSC Name", "Count", "Proportion"),
      full_width = F,
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```



## Pharmacy Primary and Secondary Stop Codes  
```{r}
pharm_sum <- provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Pharm") == T) %>%
  summarise(total = sum(provType_psc_ssc_count)) %>%
  pull
#
provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Pharm") == T) %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(provType_count = sum(provType_psc_ssc_count, na.rm = T)) %>%
  ungroup %>%
  arrange(desc(provType_count)) %>%
  mutate(prop = provType_count / pharm_sum) %>%
  slice_head(., n = 25) %>%
  adorn_totals() %>%
  mutate(provType_count = comma(provType_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary Stop Code", "SSC Name", "Count", "Proportion"),
      full_width = F,
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```



## Psychologist, etc. Primary and Secondary Stop Codes  
```{r}
psych_sum <- provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Psych") == T) %>%
  summarise(total = sum(provType_psc_ssc_count)) %>%
  pull
#
provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Psych") == T) %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(provType_count = sum(provType_psc_ssc_count, na.rm = T)) %>%
  ungroup %>%
  arrange(desc(provType_count)) %>%
  mutate(prop = provType_count / psych_sum) %>%
  slice_head(., n = 25) %>%
  adorn_totals() %>%
  mutate(provType_count = comma(provType_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary Stop Code", "SSC Name", "Count", "Proportion"),
      full_width = F,
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## "Other" Primary and Secondary Stop Codes  
```{r}
other_sum <- provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Other") == T) %>%
  summarise(total = sum(provType_psc_ssc_count)) %>%
  pull
#
provType_psc_ssc_count %>%
  filter(str_detect(provTypeCat, "Other") == T) %>%
  group_by(primaryStopCode, pStopCodeName, secondaryStopCode, sStopCodeName) %>%
  summarise(provType_count = sum(provType_psc_ssc_count, na.rm = T)) %>%
  ungroup %>%
  arrange(desc(provType_count)) %>%
  mutate(prop = provType_count / other_sum) %>%
  slice_head(., n = 25) %>%
  adorn_totals() %>%
  mutate(provType_count = comma(provType_count, accuracy = 1),
         prop = percent(prop, accuracy = 0.1)) %>%
  kbl(col.names = c("Primary SC", "PSC Name", "Secondary Stop Code", "SSC Name", "Count", "Proportion"),
      full_width = F,
      align = c(rep("l", 4), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```