---
title: "PC CRH Denominator: What is the distribution of SecondaryStopCode = 117?"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
#--
colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color,
      x)
  } else x
}
```

```{r reading-in}
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#===================
# PC CRH Encounters
pc_crh_encounters <- dbGetQuery(oabi_con,
                             "select * from [PACT_CC].[CRH].[crh_full_utilization_final_fy20_21]") %>%
  rename_all(tolower) %>%
  mutate(visitdate = ymd(visitdate),
         crh_month = ymd(str_c(year(visitdate), month(visitdate), "01", sep = "-")),
         fy = if_else(month(crh_month) > 9, year(crh_month) + 1, year(crh_month)),
         qtr = case_when(month(crh_month) %in% c(10, 11, 12) ~ 1,
                         month(crh_month) %in% c(1, 2, 3) ~ 2,
                         month(crh_month) %in% c(4, 5, 6) ~ 3,
                         month(crh_month) %in% c(7, 8, 9) ~ 4),
         fyqtr = str_c(fy, "-", qtr),
         ssc_117_flag = if_else(secondarystopcode == 117, T, F)) %>%
  left_join(., vast, by = c("spoke_sta5a_combined_cdw" = "sta5a")) %>%
  rename(sta5a = spoke_sta5a_combined_cdw) %>%
  filter(fy %in% c(2020, 2021) 
         & care_type == "Primary Care")
#---
pc_psc_ssc <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].stopCode_combos
                         where careType = 'PC'") %>%
  arrange(desc(sc_count))
```

# Review    
* Below are the top 25 Primary & Secondary stop code combinations using the following criteria to pull PC encounters from CDW:
    + `r colorize("PrimaryStopCode in (156, 176, 177, 178, 301, 322, 323, 338, 348) AND (SecondaryStopCode not in(160, 534, 539) OR SecondaryStopCode IS NULL)", "red")`
    + `r colorize("OR (PrimaryStopCode not in(160, 534, 539) AND SecondaryStopCode in (156, 176, 177, 178, 301, 322, 323, 338, 348))", "red")` 
* There are a total of `r nrow(pc_psc_ssc)` stop code combinations  
					
```{r} 
#
pc_psc_ssc %>%
  select(pStopCode_, pStopCodeName_,
         sStopCode_, sStopCodeName_, sc_count) %>%
  slice_head(., n = 25) %>%
  mutate(prop = round(sc_count / sum(pc_psc_ssc$sc_count) * 100, 1),
         pStopCode_ = as.character(pStopCode_),
         sStopCode_ = as.character(sStopCode_),
         sc_count = as.character(scales::comma(sc_count))) %>%
  janitor::adorn_totals() %>%
  mutate(prop = paste0(prop, "%")) %>%
  kbl(align = c("c", "l", "c", "l", "r", "r"),
      col.names = c("Primary SC", "PSC Name", "Secondary SC", "SSC Name", "Total Encounters", "Proportion of total")) %>%
  kable_classic("striped")
#
sc_117_as_total <- pc_psc_ssc %>%
  filter(sStopCode_ == 117) %>%
  summarise(total_with_ssc_117 = sum(sc_count)) %>%
  pull
#=======
ssc_117_sta5a <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].ssc_117_sta5a")
#
ssc_total_sta5a <- dbGetQuery(oabi_con,
                              "select * from [OABI_MyVAAccess].[crh_eval].stopCode_combos_sta5a") %>%
  filter(careType == "PC") %>%
  group_by(Sta6a) %>%
  summarise(total_pc_sc = sum(sc_count)) %>%
  rename(sta6a = Sta6a)
#
ssc_117_as_prop_of_total <- ssc_117_sta5a %>%
  left_join(., ssc_total_sta5a) %>%
  mutate(prop = ssc_117_count / total_pc_sc) %>%
  filter(prop < 1)
```

* A total of `r scales::comma(sc_117_as_total)` out of `r scales::comma(sum(pc_psc_ssc$sc_count))` encounters (`r round(sc_117_as_total / sum(pc_psc_ssc$sc_count) * 100, 1)`%) identified using the method above have a Secondary Stop Code of __117 "NURSING (2ND ONLY)"__ 
* Out of a total `r scales::comma(nrow(pc_crh_encounters))` PC CRH Encounters we identified only `r scales::comma(sum(pc_crh_encounters$ssc_117_flag, na.rm = T))` (`r round(sum(pc_crh_encounters$ssc_117_flag, na.rm = T) / nrow(pc_crh_encounters) * 100, 1)`%) with a Secondary Stop Code of __117 "NURSING (2ND ONLY)"__
* What is the distribution of the proportion of a sta5a's PC encounters that are = 117? Is use of SSC = 117 colinear with other characteristics?   
    + The plots below have `r scales::comma(nrow(ssc_117_as_prop_of_total))` observations (i.e., sta5as), from April 1st, 2019 through December 31st, 2021
    

$$\frac{\sum{\text{PC Encounters SSC = 117}}}{\sum{\text{All PC Encounters}}}\times 100$$

# National Distribution  
```{r}
#--
nat_p1 <- ggplot(data = ssc_117_as_prop_of_total,
       aes(x = prop)) +
  geom_histogram(bins = 100,
                 color = "black",
                 fill = "red") +
  scale_x_continuous(labels = scales::percent_format(),
                     limits = c(0, 1)) +
  labs(x = "Proportion of Total",
       y = "Number of Sta5as")
#
nat_p2 <- ggplot(data = ssc_117_as_prop_of_total,
       aes(y = prop)) +
  geom_boxplot(color = "black",
               fill = "royalblue") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0, 1)) +
  labs(y = "Proportion of Total") +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank())
#--
multiplot(nat_p1, nat_p2)
```

# By VISN  

```{r}
ssc_117_as_prop_of_total %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  filter(is.na(parent_visn) == F) %>%
  ggplot(data = .,
         aes(x = prop)) +
  geom_histogram(bins = 50,
                 color = "black",
                 fill = "darkorchid3") +
  scale_x_continuous(labels = scales::percent_format(),
                     limits = c(0, 1),
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_y_continuous(limits = c(0, 10), 
                     breaks = c(0, 2, 4, 6, 8, 10)) +
  facet_wrap(~parent_visn) +
  labs(x = "Proportion of Total",
       y = "Number of Sta5as")
#
ssc_117_as_prop_of_total %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  filter(is.na(parent_visn) == F) %>%
  ggplot(data = .,
         aes(y = prop)) +
  geom_boxplot(color = "black",
                 fill = "firebrick") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0, 1),
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  facet_wrap(~parent_visn) +
  labs(y = "Proportion of Total") +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  geom_hline(yintercept = 0.31,
             lty = 2)
```

# By Site Type  
```{r}
ssc_117_as_prop_of_total %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  filter(is.na(parent_visn) == F) %>%
  ggplot(data = .,
         aes(x = prop)) +
  geom_histogram(bins = 50,
                 color = "black",
                 fill = "red") +
  facet_wrap(~s_abbr) +
  labs(x = "Proportion of Total",
       y = "Number of Sta5as") +
  scale_x_continuous(labels = scales::percent_format(),
                     limits = c(0, 1),
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_y_continuous(limits = c(0, 40), 
                     breaks = c(0, 10, 20, 30, 40))
#--
ssc_117_as_prop_of_total %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  filter(is.na(parent_visn) == F) %>%
  ggplot(data = .,
         aes(y = prop)) +
  geom_boxplot(color = "black",
               fill = "dodgerblue") +
  facet_wrap(~s_abbr) +
  labs(y = "Proportion of Total") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0, 1),
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  geom_hline(yintercept = 0.31,
             lty = 2)
```

# CRH Site vs. Not CRH Site  

```{r}
pc_crh_sta5a <- pc_crh_encounters %>%
  select(sta5a) %>%
  distinct %>% pull
#
crh_flag <- vast %>%
  select(sta5a) %>%
  distinct() %>%
  mutate(crh_flag = if_else(sta5a %in% pc_crh_sta5a, "CRH Site", "Not CRH Site"))
#
ssc_117_as_prop_of_total %>%
  left_join(., crh_flag, by = c("sta6a" = "sta5a")) %>%
  filter(is.na(crh_flag) == F) %>%
  ggplot(data = .,
         aes(x = prop)) +
  geom_histogram(bins = 50,
                 color = "black",
                 fill = "red") +
  facet_wrap(~crh_flag) +
  labs(x = "Proportion of Total",
       y = "Number of Sta5as") +
  scale_x_continuous(labels = scales::percent_format(),
                     limits = c(0, 1),
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_y_continuous(limits = c(0, 45), 
                     breaks = c(0, 10, 20, 30, 40))
#
#
ssc_117_as_prop_of_total %>%
  left_join(., crh_flag, by = c("sta6a" = "sta5a")) %>%
  filter(is.na(crh_flag) == F) %>%
  ggplot(data = .,
         aes(y = prop)) +
  geom_boxplot(color = "black",
                 fill = "forestgreen") +
  facet_wrap(~crh_flag) +
  labs(y = "Proportion of Total") +
  scale_y_continuous(labels = scales::percent_format(),
                     limits = c(0, 1),
                     breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank()) +
  geom_hline(yintercept = 0.31,
             lty = 2)
```