---
title: "Primary Care CRH: Sta5as meeting inclusion criteria in all first 6 months of FY20"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.width = 12, fig.height = 12)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
##---------- Connection to PACT_CC
pactcc_con <- dbConnect(odbc::odbc(),
                        Driver = "SQL Server",
                        Server = "vhacdwsql13.vha.med.va.gov",
                        Database = "PACT_CC",
                        Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 18),
             strip.text = element_text(size = 20),
             legend.text = element_text(size = 18),
             legend.title = element_text(size = 20),
             plot.caption = element_text(size = 12))
```

```{r reading-in}
#=========================
# VAST
vast <- read_csv(here("Input", "Data", "vast_from_a06.csv"))
#
vast_to_keep <- vast%>%
  select(sta5a)
#----
# crh flags
crh_flags <- dbGetQuery(oabi_con,
                        "select * from [crh_eval].yoon_flag")
#----- PCMM count
scrssn_count <- vast %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count < 450 ~ "< 450",
    scrssn_count >= 450 & scrssn_count < 2500 ~ "450 - 2,499",
    scrssn_count >= 2500 & scrssn_count < 10000 ~ "2,500 - 9,999",
    scrssn_count >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,499", "2,500 - 9,999", "10,000+")))
#=============================
# access metrics
access_metrics_sta5a <- read_csv(here("Input", "Data", "pc_access_metrics.csv")) %>%
  inner_join(., vast_to_keep) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  select(-ends_with("avg"), -ends_with("sum"), -tc_success_prop) %>%
  left_join(., crh_flags) %>%
  mutate(table_1_columns = factor(case_when(yoon_10_flag == 1 ~ "CRH",
                                            crh_flag == 1 & yoon_10_flag == 0 ~ "Not Enough CRH",
                                            is.na(crh_flag) == T ~ "No CRH",
                                            TRUE ~ "Uh-oh"), 
                                  ordered = TRUE,
                                  levels = c("CRH", "Not Enough CRH", "No CRH")),
         analytic_period = factor(case_when(
           vssc_month >= ymd("2019-04-01") & vssc_month <= ymd("2019-09-01") ~ "6 Months Before",
           vssc_month >= ymd("2019-10-01") & vssc_month <= ymd("2020-03-01") ~ "First 6 Months of CRH",
           vssc_month >= ymd("2020-04-01") & vssc_month <= ymd("2020-09-01") ~ "6 Months After",
           vssc_month >= ymd("2020-10-01") ~ "Final Period",
           TRUE ~ NA_character_),
           ordered = TRUE,
           levels = c("6 Months Before", "First 6 Months of CRH", "6 Months After", "Final Period")))
#=====
sta5as_w_6mos <- access_metrics_sta5a %>%
  filter(first_6_mos_w_10_flag == 1) %>%
  select(sta5a) %>% distinct %>%
  left_join(., vast)
```

# Sta5as with PC CRH in the first 6 months of FY 2020  
* There are `r sum(crh_flags$first_6_mos_w_10_flag)` sta5as that had at least 10 PC CRH encounters during all of the first 6 months of FY 2020

```{r}
sta5as_w_6mos %>% group_by(parent_visn) %>%
  summarise(count = n()) %>%
  mutate(prop = count / nrow(sta5as_w_6mos)) %>%
  add_row(parent_visn = c("01", "05", "09", "10", "23"),
          count = rep(0, 5),
          prop = rep(0, 5)) %>%
  arrange(parent_visn) %>%
  adorn_totals() %>%
  mutate(prop = percent(prop, accuracy = 1)) %>%
  kbl(col.names = c("VISN", "Number of Sta5a", "%"),
      align = c("c", "r", "r")) %>%
  kable_classic("striped",
      full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```

---

```{r}
sta5as_w_6mos %>%
  group_by(s_abbr) %>%
  summarise(count = n()) %>%
  mutate(prop = count / nrow(sta5as_w_6mos)) %>%
  adorn_totals() %>%
  mutate(prop = percent(prop, accuracy = 1)) %>%
  kbl(col.names = c("Site Type", "Sta5a", "%"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```

---

```{r}
sta5as_w_6mos %>%
  left_join(., scrssn_count %>% select(sta5a, scrssn_count_cat)) %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n()) %>%
  mutate(prop = count / nrow(sta5as_w_6mos)) %>%
  adorn_totals() %>%
  mutate(prop = percent(prop, accuracy = 1)) %>%
  kbl(col.names = c("Uniques in PCMM", "Sta5a", "%"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```


# New Patient Wait Time    

* There are `r sum(crh_flags$first_6_mos_w_10_flag)` sta5as that had at least 10 PC CRH encounters during all of the first 6 months of FY 2020
* The boxplots below are comparing average new patient wait times, between those `r sum(crh_flags$first_6_mos_w_10_flag)` sta5as and the `r access_metrics_sta5a%>% filter(table_1_columns == "No CRH") %>% select(sta5a) %>% n_distinct` sta5as that have never had a PC CRH encounter


```{r}
access_6mos_df <- access_metrics_sta5a %>%
  filter(is.na(analytic_period) == F) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH")) %>%
  select(sta5a, vssc_month, new_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(sta5a, analytic_period, first_6_lab) %>%
  summarize(avg_new_pt_waitTime = mean(new_pt_waitTime, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = analytic_period, y = avg_new_pt_waitTime, fill = first_6_lab)) +
  geom_boxplot() +
  theme(legend.title = element_blank()) +
  labs(x = "Analytic Period",
       y = "Average New Patient Wait Time") +
  ggsci::scale_fill_aaas()

```

```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH")) %>%
  select(sta5a, vssc_month, new_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(vssc_month, first_6_lab) %>%
  summarise(avg_new_pt_waitTime = mean(new_pt_waitTime, na.rm = T),
            sd_new_pt_waitTime = sd(new_pt_waitTime, na.rm = T)) %>%
  mutate(val_plus_sd = avg_new_pt_waitTime + sd_new_pt_waitTime,
         val_min_sd = avg_new_pt_waitTime - sd_new_pt_waitTime) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = avg_new_pt_waitTime, group = first_6_lab, color = first_6_lab)) +
  geom_rect(aes(xmin = as.Date("2019-04-01"), xmax = as.Date("2019-10-01"),
                ymin = 0, ymax = 25),
            alpha = 0.002,
            fill = "blue",
            inherit.aes = FALSE) +
  geom_rect(aes(xmin = as.Date("2020-04-01"), xmax = as.Date("2020-10-01"),
                ymin = 0, ymax = 25),
            alpha = 0.002,
            fill = "red",
            inherit.aes = FALSE) +
  geom_line(size = 1) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Average New Patient Wait Time")
```

## Among CBOCs Only  
* The boxplots below are comparing average new patient wait times, between the `r access_6mos_df%>% filter(first_6_mos_w_10_flag == 1 & s_abbr %in% c("PCCBOC", "MSCBOC")) %>% select(sta5a) %>% n_distinct` sta5as classified as __CBOCs__ and the `r access_6mos_df%>% filter(table_1_columns == "No CRH" & s_abbr %in% c("PCCBOC", "MSCBOC")) %>% select(sta5a) %>% n_distinct` sta5as classified as __PCCBOCs__ that have never had a PC CRH encounter  

```{r}
access_6mos_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH") & s_abbr %in% c("PCCBOC", "MSCBOC")) %>%
  select(sta5a, vssc_month, new_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(sta5a, analytic_period, first_6_lab) %>%
  summarize(avg_new_pt_waitTime = mean(new_pt_waitTime, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = analytic_period, y = avg_new_pt_waitTime, fill = first_6_lab)) +
  geom_boxplot() +
  theme(legend.title = element_blank()) +
  labs(x = "Analytic Period",
       y = "Average New Patient Wait Time",
       caption = "*CBOCs Only") +
  ggsci::scale_fill_futurama()

```

```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH") & s_abbr %in% c("PCCBOC", "MSCBOC")) %>%
  select(sta5a, vssc_month, new_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(vssc_month, first_6_lab) %>%
  summarise(avg_new_pt_waitTime = mean(new_pt_waitTime, na.rm = T),
            sd_new_pt_waitTime = sd(new_pt_waitTime, na.rm = T)) %>%
  mutate(val_plus_sd = avg_new_pt_waitTime + sd_new_pt_waitTime,
         val_min_sd = avg_new_pt_waitTime - sd_new_pt_waitTime) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = avg_new_pt_waitTime, group = first_6_lab, color = first_6_lab)) +
  geom_rect(aes(xmin = as.Date("2019-04-01"), xmax = as.Date("2019-10-01"),
                ymin = 0, ymax = 25),
            alpha = 0.002,
            fill = "blue",
            inherit.aes = FALSE) +
  geom_rect(aes(xmin = as.Date("2020-04-01"), xmax = as.Date("2020-10-01"),
                ymin = 0, ymax = 25),
            alpha = 0.002,
            fill = "red",
            inherit.aes = FALSE) +
  geom_line(size = 1) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Average New Patient Wait Time",
       caption = "*CBOCs Only")
```

# Established Patient Wait Time    

* The boxplots below are comparing average established patient wait times, between those `r sum(crh_flags$first_6_mos_w_10_flag)` sta5as and the `r access_metrics_sta5a%>% filter(table_1_columns == "No CRH") %>% select(sta5a) %>% n_distinct` sta5as that have never had a PC CRH encounter

```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH")) %>%
  select(sta5a, vssc_month, established_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(sta5a, analytic_period, first_6_lab) %>%
  summarize(avg_established_pt_waitTime = mean(established_pt_waitTime, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = analytic_period, y = avg_established_pt_waitTime, fill = first_6_lab)) +
  geom_boxplot() +
  theme(legend.title = element_blank()) +
  labs(x = "Analytic Period",
       y = "Average Established Patient Wait Time") +
  ggsci::scale_fill_igv()

```


```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH")) %>%
  select(sta5a, vssc_month, established_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(vssc_month, first_6_lab) %>%
  summarise(avg_established_pt_waitTime = mean(established_pt_waitTime, na.rm = T),
            sd_established_pt_waitTime = sd(established_pt_waitTime, na.rm = T)) %>%
  mutate(val_plus_sd = avg_established_pt_waitTime + sd_established_pt_waitTime,
         val_min_sd = avg_established_pt_waitTime - sd_established_pt_waitTime) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = avg_established_pt_waitTime, group = first_6_lab, color = first_6_lab)) +
  geom_rect(aes(xmin = as.Date("2019-04-01"), xmax = as.Date("2019-10-01"),
                ymin = 0, ymax = 60),
            alpha = 0.002,
            fill = "blue",
            inherit.aes = FALSE) +
  geom_rect(aes(xmin = as.Date("2020-04-01"), xmax = as.Date("2020-10-01"),
                ymin = 0, ymax = 60),
            alpha = 0.002,
            fill = "red",
            inherit.aes = FALSE) +
  geom_line(size = 1) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Average Established Patient Wait Time")
```

## Among CBOCs Only  
* The boxplots below are comparing average established patient wait times, between the `r access_6mos_df%>% filter(first_6_mos_w_10_flag == 1 & s_abbr %in% c("PCCBOC", "MSCBOC")) %>% select(sta5a) %>% n_distinct` sta5as classified as __CBOCs__ and the `r access_6mos_df%>% filter(table_1_columns == "No CRH" & s_abbr %in% c("PCCBOC", "MSCBOC")) %>% select(sta5a) %>% n_distinct` sta5as classified as __CBOCs__ that have never had a PC CRH encounter  

```{r}
access_6mos_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH") & s_abbr %in% c("PCCBOC", "MSCBOC")) %>%
  select(sta5a, vssc_month, established_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(sta5a, analytic_period, first_6_lab) %>%
  summarize(avg_established_pt_waitTime = mean(established_pt_waitTime, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = analytic_period, y = avg_established_pt_waitTime, fill = first_6_lab)) +
  geom_boxplot() +
  theme(legend.title = element_blank()) +
  labs(x = "Analytic Period",
       y = "Average Established Patient Wait Time",
       caption = "*CBOCs Only") +
  ggsci::scale_fill_jama()

```


```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH") & s_abbr %in% c("PCCBOC", "MSCBOC")) %>%
  select(sta5a, vssc_month, established_pt_waitTime, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(vssc_month, first_6_lab) %>%
  summarise(avg_established_pt_waitTime = mean(established_pt_waitTime, na.rm = T),
            sd_established_pt_waitTime = sd(established_pt_waitTime, na.rm = T)) %>%
  mutate(val_plus_sd = avg_established_pt_waitTime + sd_established_pt_waitTime,
         val_min_sd = avg_established_pt_waitTime - sd_established_pt_waitTime) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = avg_established_pt_waitTime, group = first_6_lab, color = first_6_lab)) +
  geom_rect(aes(xmin = as.Date("2019-04-01"), xmax = as.Date("2019-10-01"),
                ymin = 0, ymax = 65),
            alpha = 0.002,
            fill = "blue",
            inherit.aes = FALSE) +
  geom_rect(aes(xmin = as.Date("2020-04-01"), xmax = as.Date("2020-10-01"),
                ymin = 0, ymax = 65),
            alpha = 0.002,
            fill = "red",
            inherit.aes = FALSE) +
  geom_line(size = 1) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Average Established Patient Wait Time",
       caption = "*CBOCs Only")
```

# Timely Care      

* The boxplots below are comparing average timely care success rate, between those `r sum(crh_flags$first_6_mos_w_10_flag)` sta5as and the `r access_metrics_sta5a%>% filter(table_1_columns == "No CRH") %>% select(sta5a) %>% n_distinct` sta5as that have never had a PC CRH encounter

```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH")) %>%
  select(sta5a, vssc_month, tc_pc_success_prop, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(sta5a, analytic_period, first_6_lab) %>%
  summarize(avg_tc_pc_success_prop = mean(tc_pc_success_prop, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = analytic_period, y = avg_tc_pc_success_prop, fill = first_6_lab)) +
  geom_boxplot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  theme(legend.title = element_blank()) +
  labs(x = "Analytic Period",
       y = "Average Timely Care") +
  ggsci::scale_fill_jco()

```


```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH")) %>%
  select(sta5a, vssc_month, tc_pc_success_prop, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(vssc_month, first_6_lab) %>%
  summarise(avg_tc_pc_success_prop = mean(tc_pc_success_prop, na.rm = T),
            sd_tc_pc_success_prop = sd(tc_pc_success_prop, na.rm = T)) %>%
  mutate(val_plus_sd = avg_tc_pc_success_prop + sd_tc_pc_success_prop,
         val_min_sd = avg_tc_pc_success_prop - sd_tc_pc_success_prop) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = avg_tc_pc_success_prop, group = first_6_lab, color = first_6_lab)) +
  geom_rect(aes(xmin = as.Date("2019-04-01"), xmax = as.Date("2019-10-01"),
                ymin = 0, ymax = 1),
            alpha = 0.002,
            fill = "blue",
            inherit.aes = FALSE) +
  geom_rect(aes(xmin = as.Date("2020-04-01"), xmax = as.Date("2020-10-01"),
                ymin = 0, ymax = 1),
            alpha = 0.002,
            fill = "red",
            inherit.aes = FALSE) +
  geom_line(size = 1) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Average Timely Care Success Rate")
```

## Among CBOCs Only  
* The boxplots below are comparing average timely care success rate, between the `r access_6mos_df%>% filter(first_6_mos_w_10_flag == 1 & s_abbr %in% c("PCCBOC", "MSCBOC")) %>% select(sta5a) %>% n_distinct` sta5as classified as __CBOCs__ and the `r access_6mos_df%>% filter(table_1_columns == "No CRH" & s_abbr %in% c("PCCBOC", "MSCBOC")) %>% select(sta5a) %>% n_distinct` sta5as classified as __CBOCs__ that have never had a PC CRH encounter  

```{r}
access_6mos_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH") & s_abbr %in% c("PCCBOC", "MSCBOC")) %>%
  select(sta5a, vssc_month, tc_pc_success_prop, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(sta5a, analytic_period, first_6_lab) %>%
  summarize(avg_tc_pc_success_prop = mean(tc_pc_success_prop, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = analytic_period, y = avg_tc_pc_success_prop, fill = first_6_lab)) +
  geom_boxplot() +
  theme(legend.title = element_blank()) +
  labs(x = "Analytic Period",
       y = "Average Timely Care",
       caption = "*CBOCs Only") +
  ggsci::scale_fill_lancet() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))

```


```{r}
access_6mos_df %>%
  filter((first_6_mos_w_10_flag == 1 | table_1_columns == "No CRH") & s_abbr %in% c("PCCBOC", "MSCBOC")) %>%
  select(sta5a, vssc_month, tc_pc_success_prop, first_6_mos_w_10_flag, analytic_period) %>%
  mutate(first_6_lab = if_else(is.na(first_6_mos_w_10_flag) == TRUE, "Never Had PC CRH", "Had PC CRH All 1st 6 Months")) %>%
  group_by(vssc_month, first_6_lab) %>%
  summarise(avg_tc_pc_success_prop = mean(tc_pc_success_prop, na.rm = T),
            sd_tc_pc_success_prop = sd(tc_pc_success_prop, na.rm = T)) %>%
  mutate(val_plus_sd = avg_tc_pc_success_prop + sd_tc_pc_success_prop,
         val_min_sd = avg_tc_pc_success_prop - sd_tc_pc_success_prop) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = avg_tc_pc_success_prop, group = first_6_lab, color = first_6_lab)) +
  geom_rect(aes(xmin = as.Date("2019-04-01"), xmax = as.Date("2019-10-01"),
                ymin = 0, ymax = 1),
            alpha = 0.002,
            fill = "blue",
            inherit.aes = FALSE) +
  geom_rect(aes(xmin = as.Date("2020-04-01"), xmax = as.Date("2020-10-01"),
                ymin = 0, ymax = 1),
            alpha = 0.002,
            fill = "red",
            inherit.aes = FALSE) +
  geom_line(size = 1) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank()) +
  labs(y = "Average Timely Care Success Rate",
       caption = "*CBOCs Only") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```