---
title: "VISN 20 CRH Encounters per 1,000 Total Encounters"
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 14, fig.height = 14)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = '-')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 15),
             strip.text = element_text(size = 15),
             legend.text = element_text(size = 14),
             legend.title = element_text(size = 16),
             plot.caption = element_text(size = 12),
             plot.title = element_text(size = 20, 
                                       face = "bold"))
#
#--
source(here("Input", "Functions", "customFacetWrap.R"))
source(here("Input", "Functions", "multiplot_05jan21.R"))
#--
igv_pal <- ggsci::pal_igv("default")(6)
```

```{r reading-in}
vast <- read_csv(here("Input", "Data","VAST_from_A06_11jan21.csv"))
#==
spokes <- dbGetQuery(oabi_con,
                     "select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy20_working
                     UNION
                     select spoke_sta5a from [PACT_CC].[CRH].CRH_sites_fy21_working")
#
spokes_v <- spokes %>% pull
#==
all_encounters <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].encounter_counts") %>%
  select(-contains("Vax")) %>%
  mutate(vizMonth = ymd(vizMonth)) %>%
  left_join(., vast, by = c("sta6a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", sta6a, ") ", short_name),
         spoke_flag = if_else(sta6a %in% spokes_v, TRUE, FALSE),
         fy = if_else(month(vizMonth) > 9, year(vizMonth) + 1, year(vizMonth)),
         qtr = case_when(month(vizMonth) %in% c(10, 11, 12) ~ 1,
                         month(vizMonth) %in% c(1, 2, 3) ~ 2,
                         month(vizMonth) %in% c(4, 5, 6) ~ 3,
                         month(vizMonth) %in% c(7, 8, 9) ~ 4)) %>%
  filter(is.na(parent_visn) == F & fy %in% c(2020, 2021)) %>%
  rename("Primary Care" = pc_encounters,
         "Mental Health" = mh_encounters,
         "Pharmacy" = pharmacy_encounters,
         "PCMHI" = pcmhi_encounters)
#
spoke_encounters <- all_encounters %>% filter(spoke_flag == T)
#==
crh_encounters <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].crh_encounters_deDup") %>%
  rename_all(tolower) %>%
  filter(fy %in% c(2020, 2021) & care_type %ni% c("Specialty", "Missing")) %>%
  mutate(crh_month = ymd(crh_month))
```

# Total
## Primary Care, Mental Health, Pharmacy, and PCMHI    
```{r}
crh_visn20_total <- crh_encounters %>% 
  filter(parent_visn == 20) %>%
  group_by(crh_month) %>%
  summarise(total_crh = n())
#
all_visn20_total <- spoke_encounters %>%
  select(2:6) %>%
  pivot_longer(-vizMonth) %>%
  group_by(vizMonth) %>%
  summarise(total = sum(value, na.rm = T))
#--
visn20_total_summary_df <- crh_visn20_total %>%
  left_join(., all_visn20_total, by = c("crh_month" = "vizMonth")) %>%
  mutate(crh_per_1k_tot = round(total_crh / total * 1000, 1))
#
ggplot(visn20_total_summary_df, 
       aes(x = crh_month, y = crh_per_1k_tot, color = "1")) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  ggsci::scale_color_lancet() +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2)
```

## By Care Type      
```{r}
lancet_pal <- ggsci::pal_lancet("lanonc")(9)
#
crh_visn20_type <- crh_encounters %>% 
  filter(parent_visn == 20) %>%
  group_by(crh_month, care_type) %>%
  summarise(total_crh = n())
#
all_visn20_type <- spoke_encounters %>%
  select(2:6) %>%
  pivot_longer(-vizMonth) %>%
  group_by(vizMonth, name) %>%
  summarise(total = sum(value, na.rm = T))
#--
visn20_type_summary_df <- crh_visn20_type %>%
  left_join(., all_visn20_type, by = c("crh_month" = "vizMonth", "care_type" = "name")) %>%
  mutate(crh_per_1k_tot = round(total_crh / total * 1000, 1))
#
ggplot(data = subset(visn20_type_summary_df, care_type != "PCMHI"),
       aes(x = crh_month, y = crh_per_1k_tot, color = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  ggsci::scale_color_lancet() +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~care_type)
#
tot_pcmhi_avg <- ggplot(data = subset(visn20_type_summary_df, care_type == "PCMHI"),
       aes(x = crh_month, y = crh_per_1k_tot, color = care_type)) +
  geom_line(size = 1,
            color = lancet_pal[4]) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~care_type)
#
tot_pcmhi_count <- visn20_type_summary_df %>%
  select(-crh_per_1k_tot) %>%
  pivot_longer(-c(crh_month, care_type)) %>% 
  mutate(name_lab = if_else(name == "total", "Total", "CRH")) %>%
  ggplot(data = .,
       aes(x = crh_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap(~care_type) +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(y = "Encounters") +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank())
#
multiplot(tot_pcmhi_avg, tot_pcmhi_count, cols = 2)
```

# Parent Stations  
## Mental Health, Primary Care, Pharmacy, and PCMHI  
```{r}
crh_parent_visn20_total <- crh_encounters %>% 
  filter(parent_visn == 20) %>%
  group_by(crh_month, parent_station_sta5a) %>%
  summarise(total_crh = n())
#
all_parent_visn20_total <- spoke_encounters %>%
  select(2:7) %>%
  pivot_longer(-c(vizMonth, parent_station_sta5a)) %>%
  group_by(vizMonth, parent_station_sta5a) %>%
  summarise(total = sum(value, na.rm = T))
#--
visn20_parent_total_summary_df <- crh_parent_visn20_total %>%
  left_join(., all_parent_visn20_total, by = c("crh_month" = "vizMonth", "parent_station_sta5a" = "parent_station_sta5a")) %>%
  mutate(crh_per_1k_tot = round(total_crh / total * 1000, 1)) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("parent_station_sta5a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", parent_station_sta5a, ") ", short_name))
#--
ggplot(data = subset(visn20_parent_total_summary_df, parent_station_sta5a %ni% c("463","668")),
       aes(x = crh_month, y = crh_per_1k_tot, color = sta5a_lab, group = sta5a_lab)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Excluding Anchorage and Spokane") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~sta5a_lab) +
  theme(legend.position = "none")
```

```{r}
anchorage1 <- ggplot(data = subset(visn20_parent_total_summary_df, parent_station_sta5a == "463"),
       aes(x = crh_month, y = crh_per_1k_tot, color = sta5a_lab, group = sta5a_lab)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~sta5a_lab) +
  theme(legend.position = "none",
        axis.title.x = element_blank())
#
anchorage2 <- visn20_parent_total_summary_df %>%
  filter(parent_station_sta5a == "463") %>%
  select(crh_month, sta5a_lab, total_crh, total) %>%
  pivot_longer(-c(crh_month, sta5a_lab)) %>%
  mutate(name_lab = if_else(name == "total", "Total", "CRH")) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap(~sta5a_lab) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank()) +
  labs(y = "Encounters")
#
multiplot(anchorage1, anchorage2, cols = 2)
#--
spokane1 <- ggplot(data = subset(visn20_parent_total_summary_df, parent_station_sta5a == "668"),
       aes(x = crh_month, y = crh_per_1k_tot, color = sta5a_lab, group = sta5a_lab)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~sta5a_lab) +
  theme(legend.position = "none",
        axis.title.x = element_blank())
#
spokane2 <- visn20_parent_total_summary_df %>%
  filter(parent_station_sta5a == "668") %>%
  select(crh_month, sta5a_lab, total_crh, total) %>%
  pivot_longer(-c(crh_month, sta5a_lab)) %>%
  mutate(name_lab = if_else(name == "total", "Total", "CRH")) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  theme(axis.title.x = element_blank(),
        legend.title = element_blank()) +
  labs(y = "Encounters") +
  facet_wrap(~sta5a_lab)
#
multiplot(spokane1, spokane2, cols = 2)
```

## By Care Type  
```{r}
crh_parent_visn20_type <- crh_encounters %>% 
  filter(parent_visn == 20) %>%
  group_by(crh_month, parent_station_sta5a, care_type) %>%
  summarise(total_crh = n())
#
all_parent_visn20_type <- spoke_encounters %>%
  select(2:7) %>%
  pivot_longer(-c(vizMonth, parent_station_sta5a)) %>%
  group_by(vizMonth, parent_station_sta5a, name) %>%
  summarise(total = sum(value, na.rm = T))
#--
visn20_parent_type_summary_df <- crh_parent_visn20_type %>%
  left_join(., all_parent_visn20_type, by = c("crh_month" = "vizMonth", 
                                              "parent_station_sta5a" = "parent_station_sta5a",
                                              "care_type" = "name")) %>%
  mutate(crh_per_1k_tot = round(total_crh / total * 1000, 1)) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("parent_station_sta5a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", parent_station_sta5a, ") ", short_name))
#--
ggplot(data = subset(visn20_parent_type_summary_df, parent_station_sta5a %ni% c("463","668") & care_type != "PCMHI"),
       aes(x = crh_month, y = crh_per_1k_tot, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       caption = "*Excluding Anchorage and Spokane",
       title = "No PCMHI") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~sta5a_lab) +
  theme(legend.title = element_blank())
#--
ggplot(data = subset(visn20_parent_type_summary_df, parent_station_sta5a %ni% c("463","668") & care_type == "PCMHI"),
       aes(x = crh_month, y = crh_per_1k_tot, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters",
       title = "PCMHI",
       caption = "*Excluding Anchorage and Spokane") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~sta5a_lab) +
  theme(legend.position = "none",
        plot.caption.position = "plot",
        plot.caption = element_text(hjust = 1))
```

```{r}
anchorage_type <- ggplot(data = subset(visn20_parent_type_summary_df, parent_station_sta5a == "463"),
       aes(x = crh_month, y = crh_per_1k_tot, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~sta5a_lab) +
  theme(legend.title = element_blank(), 
        legend.position = "none")
#
spokane_type <- ggplot(data = subset(visn20_parent_type_summary_df, parent_station_sta5a == "668"),
       aes(x = crh_month, y = crh_per_1k_tot, color = care_type, group = care_type)) +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "CRH Encounters per 1,000 Total Encounters") +
  geom_vline(xintercept = as.numeric(ymd("2020-03-01")), lty = 2) +
  facet_wrap(~sta5a_lab) +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank())
#
multiplot(anchorage_type, spokane_type, cols = 2)
```


```{r}
visn20_sta5a_total_crh <- crh_encounters %>%
  filter(parent_visn == 20) %>%
  group_by(crh_month, spoke_sta5a) %>%
  summarise(tot_crh = n())
#
visn20_sta5a_total_all <- spoke_encounters %>%
  filter(parent_visn == 20) %>%
  select(vizMonth, sta6a, Pharmacy, `Primary Care`, `Mental Health`, PCMHI) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(sta6a, vizMonth) %>%
  summarise(all_encounters = sum(value, na.rm = T))
#--
visn20_sta5a_total_caterpillar <- visn20_sta5a_total_crh %>%
  left_join(., visn20_sta5a_total_all, by = c("spoke_sta5a" = "sta6a", "crh_month" = "vizMonth")) %>%
  mutate(crh_per_1k_tot = tot_crh / all_encounters * 1000) %>%
  group_by(spoke_sta5a) %>%
  summarise(avg_crh_per_1k = mean(crh_per_1k_tot, na.rm = T),
            sd_crh_per_1k = sd(crh_per_1k_tot, na.rm = T)) %>%
  filter(is.na(sd_crh_per_1k) == F) %>%
  left_join(., vast %>% select(sta5a, short_name, parent_station_sta5a), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name))
```

# Sta5a      
* VISN 20 has `r vast %>% filter(parent_visn == 20) %>% select(sta5a) %>% n_distinct` unique sta5as in __VAST__
* The Operational Definition of spokes in VISN 20 has `r spokes %>% left_join(., vast, by = c("spoke_sta5a"="sta5a")) %>% filter(parent_visn == 20) %>% select(spoke_sta5a) %>% n_distinct()` unique sta5as
* According to our CDW data there are `r nrow(visn20_sta5a_total_caterpillar)` unique sta5as with at least 1 CRH encounter in FY20 and FY21

## Caterpillar - Total    
```{r}
ggplot(data = visn20_sta5a_total_caterpillar,
       aes(x = reorder(sta5a_lab, avg_crh_per_1k), y = avg_crh_per_1k, 
           ymin = avg_crh_per_1k - sd_crh_per_1k, ymax = avg_crh_per_1k + sd_crh_per_1k)) +
  labs(y = "Mean CRH/1,000 Total, +/- SD") +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_point() +
  geom_errorbar() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3, hjust = 0),
        axis.title.x = element_blank())
```

---

## Caterpillar - Mental Health  

```{r}
visn20_sta5a_type_crh <- crh_encounters %>%
  filter(parent_visn == 20) %>%
  group_by(crh_month, spoke_sta5a, care_type) %>%
  summarise(tot_crh = n())
#
visn20_sta5a_type_all <- spoke_encounters %>%
  filter(parent_visn == 20) %>%
  select(vizMonth, sta6a, Pharmacy, `Primary Care`, `Mental Health`, PCMHI) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(sta6a, vizMonth, name) %>%
  summarise(all_encounters = sum(value, na.rm = T))
#--
visn20_sta5a_type_caterpillar <- visn20_sta5a_type_crh %>%
  left_join(., visn20_sta5a_type_all, by = c("spoke_sta5a" = "sta6a", 
                                             "crh_month" = "vizMonth",
                                             "care_type" = "name")) %>%
  mutate(crh_per_1k_tot = tot_crh / all_encounters * 1000) %>%
  group_by(spoke_sta5a, care_type) %>%
  summarise(avg_crh_per_1k = mean(crh_per_1k_tot, na.rm = T),
            sd_crh_per_1k = sd(crh_per_1k_tot, na.rm = T)) %>%
  filter(is.na(sd_crh_per_1k) == F) %>%
  left_join(., vast %>% select(sta5a, short_name, parent_station_sta5a), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name),
         ymin = if_else(avg_crh_per_1k - sd_crh_per_1k < 0, 0, avg_crh_per_1k - sd_crh_per_1k),
         ymax = avg_crh_per_1k + sd_crh_per_1k)
```

* According to our CDW data there are `r visn20_sta5a_type_caterpillar %>% filter(care_type == "Mental Health") %>% select(spoke_sta5a) %>% n_distinct` unique sta5as with at least 1 Mental Health CRH encounter in FY20 and FY21
```{r}
ggplot(data = subset(visn20_sta5a_type_caterpillar, care_type == "Mental Health"),
       aes(x = reorder(sta5a_lab, avg_crh_per_1k), y = avg_crh_per_1k, 
           ymin = ymin, ymax = ymax)) +
  labs(y = "Mean MH CRH/1,000 Total MH, +/- SD") +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  geom_point() +
  geom_errorbar() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3, hjust = 0),
        axis.title.x = element_blank())
#--
mh_outliers_crh <- crh_encounters %>%
  filter(spoke_sta5a %in% c("687HA", "692GA", "663GC", "653GB", "692GB", "531GI") & care_type == "Mental Health") %>%
  group_by(crh_month, spoke_sta5a) %>%
  summarise(crh_tot = n())
#
mh_outliers_all <- spoke_encounters %>%
  filter(sta6a %in% c("687HA", "692GA", "663GC", "653GB", "692GB", "531GI")) %>%
  select(vizMonth, sta6a, `Mental Health`) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(vizMonth, sta6a) %>%
  summarise(all_tot = sum(value, na.rm = T))
#
mh_outliers_crh %>%
  left_join(., mh_outliers_all, by = c("crh_month" = "vizMonth", "spoke_sta5a" = "sta6a")) %>%
  pivot_longer(., -c(crh_month, spoke_sta5a)) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(name_lab = if_else(name == "crh_tot", "CRH Encounters", "All Encounters"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap(~sta5a_lab) +
  theme(legend.title = element_blank(),
        axis.title = element_blank()) +
  labs(title = "What's up with sta5as with > 500 CRH/1,000?")
```

---

## Caterpillar - Primary Care    

* According to our CDW data there are `r visn20_sta5a_type_caterpillar %>% filter(care_type == "Primary Care") %>% select(spoke_sta5a) %>% n_distinct` unique sta5as with at least 1 Primary Care CRH encounter in FY20 and FY21
```{r}
ggplot(data = subset(visn20_sta5a_type_caterpillar, care_type == "Primary Care"),
       aes(x = reorder(sta5a_lab, avg_crh_per_1k), y = avg_crh_per_1k, 
           ymin = ymin, ymax = ymax)) +
  labs(y = "Mean PC CRH/1,000 Total PC, +/- SD") +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  geom_point() +
  geom_errorbar() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3, hjust = 0),
        axis.title.x = element_blank())
#--
pc_outliers_crh <- crh_encounters %>%
  filter(spoke_sta5a %in% c("463", "648GD", "531GH", "531GI", "463GE") & care_type == "Primary Care") %>%
  group_by(crh_month, spoke_sta5a) %>%
  summarise(crh_tot = n())
#
pc_outliers_all <- spoke_encounters %>%
  filter(sta6a %in% c("463", "648GD", "531GH", "531GI", "463GE")) %>%
  select(vizMonth, sta6a, `Primary Care`) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(vizMonth, sta6a) %>%
  summarise(all_tot = sum(value, na.rm = T))
#
pc_outliers_crh %>%
  left_join(., pc_outliers_all, by = c("crh_month" = "vizMonth", "spoke_sta5a" = "sta6a")) %>%
  pivot_longer(., -c(crh_month, spoke_sta5a)) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(name_lab = if_else(name == "crh_tot", "CRH Encounters", "All Encounters"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap(~sta5a_lab) +
  theme(legend.title = element_blank(),
        axis.title = element_blank()) +
  labs(title = "What's up with sta5as with > 250 CRH/1,000?") +
  scale_y_continuous(labels = scales::comma_format())
```

---

## Caterpillar - Pharmacy      

* According to our CDW data there are `r visn20_sta5a_type_caterpillar %>% filter(care_type == "Pharmacy") %>% select(spoke_sta5a) %>% n_distinct` unique sta5as with at least 1 Pharmacy CRH encounter in FY20 and FY21
```{r}
ggplot(data = subset(visn20_sta5a_type_caterpillar, care_type == "Pharmacy"),
       aes(x = reorder(sta5a_lab, avg_crh_per_1k), y = avg_crh_per_1k, 
           ymin = ymin, ymax = ymax)) +
  labs(y = "Mean Pharmacy CRH/1,000 Total Pharmacy, +/- SD") +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  geom_point() +
  geom_errorbar() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3, hjust = 0),
        axis.title.x = element_blank())
#--
phrm_outliers_crh <- crh_encounters %>%
  filter(spoke_sta5a %in% c("687", "648GA", "653GA", "648A4", "692GB", "648GF") & care_type == "Pharmacy") %>%
  group_by(crh_month, spoke_sta5a) %>%
  summarise(crh_tot = n())
#
phrm_outliers_all <- spoke_encounters %>%
  filter(sta6a %in% c("687", "648GA", "653GA", "648A4", "692GB", "648GF")) %>%
  select(vizMonth, sta6a, `Pharmacy`) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(vizMonth, sta6a) %>%
  summarise(all_tot = sum(value, na.rm = T))
#
phrm_outliers_crh %>%
  left_join(., phrm_outliers_all, by = c("crh_month" = "vizMonth", "spoke_sta5a" = "sta6a")) %>%
  pivot_longer(., -c(crh_month, spoke_sta5a)) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(name_lab = if_else(name == "crh_tot", "CRH Encounters", "All Encounters"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap(~sta5a_lab) +
  theme(legend.title = element_blank(),
        axis.title = element_blank()) +
  labs(title = "What's up with sta5as with > 100 CRH/1,000?") +
  scale_y_continuous(labels = scales::comma_format())
```

---

## Caterpillar - PCMHI      

* According to our CDW data there are `r visn20_sta5a_type_caterpillar %>% filter(care_type == "PCMHI") %>% select(spoke_sta5a) %>% n_distinct` unique sta5as with at least 1 PCMHI CRH encounter in FY20 and FY21
```{r}
ggplot(data = subset(visn20_sta5a_type_caterpillar, care_type == "PCMHI"),
       aes(x = reorder(sta5a_lab, avg_crh_per_1k), y = avg_crh_per_1k, 
           ymin = ymin, ymax = ymax)) +
  labs(y = "Mean PCMHI CRH/1,000 Total PCMHI, +/- SD") +
  scale_y_continuous(labels = scales::comma_format(),
                     limits = c(0, NA)) +
  geom_point() +
  geom_errorbar() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3, hjust = 0),
        axis.title.x = element_blank())
#--
pcmhi_outliers_crh <- crh_encounters %>%
  filter(spoke_sta5a %in% c("531", "687GA", "653BY", "687GC") & care_type == "PCMHI") %>%
  group_by(crh_month, spoke_sta5a) %>%
  summarise(crh_tot = n())
#
pcmhi_outliers_all <- spoke_encounters %>%
  filter(sta6a %in% c("531", "687GA", "653BY", "687GC")) %>%
  select(vizMonth, sta6a, `PCMHI`) %>%
  pivot_longer(-c(vizMonth, sta6a)) %>%
  group_by(vizMonth, sta6a) %>%
  summarise(all_tot = sum(value, na.rm = T))
#
pcmhi_outliers_crh %>%
  left_join(., pcmhi_outliers_all, by = c("crh_month" = "vizMonth", "spoke_sta5a" = "sta6a")) %>%
  pivot_longer(., -c(crh_month, spoke_sta5a)) %>%
  left_join(., vast %>% select(sta5a, short_name), by = c("spoke_sta5a" = "sta5a")) %>%
  mutate(name_lab = if_else(name == "crh_tot", "CRH Encounters", "All Encounters"),
         sta5a_lab = paste0("(", spoke_sta5a, ") ", short_name)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  facet_wrap(~sta5a_lab) +
  theme(legend.title = element_blank(),
        axis.title = element_blank()) +
  labs(title = "What's up with sta5as with > 300 CRH/1,000?") +
  scale_y_continuous(labels = scales::comma_format())
```