---
title: "PC CRH Analysis: Subsetting Sta5as"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(sjPlot)
library(DT)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
pactcc_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "PACT_CC",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         initiated_pc_crh_b4_march_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-03-01"), TRUE, FALSE),
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
pilot_sites <- dbGetQuery(pactcc_con,
                          "select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY20_working 
                          UNION
                          select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY21_working ") %>%
  filter(vimpact_pilot == 1) %>%
  select(sta5a = spoke_sta5a)
#
ps_matched <- read_csv(here::here("Input", "Data", "ps_matched_sta5as.csv"))
#==
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month))
```

# 1A: All Sta5as that met PC CRH inclusion criteria before February, 2020  
```{r}
included_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  left_join(., vast %>% select(sta5a, short_name, city, state, parent_visn)) %>%
  mutate(city_state = paste0(city, ", ", state),
         sta5a_lab = paste0("V", parent_visn, " (", sta5a, ")")) %>%
  select(at_least_10_pc_crh_flag, sta5a_lab, short_name, city_state)
```

* There were `r nrow(included_sta5as) / 2` sta5as that met inclusion criteria before February, 2020  

```{r}
#--
included_sta5as %>%
  datatable(rownames = FALSE,
            colnames = c("CRH Flag", "Sta5a", "Station Name", "City, State"),
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 1)),
            pageLength = 25
            ))
```


# 1B: No pilot sites, all Sta5as that met PC CRH inclusion criteria before February, 2020  
```{r}
included_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE
         & sta5a %ni% pilot_sites$sta5a) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  left_join(., vast %>% select(sta5a, short_name, city, state, parent_visn)) %>%
  mutate(city_state = paste0(city, ", ", state),
         sta5a_lab = paste0("V", parent_visn, " (", sta5a, ")")) %>%
  select(at_least_10_pc_crh_flag, sta5a_lab, short_name, city_state)

```

* There were `r nrow(included_sta5as) / 2` non-pilot sta5as that met inclusion criteria before February, 2020  

```{r}
included_sta5as %>%
  datatable(rownames = FALSE,
            colnames = c("CRH Flag", "Sta5a", "Station Name", "City, State"),
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 1)),
            pageLength = 25
            ))
```


# 2A: All Sta5as meeting inclusion criteria for all first 6 months of FY20   
```{r}
included_sta5as <- crh_flag %>%
  filter(first_6_mos_w_10_flag == TRUE) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  left_join(., vast %>% select(sta5a, short_name, city, state, parent_visn)) %>%
  mutate(city_state = paste0(city, ", ", state),
         sta5a_lab = paste0("V", parent_visn, " (", sta5a, ")")) %>%
  select(at_least_10_pc_crh_flag, sta5a_lab, short_name, city_state)

```

* There were `r nrow(included_sta5as) / 2` sta5as that met inclusion for all first 6 months of FY20  

```{r}
included_sta5as %>%
  datatable(rownames = FALSE,
            colnames = c("CRH Flag", "Sta5a", "Station Name", "City, State"),
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 1)),
            pageLength = 25
            ))
```



# 2B: No pilot sites, all Sta5as meeting inclusion criteria for all first 6 months of FY20   
```{r}
included_sta5as <- crh_flag %>%
  filter(first_6_mos_w_10_flag == TRUE
         & sta5a %ni% pilot_sites$sta5a) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  left_join(., vast %>% select(sta5a, short_name, city, state, parent_visn)) %>%
  mutate(city_state = paste0(city, ", ", state),
         sta5a_lab = paste0("V", parent_visn, " (", sta5a, ")")) %>%
  select(at_least_10_pc_crh_flag, sta5a_lab, short_name, city_state)
```

* There were `r nrow(included_sta5as) / 2` non-pilot sta5as that met inclusion for all first 6 months of FY20  

```{r}
included_sta5as %>%
  datatable(rownames = FALSE,
            colnames = c("CRH Flag", "Sta5a", "Station Name", "City, State"),
            options = list(
              columnDefs = list(list(className = 'dt-center', targets = 1)),
            pageLength = 25
            ))
```
