---
title: "Comparing Sources for Outcomes"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(vssc_month = seq.Date(ymd("2019-10-01"), ymd("2022-12-01"), by = "month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PACT_CC].[econ].PatientPCP
#                             	where fy = 2018
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- ps_matched %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
```

# Conjecture  
* This ["new" source](https://reports.vssc.med.va.gov/ReportServer/Pages/ReportViewer.aspx?%2fAccess%2fAppointment+-+Completed+Summary&rs:Command=Render) for New and Established patient wait times has a layout that doesn't output Primary Care wait times at the sta5a-month, but rather in groups of primary stop code (e.g., 322, 323, 338, 350)
    + Instead they have columns like "Number (%) of appointments completed within 10 days where the primary stop code was (350) GeriPACT"
    + They do have a "Average wait time" column, but for each sta5a-month there is a row for as many 5 primary stop code groups
* I propose that I can take the grand mean at the sta5a-month level (i.e., aggregate from sta5a-month-stop code) by:
    1. Assume that Average Wait Time = $\frac{\text{number of days waited}}{\text{number of appointments}}$
    2. Therefore $\text{number of days waited} = (\text{Average wait time})\times(\text{number of appointments})$
    3. Take the sum of each sta5a-month's $\text{number of days waited}$ and $\text{number of appointments}$
    4. $\text{Average Wait Time} = \frac{\text{number of days Waited}}{\text{number of appointments}}$, but at the sta5a-month

# Established Patient Wait Time (from create date)
```{r}
# if avg_wait_time = (# of days waited) / (# of appointments)
# then # of days waited = (avg_wait_time) * (# of appointments)
est_wt_create_date <- read_csv(here("Input", "Data", "VSSC", "Appointments - Completed Summary", 
                            "est_pc_pt_wt_create_date.csv")) %>%
  filter(str_detect(DIVISION_FCDMD2, "FY") == T) %>%
  select(1, 2, 3, 4, 66:86) %>%
  rename(fy_mo = 2,
         division = DIVISION_FCDMD3,
         appt_count = NumberOfAppointments2,
         avg_wait_time = Textbox121) %>%
  mutate(days_waited = avg_wait_time * appt_count) %>%
  group_by(division, fy_mo) %>%
  summarise(est_pc_pt_wt2 = (sum(days_waited) / sum(appt_count))) %>%
  ungroup %>%
  mutate(mo_c = str_sub(fy_mo, start = -3),
         mo_n = match(mo_c, month.abb),
         fy = as.numeric(paste0("20", str_sub(fy_mo, start = 3, end = 4))),
         cy = if_else(mo_n > 9, fy - 1, fy),
         report_month = ymd(str_c(cy, mo_n, "01", sep = "-")),
         sta5a = if_else(str_sub(division, start = 11, end = 11) == ")",
                         str_sub(division, start = 8, end = 10),
                         str_sub(division, start = 8, end = 12)))
```

## All Sta5as  
```{r}
est_comp <- dates %>% select(vssc_month) %>%
  left_join(., est_wt_create_date %>% rename(vssc_month = report_month)) %>%
  left_join(access_metrics %>% select(vssc_month, sta5a, est_pc_pt_wt)) %>%
  mutate(difference = est_pc_pt_wt - est_pc_pt_wt2)
```

* Among all `r est_comp %>% select(sta5a) %>% n_distinct() %>% comma(accuarcy = 1)` sta5as included:
    + The mean difference is `r mean(est_comp$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + One standard deviation of the difference is `r sd(est_comp$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + The 5th percentile is `r quantile(est_comp$difference, na.rm = T, c(0.05)) %>% comma(accuracy = 0.01)` days
    + The 95th percentile is `r quantile(est_comp$difference, na.rm = T, c(0.95)) %>% comma(accuracy = 0.01)` days

```{r}
ggplot(data = est_comp,
       aes(x = difference)) +
  geom_histogram(bins = 5000) +
  labs(x = "(Original Days) - (\"New\" Days)",
       y = "Observations") +
  scale_y_continuous(labels = comma_format(accuracy = 1))
```

## CRH Sta5as  
```{r}
est_comp2 <- est_comp %>%
  filter(sta5a %in% sta5as_to_include$sta5a)
```

* Among all `r est_comp2 %>% select(sta5a) %>% n_distinct() %>% comma(accuarcy = 1)` sta5as included:
    + The mean difference is `r mean(est_comp2$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + One standard deviation of the difference is `r sd(est_comp2$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + The 5th percentile is `r quantile(est_comp2$difference, na.rm = T, c(0.05)) %>% comma(accuracy = 0.01)` days
    + The 95th percentile is `r quantile(est_comp2$difference, na.rm = T, c(0.95)) %>% comma(accuracy = 0.01)` days

```{r}
ggplot(data = est_comp2,
       aes(x = difference)) +
  geom_histogram(bins = 5000) +
  labs(x = "(Original Days) - (\"New\" Days)",
       y = "Observations") +
  scale_y_continuous(labels = comma_format(accuracy = 1))
```


# New Patient Wait Time (from create date)
```{r}
# if avg_wait_time = (# of days waited) / (# of appointments)
# then # of days waited = (avg_wait_time) * (# of appointments)
new_wt_create_date <- read_csv(here("Input", "Data", "VSSC", "Appointments - Completed Summary", 
                            "new_pc_pt_wt_create_date_no_april_fy20.csv")) %>%
  filter(str_detect(DIVISION_FCDMD2, "FY") == T) %>%
  select(1, 2, 3, 4, 66:86) %>%
  rename(fy_mo = 2,
         division = DIVISION_FCDMD3,
         appt_count = NumberOfAppointments2,
         avg_wait_time = Textbox121) %>%
  mutate(days_waited = avg_wait_time * appt_count) %>%
  group_by(division, fy_mo) %>%
  summarise(new_pc_pt_wt2 = (sum(days_waited) / sum(appt_count))) %>%
  ungroup %>%
  mutate(mo_c = str_sub(fy_mo, start = -3),
         mo_n = match(mo_c, month.abb),
         fy = as.numeric(paste0("20", str_sub(fy_mo, start = 3, end = 4))),
         cy = if_else(mo_n > 9, fy - 1, fy),
         report_month = ymd(str_c(cy, mo_n, "01", sep = "-")),
         sta5a = if_else(str_sub(division, start = 11, end = 11) == ")",
                         str_sub(division, start = 8, end = 10),
                         str_sub(division, start = 8, end = 12)))
```

## All Sta5as  
```{r}
new_comp <- dates %>% select(vssc_month) %>%
  left_join(., new_wt_create_date %>% rename(vssc_month = report_month)) %>%
  left_join(access_metrics %>% select(vssc_month, sta5a, new_pc_pt_wt)) %>%
  mutate(difference = new_pc_pt_wt - new_pc_pt_wt2)
```

* Among all `r new_comp %>% select(sta5a) %>% n_distinct() %>% comma(accuarcy = 1)` sta5as included:
    + The mean difference is `r mean(new_comp$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + One standard deviation of the difference is `r sd(new_comp$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + The 5th percentile is `r quantile(new_comp$difference, na.rm = T, c(0.05)) %>% comma(accuracy = 0.01)` days
    + The 95th percentile is `r quantile(new_comp$difference, na.rm = T, c(0.95)) %>% comma(accuracy = 0.01)` days

```{r}
ggplot(data = new_comp,
       aes(x = difference)) +
  geom_histogram(bins = 5000) +
  labs(x = "(Original Days) - (\"New\" Days)",
       y = "Observations") +
  scale_y_continuous(labels = comma_format(accuracy = 1))
```


## CRH Sta5as  
```{r}
new_comp2 <- new_comp %>%
  filter(sta5a %in% sta5as_to_include$sta5a)
```

* Among all `r new_comp2 %>% select(sta5a) %>% n_distinct() %>% comma(accuarcy = 1)` sta5as included:
    + The mean difference is `r mean(new_comp2$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + One standard deviation of the difference is `r sd(new_comp2$difference, na.rm = T) %>% comma(accuracy = 0.01)` days
    + The 5th percentile is `r quantile(new_comp2$difference, na.rm = T, c(0.05)) %>% comma(accuracy = 0.01)` days
    + The 95th percentile is `r quantile(new_comp2$difference, na.rm = T, c(0.95)) %>% comma(accuracy = 0.01)` days

```{r}
ggplot(data = new_comp2,
       aes(x = difference)) +
  geom_histogram(bins = 5000) +
  labs(x = "(Original Days) - (\"New\" Days)",
       y = "Observations") +
  scale_y_continuous(labels = comma_format(accuracy = 1))
```