---
title: "Interpreting 3-way Interaction (ITS)"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(emmeans)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
pactcc_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "PACT_CC",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

$$ \text{Established Patient Wait Time} = \beta_0 +\beta_{time}X_{time}+\beta_{\text{PC CRH}}X_{\text{PC CRH}} + \beta_{Post Imp.}X_{Post Imp.}+ $$

$$\beta_{\text{time}\times\text{PC CRH}}X_{time}X_{\text{PC CRH}}+\beta_{\text{time}\times\text{Post Imp.}}X_{time}X_{\text{Post Imp.}} +\beta_{\text{PC CRH}\times\text{Post Imp.}}X_{\text{PC CRH}}X_{\text{Post Imp.}} +$$

$$\beta_{time\times\text{PC CRH}\times\text{Post Imp.}}X_{time}X_{\text{PC CRH}}X_{\text{Post Imp.}} $$

# Established Patient Wait Time  

* $\beta_{intercept}=52.31$
* $\beta_{time}=0.57$
* $\beta_{\text{PC CRH}}=-5.46$
* $\beta_{\text{Post Imp.}}=-7.62$
* $\beta_{time\times\text{PC CRH}}=-0.06$
* $\beta_{time\times\text{Post Imp.}}=0.39$
* $\beta_{\text{PC CRH}\times\text{Post Imp.}}=2.63$
* $\beta_{time\times\text{PC CRH}\times\text{Post Imp.}}=-0.23$

```{r}
intercept <- 52.31
b_time <- 0.57
b_pc_crh <- -5.46
b_post_imp <- -7.62
b_time_x_pc_crh <- -0.06
b_time_x_post_imp <- 0.39
b_pc_crh_x_post_imp <- 2.63
b_time_x_pc_crh_x_post_imp <- -0.23
#

```

## Contrast 1  
* $Time = 1$
* $\text{Post Imp.} = 0$

### PC CRH  
$$ y_{\text{PC CRH}} = 52.31 + 0.57\times(1)+(-5.46)\times(1)+(-7.62)\times(0)+(-0.06)\times(1\times1)+0.39\times(1\times0) + 2.63\times(1\times0) +(-0.23)\times(1\times1\times0)$$

$$ y_{\text{PC CRH}} = 52.31 + 0.57+(-5.46)+0+(-0.06)+0 + 0 +0 = 47.36$$

### No PC CRH  
$$ y_{\text{No PC CRH}} = 52.31 + 0.57\times(1)+(-5.46)\times(0)+(-7.62)\times(0)+(-0.06)\times(1\times0)+0.39\times(1\times0) + 2.63\times(0\times0) +(-0.23)\times(1\times0\times0)$$

$$ y_{\text{PC CRH}} = 52.31 + 0.57+0+0+0+0 + 0 +0 = 52.88$$

### No PC CRH - PC CRH  

$$ 52.88-47.36=5.52$$

## Contrast 2  
* $Time = 1$
* $\text{Post Imp.} = 1$

### PC CRH  
$$ y_{\text{PC CRH}} = 52.31 + 0.57\times(1)+(-5.46)\times(1)+(-7.62)\times(1)+(-0.06)\times(1\times1)+0.39\times(1\times1) + 2.63\times(1\times1) +(-0.23)\times(1\times1\times1)$$

$$ y_{\text{PC CRH}} = 52.31 + 0.57+(-5.46)+(-7.62)+(-0.06)+0.39 + 2.63 +(-0.23) = 42.53$$

### No PC CRH  
$$ y_{\text{No PC CRH}} = 52.31 + 0.57\times(1)+(-5.46)\times(0)+(-7.62)\times(1)+(-0.06)\times(1\times0)+0.39\times(1\times1) + 2.63\times(0\times1) +(-0.23)\times(1\times0\times1)$$

$$ y_{\text{PC CRH}} = 52.31 + 0.57+0+(-7.62)+0+0.39 + 0 +0 = 45.65$$

### No PC CRH - PC CRH  

$$ 45.65-42.53=3.12$$

## Contrast 3  
* $Time = 17$
* $\text{Post Imp.} = 0$

### PC CRH  
$$ y_{\text{PC CRH}} = 52.31 + 0.57\times(17)+(-5.46)\times(1)+(-7.62)\times(0)+(-0.06)\times(17\times1)+0.39\times(17\times0) + 2.63\times(1\times0) +(-0.23)\times(17\times1\times0)$$

$$ y_{\text{PC CRH}} = 52.31 + 9.69+(-5.46)+0+(-1.02)+0 + 0 +0 = 55.52$$

### No PC CRH  
$$ y_{\text{No PC CRH}} = 52.31 + 0.57\times(17)+(-5.46)\times(0)+(-7.62)\times(0)+(-0.06)\times(17\times0)+0.39\times(17\times0) + 2.63\times(0\times0) +(-0.23)\times(17\times0\times0)$$

$$ y_{\text{PC CRH}} = 52.31 + 9.69+0+0+0+0 + 0 +0 = 62.0$$

### No PC CRH - PC CRH  

$$ 62.0-55.52=6.48$$

## Contrast 4  
* $Time = 17$
* $\text{Post Imp.} = 1$

### PC CRH  
$$ y_{\text{PC CRH}} = 52.31 + 0.57\times(17)+(-5.46)\times(1)+(-7.62)\times(1)+(-0.06)\times(17\times1)+0.39\times(17\times1) + 2.63\times(1\times1) +(-0.23)\times(17\times1\times1)$$

$$ y_{\text{PC CRH}} = 52.31 + 9.69+(-5.46)+(-7.62)+(-1.02)+6.63 + 2.63 +(-3.91) = 53.25$$

### No PC CRH  
$$ y_{\text{No PC CRH}} = 52.31 + 0.57\times(17)+(-5.46)\times(0)+(-7.62)\times(1)+(-0.06)\times(17\times0)+0.39\times(17\times1) + 2.63\times(0\times1) +(-0.23)\times(17\times0\times1)$$

$$ y_{\text{PC CRH}} = 52.31 + 9.69+0+(-7.62)+0+6.63 + 0 +0 = 61.01$$

### No PC CRH - PC CRH  

$$ 61.01-53.25=7.76$$

## Contrast 5  
* $Time = 1$
* $\text{PC CRH} = 1$

### Post Implementation    
$$ y_{\text{Post Imp.}} = 52.31 + 0.57\times(1)+(-5.46)\times(1)+(-7.62)\times(1)+(-0.06)\times(1\times1)+0.39\times(1\times1) + 2.63\times(1\times1) +(-0.23)\times(1\times1\times1)$$

$$ y_{\text{Post Imp.}} = 52.31 + 0.57+(-5.46)+(-7.62)+(-0.06)+0.39 + 2.63 +(-0.23) = 42.53$$

### Pre Implementation    
$$ y_{\text{Pre Imp.}} = 52.31 + 0.57\times(1)+(-5.46)\times(1)+(-7.62)\times(0)+(-0.06)\times(1\times1)+0.39\times(1\times0) + 2.63\times(1\times0) +(-0.23)\times(1\times1\times0)$$

$$ y_{\text{Pre Imp.}} = 52.31 + 0.57+(-5.46)+0+(-0.06)+0 + 0 +0 = 47.36$$

### Pre Implementation - Post Implementation     

$$ 47.36-42.53=4.83$$

## Contrast 6  
* $Time = 17$
* $\text{PC CRH} = 1$

### Post Implementation    
$$ y_{\text{Post Imp.}} = 52.31 + 0.57\times(17)+(-5.46)\times(1)+(-7.62)\times(1)+(-0.06)\times(17\times1)+0.39\times(17\times1) + 2.63\times(1\times1) +(-0.23)\times(17\times1\times1)$$

$$ y_{\text{Post Imp.}} = 52.31 + 9.69+(-5.46)+(-7.62)+(-1.02)+6.63 + 2.63 +(-3.91) = 53.25$$

### Pre Implementation    
$$ y_{\text{Pre Imp.}} = 52.31 + 0.57\times(17)+(-5.46)\times(1)+(-7.62)\times(0)+(-0.06)\times(17\times1)+0.39\times(17\times0) + 2.63\times(1\times0) +(-0.23)\times(17\times1\times0)$$

$$ y_{\text{Pre Imp.}} = 52.31 + 9.69+(-5.46)+0+(-1.02)+0 + 0 +0 = 55.52$$

### Pre Implementation - Post Implementation     

$$ 55.52-53.25=2.27$$

## Contrast 7  
* $Time = 1$
* $\text{PC CRH} = 1$
* $\text{Post Imp.} = 0$

$$ y_{7} = 52.31 + 0.57\times(1)+(-5.46)\times(1)+(-7.62)\times(0)+(-0.06)\times(1\times1)+0.39\times(1\times0) + 2.63\times(1\times0) +(-0.23)\times(1\times1\times0)$$

$$ y_{7} = 52.31 + 0.57+(-5.46)+0+(-0.06)+0 + 0 +0 = 47.36$$

## Contrast 8  
* $Time = 17$
* $\text{PC CRH} = 1$
* $\text{Post Imp.} = 1$
### PC CRH  
$$ y_{\text{PC CRH}} = 52.31 + 0.57\times(17)+(-5.46)\times(1)+(-7.62)\times(1)+(-0.06)\times(17\times1)+0.39\times(17\times1) + 2.63\times(1\times1) +(-0.23)\times(17\times1\times1)$$

$$ y_{\text{PC CRH}} = 52.31 + 9.69+(-5.46)+(-7.62)+(-1.02)+6.63 + 2.63 +(-3.91) = 53.25$$