---
title: "PC CRH Analysis: 3-way Interaction (ITS)"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(emmeans)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
pactcc_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "PACT_CC",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
# setting flag for initiated_pc_crh_b4_feb_2020
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         initiated_pc_crh_b4_march_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-03-01"), TRUE, FALSE),
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#identifying sta5as that had at least 10 PC CRH encounters per month from October, 2019 through March, 2020
sta5as_w_gt9 <- crh_flag %>%
  filter(first_6_mos_w_10_flag == 1) %>%
  select(sta5a) %>% pull
# identifying sta5as that initiated PC CRH before February, 2020
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
# identifying pilot sta5as
pilot_sites <- dbGetQuery(pactcc_con,
                          "select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY20_working 
                          UNION
                          select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY21_working ") %>%
  filter(vimpact_pilot == 1) %>%
  select(sta5a = spoke_sta5a)
# propensity score-matched sta5as
ps_matched <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/ps_matched_sta5as.csv")
# identifying ps-matched sta5as 
ps_groups_w_gt9 <- ps_matched %>%
  filter(at_least_10_pc_crh_flag == 1
         & sta5a %in% sta5as_w_gt9) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a) %>%
  pull
# timely care success rate
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#VSSC access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#make dataframe of all dates and a column for time
dates <- access_metrics %>%
  filter(vssc_month <= ymd("2020-02-01")) %>%#this is where we DO NOT drop October, 2019
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#Uniques in PCMM, categorized
scrssn_count <- dbGetQuery(pactcc_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2019
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy19, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy19 < 450 ~ "< 450",
    scrssn_count_avg_fy19 >= 450 & scrssn_count_avg_fy19 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy19 >= 2400 & scrssn_count_avg_fy19 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy19 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#x intercept at October, 2019
vline_xint <- as.numeric(ymd("2019-10-01"))
```

```{r}
sta5as_to_include <- access_metrics %>%
  select(sta5a) %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%# must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, "PC CRH", "No PC CRH")) %>%# making CRH flag
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F #must have uniques in PCMM
        # & str_detect(s_abbr, "CBOC")# only CBOCs
           & scrssn_count_cat != "< 450")# must have > 450 uniqeus in PCMM
#number of sta5as in each category of uniques in PCMM
scrssn_cat_count <- sta5as_to_include %>%
  group_by(crh_flag, scrssn_count_cat) %>%
  summarise(count = n()) %>%
  mutate(count = as.character(count)) %>%
  pivot_wider(names_from = scrssn_count_cat, values_from = count)
#=================
model_1 <- access_metrics %>%
      inner_join(., sta5as_to_include) %>%
      inner_join(., dates) %>%
      left_join(., crh_flag %>% select(sta5a, first_6_mos_w_10_flag)) %>%
      mutate(all_first_6_months = if_else(sta5a %in% ps_groups_w_gt9, 
                                          "All First 6 Months", "Not All First 6 Months"),
             tna_drop = if_else(third_next_avail > 100, TRUE, FALSE),
             post_crh_implementation = factor(if_else(vssc_month >= "2019-10-01", 
                                                      "Post Implementation", "Pre Implementation"))) %>%
  filter(tna_drop == FALSE)
#
model_1$post_crh_implementation <- relevel(model_1$post_crh_implementation, ref = "Pre Implementation")
#
# write_csv(model_1,
#           here("Output", "its_model_data_13aug22.csv"))
```

 
## Established Patient WaitTime ~ Time X CRH X Period    
* This model includes `r nrow(model_1) %>% comma(accuracy = 1)` observations (i.e., rows) from `r n_distinct(model_1$sta5a)` sta5as over 17 months from October, 2018 through February, 2020   

### All PCMM Categories    
* There are `r model_1 %>% filter(crh_flag == "PC CRH") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH") %>% select(sta5a) %>% n_distinct()` control sta5as in this model


```{r}
model_1a <- model_1
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "Established Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_1 <- lm(est_pc_pt_wt ~ time*crh_flag*post_crh_implementation, data = model_1)
#
lm_1$call
#
tab_model(lm_1,
            show.se = TRUE,
            dv.labels = "Established Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_1.emm <- emmeans(lm_1, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_1.emm, simple = "post_crh_implementation")
#
pairs(lm_1.emm, simple = "crh_flag")
#
contrast(lm_1.emm, "consec", simple = "each", combine = TRUE)
```

### 450 - 2,399 Uniques      
* There are `r model_1 %>% filter(crh_flag == "PC CRH" & scrssn_count_cat == "450 - 2,399") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH" & scrssn_count_cat == "450 - 2,399") %>% select(sta5a) %>% n_distinct()` control sta5as in this model

```{r}
model_1a <- model_1 %>%
  filter(scrssn_count_cat == "450 - 2,399")
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "Established Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_2 <- lm(est_pc_pt_wt ~ time*crh_flag*post_crh_implementation, data = subset(model_1, scrssn_count_cat == "450 - 2,399"))
#
lm_2$call
#
tab_model(lm_2,
            show.se = TRUE,
            dv.labels = "Established Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_2.emm <- emmeans(lm_2, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_2.emm, simple = "post_crh_implementation")
#
pairs(lm_2.emm, simple = "crh_flag")
#
contrast(lm_2.emm, "consec", simple = "each", combine = TRUE)
```

### 2,400 - 9,999 Uniques      
* There are `r model_1 %>% filter(crh_flag == "PC CRH" & scrssn_count_cat == "2,400 - 9,999") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH" & scrssn_count_cat == "2,400 - 9,999") %>% select(sta5a) %>% n_distinct()` control sta5as in this model

```{r}
model_1a <- model_1 %>%
  filter(scrssn_count_cat == "2,400 - 9,999")
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "Established Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_3 <- lm(est_pc_pt_wt ~ time*crh_flag*post_crh_implementation, data = subset(model_1, scrssn_count_cat == "2,400 - 9,999"))
#
lm_3$call
#
tab_model(lm_3,
            show.se = TRUE,
            dv.labels = "Established Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_3.emm <- emmeans(lm_3, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_3.emm, simple = "post_crh_implementation")
#
pairs(lm_3.emm, simple = "crh_flag")
#
contrast(lm_3.emm, "consec", simple = "each", combine = TRUE)
```

### 10,000+ Uniques      
* There are `r model_1 %>% filter(crh_flag == "PC CRH" & scrssn_count_cat == "10,000+") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH" & scrssn_count_cat == "10,000+") %>% select(sta5a) %>% n_distinct()` control sta5as in this model

```{r}
model_1a <- model_1 %>%
  filter(scrssn_count_cat == "10,000+")
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "Established Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_4 <- lm(est_pc_pt_wt ~ time*crh_flag*post_crh_implementation, 
           data = subset(model_1, scrssn_count_cat == "10,000+"))
#
lm_4$call
#
tab_model(lm_4,
            show.se = TRUE,
            dv.labels = "Established Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_4.emm <- emmeans(lm_4, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_4.emm, simple = "post_crh_implementation")
#
pairs(lm_4.emm, simple = "crh_flag")
#
contrast(lm_4.emm, "consec", simple = "each", combine = TRUE)
```

## New Patient WaitTime ~ Time X CRH X Period    
* This model includes `r nrow(model_1) %>% comma(accuracy = 1)` observations (i.e., rows) from `r n_distinct(model_1$sta5a)` sta5as over 17 months from October, 2018 through February, 2020   

### All PCMM Categories    
* There are `r model_1 %>% filter(crh_flag == "PC CRH") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH") %>% select(sta5a) %>% n_distinct()` control sta5as in this model


```{r}
model_1a <- model_1
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "New Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_1 <- lm(new_pc_pt_wt ~ time*crh_flag*post_crh_implementation, data = model_1)
#
lm_1$call
#
tab_model(lm_1,
            show.se = TRUE,
            dv.labels = "New Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_1.emm <- emmeans(lm_1, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_1.emm, simple = "post_crh_implementation")
#
pairs(lm_1.emm, simple = "crh_flag")
#
contrast(lm_1.emm, "consec", simple = "each", combine = TRUE)
```

### 450 - 2,399 Uniques      
* There are `r model_1 %>% filter(crh_flag == "PC CRH" & scrssn_count_cat == "450 - 2,399") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH" & scrssn_count_cat == "450 - 2,399") %>% select(sta5a) %>% n_distinct()` control sta5as in this model

```{r}
model_1a <- model_1 %>%
  filter(scrssn_count_cat == "450 - 2,399")
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "New Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_2 <- lm(new_pc_pt_wt ~ time*crh_flag*post_crh_implementation, data = subset(model_1, scrssn_count_cat == "450 - 2,399"))
#
lm_2$call
#
tab_model(lm_2,
            show.se = TRUE,
            dv.labels = "New Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_2.emm <- emmeans(lm_2, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_2.emm, simple = "post_crh_implementation")
#
pairs(lm_2.emm, simple = "crh_flag")
#
contrast(lm_2.emm, "consec", simple = "each", combine = TRUE)
```

### 2,400 - 9,999 Uniques      
* There are `r model_1 %>% filter(crh_flag == "PC CRH" & scrssn_count_cat == "2,400 - 9,999") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH" & scrssn_count_cat == "2,400 - 9,999") %>% select(sta5a) %>% n_distinct()` control sta5as in this model

```{r}
model_1a <- model_1 %>%
  filter(scrssn_count_cat == "2,400 - 9,999")
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "New Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_3 <- lm(new_pc_pt_wt ~ time*crh_flag*post_crh_implementation, data = subset(model_1, scrssn_count_cat == "2,400 - 9,999"))
#
lm_3$call
#
tab_model(lm_3,
            show.se = TRUE,
            dv.labels = "New Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_3.emm <- emmeans(lm_3, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_3.emm, simple = "post_crh_implementation")
#
pairs(lm_3.emm, simple = "crh_flag")
#
contrast(lm_3.emm, "consec", simple = "each", combine = TRUE)
```

### 10,000+ Uniques      
* There are `r model_1 %>% filter(crh_flag == "PC CRH" & scrssn_count_cat == "10,000+") %>% select(sta5a) %>% n_distinct()` distinct sta5as that had at least 2 consecutive months with > 9 PC CRH encounters, and `r model_1 %>% filter(crh_flag != "PC CRH" & scrssn_count_cat == "10,000+") %>% select(sta5a) %>% n_distinct()` control sta5as in this model

```{r}
model_1a <- model_1 %>%
  filter(scrssn_count_cat == "10,000+")
###
ggplot(data = model_1a,
       aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_vline(xintercept = vline_xint,
             lty = 3) +
  scale_x_date(breaks = "2 months") +
  geom_line(alpha = 0.35) +
  geom_smooth(data = subset(model_1a, vssc_month > ymd("2019-09-30")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "darkorchid3",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  geom_smooth(data = subset(model_1a, vssc_month <= ymd("2019-10-01")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = crh_flag, lty = crh_flag),
              color = "forestgreen",
              inherit.aes = FALSE,
              se = FALSE,
              method = "lm",
              size = 2) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270, vjust = 0.3)) +
  ggsci::scale_color_d3() +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  labs(y = "New Patient Wait Time (days)")
```

```{r}
options(width = 400)
lm_4 <- lm(new_pc_pt_wt ~ time*crh_flag*post_crh_implementation, 
           data = subset(model_1, scrssn_count_cat == "10,000+"))
#
lm_4$call
#
tab_model(lm_4,
            show.se = TRUE,
            dv.labels = "New Patient Wait Time",
          pred.labels = c("Intercept","Time", "PC CRH (vs. No PC CRH)",
                          "Post Implementation (vs. Pre)",
                          "Time X PC CRH (vs. No PC CRH)",
                          "Time X Post Implementation (vs. Pre)",
                          "PC CRH (vs. No PC CRH) X Post Implementation (vs. Pre)",
                          "(Time X PC CRH (vs. No PC CRH)) X Post Implementation (vs. Pre)"))
#
lm_4.emm <- emmeans(lm_4, ~ time*crh_flag*post_crh_implementation, at = list(time = c(1, 10, 17)))
#
pairs(lm_4.emm, simple = "post_crh_implementation")
#
pairs(lm_4.emm, simple = "crh_flag")
#
contrast(lm_4.emm, "consec", simple = "each", combine = TRUE)
```


