---
title: "Post-Pandemic Abstract: Tables and Other Descriptives"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month),
         tna_new_source = as.numeric(tna_new_source))
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-03-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
#--
pc_community_care <- dbGetQuery(oabi_con,
                                 "select *
                                 from [OABI_MyVAAccess].[crh_eval].F5_avg_pc_cons_post_COVID")
```

```{r}
# a vector of sta5as that:
    #1. have at least 451 average unique scrssns in pcmm FY20
    #2. are a CBOC, OOS, VAMC, or HCC
sta5as_to_start_with <- vast %>%
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F
         & scrssn_count_cat != "< 450"
         & s_abbr %in% c("PCCBOC", "MSCBOC", "VAMC", "OOS", "HCC")) %>%
  select(sta5a, s_abbr, scrssn_count_cat)
#-----
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    (last_mo_mt9_pc_crh == 1 | next_mo_mt9_pc_crh == 1),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit = replace_na(meets_inc_crit, 0)) %>%#replacing NA with 0
  mutate(
    period_meeting_citeria = factor(case_when(
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month < ymd("2020-03-01") #AND month < march 2020
      ~ "Before March 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month >= ymd("2020-03-01")#AND month between March 2020
      & vssc_month <= ymd("2020-09-01") #AND September 2020
      ~ "Between March and September 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month > ymd("2020-09-01") #AND month > Setember 2020
      ~ "After September 2020",#label
      TRUE ~ "Not Enough PC CRH"),#ELSE
      ordered = TRUE,
      levels = c("Before March 2020", 
                 "Between March and September 2020",
                 "After September 2020",
                 "Not Enough PC CRH")))
#--
sta5a_month_inc <- months_meeting_inclusion_criteria %>%
  group_by(sta5a, period_meeting_citeria) %>%
  summarise(count = n()) %>%
  filter(period_meeting_citeria != "Not Enough PC CRH") %>%
  group_by(sta5a) %>%
  summarise(period1_inc = sum(if_else(period_meeting_citeria == "Before March 2020" & count > 1, 1, 0)),
            period2_inc = sum(if_else(period_meeting_citeria == "Between March and September 2020" & count > 1, 1, 0)),
            period3_inc = sum(if_else(period_meeting_citeria == "After September 2020" & count > 1, 1, 0)))
#--
cases_controls <- sta5as_to_start_with %>%
  left_join(., sta5a_month_inc) %>%
  mutate(across(contains("period"), ~replace_na(.x, 0)),
         not_enough_crh = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0 & sta5a %in% pen_rate$sta5a, 
                                  1, 0),
         potential_control = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0 & not_enough_crh == 0, 1, 0),
         ever_met_criteria = if_else(period1_inc == 1 | period2_inc == 1 | period3_inc == 1, 1, 0),
         treated = factor(case_when(period3_inc == 1 ~ "Treated",
                             potential_control == 1 ~ "Control",
                             TRUE ~ "Drop me!"),
                          ordered = T, 
                          levels = c("Treated", "Control", "Drop me!"))) %>%
  filter(treated != "Drop me!")
#$$$$$$
gap_flag <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates) %>%
  left_join(gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  group_by(sta5a) %>%
  summarise(gap_avg = mean(gap_metric, na.rm = T)) %>%
  mutate(gap_flag = case_when(
    gap_avg < 1 ~ "< 1.0",
    gap_avg > 1.2 ~ "> 1.2",
    TRUE ~ "1.0-1.2"
  ))
#========
outcomes_avg <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates %>%
               select(-time)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, 
                     est_pc_pt_wt_pid,
                     new_pc_pt_wt_create,
                     tna_new_source,
                     new_0_20_days_create)) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  group_by(sta5a) %>%
  summarise(across(where(is.numeric), ~mean(.x, na.rm = T)))
  
#--------
analytic_df <- cases_controls %>%
  select(sta5a, treated, scrssn_count_cat) %>%
  left_join(., gap_flag) %>%
  left_join(., vast %>%
              select(sta5a, urh_vast, s_abbr)) %>%
  mutate(treated = factor(treated,
                          levels = c("Treated", "Control"),
                          ordered = TRUE),
         urh_vast2 = if_else(urh_vast == "U", "Urban", "Rural"),
         gap_flag = factor(gap_flag,
                           ordered = TRUE,
                           levels = c("< 1.0", "1.0-1.2", "> 1.2"))) %>%
  left_join(., outcomes_avg)
```


# Front Matter  

## Description of this report  

* This is a collection of tables and statistics for the post-pandemic abstract 

## Decision Points  

* Per our discussion on November 28th and 30th I am putting-together a series of tables and data descriptions to fill-in numbers in the post-pandemic abstract
    
## Analytic details  


* Description of the data:
    + The data analyzed here include the 30 months from October 2020 through March 2023
      + This is also the period in which the __gap_flag__ covariate is being created
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + There are `r analytic_df %>% select(sta5a) %>% n_distinct()` unique sta5as
      + `r sum(analytic_df$treated == "Treated")` of these met our criteria for PC CRH at least once after September 2020  
      + `r sum(str_detect(analytic_df$s_abbr, "CBOC") == T)` of these are CBOCs
      + `r sum(str_detect(analytic_df$s_abbr, "HCC|VAMC") == T)` of these are HCCs or VAMCs
      + `r sum(str_detect(analytic_df$s_abbr, "OOS") == T)` of these are OOS    
    + Treated sta5as are the `r sum(analytic_df$treated == "Treated")` sta5as that __met our inclusion criteria after September 2020__ 
    + Control sta5as are the `r sum(analytic_df$treated != "Treated")` sta5as that have __never had a PC CRH encounter__


# Gap Metric X PC CRH  

```{r}
analytic_df %>%
  tabyl(gap_flag, treated) %>%
  adorn_totals("both") %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  add_header_above(c("", "Observed" = 2, ""),
                   bold = TRUE)
#
chisq_df <- analytic_df %>%
  tabyl(gap_flag, treated) %>%
  chisq.test()
#
chisq_df$expected %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  remove_column(1) %>%
  add_header_above(c("", "Expected" = 2, ""),
                   bold = TRUE)
#
chisq_df
```

## By Uniques  
### 450 - 2,399   
```{r}
analytic_df %>%
  filter(scrssn_count_cat == "450 - 2,399") %>%
  tabyl(gap_flag, treated) %>%
  adorn_totals("both") %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  add_header_above(c("", "Observed" = 2, ""),
                   bold = TRUE)
#
chisq_df <- analytic_df %>%
  filter(scrssn_count_cat == "450 - 2,399") %>%
  tabyl(gap_flag, treated) %>%
  chisq.test()
#
chisq_df$expected %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  remove_column(1) %>%
  add_header_above(c("", "Expected" = 2, ""),
                   bold = TRUE)
#
chisq_df
```

  
### 2,400 - 9,999   
```{r}
analytic_df %>%
  filter(scrssn_count_cat == "2,400 - 9,999") %>%
  tabyl(gap_flag, treated) %>%
  adorn_totals("both") %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  add_header_above(c("", "Observed" = 2, ""),
                   bold = TRUE)
#
chisq_df <- analytic_df %>%
  filter(scrssn_count_cat == "2,400 - 9,999") %>%
  tabyl(gap_flag, treated) %>%
  chisq.test()
#
chisq_df$expected %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  remove_column(1) %>%
  add_header_above(c("", "Expected" = 2, ""),
                   bold = TRUE)
#
chisq_df
```


### 10,000+   
```{r}
analytic_df %>%
  filter(scrssn_count_cat == "10,000+") %>%
  tabyl(gap_flag, treated) %>%
  adorn_totals("both") %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  add_header_above(c("", "Observed" = 2, ""),
                   bold = TRUE)
#
chisq_df <- analytic_df %>%
  filter(scrssn_count_cat == "10,000+") %>%
  tabyl(gap_flag, treated) %>%
  chisq.test()
#
chisq_df$expected %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  remove_column(1) %>%
  add_header_above(c("", "Expected" = 2, ""),
                   bold = TRUE)
#
chisq_df
```

## By Rurality  
### Urban     
```{r}
analytic_df %>%
  filter(urh_vast2 == "Urban") %>%
  tabyl(gap_flag, treated) %>%
  adorn_totals("both") %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  add_header_above(c("", "Observed" = 2, ""),
                   bold = TRUE)
#
chisq_df <- analytic_df %>%
  filter(urh_vast2 == "Urban") %>%
  tabyl(gap_flag, treated) %>%
  chisq.test()
#
chisq_df$expected %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  remove_column(1) %>%
  add_header_above(c("", "Expected" = 2, ""),
                   bold = TRUE)
#
chisq_df
```


### Rural     
```{r}
analytic_df %>%
  filter(urh_vast2 == "Rural") %>%
  tabyl(gap_flag, treated) %>%
  adorn_totals("both") %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  add_header_above(c("", "Observed" = 2, ""),
                   bold = TRUE)
#
chisq_df <- analytic_df %>%
  filter(urh_vast2 == "Rural") %>%
  tabyl(gap_flag, treated) %>%
  chisq.test()
#
chisq_df$expected %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("", "Treated", "Control", "Total")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = T) %>%
  row_spec(4, bold = T) %>%
  remove_column(1) %>%
  add_header_above(c("", "Expected" = 2, ""),
                   bold = TRUE)
#
chisq_df
```


# Access Metrics Among Treated Sites, by Gap Status  

```{r}
lm_fxn <- function(formula, covar_name){
  analytic_df %>%
    mutate(gap_flag = relevel(factor(gap_flag, ordered = F), ref = '> 1.2')) %>%
    filter(treated == "Treated") %>%
    lm(formula, data = .) %>%
    tab_model(.,
              dv.labels = {{covar_name}})
  
}
```

## Established Patient Wait Time (PID)  
```{r}
lm_fxn(est_pc_pt_wt_pid ~ gap_flag, "Established Patient Wait Time (PID)")
```

## New Patient Wait Time (create)
```{r}
lm_fxn(new_pc_pt_wt_create ~ gap_flag, "New Patient Wait Time (create)")
```

## Third Next Available
```{r}
lm_fxn(tna_new_source ~ gap_flag, "Third Next Available")
```

## Timely Care  
```{r}
lm_fxn(tc_pc_success_prop ~ gap_flag, "Timely Care")
```

