---
title: "SGIM Poster CRH Post-COVID Plots & Tables"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 30),
             axis.text = element_text(size = 24),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 24),
             legend.title = element_text(size = 28),
             plot.caption = element_text(size = 12))
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0),
         urh_vast2 = if_else(urh_vast == "U", "U", "R")) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_metric_cat = factor(case_when(gap_metric >= 1.2 ~ "> 1.2",
                                    gap_metric < 1 ~ "< 1.0",
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ "1.0-1.2")))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}

#=================
analytic_df <- ps_matched %>%
  select(sta5a) %>%
  cross_join(., dates %>% 
               select(vssc_month)) %>%
  left_join(., ps_matched %>% 
              select(sta5a, treated_num)) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source) %>%
              mutate(tna_new_source = as.numeric(tna_new_source))) %>%
  left_join(., pen_rate %>%
              select(sta5a, vssc_month, crh_encounter_count)) %>%
  left_join(., vast %>%
              select(sta5a, urh_vast2)) %>%
  mutate(gap_cat = factor(case_when(gap_metric < 1.0 ~ "Understaffed",
                                    gap_metric >= 1.0 & gap_metric <= 1.2 ~ "Marginally Staffed",
                                    gap_metric > 1.2 ~ "Fully Staffed"), 
                          ordered = T,
                          levels = c("Understaffed", "Marginally Staffed", "Fully Staffed")))
```

# Front Matter  

## Description of this report  

* This is a collection of potential plots and tables for the post-COVID SGIM poster

    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, treated_num) %>% distinct() %>% summarise(tot = sum(treated_num))` of these met our criteria for PC CRH 
    
* Description of _Propensity Score_ matching
    + This PS model consists of 
        + Covariates matched on their average values over Q4 FY20
        + Outcomes matched on their average values over Q4 FY20
        + Site type (CBOC, VAMC/HCC, OOS) - Exact

# Plot #1  

```{r fig.asp=0.5}
p0 <- analytic_df %>%
    filter(treated_num == 1) %>%
    group_by(sta5a) %>%
    summarise(mean_gap = mean(gap_metric, na.rm = T),
              sd_gap = sd(gap_metric, na.rm = T),
              mean_val = mean(est_pc_pt_wt_pid, na.rm = T),
              sd_val = sd(est_pc_pt_wt_pid, na.rm = T)) %>%
    filter(is.na(mean_gap) == F) %>%
    mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "< 1.0",
                                      mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0-1.2",
                                      mean_gap > 1.2 ~ "> 1.2"), 
                            ordered = T,
                            levels = c("< 1.0", "1.0-1.2", "> 1.2"))) %>%
    ggplot(data = .,
           aes(x = reorder(sta5a, mean_val),
               y = mean_val,
               ymin = mean_val - sd_val,
               ymax = mean_val + sd_val,
               color = gap_cat)) +
  geom_point() +
    labs(x = "Sta5a",
         color = "Gap Metric") +
    scale_color_manual(values = c("red", "yellow2", "seagreen")) +
    theme(legend.position = "bottom",
          legend.title = element_text(size = 22))
#
plot_fxn <- function(outcome, outcome_char){
  analytic_df %>%
    filter(treated_num == 1) %>%
    group_by(sta5a) %>%
    summarise(mean_gap = mean(gap_metric, na.rm = T),
              sd_gap = sd(gap_metric, na.rm = T),
              mean_val = mean({{outcome}}, na.rm = T),
              sd_val = sd({{outcome}}, na.rm = T)) %>%
    filter(is.na(mean_gap) == F) %>%
    mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "< 1.0",
                                      mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0-1.2",
                                      mean_gap > 1.2 ~ "> 1.2"), 
                            ordered = T,
                            levels = c("< 1.0", "1.0-1.2", "> 1.2"))) %>%
    ggplot(data = .,
           aes(x = reorder(sta5a, mean_val),
               y = mean_val,
               ymin = mean_val - sd_val,
               ymax = mean_val + sd_val,
               color = gap_cat)) +
    geom_errorbar(linewidth = 0.5,
                  alpha = 0.7) +
    geom_point(alpha = 0.8) +
    labs(color = "Gap Metric",
         y = outcome_char) +
    scale_color_manual(values = c("red", "yellow2", "seagreen")) +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          legend.position = "none",
          axis.title.x = element_blank(),
          panel.grid.major.x = element_blank(),
          legend.title = element_text(size = 22))
}
#
p1 <- plot_fxn(est_pc_pt_wt_pid, "Established Patient WT +/- SD")
p2 <- plot_fxn(new_pc_pt_wt_create, "New Patient WT +/- SD")
p3 <- plot_fxn(tna_new_source, "Third Next Available +/- SD")
p_grid <- cowplot::plot_grid(p1, p2, p3, ncol = 3)
#
leg_p0 <- cowplot::get_legend(p0)
#
cowplot::plot_grid(p_grid, leg_p0, ncol = 1, rel_heights = c(1, 0.1))
```


# Plot #2  

```{r fig.asp=1.25}
analytic_df %>%
  filter(treated_num == 1) %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            mean_crh = mean(crh_encounter_count, na.rm = T),
            sd_crh = sd(crh_encounter_count, na.rm = T),
            n_valid_obs = sum(!is.na(crh_encounter_count))) %>%
  filter(is.na(mean_gap) == F) %>%
  mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "Understaffed",
                                    mean_gap >= 1.0 & mean_gap <= 1.2 ~ "Marginally Staffed",
                                    mean_gap > 1.2 ~ "Fully Staffed"), 
                          ordered = T,
                          levels = c("Understaffed", "Marginally Staffed", "Fully Staffed"))) %>%
  ggplot(data = .,
         aes(x = reorder(sta5a, mean_crh),
             y = mean_crh,
             ymin = mean_crh - sd_crh,
             ymax = mean_crh + sd_crh,
             color = gap_cat)) +
  geom_point() +
  geom_errorbar(linewidth = 0.4) +
  scale_color_manual(values = c("red", "yellow2", "seagreen")) +
  labs(y = "Mean PC CRH Encounters per Month +/- SD",
       color = "Gap Metric") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        legend.position = c(0.25, 0.8),
        legend.title = element_blank())+ 
  guides(color = guide_legend(override.aes = list(size = 3, linewidth = 1))) 
```



# Table 1    

```{r}
analytic_df$treated_num <- relevel(factor(analytic_df$treated_num, ordered = F), ref = "0")
#
trtd_fxn <- function(outcome){
  analytic_df$treated_num <- relevel(factor(analytic_df$treated_num, ordered = F), ref = "0")
  fmla <- as.formula(paste0({{outcome}},
                            "~ treated_num + (1|sta5a)"))
  #
  lmer(fmla,
       data = analytic_df)
}
#-----
fullyStaffed_fxn <- function(outcome){
  analytic_df$gap_cat <- relevel(factor(analytic_df$gap_cat, ordered = F), ref = "Fully Staffed")
  #
  fmla <- as.formula(paste0({{outcome}},
                            "~ gap_cat + (1|sta5a)"))
  #
  lmer(fmla,
       data = analytic_df)
}
#-----
margStaffed_fxn <- function(outcome){
  analytic_df$gap_cat <- relevel(factor(analytic_df$gap_cat, ordered = F), ref = "Marginally Staffed")
  #
  fmla <- as.formula(paste0({{outcome}},
                            "~ gap_cat + (1|sta5a)"))
  #
  lmer(fmla,
       data = analytic_df)
}
#-----
rural_fxn <- function(outcome){
  analytic_df$urh_vast2 <- relevel(factor(analytic_df$urh_vast2, ordered = F), ref = "U")
  #
  fmla <- as.formula(paste0({{outcome}},
                            "~ urh_vast2 + (1|sta5a)"))
  #
  lmer(fmla,
       data = analytic_df)
}
#============
trt_est <- trtd_fxn("est_pc_pt_wt_pid")
ci_trt_est <- confint(trt_est, "treated_num1", method = "profile")
#
full_est <- fullyStaffed_fxn("est_pc_pt_wt_pid")
ci_full_est <- confint(full_est, "gap_catUnderstaffed", method = "profile")
#
marg_est <- margStaffed_fxn("est_pc_pt_wt_pid")
ci_marg_est <- confint(marg_est, "gap_catUnderstaffed", method = "profile")
#
urh_est <- rural_fxn("est_pc_pt_wt_pid")
ci_urh_est <- confint(urh_est, "urh_vast2R", method = "profile")
#--
trt_new <- trtd_fxn("new_pc_pt_wt_create")
ci_trt_new <- confint(trt_new, "treated_num1", method = "profile")
#
full_new <- fullyStaffed_fxn("new_pc_pt_wt_create")
ci_full_new <- confint(full_new, "gap_catUnderstaffed", method = "profile")
#
marg_new <- margStaffed_fxn("new_pc_pt_wt_create")
ci_marg_new <- confint(marg_new, "gap_catUnderstaffed", method = "profile")
#
urh_new <- rural_fxn("new_pc_pt_wt_create")
ci_urh_new <- confint(urh_new, "urh_vast2R", method = "profile")
#--
trt_tna <- trtd_fxn("tna_new_source")
ci_trt_tna <- confint(trt_tna, "treated_num1", method = "profile")
#
full_tna <- fullyStaffed_fxn("tna_new_source")
ci_full_tna <- confint(full_tna, "gap_catUnderstaffed", method = "profile")
#
marg_tna <- margStaffed_fxn("tna_new_source")
ci_marg_tna <- confint(marg_tna, "gap_catUnderstaffed", method = "profile")
#
urh_tna <- rural_fxn("tna_new_source")
ci_urh_tna <- confint(urh_tna, "urh_vast2R", method = "profile")
#====
tibble(name_col = 
         c("Treated vs. Control", "Gap < 1.0 vs. > 1.2", "Gap < 1.0 vs. 1.0-1.2", "Rural vs. Urban"),
       est_col = 
         c(paste0(comma(fixef(trt_est)[2], accuracy = 0.01),
                  " (", comma(ci_trt_est[1], accuracy = 0.01),
                  ", ", comma(ci_trt_est[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(full_est)[2], accuracy = 0.01),
                  " (", comma(ci_full_est[1], accuracy = 0.01),
                  ", ", comma(ci_full_est[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(marg_est)[2], accuracy = 0.01),
                  " (", comma(ci_marg_est[1], accuracy = 0.01),
                  ", ", comma(ci_marg_est[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(urh_est)[2], accuracy = 0.01),
                  " (", comma(ci_urh_est[1], accuracy = 0.01),
                  ", ", comma(ci_urh_est[2], accuracy = 0.01),
                  ")")),
       new_col = 
         c(paste0(comma(fixef(trt_new)[2], accuracy = 0.01),
                  " (", comma(ci_trt_new[1], accuracy = 0.01),
                  ", ", comma(ci_trt_new[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(full_new)[2], accuracy = 0.01),
                  " (", comma(ci_full_new[1], accuracy = 0.01),
                  ", ", comma(ci_full_new[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(marg_new)[2], accuracy = 0.01),
                  " (", comma(ci_marg_new[1], accuracy = 0.01),
                  ", ", comma(ci_marg_new[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(urh_new)[2], accuracy = 0.01),
                  " (", comma(ci_urh_new[1], accuracy = 0.01),
                  ", ", comma(ci_urh_new[2], accuracy = 0.01),
                  ")")),
       tna_col = 
         c(paste0(comma(fixef(trt_tna)[2], accuracy = 0.01),
                  " (", comma(ci_trt_tna[1], accuracy = 0.01),
                  ", ", comma(ci_trt_tna[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(full_tna)[2], accuracy = 0.01),
                  " (", comma(ci_full_tna[1], accuracy = 0.01),
                  ", ", comma(ci_full_tna[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(marg_tna)[2], accuracy = 0.01),
                  " (", comma(ci_marg_tna[1], accuracy = 0.01),
                  ", ", comma(ci_marg_tna[2], accuracy = 0.01),
                  ")"),
           paste0(comma(fixef(urh_tna)[2], accuracy = 0.01),
                  " (", comma(ci_urh_tna[1], accuracy = 0.01),
                  ", ", comma(ci_urh_tna[2], accuracy = 0.01),
                  ")"))) %>%
  kbl(col.names = c("", "Established", "New", "TNA"),
      full_width = F) %>%
  kable_classic() %>%
  row_spec(0, bold = T)
```

# Table 2  

```{r}
analytic_df %>%
    group_by(sta5a, treated_num) %>%
    summarise(mean_gap = mean(gap_metric, na.rm = T)) %>%
    filter(is.na(mean_gap) == F) %>%
    mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "< 1.0",
                                      mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0-1.2",
                                      mean_gap > 1.2 ~ "> 1.2"), 
                            ordered = T,
                            levels = c("< 1.0", "1.0-1.2", "> 1.2"))) %>%
  left_join(., vast %>%
              select(sta5a, urh_vast2)) %>%
  filter(urh_vast2 == "R") %>%
  tabyl(gap_cat, treated_num) %>%
  adorn_totals() %>%
  adorn_percentages("col") %>% 
  adorn_pct_formatting(rounding = "half up", digits = 1) %>%
  adorn_ns(position = "front") %>%
  left_join(., analytic_df %>%
              group_by(sta5a, treated_num) %>%
              summarise(mean_gap = mean(gap_metric, na.rm = T)) %>%
              filter(is.na(mean_gap) == F) %>%
              mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "< 1.0",
                                                mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0-1.2",
                                                mean_gap > 1.2 ~ "> 1.2"), 
                                      ordered = T,
                                      levels = c("< 1.0", "1.0-1.2", "> 1.2"))) %>%
              left_join(., vast %>%
                          select(sta5a, urh_vast2)) %>%
              filter(urh_vast2 == "U") %>%
              tabyl(gap_cat, treated_num) %>%
              adorn_totals() %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front"),
            by = "gap_cat") %>%
  select(gap_cat, `1.x`, `0.x`, `1.y`, `0.y`) %>%
  kbl(col.names = c("", "Treated", "Control", "Treated", "Control"),
      align = c("l", rep("r", 4)),
      full_width = F) %>%
  kable_classic("striped") %>%
  row_spec(c(0, 4), bold = T) %>%
  add_header_above(c("", "Rural" = 2, "Urban" = 2),
                   bold = TRUE)

```

