---
title: "VISN 6 Gap Report"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#connecting to a06
a06_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "VHACDWA06.vha.med.va.gov",
                      Database = "CDWWork",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
vast_fips <- dbGetQuery(a06_con,
                       "select stationno, fips, lat, lon
from [CDWWork].[Dim].VAST")
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag) %>%
  left_join(., vast_fips, by = c("sta5a" = "stationno"))
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2022-10-01"), ymd("2024-03-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PCS_PCAT].[econ].PatientPCP_2020_2024
#                             	where fy = 2020
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
  
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
#-------
#nc_map <- tigris::counties(state = "NC", cb = TRUE)
```

```{r}
nc_sta5as <- c("558GA", '558GC', '565GA', '565GF', '590', '590GB', '590GC', '590GD', '590GE', '652GF')
# 
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [PACT_CC].[CRH].vw_gapMetric
                         where fy > 2022") %>%
  mutate(month_char = str_to_title(str_sub(mth, end = 3)),
         month_num = match(month_char, month.abb),
         cy = if_else(month_num > 9, as.numeric(fy) - 1, as.numeric(fy)),
         vssc_month = ymd(str_c(cy, month_num, "01", sep = "-")),
         gap_metric_capped = if_else(gap_metric > 3, 3, gap_metric),
         gap_metric_capped = na_if(gap_metric_capped, 0)) %>%
  select(sta5a = sta6a, vssc_month, gap_metric, fy, gap_metric_capped) %>%
  distinct() %>%
  inner_join(., vast)

```

# Front Matter  

## Description of this report  

* This is report looking at the gap metric of 10 sites in Washington County, NC compared to the rest of the nation and the rest of VISN 6
* All statistics below are using the `r nrow(dates)` months between October 2022 and March 2024, inclusive
* There are `r nrow(gap_metric)` observations total
* There are `r sum(gap_metric$gap_metric > 3, na.rm = T)` observations with a gap metric > 3.0  
    + I have capped the gap metric at 3.0 
* There are `r sum(gap_metric$gap_metric == 0, na.rm = T)` observations with a gap metric = 0 
    + I have replaced all zero gap metric values with NA

$$
\text{Gap Metric}=\frac{(\text{MD FTE}\times 1,200)(\text{APP FTE}\times 900)}{\text{Total Clinic Assigned Panel Size}}=\frac{\text{Maximum Clinic Patient Capacity}}{\text{Total Clinic Assigned Panel Size}}
$$

    
# By VISN  
```{r}
gap_metric %>%
  distinct %>%
  inner_join(., vast) %>%
  group_by(parent_visn) %>%
  summarise(sta5a_count = n_distinct(sta5a),
            mean_gap = mean(gap_metric_capped, na.rm = T),
            sd_gap = sd(gap_metric_capped, na.rm = T),
            pct_025 = quantile(gap_metric_capped, 0.025, na.rm = T),
            pct_975 = quantile(gap_metric_capped, 0.975, na.rm = T),
            pct_10 = quantile(gap_metric_capped, 0.10, na.rm = T),
            pct_90 = quantile(gap_metric_capped, 0.90, na.rm = T)) %>%
  mutate(mean_sd = paste0(comma(mean_gap, accuracy = 0.01), " (", comma(sd_gap, accuracy = 0.01), ")"),
         qtl_1 = paste0("[", comma(pct_10, accuracy = 0.01), ", ", comma(pct_90, accuracy = 0.01), "]"),
         qtl_2 = paste0("[", comma(pct_025, accuracy = 0.01), ", ", comma(pct_975, accuracy = 0.01), "]")) %>%
  select(parent_visn, sta5a_count, mean_sd, qtl_1, qtl_2) %>%
  adorn_totals() %>%
  kbl(col.names = c("VISN", "Sta5a Count", "Mean Gap (SD)", "[10th %-ile, 90th %-ile]", "[2.5th%-ile, 97.5th %-ile]"),
      align = c("c", rep("r", 4))) %>%
  kable_classic("striped", 
                full_width = F) %>%
  row_spec(c(0, 19), bold = T)
```

## Is VISN 6 Different?  

```{r}
gap_metric %>%
  inner_join(., vast) %>%
  mutate(visn_06_flag = factor(if_else(parent_visn == "06", "VISN 6", "Not VISN 6"), ordered = F)) %>%
  ggplot(data = .,
         aes(x = visn_06_flag, y = gap_metric_capped, fill = visn_06_flag)) +
  geom_boxplot() +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "Gap Metric")
#--
gap_metric %>%
  inner_join(., vast) %>%
  mutate(visn_06_flag = factor(if_else(parent_visn == "06", 1, 0), ordered = F),
         visn_06_flag = relevel(visn_06_flag, ref = "0")) %>%
  lm(gap_metric_capped ~ visn_06_flag,
      data = .) %>%
  tab_model()
```

* No, in the period between October 2022 and March 2024 sta5as in VISN 6 had a non-significant 0.01-unit greater Gap Metric than sta5as in the rest of the nation (p=0.36) 


# VISN 6  

```{r}
gap_metric %>%
  inner_join(., vast) %>%
  filter(parent_visn == "06") %>%
  group_by(sta5a, short_name) %>%
  summarise(mean_gap = mean(gap_metric_capped, na.rm = T),
            sd_gap = sd(gap_metric_capped, na.rm = T),
            pct_025 = quantile(gap_metric_capped, 0.025, na.rm = T),
            pct_975 = quantile(gap_metric_capped, 0.975, na.rm = T),
            pct_10 = quantile(gap_metric_capped, 0.10, na.rm = T),
            pct_90 = quantile(gap_metric_capped, 0.90, na.rm = T)) %>%
  mutate(mean_sd = paste0(comma(mean_gap, accuracy = 0.01), " (", comma(sd_gap, accuracy = 0.01), ")"),
         qtl_1 = paste0("[", comma(pct_10, accuracy = 0.01), ", ", comma(pct_90, accuracy = 0.01), "]"),
         qtl_2 = paste0("[", comma(pct_025, accuracy = 0.01), ", ", comma(pct_975, accuracy = 0.01), "]")) %>%
  arrange(desc(mean_gap)) %>%
  select(sta5a, short_name, mean_sd, qtl_1, qtl_2) %>%
  DT::datatable(.,
                colnames = c("Sta6a", "Site Name", "Mean Gap (SD)", "[10th %-ile, 90th %-ile]", "[2.5th%-ile, 97.5th %-ile]"),
                options = list(pageLength = 12))
```

## Is Washington County Different?  

```{r}
gap_metric %>%
  inner_join(., vast) %>%
  mutate(wash_cty_flag = factor(if_else(sta5a %in% nc_sta5as, "Washington County", "Not Washington County"), ordered = F)) %>%
  ggplot(data = .,
         aes(x = wash_cty_flag, y = gap_metric_capped, fill = wash_cty_flag)) +
  geom_boxplot() +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "Gap Metric")
#
gap_metric %>%
  inner_join(., vast) %>%
  mutate(wash_cty_flag = factor(if_else(sta5a %in% nc_sta5as, 1, 0), ordered = F),
         wash_cty_flag = relevel(wash_cty_flag, ref = "0")) %>%
  lm(gap_metric_capped ~ wash_cty_flag,
      data = .) %>%
  tab_model()
```

* Yes, in the period between October 2022 and March 2024 the 10 sta5as in Washington County had a 0.21 point lower (i.e., -0.21; p<0.001) Gap Metric compared to sta5as in the rest of the nation


# Washington County  

```{r}
gap_metric %>%
  inner_join(., vast) %>%
  filter(sta5a %in% nc_sta5as) %>%
  group_by(sta5a, short_name) %>%
  summarise(mean_gap = mean(gap_metric_capped, na.rm = T),
            sd_gap = sd(gap_metric_capped, na.rm = T),
            pct_025 = quantile(gap_metric_capped, 0.025, na.rm = T),
            pct_975 = quantile(gap_metric_capped, 0.975, na.rm = T),
            pct_10 = quantile(gap_metric_capped, 0.10, na.rm = T),
            pct_90 = quantile(gap_metric_capped, 0.90, na.rm = T),
            n_obs = n()) %>%
  mutate(mean_sd = paste0(comma(mean_gap, accuracy = 0.01), " (", comma(sd_gap, accuracy = 0.01), ")"),
         qtl_1 = paste0("[", comma(pct_10, accuracy = 0.01), ", ", comma(pct_90, accuracy = 0.01), "]"),
         qtl_2 = paste0("[", comma(pct_025, accuracy = 0.01), ", ", comma(pct_975, accuracy = 0.01), "]")) %>%
  arrange(desc(mean_gap)) %>%
  select(sta5a, short_name, mean_sd, qtl_1, qtl_2) %>%
  kbl(col.names = c("Sta6a", "Site Name", "Mean Gap (SD)", "[10th %-ile, 90th %-ile]", "[2.5th%-ile, 97.5th %-ile]"),
      align = c("l", "l", rep("r", 3))) %>%
  kable_classic("striped", 
                full_width = F) %>%
  row_spec(0, bold = T)
```


## Is Washington County Different Than The Rest of VISN 6?  

```{r}
gap_metric %>%
  inner_join(., vast) %>%
  filter(parent_visn == "06") %>%
  mutate(wash_cty_flag = factor(if_else(sta5a %in% nc_sta5as, "Washington County", "Not Washington County"), ordered = F)) %>%
  ggplot(data = .,
         aes(x = wash_cty_flag, y = gap_metric_capped, fill = wash_cty_flag)) +
  geom_boxplot() +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "Gap Metric")
#----
gap_metric %>%
  inner_join(., vast) %>%
  filter(parent_visn == "06") %>%
  mutate(wash_cty_flag = factor(if_else(sta5a %in% nc_sta5as, 1, 0), ordered = F),
         wash_cty_flag = relevel(wash_cty_flag, ref = "0")) %>%
  lm(gap_metric_capped ~ wash_cty_flag,
      data = .) %>%
  tab_model()
```

* Yes, in the period between October 2022 and March 2024 the 10 sta5as in Washington County had a 0.29 point lower (i.e., -0.29; p<0.001) Gap Metric compared to sta5as in the rest of VISN 6