---
title: "Autocorrelation and Time Series Clustering"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
crh_sites <- ps_matched %>%
  filter(pc_crh_criteria_met_after_sept_21 == T)
#--
analytic_df <- dates %>%
  left_join(., gap_metric) %>%
  left_join(., timely_care) %>%
  left_join(., pen_rate) %>% 
  inner_join(., vast)
```

# Front Matter  

## Description of this report  

* A brief description of the contents

## Decision Points  

* What precipitated this report
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v6.0__
    + PS model v6.0 consists of 
        + Covariates matched on their average values in FY21 Q2
        + Outcomes matched on their average values over October 2020 - March 2021
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact


* Description of analyses



# Gap Metric    

## ACF  

* ACF is the [Autocorrelation Function](https://online.stat.psu.edu/stat510/lesson/2/2.1)


* It is a measure of correlation between $x_t$ and $x_{t-h}$ at different values of $h$, or "lags"
* This corresponds to the __MA__ (Moving Average) part of ARIMA models
* A model can use as many lags as needed; each additional lag adds an error term (multiplied by a coefficient) to the model 
    + A $MA(1)$ model is $x_t=\mu+w_t+\theta_1w_{t-1}$
    + A $MA(2)$ model is $x_t=\mu+w_t+\theta_1w_{t-1}+\theta_2w_{t-2}$
    + And so on 
* This means we can calculate the relative covariance between timepoints (i.e., the ACF) like this:
    + In a $MA(1)$ model it is $\rho_1=\frac{\theta_1}{1+\theta_1^2}$
    + In a $MA(2)$ model they are $\rho_1=\frac{\theta_1+\theta_1\theta_2}{1+\theta_1^2+\theta_2^2}$ and $\rho_2=\frac{\theta_2}{1+\theta_1^2+\theta_2^2}$
* Below is a 1% sample of Sta5as and their $ACF$ for the Gap Metric

```{r}
analytic_df %>%
  select(sta5a) %>%
  distinct %>%
  slice_sample(., prop = 0.01) %>%
  left_join(., analytic_df) %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(mean_val = mean(gap_metric, na.rm = T),
         min_val = min(gap_metric, na.rm = T),
         max_val = max(gap_metric, na.rm = T),
         value_norm = (gap_metric - min_val) / (max_val - min_val)) %>%
  tsibble::as_tsibble(., key = sta5a, index = time) %>%
  feasts::ACF(gap_metric, 
              na.action = na.pass,
              lag_max = 6) %>%
  autoplot()
```

## PACF  

* PACF is the [Partial Autocorrelation Function](https://online.stat.psu.edu/stat510/lesson/2/2.2)

* The PACF is a conditional correlation between $x_t$ and $x_{t-h}$, conditional on the set of observations that come between timepoints $t$ and $t-h$
* The first order partial autocorrelation is defined as the first order autocorrelation
* The second order partial autocorrelation is

$$
\frac{Covariance(x_t, x_{t-2}|x_{t-1})}{\sqrt{(Variance(x_t|x_{t-1})Variance(x_{t-2}|x_{t-1}))}}
$$

```{r}
analytic_df %>%
  select(sta5a) %>%
  distinct %>%
  slice_sample(., prop = 0.01) %>%
  left_join(., analytic_df) %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(mean_val = mean(gap_metric, na.rm = T),
         min_val = min(gap_metric, na.rm = T),
         max_val = max(gap_metric, na.rm = T),
         value_norm = (gap_metric - min_val) / (max_val - min_val)) %>%
  tsibble::as_tsibble(., key = sta5a, index = time) %>%
  feasts::PACF(gap_metric, 
              na.action = na.pass,
              lag_max = 6) %>%
  autoplot()
```

# Time Series Clustering  
* This uses [Dynamic Time Warping (DTW)](https://en.wikipedia.org/wiki/Dynamic_time_warping) to make 3 groups using a "partitional" algorithm
* Most of what I've learned about time series clustering over the past few days comes from [this article](https://journal.r-project.org/archive/2019/RJ-2019-023/RJ-2019-023.pdf)

## Gap Metric  
```{r}
gap_wide <- analytic_df %>%
  select(sta5a, vssc_month, gap_metric) %>%
  group_by(sta5a) %>%
  summarise(has_na = if_else(sum(is.na(gap_metric)) > 0, 1, 0),
            value_gt_20 = if_else(sum(if_else(gap_metric > 20, 1, 0)) > 0, 1, 0)) %>%
  filter(has_na == 0 & value_gt_20 == 0) %>%
  select(sta5a) %>%
  distinct() %>%
  left_join(., analytic_df) %>%
  select(sta5a, vssc_month, gap_metric) %>%
  pivot_wider(names_from = vssc_month,
              values_from = gap_metric)
#
gap_cluster <- gap_wide %>%
  select(-sta5a) %>%
  as.ts() %>%
  dtwclust::tsclust(
    series = .,
    type = "partitional",
    k = 3,
    distance = "dtw_basic",
    seed = 123
  )
#
gap_wide %>%
  bind_cols(., gap_cluster@cluster) %>%
  rename(cluster = `...37`) %>%
  pivot_longer(-c(sta5a, cluster)) %>%
  mutate(vssc_month = ymd(name),
         cluster = factor(cluster,
                          ordered = T,
                          levels = c("3", "1", "2"))) %>%
  ggplot(.,
         aes(x = vssc_month, y = value, group = sta5a)) + 
  geom_line(alpha = 0.2) +
  facet_wrap(~cluster) +
  labs(y = "Gap Metric") +
  theme(legend.position = "none")
#
gap_wide %>%
  bind_cols(., gap_cluster@cluster) %>%
  rename(cluster = `...37`) %>%
  pivot_longer(-c(sta5a, cluster)) %>%
  mutate(vssc_month = ymd(name),
         cluster = factor(cluster,
                          ordered = T,
                          levels = c("3", "1", "2"))) %>%
  ggplot(data = .,
         aes(x = cluster, y = value, fill = cluster, group = cluster)) +
  geom_boxplot() +
  labs(y = "Gap Metric",
       x = "Cluster") +
  theme(legend.position = "none")
```

## Timely Care    
```{r}
tc_wide <- analytic_df %>%
  select(sta5a, vssc_month, tc_pc_success_prop) %>%
  group_by(sta5a) %>%
  summarise(has_na = if_else(sum(is.na(tc_pc_success_prop)) > 0, 1, 0),
            value_gt_20 = if_else(sum(if_else(tc_pc_success_prop > 20, 1, 0)) > 0, 1, 0)) %>%
  filter(has_na == 0 & value_gt_20 == 0) %>%
  select(sta5a) %>%
  distinct() %>%
  left_join(., analytic_df) %>%
  select(sta5a, vssc_month, tc_pc_success_prop) %>%
  pivot_wider(names_from = vssc_month,
              values_from = tc_pc_success_prop)
#
tc_cluster <- tc_wide %>%
  select(-sta5a) %>%
  as.ts() %>%
  dtwclust::tsclust(
    series = .,
    type = "partitional",
    k = 3,
    distance = "dtw_basic",
    seed = 123
  )
#
tc_wide %>%
  bind_cols(., tc_cluster@cluster) %>%
  rename(cluster = `...37`) %>%
  pivot_longer(-c(sta5a, cluster)) %>%
  mutate(vssc_month = ymd(name),
         cluster = factor(cluster,
                          ordered = T,
                          levels = c("1", "2", "3"))) %>%
  ggplot(.,
         aes(x = vssc_month, y = value, group = sta5a)) + 
  geom_line(alpha = 0.2) +
  facet_wrap(~cluster) +
  labs(y = "Timely Care Success") +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.title.x = element_blank())
#
tc_wide %>%
  bind_cols(., tc_cluster@cluster) %>%
  rename(cluster = `...37`) %>%
  pivot_longer(-c(sta5a, cluster)) %>%
  mutate(vssc_month = ymd(name),
         cluster = factor(cluster,
                          ordered = T,
                          levels = c("1", "2", "3"))) %>%
  ggplot(data = .,
         aes(x = cluster, y = value, fill = cluster, group = cluster)) +
  geom_boxplot() +
  labs(y = "Timely Care Success",
       x = "Cluster") +
  scale_y_continuous(labels = percent_format()) +
  theme(legend.position = "none")
```