---
title: "How many cases & controls?"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2018-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
# a vector of sta5as that:
    #1. have at least 451 average unique scrssns in pcmm FY20
    #2. are a CBOC, OOS, VAMC, or HCC
sta5as_to_include <- vast %>%
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F
         & scrssn_count_cat != "< 450"
         & s_abbr %in% c("PCCBOC", "MSCBOC", "VAMC", "OOS", "HCC")) %>%
  select(sta5a, s_abbr, scrssn_count_cat)
#-----
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    (last_mo_mt9_pc_crh == 1 | next_mo_mt9_pc_crh == 1),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit = replace_na(meets_inc_crit, 0)) %>%#replacing NA with 0
  mutate(
    period_meeting_citeria = factor(case_when(
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month < ymd("2020-03-01") #AND month < march 2020
      ~ "Before March 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month >= ymd("2020-03-01")#AND month between March 2020
      & vssc_month <= ymd("2020-09-01") #AND September 2020
      ~ "Between March and September 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month > ymd("2020-09-01") #AND month > Setember 2020
      ~ "After September 2020",#label
      TRUE ~ "Not Enough PC CRH"),#ELSE
      ordered = TRUE,
      levels = c("Before March 2020", 
                 "Between March and September 2020",
                 "After September 2020",
                 "Not Enough PC CRH")))
#--
sta5a_month_inc <- months_meeting_inclusion_criteria %>%
  group_by(sta5a, period_meeting_citeria) %>%
  summarise(count = n()) %>%
  filter(period_meeting_citeria != "Not Enough PC CRH") %>%
  group_by(sta5a) %>%
  summarise(period1_inc = sum(if_else(period_meeting_citeria == "Before March 2020" & count > 1, 1, 0)),
            period2_inc = sum(if_else(period_meeting_citeria == "Between March and September 2020" & count > 1, 1, 0)),
            period3_inc = sum(if_else(period_meeting_citeria == "After September 2020" & count > 1, 1, 0)))
#--
analytic_df <- sta5as_to_include %>%
  left_join(., sta5a_month_inc) %>%
  mutate(across(contains("period"), ~replace_na(.x, 0)),
         not_enough_crh = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0 & sta5a %in% pen_rate$sta5a, 
                                  1, 0),
         potential_control = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0 & not_enough_crh == 0, 1, 0),
         ever_met_criteria = if_else(period1_inc == 1 | period2_inc == 1 | period3_inc == 1, 1, 0))
```

# Front Matter  

## Description of this report  

* This is a closer look at the number of sta5as that we are considering for inclusion as cases in our study, as well as how many sta5as we are then left with that have never used PC CRH

## Decision Points  

* Per our meeting on November 14th I am creating this report to help guide the discussion about propensity score matching
    
## Let's Talk About Sta5as    


* The world of all potential sta5as:
    + There are `r nrow(analytic_df) %>% comma()` sta5as total
    + There are `r sum(analytic_df$ever_met_criteria)` sta5as that ever met our inclusion criteria
    + There are `r sum(analytic_df$period3_inc)` sta5as that met our inclusion criteria after September 2020
    + There are `r sum(analytic_df$not_enough_crh)` sta5as that didn't meet our criteria but had more than zero PC CRH encounters during the whole study period
    + That means that, if we restrict our pool of potential controls to those sta5as that have never had PC CRH, `r nrow(analytic_df) - sum(analytic_df$ever_met_criteria) - sum(analytic_df$not_enough_crh)` sta5as are eligible to be controls
    
## Categorizing Sta5as by CRH Experience  

* We have discussed categorizing sta5as by how much experience they have had with CRH
* The terminology we have been using is early, middle and late adopters
* Out of the `r sum(analytic_df$period3_inc)` sta5as that met our inclusion criteria after September 2020:
    + `r sum(analytic_df$period3_inc == 1 & analytic_df$period1_inc == 1)` also met our inclusion before March 2020
    + `r sum(analytic_df$period3_inc == 1 & analytic_df$period2_inc == 1 & analytic_df$period1_inc == 0)` also met our inclusion criteria between March and September 2020, but __not__ before March 2020
    + `r sum(analytic_df$period1_inc == 0 & analytic_df$period2_inc == 0 & analytic_df$period3_inc == 1)` sta5as only met our inclusion criteria after September 2020
    

