---
title: "PC CRH - Cerner in Post-COVID"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
# penetration rate
pen_rate <- dbGetQuery(oabi_con,
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  mutate(crh_month = ymd(crh_month))
#cerner pc encounters
cerner_pc <- dbGetQuery(oabi_con,
                        "select *
                        from [OABI_MyVAAccess].[crh_eval].A1_pc_enc_scrssn_count") %>%
  mutate(visitMonth = ymd(visitMonth),
         sta5a = Sta6a)
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
# covariates <- dbGetQuery(oabi_con,
#                          "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
#   rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
#   mutate(vssc_month = ymd(vssc_month)) %>%
#   mutate(pct_male = male_count / scrssn_count * 100,
#          pct_white = race_white_count / scrssn_count * 100,
#          pct_rural = urh_rural_count / scrssn_count * 100) %>%
#   select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
#          avg_age_oct1_2022, sta5a, vssc_month, 
#          parent_visn, census_division,
#          nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
#          pcmm_count_fy_qtr,
#          adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
#          shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
sta5as_to_include <- access_metrics %>%
  select(sta5a) %>%
  distinct %>%
  left_join(., crh_flag %>% 
              select(sta5a, not_enough_crh_before_oct_21, had_pccrh_after_sep_21)) %>%
  mutate(crh_group = case_when(
    not_enough_crh_before_oct_21 == 1 ~ "Some PC CRH",
    had_pccrh_after_sep_21 == 1 ~ "PC CRH",
    TRUE ~ "No PC CRH"
  )) %>% 
  left_join(., vast %>% select(sta5a, s_abbr)) %>% 
  mutate(s_abbr2 = case_when(
    s_abbr %in% c("VAMC", "HCC") ~ "VAMC/HCC",
    str_detect(s_abbr, "CBOC") ~ "CBOC",
    s_abbr == "OOS" ~ "OOS",
    TRUE ~ "Uh-Oh!"
  )) %>%
  filter(is.na(s_abbr) == F) %>% 
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F
         & scrssn_count_cat != "< 450")
#=================
crh_sta5as <- sta5as_to_include %>%
  filter(had_pccrh_after_sep_21 == T)
```

# Front Matter  
* This document takes a look at several potential data issues that we may encounter in the post-COVID PC CRH analysis:
    + How many sites have switched to Cerner, and can we obtain encounter data from these sites?
    + Among sites that have switched to Cerner, how many are PC CRH sites in the post-COVID analysis?
    + Are we capturing PC CRH encounters at sites that have switched to Cerner?

```{r}
sta5as_w_cerner <- cerner_pc %>%
  group_by(sta5a) %>%
  filter(!all(is.na(encounter_count_cerner))) %>%
  select(sta5a) %>%
  distinct()
#
cerner_counts <- cerner_pc %>%
  filter(sta5a %in% sta5as_w_cerner$sta5a) %>%
  group_by(sta5a) %>%
  summarise(total_cerner_pc = comma(sum(encounter_count_cerner, na.rm = T)),
            total_cerner_pc_num = sum(encounter_count_cerner, na.rm = T)) %>%
  arrange(desc(total_cerner_pc_num))
#
first_month <- cerner_pc %>%
  filter(is.na(encounter_count_cerner) == F) %>%
  group_by(sta5a) %>%
  summarise(first_cerner_month = min(visitMonth))
```


## Cerner Sites  

* There are `r nrow(sta5as_w_cerner)` sta5as that have at least one month with more than zero Cerner PC encounters: 

```{r}
sta5as_w_cerner %>%
  left_join(., vast %>% select(sta5a, short_name, parent_visn)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  ungroup %>%
  left_join(., cerner_counts) %>%
  left_join(., first_month) %>%
  arrange(desc(total_cerner_pc_num)) %>%
  select(parent_visn, lab_name, total_cerner_pc, first_cerner_month) %>%
  kbl(col.names = c("VISN", "Sta5a", "Total Cerner PC Encounters", "First Month w/ Cerner"),
      align = c("c", "l", "r", "l")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

## Over Time I    

```{r}
top_8 <- cerner_counts[1:8,1]
cerner_pc %>%
  filter(sta5a %in% top_8$sta5a
         & visitMonth > ymd("2020-09-01")) %>%
  left_join(., vast %>% select(sta5a, short_name)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  select(lab_name, visitMonth, encounter_count_cerner, pc_encounter_cdw, pc_encounter_total) %>%
  pivot_longer(-c(lab_name, visitMonth))  %>%
  mutate(name2 = case_when(name == "pc_encounter_cdw" ~ "CDW",
                           name == "encounter_count_cerner" ~ "Cerner",
                           name == "pc_encounter_total" ~ "Total")) %>%
  ggplot(data = .,
         aes(x = visitMonth,
             y = value, 
             group = name2,
             color = name2)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~lab_name) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title = element_blank())
```

## Over Time II    

```{r}
middle_8 <- cerner_counts[9:16,1]
cerner_pc %>%
  filter(sta5a %in% middle_8$sta5a
         & visitMonth > ymd("2020-09-01")) %>%
  left_join(., vast %>% select(sta5a, short_name)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  select(lab_name, visitMonth, encounter_count_cerner, pc_encounter_cdw, pc_encounter_total) %>%
  pivot_longer(-c(lab_name, visitMonth))  %>%
  mutate(name2 = case_when(name == "pc_encounter_cdw" ~ "CDW",
                           name == "encounter_count_cerner" ~ "Cerner",
                           name == "pc_encounter_total" ~ "Total")) %>%
  ggplot(data = .,
         aes(x = visitMonth,
             y = value, 
             group = name2,
             color = name2)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~lab_name) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title = element_blank())
```

## Over Time III    

```{r}
bottom_9 <- cerner_counts[17:25,1]
cerner_pc %>%
  filter(sta5a %in% bottom_9$sta5a
         & visitMonth > ymd("2020-09-01")) %>%
  left_join(., vast %>% select(sta5a, short_name)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  select(lab_name, visitMonth, encounter_count_cerner, pc_encounter_cdw, pc_encounter_total) %>%
  pivot_longer(-c(lab_name, visitMonth))  %>%
  mutate(name2 = case_when(name == "pc_encounter_cdw" ~ "CDW",
                           name == "encounter_count_cerner" ~ "Cerner",
                           name == "pc_encounter_total" ~ "Total")) %>%
  ggplot(data = .,
         aes(x = visitMonth,
             y = value, 
             group = name2,
             color = name2)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~lab_name) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title = element_blank())
```


# CRH Sites With Cerner Only  

```{r}
cerner_sta5a_w_crh <- cerner_counts %>%
  filter(sta5a %in% crh_sta5as$sta5a)
```

* There are `r nrow(cerner_sta5a_w_crh)` __Pre-COVID__ PC CRH sta5as that switched to Cerner
* As we saw above, none of these sites switched before the end of our study period (i.e., February 29th, 2020)


## Top 6  
```{r}
top_6 <- cerner_counts %>% 
  filter(sta5a %in% cerner_sta5a_w_crh$sta5a) %>%
  slice_head(., n = 6)
#--
cerner_pc %>%
  filter(sta5a %in% top_6$sta5a
         & visitMonth > ymd("2020-09-01")) %>%
  left_join(., vast %>% select(sta5a, short_name)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  select(lab_name, visitMonth, encounter_count_cerner, pc_encounter_cdw, pc_encounter_total) %>%
  pivot_longer(-c(lab_name, visitMonth))  %>%
  mutate(name2 = case_when(name == "pc_encounter_cdw" ~ "CDW",
                           name == "encounter_count_cerner" ~ "Cerner",
                           name == "pc_encounter_total" ~ "Total")) %>%
  ggplot(data = .,
         aes(x = visitMonth,
             y = value, 
             group = name2,
             color = name2)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~lab_name) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title = element_blank())
```

## Bottom 11   
```{r}
bottom_11 <- cerner_counts %>% 
  filter(sta5a %in% cerner_sta5a_w_crh$sta5a) %>%
  slice_tail(., n = 11)
#--
cerner_pc %>%
  filter(sta5a %in% bottom_11$sta5a
         & visitMonth > ymd("2020-09-01")) %>%
  left_join(., vast %>% select(sta5a, short_name)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  select(lab_name, visitMonth, encounter_count_cerner, pc_encounter_cdw, pc_encounter_total) %>%
  pivot_longer(-c(lab_name, visitMonth))  %>%
  mutate(name2 = case_when(name == "pc_encounter_cdw" ~ "CDW",
                           name == "encounter_count_cerner" ~ "Cerner",
                           name == "pc_encounter_total" ~ "Total")) %>%
  ggplot(data = .,
         aes(x = visitMonth,
             y = value, 
             group = name2,
             color = name2)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~lab_name) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title = element_blank())
```

# PC CRH Encounters vs. Total PC Encounters    
## Top 6  

```{r}
pen_rate %>%
  left_join(., vast %>% select(sta5a, parent_visn, short_name)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  filter(sta5a %in% top_6$sta5a) %>%
  rename("PC CRH Encounters" = crh_encounter_count,
         "PC Encounters" = pc_encounter_total) %>%
  select(lab_name, crh_month, "PC CRH Encounters", "PC Encounters") %>%
  pivot_longer(-c(lab_name, crh_month)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name, color = name)) +
  geom_line() +
  facet_wrap(~lab_name) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title = element_blank())
```

## Bottom 11    

```{r}
pen_rate %>%
  left_join(., vast %>% select(sta5a, parent_visn, short_name)) %>%
  mutate(lab_name = paste0("(", sta5a, ") ", short_name)) %>%
  filter(sta5a %in% bottom_11$sta5a) %>%
  rename("PC CRH Encounters" = crh_encounter_count,
         "PC Encounters" = pc_encounter_total) %>%
  select(lab_name, crh_month, "PC CRH Encounters", "PC Encounters") %>%
  pivot_longer(-c(lab_name, crh_month)) %>%
  ggplot(data = .,
         aes(x = crh_month, y = value, group = name, color = name)) +
  geom_line() +
  facet_wrap(~lab_name) +
  scale_y_continuous(labels = scales::comma_format()) +
  theme(axis.title = element_blank())
```