---
title: "Comparing Treated to Control and non-Included Users"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(vssc_month = seq.Date(ymd("2020-06-01"),
                                      ymd("2021-07-01"),
                                      "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)

#----------
pc_encounters <- dbGetQuery(oabi_con,
                            "select *
from [OABI_MyVAAccess].[crh_eval].[A1_pc_enc_scrssn_count]
where visitMonth < cast('2021-07-01' as date)
	AND visitMonth > cast('2020-06-01' as date)") %>%
  rename(sta5a = Sta6a) %>%
  mutate(vssc_month = ymd(visitMonth))
#--------
pc_cons <- dbGetQuery(oabi_con,
                      "with CTE as(
select count(*) as total_cons, sum(non_va) as non_va_cons, sta6a
	, DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01') as activityMonth
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where stopCode_group = 'Primary Care'
	AND year(activityDateTime) > 2020
group by Sta6a, DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01'))
select a.sta6a as sta5a, total_cons, non_va_cons
, pcmm_scrssn_count
, activityMonth as vssc_month
from CTE as a
left join [OABI_MyVAAccess].[crh_eval].F2_pcmm_scrssn_count as b
	on a.Sta6a = b.sta5a") %>%
  mutate(non_va_cons_per_10k_pcmm = non_va_cons / pcmm_scrssn_count * 10000,
         vssc_month = ymd(vssc_month))
```

```{r}
sta5as_to_include <- access_metrics %>%
  select(sta5a) %>%
  distinct %>%
  left_join(., crh_flag %>% 
              select(sta5a, not_enough_crh_before_oct_21, had_pccrh_after_sep_21)) %>%
  mutate(crh_group = case_when(
    not_enough_crh_before_oct_21 == 1 ~ "Some PC CRH",
    had_pccrh_after_sep_21 == 1 ~ "PC CRH",
    TRUE ~ "No PC CRH"
  )) %>% 
  left_join(., vast %>% select(sta5a, s_abbr)) %>% 
  mutate(s_abbr2 = case_when(
    s_abbr %in% c("VAMC", "HCC") ~ "VAMC/HCC",
    str_detect(s_abbr, "CBOC") ~ "CBOC",
    s_abbr == "OOS" ~ "OOS",
    TRUE ~ "Uh-Oh!"
  )) %>%
  filter(is.na(s_abbr) == F) %>% 
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F
         & scrssn_count_cat != "< 450")
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
  inner_join(., sta5as_to_include) %>%#restrict to our table from above
  # filter(vssc_month > ymd("2019-09-01")) %>%#restrict to our timeframe
  inner_join(., dates) %>%
  left_join(., pc_encounters %>% select(sta5a, pc_encounter_total, vssc_month)) %>%
  left_join(., pc_cons %>% select(vssc_month, sta5a, non_va_cons_per_10k_pcmm)) %>%
  left_join(., covariates) %>%
  select(crh_group
         , vssc_month
         , sta5a
         , pc_encounter_total
         , scrssn_count_avg_fy20
         , s_abbr2
         , team_pcp_ap_fte_total
         , obs_exp_panel_ratio
         , non_va_cons_per_10k_pcmm
         , nosos_risk_score
         , adi_natRnk_avg
         , pct_rural
         , est_pc_pt_wt
         , new_pc_pt_wt
         , third_next_avail)
```

# Front Matter  

## Description of this report  

* This is a comparison of three groups: sta5as that met our inclusion criteria after September 2021, sta5as that had zero PC CRH encounters before October 2021, and sta5as that more than zero PC CRH encounters before October 2021 but not enough to meet our inclusion criteria

## Decision Points  

* Per our discussion on 6/15 we are going to consider not using propensity score matching for the post-COVID analysis
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_group) %>% distinct() %>% summarise(tot = sum(crh_group == "PC CRH"))` of these met our criteria for PC CRH 
      + `r analytic_df %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
```{r}
ttest_fxn <- function(covar, covar_name){
  accuracy_val <- if(covar_name %in% c("NOSOS", "Obs:Exp"))
  {0.01}
  else if(str_detect(covar_name, "Encounters|ScrSSN")){1}
  else{0.1}
  #--
  analytic_df %>%
  select(crh_group, {{covar}}, vssc_month, sta5a) %>%
  pivot_wider(names_from = crh_group, values_from = {{covar}}) %>%
  summarise(mean_crh = mean(`PC CRH`, na.rm = T),
            sd_crh = sd(`PC CRH`, na.rm = T),
            mean_ctrl = mean(`No PC CRH`, na.rm = T),
            sd_ctrl = sd(`No PC CRH`, na.rm = T),
            mean_some = mean(`Some PC CRH`, na.rm = T),
            sd_some = sd(`Some PC CRH`, na.rm = T),
            crh_val = paste0(comma(mean_crh, accuracy = accuracy_val),
                             " (",
                             comma(sd_crh, accuracy = accuracy_val),
                             ")"),
            ctrl_val = paste0(comma(mean_ctrl, accuracy = accuracy_val),
                              " (",
                              comma(sd_ctrl, accuracy = accuracy_val),
                              ")"),
            some_val = paste0(comma(mean_some, accuracy = accuracy_val),
                              " (",
                              comma(sd_some, accuracy = accuracy_val),
                              ")"),
            t_test_p1 = if_else(t.test(`No PC CRH`, `PC CRH`)$p.value < 0.001,
                               "< 0.001",
                               comma(t.test(`No PC CRH`, `PC CRH`)$p.value,
                                     accuracy = 0.001)),
            t_test_p2 = if_else(t.test(`No PC CRH`, `Some PC CRH`)$p.value < 0.001,
                                "< 0.001",
                                comma(t.test(`No PC CRH`, `Some PC CRH`)$p.value,
                                      accuracy = 0.001))) %>%
  mutate(covar_name = {{covar_name}}) %>%
  select(covar_name, ctrl_val, crh_val, t_test_p1, some_val, t_test_p2)
}
```

```{r}

s_abbr_tab <- analytic_df %>%
  filter(vssc_month == ymd("2021-1-01")) %>%
  group_by(crh_group, s_abbr2) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = crh_group, values_from = count) %>%
  mutate(t_test_p1 = "NA",
         t_test_p2 = "NA") %>%
  rename(crh_val = `PC CRH`,
         ctrl_val = `No PC CRH`,
         some_val = `Some PC CRH`,
         covar_name = s_abbr2) %>%
  janitor::adorn_totals() %>%
  mutate(crh_val = as.character(crh_val),
         ctrl_val = as.character(ctrl_val),
         some_val = as.character(some_val))
#--
encounter_tot <- analytic_df %>%
  group_by(crh_group) %>%
  summarise(pc_enc_tot = comma(sum(pc_encounter_total, na.rm = T), accuracy = 1)) %>%
  mutate(covar_name = "Total PC Encounters") %>%
  pivot_wider(names_from = crh_group, values_from = pc_enc_tot) %>%
  mutate(t_test_p2 = "NA",
         t_test_p2 = "NA") %>%
  rename(crh_val = `PC CRH`,
         ctrl_val = `No PC CRH`,
         some_val = `Some PC CRH`)
#--
encounter_tot %>%
  bind_rows(ttest_fxn(pc_encounter_total, "PC Encounters per month")) %>%
  bind_rows(ttest_fxn(scrssn_count_avg_fy20, "Unique ScrSSNs")) %>%
  bind_rows(., s_abbr_tab) %>%
  bind_rows(ttest_fxn(team_pcp_ap_fte_total, "PCP/AP FTE")) %>%
  bind_rows(ttest_fxn(obs_exp_panel_ratio, "Obs:Exp")) %>%
  bind_rows(ttest_fxn(non_va_cons_per_10k_pcmm, 
                      "Non-VA Consults per 10k Uniques")) %>%
  bind_rows(ttest_fxn(nosos_risk_score, "NOSOS")) %>%
  bind_rows(ttest_fxn(adi_natRnk_avg, "ADI")) %>%
  bind_rows(ttest_fxn(pct_rural, "% Rural")) %>%
  bind_rows(ttest_fxn(est_pc_pt_wt, "EPWT")) %>%
  bind_rows(ttest_fxn(new_pc_pt_wt, "NPWT")) %>%
  bind_rows(ttest_fxn(third_next_avail, "TNA")) %>%
  select(covar_name, ctrl_val, crh_val, t_test_p1, some_val, t_test_p2) %>%
  kbl(col.names = c("Variable", "No PC CRH (SD)", "PC CRH (SD)", "p for difference with No PC CRH",
                    "Some PC CRH (SD)", "p for difference with No PC CRH")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```