---
title: "CRH Stations - When and How Much?"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         period_of_first_inclusion = case_when(
           first_mo_w_mt9_pc_crh < ymd("2020-03-01") ~ "Before March 2020",
           first_mo_w_mt9_pc_crh >= ymd("2020-03-01") 
           & first_mo_w_mt9_pc_crh < ymd("2020-10-01") ~ "Between March 2020 and September 2020",
           first_mo_w_mt9_pc_crh >= ymd("2020-10-01") ~ "After September 2020"
         ))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
sta5as_to_include <- vast %>%
  select(sta5a) %>%
  left_join(., scrssn_count %>% select(sta5a, scrssn_count_cat)) %>%
  filter(scrssn_count_cat != "< 450")
#--
sta5as_w_any_crh <- pen_rate %>%
  filter(is.na(crh_encounter_count) == F) %>%
  select(sta5a) %>%
  distinct %>%
  left_join(., crh_flag %>% select(sta5a, period_of_first_inclusion)) %>%
  inner_join(., sta5as_to_include %>% select(sta5a)) %>%
  mutate(period_of_first_inclusion = factor(if_else(is.na(period_of_first_inclusion) == T,
                                             "Not enough PC CRH",
                                             period_of_first_inclusion),
                                            ordered = TRUE,
                                            levels = c("Before March 2020",
                                                       "Between March 2020 and September 2020",
                                                       "After September 2020",
                                                       "Not enough PC CRH")))
#=================
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(this_mo_mt9_pcCRH = if_else(crh_encounter_count > 9, 1, 0),
         next_mo_mt9_pcCRH = if_else(lead(crh_encounter_count, 1) > 9, 1, 0),
         last_mo_mt9_pcCRH = if_else(lag(crh_encounter_count, 1) > 9, 1, 0),
         meets_inclusion_criteria = if_else((this_mo_mt9_pcCRH == 1 & next_mo_mt9_pcCRH == 1) | 
                                              (this_mo_mt9_pcCRH == 1 & last_mo_mt9_pcCRH == 1), 1, 0)) %>%
  filter(meets_inclusion_criteria == 1) %>%
  complete(vssc_month = seq(ymd("2020-02-01"), ymd("2022-12-01"), by = "month")) %>%
  mutate(rowNum = row_number()) %>%
  select(sta5a, vssc_month, crh_encounter_count, meets_inclusion_criteria, rowNum)
```

# Front Matter  

## Description of this report  

* This is starting out as a description of PC CRH engagement

## Decision Points  

* Per our discussion on October 4th I am going to make some descriptions of CRH users and when they became users
    



# PC CRH Encounters in the 12 months after first meeting our inclusion criteria  

* Below is a table describing these 3 periods of meeting inclusion criteria in terms of the number of total encounters and the proportion of the following 12 months that sta5as received CRH support for PC
* This does mean that I had to exclude `r crh_flag %>% filter(first_mo_w_mt9_pc_crh > "2021-12-01" & crh_10_flag == 1) %>% nrow()` sta5as that met our inclusion criteria after December 2021  

```{r}
n_sta5a <- sta5as_w_any_crh %>%
  group_by(period_of_first_inclusion) %>%
  tally()
#--
months_meeting_inclusion_criteria %>%
  inner_join(., sta5as_w_any_crh) %>%
  filter(rowNum <= 12
         & vssc_month <= ymd("2021-12-01")) %>%
  summarise(total_crh_encounter_count = sum(crh_encounter_count, na.rm = T),
           sum_mos = sum(meets_inclusion_criteria, na.rm = T),
           prop_mos = sum_mos / 12,
           avg_pc_crh_encounter = total_crh_encounter_count / sum_mos,
           avg_pc_crh_encounter12 = total_crh_encounter_count / 12
           ) %>%
  left_join(., sta5as_w_any_crh) %>%
  ungroup %>%
  group_by(period_of_first_inclusion) %>%
  summarise(total_crh_encounters = sum(total_crh_encounter_count, na.rm = T),
            avg_prop_mos = mean(prop_mos),
            avg_mos = mean(sum_mos),
            avg_pc_crh_encounter = mean(avg_pc_crh_encounter),
            avg_pc_crh_encounter12 = mean(avg_pc_crh_encounter12)) %>%
  mutate(across(c(4:6), ~comma(., accuracy = 0.1)),
         total_crh_encounters = comma(total_crh_encounters, accuracy = 1),
         avg_prop_mos = percent(avg_prop_mos, accuracy = 0.1)) %>%
  right_join(., n_sta5a %>%
               filter(str_detect(period_of_first_inclusion, "enough") == F)) %>%
  select(c(1, 7, 2, 3, 4, 5, 6)) %>%
  kbl(col.names = c("Period first meeting inclusion criteria",
                    "Number of sta5a", 
                    "Total PC CRH encounters in following 12 months",
                    "Average % of following 12 months",
                    "Average number of following 12 months",
                    "Average number of PC CRH encounters per month",
                    "Average number of PC CRH encounters out of 12 months"
                    ),
      align = c("l", rep("r", 6))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


# How many sta5as meet inclusion criteria during each period?  

```{r}
met_criteria_before_march_20 <- months_meeting_inclusion_criteria %>%
  filter(vssc_month < ymd("2020-03-01")
         & meets_inclusion_criteria == 1) %>%
  select(sta5a) %>%
  distinct
#--
met_criteria_between_march_20_sept_20 <- months_meeting_inclusion_criteria %>%
  filter(vssc_month >= ymd("2020-03-01")
         & vssc_month <= ymd("2020-09-01")
         & meets_inclusion_criteria == 1) %>%
  select(sta5a) %>%
  distinct
#--
met_criteria_after_sept_20 <- months_meeting_inclusion_criteria %>%
  filter(vssc_month > ymd("2020-09-01")
         & meets_inclusion_criteria == 1) %>%
  select(sta5a) %>%
  distinct
```

* Out of the `r months_meeting_inclusion_criteria %>% select(sta5a) %>% n_distinct` sta5as that ever met our inclusion criteria:
    + `r met_criteria_before_march_20 %>% nrow` met these criteria before March 2020
    + `r met_criteria_between_march_20_sept_20 %>% nrow` met the criteria between March and September 2020
    + `r met_criteria_after_sept_20 %>% nrow` met the criteria after September 2020


# How many sta5as meet inclusion criteria some periods and not others  

```{r}
met_1_not_2_3 <- met_criteria_before_march_20 %>%
  filter(sta5a %ni% met_criteria_between_march_20_sept_20$sta5a
         & sta5a %ni% met_criteria_after_sept_20$sta5a)
#
met_2_not_1_3 <- met_criteria_between_march_20_sept_20 %>%
  filter(sta5a %ni% met_criteria_before_march_20$sta5a
         & sta5a %ni% met_criteria_after_sept_20$sta5a)
#
met_3_not_1_2 <- met_criteria_after_sept_20 %>%
  filter(sta5a %ni% met_criteria_before_march_20$sta5a
         & sta5a %ni% met_criteria_between_march_20_sept_20$sta5a)
#
met_1_2_not_3 <- met_criteria_before_march_20 %>%
  bind_rows(., met_criteria_between_march_20_sept_20) %>%
  distinct() %>%
  filter(sta5a %ni% met_criteria_after_sept_20$sta5a)
#
met_1_3_not_2 <- met_criteria_before_march_20 %>%
  bind_rows(., met_criteria_after_sept_20) %>%
  distinct %>%
  filter(sta5a %ni% met_criteria_between_march_20_sept_20$sta5a)
#
met_2_3_not_1 <- met_criteria_between_march_20_sept_20 %>%
  bind_rows(., met_criteria_after_sept_20) %>%
  distinct %>%
  filter(sta5a %ni% met_criteria_before_march_20)
#
met_1_2_3 <- met_criteria_before_march_20 %>%
  bind_rows(., met_criteria_between_march_20_sept_20) %>%
  bind_rows(., met_criteria_after_sept_20) %>%
  distinct %>%
  filter(sta5a %in% met_criteria_before_march_20$sta5a
         & sta5a %in% met_criteria_between_march_20_sept_20$sta5a
         & sta5a %in% met_criteria_after_sept_20$sta5a)
```

* There are a total of `r months_meeting_inclusion_criteria %>% select(sta5a, meets_inclusion_criteria) %>% distinct() %>% filter(is.na(meets_inclusion_criteria) == F) %>% nrow()` stations that ever met our inclusion criteria

* `r nrow(met_1_not_2_3)` sta5as met inclusion criteria in period 1, but not periods 2 and 3
* `r nrow(met_2_not_1_3)` sta5as met inclusion criteria in period 2, but not periods 1 and 3
* `r nrow(met_3_not_1_2)` sta5as met inclusion criteria in period 3, but not periods 1 and 2
* `r nrow(met_1_2_not_3)` sta5as met inclusion criteria in periods 1 and 2, but not period 3
* `r nrow(met_1_3_not_2)` sta5as met inclusion criteria in periods 1 and 3, but not period 2
* `r nrow(met_2_3_not_1)` sta5as met inclusion criteria in periods 2 and 3, but not period 1
* `r nrow(met_1_2_3)` sta5as met inclusion criteria in periods 1, 2, and 3