---
title: "PC CRH Inclusion in 3 Periods"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             plot.title = element_text(size = 24),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2018-09-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```



# Front Matter  

## Description of this report  

* This report is a description of how many stations meet our inclusion criteria during our 3 periods of consideration: Before March 2020, Between March and September 2020, and After September 2020

# How The Flag Gets Made  

* Below is the code chunk where I create a flag for each sta5a-month determining whether it meets our inclusion criteria

```{r class.source = 'fold-show'}
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    (last_mo_mt9_pc_crh == 1 | next_mo_mt9_pc_crh == 1),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit = replace_na(meets_inc_crit, 0))#replacing NA with 0
```

* The code chunk below is where I combine that criteria with our 3 periods to make a flag designating each sta5a-month-inclusion by the period in which it occurred 

```{r class.source = 'fold-show'}
months_meeting_inclusion_criteria <- months_meeting_inclusion_criteria %>%
  mutate(
    period_meeting_citeria = factor(case_when(
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month < ymd("2020-03-01") #AND month < march 2020
      ~ "Before March 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month >= ymd("2020-03-01")#AND month between March 2020
      & vssc_month <= ymd("2020-09-01") #AND September 2020
      ~ "Between March and September 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month > ymd("2020-09-01") #AND month > Setember 2020
      ~ "After September 2020",#label
      TRUE ~ "Not Enough PC CRH"),#ELSE
      ordered = TRUE,
      levels = c("Before March 2020", 
                 "Between March and September 2020",
                 "After September 2020",
                 "Not Enough PC CRH")))
```

* This final code chunk contains the last bit of logic 

```{r class.source = 'fold-show'}
sta5a_period_table <- months_meeting_inclusion_criteria %>%
  group_by(sta5a, period_meeting_citeria) %>%#group by station and period
  summarise(sta5a_period_count = n()) %>%#count of each
  mutate(
    include_me = if_else(sta5a_period_count > 1, 1, 0)) %>%#if a sta5a-period had > 1 counts in a period then 1 else 0
  group_by(period_meeting_citeria) %>%# group by period
  summarise(count = sum(include_me))#sum(include_me) by period gives us the final table
```


```{r}
sta5a_period_table %>%
  kbl(col.names = c("", "Sta5as")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```


# Visulizing Months Meeting Inclusion  


## Before March 2020  
```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#
months_meeting_inclusion_criteria %>%
  filter(vssc_month < ymd("2020-03-01")
         & vssc_month > ymd("2018-09-01")
         & meets_inc_crit == 1) %>%
  ggplot(data = .,
         aes(x = vssc_month)) +
  geom_histogram(bins = 17,
                 color = "black",
                 fill = cbbPalette[2]) +
  labs(x = "Month", 
       y = "Sta5as Meeting Inclusion Criteria",
       title = "Before March 2020")
```

## Between March and September 2020  
```{r}
months_meeting_inclusion_criteria %>%
  filter(vssc_month >= ymd("2020-03-01")
         & vssc_month <= ymd("2020-09-01")
         & meets_inc_crit == 1) %>%
  ggplot(data = .,
         aes(x = vssc_month)) +
  geom_histogram(bins = 7,
                 color = "black",
                 fill = cbbPalette[3]) +
  labs(x = "Month", 
       y = "Sta5as Meeting Inclusion Criteria",
       title = "Between March and September 2020")
```

## After September 2020    
```{r}
months_meeting_inclusion_criteria %>%
  filter(vssc_month > ymd("2020-09-01")
         & meets_inc_crit == 1) %>%
  ggplot(data = .,
         aes(x = vssc_month)) +
  geom_histogram(bins = 36,
                 color = "black",
                 fill = cbbPalette[4]) +
  labs(x = "Month", 
       y = "Sta5as Meeting Inclusion Criteria",
       title = "After September 2020")
```

## All 35 Months  
```{r}
months_meeting_inclusion_criteria %>%
  filter(meets_inc_crit == 1) %>%
  ggplot(data = .,
         aes(x = vssc_month)) +
  geom_histogram(bins = 61,
                 color = "black",
                 fill = cbbPalette[8]) +
  labs(x = "Month", 
       y = "Sta5as Meeting Inclusion Criteria",
       title = "All 35 Months")
```

## Do CRH Encounters Over Time Look Like This Too?    

```{r}
pen_rate %>% 
  filter(vssc_month > ymd("2018-09-01")) %>%
  group_by(vssc_month) %>%
  summarise(tot_crh = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = tot_crh)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(x = "Month",
       y = "Total PC CRH")
```

### By Type   
```{r}
all_encounters_by_type <- dbGetQuery(oabi_con,
                                     "with CTE as (
	select *,
		vizMonth = DATEFROMPARTS(year(visitdate), month(visitdate), '01')
	from [PACT_CC].[CRH].C_crh_utilization_final
)
select vizMonth, care_type, count(*) as encounter_count
from CTE
group by vizMonth, care_type") %>%
  mutate(vizMonth = as.Date(vizMonth)) %>%
  filter(vizMonth > ymd("2018-09-01"))
#----
ggplot(data = all_encounters_by_type,
       aes(x = vizMonth, y = encounter_count, color = care_type, group = care_type)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters") +
  theme(legend.position = "right")
```

### PC As a Table  

```{r}
pen_rate %>% 
  filter(vssc_month > ymd("2021-12-01")) %>%
  group_by(vssc_month) %>%
  summarise(total_crh = sum(crh_encounter_count, na.rm = T)) %>%
  arrange(vssc_month) %>%
  mutate(total_crh = comma(total_crh)) %>%
  kbl(col.names = c("Month", "Total CRH"),
      align = c("c", "r")) %>%
  kable_classic("striped",
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE)
```

### VISNs 20 & 23  

```{r}
all_encounters_type_visn <- dbGetQuery(oabi_con,
                                       "with CTE as (
	select *,
		vizMonth = DATEFROMPARTS(year(visitdate), month(visitdate), '01')
	from [PACT_CC].[CRH].C_crh_utilization_final
)
select vizMonth, care_type, count(*) as encounter_count, b.parent_visn
from CTE as a
left join [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as b
on a.spoke_sta5a_combined_cdw = b.sta5a
group by vizMonth, care_type, parent_visn") %>%
  mutate(vizMonth = as.Date(vizMonth)) %>%
  filter(vizMonth > ymd("2018-09-01"))
```

```{r}
all_encounters_type_visn %>%
  filter(parent_visn == "20") %>%
  ggplot(data = .,
         aes(x = vizMonth, y = encounter_count, group = care_type, color = care_type)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters",
       title = "VISN 20") +
  theme(legend.position = "right")
```

```{r}
all_encounters_type_visn %>%
  filter(parent_visn == "23") %>%
  ggplot(data = .,
         aes(x = vizMonth, y = encounter_count, group = care_type, color = care_type)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters",
       title = "VISN 23") +
  theme(legend.position = "right")
```


```{r}
library(plotly)
all_encounters_type_visn %>%
  filter(care_type == "Primary Care") %>%
  plot_ly(data = .,
               x = ~vizMonth,
               y = ~encounter_count,
               color = ~parent_visn) %>%
  add_lines() %>%
  layout(showlegend = FALSE,
         xaxis = list(
           title = "Month"
         ),
         yaxis = list(
           title = "PC CRH Encounters"
         ))
```