---
title: "Gap Metric vs. Timely Care"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
```



# Front Matter  

## Description of this report  

* This is an initial look at the correlation between the Gap Metric and Timely Care

## Decision Points  

* In order to move the post-COVID analysis forward we are going to look at the correlations between two new-to-this-analysis covariates: the Gap Metric and Timely Care
* A brief refresher on what the Timely Care metric _is_:
    + A Timely Care $Request$ is when a patient requests an appointment to primary care as either a walk-in or a first next available
    + The denominator of the metric is the number of Timely Care $Requests$ made to primary care during a particular sta5a-month
    + And the numerator is the number of those that were seen __in primary care__ (i.e., $Successes$)
    + Putting these together we get the Timely Care metric:
    
$$
\text{Timely Care Success Rate} = \frac{\sum{Successes}}{\sum{Requests}}
$$

* The Gap Metric is the sta5a-month-specific ratio of observed to expected panel size, with the CRH contribution removed:

$$
\text{Gap Metric}=\frac{Observed Panel Size}{Expected Panel Size}
$$
    
 
# Overall  

```{r}
gap_vs_tc <- gap_metric %>% 
  select(sta5a, vssc_month, gap_metric) %>%
  left_join(., timely_care %>% select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  left_join(., vast) %>%
  left_join(scrssn_count) %>%
  mutate(urh2 = if_else(urh_vast == "U", "Urban", "Rural")) %>%
  filter(gap_metric < 3
         & tc_pc_success_prop != 0
         & is.na(urh2) == F
         & is.na(scrssn_count_cat) == F)
```


```{r}
ggplot(data = gap_vs_tc,
       aes(y = gap_metric,
           x = tc_pc_success_prop)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm",
              se = F) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = comma_format()) +
  labs(x = "Timely Care PC Success Rate",
       y = "Gap Metric") +
  ggpubr::stat_cor(method = "pearson")
```

# By Site Type  

```{r}
ggplot(data = gap_vs_tc,
       aes(y = gap_metric,
           x = tc_pc_success_prop)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm",
              se = F) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = comma_format()) +
  labs(x = "Timely Care PC Success Rate",
       y = "Gap Metric") +
  ggpubr::stat_cor(method = "pearson") +
  facet_wrap(~s_abbr)
```

# By URH (VAST)    

```{r}
ggplot(data = gap_vs_tc,
         aes(y = gap_metric,
             x = tc_pc_success_prop)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm",
              se = F) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = comma_format()) +
  labs(x = "Timely Care PC Success Rate",
       y = "Gap Metric") +
  ggpubr::stat_cor(method = "pearson") +
  facet_wrap(~urh2)
```

# By PCMM Uniques in FY20  

```{r}
ggplot(data = gap_vs_tc,
         aes(y = gap_metric,
             x = tc_pc_success_prop)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "lm",
              se = F) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = comma_format()) +
  labs(x = "Timely Care PC Success Rate",
       y = "Gap Metric") +
  ggpubr::stat_cor(method = "pearson") +
  facet_wrap(~scrssn_count_cat)
```