---
title: "A Closer Look at The Gap Metric"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
analytic_df <- dates %>%
  cross_join(., vast %>% select(sta5a)) %>%
  left_join(., gap_metric) %>%
  left_join(., pen_rate) %>%
  inner_join(., vast) %>%
  left_join(., scrssn_count %>% select(sta5a, scrssn_count_cat)) %>%
  filter(is.na(scrssn_count_cat) == F
         & scrssn_count_cat != "< 450")
```


# Front Matter  

## Description of this report  

* A brief description of the contents

## Decision Points  

* What precipitated this report
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct() %>% comma()` sta5as
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
  

# Gap Metric Description  

* The Gap Metric is the sta5a-month-specific ratio of observed to expected panel size, with the CRH contribution removed:

$$
\text{Gap Metric}=\frac{(\text{MD FTE}\times 1200)+(\text{APP FTE}\times 900)}{\text{Total clinic assigned panel size}}=\frac{\text{Maximum clinic patient capacity}}{\text{Total clinic assigned panel size}}
$$

```{r}
analytic_df %>%
  filter(gap_metric <= 2.5) %>%
  ggplot(data = .,
         aes(y = gap_metric)) +
  geom_boxplot() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(caption = "*Removed 31 obs. w/ gap > 2.5")
```

# Gap Metric Category by PC CRH Encounter Category  
## With Missing  
```{r}
analytic_df %>%
  select(sta5a, vssc_month, gap_metric, crh_encounter_count) %>%
  mutate(gap_cat = factor(case_when(
    gap_metric < 1 ~ "< 1",
    gap_metric >= 1 & gap_metric < 1.2 ~ "1.0-1.99",
    gap_metric >= 1.2 ~ "1.2+",
    is.na(gap_metric) == T ~ "NA"
  ),
  ordered = T,
  levels = c("< 1", "1.0-1.99", "1.2+", "NA")),
  crh_cat = factor(case_when(
    is.na(crh_encounter_count) == T ~ "0/NA",
    crh_encounter_count < 10 ~ "< 10",
    crh_encounter_count >= 10 ~ "10+"
  ),
  ordered = TRUE,
  levels = c("< 10", "10+", "0/NA"))) %>%
  tabyl(gap_cat, crh_cat) %>%
  adorn_totals("both") %>%
  janitor::adorn_percentages("all") %>%
  adorn_pct_formatting() %>%
  adorn_ns("front") %>%
  kbl(col.names = c("Gap", "< 10", "10+", "0/NA", "Total"),
      align = c("l", rep("r", 4))) %>%
  kable_classic("striped") %>%
  add_header_above(c("", "PC CRH Encounters" = 3, "")) %>%
  row_spec(0, bold = T)
```

## Without Missing  

```{r}
analytic_df %>%
  select(sta5a, vssc_month, gap_metric, crh_encounter_count) %>%
  filter(is.na(gap_metric) == F
         & is.na(crh_encounter_count) == F) %>%
  mutate(gap_cat = factor(case_when(
    gap_metric < 1 ~ "< 1",
    gap_metric >= 1 & gap_metric < 1.2 ~ "1.0-1.99",
    gap_metric >= 1.2 ~ "1.2+"
  ),
  ordered = T,
  levels = c("< 1", "1.0-1.99", "1.2+")),
  crh_cat = factor(case_when(
    crh_encounter_count < 10 ~ "< 10",
    crh_encounter_count >= 10 ~ "10+"
  ),
  ordered = TRUE,
  levels = c("< 10", "10+"))) %>%
  tabyl(gap_cat, crh_cat) %>%
  adorn_totals("both") %>%
  janitor::adorn_percentages("all") %>%
  adorn_pct_formatting() %>%
  adorn_ns("front") %>%
  kbl(col.names = c("Gap", "< 10", "10+", "Total"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped") %>%
  add_header_above(c("", "PC CRH Encounters" = 3)) %>%
  row_spec(0, bold = T)
```

```{r}
analytic_df %>%
  select(sta5a, vssc_month, gap_metric, crh_encounter_count) %>%
  filter(is.na(gap_metric) == F
         & is.na(crh_encounter_count) == F) %>%
  mutate(gap_cat = factor(case_when(
    gap_metric < 1 ~ "< 1",
    gap_metric >= 1 & gap_metric < 1.2 ~ "1.0-1.99",
    gap_metric >= 1.2 ~ "1.2+"
  ),
  ordered = T,
  levels = c("< 1", "1.0-1.99", "1.2+"))) %>%
  group_by(gap_cat) %>%
  summarise(obs = n(),
            total_crh_enc = sum(crh_encounter_count)) %>%
  mutate(enc_per_obs = comma(total_crh_enc / obs, accuracy = 0.1)) %>%
  adorn_totals() %>%
  janitor::adorn_percentages("col") %>%
  adorn_pct_formatting() %>%
  adorn_ns("front") %>%
  kbl(col.names = c("Gap Metric", "Observations", "Total PC RH Encounters", "Encounters per Observation"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

## Does Having more than 10 PC CRH Encounters in a Month Predict Gap < 1?  

```{r}
analytic_df %>%
  mutate(crh_enc_gt9 = if_else(crh_encounter_count > 9, 1, 0),
         gap_lt_1 = if_else(gap_metric < 1, 1, 0)) %>%
  glm(gap_lt_1 ~ crh_enc_gt9,
      data = .,
      family = "binomial") %>%
  tab_model()
```
