---
title: "Post-COVID PC CRH Analysis: Outcomes X Exposure"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0),
         urh_vast2 = if_else(urh_vast == "U", "Urban", "Rural")) %>%
  filter(drop_flag == 0
         & s_abbr %in% c("PCCBOC", "MSCBOC", "VAMC", "HCC", "OOS")) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month),
         tna_new_source = as.numeric(tna_new_source)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+"))) %>%
  filter(sta5a %in% vast$sta5a)
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
crh_sta5as <- crh_flag %>%
  mutate(crh_criteria_met = case_when(
    first_mo_w_mt9_pc_crh > ymd("2020-03-01") & crh_10_flag == 1 ~ "Met PC CRH Criteria",
    crh_flag == 1 & crh_10_flag == 0 ~ "Not Enough PC CRH"
  ))
#
vast_sta5as <- vast %>%
  select(sta5a) %>%
  distinct
#
analytic_df <- dates %>%
  cross_join(., vast_sta5as) %>%
  left_join(., vast) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month,
                     est_pc_pt_wt_pid,
                     new_pc_pt_wt_create,
                     tna_new_source,
                     new_0_20_days_create)) %>%
  left_join(., timely_care) %>%
  left_join(., crh_sta5as) %>%
  left_join(., scrssn_count) %>%
  mutate(crh_criteria_met = if_else(is.na(crh_criteria_met) == T, 
                                    "Zero PC CRH",
                                    crh_criteria_met)) %>%
  filter(scrssn_count_cat != "< 450")
```

# Front Matter  

## Description of this report  

* This is an exploration of a categorical measure of PC CRH engagement and it's relationship with our 5 outcomes: NPWT, EPWT (PID), TNA, Timely Care, and  % of New Patients seen within 0-20 days

## Decision Points  

* Per our meeting on September 27th we are moving forward with our pre-analysis exploration of the post-COVID PC CRH data
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_criteria_met) %>% distinct() %>% summarise(tot = sum(crh_criteria_met == "Met PC CRH Criteria"))` of these met our criteria for PC CRH after March 2020 
      + `r analytic_df %>% select(sta5a, crh_criteria_met) %>% distinct() %>% summarise(tot = sum(crh_criteria_met == "Not Enough PC CRH"))` had more than zero PC CRH encounters but not enough to meet our inclusion criteria 
      + `r analytic_df %>% select(sta5a, crh_criteria_met) %>% distinct() %>% summarise(tot = sum(crh_criteria_met == "Zero PC CRH"))` had zero PC CRH encounters
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    

# Correlation Matrix  

```{r}
foo <- analytic_df %>%
  select(new_pc_pt_wt_create, est_pc_pt_wt_pid, tna_new_source, tc_pc_success_prop, new_0_20_days_create) %>%
  drop_na()
#--
cor(foo) %>% as.data.frame %>%
  mutate(across(where(is.numeric), ~comma(., accuracy = 0.001))) %>%
  kbl(col.names = names(foo),
      align = rep("r", 4),
      full_width = F) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

```{r functions}
over_time_fxn <- function(outcome, outcome_char){
  plot_df <- analytic_df %>%
    select(sta5a, vssc_month, crh_criteria_met, urh_vast2, {{outcome}})
  #--
  y_label <- if(str_detect({{outcome_char}}, "new")){"New Patient Wait Time (Days)"}
    else if(str_detect({{outcome_char}}, "est_pc")){"Established Patient Wait Time (Days)"}
    else if(str_detect({{outcome_char}}, "tna")){"Third Next Available (days)"}
    else if(str_detect({{outcome_char}}, "tc_pc")){"Timely Care Success Rate"}
    else{"New Patients Seen in 0-20 Days"}
  #--
  y_max <- ceiling(quantile(plot_df[ncol(plot_df)], 0.99, na.rm = T))
  #--
  if(str_detect(outcome_char, "tc_pc|0_20")){
  ggplot(data = plot_df,
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_line(alpha = 0.2) +
    labs(y = y_label) +
    scale_y_continuous(limits = c(0, 1),
                       labels = percent_format(accuracy = 1)) +
    theme(axis.title.x = element_blank())
  }
  else{
    ggplot(data = plot_df,
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_line(alpha = 0.2) +
    labs(y = y_label,
         caption = "*Removed observations > 99th %ile") +
    scale_y_continuous(limits = c(0, y_max),
                       labels = comma_format(accuracy = 1)) +
    theme(axis.title.x = element_blank())
  }
}
#over_time_fxn(est_pc_pt_wt_pid, "est_pc_pt_wt_create") + facet_wrap(~urh_vast2)
#---------
box_plot_fxn <- function(outcome, outcome_char){
  plot_df <- analytic_df %>%
    select(sta5a, vssc_month, crh_criteria_met, urh_vast2, {{outcome}})
  #--
  y_label <- if(str_detect({{outcome_char}}, "new")){"New Patient Wait Time (Days)"}
  else if(str_detect({{outcome_char}}, "est_pc")){"Established Patient Wait Time (Days)"}
  else if(str_detect({{outcome_char}}, "tna")){"Third Next Available (days)"}
  else if(str_detect({{outcome_char}}, "tc_pc")){"Timely Care Success Rate"}
  else{"New Patients Seen in 0-20 Days"}
  #--
  y_max <- ceiling(quantile(plot_df[ncol(plot_df)], 0.99, na.rm = T))
  #--
  if(str_detect({{outcome_char}}, "tc_pc|0_20")){
    ggplot(data = plot_df,
           aes(x = crh_criteria_met, y = {{outcome}})) +
      geom_boxplot() +
      scale_y_continuous(limits = c(0, 1),
                         labels = percent_format(accuracy = 1)) + 
      labs(y = y_label) +
      theme(axis.title.x = element_blank())
  }
  else{
    ggplot(data = plot_df,
           aes(x = crh_criteria_met, y = {{outcome}})) +
      geom_boxplot() +
      scale_y_continuous(limits = c(0, y_max)) + 
      labs(y = y_label,
           caption = "*Removed observations > 99th %ile") +
      theme(axis.title.x = element_blank())
  }
}
#-----------
table_fxn <- function(outcome, outcome_char){
  table_df <- analytic_df %>%
    select(sta5a, crh_criteria_met, vssc_month, {{outcome}})
  #--
  if(str_detect({{outcome_char}}, "tc_pc|0_20")){
    table_df %>%
      group_by(crh_criteria_met) %>%
      summarise(avg_val = mean({{outcome}}, na.rm = T),
                sd_val = sd({{outcome}}, na.rm = T),
                n_val = sum(!is.na({{outcome}})),
                n_sta5a = n_distinct(sta5a),
                qtl_25 = quantile({{outcome}}, 0.25, na.rm = T),
                qtl_75 = quantile({{outcome}}, 0.75, na.rm = T),
                min_val = min({{outcome}}, na.rm = T),
                max_val = max({{outcome}}, na.rm = T)) %>%
      mutate(across(c(2, 3, 6, 7, 8, 9), ~percent(., accuracy = 0.1)),
             n_val = comma(n_val, accuracy = 1),
             n_sta5a = comma(n_sta5a, accuracy = 1),
             avg_sd_disp = paste0(avg_val, " (", sd_val, ")"),
             qtl_disp = paste0("(", qtl_25, ", ", qtl_75, ")"),
             min_max = paste0("[", min_val, ", ", max_val, "]")) %>%
      select(crh_criteria_met, n_val, n_sta5a, avg_sd_disp, qtl_disp, min_max) %>%
      kbl(col.names = c("", "Observations", "Sta5as", "Average (SD)", "(25th %ile, 75th %ile)", "[min, max]"),
          align = c("l", rep("r", 5))) %>%
      kable_classic("striped") %>%
      row_spec(0, bold = T)
  }
  else {
    table_df %>%
      group_by(crh_criteria_met) %>%
      summarise(avg_val = mean({{outcome}}, na.rm = T),
                sd_val = sd({{outcome}}, na.rm = T),
                n_val = sum(!is.na({{outcome}})),
                n_sta5a = n_distinct(sta5a),
                qtl_25 = quantile({{outcome}}, 0.25, na.rm = T),
                qtl_75 = quantile({{outcome}}, 0.75, na.rm = T),
                min_val = min({{outcome}}, na.rm = T),
                max_val = max({{outcome}}, na.rm = T)) %>%
      mutate(across(c(2, 3, 6, 7, 8, 9), ~comma(., accuracy = 0.1)),
             n_val = comma(n_val, accuracy = 1),
             n_sta5a = comma(n_sta5a, accuracy = 1),
             avg_sd_disp = paste0(avg_val, " (", sd_val, ")"),
             qtl_disp = paste0("(", qtl_25, ", ", qtl_75, ")"),
             min_max = paste0("[", min_val, ", ", max_val, "]")) %>%
      select(crh_criteria_met, n_val, n_sta5a, avg_sd_disp, qtl_disp, min_max) %>%
      kbl(col.names = c("", "Observations", "Sta5as", "Average (SD)", "(25th %ile, 75th %ile)", "[min, max]"),
          align = c("l", rep("r", 5))) %>%
      kable_classic("striped") %>%
      row_spec(0, bold = T)
  }
}
```


# New Patient Wait Time From Create Date    

```{r}
table_fxn(new_pc_pt_wt_create, "new_pc_pt_wt_create")
#
over_time_fxn(new_pc_pt_wt_create, "new_pc_pt_wt_create")
#
box_plot_fxn(new_pc_pt_wt_create, "new_pc_pt_wt_create")
```

# Established Patient Wait Time From PID  

```{r}
table_fxn(est_pc_pt_wt_pid, "est_pc_pt_wt_pid")
#
over_time_fxn(est_pc_pt_wt_pid, "est_pc_pt_wt_pid")
#
box_plot_fxn(est_pc_pt_wt_pid, "est_pc_pt_wt_pid")
```

# Third Next Available  

```{r}
table_fxn(tna_new_source, "tna_new_source")
#
over_time_fxn(tna_new_source, "tna_new_source")
#
box_plot_fxn(tna_new_source, "tna_new_source")
```

# Timely Care Success Rate  

```{r}
table_fxn(tc_pc_success_prop, "tc_pc_success_prop")
#
over_time_fxn(tc_pc_success_prop, "tc_pc_success_prop")
#
box_plot_fxn(tc_pc_success_prop, "tc_pc_success_prop")
```

# New Patients Seen in 0-20 Days  

```{r}
table_fxn(new_0_20_days_create, "new_0_20_days_create")
#
over_time_fxn(new_0_20_days_create, "new_0_20_days_create")
#
box_plot_fxn(new_0_20_days_create, "new_0_20_days_create")
```
