---
title: "Post-COVID CRH Analysis"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2021-10-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- ps_matched %>%
  filter(pc_crh_criteria_met_after_march_20 == 1) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, 
                            "PC CRH", "No PC CRH"))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month > ymd("2021-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
#analytic_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df$treat <- relevel(analytic_df$treat, ref = 'Control')
```

# Front Matter  

## Description of this report  

* This is an iteration of the _Post-COVID_ analysis

## Decision Points  

* We have a new source for new and established patient wait times
    + They no longer exist in the PC cube on vssc
    + It is still unclear if third next available still exists somewhere else
* This new source doesn't have established patient wait time (__from create date__), which is the version we have been using
    + Has some funky qualities anyway, including a bimodal distribution
* This means we have switched to established patient wait time (__from patient indicated date__)
* New patient wait time comes in both flavors; we are moving forward with __from create date__, which is the same as we have been using
* The propensity score has also been re-run with these new data

    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH after March, 2020 
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v6.0__
    + PS model v6.0 consists of 
        + Covariates matched on their average values in FY21 Q2
        + Outcomes matched on their average values over October 2020 - March 2021
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact

* Description of analyses  
    + This analysis is a Time Series with covariates
    + We will use a mixed-effects model __with REML__ 
    + We will allow random intercepts for sta5a
    + On the LHS of the model we have New Patient Wait Time, Established Patient Wait Time, and Third Next Available 
    + In addition to an interaction between _treat_ and _time_, all models have the following covariates:
        + Observed:Expected PC Panel Size 
        + Proportion male 
        + Proportion rural 

$$Y_{jt}=\beta_0 +\beta_1time_t+ \beta_2Z_{jt}+\beta_4treat_j+\beta_5time_ttreat_j+v_j+u_{jt}$$

```{r}
plot_fxn <- function(outcome, outcome_c){
  ylab <- if(outcome_c == "est_pc_pt_wt_pid"){
    "Established Patient Wait Time (days)"
  }
  else if(outcome_c == "new_pc_pt_wt_create"){
    "New Patient Wait Time (days)"
  }
  else{
    "Third Next Available (days)"
  }
  #
  ymax <- if(outcome_c == "est_pc_pt_wt_pid"){
    30
  }
  else if(outcome_c == "new_pc_pt_wt_create"){
    75
  }
  else{
    60
  }

  ggplot(data = analytic_df,
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_line(linewidth = 0.75, alpha = 0.15) +
    geom_smooth(linewidth = 1.25, data = analytic_df,
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    ggsci::scale_color_aaas() +
    theme(axis.title.x = element_blank()) +
    labs(y = ylab) +
    scale_y_continuous(limits = c(0, ymax))
}
```


# Established Patient Wait Time  
```{r}
plot_fxn(est_pc_pt_wt_pid, "est_pc_pt_wt_pid")
```

```{r}
est_pc_pt_lm <- lmer(est_pc_pt_wt_pid ~ time * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
```



#### Model Estimates    
```{r}
tab_model(est_pc_pt_lm,
          dv.labels = c("Established Patient Wait Time (PID)"))
```

# New Patient Wait Time  
```{r}
plot_fxn(new_pc_pt_wt_create, "new_pc_pt_wt_create")
```

```{r}
new_pc_pt_lm <- lmer(new_pc_pt_wt_create ~ time * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
```



#### Model Estimates    
```{r}
tab_model(new_pc_pt_lm,
          dv.labels = c("New Patient Wait Time (create)"))
```

# Third Next Available  
```{r}
plot_fxn(third_next_avail, "third_next_avail")
```

```{r}
tna_lm <- lmer(third_next_avail ~ time * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
```



#### Model Estimates    
```{r}
tab_model(tna_lm,
          dv.labels = c("Third Next Available"))
```


# All Together  

```{r}
tab_model(new_pc_pt_lm, est_pc_pt_lm, tna_lm,
          dv.labels = c("New Patient Wait Time (create)",
                        "Established Patient Wait Time (PID)",
                        "Third Next Available"),
          show.ci = FALSE,
          show.se = TRUE)
```