---
title: "% of New Patients seen in 0-20 days: Logistic Edition"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2021-10-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PACT_CC].[econ].PatientPCP
#                             	where fy = 2018
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- ps_matched %>%
  filter(pc_crh_criteria_met_after_march_20 == 1) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  inner_join(., vast %>% select(sta5a, s_abbr, urh_vast)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, 
                            "PC CRH", "No PC CRH"))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month > ymd("2021-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
  mutate(new_0_20_days_create_pct = new_0_20_days_create * 100,
         treat = factor(case_when(
           sta5a %in% crh_sta5as ~ "PC CRH",
           TRUE ~ "Control")),
         treat2 = if_else(sta5a %in% crh_sta5as, 1, 0),
         new_0_20_pct_gt_80 = factor(if_else(new_0_20_days_create_pct > 80,
                                      "> 80%", "<= 80%"),
                                     ordered = T),
         new_0_20_pct_gt_80_2 = if_else(new_0_20_days_create_pct > 80,
                                        1, 0)) %>%
  left_join(., covariates)
#
analytic_df$treat <- relevel(analytic_df$treat, ref = 'Control')
```

# Front Matter  

## Description of this report  

* I am exploring using __% of new patients seen in 0-20 days (from create date)__, a new outcome we are looking at

## Decision Points  

* After meeting on April 12th we decided to investigate using this outcome as a binary $<80%\text{vs.}\ge80$ 
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH 
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v6.0__
    + PS model v6.0 consists of 
        + Covariates matched on their average values in FY21 Q2
        + Outcomes matched on their average values over October 2020 - March 2021
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact
        
* Description of analyses  
    + This analysis is a Time Series with covariates
    + We will use a generalized linear mixed-effects model  
    + We will use a __binomial__ distribution (i.e., we'll estimate odds ratios)
    + We will allow random intercepts for sta5a
    + On the LHS of the model we have a binary $<80%\text{vs.}\ge80$    
    + In addition to an interaction between _treat_ and _time_, all models have the following covariates:
        + Observed:Expected PC Panel Size 
        + Proportion male 
        + Proportion rural 

# Overall  

```{r}
#new_0_20_days_create
analytic_df %>%
  ggplot(data = .,
         aes(x = new_0_20_days_create,
             fill = "foo")) +
  geom_histogram(bins = 50,
                 color = "black") +
  ggsci::scale_fill_aaas() +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.position = "none") +
  labs(x = "New Patients Seen in 0-20 Days (create)",
       y = "Observations")
```

```{r}
ggplot(data = analytic_df,
       aes(x = "foo",
           y = new_0_20_days_create,
           fill = "bar")) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none") +
  labs(y = "New Patients Seen in 0-20 Days (create)")
```

## By Urban/Rural  
```{r}
analytic_df %>%
  mutate(urh2 = if_else(urh_vast == "U",
                        "Urban", "Rural")) %>%
  select(urh2, new_0_20_days_create) %>%
  pivot_longer(-urh2) %>%
  ggplot(data = .,
         aes(x = value,
             fill = urh2)) +
  geom_histogram(bins = 50,
                 color = "black",
                 position = "identity") +
  ggsci::scale_fill_aaas() +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.position = "none") +
  labs(x = "New Patients Seen in 0-20 Days (create)",
       y = "Observations") +
  facet_wrap(~urh2)
```

## By Site Type    
```{r}
analytic_df %>%
  select(s_abbr, new_0_20_days_create) %>%
  pivot_longer(-s_abbr) %>%
  ggplot(data = .,
         aes(x = value,
             fill = s_abbr)) +
  geom_histogram(bins = 50,
                 color = "black",
                 position = "identity") +
  ggsci::scale_fill_aaas() +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.position = "none") +
  labs(x = "New Patients Seen in 0-20 Days (create)",
       y = "Observations") +
  facet_wrap(~s_abbr)
```

## By New Patient Wait Time  

```{r}
analytic_df %>%
  ggplot(data = .,
         aes(x = new_0_20_days_create,
             y = new_pc_pt_wt_create)) +
  geom_point() +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_y_continuous(limits = c(0, 200)) +
  labs(x = "New Patients Seen in 0-20 Days (create)",
       y = "New Patient Wait Time (create)") +
  geom_smooth(se = FALSE,
              method = "lm")
#
tab_model(
  lm(new_pc_pt_wt_create ~ new_0_20_days_create_pct, data = analytic_df),
  dv.labels = c("New Pt WT (Create)")
)
```

# As an outcome  

```{r}
ggplot(data = analytic_df,
       aes(x = vssc_month,
           y = new_0_20_days_create,
           group = sta5a)) +
  geom_line(alpha = 0.2) +
  geom_smooth(method = "lm",
              se = FALSE,
              aes(group = treat,
                  color = treat),
              linewidth = 1.2) +
  ggsci::scale_color_aaas() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(y = "New Patients Seen in 0-20 Days") +
  theme(axis.title.x = element_blank())
```

```{r warning = TRUE}
new_0_20_lm <- glmer(new_0_20_pct_gt_80 ~ time * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                    family = binomial(link = "logit"))
```

## Attempted plot #2  
```{r}
ggeffects::ggpredict(new_0_20_lm, c("time [1:15]", "treat")) %>%
  tibble %>%
  left_join(., dates, by = c("x" = "time")) %>%
  ggplot(data = .,
         aes(y = predicted, x = vssc_month, group = group, color = group)) + 
  geom_ribbon(aes(ymax = conf.high, ymin = conf.low, x = vssc_month, group = group),
              alpha = 0.3,
              inherit.aes = FALSE) +
  geom_line(linewidth = 1.25) +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  labs(y = "Predicted probability of \">80%\"") +
  ggsci::scale_color_aaas() +
  theme(axis.title.x = element_blank())
```




#### Model Estimates    
```{r warning = TRUE}
summary(new_0_20_lm)
#
tab_model(new_0_20_lm,
          dv.labels = c("New Patients Seen in 0-20 Days (create)"))
```