---
title: "Post-COVID Distribution of Outcomes: Looking for cutoffs"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month > ymd("2020-02-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- ps_matched %>%
  filter(pc_crh_criteria_met_after_march_20 == 1) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, 
                            "PC CRH", "No PC CRH")) %>%#making the crh_flag
  left_join(., scrssn_count)
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month > ymd("2020-06-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
  filter(scrssn_count_cat != "< 450")#3: must have scrssn_count_avg_fy20 >= 450
```

# Front Matter  

## Description of this report  

* This is a look at the distribution of our outcomes, and to look for natural cutpoints use in stratified analyses

## Decision Points  

* We are moving forward with the Post-COVID analysis and presentation
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH 
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v6.0__
    + PS model v6.0 consists of 
        + Covariates matched on their average values in FY21 Q2
        + Outcomes matched on their average values over October 2020 - March 2021
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact


# Established Patient Wait-Time  

```{r}
est_pt_df <- analytic_df %>%
  select(sta5a, vssc_month, est_pc_pt_wt)
```

```{r}
est_pt_df %>%
  ggplot(data = .,
         aes(x = est_pc_pt_wt)) +
  geom_histogram(bins = 100,
                 fill = "red",
                 color = "black") +
  labs(x = "Established Pt WT (days)",
       y = "Observations") +
  theme(legend.position = "none")
```

```{r}
caterpillar_fxn <- function(outcome, outcome_c){
  plot_df <- 
    if({{outcome_c}} == "est_pc_pt_wt"){
      est_pt_df
    }
    else if({{outcome_c}} == "new_pc_pt_wt"){
      new_pt_df
    }
    else {tna_pt_df}
#------      
  plot_df %>%
    group_by(sta5a) %>%
    summarise(mean_val = mean({{outcome}}, na.rm = T),
              sd_val = sd({{outcome}}, na.rm = T)) %>%
    ggplot(data = .,
           aes(x = reorder(sta5a, mean_val), y = mean_val,
               ymin = mean_val - sd_val,
               ymax = mean_val + sd_val)) +
    geom_errorbar() +
    geom_point() +
    labs(y = "Average Value (+/- SD)",
         x = "Sta5a") +
    theme(axis.text.x = element_blank())
}
#
caterpillar_fxn(est_pc_pt_wt, "est_pc_pt_wt")
```


## By clinic type  
```{r}
est_pt_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  ggplot(data = .,
         aes(x = est_pc_pt_wt,
             fill = s_abbr)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Established Pt WT (days)",
       y = "Observations") +
  facet_wrap(~s_abbr) +
  theme(legend.position = "none")
```

## By Urban/Rural    
```{r}
est_pt_df %>%
  left_join(., vast %>% select(sta5a, urh_vast)) %>%
  mutate(urh2 = if_else(urh_vast == "U",
                        "Urban", "Rural")) %>%
  ggplot(data = .,
         aes(x = est_pc_pt_wt,
             fill = urh2)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Established Pt WT (days)",
       y = "Observations") +
  facet_wrap(~urh2) +
  theme(legend.position = "none")
```

## By clinic size  
```{r}
est_pt_df %>%
  left_join(., scrssn_count) %>%
  ggplot(data = .,
         aes(x = est_pc_pt_wt,
             fill = scrssn_count_cat)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Established Pt WT (days)",
       y = "Observations") +
  facet_wrap(~scrssn_count_cat) +
  theme(legend.position = "none")
```

# New Patient Wait-Time  

```{r}
new_pt_df <- analytic_df %>%
  select(sta5a, vssc_month, new_pc_pt_wt)
```

```{r}
new_pt_df %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt)) +
  geom_histogram(bins = 100,
                 fill = "Blue",
                 color = "black") +
  labs(x = "New Pt WT (days)",
       y = "Observations")
```

```{r}
caterpillar_fxn(new_pc_pt_wt, "new_pc_pt_wt")
```

## By clinic type  
```{r}
new_pt_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt,
             fill = s_abbr)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "New Pt WT (days)",
       y = "Observations") +
  facet_wrap(~s_abbr) +
  theme(legend.position = "none")
```

## By Urban/Rural    
```{r}
new_pt_df %>%
  left_join(., vast %>% select(sta5a, urh_vast)) %>%
  mutate(urh2 = if_else(urh_vast == "U",
                        "Urban", "Rural")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt,
             fill = urh2)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "New Pt WT (days)",
       y = "Observations") +
  facet_wrap(~urh2) +
  theme(legend.position = "none")
```

## By clinic size  
```{r}
new_pt_df %>%
  left_join(., scrssn_count) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt,
             fill = scrssn_count_cat)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "New Pt WT (days)",
       y = "Observations") +
  facet_wrap(~scrssn_count_cat) +
  theme(legend.position = "none")
```

# Third Next Available    

```{r}
tna_pt_df <- analytic_df %>%
  select(sta5a, vssc_month, third_next_avail)
```

```{r}
tna_pt_df %>%
  ggplot(data = .,
         aes(x = third_next_avail)) +
  geom_histogram(bins = 100,
                 fill = "seagreen",
                 color = "black") +
  labs(x = "Third Next Available (days)",
       y = "Observations") +
  theme(legend.position = "none")
```

```{r}
caterpillar_fxn(third_next_avail, "third_next_avail")
```

## By clinic type  
```{r}
tna_pt_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  ggplot(data = .,
         aes(x = third_next_avail,
             fill = s_abbr)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Third Next Available (days)",
       y = "Observations") +
  facet_wrap(~s_abbr) +
  theme(legend.position = "none")
```

## By Urban/Rural    
```{r}
tna_pt_df %>%
  left_join(., vast %>% select(sta5a, urh_vast)) %>%
  mutate(urh2 = if_else(urh_vast == "U",
                        "Urban", "Rural")) %>%
  ggplot(data = .,
         aes(x = third_next_avail,
             fill = urh2)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Third Next Available (days)",
       y = "Observations") +
  facet_wrap(~urh2) +
  theme(legend.position = "none")
```

## By clinic size  
```{r}
tna_pt_df %>%
  left_join(., scrssn_count) %>%
  ggplot(data = .,
         aes(x = third_next_avail,
             fill = scrssn_count_cat)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Third Next Available (days)",
       y = "Observations") +
  facet_wrap(~scrssn_count_cat) +
  theme(legend.position = "none")
```


# Established Patient Wait Time Part II  

## Sta5a average > 40 days?  
```{r}
avg_est_gt_40 <- est_pt_df %>%
  group_by(sta5a) %>%
  summarise(avg = mean(est_pc_pt_wt, na.rm = T)) %>%
  ungroup %>%
  mutate(avg_gt_40 = if_else(avg > 40, "> 40 days", "<= 40 days")) %>%
  distinct
#
est_pt_df %>%
  left_join(., avg_est_gt_40) %>%
  ggplot(data = .,
         aes(x = est_pc_pt_wt,
             fill = avg_gt_40)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Established Pt WT (days)",
       y = "Observations") +
  facet_wrap(~avg_gt_40) +
  theme(legend.position = "none")
```

### Who are the `r sum(avg_est_gt_40$avg_gt_40 == "> 40 days")` sta5as that mave an average Established Patient Wait Time > 40 days?  

```{r}
gt_40_sta5as <- avg_est_gt_40 %>%
  filter(avg_gt_40 == "> 40 days") %>%
  select(sta5a) %>%
  distinct %>%
  left_join(crh_flag)
```

* `r sum(gt_40_sta5as$had_pcCRH_after_march20, na.rm = T)` (`r (sum(gt_40_sta5as$had_pcCRH_after_march20, na.rm = T) / nrow(avg_est_gt_40)) %>% percent(accuracy = 0.1)`) of them are CRH sites

* `r (sum(gt_40_sta5as$s_abbr %in% c("PCCBOC", "MSCBOC")) / nrow(avg_est_gt_40)) %>% percent(accuracy = 0.1)` of them are CBOCs


## By CRH Status, Where the Average > 40 Days    
```{r}
est_pt_df %>%
  left_join(., avg_est_gt_40) %>%
  filter(avg_gt_40 == "> 40 days") %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as,
                              "PC CRH", "Control")) %>%
  ggplot(data = .,
         aes(x = est_pc_pt_wt,
             fill = crh_flag)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Established Pt WT (days)",
       y = "Observations") +
  facet_wrap(~crh_flag) +
  theme(legend.position = "none")
```

## By CRH Status, Where the Average < 41 Days    
```{r}
est_pt_df %>%
  left_join(., avg_est_gt_40) %>%
  filter(avg_gt_40 != "> 40 days") %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as,
                              "PC CRH", "Control")) %>%
  ggplot(data = .,
         aes(x = est_pc_pt_wt,
             fill = crh_flag)) +
  geom_histogram(bins = 100,
                 color = "black") +
  labs(x = "Established Pt WT (days)",
       y = "Observations") +
  facet_wrap(~crh_flag) +
  theme(legend.position = "none")
```