---
title: "PC CRH in Post-COVID"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month),
         tna_new_source = as.numeric(tna_new_source)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month > ymd("2020-02-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, crh_encounter_count, pc_encounter_total,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- ps_matched %>%
  filter(pc_crh_criteria_met_after_march_20 == 1) %>%
  select(sta5a) %>%
  pull
#3: must have scrssn_count_avg_fy18 >= 450
#=================
#making the analytic dataset
analytic_df <- covariates %>%# start with access metrics
      filter(sta5a %in% crh_sta5as) %>%#restrict to our table from above
      filter(vssc_month > ymd("2021-09-01")
             & vssc_month < ymd("2023-01-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
      left_join(., scrssn_count) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  left_join(., access_metrics)
```

```{r}
unique_hubs <- dbGetQuery(oabi_con,
                          "select distinct Hub_Location
from [PACT_CC].[CRH].CRH_sites_FY20_working
where SiteType = 'PC'
UNION
select distinct Hub_Location
from [PACT_CC].[CRH].CRH_sites_FY21_working
where SiteType = 'PC'
UNION
select distinct Hub_Location
from [PACT_CC].[CRH].CRH_sites_FY22_working
where SiteType = 'PC'")
#
unique_states <- vast %>%
  filter(sta5a %in% crh_sta5as) %>%
  select(state) %>%
  distinct()
```

```{r}
non_crh_sta5as <- ps_matched %>%
  filter(pc_crh_criteria_met_after_march_20 == 0) %>%
  select(sta5a) %>%
  pull
#--
pc_encounters <- dbGetQuery(oabi_con,
                                    "select sum(pc_encounter_total) as pc_encounter_total, sta6a
from [OABI_MyVAAccess].[crh_eval].A1_pc_enc_scrssn_count
where visitMonth > cast('2019-09-01' as date)
group by Sta6a")
#--
crh_sta5as_pc_encounters <- pc_encounters %>%
  filter(sta6a %in% crh_sta5as) %>%
  summarise(total = sum(pc_encounter_total, na.rm = T))
#--
noCrh_sta5as_pc_encounters <- pc_encounters %>%
  filter(sta6a %in% non_crh_sta5as) %>%
  summarise(total = sum(pc_encounter_total, na.rm = T))
```

# Front Matter  

## Description of this report   

* This is a deeper dive into characteristics of sta5as that met our inclusion criteria and patients with PC CRH visits
 
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + All of these met our criteria for inclusion __after__ March 2020 
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + There are `r nrow(unique_hubs)` unique hubs
    + The PC CRH sites serve `r nrow(unique_states)` states
    + Each row is a sta5a-month

* Among the `r length(crh_sta5as)` that were PC CRH sites there were a total of `r crh_sta5as_pc_encounters$total %>% comma()` PC encounters 

* Among the `r length(non_crh_sta5as)` that were Control sites there were a total of `r noCrh_sta5as_pc_encounters$total %>% comma()` PC encounters 
    
# PC CRH as a Rate per 1,000 PC Encounters  

```{r}
analytic_df %>%
  group_by(sta5a) %>%
  summarise(pcCRH_rate_mean = mean(pc_crh_per_1k_total_pc, na.rm = T),
            pcCRH_rate_sd = sd(pc_crh_per_1k_total_pc, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = reorder(sta5a, pcCRH_rate_mean))) +
  geom_point(aes(y = pcCRH_rate_mean)) +
  geom_errorbar(aes(ymin = pcCRH_rate_mean - pcCRH_rate_sd, 
                    ymax = pcCRH_rate_mean + pcCRH_rate_sd),
                alpha = 0.75) +
  theme(axis.text.x = element_blank()) +
  geom_hline(yintercept = 0) +
  labs(y = "Average PC CRH per 1,000 (+/- SD)",
       x = "Sta5a") +
  scale_y_continuous(labels = comma_format(accuracy = 1))
```

### Just the top 20  
```{r}
top_20 <- analytic_df %>%
  group_by(sta5a) %>%
  summarise(pcCRH_rate_mean = mean(pc_crh_per_1k_total_pc, na.rm = T),
            pcCRH_rate_sd = sd(pc_crh_per_1k_total_pc, na.rm = T)) %>%
  slice_max(n = 20, order_by = pcCRH_rate_mean) %>%
  select(sta5a) %>%
  pull
#
analytic_df %>%
  filter(sta5a %in% top_20) %>%
  left_join(., vast %>% select(sta5a, short_name, city, state)) %>%
  mutate(short_name2 = paste0("(", sta5a, ") ", short_name, " (", state, ")")) %>%
  group_by(short_name2) %>%
  summarise(pcCRH_rate_mean = mean(pc_crh_per_1k_total_pc, na.rm = T),
            pcCRH_rate_sd = sd(pc_crh_per_1k_total_pc, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = reorder(short_name2, pcCRH_rate_mean))) +
  geom_point(aes(y = pcCRH_rate_mean)) +
  geom_errorbar(aes(ymin = pcCRH_rate_mean - pcCRH_rate_sd, 
                    ymax = pcCRH_rate_mean + pcCRH_rate_sd),
                alpha = 0.75) +
  theme(axis.text.x = element_text(angle = 270,
                                   hjust = 0, vjust = 0.3)) +
  geom_hline(yintercept = 0) +
  labs(y = "Average PC CRH per 1,000 (+/- SD)",
       x = "Sta5a") +
  scale_y_continuous(labels = comma_format(accuracy = 1))
```

### Just the top 10 VAMC  
```{r}
top_10_vamc <- analytic_df %>%
  filter(s_abbr == "VAMC") %>%
  group_by(sta5a) %>%
  summarise(pcCRH_rate_mean = mean(pc_crh_per_1k_total_pc, na.rm = T),
            pcCRH_rate_sd = sd(pc_crh_per_1k_total_pc, na.rm = T)) %>%
  slice_max(n = 10, order_by = pcCRH_rate_mean) %>%
  select(sta5a) %>%
  pull
#
analytic_df %>%
  filter(sta5a %in% top_10_vamc) %>%
  left_join(., vast %>% select(sta5a, short_name, city, state)) %>%
  mutate(short_name2 = paste0("(", sta5a, ") ", short_name, " (", state, ")")) %>%
  group_by(short_name2) %>%
  summarise(pcCRH_rate_mean = mean(pc_crh_per_1k_total_pc, na.rm = T),
            pcCRH_rate_sd = sd(pc_crh_per_1k_total_pc, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = reorder(short_name2, pcCRH_rate_mean))) +
  geom_point(aes(y = pcCRH_rate_mean)) +
  geom_errorbar(aes(ymin = pcCRH_rate_mean - pcCRH_rate_sd, 
                    ymax = pcCRH_rate_mean + pcCRH_rate_sd),
                alpha = 0.75) +
  theme(axis.text.x = element_text(angle = 270,
                                   hjust = 0, vjust = 0.3)) +
  geom_hline(yintercept = 0) +
  labs(y = "Average PC CRH per 1,000 (+/- SD)",
       x = "Sta5a") +
  scale_y_continuous(labels = comma_format(accuracy = 1))
```

## By Site Type  

```{r}
analytic_df %>%
  group_by(sta5a) %>%
  summarise(pcCRH_rate_mean = mean(pc_crh_per_1k_total_pc, na.rm = T),
            pcCRH_rate_sd = sd(pc_crh_per_1k_total_pc, na.rm = T)) %>%
  left_join(., vast) %>%
  ggplot(data = .,
         aes(x = reorder(sta5a, pcCRH_rate_mean))) +
  geom_point(aes(y = pcCRH_rate_mean)) +
  geom_errorbar(aes(ymin = pcCRH_rate_mean - pcCRH_rate_sd, 
                    ymax = pcCRH_rate_mean + pcCRH_rate_sd),
                alpha = 0.75) +
  theme(axis.text.x = element_blank()) +
  geom_hline(yintercept = 0) +
  labs(y = "Average PC CRH per 1,000 (+/- SD)",
       x = "Sta5a") +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  facet_wrap(~s_abbr)
```


## Assigning Color to Rurality  
```{r}
analytic_df %>%
  group_by(sta5a) %>%
  summarise(pcCRH_rate_mean = mean(pc_crh_per_1k_total_pc, na.rm = T),
            pcCRH_rate_sd = sd(pc_crh_per_1k_total_pc, na.rm = T)) %>%
  left_join(., vast) %>%
  mutate(urh_vast2 = factor(if_else(urh_vast == "U", "Urban", "Rural"),
                            ordered = TRUE,
                            levels = c("Urban", "Rural"))) %>%
  ggplot(data = .,
         aes(x = reorder(sta5a, pcCRH_rate_mean))) +
  geom_point(aes(y = pcCRH_rate_mean, color = urh_vast2),
             size = 1.5) +
  geom_errorbar(aes(ymin = pcCRH_rate_mean - pcCRH_rate_sd, 
                    ymax = pcCRH_rate_mean + pcCRH_rate_sd),
                alpha = 0.75) +
  theme(axis.text.x = element_blank()) +
  geom_hline(yintercept = 0) +
  labs(y = "Average PC CRH per 1,000 PC Encounters (+/- SD)",
       x = "Sta5a") +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  ggsci::scale_color_aaas()
```



# Some tables  
## CRH Encounters  
```{r}
analytic_df %>%
  summarise(`CRH Encounters` = sum(crh_encounter_count, na.rm = T),
            `PC Encounters` = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(`CRH per 1,000 PC` =`CRH Encounters` / `PC Encounters` * 1000,
         foo = "foo") %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  mutate(value = if_else(str_detect(name, "1,000"), 
                         comma(value, accuracy = 0.1),
                         comma(value, accuracy = 1))) %>%
  kbl(col.names = c("", ""),
      align = c("l", "r")) %>%
  kable_classic("striped", 
                full_width = F)
```

## CRH Encounters Since October, 2019    
```{r}

analytic_df2 <- covariates %>%# start with access metrics
      filter(sta5a %in% crh_sta5as) %>%#restrict to our table from above
      filter(vssc_month > ymd("2019-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
      left_join(., scrssn_count) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
analytic_df2 %>%
  summarise(`CRH Encounters` = sum(crh_encounter_count, na.rm = T),
            `PC Encounters` = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(`CRH per 1,000 PC` =`CRH Encounters` / `PC Encounters` * 1000,
         foo = "foo") %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  mutate(value = if_else(str_detect(name, "1,000"), 
                         comma(value, accuracy = 0.1),
                         comma(value, accuracy = 1))) %>%
  kbl(col.names = c("", ""),
      align = c("l", "r")) %>%
  kable_classic("striped", 
                full_width = F)
```

## By Site Type  
```{r}
analytic_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  group_by(s_abbr) %>%
  summarise(`CRH Encounters` = sum(crh_encounter_count, na.rm = T),
            `PC Encounters` = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(`CRH per 1,000 PC` =`CRH Encounters` / `PC Encounters` * 1000) %>%
  mutate_at(2:3, comma_format()) %>%
  mutate_at(4, comma_format(accuracy = 0.1)) %>%
  kbl(col.names = c("Type", "PC CRH Encounters", "PC Encounters", "CRH per 1,000 PC"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped", 
                full_width = F) %>%
  row_spec(0, bold = TRUE)
```

## By Urban/Rural    
```{r}
analytic_df %>%
  left_join(., vast %>% select(sta5a, urh_vast)) %>%
  mutate(urh_vast2 = if_else(urh_vast == "U", "Urban", "Rural")) %>%
  group_by(urh_vast2) %>%
  summarise(`CRH Encounters` = sum(crh_encounter_count, na.rm = T),
            `PC Encounters` = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(`CRH per 1,000 PC` =`CRH Encounters` / `PC Encounters` * 1000) %>%
  mutate_at(2:3, comma_format()) %>%
  mutate_at(4, comma_format(accuracy = 0.1)) %>%
  kbl(col.names = c("", "PC CRH Encounters", "PC Encounters", "CRH per 1,000 PC"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped", 
                full_width = F) %>%
  row_spec(0, bold = TRUE)
```

## By Uniques  
```{r}
analytic_df %>%
  group_by(scrssn_count_cat) %>%
  summarise(`CRH Encounters` = sum(crh_encounter_count, na.rm = T),
            `PC Encounters` = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(`CRH per 1,000 PC` =`CRH Encounters` / `PC Encounters` * 1000) %>%
  mutate_at(2:3, comma_format()) %>%
  mutate_at(4, comma_format(accuracy = 0.1)) %>%
  kbl(col.names = c("Unique ScrSSNs", "PC CRH Encounters", "PC Encounters", "CRH per 1,000 PC"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped", 
                full_width = F) %>%
  row_spec(0, bold = TRUE)
```

## Uniques  
```{r}
uniques_by_sta5a <- dbGetQuery(oabi_con,
                               "with cte as(
	select *
		, datefromparts(year(visitDate), month(visitDate), '01') as visitMonth
	from [PACT_CC].CRH.C_crh_utilization_final
	where care_type = 'Primary care'
		and visitdate > cast('2020-03-01' as date)
	and spoke_sta5a_combined_cdw in(select sta5a from [OABI_MyVAAccess].[crh_eval].ps_matched)
	)
select count(distinct scrssn) as scrssn_count
	, spoke_sta5a_combined_cdw as sta5a
from cte
group by spoke_sta5a_combined_cdw") %>%
  filter(sta5a %in% crh_sta5as)
#--
tibble(`Uniques Served by CRH` = sum(uniques_by_sta5a$scrssn_count),
       `CRH Encounters` = sum(analytic_df$crh_encounter_count, na.rm = T),
       `CRH Encounters per Unique` = `CRH Encounters` / `Uniques Served by CRH`,
       foo = "foo") %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  mutate(value = if_else(str_detect(name, "per"), 
                         comma(value, accuracy = 0.01),
                         comma(value, accuracy = 1))) %>%
  kbl(col.names = c("", ""),
      align = c("l", "r")) %>%
  kable_classic("striped", 
                full_width = F) %>%
  row_spec(0, bold = TRUE)
```

### By Site Type  
```{r}
uniques_by_type <- uniques_by_sta5a %>%
  left_join (., vast) %>%
  group_by(s_abbr) %>%
  summarise(`Uniques Served by CRH` = sum(scrssn_count))
#
analytic_df %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  group_by(s_abbr) %>%
  summarise(`CRH Encounters` = sum(crh_encounter_count, na.rm = T)) %>%
  left_join(., uniques_by_type) %>%
  mutate(`CRH per Unique` =`CRH Encounters` / `Uniques Served by CRH`) %>%
  mutate_at(4, comma_format(accuracy = 0.1)) %>%
  adorn_totals() %>%
  mutate_at(2:3, comma_format(accuracy = 1)) %>%
  kbl(col.names = c("Site Type", "CRH Encounters", "Uniques Served by CRH", "CRH per Unique"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(6, bold = TRUE)
```

### By Urban/Rural    
```{r}
uniques_by_urh <- uniques_by_sta5a %>%
  left_join (., vast) %>%
  mutate(urh_vast2 = if_else(urh_vast == "U", "Urban", "Rural")) %>%
  group_by(urh_vast2) %>%
  summarise(`Uniques Served by CRH` = sum(scrssn_count))
#
analytic_df %>%
  left_join(., vast %>% select(sta5a, urh_vast)) %>%
  mutate(urh_vast2 = if_else(urh_vast == "U", "Urban", "Rural")) %>%
  group_by(urh_vast2) %>%
  summarise(`CRH Encounters` = sum(crh_encounter_count, na.rm = T)) %>%
  left_join(., uniques_by_urh) %>%
  mutate(`CRH per Unique` =`CRH Encounters` / `Uniques Served by CRH`) %>%
  mutate_at(4, comma_format(accuracy = 0.1)) %>%
  adorn_totals() %>%
  mutate_at(2:3, comma_format(accuracy = 1)) %>%
  kbl(col.names = c("Site Type", "CRH Encounters", "Uniques Served by CRH", "CRH per Unique"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(3, bold = TRUE)
```


# Characteristics of Sta5as with PC CRH  

```{r}
covariates %>%
  filter(sta5a %in% crh_sta5as
         & vssc_month >= ymd("2020-04-01")
         & vssc_month <= ymd("2022-10-01")) %>%
  select(4, 5, 9:18) %>%
  pivot_longer(-sta5a) %>%
  group_by(name) %>%
  summarise(
    val_mean = case_when(
      str_detect(name, "pct") == T ~ percent(mean(value / 100, na.rm = T), accuracy = 0.1),
      str_detect(name, "shep") == T ~ percent(mean(value, na.rm = T), accuracy = 0.1),
      TRUE ~ comma(mean(value, na.rm = T), accuracy = 0.1)),
    val_sd = case_when(
        str_detect(name, "pct") == T ~ percent(sd(value / 100, na.rm = T), accuracy = 0.1),
        str_detect(name, "shep") == T ~ percent(sd(value, na.rm = T), accuracy = 0.1),
        TRUE ~ comma(sd(value, na.rm = T), accuracy = 0.1)),
    val_min = case_when(
      str_detect(name, "pct") == T ~ percent(min(value / 100, na.rm = T), accuracy = 0.1),
      str_detect(name, "shep") == T ~ percent(min(value, na.rm = T), accuracy = 0.1),
      TRUE ~ comma(min(value, na.rm = T), accuracy = 0.1)),
    val_max = case_when(
      str_detect(name, "pct") == T ~ percent(max(value / 100, na.rm = T), accuracy = 0.1),
      str_detect(name, "shep") == T ~ percent(max(value, na.rm = T), accuracy = 0.1),
      TRUE ~ comma(max(value, na.rm = T), accuracy = 0.1)),
    val_25th = case_when(
      str_detect(name, "pct") == T ~ percent(quantile(value / 100, 0.25, na.rm = T), 
                                             accuracy = 0.1),
      str_detect(name, "shep") == T ~ percent(quantile(value, 0.25, na.rm = T), 
                                              accuracy = 0.1),
      TRUE ~ comma(quantile(value, 0.25, na.rm = T), accuracy = 0.1)),
    val_75th = case_when(
      str_detect(name, "pct") == T ~ percent(quantile(value / 100, 0.75, na.rm = T), 
                                             accuracy = 0.1),
      str_detect(name, "shep") == T ~ percent(quantile(value, 0.75, na.rm = T), 
                                              accuracy = 0.1),
      TRUE ~ comma(quantile(value, 0.75, na.rm = T), accuracy = 0.1))) %>%
  mutate(name2 = case_when(
    name == "adi_natRnk_avg" ~ "ADI",
    name == "avg_age_oct1_2022" ~ "Age",
    name == "avg_driveDist" ~ "Drive Distance",
    name == "nosos_risk_score" ~ "NOSOS",
    name == "obs_exp_panel_ratio" ~ "Observed:Expected Panel Size",
    name == "pcmm_count_fy_qtr" ~ "Uniques in PCMM",
    name == "pct_male" ~ "Proportion Male",
    name == "pct_rural" ~ "Proportion Rural",
    name == "pct_white" ~ "Proportion White",
    name == "shep_access_metric" ~ "SHEP Access Composite",
    name == "team_pcp_ap_fte_total" ~ "Team PCP/AP FTE"
  )
  ) %>%
  distinct %>%
  ungroup %>%
  mutate(val_mean_sd = paste0(val_mean, " (", val_sd, ")"),
         val_min_max = paste0("[", val_min, ", ", val_max, "]"),
         val_25_75 = paste0("(", val_25th, ", ", val_75th, ")")) %>%
  select(name2, 8:11) %>%
  kbl(col.names = c("", "Average (SD)", "[Min., Max.]", "(25th %ile, 75th %ile)")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```

# Characteristics of Patients With PC CRH  

```{r}
patient_chars <- dbGetQuery(oabi_con,
                            "with CTE as(
            	select a.scrssn, a.age_oct1_2022
            	, a.DOB, a.DRIVETIMEPC, a.GENDER, a.LAT, a.LON, a.Race, a.TRACT, a.URH
            	, b.fips
            		, c.adi_natrank
            	from [OABI_MyVAAccess].[crh_eval].J_pat_chars as a
            	left join [PCS_PCAT].PSSG.PatientBlockGroup2020Q4 as b
            		on a.scrssn = b.ScrSSN_char
            	left join [PCS_PCAT].[PSSG].adi2020 as c
            		on SUBSTRING(b.fips, 1, 12) = c.FIPS
            	)
            select *
            from cte
            UNION
            select a.scrssn, a.age_oct1_2022
            	, a.DOB, a.DRIVETIMEPC, a.GENDER, a.LAT, a.LON, a.Race, a.TRACT, a.URH
            	, b.fips
            	, c.ADI_NATRANK
            from cte as a
            left join [PCS_PCAT].PSSG.PatientBlockGroup2021Q4 as b
            	on a.scrssn = b.ScrSSN_char
            left join [PCS_PCAT].[PSSG].adi2020 as c
            	on SUBSTRING(b.fips, 1, 12) = c.FIPS
            where scrssn IN(select distinct scrssn from cte where fips IS NULL)") %>%
  filter(is.na(fips) == F)
#
paste0_fxn <- function(column){
  paste0(round(mean({{column}}, na.rm = T), 2), " (", 
                           round(sd({column}, na.rm = T), 2), ")")
}
#
patient_chars %>%
  summarise(`Age` = paste0_fxn(age_oct1_2022),
            `Drivetime to PC` = paste0_fxn(DRIVETIMEPC),
            `ADI` = paste0_fxn(as.numeric(adi_natrank)),
            `Male` = percent(sum(patient_chars$GENDER == "M", na.rm = T) / nrow(patient_chars),
                           accuracy = 0.1),
            `Male Count` = comma(sum(patient_chars$GENDER == "M", na.rm = T)),
            `Urban` = percent(sum(patient_chars$URH == "U", na.rm = T) / nrow(patient_chars),
                           accuracy = 0.1),
            `Urban count` = comma(sum(patient_chars$URH == "U", na.rm = T)),
            `White` = percent(sum(patient_chars$Race == "WHITE", na.rm = T) / nrow(patient_chars),
                           accuracy = 0.1),
            `Black` = percent(sum(patient_chars$Race == "BLACK", na.rm = T) / nrow(patient_chars),
                           accuracy = 0.1)) %>%
  mutate(foo = "foo") %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  kbl(col.names = c("Measure", "Value"),
      align = c("l", "r")) %>%
  kable_classic("striped",
      full_width = F)
```

# Total PC CRH Encounters Over Time   
```{r}
theme_update(axis.title = element_text(size = 30),
             axis.text = element_text(size = 22),
             legend.text = element_text(size = 26),
             legend.title = element_blank(),
             legend.position = "bottom")
#
covariates %>% 
  filter(sta5a %in% crh_sta5as
         & vssc_month > ymd("2019-09-01")) %>%
  group_by(vssc_month) %>%
  summarise(total_pc_crh = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = total_pc_crh)) +
  geom_line(linewidth = 1.25,
            color = "#994F00") +
  scale_y_continuous(limits = c(0, NA), 
                     labels = comma_format(accuracy = 1)) +
  labs(y = "PC CRH Encounters per Month") +
  theme(axis.title.x = element_blank()) +
  geom_vline(xintercept = ymd("2020-03-01"), lty = 2) +
  geom_label(label = "March 2020",
             x = as.numeric(ymd("2020-03-01")),
             y = 2500,
             size = 12) +
  geom_segment(aes(x = ymd("2021-10-01"), xend = ymd("2022-12-01"),
                   y = 10000, yend = 10000),
               lineend = "round",
               linewidth = 1.25) +
  geom_label(label = "Study Period",
             x = as.numeric(ymd("2022-05-01")),
             y = 8500,
             size = 14)
```

# Wait Times at Baseline   
```{r}
analytic_df %>%
  filter(vssc_month == ymd("2021-10-01")) %>%
  select(sta5a, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source) %>%
  pivot_longer(-sta5a) %>%
  group_by(name) %>%
  summarise(avg_val = round(mean(value, na.rm = T),3),
            sd_val = round(sd(value, na.rm = T),3),
            qtl_25 = round(quantile(value, 0.25, na.rm = T),3),
            qtl_75 = round(quantile(value, 0.75, na.rm = T),3)) %>%
  kbl() %>%
  kable_classic("striped")
```