---
title: "PC CRH: Covariates of Interest Over 3 Periods"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(emmeans)
library(gtsummary)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
pactcc_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "PACT_CC",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
#
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
```

```{r reading-in-PCCCs}
# PC CCs by VISN Month
pc_cc_count_by_visn_month <- dbGetQuery(oabi_con,
  "with pccc_cte as(
  	select a.*, vizMonth = DATEFROMPARTS(year(a.activityDateTime), month(a.activityDateTime), '01')
  	  , fy = case when month(activityDateTime) > 9 then year(activityDateTime) + 1 else year(activityDateTime) end
  	  , qtr = case
  	    when month(activityDateTime) IN(10, 11, 12) then 1
  	    when month(activityDateTime) IN(1, 2, 3) then 2
  	    when month(activityDateTime) IN(4, 5, 6) then 3
  	    when month(activityDateTime) IN(7, 8, 9) then 4 end
  		, b.parent_visn
  	from [OABI_MyVAAccess].[crh_eval].G_pc_communityCare_referrals as a
  	inner join [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as b
  	on a.Sta6a = b.sta5a
  	where Activity <> 'CANCELLED'
  		AND Activity <> 'DISCONTINUED'
  		AND non_va = 1
  		)
  select count(*) as pc_cc_count
  	, parent_visn, vizMonth, fy, qtr
  from pccc_cte
  group by parent_visn, vizMonth, fy, qtr;") %>%
  mutate(join_qtr = if_else(fy == 2022 & qtr == 4, 3, as.numeric(qtr)))# as of now PCMM not updated through Q4, FY22
#--
scrssn_count_by_visn_qtr <- dbGetQuery(oabi_con,
  "with pcmm_cte as(
  	select a.scrssn_char, b.parent_visn, a.fy, a.qtr
  	from [PACT_CC].[econ].PatientPCP as a
  	inner join [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as b
  		on a.Sta5a = b.sta5a
  	where a.fy > 2018
  	)
  select count(distinct scrssn_char) as scrssn_count, parent_visn, fy, qtr
  from pcmm_cte
  group by parent_visn, fy, qtr")
#==--
pccc_per_10k_pcmm_visn_month <- pc_cc_count_by_visn_month %>%
  left_join(., scrssn_count_by_visn_qtr, by = c("parent_visn", "fy" = "fy", "join_qtr" = "qtr")) %>%
  mutate(pc_cc_per_10k_pcmm = (pc_cc_count / scrssn_count) * 10000,
         vizMonth = ymd(vizMonth))
```

```{r reading-in-outcomes-visn-month}
file_paths <- list.files(path = "H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Analytic df/E2_vssc_cube_access_metrics", pattern = "visn",
                                           full.names = TRUE)
#
est_pt_wt_visn_month <- read_csv(file_paths[1]) %>%
      rename_all(tolower) %>%
      mutate(month_n = match(str_to_title(str_sub(`fiscal date`, end = 3)), month.abb),
             fy = as.numeric(str_sub(`fiscal date`, start = -2)),
             cy2 = if_else(month_n > 9, fy - 1, fy),
             cy = as.numeric(str_c("20", cy2)),
             vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
             visn = str_sub(visn, start = 2)) %>%
      select(visn, vssc_month, value = 3)
#
new_pt_wt_visn_month <- read_csv(file_paths[2]) %>%
      rename_all(tolower) %>%
      mutate(month_n = match(str_to_title(str_sub(`fiscal date`, end = 3)), month.abb),
             fy = as.numeric(str_sub(`fiscal date`, start = -2)),
             cy2 = if_else(month_n > 9, fy - 1, fy),
             cy = as.numeric(str_c("20", cy2)),
             vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
             visn = str_sub(visn, start = 2)) %>%
      select(visn, vssc_month, value = 3)
#
tna_visn_month <- read_csv(file_paths[3]) %>%
      rename_all(tolower) %>%
      mutate(month_n = match(str_to_title(str_sub(`fiscal date`, end = 3)), month.abb),
             fy = as.numeric(str_sub(`fiscal date`, start = -2)),
             cy2 = if_else(month_n > 9, fy - 1, fy),
             cy = as.numeric(str_c("20", cy2)),
             vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
             visn = str_sub(visn, start = 2)) %>%
      select(visn, vssc_month, value = 3)
```

```{r reading-in-crh_encounters-visn-month}
pc_encounters_for_denom <- dbGetQuery(oabi_con,
                                      "select * from [OABI_MyVAAccess].[crh_eval].A2_pc_enc_scrssn_count_visn") %>%
  mutate(crh_month = ymd(visitMonth))
#
crh_encounters_visn_month <- dbGetQuery(oabi_con,
                          "with CTE as(
                            	select *
                            		, DATEFROMPARTS(year(visitdate), month(visitdate), '01') as crh_month
                            	from [PACT_CC].[CRH].C_crh_utilization_final
                            	where care_type = 'Primary Care'
                            	)
                            select count(*) as crh_encounter_count, count(distinct scrssn) as crh_scrssn_count
                            	, spoke_sta5a_combined_cdw as sta5a
                            	, crh_month
                            from CTE
                            group by spoke_sta5a_combined_cdw
                            	, crh_month;") %>%
  mutate(crh_month = ymd(crh_month)) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  group_by(crh_month, parent_visn) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  left_join(., pc_encounters_for_denom, by = c("crh_month", "parent_visn")) %>%
  mutate(pc_crh_per_1k_total_pc_enc = (crh_encounter_count / (crh_encounter_count + pc_encounter_total) * 1000)) %>%
  filter(is.na(parent_visn) == F)
#
months_in_crh <- crh_encounters_visn_month %>% select(crh_month) %>% distinct
```

```{r working-with-dates}
dates <- est_pt_wt_visn_month %>% select(vssc_month) %>%
  distinct %>%
  mutate(fy = case_when(month(vssc_month) > 9 ~ year(vssc_month) + 1,
                        TRUE ~ year(vssc_month)),
         qtr = case_when(month(vssc_month) %in% c(10, 11, 12) ~ 1,
                         month(vssc_month) %in% c(1, 2, 3) ~ 2,
                         month(vssc_month) %in% c(4, 5, 6) ~ 3,
                         month(vssc_month) %in% c(7, 8, 9) ~ 4),
         period_value = factor(case_when(vssc_month > ymd("2021-02-01") ~ "March 2021 and Later",
                                  vssc_month < ymd("2020-03-01") ~ "February 2020 and Before",
                                  TRUE ~ "March 2020 - February, 2021"), ordered = TRUE,
                               levels = c("February 2020 and Before","March 2020 - February, 2021", "March 2021 and Later"))) %>% 
  filter(fy > 2018)

```

# Established Patient Wait Time - VISN Month   

* These data include the `r nrow(dates)` months from October, 2018 through July, 2022 (inclusive)

## Boxplot  
```{r est_pt_boxplot}
est_pt_wt_visn_month %>%
  inner_join(., dates) %>%
  ggplot(data = .,
         aes(x = period_value, y = value, fill = period_value)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time") +
  ggsci::scale_fill_jama()
```


## As a Table  
```{r est_pt_table}
est_pt_wt_visn_month %>%
  inner_join(., dates) %>%
  select(value, period_value) %>%
  rename(`Established Patient Wait Time` = value) %>%
  tbl_summary(by = period_value,
              statistic = all_continuous() ~ "{mean} ({sd})",
              digits = all_continuous() ~ 1) %>%
  add_p() %>%
  modify_header()
```


## t-test of period 1 vs. period 3  
```{r est_pt_ttests}
est_pt_wt_visn_month %>%
  inner_join(., dates) %>%
  rename(`Established Patient Wait Time` = value) %>%
  filter(period_value != "March 2020 - February, 2021") %>%
  t.test(data = .,
         `Established Patient Wait Time` ~ period_value)
```

# New Patient Wait Time - VISN Month   

* These data include the `r nrow(dates)` months from October, 2018 through July, 2022 (inclusive)

## Boxplot  
```{r new_pt_boxplot}
new_pt_wt_visn_month %>%
  inner_join(., dates) %>%
  ggplot(data = .,
         aes(x = period_value, y = value, fill = period_value)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time") +
  ggsci::scale_fill_aaas()
```

## As a Table  
```{r new_pt_table}
new_pt_wt_visn_month %>%
  inner_join(., dates) %>%
  select(value, period_value) %>%
  rename(`New Patient Wait Time` = value) %>%
  tbl_summary(by = period_value,
              statistic = all_continuous() ~ "{mean} ({sd})",
              digits = all_continuous() ~ 1) %>%
  add_p() %>%
  modify_header()
```

## t-test of period 1 vs. period 3  
```{r new_pt_ttests}
new_pt_wt_visn_month %>%
  inner_join(., dates) %>%
  rename(`New Patient Wait Time` = value) %>%
  filter(period_value != "March 2020 - February, 2021") %>%
  t.test(data = .,
         `New Patient Wait Time` ~ period_value)
```

# Third Next Available - VISN Month   

* These data include the `r nrow(dates)` months from October, 2018 through July, 2022 (inclusive)

## Boxplot  
```{r tna_boxplot}
tna_visn_month %>%
  inner_join(., dates) %>%
  ggplot(data = .,
         aes(x = period_value, y = value, fill = period_value)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Third Next Available") +
  ggsci::scale_fill_lancet()
```

## As a Table  
```{r tna_table}
tna_visn_month %>%
  inner_join(., dates) %>%
  select(value, period_value) %>%
  rename(`Third Next Available` = value) %>%
  tbl_summary(by = period_value,
              statistic = all_continuous() ~ "{mean} ({sd})",
              digits = all_continuous() ~ 1) %>%
  add_p() %>%
  modify_header()
```

## t-test of period 1 vs. period 3  
```{r tna_ttests}
tna_visn_month %>%
  inner_join(., dates) %>%
  rename(`Third Next Available` = value) %>%
  filter(period_value != "March 2020 - February, 2021") %>%
  t.test(data = .,
         `Third Next Available` ~ period_value)
```

# PC Community Care Episodes per 10,000 Uniques in PCMM - VISN Month   

* These data include the `r nrow(dates)` months from October, 2018 through July, 2022 (inclusive)

## Boxplot  
```{r pccc_boxplot}
pccc_per_10k_pcmm_visn_month %>%
  inner_join(., dates %>% select(period_value, vizMonth = vssc_month)) %>%
  ggplot(data = .,
         aes(x = period_value, y = pc_cc_per_10k_pcmm, fill = period_value)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "PC CC Episodes per 10,000 in PCMM") +
  ggsci::scale_fill_jco()
```

## As a Table  
```{r pccc_table}
pccc_per_10k_pcmm_visn_month %>%
  inner_join(., dates %>% select(period_value, vizMonth = vssc_month)) %>%
  select(pc_cc_per_10k_pcmm, period_value) %>%
  rename(`PC CC Episodes per 10,000 in PCMM` = pc_cc_per_10k_pcmm) %>%
  tbl_summary(by = period_value,
              statistic = all_continuous() ~ "{mean} ({sd})",
              digits = all_continuous() ~ 1) %>%
  add_p() %>%
  modify_header()
```

## t-test of period 1 vs. period 3  
```{r pccc_ttests}
pccc_per_10k_pcmm_visn_month %>%
  inner_join(., dates %>% select(period_value, vizMonth = vssc_month)) %>%
  rename(`PC CC Episodes per 10,000 in PCMM` = pc_cc_per_10k_pcmm) %>%
  filter(period_value != "March 2020 - February, 2021") %>%
  t.test(data = .,
         `PC CC Episodes per 10,000 in PCMM` ~ period_value)
```

# PC CRH Encounters per 1,000 PC Encounters - VISN Month   

* These data include the `r nrow(months_in_crh)` months from October, 2019 through June, 2022 (inclusive)

## Boxplot  
```{r crh_boxplot}
crh_encounters_visn_month %>%
  inner_join(., dates %>% select(period_value, crh_month = vssc_month)) %>%
  ggplot(data = .,
         aes(x = period_value, y = pc_crh_per_1k_total_pc_enc, fill = period_value)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "PC CRH Encounters per 1,000 PC Encounters") +
  ggsci::scale_fill_nejm()
```

## As a Table  
```{r crh_table}
crh_encounters_visn_month %>%
  inner_join(., dates %>% select(period_value, crh_month = vssc_month)) %>% ungroup %>%
  select(pc_crh_per_1k_total_pc_enc, period_value) %>%
  rename(`PC CRH Encounters per 1,000 PC Encounters` = pc_crh_per_1k_total_pc_enc) %>%
  tbl_summary(by = period_value,
              statistic = all_continuous() ~ "{mean} ({sd})",
              digits = all_continuous() ~ 1) %>%
  add_p() %>%
  modify_header()
```

## t-test of period 1 vs. period 3  
```{r crh_ttests}
crh_encounters_visn_month %>%
  inner_join(., dates %>% select(period_value, crh_month = vssc_month)) %>% ungroup %>%
  rename(`PC CRH Encounters per 1,000 PC Encounters` = pc_crh_per_1k_total_pc_enc) %>%
  filter(period_value != "March 2020 - February, 2021") %>%
  t.test(data = .,
         `PC CRH Encounters per 1,000 PC Encounters` ~ period_value)
```