---
title: "What's with the variance in New Patient Wait Time?"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("Input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v4_noVISN.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- access_metrics %>%#1: must have Access metrics
  select(sta5a) %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, 
                            "PC CRH", "No PC CRH")) %>%#making the crh_flag
  left_join(., scrssn_count) %>%
  filter(scrssn_count_cat != "< 450")#3: must have scrssn_count_avg_fy18 >= 450
#-
sta5as_to_include_matched <- ps_matched %>% 
  filter(sta5a %in% crh_sta5as) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df_noMatch <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2019-10-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "No PC CRH")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., scrssn_count) %>%
  mutate(s_abbr2 = case_when(
    str_detect(s_abbr, "CBOC") ~ "CBOC",
    str_detect(s_abbr, "VAMC|HCC") ~ "VAMC/HCC",
    str_detect(s_abbr, "OOS") ~ "OOS"
  ))
#=================
#making the analytic dataset
analytic_df_withMatch <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include_matched) %>%#restrict to our table from above
      filter(vssc_month < ymd("2019-10-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "No PC CRH")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  left_join(., scrssn_count) %>%
  mutate(s_abbr2 = case_when(
    str_detect(s_abbr, "CBOC") ~ "CBOC",
    str_detect(s_abbr, "VAMC|HCC") ~ "VAMC/HCC",
    str_detect(s_abbr, "OOS") ~ "OOS"
  ))
```

```{r functions}
time_fxn <- function(outcome, facet){
  if(missing(facet)){
    plot1 <- analytic_df_noMatch %>%
      filter({{outcome}} < 75) %>%
      ggplot(data = .,
             aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
      geom_line(alpha = 0.3) +
      geom_smooth(aes(group = treat, color = treat),
                  method = "lm", 
                  se = F) +
      labs(y = "New Patient Wait Time",
           title = "No Matching") +
      theme(axis.title.x = element_blank()) +
      scale_x_date(breaks = "4 months")
    #--
    plot2 <- analytic_df_withMatch %>%
      filter({{outcome}} < 75) %>%
      ggplot(data = .,
             aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
      geom_line(alpha = 0.3) +
      geom_smooth(aes(group = treat, color = treat),
                  method = "lm", 
                  se = F) +
      labs(y = "New Patient Wait Time",
           title = "Matched") +
      theme(axis.title.x = element_blank()) +
      scale_x_date(breaks = "4 months")
  }
  else{
    plot1 <- analytic_df_noMatch %>%
      filter({{outcome}} < 75) %>%
      ggplot(data = .,
             aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
      geom_line(alpha = 0.3) +
      geom_smooth(aes(group = treat, color = treat),
                  method = "lm", 
                  se = F) +
      labs(y = "New Patient Wait Time",
           title = "No Matching") +
      theme(axis.title.x = element_blank(),
            axis.text.x = element_text(angle = 270, vjust = 0.3)) +
      facet_wrap({{facet}}) +
      scale_x_date(breaks = "4 months", 
                   date_labels = "%b-%y")
    #-
    plot2 <- analytic_df_withMatch %>%
      filter({{outcome}} < 75) %>%
      ggplot(data = .,
             aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
      geom_line(alpha = 0.3) +
      geom_smooth(aes(group = treat, color = treat),
                  method = "lm", 
                  se = F) +
      labs(y = "New Patient Wait Time",
           title = "Matched") +
      theme(axis.title.x = element_blank(),
            axis.text.x = element_text(angle = 270, vjust = 0.3)) +
      facet_wrap({{facet}}) +
      scale_x_date(breaks = "4 months", 
                   date_labels = "%b-%y")
  }
  #--
  multiplot(plot1, plot2)
}
#-------------
bp_fxn <- function(outcome, facet){
    bp_p1 <- analytic_df_noMatch %>%
      ggplot(data = .,
             aes(y = {{outcome}}, x = treat, fill = treat)) +
      geom_boxplot() +
      labs(y = "New Patient Wait Time",
           title = "No Matching") +
      theme(legend.position = "none",
            axis.title.x = element_blank()) +
      scale_y_continuous(limits = c(0, 100))
    #
    bp_p2 <- analytic_df_withMatch %>%
      ggplot(data = .,
             aes(y = {{outcome}}, x = treat, fill = treat)) +
      geom_boxplot() +
      labs(y = "New Patient Wait Time",
           title = "Matched") +
      theme(legend.position = "none",
            axis.title.x = element_blank()) +
      scale_y_continuous(limits = c(0, 100))
    #--
    if(missing(facet)){
      multiplot(bp_p1, bp_p2)
    }
    else{
      multiplot(bp_p1 + facet_wrap({{facet}}), bp_p2 + facet_wrap({{facet}}))
    }
}
```

# Front Matter  

## Description of this report  

* This report examines New Patient Wait Time over time so see if there is anything wonky going on

## Decision Points  

* During our meeting on 12/14/2022 team-members expressed concern about the amount of variance we were still seeing in our outcomes after matching. This report examines those outcomes and tries to identify any associations between variability or extreme-ness in our outcomes and sta5a-level characteristics
    
## Analytic details  


* Description of the __non-matched__ dataset:

    + The first observation in the data occurs on `r min(analytic_df_noMatch$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df_noMatch$vssc_month)`
    + There are `r nrow(analytic_df_noMatch) %>% comma()` rows in the data
    + These rows come from `r analytic_df_noMatch %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df_noMatch %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df_noMatch %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "CBOC") == T))` of these are CBOCs
      + `r analytic_df_noMatch %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df_noMatch %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of the __matched__ dataset:

    + The first observation in the data occurs on `r min(analytic_df_withMatch$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df_withMatch$vssc_month)`
    + There are `r nrow(analytic_df_withMatch) %>% comma()` rows in the data
    + These rows come from `r analytic_df_withMatch %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df_withMatch %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df_withMatch %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "CBOC") == T))` of these are CBOCs
      + `r analytic_df_withMatch %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df_withMatch %>% select(sta5a, s_abbr2) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr2, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + I am applying __Propensity Score v4.0__
    + PS model v4.0 consists of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Site type (CBOC, VAMC/HCC, OOS)


# New Patient Wait Time    

## Over Time  
```{r}
time_fxn(new_pc_pt_wt)
```

### Boxplots  
```{r}
bp_fxn(new_pc_pt_wt)
```


## By Site Type  

```{r}
time_fxn(new_pc_pt_wt, "s_abbr2")
```

### Boxplots  
```{r}
bp_fxn(new_pc_pt_wt, "s_abbr2")
```

## By Categorical Uniques  

```{r}
time_fxn(new_pc_pt_wt, "scrssn_count_cat")
```

### Boxplots  
```{r}
bp_fxn(new_pc_pt_wt, "scrssn_count_cat")
```

## What kinds of sta5as have New Patient Wait Time > 50?  

```{r}
newPtWt_gt50_noMatch <- analytic_df_noMatch %>%
  filter(new_pc_pt_wt > 50) %>%
  select(sta5a, vssc_month) %>%
  distinct() %>%
  left_join(., analytic_df_noMatch %>% select(sta5a, s_abbr2)) %>%
  left_join(., scrssn_count) %>%
  distinct %>%
  group_by(sta5a, s_abbr2, scrssn_count_cat) %>%
  summarise(first_month_w_gt50_newPtWt = min(vssc_month),
            count_vssc_months_gt50_newPtWt = n())
#
newPtWt_gt50_siteType_noMatch <- newPtWt_gt50_noMatch %>%
  group_by(s_abbr2) %>%
  summarise(count = n(),
            prop = count / nrow(newPtWt_gt50_noMatch)) %>%
  rename(name = s_abbr2) %>%
  mutate(value = paste0(
    count, " (", percent(prop, accuracy = 0.1), ")"
  )) %>%
  select(name, value)
#
newPtWt_gt50_uniques_noMatch <- newPtWt_gt50_noMatch %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n(),
            prop = count / nrow(newPtWt_gt50_noMatch)) %>%
  rename(name = scrssn_count_cat) %>%
  mutate(value = paste0(
    count, " (", percent(prop, accuracy = 0.1), ")"
  )) %>%
  select(name, value)
#----
newPtWt_gt50_withMatch <- analytic_df_withMatch %>%
  filter(new_pc_pt_wt > 50) %>%
  select(sta5a, vssc_month) %>%
  distinct() %>%
  left_join(., analytic_df_noMatch %>% select(sta5a, s_abbr2)) %>%
  left_join(., vast) %>%
  left_join(., scrssn_count) %>%
  distinct %>%
  group_by(sta5a, s_abbr2, scrssn_count_cat) %>%
  summarise(first_month_w_gt50_newPtWt = min(vssc_month),
            count_vssc_months_gt50_newPtWt = n())
#
newPtWt_gt50_siteType_withMatch <- newPtWt_gt50_withMatch %>%
  group_by(s_abbr2) %>%
  summarise(count = n(),
            prop = count / nrow(newPtWt_gt50_withMatch)) %>%
  rename(name = s_abbr2) %>%
  mutate(value = paste0(
    count, " (", percent(prop, accuracy = 0.1), ")"
  )) %>%
  select(name, value)
#
newPtWt_gt50_uniques_withMatch <- newPtWt_gt50_withMatch %>%
  group_by(scrssn_count_cat) %>%
  summarise(count = n(),
            prop = count / nrow(newPtWt_gt50_withMatch)) %>%
  rename(name = scrssn_count_cat) %>%
  mutate(value = paste0(
    count, " (", percent(prop, accuracy = 0.1), ")"
  )) %>%
  select(name, value)
#--------
newPtWt_tbl_noMatch <- newPtWt_gt50_siteType_noMatch %>%
  bind_rows(., newPtWt_gt50_uniques_noMatch)
#
newPtWt_tbl_withMatch <- newPtWt_gt50_siteType_withMatch %>%
  bind_rows(., newPtWt_gt50_uniques_withMatch)
#--==
```


### By Site Type  
```{r}
newPtWt_tbl_noMatch %>%
  left_join(., newPtWt_tbl_withMatch, by = "name") %>%
  slice(1:3) %>%
  kbl(col.names = c("", "No Match", "Matched"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

### By Uniques   
```{r}
newPtWt_tbl_noMatch %>%
  left_join(., newPtWt_tbl_withMatch, by = "name") %>%
  slice(4:6) %>%
  kbl(col.names = c("", "No Match", "Matched"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

### A sample of sta5as  

* Since there are `r nrow(newPtWt_gt50_noMatch)` un-matched sta5as that have at least one month with New Patient Wait Time > 50 days, below is a sample of 15 of them

```{r}
newPtWt_gt50_noMatch %>%
  ungroup %>% 
  left_join(., vast %>% select(sta5a, short_name)) %>%
  select(6, 1, 2, 3, 4, 5) %>%
  slice_sample(n = 15) %>%
  kbl(col.names = c("Site Name", "Sta5a", "Type", "Uniques",
                    "First month w/ NPWT > 25", "Number of months w/ NPWT > 25")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

* Since there are `r nrow(newPtWt_gt50_withMatch)` matched sta5as that have at least one month with New Patient Wait Time > 25 days, below is a sample of 15 of them

```{r}
newPtWt_gt50_withMatch %>%
  ungroup %>% 
  left_join(., vast %>% select(sta5a, short_name)) %>%
  select(6, 1, 2, 3, 4, 5) %>%
  slice_sample(n = 15) %>%
  kbl(col.names = c("Site Name", "Sta5a", "Type", "Uniques",
                    "First month w/ NPWT > 25", "Number of months w/ NPWT > 25")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```