---
title: "Outcome Trends: when does \"post-COVID\" start?"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month > ymd("2020-02-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(crh_10_flag == 1) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- access_metrics %>%#1: must have Access metrics
  select(sta5a) %>%
  inner_join(ps_matched) %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, 
                            "PC CRH", "No PC CRH")) %>%#making the crh_flag
  left_join(., scrssn_count) %>%
  filter(scrssn_count_cat != "< 450")#3: must have scrssn_count_avg_fy18 >= 450
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
     # filter(vssc_month > ymd("2019-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
  mutate(periods_option_1 = 
           factor(case_when(vssc_month < ymd("2020-03-01") ~ "< 3/20",
                            vssc_month >= ymd("2020-03-01") 
                              & vssc_month < ymd("2020-07-01") ~ "3/20-6/20",
                            vssc_month >= ymd("2020-07-01") ~ "7/20-9/22"),
                  ordered = TRUE,
                  levels = c("< 3/20", "3/20-6/20", "7/20-9/22")),
         periods_option_2 = 
           factor(case_when(vssc_month < ymd("2020-03-01") ~ "< 3/20",
                            vssc_month >= ymd("2020-03-01") 
                            & vssc_month < ymd("2021-03-01") ~ "3/20-2/21",
                            vssc_month >= ymd("2021-03-01") ~ "3/21-9/22"),
                  ordered = TRUE,
                  levels = c("< 3/20", "3/20-2/21", "3/21-9/22"))) %>%
  filter(sta5a != "459GA"
         & vssc_month < ymd("2022-11-01"))
```

# Front Matter  

## Description of this report  

* This is an initial look at our outcomes over time, and comparing the pre-COVID study period to 2 potential post-COVID periods

## Decision Points  

* Per our meeting on January 19th 2023 I am going to begin the process of analyzing PC CRH "post-COVID"
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH
      + I've dropped (459GA) Maui because it had TNA > 200 in FY19 & FY20 
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v5.0__
    + PS model v5.0 consists of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact


# Outcomes    

```{r}
analytic_df %>% select(sta5a, new_pc_pt_wt, est_pc_pt_wt, third_next_avail, vssc_month) %>%
  pivot_longer(-c(vssc_month, sta5a)) %>%
  mutate(name2 = 
           case_when(
             name == "est_pc_pt_wt" ~ "Est. Pt WT",
             name == "new_pc_pt_wt" ~ "New Pt WT",
             TRUE ~ "3rd Next Avail."
           )) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = sta5a)) +
  geom_line(alpha = 0.3) +
  scale_x_date(breaks = "6 months",
               date_labels = "%m-%Y") +
  facet_wrap(~name2) +
  labs(y = "Days") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270,
                                   vjust = 0.3))
```

## New Patient Wait Time  

```{r}
analytic_df %>%
  ggplot(data = .,
         aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  scale_x_date(breaks = "3 months",
               date_labels = "%m-%Y") +
  labs(y = "Days") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270,
                                   vjust = 0.3))
```

```{r functions}

fxn_option_march_21 <- function(outcome){
  p1 <- ggplot(data = analytic_df,
               aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_line(alpha = 0.3) +
    geom_smooth(data = subset(analytic_df, vssc_month < ymd("2020-03-01")),
                aes(x = vssc_month, y = {{outcome}}),
                method = "lm", se = F,
                inherit.aes = FALSE, color = "blue") +
    geom_smooth(data = subset(analytic_df, vssc_month >= ymd("2021-03-01")),
                aes(x = vssc_month, y = {{outcome}}),
                method = "lm", se = F,
                inherit.aes = FALSE, color = "forestgreen") +
    geom_smooth(data = subset(analytic_df, vssc_month < ymd("2021-03-01")
                              & vssc_month >= ymd("2020-03-01")),
                aes(x = vssc_month, y = {{outcome}}),
                method = "lm", se = F,
                inherit.aes = FALSE, color = "red") +
    scale_x_date(breaks = "6 months",
                 date_labels = "%m-%Y") +
    labs(y = "Days") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(angle = 270,
                                     vjust = 0.3))
  #
  p2 <- ggplot(data = analytic_df,
               aes(x = periods_option_2, y = {{outcome}}, fill = periods_option_2)) +
    geom_boxplot() +
    labs(y = "Days") +
    theme(legend.position = "none",
          axis.title.x = element_blank()) +
    ggsci::scale_fill_aaas()
  #--
  multiplot(p1, p2, cols = 2)
}
#--
fxn_lm_march_21 <- function(outcome, outcome_q){
  lm_df <- analytic_df %>%
    filter(vssc_month < ymd("2021-03-01")
           & vssc_month >= ymd("2020-03-01")) %>%
    select({{outcome}}, time) %>%
    rename(value = {{outcome}})
  #
  lm_1 <- lm(value ~ time,
             data = lm_df)
  #--
  dv_lab <- if (outcome_q == "est_pc_pt_wt"){
    "Established Patient WaitTime"
  }
  else if(outcome_q == 'new_pc_pt_wt'){
    "New Patient WaitTime"
  }
  else if(outcome_q == "third_next_avail"){
    "Third Next Available"
  }
  tab_model(lm_1,
            dv.labels = dv_lab)
}
#--
fxn_lm_july_20 <- function(outcome, outcome_q){
  lm_df <- analytic_df %>%
    filter(vssc_month < ymd("2020-07-01")
           & vssc_month >= ymd("2020-03-01")) %>%
    select({{outcome}}, time) %>%
    rename(value = {{outcome}})
  #
  lm_1 <- lm(value ~ time,
             data = lm_df)
  #--
  dv_lab <- if (outcome_q == "est_pc_pt_wt"){
    "Established Patient WaitTime"
  }
  else if(outcome_q == 'new_pc_pt_wt'){
    "New Patient WaitTime"
  }
  else if(outcome_q == "third_next_avail"){
    "Third Next Available"
  }
  tab_model(lm_1,
            dv.labels = dv_lab)
}
#--
fxn_option_july_20 <- function(outcome){
  p1 <- ggplot(data = analytic_df,
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
  geom_line(alpha = 0.3) +
  geom_smooth(data = subset(analytic_df, vssc_month < ymd("2020-03-01")),
              aes(x = vssc_month, y = {{outcome}}),
              method = "lm", se = F,
              inherit.aes = FALSE, color = "blue") +
  geom_smooth(data = subset(analytic_df, vssc_month >= ymd("2020-07-01")),
              aes(x = vssc_month, y = {{outcome}}),
              method = "lm", se = F,
              inherit.aes = FALSE, color = "forestgreen") +
    geom_smooth(data = subset(analytic_df, vssc_month < ymd("2020-07-01")
                              & vssc_month >= ymd("2020-03-01")),
                aes(x = vssc_month, y = {{outcome}}),
                method = "lm", se = F,
                inherit.aes = FALSE, color = "red") +
  scale_x_date(breaks = "6 months",
               date_labels = "%m-%Y") +
  labs(y = "Days") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270,
                                   vjust = 0.3))
  #
  p2 <- ggplot(data = analytic_df,
       aes(x = periods_option_1, y = {{outcome}}, fill = periods_option_1)) +
  geom_boxplot() +
  labs(y = "Days") +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  ggsci::scale_fill_aaas()
  #--
  multiplot(p1, p2, cols = 2)
}
```


### When Does post-COVID Start? 

 
* March, 2021?    
```{r}
#
fxn_option_march_21(new_pc_pt_wt)
#
fxn_lm_march_21(new_pc_pt_wt, "new_pc_pt_wt")
```

 
* July, 2020?  
```{r}
fxn_option_july_20(new_pc_pt_wt)
#
fxn_lm_july_20(new_pc_pt_wt, "new_pc_pt_wt")
```

## Established Patient Wait Time  

```{r}
analytic_df %>%
  ggplot(data = .,
         aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  scale_x_date(breaks = "3 months",
               date_labels = "%m-%Y") +
  labs(y = "Days") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270,
                                   vjust = 0.3))
```

### When Does post-COVID Start?  
* March 2021?  
```{r}
fxn_option_march_21(est_pc_pt_wt)
#
fxn_lm_march_21(est_pc_pt_wt, "est_pc_pt_wt")
```

 
* July 2020?    
```{r}
fxn_option_july_20(est_pc_pt_wt)
#
fxn_lm_july_20(est_pc_pt_wt, "est_pc_pt_wt")
```

## Third Next Available  

```{r}
analytic_df %>%
  ggplot(data = .,
         aes(x = vssc_month, y = third_next_avail, group = sta5a)) +
  geom_line(alpha = 0.3) +
  scale_x_date(breaks = "3 months",
               date_labels = "%m-%Y") +
  labs(y = "Days") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 270,
                                   vjust = 0.3))
```

### When Does post-COVID Start?  
* March 2021?  
```{r}
fxn_option_march_21(third_next_avail)
#
fxn_lm_march_21(third_next_avail, "third_next_avail")
```

 
* July 2020?    
```{r}
fxn_option_july_20(third_next_avail)
#
fxn_lm_july_20(third_next_avail, "third_next_avail")
```