---
title: "Tables and Plots for Pre-COVID Manuscript"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01") 
         & vssc_month > ymd("2018-09-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>% 
  filter(sta5a %in% crh_sta5as) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
      left_join(., vast %>% select(sta5a, s_abbr)) %>%
  left_join(., covariates)
```

```{r}
unique_hubs <- dbGetQuery(oabi_con,
                          "select distinct Hub_Location
from [PACT_CC].[CRH].CRH_sites_FY20_working
where SiteType = 'PC'")
#
included_crh_sites <- sta5as_to_include %>%
  filter(crh_flag == "PC CRH") %>%
  select(sta5a) %>%
  distinct %>%
  pull
#
unique_states <- vast %>%
  filter(sta5a %in% included_crh_sites) %>%
  select(state) %>%
  distinct()
```

# Front Matter  

## Description of this report  

* This is the third iteration of our plots and tables for the pre-COVID PC CRH manuscript

## Decision Points  

* Per our discussion on March 10th I'm going to:
    + Inlcude all our covariates in the plots showing the counterfactual
  
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + There are `r nrow(unique_hubs)` unique hubs
    + The PC CRH sites serve `r nrow(unique_states)` states
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v5.0__
    + PS model v5.0 consists of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact


# Table 1  
## PC CRH vs. No PC CRH  
```{r}

#=================
#making the analytic dataset
analytic_df_preMatch <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
      left_join(., vast %>% select(sta5a, s_abbr)) %>%
  left_join(., covariates)
#--
covar_summary <- analytic_df_preMatch %>%
  group_by(crh_flag) %>%
  summarise(unique_sta5as = comma(n_distinct(sta5a)),
            obs_months = comma(n()),
            newPtWt = paste0(round(mean(new_pc_pt_wt, na.rm = T), 2), " (", 
                             round(sd(new_pc_pt_wt, na.rm = T), 2), ")"),
            estPtWt = paste0(round(mean(est_pc_pt_wt, na.rm = T), 2), " (", 
                             round(sd(est_pc_pt_wt, na.rm = T), 2), ")"),
            tna = paste0(round(mean(third_next_avail, na.rm = T), 2), " (", 
                         round(sd(third_next_avail, na.rm = T), 2), ")"),
            obs_exp = paste0(round(mean(obs_exp_panel_ratio, na.rm = T), 2)," (",
                             round(sd(obs_exp_panel_ratio, na.rm = T), 2), ")"),
            male = paste0(round(mean(pct_male, na.rm = T), 2), " (", 
                          round(sd(pct_male, na.rm = T), 2), ")"),
            rural = paste0(round(mean(pct_rural, na.rm = T), 2), " (", 
                           round(sd(pct_rural, na.rm = T), 2), ")"),
            nosos = paste0(round(mean(nosos_risk_score, na.rm = T), 2), " (", 
                           round(sd(nosos_risk_score, na.rm = T), 2), ")"),
            adi = paste0(round(mean(adi_natRnk_avg, na.rm = T), 2), " (", 
                           round(sd(adi_natRnk_avg, na.rm = T), 2), ")"),
            fte = paste0(round(mean(team_pcp_ap_fte_total, na.rm = T), 2), " (", 
                           round(sd(team_pcp_ap_fte_total, na.rm = T), 2), ")"),
            uniques = paste0(round(mean(pcmm_count_fy_qtr, na.rm = T), 2), " (", 
                           round(sd(pcmm_count_fy_qtr, na.rm = T), 2), ")")) %>%
  pivot_longer(-crh_flag) %>%
  pivot_wider(names_from = crh_flag, values_from = value) 
#--
s_abbr_count2 <- analytic_df_preMatch %>% select(sta5a, s_abbr, crh_flag) %>%
  distinct() %>%
  mutate(s_abbr1 = case_when(
    str_detect(s_abbr, "CBOC") ~ "CBOC",
    str_detect(s_abbr, "VAMC|HCC") ~ "VAMC & HCC",
    TRUE ~ "OOS"
  )) %>%
  group_by(crh_flag, s_abbr1) %>%
  summarise(count = as.character(n())) %>%
  pivot_wider(names_from = crh_flag, values_from = count) %>%
  rename(name = s_abbr1)
#--
t_test_covars2 <- analytic_df_preMatch %>%
  select(crh_flag, 
         newPtWt = new_pc_pt_wt, 
         estPtWt = est_pc_pt_wt, 
         tna = third_next_avail, 
         obs_exp = obs_exp_panel_ratio,
         male = pct_male, 
         rural = pct_rural,
         nosos = nosos_risk_score,
         adi = adi_natRnk_avg,
         fte = team_pcp_ap_fte_total,
         uniques = pcmm_count_fy_qtr) %>%
  pivot_longer(-crh_flag) %>%
  group_by(name, crh_flag) %>%
  nest() %>%
  pivot_wider(names_from = crh_flag, values_from = data) %>%
  mutate(t_test = map2(`No PC CRH`, `PC CRH`, ~{t.test(.x$value, .y$value) %>% broom::tidy()}),
         `No PC CRH` = map(`No PC CRH`, nrow),
         `PC CRH` = map(`PC CRH`, nrow)) %>%
  unnest(cols = c(`No PC CRH`, `PC CRH`, t_test)) %>%
  select(name, p.value) %>%
  mutate(p.value = if_else(p.value < 0.001, "<0.001", 
                           as.character(round(p.value, 3))))
#
penRate2 <- dbGetQuery(oabi_con,
                      "select *
                      from [crh_eval].B1_crh_penRate") %>%
  mutate(crh_month = ymd(crh_month)) %>%
  inner_join(., sta5as_to_include) %>%
  filter(crh_month < ymd("2020-03-01")
         & crh_month > ymd("2018-09-01")) %>%
  rename(vssc_month = crh_month)
#--
crh_use <- sta5as_to_include %>%
  select(sta5a) %>%
  full_join(., dates %>% select(vssc_month), by = character()) %>%
  left_join(., penRate2) %>%
  mutate(crh_count_w_zero = replace_na(crh_encounter_count, 0)) %>%
  filter(is.na(crh_flag) == F) %>%
  group_by(crh_flag) %>%
  summarise(crh_encounter_sum = comma(sum(crh_encounter_count, na.rm = T)),
            months_w_gt9_pcCRH = comma(sum(case_when(
              crh_encounter_count > 9 ~ 1,
              TRUE ~ 0
            ))),
            pcCRH_per_month = paste0(round(mean(crh_count_w_zero, na.rm = T), 2), " (",
                                     round(sd(crh_count_w_zero, na.rm = T), 2), ")")) %>%
  pivot_longer(-crh_flag) %>%
  pivot_wider(names_from = crh_flag, values_from = value) %>%
  mutate(name2 = case_when(
    name == "crh_encounter_sum" ~ "Total PC CRH Encounters",
    name == "months_w_gt9_pcCRH" ~ "Total Facility-months with > 9 PC CRH Encounters",
    name == "pcCRH_per_month" ~ "Average (SD) PC CRH Encounters per Facility-month"
  )) %>%
  select(4, 2, 3) %>%
  mutate(p.value = "NA")
#--
covar_summary %>%
  left_join(., t_test_covars2) %>%
  bind_rows(s_abbr_count2) %>%
  mutate(p.value = replace_na(p.value, "NA")) %>%
  mutate(name2 = 
           case_when(
             name == "unique_sta5as" ~ "Number of Facilities",
             name == "obs_months" ~ "Months of Observation",
             name == "newPtWt" ~ "New Patient Wait Time",
             name == "estPtWt" ~ "Established Patient Wait Time",
             name == "tna" ~ "Third Next Available",
             name == "obs_exp" ~ "Observed:Expected Panel Size Ratio",
             name == "male" ~ "Male Patients (%)",
             name == "rural" ~ "Rural Patients (%)",
             name == "nosos" ~ "NOSOS",
             TRUE ~ name
           )) %>%
  select(5, 2, 3, 4) %>%
  bind_rows(crh_use) %>%
  kbl(col.names = c("", "PC CRH \nAvg (SD)",
                    "No PC CRH \nAvg (SD)",
                    "p-value for difference")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```

# Table 2
## Matched Pre-Post t-tests  
```{r}
# making un-matched sta5a lookup table
sta5as_w_crh_b4_feb20 <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == T) %>%
  select(sta5a) %>%
  pull
#
scrssn_count_exclusion <- scrssn_count %>% filter(scrssn_count_cat == "< 450") %>%
  select(sta5a) %>% pull
#
sta5as_wo_pcCRH <- crh_flag %>%
  filter(crh_10_flag == 0 & sta5a %ni% scrssn_count_exclusion) %>%
  select(sta5a) %>%
  pull
#
sta5as_to_include2 <- access_metrics %>%
  select(sta5a) %>% distinct %>%
  filter(sta5a %in% sta5as_w_crh_b4_feb20 | sta5a %in% sta5as_wo_pcCRH) %>%
  mutate(crh_flag = factor(if_else(sta5a %in% sta5as_w_crh_b4_feb20, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#-----
prePost_analytic_df <- analytic_df %>%
  mutate(period = factor(if_else(vssc_month < ymd("2019-10-01"),
                          "Pre-Implementation",
                          "Post-Implementation"),
                         ordered = TRUE,
                         levels = c("Pre-Implementation", "Post-Implementation")))
#===
paste0_fxn <- function(covariate){
  paste0(round(mean({{covariate}}, na.rm = T), 2), " (", 
                           round(sd({{covariate}}, na.rm = T), 2), ")")
}
#--
# prePost_analytic_df %>%
#   select(crh_flag, period, new_pc_pt_wt, est_pc_pt_wt, third_next_avail) %>%
#   pivot_longer(-c(crh_flag, period)) %>%
#   group_by(crh_flag, period, name) %>%
#   summarise(value2 = paste0_fxn(value))
#--
prePost_analytic_df %>%
  select(crh_flag, period, new_pc_pt_wt, est_pc_pt_wt, third_next_avail) %>%
  pivot_longer(-c(crh_flag, period)) %>%
  group_by(crh_flag, period, name) %>%
  nest() %>%
  pivot_wider(names_from = crh_flag, values_from = data) %>%
  mutate(t_test = map2(`No PC CRH`, `PC CRH`, ~{t.test(.x$value, .y$value) %>% broom::tidy()}),
         `No PC CRH` = map(`No PC CRH`, nrow),
         `PC CRH` = map(`PC CRH`, nrow)) %>%
  unnest(cols = c(`No PC CRH`, `PC CRH`, t_test)) %>%
  rename(est_diff = estimate,
         mean_no_CRH = estimate1,
         mean_CRH = estimate2) %>%
  select(period, name, est_diff, mean_no_CRH, mean_CRH, p.value) %>%
  mutate(
    name2 = case_when(
      name == "new_pc_pt_wt" ~ "NPWT",
      name == "est_pc_pt_wt" ~ "EPWT",
      TRUE ~ "TNA"
      ),
    name_disp = paste0(name2, " - ", period)
  ) %>%
  ungroup %>%
  mutate_if(is.numeric, comma, accuracy = 0.001) %>%
  select(name_disp, 4, 5, 3, 6) %>%
  kbl(col.names = c("Measure", "No PC CRH", "PC CRH", "Difference", "p-value")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```


# Table 3  
## Baseline Linear Trend Model  

```{r}
baselineLinearTrend_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "No PC CRH")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
#baselineLinearTrend_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
#baselineLinearTrend_df$treat <- relevel(analytic_df$treat, ref = 'No PC CRH')
```


```{r}
bline_trend1 <- lmer(est_pc_pt_wt ~ treat * post    
                     + time * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = baselineLinearTrend_df,
                     REML = TRUE)
#
bline_trend2 <- lmer(new_pc_pt_wt ~ treat * post    
                     + time * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = baselineLinearTrend_df,
                     REML = TRUE)
#
bline_trend3 <- lmer(third_next_avail ~ treat * post    
                     + time * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = baselineLinearTrend_df,
                     REML = TRUE)
#--
tab_model(bline_trend1, bline_trend2, bline_trend3,
          dv.labels = c("Established Pt WT", "New Pt WT", "3rd Next Available"),
          show.se = TRUE)
```


# Propensity Score Diagnostic Output  

```{r}
source(here("Input", "Analytic df", "F2_propensity_score_matching","ps_match_pre_covid.R"))
```

```{r}
ps_plot_df_pcmm <- tibble(
  covariate = attributes(summary(opt_match_pcmm_wVISN)$sum.all)$dimnames[[1]], 
  smd_matched = summary(opt_match_pcmm_wVISN)$sum.matched[,3], 
  smd_preMatch = summary(opt_match_pcmm_wVISN)$sum.all[,3]) %>%
  mutate(covariate = str_remove(covariate, "s_abbr2|census_division|pilot_visn_flag"),
         covariate = str_replace(covariate, "parent_visn", "V"),
         covar_lab = factor(case_when(
           covariate == "distance" ~ "Distance",
           #str_detect(covariate, "PCCBOC") == TRUE ~ "PCCBOC",
           str_detect(covariate, "HCC") == TRUE ~ "VAMC/HCC",
           #str_detect(covariate, "VAMC") == TRUE ~ "VAMC",
           #str_detect(covariate, "MSCBOC") == TRUE ~ "MSCBOC",
           str_detect(covariate, "CBOC") == TRUE ~ "CBOC",
           str_detect(covariate, "OOS") == TRUE ~ "OOS",
           str_detect(covariate, "nosos") == TRUE ~ "NOSOS",
           str_detect(covariate, "obs_exp") == TRUE ~ "Obs:Exp",
           str_detect(covariate, "team") == TRUE ~ "PCP/AP FTE",
           str_detect(covariate, "pcmm_") == TRUE ~ "PCMM ScrSSN Count",
           str_detect(covariate, "est_") == TRUE ~ "Established Patient WT",
           str_detect(covariate, "new_") == TRUE ~ "New Patient WT",
           str_detect(covariate, "third_") == TRUE ~ "Third-Next Available",
           str_detect(covariate, "adi") == TRUE ~ "ADI, Avg",
           str_detect(covariate, "age") == TRUE ~ "Age, Avg",
           str_detect(covariate, "male") == TRUE ~ "Male %",
           str_detect(covariate, "white") == TRUE ~ "White %",
           str_detect(covariate, "rural") == TRUE ~ "Rural %",
           str_detect(covariate, "gap") == TRUE ~ "Gap Metric",
           str_detect(covariate, "non_va") == TRUE ~ "Non-VA Consults per 10,000 in PCMM",
           TRUE ~ covariate
         ), ordered = TRUE, levels = rev(c("Distance","Not a Pilot VISN",
                                       "Pilot VISN","NOSOS","Obs:Exp","PCP/AP FTE",
                                       "PCMM ScrSSN Count", "Rural %", "ADI, Avg",
                                       "Non-VA Consults per 10,000 in PCMM",
                                       "Third-Next Available", "New Patient WT", 
                                       "Established Patient WT", "VAMC/HCC", "CBOC",
                                       "HCC", "VAMC", "OOS",
                                       "MSCBOC", "PCCBOC"
                                       #, "V01", "V02", "V04", "V05",
                                       #"V06", "V07", "V08", "V09", "V10", "V12", "V15",
                                       #"V16", "V17", "V19", "V20", "V21", "V22", "V23"
                                       )))) %>%
  select(-covariate) %>%
  pivot_longer(-covar_lab) %>%
  mutate(abs_smd = abs(value),
         name_lab = if_else(name == "smd_matched", "Matched", "Un-Matched")) %>%
  filter(is.na(covar_lab) == F)
#
ggplot(data = ps_plot_df_pcmm,
       aes(x = abs_smd, y = covar_lab, group = name_lab, fill = name_lab)) +
  geom_point(shape = 21,
             size = 2.25) +
  scale_fill_manual(values = c(
    "Matched" = "black",
    "Un-Matched" = "white"
  )) +
  labs(x = "Absolute Standardized Mean Difference") +
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept = 0, lty = 1) +
  geom_vline(xintercept = 0.05, lty = 2) +
  geom_vline(xintercept = 0.1, lty = 1)
```

# Outcome Plots  
```{r}
plot_fxn <- function(outcome, outcome_c){
  ylab <- if(outcome_c == "est_pc_pt_wt"){
    "Established Patient Wait Time (days)"
  }
  else if(outcome_c == "new_pc_pt_wt"){
    "New Patient Wait Time (days)"
  }
  else{
    "Third Next Available (days)"
  }

  ggplot(data = subset(baselineLinearTrend_df, third_next_avail < 50
                       & new_pc_pt_wt < 100),
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_line(linewidth = 0.75, alpha = 0.15) +
    geom_smooth(linewidth = 1.25, data = subset(baselineLinearTrend_df, 
                                                vssc_month < ymd("2019-10-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    geom_smooth(linewidth = 1.25, data = subset(baselineLinearTrend_df, 
                                                vssc_month > ymd("2019-09-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    ggsci::scale_color_aaas() +
    theme(axis.title.x = element_blank()) +
    labs(y = ylab)
}
#
```


 
```{r}
timepoints <- tibble(
  vssc_month = seq(ymd("2018-10-01"), ymd("2020-02-01"), "1 month")
) %>%
  rownames_to_column(var = "time") %>%
  mutate(time = as.numeric(time))
#
avg_values <- baselineLinearTrend_df %>%
  group_by(treat) %>%
  summarise(obs_exp_panel_ratio = mean(obs_exp_panel_ratio, na.rm = T),
            pct_male = mean(pct_male, na.rm = T),
            pct_rural = mean(pct_rural, na.rm = T)) %>%
  full_join(., timepoints, by = character()) %>%
  mutate(post = if_else(time > 12, "Post Intervention (i.e., FY20)", "Pre-Intervention (i.e., FY19)"))
#--------
cf_plot_fxn <- function(outcome, outcome2){
  y_lab <- if(outcome == "est_pc_pt_wt"){
    "EPWT (days)"
  }
  else if(outcome == "new_pc_pt_wt"){
    "NPWT (days)"
  }
  else{
    "TNA (days)"
  }
  #--
  yaxis_max <- if(outcome == "new_pc_pt_wt"){
    75
  }
  else if(outcome == "third_next_avail"){
    40
  }
  else{
    NA
  }
  #--
 lm_fml <- as.formula(paste0({{outcome}}, " ~ treat * post + time * treat + obs_exp_panel_ratio + pct_male + pct_rural")) 
  #
bline_trend_all <- lm(lm_fml,
                      data = baselineLinearTrend_df)
#
crh_all <- predict(bline_trend_all, avg_values %>%
                     filter(treat == "PC CRH")) %>%
  tibble(predicted = `.`) %>%
  rownames_to_column(var = "time") %>%
  mutate(time = as.numeric(time)) %>%
  left_join(timepoints)
#
noCrh_all <- predict(bline_trend_all, avg_values %>%
                       filter(treat == "No PC CRH")) %>%
  tibble(predicted = `.`) %>%
  rownames_to_column(var = "time") %>%
  mutate(time = as.numeric(time)) %>%
  left_join(timepoints)
#======
lm_fml2 <- as.formula(paste0({{outcome}}, " ~ treat + time * treat + obs_exp_panel_ratio + pct_male + pct_rural")) 
#
bline_trend_post <- lm(lm_fml2,
                       data = subset(baselineLinearTrend_df, time > 12))
#
crh_post <- predict(bline_trend_post, avg_values %>%
                      filter(treat == "PC CRH" & time > 12)) %>%
  tibble(predicted = `.`) %>%
  rownames_to_column(var = "time") %>%
  mutate(time = as.numeric(time) + 12) %>%
  left_join(timepoints)
#
noCrh_post <- predict(bline_trend_post, avg_values %>%
                        filter(treat == "No PC CRH" & time > 12)) %>%
  tibble(predicted = `.`) %>%
  rownames_to_column(var = "time") %>%
  mutate(time = as.numeric(time) + 12) %>%
  left_join(timepoints)
#--------------------
ggplot() +
  geom_line(data = subset(baselineLinearTrend_df, sta5a != "459GA"),
            aes(group = sta5a, x = vssc_month, y = {{outcome2}}),
            alpha = 0.2) +
  geom_line(data = subset(crh_all, time < 13),
            aes(x = vssc_month, y = predicted,
                color = "PC CRH"),
            linewidth = 1.25) +
  geom_line(data = crh_post,
            aes(x = vssc_month, y = predicted,
                color = "PC CRH"),
            linewidth = 1.25) +
  geom_line(data = subset(noCrh_all, time < 13),
            aes(x = vssc_month, y = predicted,
                color = "Matched Control"),
            linewidth = 1.25) +
  geom_line(data = noCrh_post,
            aes(x = vssc_month, y = predicted,
                color = "Matched Control"),
            linewidth = 1.25) +
  scale_color_manual(name = "",
                     values = c(`PC CRH` = "blue",
                                `Matched Control` = "red")) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.title.y = element_text(size = 25),
        legend.text = element_text(size = 20)) +
  labs(y = y_lab) +
  scale_y_continuous(limits = c(0, yaxis_max))
}

```



## All together  
```{r fig.width = 15, fig.height = 15}
multiplot(cf_plot_fxn("new_pc_pt_wt", new_pc_pt_wt) + theme(legend.position = "none"), 
          cf_plot_fxn("est_pc_pt_wt", est_pc_pt_wt) + theme(legend.position = "none"), 
          cf_plot_fxn("third_next_avail", third_next_avail))
```

