---
title: "% of New Patients Seen in 0-20 days: A closer look"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom",
             plot.title = element_text(size = 24))
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```



```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```


# Front Matter  

## Description of this report  

* We are considering a new access metric "% of new patients seen in 0-20 days"
* This document takes a closer look at the distributional qualities of this covariate
* Also, Peter asked what happens when a sta5a has 0 new patients ask for an appointment in a month

```{r}
apts_in_0_20 <- read_csv(here("Input", "Data", "VSSC", "Appointments - New 0-20",
                              "completed_new_0_20_month_sta5a.csv")) %>%
  rename_all(tolower) %>%
  rename(date = 1,
         div_name = 2,
         completed_in_0_20 = 3) %>%
  mutate(month_n = match(str_to_title(str_sub(date, end = 3)), month.abb),
         fy = as.numeric(str_sub(date, start = -2)),
         cy2 = if_else(month_n > 9, fy - 1, fy),
         cy = as.numeric(str_c("20", cy2)),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         sta5a = if_else(str_sub(div_name, start = 11, end = 11) == ")",
                         str_sub(div_name, start = 8, end = 10),
                         str_sub(div_name, start = 8, end = 12)))
#
appts_total <- read_csv(here("Input", "Data", "VSSC", "Appointments - New 0-20",
                              "completed_new_appointments_month_sta5a.csv")) %>%
  rename_all(tolower) %>%
  rename(date = 1,
         div_name = 2,
         new_pt_appt_reqs = 3) %>%
  mutate(month_n = match(str_to_title(str_sub(date, end = 3)), month.abb),
         fy = as.numeric(str_sub(date, start = -2)),
         cy2 = if_else(month_n > 9, fy - 1, fy),
         cy = as.numeric(str_c("20", cy2)),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         sta5a = if_else(str_sub(div_name, start = 11, end = 11) == ")",
                         str_sub(div_name, start = 8, end = 10),
                         str_sub(div_name, start = 8, end = 12)))
#--
new_0_20_days_create <- read_csv(here("Input", "Data", "VSSC", "Appointments - Completed Summary",
                                      "appt_cube_new_pt_pct_appts_0_20_days_create.csv")) %>%
  rename_all(tolower) %>%
  rename(date = 1,
         div_name = 2) %>%
  mutate(month_n = match(str_to_title(str_sub(date, end = 3)), month.abb),
         fy = as.numeric(str_sub(date, start = -2)),
         cy2 = if_else(month_n > 9, fy - 1, fy),
         cy = as.numeric(str_c("20", cy2)),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         sta5a = if_else(str_sub(div_name, start = 11, end = 11) == ")",
                         str_sub(div_name, start = 8, end = 10),
                         str_sub(div_name, start = 8, end = 12))) %>%
  select(vssc_month, sta5a, new_0_20_days_create = 3)
```

```{r}
appts_0_20_calc <- appts_total %>%
  left_join(., apts_in_0_20) %>%
  left_join(., new_0_20_days_create) %>%
  mutate(new_0_20_calc = completed_in_0_20 / new_pt_appt_reqs,
         calc_vssc_match = if_else((new_0_20_calc == new_0_20_days_create) |
                                     (is.na(new_0_20_calc) & is.na(new_0_20_days_create)), 
                                   T, F),
         calc_vssc_diff = new_0_20_calc - new_0_20_days_create)
```

```{r}
dates <- tibble(
  vssc_month = seq.Date(min(appts_0_20_calc$vssc_month), max(appts_0_20_calc$vssc_month), 
                        "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
```

# Calculating the Metric  

* When I download the components of this metric (i.e., __new patient appointments__ per month and __number of those seen in 0-20 days__) and calculate this metric "by hand" i get a total of `r sum(appts_0_20_calc$calc_vssc_match, na.rm = T) %>% comma()` out of `r nrow(appts_0_20_calc) %>% comma()` (`r (sum(appts_0_20_calc$calc_vssc_match, na.rm = T) / nrow(appts_0_20_calc)) %>% percent(accuracy = .1)`) observations match exactly

* The remaining `r (nrow(appts_0_20_calc) - sum(appts_0_20_calc$calc_vssc_match, na.rm = T)) %>% comma()` (`r ((nrow(appts_0_20_calc) - sum(appts_0_20_calc$calc_vssc_match, na.rm = T)) / nrow(appts_0_20_calc)) %>% percent(accuracy = 0.1)`) have an average difference of `r mean(appts_0_20_calc$calc_vssc_diff, na.rm = T) %>% percent(accuracy = 0.0001)`
    + Only `r appts_0_20_calc %>% filter(abs(calc_vssc_diff) > 0.01) %>% nrow()` (`r ((appts_0_20_calc %>% filter(abs(calc_vssc_diff) > 0.01) %>% nrow()) / nrow(appts_0_20_calc)) %>% percent(accuracy = 0.01)`) observations have a difference greater than +/- 1%


```{r}
ggplot(data = appts_0_20_calc,
       aes(x = calc_vssc_diff)) +
  stat_ecdf() +
  scale_y_continuous(labels = percent_format()) +
  scale_x_continuous(labels = percent_format()) +
  labs(y = "eCDF",
       x = "Difference")
#--
appts_0_20_calc %>%
  filter(calc_vssc_diff != 0) %>%
  ggplot(data = .,
         aes(x = calc_vssc_diff)) +
  geom_histogram(color = "black", fill = "seagreen") +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  labs(x = "Difference",
       y = "Observations",
       title = "Only observations with differences != 0")
```


# What happens when there are no new patient appointments?  
* So what happens when a sta5a has no new patient appointment requests?
* In that case there is no observation made: it is reported as missing
* The converse is also true: when a sta5a does have new patient appointment requests in a month but completes none of them they get a zero

## In VISN 2  
```{r}
sta5as_w_no_new_pt_reqs <- appts_0_20_calc %>%
  filter(new_pt_appt_reqs == 0) %>%
  select(sta5a) %>%
  distinct() %>%
  pull
#
new_0_20_days_create %>%
  left_join(., vast) %>%
  filter(sta5a %in% c("526GA", "526GB")) %>%
  ggplot(data = .,
       aes(y = new_0_20_days_create, x = vssc_month, group = short_name, color = short_name)) +
  geom_line(linewidth = 1) +
  geom_point(shape = 5, size = 1.5) +
  theme(legend.position = "right") +
  ggthemes::scale_color_colorblind() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(y = "New Patient Appointments Completed in 0-20 Days") +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  facet_wrap(~short_name)
```

## In VISN 23  
```{r}
#
new_0_20_days_create %>%
  left_join(., vast) %>%
  filter(sta5a %in% c("636GN", "636GJ")) %>%
  ggplot(data = .,
       aes(y = new_0_20_days_create, x = vssc_month, group = short_name, color = short_name)) +
  geom_line(linewidth = 1) +
  geom_point(shape = 5, size = 1.5) +
  theme(legend.position = "right") +
  ggthemes::scale_color_fivethirtyeight() +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(y = "New Patient Appointments Completed in 0-20 Days") +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  facet_wrap(~short_name)
```

# Characterization of the metric  

* The metric appears to be calculated as $\frac{\text{New Patient Appts. Seen in 0-20 days}}{\text{New Patient Appts. Requested}}$
* As a result it has some quirks:
    + Because the numerator can never be greater than the denominator, it cannot have values $>1.0$ or $<0.0$ 
    + Because new patients only represent about 5% of all patients seen, we see sta5a-months with zero $\text{New Patient Appts. Requested}$, which naturally leads to sta5a-months with missing observations
    + Finally, as a result of both the fact that only 1 in 20 patients is a new patient and that this metric is a proportion, there are peaks in the histogram at 0%, 50%, and 100%
    
```{r}
ggplot(data = appts_0_20_calc,
       aes(x = new_0_20_days_create)) +
  geom_histogram(bins = 100,
                 fill = "cornflowerblue",
                 color = "black") +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "% of New Patient Appointments Completed in 0-20 Days",
        y = "Observations")
```

* The overall average is `r mean(appts_0_20_calc$new_0_20_days_create, na.rm = T) %>% percent(accuracy = 0.1)` (SD = `r sd(appts_0_20_calc$new_0_20_days_create, na.rm = T) %>% percent(accuracy = 0.1)`)

```{r}
appts_0_20_calc %>%
  group_by(vssc_month) %>%
  summarise(total_requests = sum(new_pt_appt_reqs, na.rm = T),
            total_completed_in_0_20 = sum(completed_in_0_20, na.rm = T)) %>%
  mutate(prop_completed_in_0_20 = total_completed_in_0_20 / total_requests) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = prop_completed_in_0_20)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     limits = c(0, 1)) +
  labs(y = "Proportion of New Patient Reqs. Completed in 0-20 days") +
  theme(axis.title.x = element_blank())
```

### By Site Type  
```{r}
appts_0_20_calc %>%
  left_join(., vast) %>%
  filter(is.na(s_abbr) == F) %>%
  group_by(s_abbr) %>%
  summarise(mean_val = percent(mean(new_0_20_days_create, na.rm = T), accuracy = 0.1),
            sd_val = percent(sd(new_0_20_days_create, na.rm = T), accuracy = 0.1),
            qtl_25 = percent(quantile(new_0_20_days_create, 0.25, na.rm = TRUE), accuracy = 0.1),
            qtl_75 = percent(quantile(new_0_20_days_create, 0.75, na.rm = TRUE), accuracy = 0.1)) %>%
  mutate(mean_sd = paste0(mean_val, " (", sd_val, ")"),
         qrtls = paste0("[", qtl_25, ", ", qtl_75, "]")) %>%
  select(1, 6, 7) %>%
  kbl(col.names = c("Site Type", "Mean (SD)", "[25th %-ile, 75th %-ile]"),
      align = c("l", "c", "c")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```

```{r}
appts_0_20_calc %>%
  left_join(., vast) %>%
  filter(is.na(s_abbr) == F) %>%
  group_by(vssc_month, s_abbr) %>%
  summarise(total_requests = sum(new_pt_appt_reqs, na.rm = T),
            total_completed_in_0_20 = sum(completed_in_0_20, na.rm = T)) %>%
  mutate(prop_completed_in_0_20 = total_completed_in_0_20 / total_requests) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = prop_completed_in_0_20, color = s_abbr)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     limits = c(0, 1)) +
  labs(y = "Proportion of New Patient Reqs. Completed in 0-20 days") +
  theme(axis.title.x = element_blank(),
        legend.position = "right")
```

### By Uniques in PCMM  
```{r}
appts_0_20_calc %>%
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F) %>%
  group_by(scrssn_count_cat) %>%
  summarise(mean_val = percent(mean(new_0_20_days_create, na.rm = T), accuracy = 0.1),
            sd_val = percent(sd(new_0_20_days_create, na.rm = T), accuracy = 0.1),
            qtl_25 = percent(quantile(new_0_20_days_create, 0.25, na.rm = TRUE), accuracy = 0.1),
            qtl_75 = percent(quantile(new_0_20_days_create, 0.75, na.rm = TRUE), accuracy = 0.1)) %>%
  mutate(mean_sd = paste0(mean_val, " (", sd_val, ")"),
         qrtls = paste0("[", qtl_25, ", ", qtl_75, "]")) %>%
  select(1, 6, 7) %>%
  kbl(col.names = c("Site Type", "Mean (SD)", "[25th %-ile, 75th %-ile]"),
      align = c("l", "c", "c")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```



```{r}
appts_0_20_calc %>%
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F) %>%
  group_by(vssc_month, scrssn_count_cat) %>%
  summarise(total_requests = sum(new_pt_appt_reqs, na.rm = T),
            total_completed_in_0_20 = sum(completed_in_0_20, na.rm = T)) %>%
  mutate(prop_completed_in_0_20 = total_completed_in_0_20 / total_requests) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = prop_completed_in_0_20, color = scrssn_count_cat)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = percent_format(accuracy = 1),
                     limits = c(0, 1)) +
  labs(y = "Proportion of New Patient Reqs. Completed in 0-20 days") +
  theme(axis.title.x = element_blank(),
        legend.position = "right") +
  ggthemes::scale_color_wsj()
```

# As a binary: > 79% vs. < 80%  
```{r}
new_pt_0_20_binary <- appts_0_20_calc %>%
  mutate(new_0_20_gt79 = if_else(new_0_20_days_create > 0.79, TRUE, FALSE))
#
prop_gt_79pct_month <- new_pt_0_20_binary %>% 
  group_by(vssc_month) %>%
  summarise(number_gt_79 = sum(new_0_20_gt79, na.rm = T),
            number_total = n(),
            prop_gt_79 = number_gt_79 / number_total)
```

* On average `r mean(prop_gt_79pct_month$prop_gt_79, na.rm = T) %>% percent(accuracy = 0.1)` of sta5as see at least 80% of their new patient requests within 20 days
    + This is an average of `r mean(prop_gt_79pct_month$number_gt_79) %>% comma(., accuracy = 0.1)` sta5as out of an average total of `r mean(prop_gt_79pct_month$number_total) %>% comma(., accuracy = 0.1)` sta5as per month

```{r}
new_pt_0_20_binary %>% 
  group_by(vssc_month) %>%
  summarise(number_gt_79 = sum(new_0_20_gt79, na.rm = T),
            number_total = n(),
            prop_gt_79 = number_gt_79 / number_total) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = prop_gt_79)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, 1)) +
  labs(y = "Proportion of sta5as where measure is >79%") +
  theme(axis.title.x = element_blank())
```

## By Site Type  
```{r}
new_pt_0_20_binary %>% 
  left_join(., vast) %>%
  filter(is.na(s_abbr) == F) %>%
  group_by(vssc_month, s_abbr) %>%
  summarise(number_gt_79 = sum(new_0_20_gt79, na.rm = T),
            number_total = n(),
            prop_gt_79 = number_gt_79 / number_total) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = prop_gt_79, color = s_abbr)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, 1)) +
  labs(y = "Proportion of sta5as where measure is >79%") +
  theme(axis.title.x = element_blank(),
        legend.position = "right")

```

## By Uniques    
```{r}
new_pt_0_20_binary %>% 
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F) %>%
  group_by(vssc_month, scrssn_count_cat) %>%
  summarise(number_gt_79 = sum(new_0_20_gt79, na.rm = T),
            number_total = n(),
            prop_gt_79 = number_gt_79 / number_total) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = prop_gt_79, color = scrssn_count_cat)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, 1)) +
  labs(y = "Proportion of sta5as where measure is >79%") +
  theme(axis.title.x = element_blank(),
        legend.position = "right") +
  ggthemes::scale_color_gdocs()

```