---
title: "CITS - pre-COVID, with Matching, No Covariates"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(lmerTest)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v4_noVISN.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>% 
  filter(sta5a %in% crh_sta5as) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
      inner_join(., ps_matched, by = "sta5a") %>%# only PS matched pairs
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "No PC CRH")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup
#
analytic_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df$treat <- relevel(analytic_df$treat, ref = 'No PC CRH')
```

# Front Matter  

## Description of this report  

* This is a matched CITS analysis of PC CRH pre-COVID
    + There are no covariates

## Decision Points  

* After deciding to move ahead with __Propensity Score Model v4.0__ this is the first analysis
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + I am applying __Propensity Score v4.0__
    + PS model v4.0 consisted of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Site type (CBOC, VAMC/HCC, OOS)

* Description of analyses  
    + This analysis is a Comparative Interrupted Time Series without covariates
    + We will use a mixed-effects model __without REML__ 
    + We will allow random intercepts for sta5a
    + On the LHS of the model we have New Patient Wait Time, Established Patient Wait Time, and Third Next Available 
    + On the RHS of the model we have:
        + Treatment (PC CRH, No PC CRH)
        + Post Intervention (1/0)
        + An interaction between Treatment and Post


# New Patient Wait Time  

```{r}
ggplot(data = subset(analytic_df, new_pc_pt_wt < 100),
       aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  geom_smooth(data = subset(analytic_df, vssc_month < ymd("2019-10-01")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = treat, color = treat),
              inherit.aes = F,
              method = lm, se = F) +
  geom_smooth(data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
              aes(x = vssc_month, y = new_pc_pt_wt, group = treat, color = treat),
              inherit.aes = F,
              method = lm, se = F) +
  ggsci::scale_color_aaas() +
  theme(axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time (days)")
```

```{r}
bline_mean_1 <- lmer(new_pc_pt_wt ~ treat * post + (1|sta5a),
                     data = analytic_df,
                     REML = FALSE)
```

#### Residuals X Fitted Values  
```{r}
plot(bline_mean_1)
```

#### QQ Plot  
```{r}
qqnorm(resid(bline_mean_1))
```

#### Regular Standard Errors  
```{r}
tab_model(bline_mean_1,
          dv.labels = "New Patient Wait Time",
          show.se = TRUE)
```

#### Sandwiched Standard Errors  
```{r}
clubSandwich::coef_test(bline_mean_1, "CR1")
```

# Established Patient Wait Time  

```{r}
ggplot(data = analytic_df,
       aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  geom_smooth(data = subset(analytic_df, vssc_month < ymd("2019-10-01")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = treat, color = treat),
              inherit.aes = F,
              method = lm, se = F) +
  geom_smooth(data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
              aes(x = vssc_month, y = est_pc_pt_wt, group = treat, color = treat),
              inherit.aes = F,
              method = lm, se = F) +
  ggsci::scale_color_jco() +
  theme(axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time (days)")
```

```{r}
bline_mean_2 <- lmer(est_pc_pt_wt ~ treat * post + (1|sta5a),
                     data = analytic_df,
                     REML = FALSE)
```

#### Residuals X Fitted Values  
```{r}
plot(bline_mean_2)
```

#### QQ Plot  
```{r}
qqnorm(resid(bline_mean_2))
```

#### Regular Standard Errors  
```{r}
tab_model(bline_mean_2,
          dv.labels = "Established Patient Wait Time",
          show.se = TRUE)
```

#### Sandwiched Standard Errors  
```{r}
clubSandwich::coef_test(bline_mean_2, "CR1")
```

# Third Next Available  

```{r}
ggplot(data = subset(analytic_df, third_next_avail < 75),
       aes(x = vssc_month, y = third_next_avail, group = sta5a)) +
  geom_line(alpha = 0.3) +
  geom_smooth(data = subset(analytic_df, vssc_month < ymd("2019-10-01")),
              aes(x = vssc_month, y = third_next_avail, group = treat, color = treat),
              inherit.aes = F,
              method = lm, se = F) +
  geom_smooth(data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
              aes(x = vssc_month, y = third_next_avail, group = treat, color = treat),
              inherit.aes = F,
              method = lm, se = F) +
  ggsci::scale_color_aaas() +
  theme(axis.title.x = element_blank()) +
  labs(y = "Third Next Available (days)")
```

```{r}
bline_mean_3 <- lmer(third_next_avail ~ treat * post + (1|sta5a),
                     data = analytic_df,
                     REML = FALSE)
```

#### Residuals X Fitted Values  
```{r}
plot(bline_mean_3)
```

#### QQ Plot  
```{r}
qqnorm(resid(bline_mean_3))
```

#### Regular Standard Errors  
```{r}
tab_model(bline_mean_3,
          dv.labels = "Third Next Available",
          show.se = TRUE)
```

#### Sandwiched Standard Errors  
```{r}
clubSandwich::coef_test(bline_mean_3, "CR1")
```


# All Together  

```{r}
tab_model(bline_mean_1, bline_mean_2, bline_mean_3, show.se = TRUE, show.ci = FALSE)
```