---
title: "A Closer Look at Third Next Available"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_2.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PACT_CC].[econ].PatientPCP
#                             	where fy = 2018
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
      left_join(., vast %>% select(sta5a, s_abbr))
```

```{r}
ps_matched_5_1 <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_1_noCRH_among_controls.csv"))
#this is where exclusion criteria are applied:
sta5as_to_include2 <- ps_matched_5_1 %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df2 <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include2) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates)
```

# Front Matter  

## Description of this report  

* This is a closer look at __Third Next Available__ and trying to determine whether we can get a better propensity score match 

## Decision Points  

* Detail any specific questions being answered or decisions being made
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    + Propensity score matching restrictions (i.e., pairs, weights, none)
    + What else?
    
* Description of _Propensity Score_ matching
    + This report uses both __Propensity Score v5.1 and v5.2__


# TNA During FY19    

```{r}
dates <- tibble(
  vssc_month = seq.Date(ymd("2018-10-01"),
                  ymd("2020-02-01"),
                  "1 month")) %>%
  rownames_to_column(var = "time") %>%
  mutate(time = str_pad(time,
                        side = "left",
                        pad = "0",
                        width = 2))
#########
access_metrics_v5_1 <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  filter(vssc_month >= ymd("2018-10-01")
         & vssc_month <= ymd("2019-09-01")) %>%
  inner_join(., ps_matched_5_1) %>%
  mutate(crh_flag = if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "Control"),
         version = "v5.1")
#########
access_metrics_v5_2 <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  filter(vssc_month >= ymd("2018-10-01")
         & vssc_month <= ymd("2019-09-01")) %>%
  inner_join(., ps_matched) %>%
  mutate(crh_flag = if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "Control"),
         version = "v5.2")
```

## Mean Values per Month by Treated vs. Control   
```{r}
access_metrics_v5_1 %>%
  bind_rows(access_metrics_v5_2) %>%
  group_by(crh_flag, vssc_month, version) %>%
  summarise(mean_val = mean(third_next_avail, na.rm = T),
            sd_val = sd(third_next_avail, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, group = crh_flag, color = crh_flag,
             y = mean_val,
             ymin = mean_val - sd_val,
             ymax = mean_val + sd_val)) +
  geom_point(position = position_dodge(width = 1)) +
  geom_line() +
  geom_errorbar(position = position_dodge(width = 1)) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Mean +/- SD") +
  scale_y_continuous(limits = c(0, NA)) +
  facet_wrap(~version)
```

## As Violin Plots  
```{r}
access_metrics_v5_1 %>%
  bind_rows(access_metrics_v5_2) %>%
  select(vssc_month, third_next_avail, crh_flag, version) %>% 
  left_join(dates) %>%
  ggplot(data = .,
         aes(x = time, y = third_next_avail, fill = crh_flag, color = crh_flag)) +
  geom_jitter(alpha = 0.25) +
  geom_violin() +
  scale_y_continuous(limits = c(0, NA)) +
  labs(y = "Third Next Available (days)",
       x = "Month") +
  facet_wrap(~version)
```

## As Regression Lines    
```{r}
access_metrics_v5_1 %>%
  bind_rows(access_metrics_v5_2) %>%
  select(vssc_month, third_next_avail, crh_flag, version) %>% 
  left_join(dates) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = third_next_avail, color = crh_flag, group = crh_flag)) +
  geom_smooth(method = "lm",
              se = F) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(y = "Third Next Available (days)",
       x = "Month") +
  facet_wrap(~version)
```
