---
title: "Gap Metric: Removing CRH Contribution in Denominator"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             plot.title = element_text(size = 24),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0),
         s_abbr2 = case_when(str_detect(s_abbr, "CBOC") ~ "CBOC",
                             str_detect(s_abbr, "VAMC|HCC") ~ "VAMC/HCC",
                             s_abbr == "OOS" ~ "OOS")) %>%
  filter(drop_flag == 0
         & is.na(s_abbr2) == F) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well as 
  #flags for treated/control
  #PS matching weights
  #flags for meeting inclusion criteria in 3 periods
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv")) %>%
  rename(treated_ever = treated_num)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(tna_new_source = as.numeric(tna_new_source))
#making a time/date dataset
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time") %>%
  mutate(fy = if_else(month(vssc_month) > 9, year(vssc_month) + 1, year(vssc_month)),
         qtr = case_when(month(vssc_month) %in% c(10, 11, 12) ~ 1,
                         month(vssc_month) %in% c(1, 2, 3) ~ 2,
                         month(vssc_month) %in% c(4, 5, 6) ~ 3,
                         month(vssc_month) %in% c(7, 8, 9) ~ 4,
                         TRUE ~ 99))
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
#average age on october 1st 2022
age_sta5a_qtr <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].D1_age_sta5a_qtr")
#sta5a-fy-specific counts of gender, race, and urh, as well as total uniques
race_gender_urh <- dbGetQuery(oabi_con,
                              "select * from [OABI_MyVAAccess].[crh_eval].D2_race_gender_urh_count") %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100)
#sta5a-fy_qtr-specific average ADI and quartile counts, as well as total
adi_sta5a_fy <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].D3_adi_sta5a_fy")
#sta5a-month-specific average Nosos, Obs:Exp, and Team PCP/AP FTE
nosos_obs_exp_team_fte <- dbGetQuery(oabi_con,
                                     "select * from [OABI_MyVAAccess].[crh_eval].F1_2_vssc_covars") %>%
  mutate(vssc_month = ymd(vssc_month))
#sta5a-fy-specific average drive distance and time to closest PC site
drive_time <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].D4_avg_drive_time")
#sta5a-month-specific timely care success rate
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#sta5a-month-specific PC CRH penetration rate and it's components
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month),
         treated_month = if_else(crh_encounter_count > 9, 1, 0))#time-varying treated
#--
sta5as_to_start <- vast %>%
  left_join(., scrssn_count %>%
              select(sta5a, scrssn_count_cat)) %>%
  filter(s_abbr %in% c("PCCBOC", "MSCBOC", "HCC", "OOS", "VAMC")
         & scrssn_count_cat != "< 450") %>%
  select(sta5a)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_capped = if_else(gap_metric > 3, 3, gap_metric),
         gap2_capped = if_else(gap_metric2 > 3, 3, gap_metric2),
         gap_cat = factor(case_when(gap_metric < 1.0 ~ "< 1.0",
                                    gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
                                    gap_metric > 1.2 ~ "> 1.2",
                                     TRUE ~ "Missing"),
                          ordered = TRUE,
                          levels = c("< 1.0", "1.0 - 1.2", "> 1.2", "Missing")),
         gap_cat2 = factor(case_when(gap_metric2 < 1.0 ~ "< 1.0",
                                     gap_metric2 >= 1.0 & gap_metric2 <= 1.2 ~ "1.0 - 1.2",
                                     gap_metric2 > 1.2 ~ "> 1.2",
                                     TRUE ~ "Missing"),
                           ordered = TRUE,
                           levels = c("< 1.0", "1.0 - 1.2", "> 1.2", "Missing"))) %>%
  inner_join(., sta5as_to_start %>%
               cross_join(., dates %>%
                            select(vssc_month)),
             by = c("sta5a", "vssc_month"))
#
mean_gap <- gap_metric %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            mean_gap2 = mean(gap_metric2, na.rm = T)) %>%
  mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "< 1.0",
                                    mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0 - 1.2",
                                    mean_gap > 1.2 ~ "> 1.2",
                                     TRUE ~ "Missing"),
                          ordered = TRUE,
                          levels = c("< 1.0", "1.0 - 1.2", "> 1.2", "Missing")),
         gap_cat2 = factor(case_when(mean_gap2 < 1.0 ~ "< 1.0",
                                    mean_gap2 >= 1.0 & mean_gap2 <= 1.2 ~ "1.0 - 1.2",
                                    mean_gap2 > 1.2 ~ "> 1.2",
                                     TRUE ~ "Missing"),
                          ordered = TRUE,
                          levels = c("< 1.0", "1.0 - 1.2", "> 1.2", "Missing")))
```



# Front Matter  

## Description of this report  

* This is a comparison of 2 versions of the gap metric:

$$
\text{Gap Metric}_1 = \frac{(\text{Expected PS}_{total}-\text{Expected PS}_{CRH})}{\text{Observed PS}_{Total}- \text{Observed PS}_{CRH}}
$$

$$
\text{Gap Metric}_2 = \frac{(\text{Expected PS}_{total}-\text{Expected PS}_{CRH})}{\text{Observed PS}_{Total}}
$$

## Decision Points  

* Per our discussion on June 6th I am examining a version of the gap metric that doesn't correct for CRH panel size in the denominator

# Sta5a-Month  

* There are `r gap_metric %>% filter(gap_metric != gap_metric2) %>% nrow() %>% comma(., accuracy = 1)` (`r ((gap_metric %>% filter(gap_metric != gap_metric2) %>% nrow()) / nrow(gap_metric)) %>% percent(., accuracy = 0.1)`) observations where these 2 versions of the gap metric do not agree

```{r}
gap_metric %>%
  ggplot(data = .,
         aes(x = gap_capped, y = gap2_capped)) +
  geom_point() +
  ggpubr::stat_cor(p.accuracy = 0.001,
                   color = "red") +
  labs(x = "Gap Metric 1",
       y = "Gap Metric 2")
#
gap_tot_chisq <- gap_metric %>%
  tabyl(gap_cat, gap_cat2) %>%
  chisq.test()
#
gap_tot_chisq$observed %>%
  rownames_to_column() %>%
  select(-rowname) %>%
  as.data.frame() %>%
  janitor::adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~ comma(.x, accuracy = 1))) %>%
  kbl(col.names = c("Gap Metric 1", "< 1.0", "1.0 - 1.2", "> 1.2", "Missing", "Total"),
      align = c("c", rep("r", 5))) %>%
  kable_classic("striped") %>%
  add_header_above(c("", "Gap Metric 2" = 4, " "))
```


```{r}
diff_hist <- gap_metric %>%
  filter(gap_metric != gap_metric2) %>%
  mutate(difference = gap_metric - gap_metric2,
         diff_cap = if_else(difference > 2, 2, difference)) %>%
  ggplot(data = .,
         aes(x = diff_cap)) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_histogram(color = "black",
                 fill = "skyblue") +
  labs(x = "Gap Metric 1 - Gap Metric 2",
       y = "Observations")
#
diff_bp <-  gap_metric %>%
  filter(gap_metric != gap_metric2) %>%
  mutate(difference = gap_metric - gap_metric2,
         diff_cap = if_else(difference > 2, 2, difference)) %>%
  ggplot(data = .,
         aes(y = diff_cap)) +
  geom_boxplot(color = "black",
               fill = "seagreen") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Gap Metric 1 - Gap Metric 2")
#
cowplot::plot_grid(diff_hist, diff_bp, ncol = 2)
```


# Average Gap  

* There are `r mean_gap %>% filter(gap_cat != gap_cat2) %>% nrow()` (`r ((mean_gap %>% filter(gap_cat != gap_cat2) %>% nrow()) / nrow(sta5as_to_start)) %>% percent(., accuracy = 0.1)`) sta5as that do not fall into the same mean gap category using this new version of the gap metric 

```{r}
gap_chisq <- mean_gap %>%
  tabyl(gap_cat, gap_cat2) %>%
  chisq.test()
#
gap_chisq$observed %>%
  rownames_to_column() %>%
  select(-rowname) %>%
  as.data.frame() %>%
  janitor::adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~ comma(.x, accuracy = 1))) %>%
  kbl(col.names = c("Gap Metric 1", "< 1.0", "1.0 - 1.2", "> 1.2", "Missing", "Total"),
      align = c("c", rep("r", 5))) %>%
  kable_classic("striped") %>%
  add_header_above(c("", "Gap Metric 2" = 5))
```

    
