---
title: "CRH-Corrected Panel Fullness & Gap Metric"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
#--
sta5as_to_start <- vast %>%
  left_join(., scrssn_count %>%
              select(sta5a, scrssn_count_cat)) %>%
  filter(s_abbr %in% c("PCCBOC", "MSCBOC", "HCC", "OOS", "VAMC")
         & scrssn_count_cat != "< 450") %>%
  select(sta5a)
#-------
gap_metric_2 <- dbGetQuery(oabi_con,
                           "select distinct *
                           from [PACT_CC].[CRH].[vw_gapMetric]
                           where fy > 2020") %>%
  mutate(gap_month = ymd(str_c(cy, mth_num, "01", sep = "-"))) %>%
  mutate(across(contains("PanelSize"), ~as.numeric(.x)),
         expectedPanelSize_CRH_0 = replace_na(expectedPanelSize_CRH, 0),
         observedPanelSize_CRH_0 = replace_na(observedPanelSize_CRH, 0),
         expectedPanelSize_total = expectedPanelSize_AllTeamTypes - expectedPanelSize_CRH_0,
         observedPanelSize_total = observedPanelSize_AllTeamTypes - observedPanelSize_CRH_0,
         panel_fullness = observedPanelSize_AllTeamTypes / (expectedPanelSize_total),#unadjusted numerator / crh-adjusted denominator
         pf_pct = panel_fullness * 100) %>%
  right_join(., sta5as_to_start %>%
               rename(sta6a = sta5a) %>%
               cross_join(., dates %>%
                            select(gap_month = vssc_month)))
```

# Front Matter  

## Description of this report  

* This document looks at the gap metric as executed by Jorge, as well as the relationship between the gap metric and panel fullness


    

```{r}

#--
analytic_df <- sta5as_to_start %>%
  cross_join(., dates %>%
               select(vssc_month)) %>%
  left_join(., gap_metric %>%
              mutate(pf_1_calc = observed_panel_size / expected_ps_tot,#unadjusted numerator / crh-adjusted denominator
                     pf_1_pct = pf_1_calc * 100) %>%
              select(sta5a, vssc_month, gap_metric_1 = gap_metric, pf_1_calc, pf_1_pct)) %>%
  left_join(., gap_metric_2 %>%
              mutate(gap_metric_2 = expectedPanelSize_total / observedPanelSize_total) %>%
              select(sta5a = sta6a, vssc_month = gap_month,
                     pf_2_calc = panel_fullness, pf_2_pct = pf_pct,
                     gap_metric_2)) %>%
  left_join (., access_metrics %>%
               select(sta5a, vssc_month, panel_fullness_vssc = panel_fullness)) %>%
  mutate(match_flag = if_else(round(gap_metric_1, 3) == gap_metric_2, 1, 0),
         match_diff = gap_metric_1 - gap_metric_2) %>%
  distinct()
```

# Gap Metric  

$$
\text{Gap Metric}_{\text{CRH-Corrected}}=\frac{(\text{Expected PS}_{total}-\text{Expected PS}_{CRH})}{(\text{Observed PS}_{total}-\text{Observed PS}_{CRH})}
$$


* The plots below have `r analytic_df %>% filter(gap_metric_1 > 3 | gap_metric_2 > 3) %>% nrow()` (`r ((analytic_df %>% filter(gap_metric_1 > 3 | gap_metric_2 > 3) %>% nrow()) / nrow(analytic_df)) %>% percent(., accuracy = 0.01)`) observations with a gap metric > 3 removed

```{r}
library(magrittr)
#analytic_df %$% cor(gap_metric_1, gap_metric_2,use = "complete.obs")
analytic_df %>%
  filter(gap_metric_1 < 3
         & gap_metric_2 < 3) %>%
  ggplot(data = .,
         aes(x = gap_metric_1, y = gap_metric_2)) +
  geom_point(alpha = 0.45) +
  ggpubr::stat_cor(label.y = 4, label.x = 0.5,
                   p.accuracy = 0.001,
                   color = "red") +
  labs(x = "Gap Metric - Bjarni",
       y = "Gap Metric - Jorge")
#--
bp_gap <- analytic_df %>%
  filter(gap_metric_1 < 3
         & gap_metric_2 < 3) %>%
  select(sta5a, gap_metric_1, gap_metric_2) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = if_else(name == "gap_metric_1", "Bjarni", "Jorge")) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  geom_hline(yintercept = 1.2, lty = 3) +
  labs(y = "Gap Metric")
#
de_gap <- 
  analytic_df %>%
  filter(gap_metric_1 < 3
         & gap_metric_2 < 3) %>%
  select(sta5a, gap_metric_1, gap_metric_2) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = if_else(name == "gap_metric_1", "Bjarni", "Jorge")) %>%
  ggplot(data = .,
         aes(x = value, fill = name_lab)) +
  geom_histogram(position = "dodge2",
                 bins = 50) +
  scale_y_continuous(labels = comma_format()) +
  geom_vline(xintercept = 1.2, lty = 3) +
  labs(y = "Observations",
       x = "Gap Metric")
#--
cowplot::plot_grid(bp_gap, de_gap, ncol = 2)
```

# Panel Fullness   

$$
\text{Panel Fullness}_{\text{CRH-Corrected}}=\frac{\text{Observed PS}_{total}}{(\text{Expected PS}_{total}-\text{Expected PS}_{CRH})}\times 100
$$


* The plots below have `r analytic_df %>% filter(pf_1_calc > 2 | pf_2_calc > 2) %>% nrow()` (`r ((analytic_df %>% filter(pf_1_calc > 2 | pf_2_calc > 2) %>% nrow()) / nrow(analytic_df)) %>% percent(., accuracy = 0.01)`) observations with a panel fullness > 200% removed


```{r}
analytic_df %>%
  filter(pf_1_calc < 2
         & pf_2_calc < 2) %>%
  ggplot(data = .,
         aes(x = pf_2_calc, y = pf_1_calc)) +
  geom_smooth(method = "lm",
              se = F) +
  geom_point(alpha = 0.45) +
  ggpubr::stat_cor(label.y = 1.75, label.x = 0.125,
                   p.accuracy = 0.001,
                   color = "red") +
  scale_y_continuous(labels = percent_format()) +
  scale_x_continuous(labels = percent_format())+
  labs(x = "Panel Fullness - Jorge",
       y = "Panel Fullness - Bjarni")
#----

#--
bp_pf <- analytic_df %>%
  filter(pf_1_calc < 2
         & pf_2_calc < 2) %>%
  select(sta5a, pf_1_calc, pf_2_calc) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = if_else(name == "pf_1_calc", "Bjarni", "Jorge")) %>%
  ggplot(data = .,
         aes(x = name_lab, y = value, fill = name_lab)) +
  geom_boxplot() +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "Panel Fullness")
#
de_pf <- 
  analytic_df %>%
  filter(pf_1_calc < 2
         & pf_2_calc < 2) %>%
  select(sta5a, pf_1_calc, pf_2_calc) %>%
  pivot_longer(-sta5a) %>%
  mutate(name_lab = if_else(name == "pf_1_calc", "Bjarni", "Jorge")) %>%
  ggplot(data = .,
         aes(x = value, fill = name_lab)) +
  geom_histogram(position = "dodge2",
                 bins = 50) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(labels = percent_format()) +
  labs(y = "Observations",
       x = "Panel Fullness")
#--
cowplot::plot_grid(bp_pf, de_pf, ncol = 2)
```


# Where are the differences?  


```{r}
obs_comp_df <- sta5as_to_start %>%
  cross_join(., dates %>%
               select(vssc_month)) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, obs_ps_1 = observed_panel_size, observedPanelSize_CRH_1 = observed_panel_size_crh)) %>%
  left_join(., gap_metric_2 %>%
              select(sta5a = sta6a, vssc_month = gap_month, obs_ps_2 = observedPanelSize_AllTeamTypes,
                     observedPanelSize_CRH_2 = observedPanelSize_CRH)) %>%
  mutate(observedPanelSize_CRH_diff = (observedPanelSize_CRH_1 - observedPanelSize_CRH_2),
         observedPanelSize_CRH_diff_0 = replace_na(observedPanelSize_CRH_diff, 0),
         mismatch = if_else(observedPanelSize_CRH_1 != observedPanelSize_CRH_2, 1, 0),
         max_val = case_when(observedPanelSize_CRH_diff_0 == 0 ~ NA,
                             observedPanelSize_CRH_1 > observedPanelSize_CRH_2 ~ observedPanelSize_CRH_1,
                             observedPanelSize_CRH_1 < observedPanelSize_CRH_2 ~ observedPanelSize_CRH_2),
         diff_prop_max = observedPanelSize_CRH_diff / max_val)
```

* There are `r obs_comp_df %>% filter(mismatch == 1) %>% nrow()` (`r (((obs_comp_df %>% filter(mismatch == 1) %>% nrow())) / nrow(analytic_df)) %>% percent(., accuracy = 0.1)`) observations where these two sources of __observed CRH panel size__ do not agree

```{r}
# obs_comp_df %>%
#   ggplot(data = .,
#          aes(x = obs_ps_1, y = obs_ps_2)) +
#   geom_point() +
#   ggpubr::stat_cor(p.accuracy = 0.001,
#                    color = "red") +
#   scale_y_continuous(labels = comma_format()) +
#   scale_x_continuous(labels = comma_format()) +
#   labs(y = "Observed Panel Size - Bjarni",
#        x = "Observed Panel Size - Jorge")
#===
obs_comp_df %>%
  ggplot(data = .,
         aes(x = observedPanelSize_CRH_1, y = observedPanelSize_CRH_2)) +
  geom_smooth(method = "lm",
              se = F) +
  geom_point() +
  ggpubr::stat_cor(p.accuracy = 0.001,
                   color = "red") +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(labels = comma_format()) +
  labs(y = "Observed CRH Panel Size - Bjarni",
       x = "Observed CRH Panel Size - Jorge")
#
obs_visn_lm <- obs_comp_df %>%
  left_join(., vast %>%
              select(sta5a, parent_visn)) %>%
  mutate(parent_visn = relevel(factor(parent_visn, ordered = F), ref = "09")) %>%
  lm(data = .,
     observedPanelSize_CRH_diff ~ parent_visn)
#--
#tab_model(obs_visn_lm)
#lm(observedPanelSize_CRH_1 ~ observedPanelSize_CRH_2, data = obs_comp_df) %>% tab_model()
```

```{r}
exp_comp_df <- sta5as_to_start %>%
  cross_join(., dates %>%
               select(vssc_month)) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, exp_ps_1 = expected_panel_size, expectedPanelSize_CRH_1 = expected_panel_size_crh)) %>%
  left_join(., gap_metric_2 %>%
              select(sta5a = sta6a, vssc_month = gap_month, exp_ps_2 = expectedPanelSize_AllTeamTypes,
                     expectedPanelSize_CRH_2 = expectedPanelSize_CRH))%>%
  mutate(expectedPanelSize_CRH_diff = (expectedPanelSize_CRH_1 - expectedPanelSize_CRH_2),
         expectedPanelSize_CRH_diff_0 = replace_na(expectedPanelSize_CRH_diff, 0),
         mismatch = if_else(expectedPanelSize_CRH_1 != expectedPanelSize_CRH_2, 1, 0),
         max_val = case_when(expectedPanelSize_CRH_diff_0 == 0 ~ NA,
                             expectedPanelSize_CRH_1 > expectedPanelSize_CRH_2 ~ expectedPanelSize_CRH_1,
                             expectedPanelSize_CRH_1 < expectedPanelSize_CRH_2 ~ expectedPanelSize_CRH_2),
         diff_prop_max = expectedPanelSize_CRH_diff / max_val)
```


* There are `r exp_comp_df %>% filter(mismatch == 1) %>% nrow()` (`r (((exp_comp_df %>% filter(mismatch == 1) %>% nrow())) / nrow(analytic_df)) %>% percent(., accuracy = 0.1)`) observations where these two sources of __expected CRH panel size__ do not agree

```{r}
# exp_comp_df %>%
#   ggplot(data = .,
#          aes(x = exp_ps_1, y = exp_ps_2)) +
#   geom_point() +
#   ggpubr::stat_cor(p.accuracy = 0.001,
#                    color = "red") +
#   scale_y_continuous(labels = comma_format()) +
#   scale_x_continuous(labels = comma_format()) +
#   labs(y = "Expected Panel Size - Bjarni",
#        x = "Expected Panel Size - Jorge")
#===
exp_comp_df %>%
  ggplot(data = .,
         aes(x = expectedPanelSize_CRH_1, y = expectedPanelSize_CRH_2)) +
  geom_point() +
  ggpubr::stat_cor(p.accuracy = 0.001,
                   color = "red") +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(labels = comma_format()) +
  labs(y = "Expected CRH Panel Size - Bjarni",
       x = "Expected CRH Panel Size - Jorge")
```