---
title: "PC CRH Description: Pre-COVID"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(s_abbr2 = case_when(
    s_abbr %in% c("PCCBOC", "MSCBOC") ~ "CBOC",
    s_abbr %in% c("VAMC", "HCC") ~ "VAMC/HCC",
    s_abbr == "OOS" ~ "OOS",
    TRUE ~ "Uh-oh!"
  ),
  urh2 = if_else(urh_vast %in% c("R", "H"), "Rural", "Urban"))
#-------
sta5a_demog_no_missing <- read_csv(here("Input", "Data", "sta5a_demog_no_missing.csv"))
#propensity score matched sta5as
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_pre_covid.csv"))
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month),
         tna_new_source = as.numeric(tna_new_source))
#--
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [OABI_MyVAAccess].[crh_eval].C1_crh_flag")
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2018-10-01"), ymd("2020-02-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_black = race_black_count / scrssn_count * 100,
         pct_other = race_other_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(-pc_encounter_total)
#--------
pc_encounters <- dbGetQuery(oabi_con,
                            "select *
                            from [OABI_MyVAAccess].[crh_eval].A1_pc_enc_scrssn_count") %>%
  mutate(visitMonth = ymd(visitMonth))
#-----
pc_cons <- dbGetQuery(oabi_con,
                      "with CTE as(
select count(*) as total_cons, actyMonth, sum(non_va) as non_va_cons, sta6a, fy, qtr
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where stopCode_group = 'Primary Care'
group by Sta6a, actyMonth, fy, qtr),
cte2 as(
	select count(*) as pcmm_scrssn_count, sta5a, fy, qtr
	from [PACT_CC].[econ].PatientPCP
	where fy > 2016 AND fy < 2021
	group by sta5a, fy, qtr
)
select a.sta6a, actyMonth, tot_cons = cast(total_cons as float), non_va_cons = cast(non_va_cons as float), 
			non_va_cons_rate_per_10k_pcmm = (cast(non_va_cons as float) / cast(pcmm_scrssn_count as float)) * 10000
from CTE as a
left join cte2 as b
	on a.Sta6a = b.Sta5a
		and a.fy = b.FY
		and a.qtr = b.QTR") %>%
  mutate(actyMonth = ymd(actyMonth))
#--------
pen_rate <- dbGetQuery(oabi_con,
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate")
#-------
crh_counts <- dbGetQuery(oabi_con,
                         "
          with CTE as(
          	select *
          		, DATEFROMPARTS(year(visitdate), month(visitdate), '01') as crh_month
          	from [PACT_CC].[CRH].C_crh_utilization_final
          	where care_type = 'Primary Care'
          )
          select count(*) as pc_crh_enc_count
          	, count(distinct scrssn) as pc_crh_scrssn_count
          	, sta5a = spoke_sta5a_combined_cdw
          from cte
          where crh_month > cast('2018-09-01' as date)
          	and crh_month < cast('2020-03-01' as date)
          group by spoke_sta5a_combined_cdw")
```

```{r}
# a vector of sta5as meeting our pc crh criteria
matched_treated <- ps_matched %>%
  filter(at_least_10_pc_crh_flag == 1) %>%
  select(sta5a) %>%
  pull
#--
matched_control <- ps_matched %>%
  filter(at_least_10_pc_crh_flag == 0) %>%
  select(sta5a) %>%
  pull
#--
unMatched_treated <- sta5a_demog_no_missing %>%
  filter(at_least_10_pc_crh_flag == T) %>%
  select(sta5a) %>%
  pull
#--
all_control <- sta5a_demog_no_missing %>%
  filter(at_least_10_pc_crh_flag == F) %>%
  select(sta5a) %>%
  pull
#--
zeroCrh_control <- sta5a_demog_no_missing %>%
  select(-not_enough_crh_before_march_20) %>%
  left_join(., crh_flag) %>%
  filter(at_least_10_pc_crh_flag == F
         & not_enough_crh_before_march_20 == F) %>%
  select(sta5a) %>%
  pull
```

```{r}
table1_df <- covariates %>%
  select(-c(est_pc_pt_wt, new_pc_pt_wt, third_next_avail)) %>%
  filter(vssc_month > ymd("2018-06-01")
         & vssc_month < ymd("2020-03-01")) %>%#restrict to our timeframe
  left_join(., dates) %>%
  left_join(., scrssn_count) %>%
  left_join(., access_metrics) %>%
  left_join(., pc_cons, by = c("sta5a" = "sta6a", "vssc_month" = "actyMonth")) %>%
  left_join(., pc_encounters, by = c("sta5a" = "Sta6a", "vssc_month" = "visitMonth")) %>%
  mutate(unMatched_vs_allEligible = case_when(sta5a %in% unMatched_treated ~ "Treated",
                                              sta5a %in% all_control ~ "Control"),
         unMatched_vs_zeroControl = case_when(sta5a %in% unMatched_treated ~ "Treated",
                                              sta5a %in% zeroCrh_control ~ "Control"),
         matched_vs_allEligible = case_when(sta5a %in% matched_treated ~ "Treated",
                                              sta5a %in% all_control ~ "Control"),
         matched_vs_zeroControl = case_when(sta5a %in% matched_treated ~ "Treated",
                                              sta5a %in% zeroCrh_control ~ "Control"),
         matched = case_when(sta5a %in% matched_treated ~ "Treated",
                                              sta5a %in% matched_control ~ "Control"),
         non_va_cons_rate_per_10k_pcmm = replace_na(non_va_cons_rate_per_10k_pcmm, 0))
```

```{r}
analytic_df <- covariates %>%
  rename(scrssn_count_covars = scrssn_count) %>%
  select(-c(est_pc_pt_wt, new_pc_pt_wt, third_next_avail)) %>%
  filter(vssc_month > ymd("2019-09-01")
         & vssc_month < ymd("2020-03-01")) %>%
  left_join(., access_metrics) %>%
  left_join(., pc_cons, by = c("sta5a" = "sta6a", "vssc_month" = "actyMonth")) %>%
  left_join(., pc_encounters %>% select(-c(fy, qtr)), 
            by = c("sta5a" = "Sta6a", "vssc_month" = "visitMonth")) %>%
  mutate(unMatched_vs_allEligible = case_when(sta5a %in% unMatched_treated ~ "Treated",
                                              sta5a %in% all_control ~ "Control"),
         unMatched_vs_zeroControl = case_when(sta5a %in% unMatched_treated ~ "Treated",
                                              sta5a %in% zeroCrh_control ~ "Control"),
         matched_vs_allEligible = case_when(sta5a %in% matched_treated ~ "Treated",
                                            sta5a %in% all_control ~ "Control"),
         matched_vs_zeroControl = case_when(sta5a %in% matched_treated ~ "Treated",
                                            sta5a %in% zeroCrh_control ~ "Control"),
         matched = case_when(sta5a %in% matched_treated ~ "Treated",
                             sta5a %in% matched_control ~ "Control"),
         non_va_cons_rate_per_10k_pcmm = replace_na(non_va_cons_rate_per_10k_pcmm, 0))
```


# Front Matter  

## Description of this report  

* This is a collection of tables describing the sta5as and patients engaged with PC CRH 

## Decision Points  

* Per our discussion on August 23rd I am putting these tables together for the pre-COVID PC CRH manuscript
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a) %>% n_distinct()` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses the pre-COVID PS matching model
    + This model consists of: 
        + Outcomes matched on their average values over FY19
        + Exact match on site type (CBOC, VAMC/HCC, OOS) and VISN
        + "Optimally" matched on FY18 Q4 average values of PCMM uniques, Obs:Exp panel size ratio, proportion rural, non-VA consults per 10,000 in PCMM


# Table 1  

```{r}
table_fxn <- function(group_column, period){
  table_df <- if(period == "clinic"){
    table1_df %>% 
      filter(vssc_month >= ymd("2018-07-01") & vssc_month <= ymd("2018-09-01")) %>%
    select(sta5a, {{group_column}},
           pc_encounter_total, 
           pcmm_count_fy_qtr, 
           obs_exp_panel_ratio,
           team_pcp_ap_fte_total,
           non_va_cons_rate_per_10k_pcmm,
           nosos_risk_score,
           adi_natRnk_avg,
           pct_rural)
  }
  else if(period == "outcome"){
    table1_df %>% 
      filter(vssc_month >= ymd("2018-10-01") & vssc_month <= ymd("2019-09-01")) %>%
    select(sta5a, {{group_column}},
           est_pc_pt_wt_pid,
           new_pc_pt_wt_create,
           third_next_avail)
  }
  else {table1_df}
  #
  table_df %>%
    filter(is.na({{group_column}}) == F) %>%
    pivot_longer(-c(sta5a, {{group_column}})) %>%
    group_by({{group_column}}, name) %>%
    nest() %>%
    pivot_wider(names_from = {{group_column}}, values_from = data) %>%
    mutate(t_test = map2(`Control`, `Treated`, ~{t.test(.x$value, .y$value) %>% broom::tidy()}),
           control_nrow = map(`Control`, ~{sum(!is.na(.x$value))}),
           treated_nrow = map(`Treated`, ~{sum(!is.na(.x$value))}),
           control_sd = map(`Control`, ~sd(.x$value, na.rm = T)),
           treated_sd = map(`Treated`, ~sd(.x$value, na.rm = T))) %>%
    unnest(cols = c(control_nrow, treated_nrow, t_test, control_sd, treated_sd)) %>%
    ungroup() %>%
    mutate(control_estimate = paste0(
      comma(estimate1, accuracy = 0.01), " (", comma(control_sd, accuracy = 0.01), ")"
    ),
    treated_estimate = paste0(
      comma(estimate2, accuracy = 0.01), " (", comma(treated_sd, accuracy = 0.01), ")"
    ),
    across(contains("nrow"), comma)) %>%
    select(name, control_nrow, treated_nrow, treated_estimate, control_estimate, estimate, p.value) %>%
    mutate(p.value = if_else(p.value < 0.001, "<0.001",
                             comma(p.value, accuracy = 0.001)),
           estimate = comma(estimate, accuracy = 0.01)) %>%
    kbl(col.names = c("", "Control Obs.", "Treated Obs.", "Treated Mean (SD)", "Control Mean (SD)", 
                      "Difference", "p-value for Difference"),
        align = c("l", rep("r", 5))) %>%
    kable_classic("striped") %>%
    row_spec(0, bold = T)
}
#
```

## Un-Matched Treated Clinics vs. All Eligible Clinics  

* There are `r analytic_df %>% filter(unMatched_vs_allEligible == "Control") %>% select(sta5a) %>% n_distinct()` "Control" sta5as
* There are `r analytic_df %>% filter(unMatched_vs_allEligible == "Treated") %>% select(sta5a) %>% n_distinct()` "Treated" sta5as

```{r}
analytic_df %>%
  filter(is.na(unMatched_vs_allEligible) == F) %>%
  group_by(unMatched_vs_allEligible) %>%
  summarise(total_pc_visits = comma(sum(pc_encounter_total, na.rm = T))) %>%
  pivot_wider(names_from = unMatched_vs_allEligible, values_from = total_pc_visits) %>%
  mutate(col1 = "Total PC Encounters") %>%
  select(3, 1, 2) %>%
  kbl(col.names = c("", "Control", "Un-Matched Treated"),
      align = c("c", "r", "r")) %>%
  kable_classic(full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
table_fxn(unMatched_vs_allEligible, "clinic")
```

```{r}
table_fxn(unMatched_vs_allEligible, "outcome")
```



## Un-Matched Treated Clinics vs. Control Clinics With Zero PC CRH    

* There are `r analytic_df %>% filter(unMatched_vs_zeroControl == "Control") %>% select(sta5a) %>% n_distinct()` "Control" sta5as
* There are `r analytic_df %>% filter(unMatched_vs_zeroControl == "Treated") %>% select(sta5a) %>% n_distinct()` "Treated" sta5as

```{r}
analytic_df %>%
  filter(is.na(unMatched_vs_zeroControl) == F) %>%
  group_by(unMatched_vs_zeroControl) %>%
  summarise(total_pc_visits = comma(sum(pc_encounter_total, na.rm = T))) %>%
  pivot_wider(names_from = unMatched_vs_zeroControl, values_from = total_pc_visits) %>%
  mutate(col1 = "Total PC Encounters") %>%
  select(3, 1, 2) %>%
  kbl(col.names = c("", "Control", "Un-Matched Treated"),
      align = c("c", "r", "r")) %>%
  kable_classic(full_width = F) %>%
  row_spec(0, bold = T)
```


```{r}
table_fxn(unMatched_vs_zeroControl, "clinic")
```

```{r}
table_fxn(unMatched_vs_zeroControl, "outcome")
```

## Matched Clinics      

* There are `r analytic_df %>% filter(matched == "Control") %>% select(sta5a) %>% n_distinct()` "Control" sta5as
* There are `r analytic_df %>% filter(matched == "Treated") %>% select(sta5a) %>% n_distinct()` "Treated" sta5as

```{r}
analytic_df %>%
  filter(is.na(matched) == F) %>%
  group_by(matched) %>%
  summarise(total_pc_visits = comma(sum(pc_encounter_total, na.rm = T))) %>%
  pivot_wider(names_from = matched, values_from = total_pc_visits) %>%
  mutate(col1 = "Total PC Encounters") %>%
  select(3, 1, 2) %>%
  kbl(col.names = c("", "Control", "Treated"),
      align = c("c", "r", "r")) %>%
  kable_classic(full_width = F) %>%
  row_spec(0, bold = T)
```


```{r}
table_fxn(matched, "clinic")
```

```{r}
table_fxn(matched, "outcome")
```

# Table 2  

```{r}
table2_1_fxn <- function(group_var, is_crh){
  if({{is_crh}} == T){
    crh_counts %>% filter(sta5a %in% matched_treated) %>%
      rename(pc_encounter_total = pc_crh_enc_count,
             scrssn_count = pc_crh_scrssn_count) %>%
      summarise(encounter_count = sum(pc_encounter_total),
                scrssn_count = sum(scrssn_count)) %>%
      mutate(pc_per_unique = encounter_count / scrssn_count,
             foo = "foo") %>%
      pivot_longer(-foo) %>%
      select(-foo) %>%
      mutate(value = comma(value, accuracy = 0.01)) %>%
      rename("{{group_var}}_crh" := value)
  }
  else {
    pc_encounters %>%
      filter(visitMonth > ymd("2018-09-01") & visitMonth < ymd("2020-03-01")
             & Sta6a %in% {{group_var}}) %>%
      summarise(encounter_count = sum(pc_encounter_total),
                scrssn_count = sum(scrssn_count)) %>%
      mutate(pc_per_unique = encounter_count / scrssn_count,
             foo = "foo") %>%
      pivot_longer(-foo) %>%
      select(-foo) %>%
      mutate(value = comma(value, accuracy = 0.01)) %>%
      rename({{group_var}} := value)
  }
}
#
table2_1_fxn(matched_treated, is_crh = TRUE) %>%
  left_join(., table2_1_fxn(matched_treated, is_crh = FALSE)) %>%
  left_join(., table2_1_fxn(all_control, is_crh = FALSE)) %>%
  left_join(., table2_1_fxn(matched_control, is_crh = FALSE)) %>%
  kbl(col.names = c("", "Treated & Matched, PC CRH Encounters",
                    "Treated & Matched, PC Encounters",
                    "Control, PC Encounters",
                    "Control & Matched, PC Encounters"),
      align = c("l", rep("r", 4))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

```{r}
table2_2_fxn <- function(group_var) {
  vast %>%
  filter(sta5a %in% {{group_var}}) %>%
  group_by(s_abbr2) %>%
  summarise(count = n()) %>%
  mutate(prop = count / length({{group_var}}),
         value = paste0(count, " (", percent(prop, accuracy = 0.1), ")")) %>%
    select(s_abbr2, value) %>%
    rename({{group_var}} := value)
}
#--
table2_2_fxn(matched_treated) %>%
  left_join(., table2_2_fxn(all_control)) %>%
  left_join(., table2_2_fxn(matched_control)) %>%
  kbl(col.names = c("", "Matched, Treated", "All Eligible Control", "Matched Control"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
#--
table2_3_fxn <- function(group_var){
  analytic_df %>%
    filter(sta5a %in% {{group_var}}
           & vssc_month == ymd("2019-10-01")) %>%
    select(sta5a, pcmm_count_fy_qtr, pct_rural, avg_age_oct1_2022, avg_driveTime, adi_natRnk_avg,
           pct_male, pct_white, pct_black, pct_other, new_pc_pt_wt_create, est_pc_pt_wt_pid, third_next_avail) %>%
    pivot_longer(-sta5a) %>%
    group_by(name) %>%
    summarise(avg_val = mean(value, na.rm = T),
              sd_val = sd(value, na.rm = T)) %>%
    mutate(name = factor(name, ordered = T,
                         levels = c("pcmm_count_fy_qtr", "pct_rural", "avg_age_oct1_2022",
                                    "avg_driveTime",
                                    "adi_natRnk_avg", "pct_male", "pct_white",
                                    "pct_black", "pct_other", "new_pc_pt_wt_create",
                                    "est_pc_pt_wt_pid", "third_next_avail")),
           {{group_var}} := paste0(comma(avg_val, accuracy = 0.1), " (",
                                   comma(sd_val, accuracy = 0.1), ")")) %>%
    select(-c(avg_val, sd_val)) %>%
    arrange(name)
}
#--
pVal_matched_all_eligible <- analytic_df %>%
  filter(vssc_month == ymd("2019-10-01")) %>%
  summarise(across(c(pcmm_count_fy_qtr, pct_rural, avg_age_oct1_2022, avg_driveTime, adi_natRnk_avg,
                     pct_male, pct_white, pct_black, pct_other, new_pc_pt_wt_create, est_pc_pt_wt_pid, third_next_avail),
                   ~list(t.test(.x ~ matched_vs_allEligible)$p.value))) %>%
  unlist() %>%
  as.data.frame() %>%
  rownames_to_column(var = "name")%>%
  rename(value = ".") %>%
  mutate(pval_disp1 = if_else(value < 0.001, "< 0.001", comma(value, accuracy = 0.001))) %>%
  select(name, pval_disp1)
#--
pVal_matched_matched_control <- analytic_df %>%
  filter(vssc_month == ymd("2019-10-01")) %>%
  summarise(across(c(pcmm_count_fy_qtr, pct_rural, avg_age_oct1_2022, avg_driveTime, adi_natRnk_avg,
                     pct_male, pct_white, pct_black, pct_other, new_pc_pt_wt_create, est_pc_pt_wt_pid, third_next_avail),
                   ~list(t.test(.x ~ matched_vs_zeroControl)$p.value))) %>%
  unlist() %>%
  as.data.frame() %>%
  rownames_to_column(var = "name")%>%
  rename(value = ".") %>%
  mutate(pval_disp2 = if_else(value < 0.001, "< 0.001", comma(value, accuracy = 0.001))) %>%
  select(name, pval_disp2)
#
table2_3_fxn(matched_treated) %>%
  left_join(., table2_3_fxn(all_control)) %>%
  left_join(., pVal_matched_all_eligible) %>%
  left_join(., table2_3_fxn(matched_control)) %>%
  left_join(., pVal_matched_matched_control) %>%
  kbl(col.names = c("", "Matched, Treated", "All Eligible Control", "Matched-Treated vs. All Controls", "Matched Control",
                    "Matched-Treated vs. Matched-Control"),
      align = c("l", rep("r", 5))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


```{r}
table2_4_fxn <- function(group_var, is_crh, group_var2){
  if({{is_crh}} == T){
    crh_counts %>% filter(sta5a %in% matched_treated) %>%
      left_join(., vast) %>%
      left_join(., scrssn_count) %>%
      select(encounter_total = pc_crh_enc_count,
             {{group_var2}}) %>%
      pivot_longer(-{{group_var2}}) %>%
      group_by({{group_var2}}, name) %>%
      summarise("{{group_var}}_crh" := sum(value)) %>%
      select(-name) %>%
      adorn_percentages("col") %>%
      adorn_pct_formatting() %>%
      adorn_ns(position = "front")
  }
  else {
    pc_encounters %>%
      filter(visitMonth > ymd("2018-09-01") & visitMonth < ymd("2020-03-01")
             & Sta6a %in% {{group_var}}) %>%
      left_join(., vast, by = c("Sta6a" = "sta5a")) %>%
      left_join(., scrssn_count, by = c("Sta6a" = "sta5a")) %>%
      select(pc_encounter_total, {{group_var2}}) %>%
      group_by({{group_var2}}) %>%
      summarise({{group_var}} := sum(pc_encounter_total)) %>%
      adorn_percentages("col") %>%
      adorn_pct_formatting() %>%
      adorn_ns("front")
  }
}
```

## Site Type  
```{r}
table2_4_fxn(matched_treated, TRUE, s_abbr2) %>%
  left_join(., table2_4_fxn(matched_treated, FALSE, s_abbr2)) %>%
  left_join(., table2_4_fxn(matched_control, FALSE, s_abbr2)) %>%
  kbl(col.names = c("", "PC CRH Among Matched, Treated", "Matched, Treated", 
                    "Matched Control"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

### Chi-Squared Test  
```{r}
chisq_fxn1 <- function(input_df, row_names){
  obs_df <- data.frame(input_df$observed) %>%
    mutate(join_col = row_names)
  exp_df <- data.frame(input_df$expected) %>%
    mutate(join_col = row_names)
  #--
  obs_df %>% 
    left_join(exp_df, by = "join_col") %>%
    select(join_col, col1.x, col2.x, col1.y, col2.y) %>%
  kbl(col.names = c("", rep(c("PC CRH", "PC, Matched-Treated"), 2))) %>%
  kable_classic("striped") %>%
  add_header_above(c("", "Observed" = 2, "Expected" = 2),
                   bold = T)
}
#
chisq_fxn2 <- function(input_df, row_names){
  obs_df <- data.frame(input_df$observed) %>%
    mutate(join_col = row_names)
  exp_df <- data.frame(input_df$expected) %>%
    mutate(join_col = row_names)
  #--
  obs_df %>% 
    left_join(exp_df, by = "join_col") %>%
    select(join_col, col1.x, col2.x, col1.y, col2.y) %>%
  kbl(col.names = c("", rep(c("PC, Matched-Treated", "PC, Matched-Control"), 2))) %>%
  kable_classic("striped") %>%
  add_header_above(c("", "Observed" = 2, "Expected" = 2),
                   bold = T)
}
#--
chisq_1 <- chisq.test(data.frame(col1 = c(76390, 7929, 30743),
                      col2 = c(725212, 24808, 731027)))
#---

chisq_1
chisq_fxn1(chisq_1,  c("CBOC", "OOS", "VAMC/HCC"))

chisq_2 <- chisq.test(data.frame(col1 = c(725212, 24808, 731027),
                      col2 = c(572077, 25215, 762259)))
#--==
chisq_2
chisq_fxn2(chisq_2,  c("CBOC", "OOS", "VAMC/HCC"))
```

## Site Size    
```{r}
table2_4_fxn(matched_treated, TRUE, scrssn_count_cat) %>%
  left_join(., table2_4_fxn(matched_treated, FALSE, scrssn_count_cat)) %>%
  left_join(., table2_4_fxn(matched_control, FALSE, scrssn_count_cat)) %>%
  kbl(col.names = c("", "PC CRH Among Matched, Treated", "Matched, Treated", 
                    "Matched Control"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
#----
chisq_3 <- chisq.test(data.frame(col1 = c(24600, 69941, 20521),
                                 col2 = c(71101, 542315, 867631)))
chisq_3
chisq_fxn1(chisq_3, c("450-2,399", "2,400-9,999", "10,000+"))
#--==
chisq_4 <- chisq.test(data.frame(col1 = c(71101, 542315, 867631),
                                 col2 = c(158385, 433467, 767699)))
chisq_4
chisq_fxn2(chisq_4, c("450-2,399", "2,400-9,999", "10,000+"))
```

## Site URH      
```{r}
table2_4_fxn(matched_treated, TRUE, urh2) %>%
  left_join(., table2_4_fxn(matched_treated, FALSE, urh2)) %>%
  left_join(., table2_4_fxn(matched_control, FALSE, urh2)) %>%
  kbl(col.names = c("", "PC CRH Among Matched, Treated", "Matched, Treated", 
                    "Matched Control"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
#----
chisq_5 <- chisq.test(data.frame(col1 = c(58506, 56556),
                                 col2 = c(275015, 1206032)))
chisq_5
chisq_fxn1(chisq_5, c("Rural", "Urban"))
#----
chisq_6 <- chisq.test(data.frame(col1 = c(275015, 1206032),
                                 col2 = c(202938, 1156613)))
chisq_6
chisq_fxn2(chisq_6, c("Rural", "Urban"))
```

# Table 3  

```{r}
new_boot <- read_csv(here("Input", "Bootstrap", "new_pc_pt_wt_boot.csv")) %>%
  mutate(ctrl_post_minus_pre = ctrl_post_slope - ctrl_pre_slope,
         trtd_post_minus_pre = trtd_post_slope - trtd_pre_slope,
         trtd_minus_ctrl_pre_slope = trtd_pre_slope - ctrl_pre_slope,
         trtd_minus_ctrl_post_slope = trtd_post_slope - ctrl_post_slope,
         trtd_jump_minus_ctrl_jump = trtd_jump - ctrl_jump,
         last_cell = trtd_minus_ctrl_post_slope - trtd_minus_ctrl_pre_slope,
         foo = "foo") %>%
  pivot_longer(-foo) %>%
  group_by(name) %>%
  summarise(mean_val = mean(value),
            sd_val = sd(value),
            n_val = 5000,
            ci_low = quantile(value, probs = 0.025),
            ci_high = quantile(value, probs = 0.975)) %>%
  mutate(disp_val = 
           paste0(
             comma(mean_val, accuracy = 0.001), " (",
             comma(ci_low, accuracy = 0.001), ", ",
             comma(ci_high, accuracy = 0.001), ")")) %>%
  select(name, disp_val) %>%
  pivot_wider(names_from = name, values_from = disp_val)
#
est_boot <- read_csv(here("Input", "Bootstrap", "est_pc_pt_wt_boot.csv")) %>%
  mutate(ctrl_post_minus_pre = ctrl_post_slope - ctrl_pre_slope,
         trtd_post_minus_pre = trtd_post_slope - trtd_pre_slope,
         trtd_minus_ctrl_pre_slope = trtd_pre_slope - ctrl_pre_slope,
         trtd_minus_ctrl_post_slope = trtd_post_slope - ctrl_post_slope,
         trtd_jump_minus_ctrl_jump = trtd_jump - ctrl_jump,
         last_cell = trtd_minus_ctrl_post_slope - trtd_minus_ctrl_pre_slope,
         foo = "foo") %>%
  pivot_longer(-foo) %>%
  group_by(name) %>%
  summarise(mean_val = mean(value),
            sd_val = sd(value),
            n_val = 5000,
            ci_low = quantile(value, probs = 0.025),
            ci_high = quantile(value, probs = 0.975)) %>%
  mutate(disp_val = 
           paste0(
             comma(mean_val, accuracy = 0.001), " (",
             comma(ci_low, accuracy = 0.001), ", ",
             comma(ci_high, accuracy = 0.001), ")")) %>%
  select(name, disp_val) %>%
  pivot_wider(names_from = name, values_from = disp_val)
#
tna_boot <- read_csv(here("Input", "Bootstrap", "third_next_avail_boot.csv")) %>%
  mutate(ctrl_post_minus_pre = ctrl_post_slope - ctrl_pre_slope,
         trtd_post_minus_pre = trtd_post_slope - trtd_pre_slope,
         trtd_minus_ctrl_pre_slope = trtd_pre_slope - ctrl_pre_slope,
         trtd_minus_ctrl_post_slope = trtd_post_slope - ctrl_post_slope,
         trtd_jump_minus_ctrl_jump = trtd_jump - ctrl_jump,
         last_cell = trtd_minus_ctrl_post_slope - trtd_minus_ctrl_pre_slope,
         foo = "foo") %>%
  pivot_longer(-foo) %>%
  group_by(name) %>%
  summarise(mean_val = mean(value),
            sd_val = sd(value),
            n_val = 5000,
            ci_low = quantile(value, probs = 0.025),
            ci_high = quantile(value, probs = 0.975)) %>%
  mutate(disp_val = 
           paste0(
             comma(mean_val, accuracy = 0.001), " (",
             comma(ci_low, accuracy = 0.001), ", ",
             comma(ci_high, accuracy = 0.001), ")")) %>%
  select(name, disp_val) %>%
  pivot_wider(names_from = name, values_from = disp_val)
```

## New Patient Wait Time  
### Slope  

```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c("$\\beta_{time}$", 
            "$\\beta_{time} + \\beta_{treat}\\beta_{time}$", 
            "$\\beta_{treat}\\beta_{time}$"),
  col_3 = c("$\\beta_{time}+\\beta_{post}\\beta_{time}$",
            "$\\beta_{time}+\\beta_{post}\\beta_{time} +$ \n  $\\beta_{post}\\beta_{time}\\beta_{treat}$",
            "$\\beta_{post}\\beta_{time}\\beta_{treat}$"),
  col_4 = c("$\\beta_{post}\\beta_{time}$",
            "$\\beta_{post}\\beta_{time} +$ \n $\\beta_{post}\\beta_{time}\\beta_{treat} -$\n$\\beta_{treat}\\beta_{time}$",
            "$\\beta_{post}\\beta_{time}\\beta_{treat}-\\beta_{treat}\\beta_{time}$")
) %>%
  kbl(escape = F,
      col.names = c("", "Pre Slope", "Post Slope", "Post - Pre"),
      align = c("l", rep("c", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(new_boot$ctrl_pre_slope, 
            new_boot$trtd_pre_slope,
            new_boot$trtd_minus_ctrl_pre_slope),
  col_3 = c(new_boot$ctrl_post_slope, 
            new_boot$trtd_post_slope,
            new_boot$trtd_minus_ctrl_post_slope),
  col_4 = c(new_boot$ctrl_post_minus_pre, 
            new_boot$trtd_post_minus_pre, 
            new_boot$last_cell)
) %>%
  kbl(col.names = c("", "Pre Slope Mean (95% CI)", "Post Slope Mean (95% CI)", "Post - Pre Mean (95% CI)"),
      align = c("l", rep("c", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

### DiD/"Jump"  

```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c("$\\beta_{post}$", "$\\beta_{post} + \\beta_{treat}\\beta_{post}$", "$\\beta_{treat}\\beta_{post}$")
) %>%
  kbl(escape = F,
      col.names = c("", "Intervention \"Jump\""),
      align = c("l", "c")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(new_boot$ctrl_jump, new_boot$trtd_jump, new_boot$trtd_jump_minus_ctrl_jump)
) %>%
  kbl(col.names = c("", "Intervention \"Jump\""),
      align = c("l", "c")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## Established Patient Wait Time  
### Slope  


```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(est_boot$ctrl_pre_slope, 
            est_boot$trtd_pre_slope,
            est_boot$trtd_minus_ctrl_pre_slope),
  col_3 = c(est_boot$ctrl_post_slope, 
            est_boot$trtd_post_slope,
            est_boot$trtd_minus_ctrl_post_slope),
  col_4 = c(est_boot$ctrl_post_minus_pre, 
            est_boot$trtd_post_minus_pre, 
            est_boot$last_cell)
) %>%
  kbl(col.names = c("", "Pre Slope Mean (95% CI)", "Post Slope Mean (95% CI)", "Post - Pre Mean (95% CI)"),
      align = c("l", rep("c", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

### DiD/"Jump"  

```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(est_boot$ctrl_jump, est_boot$trtd_jump, est_boot$trtd_jump_minus_ctrl_jump)
) %>%
  kbl(col.names = c("", "Intervention \"Jump\""),
      align = c("l", "c")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## Third Next Available    
### Slope  


```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(tna_boot$ctrl_pre_slope, 
            tna_boot$trtd_pre_slope,
            tna_boot$trtd_minus_ctrl_pre_slope),
  col_3 = c(tna_boot$ctrl_post_slope, 
            tna_boot$trtd_post_slope,
            tna_boot$trtd_minus_ctrl_post_slope),
  col_4 = c(tna_boot$ctrl_post_minus_pre, 
            tna_boot$trtd_post_minus_pre, 
            tna_boot$last_cell)
) %>%
  kbl(col.names = c("", "Pre Slope Mean (95% CI)", "Post Slope Mean (95% CI)", "Post - Pre Mean (95% CI)"),
      align = c("l", rep("c", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

### DiD/"Jump"  

```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(tna_boot$ctrl_jump, tna_boot$trtd_jump, tna_boot$trtd_jump_minus_ctrl_jump)
) %>%
  kbl(col.names = c("", "Intervention \"Jump\""),
      align = c("l", "c")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```