---
title: "PC CRH - Pre-COVID Analysis"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
set.seed(1234)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(urh_vast2 = if_else(urh_vast == "U", "U", "R"))
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_pre_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(vssc_month = seq.Date(ymd("2018-10-01"), ymd("2020-02-01"), "1 month")) %>%
  rowid_to_column(., var = "time") %>%
  mutate(time2 = time - 12)
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PACT_CC].[econ].PatientPCP
#                             	where fy = 2018
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#
vimpact <- dbGetQuery(oabi_con,
                      "select distinct spoke_sta5a as sta5a, vimpact_pilot
from [PACT_CC].[CRH].CRH_sites_FY20_working")
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  mutate(nosos_x_10 = nosos_risk_score * 10,
         panel_ratio_x_10 = obs_exp_panel_ratio * 10,
         adi_div_10 = adi_natRnk_avg / 10) %>%
  left_join(., vast %>% select(sta5a, urh_vast2)) %>%
  left_join(., vimpact) %>%
  mutate(vimpact_pilot = if_else(vimpact_pilot == 1, 1, 0))
#
analytic_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df$treat <- relevel(analytic_df$treat, ref = 'Control')
```



# Front Matter  

## Description of this report  

* This is a description of the three pre-COVID analyses

## Decision Points  

* Per our discussions:
    + This analysis includes a __3-way interaction:__ _time X treat X post_
        + This is per the discussion we had on August 23rd
    + This analysis uses the newest version of the PS match
    + This analysis uses Established Patient Wait Time from patient-indicated date
    + I've re-scaled some covariates:
        + Multiplied NOSOS and Panel Ratio by 10, meaning that the coefficients can be interpreted as a one-tenth unit change
        + Divided ADI by 10, meaning that the coefficient can be interpreted as a change of 10%-iles 
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses the pre-COVID PS matching model
    + This model consists of: 
        + Outcomes matched on their average values over FY19
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact
        + Matched on FY18 Q4 average values of PCMM uniques, Obs:Exp panel size ratio, proportion rural, non-VA consults per 10,000 in PCMM

* Description of analyses  
    + These analyses are a Comparative Interrupted Time Series with covariates
    + They are mixed-effects models and allow random intercepts for sta5a
    + On the LHS of the model we have New Patient Wait Time, Established Patient Wait Time (PID), and Third Next Available 
    + In addition to the various combinations of _treat_, _time_, and _post_, all models have the following covariates:
        + Observed:Expected PC Panel Size 
        + Proportion male 
        + Proportion rural 
        + ADI
        + NOSOS
    + I also run a parametric, 500 simulation bootstrap for the confidence intervals on our fixed-effects estimates

* Refresher on the [NOSOS](https://www.herc.research.va.gov/include/page.asp?id=risk-adjustment)  
    + It was designed to predict cost
    + It is centered around 1
    + A veteran with a value of 1 would be expected to have annual costs that are the national average for VA patients
    + A veteran with a value of 2.5 would be expected to incur 2.5-times the national average annual costs for VA patients

## Covariate description  

```{r}
analytic_df %>% 
  select(obs_exp_panel_ratio, pct_male, pct_rural, nosos_risk_score, adi_natRnk_avg) %>%
  rownames_to_column() %>%
  pivot_longer(-rowname) %>%
  group_by(name) %>%
  summarise(mean_val = mean(value, na.rm = T),
            med_val = median(value, na.rm = T),
            sd_val = sd(value, na.rm = T),
            qtl_25 = quantile(value, probs = 0.25, na.rm = T),
            qtl_75 = quantile(value, probs = 0.75, na.rm = T)) %>%
  mutate(
    name2 = case_when(
      name == "obs_exp_panel_ratio" ~ "Obs:Exp",
      name == "pct_male" ~ "% male",
      name == "pct_rural" ~ "% rural",
      name == "nosos_risk_score" ~ "NOSOS",
      name == "adi_natRnk_avg" ~ "ADI"),
    mean_val2 = if_else(str_detect(name, "obs_|adi_|nosos"),
                          paste0(round(mean_val, 2), " (", round(sd_val, 2), ")"),
                        paste0(percent(mean_val / 100, accuracy = 0.1), 
                               " (", round(sd_val, 1), ")")),
    med_val2 = if_else(str_detect(name, "obs_|adi_|nosos"),
                       as.character(round(med_val, 2)),
                       percent(med_val / 100, accuracy = 0.1)),
    qtls = if_else(str_detect(name, "obs_|adi_|nosos"),
                   paste0(round(qtl_25, 2), ", ", round(qtl_75, 2)),
                   paste0(round(qtl_25, 1), "%, ", round(qtl_75, 1), "%"))) %>%
  select(7:10) %>%
  kbl(col.names = c("", "Mean (SD)", "Median", "25th, 75th %-iles"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped", full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
plot_fxn <- function(outcome, outcome_c){
  ylab <- if(outcome_c == "est_pc_pt_wt_pid"){
    "Established Patient Wait Time (days)"
  }
  else if(outcome_c == "new_pc_pt_wt"){
    "New Patient Wait Time (days)"
  }
  else{
    "Third Next Available (days)"
  }
#

  ggplot(data = analytic_df,
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_smooth(linewidth = 1, data = subset(analytic_df, vssc_month < ymd("2019-10-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    geom_smooth(linewidth = 1, data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    ggthemes::scale_color_colorblind() +
    theme(axis.title.x = element_blank()) +
    labs(y = ylab) +
    scale_y_continuous(limits = c(0, NA))
}
#
```

# Baseline Linear Trend  

* This model includes _time2_ (i.e., months) as well as an interaction between _time2_ and _treat_, an interaction between _treat_ and _post_, and a 3-way interaction between _time2_ _treat_ and _post_
* We chose to center time (i.e., __time2__) to facilitate interpretation of the instantaneous change at implementation

$$Y_{jt}=\beta_{0} +\beta_1Z_{jt}+ \beta_{2}time2_{t} +  \beta_{3}post_{t}+\beta_{4}treat_{j}+\beta_{5}time2_{t}treat_{j}+\beta_{6}post_{t}treat_{j} +\beta_{7}time2_{t}post_{t}treat_{j} + v_{j}+u_{jt}$$

# Dates  
* Below is a table describing the relationship between month of the year and the analytic variable __time2__  

```{r}
dates %>%
  kbl(col.names = c("time", "Month of Year", "time2"),
      align = rep("c", 3)) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = TRUE)
```

# Established Patient Wait Time  

## Observed Values  

```{r}
plot_fxn(est_pc_pt_wt_pid, "est_pc_pt_wt_pid")
```

## Predicted Values    

```{r}
bline_trend1 <- lmer(est_pc_pt_wt_pid ~ 
                       treat * post * time2
                     + panel_ratio_x_10
                     + pct_male
                     + pct_rural
                     + nosos_x_10
                     + adi_div_10
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_1 <- ggeffects::ggpredict(bline_trend1, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2"))
#--
p_pred_1 <- ggplot(data = pred_1,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_1, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  geom_line(data = subset(pred_1, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time")
#
p_pred_1
```


#### Model Estimates    
```{r}
bline_trend1b <- lmer(est_pc_pt_wt_pid ~ 
                       treat * post * time2
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + nosos_risk_score
                     + adi_natRnk_avg
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
tab_model(bline_trend1, bline_trend1b,
          dv.labels = c("Established Patient Wait Time (PID)", "Without Scaling"),
          digits = 3)
```

#### Bootstrapped Confidence Intervals  
```{r}
confint(bline_trend1, method = "boot", oldNames = F, nsim = 500)
```



# New Patient Wait Time  

## Observed Values  

```{r}
plot_fxn(new_pc_pt_wt, "new_pc_pt_wt")
```

## Predicted Values  

```{r}
bline_trend2 <- lmer(new_pc_pt_wt ~ 
                       treat * post * time2
                     + panel_ratio_x_10
                     + pct_male
                     + pct_rural
                     + nosos_x_10
                     + adi_div_10
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_2 <- ggeffects::ggpredict(bline_trend2, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2"))
#--
p_pred_2 <- ggplot(data = pred_2,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_2, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  geom_line(data = subset(pred_2, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time")
#
p_pred_2
```


#### Model Estimates      
```{r}
bline_trend2b <- lmer(new_pc_pt_wt ~ 
                       treat * post * time2
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + nosos_risk_score
                     + adi_natRnk_avg
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
tab_model(bline_trend2, bline_trend2b,
          dv.labels = c("New Patient Wait Time", "Without Scaling"),
          digits = 3)
```

#### Bootstrapped Confidence Intervals  
```{r}
confint(bline_trend2, method = "boot", oldNames = F, nsim = 500)
```



# Third Next Available    

## Observed Values  

```{r}
plot_fxn(third_next_avail, "third_next_avail")
```

## Predicted Values  

```{r}
bline_trend3 <- lmer(third_next_avail ~ 
                       treat * post * time2
                     + panel_ratio_x_10
                     + pct_male
                     + pct_rural
                     + nosos_x_10
                     + adi_div_10
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_3 <- ggeffects::ggpredict(bline_trend3, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2"))
#--
p_pred_3 <- ggplot(data = pred_3,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_3, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  geom_line(data = subset(pred_3, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  scale_y_continuous(limits = c(0, 15)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title.x = element_blank()) +
  labs(y = "Third Next Available")
#-
p_pred_3
```


#### Model Estimates      
```{r}
bline_trend3b <- lmer(third_next_avail ~ 
                       treat * post * time2
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + nosos_risk_score
                     + adi_natRnk_avg
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
tab_model(bline_trend3, bline_trend3b,
          dv.labels = c("Third Next Available", "Without Scaling"),
          digits = 3)
```


#### Bootstrapped Confidence Intervals  
```{r}
confint(bline_trend3, method = "boot", oldNames = F, nsim = 500)
```

# All Together in One Plot  

```{r fig.width = 12, fig.height = 15}
multiplot(p_pred_1 + theme(legend.position = "none"),
          p_pred_2 + theme(legend.position = "none"),
          p_pred_3,
          cols = 1)
```


# Rural Clinics Only   

```{r}
analytic_df2 <- analytic_df %>%
  filter(urh_vast2 == "R")
#----
glm_table_fxn <- function(outcome){
  glm_fmla <- as.formula(paste0(outcome, " ~ treat * post * time2 + panel_ratio_x_10 + pct_male + pct_rural + nosos_x_10 + adi_div_10 + (1|sta5a)"))
  
  #-----
  glm_1 <- lmerTest::lmer(glm_fmla,
       data = analytic_df,
       REML = TRUE) 
  glm_summ1 <- summary(glm_1)
  #
  glm_coef1 <- glm_summ1$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3)
  
  #-----
  glm_2 <- lmerTest::lmer(glm_fmla,
                          data = analytic_df2,
                          REML = TRUE) 
  glm_summ2 <- summary(glm_2)
  #
  glm_coef2 <- glm_summ2$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3)
  #===============
  #-----------------
  glm_coef1 %>% left_join(., glm_coef2, by = "rowname")%>%
    mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.001)),
           p.x = if_else(as.numeric(p.x) < 0.05 | p.x == "0.000", cell_spec(p.x, background = "skyblue"), cell_spec(p.x, background = "white")),
           p.y = if_else(as.numeric(p.y) < 0.05 | p.y == "0.000", cell_spec(p.y, background = "skyblue"), cell_spec(p.y, background = "white"))) %>%
    kbl(col.names = c("", "Estimate", "p", "Estimate", "p"),
        align = c("l", rep("c", 4)),
        escape = F) %>%
    kable_classic("striped") %>%
    add_header_above(c("", "All Sta5a" = 2, "Rural Sta5a" = 2),
                     bold = T) %>%
    column_spec(3, border_right = T)
}
```

## Established Patient Wait Time  

```{r}
glm_table_fxn("est_pc_pt_wt_pid")
```

## New Patient Wait Time  

```{r}
glm_table_fxn("new_pc_pt_wt_create")
```

## Third Next Available  

```{r}
glm_table_fxn("third_next_avail")
```

# Penetration Rate vs. Binary Indicator  

```{r}
glm_table_fxn2 <- function(outcome){
  glm_fmla1 <- as.formula(paste0(outcome, " ~ treat * post * time2 + panel_ratio_x_10 + pct_male + pct_rural + nosos_x_10 + adi_div_10 + (1|sta5a)"))
  glm_fmla2 <- as.formula(paste0(outcome, " ~ pc_crh_per_1k_total_pc * post * time2 + panel_ratio_x_10 + pct_male + pct_rural + nosos_x_10 + adi_div_10 + (1|sta5a)"))
  
  #-----
  glm_1 <- lmerTest::lmer(glm_fmla1,
       data = analytic_df,
       REML = TRUE) 
  glm_summ1 <- summary(glm_1)
  #
  glm_coef1 <- glm_summ1$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3)
  
  #-----
  glm_2 <- lmerTest::lmer(glm_fmla2,
                          data = analytic_df,
                          REML = TRUE) 
  glm_summ2 <- summary(glm_2)
  #
  glm_coef2 <- glm_summ2$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3) %>%
    mutate(rowname2 = rowname) %>%
    select(rowname, rowname2, Estimate, p)
  #===============
  #-----------------
  glm_coef1 %>% full_join(., glm_coef2, by = "rowname")%>%
    mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.001)),
           p.x = if_else(as.numeric(p.x) < 0.05 | p.x == "0.000", cell_spec(p.x, background = "skyblue"), cell_spec(p.x, background = "white")),
           p.y = if_else(as.numeric(p.y) < 0.05 | p.y == "0.000", cell_spec(p.y, background = "skyblue"), cell_spec(p.y, background = "white"))) %>%
    kbl(col.names = c("", "Estimate", "p", "", "Estimate", "p"),
        align = c("l", "c", "c", "l", "c", "c"),
        escape = F) %>%
    kable_classic("striped") %>%
    add_header_above(c("Binary Treated" = 3, "Penetration Rate" = 3),
                     bold = T) %>%
    column_spec(3, border_right = T)
}
```

## Established Patient Wait Time  

```{r}
glm_table_fxn2("est_pc_pt_wt_pid")
```

## New Patient Wait Time  

```{r}
glm_table_fxn2("new_pc_pt_wt_create")
```

## Third Next Available  

```{r}
glm_table_fxn2("third_next_avail")
```

# Effect of V-IMPACT Pilot Status    


```{r}
glm_table_fxn3 <- function(outcome){
  glm_fmla1 <- as.formula(paste0(outcome, " ~ treat * post * time2 + panel_ratio_x_10 + pct_male + pct_rural + nosos_x_10 + adi_div_10 + vimpact_pilot + (1|sta5a)"))
  glm_fmla2 <- as.formula(paste0(outcome, " ~ treat * post * time2 + panel_ratio_x_10 + pct_male + pct_rural + nosos_x_10 + adi_div_10 + (1|sta5a)"))
  
  #-----
  glm_1 <- lmerTest::lmer(glm_fmla1,
       data = analytic_df,
       REML = TRUE) 
  glm_summ1 <- summary(glm_1)
  #
  glm_coef1 <- glm_summ1$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3)
  
  #-----
  glm_2 <- lmerTest::lmer(glm_fmla2,
                          data = analytic_df,
                          REML = TRUE) 
  glm_summ2 <- summary(glm_2)
  #
  glm_coef2 <- glm_summ2$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3)
  #===============
  #-----------------
  glm_coef1 %>% full_join(., glm_coef2, by = "rowname")%>%
    mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.001)),
           p.x = if_else(as.numeric(p.x) < 0.05 | p.x == "0.000", cell_spec(p.x, background = "skyblue"), cell_spec(p.x, background = "white")),
           p.y = if_else(as.numeric(p.y) < 0.05 | p.y == "0.000", cell_spec(p.y, background = "skyblue"), cell_spec(p.y, background = "white"))) %>%
    kbl(col.names = c("", "Estimate", "p", "Estimate", "p"),
        align = c("l", "c", "c", "c", "c"),
        escape = F) %>%
    kable_classic("striped") %>%
    add_header_above(c("", "V-Impact" = 2, "No V-IMPACT" = 2),
                     bold = T) %>%
    column_spec(3, border_right = T)
}
```

## Established Patient Wait Time  

```{r}
glm_table_fxn3("est_pc_pt_wt_pid")
```

## New Patient Wait Time  

```{r}
glm_table_fxn3("new_pc_pt_wt_create")
```

## Third Next Available  

```{r}
glm_table_fxn3("third_next_avail")
```

```{r}
glm_table_fxn4 <- function(outcome){
  glm_fmla1 <- as.formula(paste0(outcome, " ~ treat * post * time2 + panel_ratio_x_10 + pct_male + pct_rural + nosos_x_10 + adi_div_10 + vimpact_pilot + (1|sta5a)"))
  glm_fmla2 <- as.formula(paste0(outcome, " ~ treat * post * time2 + panel_ratio_x_10 + pct_male + pct_rural + nosos_x_10 + adi_div_10 + (1|sta5a)"))
  
  #-----
  glm_1 <- lmerTest::lmer(glm_fmla2,
       data = analytic_df,
       REML = TRUE) 
  glm_summ1 <- summary(glm_1)
  #
  glm_coef1 <- glm_summ1$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3)
  
  #-----
  glm_2 <- analytic_df %>%
  filter(vimpact_pilot == F) %>%
    lmerTest::lmer(glm_fmla2,
                          data = .,
                          REML = TRUE) 
  glm_summ2 <- summary(glm_2)
  #
  glm_coef2 <- glm_summ2$coefficients %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    select(1, 2, 6) %>%
    rename(p = 3)
  #===============
  #-----------------
  glm_coef1 %>% full_join(., glm_coef2, by = "rowname")%>%
    mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.001)),
           p.x = if_else(as.numeric(p.x) < 0.05 | p.x == "0.000", cell_spec(p.x, background = "skyblue"), cell_spec(p.x, background = "white")),
           p.y = if_else(as.numeric(p.y) < 0.05 | p.y == "0.000", cell_spec(p.y, background = "skyblue"), cell_spec(p.y, background = "white"))) %>%
    kbl(col.names = c("", "Estimate", "p", "Estimate", "p"),
        align = c("l", "c", "c", "c", "c"),
        escape = F) %>%
    kable_classic("striped") %>%
    add_header_above(c("", "V-Impact" = 2, "No V-IMPACT" = 2),
                     bold = T) %>%
    column_spec(3, border_right = T)
}
```

## Established Patient Wait Time  

```{r}
glm_table_fxn4("est_pc_pt_wt_pid")
```

## New Patient Wait Time  

```{r}
glm_table_fxn4("new_pc_pt_wt_create")
```

## Third Next Available  

```{r}
glm_table_fxn4("third_next_avail")
```

# Clustered at VISN and Sta5a  

```{r}
visn_cluster_fxn <- function(outcome){
  glm_fmla <- as.formula(paste0(outcome, 
                                 " ~ treat * post * time2 + panel_ratio_x_10", 
                                 " + pct_male + pct_rural + nosos_x_10 + adi_div_10 + (1|sta5a) + (1|parent_visn)"))
  #---
  lmer(glm_fmla,
       data = analytic_df)
}
#
est_mod <- visn_cluster_fxn("est_pc_pt_wt_pid")
new_mod <- visn_cluster_fxn("new_pc_pt_wt_create")
tna_mod <- visn_cluster_fxn("third_next_avail")
#
tab_model(est_mod, new_mod, tna_mod)
```