---
title: "Pre-COVID Plots and Tables"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(s_abbr2 = case_when(s_abbr %in% c("MSCBOC", "PCCBOC") ~ "CBOC",
                             s_abbr %in% c("HCC", "VAMC") ~ "VAMC/HCC",
                             TRUE ~ s_abbr))
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_1_noCRH_among_controls.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(vssc_month = seq.Date(ymd("2017-06-01"),
                                      ymd("2020-02-01"),
                                      "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#----------
pc_encounters <- dbGetQuery(oabi_con,
                            "select *
from [OABI_MyVAAccess].[crh_eval].[A1_pc_enc_scrssn_count]
where visitMonth < cast('2020-03-01' as date)
	AND visitMonth > cast('2018-06-01' as date)") %>%
  rename(sta5a = Sta6a) %>%
  mutate(vssc_month = ymd(visitMonth))
#--------
pc_cons <- dbGetQuery(oabi_con,
                      "with CTE as(
select count(*) as total_cons, sum(non_va) as non_va_cons, sta6a
	, DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01') as activityMonth
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where stopCode_group = 'Primary Care'
	AND year(activityDateTime) > 2016 AND year(activityDateTime) < 2020
group by Sta6a, DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01'))
select a.sta6a as sta5a, total_cons, non_va_cons
, pcmm_scrssn_count
, activityMonth as vssc_month
from CTE as a
left join [OABI_MyVAAccess].[crh_eval].F2_pcmm_scrssn_count as b
	on a.Sta6a = b.sta5a") %>%
  mutate(non_va_cons_per_10k_pcmm = non_va_cons / pcmm_scrssn_count * 10000,
         vssc_month = ymd(vssc_month))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df_matched <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-06-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%
      left_join(., vast %>% select(sta5a, s_abbr2)) %>%
  left_join(., covariates) %>%
  left_join(., pc_encounters %>% select(sta5a, pc_encounter_total, vssc_month)) %>%
  left_join(., scrssn_count) %>%
  left_join(., pc_cons %>% select(vssc_month, sta5a, non_va_cons_per_10k_pcmm)) %>%
  select(crh_flag
         , panel_fullness
         , vssc_month
         , sta5a
         , pc_encounter_total
         , scrssn_count_avg_fy18
         , s_abbr2
         , team_pcp_ap_fte_total
         , obs_exp_panel_ratio
         , non_va_cons_per_10k_pcmm
         , nosos_risk_score
         , adi_natRnk_avg
         , pct_rural
         , est_pc_pt_wt_pid
         , new_pc_pt_wt
         , third_next_avail)
```

```{r}
source(here("Input", "Analytic df", "F2_propensity_score_matching","ps_match_pre_covid.R"))
#
analytic_df_noMatch <- sta5a_demog_no_missing %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH"))) %>%
  left_join(., dates, by = character()) %>%
  left_join(., vast %>% select(sta5a, s_abbr2)) %>%
  left_join(., covariates) %>%
  left_join(., pc_encounters %>% select(sta5a, pc_encounter_total, vssc_month)) %>%
  left_join(., scrssn_count) %>%
  left_join(., access_metrics) %>%
  left_join(., pc_cons %>% select(vssc_month, sta5a, non_va_cons_per_10k_pcmm)) %>%
  filter(vssc_month < ymd("2020-03-01") 
         & vssc_month > ymd("2017-06-01")) %>%
  select(crh_flag
         , panel_fullness
         , vssc_month
         , sta5a
         , pc_encounter_total
         , scrssn_count_avg_fy18
         , s_abbr2
         , team_pcp_ap_fte_total
         , obs_exp_panel_ratio
         , non_va_cons_per_10k_pcmm
         , nosos_risk_score
         , adi_natRnk_avg
         , pct_rural
         , est_pc_pt_wt_pid
         , new_pc_pt_wt
         , third_next_avail)
```

# Front Matter  

## Description of this report  

* This is the first iteration of a plots and tables document for the pro-COVID paper


* Description of _Propensity Score_ matching
    + This report uses a variation of __Propensity Score v5.1__
    + PS model v5.1 consists of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Removed ADI and NOSOS
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact
    + __This version restricted the pool of potential controls to those sta5as that have never had a PC CRH encounter__

# Table 1  
```{r}
ttest_fxn <- function(df, variable, covar_name){
  accuracy_val <- if(covar_name %in% c("NOSOS", "Obs:Exp", "Panel Fullness"))
  {0.001}
  else if(str_detect(covar_name, "Encounters|ScrSSN")){1}
  else{0.1}
  #--
  start_month <- if(str_detect(covar_name, "PWT|TNA")){ymd("2017-10-01")}
  else{ymd("2018-07-01")}
  #--
  end_month <- if(str_detect(covar_name, "PWT|TNA")){ymd("2018-09-01")}
  else{ymd("2018-09-01")}
  #--
  df %>%
    select(crh_flag, {{variable}}, vssc_month, sta5a) %>%
    filter(vssc_month >= start_month
           & vssc_month <= end_month) %>%
    pivot_wider(names_from = crh_flag, values_from = {{variable}}) %>%
    summarise(mean_crh = mean(`PC CRH`, na.rm = T),
              sd_crh = sd(`PC CRH`, na.rm = T),
              mean_ctrl = mean(`No PC CRH`, na.rm = T),
              sd_ctrl = sd(`No PC CRH`, na.rm = T),
              crh_val = paste0(comma(mean_crh, accuracy = accuracy_val),
                               " (",
                               comma(sd_crh, accuracy = accuracy_val),
                               ")"),
              ctrl_val = paste0(comma(mean_ctrl, accuracy = accuracy_val),
                               " (",
                               comma(sd_ctrl, accuracy = accuracy_val),
                               ")"),
              t_test_p = if_else(t.test(`No PC CRH`, `PC CRH`)$p.value < 0.001,
                                 "< 0.001",
                                 comma(t.test(`No PC CRH`, `PC CRH`)$p.value,
                                       accuracy = 0.001))) %>%
    mutate(covar_name = {{covar_name}},
           start_month = as.character(start_month),
           end_month = as.character(end_month)) %>%
    select(covar_name, crh_val, ctrl_val, t_test_p, start_month, end_month)
}
```

## Un Matched
```{r}
noMatch_s_abbr <- analytic_df_noMatch %>%
  filter(vssc_month == ymd("2018-09-01")) %>%
  group_by(crh_flag, s_abbr2) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = crh_flag, values_from = count) %>%
  mutate(t_test_p = "NA", 
         start_month = "2018-09-01",
         end_month = "2018-09-01") %>%
  rename(crh_val = `PC CRH`,
         ctrl_val = `No PC CRH`,
         covar_name = s_abbr2) %>%
  janitor::adorn_totals() %>%
  mutate(crh_val = as.character(crh_val),
         ctrl_val = as.character(ctrl_val))
#--
noMatch_encounter_tot <- analytic_df_noMatch %>%
  filter(vssc_month > ymd("2018-06-01")
         & vssc_month < ymd("2018-10-01")) %>%
  group_by(crh_flag) %>%
  summarise(pc_enc_tot = comma(sum(pc_encounter_total, na.rm = T), accuracy = 1)) %>%
  mutate(covar_name = "Total PC Encounters") %>%
  pivot_wider(names_from = crh_flag, values_from = pc_enc_tot) %>%
  mutate(t_test_p = "NA",
         start_month = "2018-07-01",
         end_month = "2018-09-01") %>%
  rename(crh_val = `PC CRH`,
         ctrl_val = `No PC CRH`)
#--
noMatch_encounter_tot %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, pc_encounter_total, "PC Encounters per month")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, scrssn_count_avg_fy18, "Unique ScrSSNs")) %>%
  bind_rows(., noMatch_s_abbr) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, team_pcp_ap_fte_total, "PCP/AP FTE")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, obs_exp_panel_ratio, "Obs:Exp")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, non_va_cons_per_10k_pcmm, 
                      "Non-VA Consults per 10k Uniques")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, nosos_risk_score, "NOSOS")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, adi_natRnk_avg, "ADI")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, pct_rural, "% Rural")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, panel_fullness, "Panel Fullness")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, est_pc_pt_wt_pid, "EPWT")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, new_pc_pt_wt, "NPWT")) %>%
  bind_rows(ttest_fxn(analytic_df_noMatch, third_next_avail, "TNA")) %>%
  kbl(col.names = c("Variable", "CRH Value (SD)", "Control Value (SD)", "p for difference",
                    "Start Month", "End Month")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

## Matched
```{r}
match_s_abbr <- analytic_df_matched %>%
  filter(vssc_month == ymd("2018-09-01")) %>%
  group_by(crh_flag, s_abbr2) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = crh_flag, values_from = count) %>%
  mutate(t_test_p = "NA", 
         start_month = "2018-09-01",
         end_month = "2018-09-01") %>%
  rename(crh_val = `PC CRH`,
         ctrl_val = `No PC CRH`,
         covar_name = s_abbr2) %>%
  janitor::adorn_totals() %>%
  mutate(crh_val = as.character(crh_val),
         ctrl_val = as.character(ctrl_val))
#--
matched_encounter_tot <- analytic_df_matched %>%
  filter(vssc_month > ymd("2018-06-01")
         & vssc_month < ymd("2018-10-01")) %>%
  group_by(crh_flag) %>%
  summarise(pc_enc_tot = comma(sum(pc_encounter_total, na.rm = T), accuracy = 1)) %>%
  mutate(covar_name = "Total PC Encounters") %>%
  pivot_wider(names_from = crh_flag, values_from = pc_enc_tot) %>%
  mutate(t_test_p = "NA",
         start_month = "2018-07-01",
         end_month = "2018-09-01") %>%
  rename(crh_val = `PC CRH`,
         ctrl_val = `No PC CRH`)
#--
matched_encounter_tot %>%
  bind_rows(ttest_fxn(analytic_df_matched, pc_encounter_total, "PC Encounters per month")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, scrssn_count_avg_fy18, "Unique ScrSSNs")) %>%
  bind_rows(., match_s_abbr) %>%
  bind_rows(ttest_fxn(analytic_df_matched, team_pcp_ap_fte_total, "PCP/AP FTE")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, obs_exp_panel_ratio, "Obs:Exp")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, non_va_cons_per_10k_pcmm, 
                      "Non-VA Consults per 10k Uniques")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, nosos_risk_score, "NOSOS")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, adi_natRnk_avg, "ADI")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, pct_rural, "% Rural")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, panel_fullness, "Panel Fullness")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, est_pc_pt_wt_pid, "EPWT")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, new_pc_pt_wt, "NPWT")) %>%
  bind_rows(ttest_fxn(analytic_df_matched, third_next_avail, "TNA")) %>%
  kbl(col.names = c("Variable", "CRH Value (SD)", "Control Value (SD)", "p for difference",
                    "Start Month", "End Month")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

# Plots  

## Average Values Over Time  
```{r}
plot_fxn <- function(outcome, outcome_c){
  ylab <- if(outcome_c == "est_pc_pt_wt"){
    "EPWT (days)"
  }
  else if(outcome_c == "new_pc_pt_wt"){
    "NPWT (days)"
  }
  else{
    "TNA (days)"
  }
#
    df <- if(outcome_c == "est_pc_pt_wt"){
    analytic_df
  }
  else if(outcome_c == "new_pc_pt_wt"){
    analytic_df
  }
  else{
    analytic_df2
  }
  ggplot(data = df,
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_smooth(linewidth = 1, data = subset(df, vssc_month < ymd("2019-10-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    geom_smooth(linewidth = 1, data = subset(df, vssc_month > ymd("2019-09-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    ggthemes::scale_color_colorblind() +
    theme(axis.title.x = element_blank()) +
    labs(y = ylab) +
    scale_y_continuous(limits = c(0, NA))
}
#
```

```{r}
reg_dates <- tibble(vssc_month = seq.Date(ymd("2018-10-01"), ymd("2020-02-01"), "1 month")) %>%
  rowid_to_column(., var = "time") %>%
  mutate(time2 = time - 12)
#--
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., reg_dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
analytic_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df$treat <- relevel(analytic_df$treat, ref = 'Control')
```

```{r}
ps_matched_5_2 <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_2.csv"))
#this is where exclusion criteria are applied:
sta5as_to_include2 <- ps_matched_5_2 %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df2 <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include2) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., reg_dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
analytic_df2$post <- relevel(analytic_df2$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df2$treat <- relevel(analytic_df2$treat, ref = 'Control')
```

```{r}
est_p <- plot_fxn(est_pc_pt_wt, "est_pc_pt_wt")
#
new_p <- plot_fxn(new_pc_pt_wt, "new_pc_pt_wt")
#
tna_p <- plot_fxn(third_next_avail, "third_next_avail")
#
gridExtra::grid.arrange(est_p, new_p, tna_p, ncol = 1)
```

## Predicted Values  

```{r}
bline_trend1 <- lmer(est_pc_pt_wt ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + nosos_risk_score
                     + adi_natRnk_avg
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_1 <- ggeffects::ggpredict(bline_trend1, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., reg_dates, by = c("x" = "time2"))
#--
pred_p_1 <- ggplot(data = pred_1,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_1, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  geom_line(data = subset(pred_1, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title.x = element_blank()) +
  labs(y = "Predicted EPWT")
```
```{r}
bline_trend2 <- lmer(new_pc_pt_wt ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + nosos_risk_score
                     + adi_natRnk_avg
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_2 <- ggeffects::ggpredict(bline_trend2, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., reg_dates, by = c("x" = "time2"))
#--
pred_p_2 <- ggplot(data = pred_2,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_2, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  geom_line(data = subset(pred_2, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title.x = element_blank()) +
  labs(y = "Predicted NPWT")
```

```{r}
bline_trend3 <- lmer(third_next_avail ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + nosos_risk_score
                     + adi_natRnk_avg
                     + (1|sta5a),
                     data = analytic_df2,
                     REML = TRUE)
#
pred_3 <- ggeffects::ggpredict(bline_trend3, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., reg_dates, by = c("x" = "time2"))
#--
pred_p_3 <- ggplot(data = pred_3,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_3, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  geom_line(data = subset(pred_3, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title.x = element_blank()) +
  labs(y = "Predicted TNA")
```

```{r}
gridExtra::grid.arrange(pred_p_1, pred_p_2, pred_p_3,
                        ncol = 1)
```