---
title: "GANTT 1.5.6"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
# theme_update(axis.title = element_text(size = 20),
#              axis.text = element_text(size = 16),
#              strip.text = element_text(size = 14),
#              legend.text = element_text(size = 18),
#              legend.title = element_blank(),
#              plot.caption = element_text(size = 12),
#              legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
sta5as_to_start <- vast %>%
  left_join(., scrssn_count %>%
              select(sta5a, scrssn_count_cat)) %>%
  filter(s_abbr %in% c("PCCBOC", "MSCBOC", "HCC", "OOS", "VAMC")
         & scrssn_count_cat != "< 450") %>%
  select(sta5a)
#==
analytic_df <- sta5as_to_start %>%
  cross_join (., dates %>%
                select(vssc_month)) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  left_join(., pen_rate %>%
              select(sta5a, vssc_month, crh_encounter_count)) %>%
  left_join(., ps_matched %>%
              select(sta5a, treated, treated_num)) %>%
  mutate(crh_encounter_count0 = replace_na(crh_encounter_count, 0),
         treated_num = replace_na(treated_num, 0),
         treated = replace_na(treated, "Control"),
         gap_cat = factor(case_when(gap_metric < 1.0 ~ "< 1.0",
                             gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
                             gap_metric > 1.2 ~ "> 1.2",
                             TRUE ~ "Missing"),
                          ordered = TRUE,
                          levels = c("< 1.0", "1.0 - 1.2", "> 1.2", "Missing")))
```

# Front Matter  

## Description of this report  

* This report addresses section 1.5.6 of the GANTT chart
* This report is an exploration of PC CRH encounters vs. the gap metric
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This PS model consists of 
        + Covariates matched on their average values over Q4 FY20
        + Outcomes matched on their average values over Q4 FY20
        + Site type (CBOC, VAMC/HCC, OOS) - Exact


```{r}
p1 <- analytic_df %>%
  filter(gap_metric < 3) %>%
  ggplot(data = .,
         aes(x = gap_metric, y = crh_encounter_count0)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm",
              se = FALSE) +
  ggpubr::stat_cor(method = "pearson") +
  labs(x = "Gap Metric",
       y = "CRH Encounters",
       title = "All Sta5as, with Zeros")
p2 <- analytic_df %>%
  filter(gap_metric < 3) %>%
  ggplot(data = .,
         aes(x = gap_metric, y = crh_encounter_count)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm",
              se = FALSE) +
  ggpubr::stat_cor(method = "pearson") +
  labs(x = "Gap Metric",
       y = "CRH Encounters",
       title = "All Sta5as, without Zeros")
#
cowplot::plot_grid(p1, p2)
```

```{r}
p1 <- analytic_df %>%
  filter(gap_metric < 3
         & treated_num == 0) %>%
  ggplot(data = .,
         aes(x = gap_metric, y = crh_encounter_count0)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm",
              se = FALSE) +
  ggpubr::stat_cor(method = "pearson") +
  labs(x = "Gap Metric",
       y = "CRH Encounters",
       title = "Controls, with zeros")
#
p2 <- analytic_df %>%
  filter(gap_metric < 3
         & treated_num == 0) %>%
  ggplot(data = .,
         aes(x = gap_metric, y = crh_encounter_count)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm",
              se = FALSE) +
  ggpubr::stat_cor(method = "pearson") +
  labs(x = "Gap Metric",
       y = "CRH Encounters",
       title = "Controls, without zeros") 
#--
cowplot::plot_grid(p1, p2)
```

```{r}
analytic_df %>%
  group_by(treated_num) %>%
  summarise(total_pc_crh = sum(crh_encounter_count, na.rm = T),
            sites = n() / 36) %>%
  mutate(pc_crh_per_site = comma(total_pc_crh / sites, accuracy = 0.1),
         total_pc_crh = comma(total_pc_crh, accuracy = 1),
         treated_num = if_else(treated_num == 1, "Treated", "Control")) %>%
  kbl(col.names = c("", "Total PC CRH Encounters", "Sta5a", "PC CRH per sta5a"),
      align = c("l", rep("r", 3)),
      full_width = F) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
#
control_mt_0_pc_crh <- analytic_df %>%
  filter(treated_num == 0) %>%
  group_by(sta5a) %>%
  summarise(tot_pc_crh = sum(crh_encounter_count, na.rm = T)) %>%
  filter(tot_pc_crh > 0)
```

* There are `r nrow(control_mt_0_pc_crh)` control sta5as that had at least 1 PC CRH encounter in our study period

```{r}


#--
p1 <- analytic_df %>%
  filter(treated_num == 0) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black",
                 fill = "dodgerblue") +
  labs(x = "CRH Encounters per Month",
       y = "Sta5a-Months") +
  scale_y_continuous(labels = scales::comma_format())
#
p2 <- analytic_df %>%
  filter(treated_num == 0
         & crh_encounter_count < 31) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black",
                 fill = "seagreen") +
  labs(x = "CRH Encounters per Month",
       y = "Sta5a-Months",
       caption = "*Only the first 30 integers") +
  scale_y_continuous(labels = scales::comma_format())
#
p3 <- analytic_df %>%
  filter(treated_num == 0) %>%
  ggplot(data = .,
         aes(y = crh_encounter_count)) +
  geom_boxplot(fill = "darkorchid") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "PC CRH Encounters per Month")
#
cowplot::plot_grid(p1, p2)
#
p3
```

```{r}

analytic_df %>%
  filter(sta5a %in% control_mt_0_pc_crh$sta5a) %>%
  group_by(gap_cat) %>%
  summarise(observations = n(),
            tot_pc_crh = sum(crh_encounter_count0),
            mean_pc_crh = mean(crh_encounter_count, na.rm = T),
            mean_pc_crh0 = mean(crh_encounter_count0),
            qtl_25 = comma(quantile(crh_encounter_count, 0.25, na.rm = T)),
            qtl_75 = comma(quantile(crh_encounter_count, 0.75, na.rm = T)),
            qtl_025 = comma(quantile(crh_encounter_count, 0.025, na.rm = T)),
            qtl_975 = comma(quantile(crh_encounter_count, 0.975, na.rm = T))) %>%
  mutate(across(c(4:5), ~comma(.x, accuracy = 0.01)),
         qtl_25_75 = paste0("[", qtl_25, ", ", qtl_75, "]"),
         qtl_025_975 = paste0("[", qtl_025, ", ", qtl_975, "]")) %>%
  select(-c(qtl_25, qtl_75, qtl_025, qtl_975)) %>%
  adorn_totals() %>%
  mutate(across(c(2, 3), ~comma(.x, accuracy = 1))) %>%
  kbl(col.names = c("", "Observations", "PC CRH Encounters", "Avg. PC CRH", "Avg. PC CRH (with zeros)",
                    "[25th %ile, 75th %ile]", "[2.5th %ile, 97.5th %ile]"),
      align = c("l", rep("r", 6))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
#
p1 <- analytic_df %>%
  filter(treated_num == 0
         & is.na(gap_metric) == F) %>%
  ggplot(data = .,
         aes(fill = gap_cat, y = crh_encounter_count, group = gap_cat)) +
  geom_boxplot() +
  theme(legend.position = "right",
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "CRH Encounters per Month",
       fill = "Gap")
#
p2 <- analytic_df %>%
  filter(treated_num == 0
         & is.na(gap_metric) == F) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count, fill = gap_cat)) +
  geom_histogram(color = "black") +
  facet_wrap(~gap_cat) +
  labs(x = "CRH Encounters",
       y = "Sta5a-Months",
       fill = "Gap")
#
cowplot::plot_grid(p1, p2)
```

## Missing Gap?  

```{r}
missing_gap_sta5as <- analytic_df %>% 
  filter(gap_cat == "Missing"
         & sta5a %in% control_mt_0_pc_crh$sta5a) %>%
  select(sta5a) %>%
  distinct
```

* What's up with the `r nrow(missing_gap_sta5as)` sta5as missing gap?

```{r}
gap_metric %>%
  inner_join(., dates %>% select(vssc_month)) %>%
  filter(sta5a %in% missing_gap_sta5as$sta5a) %>%
  select(sta5a, vssc_month, observed_ps_tot, expected_ps_tot) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  ggplot(data = .,
         aes(y = value, x = vssc_month, group = name, color = name)) +
  geom_line() +
  facet_wrap(~sta5a) +
  scale_y_continuous(labels = scales::comma_format(accuracy = 1)) +
  labs(x = "Month",
       y = "Panel Size")
```

# Categorizing CRH Encounters  
```{r}
crh_enc_qntl_33 <- analytic_df %>%
  filter(treated_num == 0) %>%
  summarise(qntl_33 = quantile(crh_encounter_count, 0.333, na.rm = T)) %>%
  pull()
crh_enc_qntl_66 <- analytic_df %>%
  filter(treated_num == 0) %>%
  summarise(qntl_66 = quantile(crh_encounter_count, 0.667, na.rm = T)) %>%
  pull()
```

* The first tertile of CRH encounters among these sta5as is `r crh_enc_qntl_33`
* The second tertile of CRH encounters among these sta5as is `r crh_enc_qntl_66`

```{r}
chisq_df <- analytic_df %>%
  filter(treated_num == 0) %>%
  mutate(crh_trtl = factor(case_when(crh_encounter_count <= crh_enc_qntl_33 ~ "Bottom 1/3",
                                     crh_encounter_count > crh_enc_qntl_33 & crh_encounter_count <= crh_enc_qntl_66 ~ "Middle 1/3",
                                     crh_encounter_count > crh_enc_qntl_66 ~ "Top 1/3",
                                     TRUE ~ "No PC CRH"),
                           ordered = TRUE,
                           levels = c("Bottom 1/3", "Middle 1/3", "Top 1/3", "No PC CRH")))
#
crh_gap_chisq <- chisq_df %>%
  filter(treated_num == 0) %>%
  tabyl(gap_cat, crh_trtl) %>%
  chisq.test()
#--
crh_gap_chisq$observed %>%
  tibble() %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 1))) %>%
  kbl(col.names = c("Gap", "Bottom 1/3", "Middle 1/3", "Top 1/3", "No PC CRH", "Total"),
      full_width = F,
      align = c("l", rep("r", 5)),
      caption = "<b>Observed</b>") %>%
  kable_classic("striped") %>%
  row_spec(c(0, 5), bold = TRUE) %>%
  add_header_above(c("", "Tertiles of PC CRH Encounters" = 4, ""),
                   bold = T)
#--
crh_gap_chisq$expected %>%
  tibble() %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("Gap", "Bottom 1/3", "Middle 1/3", "Top 1/3", "No PC CRH", "Total"),
      full_width = F,
      align = c("l", rep("r", 5)),
      caption = "<b>Expected</b>") %>%
  kable_classic("striped") %>%
  row_spec(c(0, 5), bold = TRUE) %>%
  add_header_above(c("", "Tertiles of PC CRH Encounters" = 4, ""),
                   bold = T)
#
crh_gap_chisq
```

# No CRH X Gap < 1.0  

```{r}
no_crh_gap_lt_1 <- analytic_df %>%
  mutate(flag_ = if_else(treated_num == 0
         & gap_metric < 1.0
         & crh_encounter_count0 == 0, 1, 0)) %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(months_meet_crit_3 = if_else(flag_ == 1 
                                      & lead(flag_, 1) == 1
                                      & lead(flag_, 2) == 1, 1, 0)) %>%
  summarise(keep_me = if_else(sum(months_meet_crit_3) > 0, 1, 0)) %>%
  filter(keep_me == 1) %>%
  select(sta5a) %>%
  distinct()
#
treated_ever_never_gap <- analytic_df %>%
  filter(treated_num == 1) %>%
  group_by(sta5a) %>%
  summarise(ever_gap_lt_1 = 
              if_else(
                sum(
                  if_else(gap_metric < 1.0, 1, 0), na.rm = T) > 0, 
                1, 0),
            month_count = 
              sum(
                if_else(gap_metric < 1.0, 
                        1, 0), na.rm = T))
```

* There are `r nrow(no_crh_gap_lt_1)` control sta5as that have at least 3 consecutive months with 0 CRH Encounters and a gap metric < 1.0

```{r}
no_crh_gap_lt_1 %>%
  left_join(., vast) %>%
  group_by(parent_visn) %>%
  tally() %>%
  left_join(., vast %>%
              filter(sta5a %in% sta5as_to_start$sta5a) %>%
              group_by(parent_visn) %>%
              summarise(tot_sta5a = n())) %>%
  mutate(prop_sta5as = n / tot_sta5a) %>%
  left_join(., vast %>%
              inner_join(., treated_ever_never_gap %>% 
                           filter(ever_gap_lt_1 == 1) %>%
                           select(sta5a)) %>%
              group_by(parent_visn) %>%
              summarise(count_treated = n()),
            by = "parent_visn") %>%
  left_join(., vast %>%
              inner_join(., treated_ever_never_gap %>% 
                           filter(ever_gap_lt_1 == 0) %>%
                           select(sta5a)) %>%
              group_by(parent_visn) %>%
              summarise(count_treated = n()),
            by = "parent_visn") %>%
  mutate(prop_treated.x = count_treated.x / tot_sta5a,
         prop_treated.y = count_treated.y / tot_sta5a,
         across(contains("prop_"), ~percent(.x, accuracy = 0.1))) %>%
  adorn_totals() %>%
  mutate(tot_sta5a = comma(tot_sta5a),
         col.a = paste0(n, " (", prop_sta5as, ")"),
         col.x = paste0(count_treated.x, " (", prop_treated.x, ")"),
         col.y = paste0(count_treated.y, " (", prop_treated.y, ")")) %>%
  select(parent_visn, tot_sta5a, col.a, col.x, col.y) %>%
  kbl(col.names = c("VISN", "Sta5as in VISN", "Controls w/ at Least 3 months w/ gap < 1.0 & 0 PC CRH (%)",
                    "Treated Sta5as, Ever Gap (%)", "Treated Sta5as, Never Gap (%)"),
      full_width = F,
      align = c("c", rep("r", 4))) %>%
  kable_classic("striped") %>%
  row_spec(c(0, 19), bold = TRUE)
```

## More restrictive criteria  

* In the table below sta5as in the "Treated Ever Gap" column needed to have at least 3 consecutive months with a gap < 1.0

```{r}
treated_3mos_ever_never_gap <- analytic_df %>%
  filter(treated_num == 1) %>%
  mutate(gap_lt_1 = if_else(gap_metric < 1.0, 1, 0)) %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(flag_ = if_else(gap_lt_1 == 1
                                       & lead(gap_lt_1, 1) == 1
                                       & lead(gap_lt_1, 2) == 1, 1, 0)) %>%
  group_by(sta5a) %>%
  summarise(ge_3mos_gap_lt_1 = if_else(sum(flag_, na.rm = T) > 0, 1, 0),
            month_count = sum(gap_lt_1, na.rm = T))

#
no_crh_gap_lt_1 %>%
  left_join(., vast) %>%
  group_by(parent_visn) %>%
  tally() %>%
  left_join(., vast %>%
              filter(sta5a %in% sta5as_to_start$sta5a) %>%
              group_by(parent_visn) %>%
              summarise(tot_sta5a = n())) %>%
  mutate(prop_sta5as = n / tot_sta5a) %>%
  left_join(., vast %>%
              inner_join(., treated_3mos_ever_never_gap %>% 
                           filter(ge_3mos_gap_lt_1 == 1) %>%
                           select(sta5a)) %>%
              group_by(parent_visn) %>%
              summarise(count_treated = n()),
            by = "parent_visn") %>%
  left_join(., vast %>%
              inner_join(., treated_3mos_ever_never_gap %>% 
                           filter(ge_3mos_gap_lt_1 == 0) %>%
                           select(sta5a)) %>%
              group_by(parent_visn) %>%
              summarise(count_treated = n()),
            by = "parent_visn") %>%
  mutate(prop_treated.x = count_treated.x / tot_sta5a,
         prop_treated.y = count_treated.y / tot_sta5a,
         across(contains("count_"), ~replace_na(.x, 0)),
         across(contains("prop_"), ~replace_na(.x, 0)),
         across(contains("prop_"), ~percent(.x, accuracy = 0.1))) %>%
  adorn_totals() %>%
  mutate(tot_sta5a = comma(tot_sta5a),
         col.a = paste0(n, " (", prop_sta5as, ")"),
         col.x = paste0(count_treated.x, " (", prop_treated.x, ")"),
         col.y = paste0(count_treated.y, " (", prop_treated.y, ")")) %>%
  select(parent_visn, tot_sta5a, col.a, col.x, col.y) %>%
  kbl(col.names = c("VISN", "Sta5as in VISN", "Controls w/ at Least 3 months w/ gap < 1.0 & 0 PC CRH (%)",
                    "Treated Sta5as, Ever Gap (%)", "Treated Sta5as, Never Gap (%)"),
      full_width = F,
      align = c("c", rep("r", 4))) %>%
  kable_classic("striped") %>%
  row_spec(c(0, 19), bold = TRUE)
```

## Number of Months  

```{r}
months_no_crh_gap_lt_1 <- analytic_df %>%
  mutate(flag_ = if_else(treated_num == 0
                         & gap_metric < 1.0
                         & crh_encounter_count0 == 0, 1, 0)) %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(months_meet_crit_3 = if_else(flag_ == 1 
                                      & lead(flag_, 1) == 1
                                      & lead(flag_, 2) == 1, 1, 0)) %>%
  summarise(keep_me = if_else(sum(months_meet_crit_3) > 0, 1, 0),
            month_count = sum(months_meet_crit_3)) %>%
  filter(keep_me == 1) %>%
  distinct()
#--
months_no_crh_gap_lt_1 %>%
  left_join(., vast) %>%
  group_by(parent_visn) %>%
  summarise(ctrl_gap_sta5a_count = n(),
            ctrl_month_gap_count = sum(month_count)) %>%
  left_join(., vast %>%
              filter(sta5a %in% sta5as_to_start$sta5a) %>%
              group_by(parent_visn) %>%
              summarise(sta5a_count_tot = n(),
                        tot_months = n() * 36)) %>%
  left_join(., vast %>%
              select(sta5a, parent_visn) %>%
              inner_join(., treated_ever_never_gap %>% 
                           filter(ever_gap_lt_1 == 1)) %>%
              group_by(parent_visn) %>%
              summarise(month_count = sum(month_count)),
            by = "parent_visn") %>%
  left_join(., vast %>%
              select(sta5a, parent_visn) %>%
              inner_join(., treated_ever_never_gap %>% 
                           filter(ever_gap_lt_1 == 0)) %>%
              group_by(parent_visn) %>%
              summarise(month_count = sum(month_count)),
            by = "parent_visn") %>%
  mutate(prop.a = ctrl_month_gap_count / tot_months,
         prop.x = month_count.x / tot_months,
         prop.y = month_count.y / tot_months,
         across(contains("prop"), ~percent(.x, accuracy = 0.1))) %>%
  adorn_totals() %>%
  mutate(col.a = paste0(ctrl_month_gap_count, " (", prop.a, ")"),
         col.x = paste0(month_count.x, " (", prop.x, ")"),
         col.y = paste0(month_count.y, " (", prop.y, ")"),
         tot_months = comma(tot_months)) %>%
  select(parent_visn, sta5a_count_tot, tot_months, col.a, col.x, col.y) %>%
  kbl(col.names = c("VISN", "Sta5as in VISN", "Sta5a-Months of Observation",
                    "Control Sta5a-Months w/ gap < 1.0 & 0 PC CRH",
                    "Treated Sta5a-Months w/ gap < 1.0",
                    "foo"),
      full_width = F,
      align = c("c", rep("r", 5))) %>%
  kable_classic("striped") %>%
  row_spec(c(0, 19), bold = TRUE)
```

### More restrictive criteria  

```{r}
months_no_crh_gap_lt_1 %>%
  left_join(., vast) %>%
  group_by(parent_visn) %>%
  summarise(ctrl_gap_sta5a_count = n(),
            ctrl_month_gap_count = sum(month_count)) %>%
  left_join(., vast %>%
              filter(sta5a %in% sta5as_to_start$sta5a) %>%
              group_by(parent_visn) %>%
              summarise(sta5a_count_tot = n(),
                        tot_months = n() * 36)) %>%
  left_join(., vast %>%
              select(sta5a, parent_visn) %>%
              inner_join(., treated_3mos_ever_never_gap %>% 
                           filter(ge_3mos_gap_lt_1 == 1)) %>%
              group_by(parent_visn) %>%
              summarise(month_count = replace_na(sum(month_count, na.rm = T), 0)),
            by = "parent_visn") %>%
  left_join(., vast %>%
              select(sta5a, parent_visn) %>%
              inner_join(., treated_3mos_ever_never_gap %>% 
                           filter(ge_3mos_gap_lt_1 == 0)) %>%
              group_by(parent_visn) %>%
              summarise(month_count = replace_na(sum(month_count, na.rm = T), 0)),
            by = "parent_visn") %>%
  mutate(across(contains("month_"), ~replace_na(.x, 0)),
         prop.a = ctrl_month_gap_count / tot_months,
         prop.x = month_count.x / tot_months,
         prop.y = month_count.y / tot_months,
         across(contains("prop"), ~percent(.x, accuracy = 0.1))) %>%
  adorn_totals() %>%
  mutate(col.a = paste0(ctrl_month_gap_count, " (", prop.a, ")"),
         col.x = paste0(month_count.x, " (", prop.x, ")"),
         col.y = paste0(month_count.y, " (", prop.y, ")"),
         tot_months = comma(tot_months)) %>%
  select(parent_visn, sta5a_count_tot, tot_months, col.a, col.x, col.y) %>%
  kbl(col.names = c("VISN", "Sta5as in VISN", "Sta5a-Months of Observation",
                    "Control Sta5a-Months w/ gap < 1.0 & 0 PC CRH",
                    "Treated Sta5a-Months w/ 3 months gap < 1.0",
                    "Treated Sta5a-Months w/ gap < 1.0"),
      full_width = F,
      align = c("c", rep("r", 5))) %>%
  kable_classic("striped") %>%
  row_spec(c(0, 19), bold = TRUE)
```