---
title: "High/Low CRH Users by Gap Metric: GANTT 1.4"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(magrittr)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(gap_metric_cat = factor(case_when(gap_metric >= 1.2 ~ "> 1.2",
                                    gap_metric < 1 ~ "< 1.0",
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ "1.0-1.2"),
                                 ordered = TRUE,
                                 levels = c("< 1.0", "1.0-1.2", "> 1.2")))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- ps_matched %>%
  filter(treated_num == 1) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
     # filter(vssc_month > ymd("2019-09-01")) %>%#restrict to our timeframe
      left_join(., dates)
```

# Front Matter  

## Description of this report  

* This is a report for section 1.4 of the GANTT chart
* The sites included here are the `r length(crh_sta5as)` Treated sites that met meaningful use criteria

# Classify High/Low CRH Utilizers by Gap Metric  


# CRH Encounters  
## Total

```{r}
p1 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  group_by(sta5a) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black", fill = "seagreen") +
  labs(x = "Total CRH Encounters",
       y = "Observations") +
  scale_x_continuous(labels = scales::comma_format())
#
p2 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  group_by(sta5a) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  filter(sta5a %in% crh_sta5as) %>%
  ggplot(data = ., 
         aes(y = crh_encounter_count, x = "a")) +
  geom_boxplot(color = "black", fill = "darkorchid") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "Total CRH Encounters") +
  scale_y_continuous(labels = scales::comma_format())
#-----
multiplot(p1, p2, cols = 2)
```


### Total by Site Type  

```{r}
p1 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  group_by(sta5a) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black", fill = "dodgerblue") +
  labs(x = "Total CRH Encounters",
       y = "Observations") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~s_abbr) +
  scale_x_continuous(labels = scales::comma_format())
#
p2 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  group_by(sta5a) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  ggplot(data = .,
         aes(x = s_abbr, y = crh_encounter_count)) +
  geom_boxplot(color = "black", 
               fill = "aquamarine3") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(y = "Total CRH Encounters") +
  theme(axis.title.x = element_blank())
#
multiplot(p1, p2, cols = 2)
```

## Per Month  
```{r}
p1 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black", fill = "dodgerblue") +
  labs(x = "CRH Encounters per Month",
       y = "Observations") +
  scale_y_continuous(labels = scales::comma_format())
#
p2 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  ggplot(data = ., 
         aes(y = crh_encounter_count, x = "a")) +
  geom_boxplot(color = "black", fill = "darkorchid") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "CRH Encounters per Month")
#-----
multiplot(p1, p2, cols = 2)
```

### Per Month by Site Type  

```{r}
p1 <- pen_rate %>% inner_join(., dates) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black", fill = "seagreen") +
  labs(x = "CRH Encounters per Month",
       y = "Observations") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~s_abbr)
#
p2 <- pen_rate %>% inner_join(., dates) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  ggplot(data = ., 
         aes(y = crh_encounter_count, x = s_abbr)) +
  geom_boxplot(color = "black", fill = "darkorchid") +
  theme(axis.title.x = element_blank()) +
  labs(y = "CRH Encounters per Month")
#-----
multiplot(p1, p2, cols = 2)
```

# Per Month by Gap Metric Category  

```{r}
pen_rate %>% inner_join(., dates) %>%
  left_join(., gap_metric) %>%
  filter(sta5a %in% sta5as_to_include$sta5a
         & crh_encounter_count > 0
         & is.na(gap_metric_cat) == F) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black",
                 fill = "blueviolet") +
  facet_wrap(~gap_metric_cat) +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "CRH Encounters per Month",
       y = "Observations",
       caption = "*Only sta5a-months with > 0 CRH encounters")
#
pen_rate %>% inner_join(., dates) %>%
  left_join(., gap_metric) %>%
  filter(sta5a %in% sta5as_to_include$sta5a
         & crh_encounter_count > 0
         & is.na(gap_metric_cat) == F) %>%
  ggplot(data = .,
         aes(y = crh_encounter_count,
             x = gap_metric_cat)) +
  geom_boxplot(color = "black",
                 fill = "cadetblue4") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(y = "CRH Encounters per Month",
       x = "Gap Metric",
       caption = "*Only treated sta5as with at least 1 CRH encounter that month")
```

### As tables    
```{r}
tab1 <- sta5as_to_include %>%
  select(sta5a) %>%
  cross_join(., dates %>% select(vssc_month)) %>%
  left_join(., pen_rate) %>%
  left_join(., gap_metric) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  mutate(crh_encounter_count = replace_na(crh_encounter_count, 0))
```

* There are `r nrow(tab1)`sta5a-months included
* These come from `r n_distinct(tab1$sta5a)` unique sta5as


```{r}
tab1 %>%
  tabyl(gap_metric_cat) %>%
  adorn_totals("row") %>%
  select(-valid_percent) %>%
  mutate(n = scales::comma(n),
         percent = scales::percent(percent, accuracy = 0.1)) %>%
  kbl(col.names = c("Gap Category", "Observations", "%"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(c(0, 5), bold = T)
#
tab1 %>%
  group_by(gap_metric_cat) %>%
  summarise(mean_val = comma(mean(crh_encounter_count), accuracy = 0.1),
            sd_val = comma(sd(crh_encounter_count), accuracy = 0.1),
            n_obs = n(),
            min_val = min(crh_encounter_count),
            max_val = comma(max(crh_encounter_count)),
            qtl_25 = quantile(crh_encounter_count, 0.25),
            qtl_85 = quantile(crh_encounter_count, 0.85)) %>%
  mutate(mean_sd = paste0(mean_val, " (", sd_val, ")"),
         min_max = paste0("[", min_val, ", ", max_val, "]"),
         qtls = paste0("{", qtl_25, ", ", qtl_85, "}")) %>%
  adorn_totals("row") %>%
  mutate(n_obs = comma(n_obs)) %>%
  select(gap_metric_cat, n_obs, mean_sd, min_max, qtls) %>%
  kbl(col.names = c("Gap Category", "Observations", "Mean (SD)", "[Min., Max.]", "{25th %-ile, 85th %-ile}"),
      align = c("l", rep("r", 4)),
      caption = "<b>CRH Encounters per Month by Gap Category</b>") %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(c(0, 5), bold = T)
```

# Per Month by Continuous Gap Metric  

```{r}
gap_encounter_cor <- pen_rate %>% 
  inner_join(., dates) %>%
  left_join(., gap_metric) %>%
  filter(sta5a %in% sta5as_to_include$sta5a
         & gap_metric < 5) %$%
  cor(gap_metric, crh_encounter_count, "complete.obs") %>%
  comma(., accuracy = 0.001)
#
pen_rate %>% inner_join(., dates) %>%
  left_join(., gap_metric) %>%
  filter(sta5a %in% sta5as_to_include$sta5a
         & gap_metric < 5) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count, y = gap_metric)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm", se = F) +
  geom_text(x = 500, y = 3.5,
            label = paste0("r = ", gap_encounter_cor),
            color = "red") +
  labs(x = "CRH Encounters per Month",
       y = "Gap Metric")
```

# Proportion of Clinics With a Gap That Meet Meaningful Use    


```{r}
create_formatted_totals <- function(rows, cols, dat) {
  dat_pct <- dat |>
    tabyl({{ rows }}, {{ cols }}) |>
    adorn_percentages() |>
    adorn_pct_formatting() |>
    adorn_ns(position = "front")
  
  
  totals <- dat |>
    tabyl({{ rows }}, {{ cols }}) |>
    adorn_totals(c("row", "col")) |>
    mutate(across(where(is.numeric), comma))
  
  # Add row totals
  dat_pct$Total <- head(totals$Total, -1)
  
  # Add col totals
  dat_pct <- rbind(dat_pct, tail(totals, 1))
  
  return(dat_pct)
}
#
create_formatted_totals(crh_cat, gap_metric_cat, pen_rate %>% inner_join(., dates) %>%
                          left_join(., gap_metric) %>%
                          filter(sta5a %in% crh_sta5as) %>%
                          mutate(crh_encounter_count = replace_na(crh_encounter_count, 0),
                                 crh_cat = if_else(crh_encounter_count > 9, "Yes", "No"))) %>%
  kbl(col.names = c("At Least 10 CRH Encounters?", "Gap < 1.0", "Gap 1.0-1.2", "Gap > 1.2", "Missing", "Total"),
      align = c("l", rep("r", 5))) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(c(0, 3), bold = TRUE)
```


# CRH Penetration Rate    

```{r}
p1 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  ggplot(data = .,
         aes(x = pc_crh_per_1k_total_pc)) +
  geom_histogram(color = "black", fill = "seagreen") +
  labs(x = "Penetration Rate",
       y = "Observations") +
  scale_x_continuous(labels = scales::comma_format()) +
  scale_y_continuous(labels = scales::comma_format())
#
p2 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  ggplot(data = ., 
         aes(y = pc_crh_per_1k_total_pc, x = "a")) +
  geom_boxplot(color = "black", fill = "darkorchid") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "Penetration Rate") +
  scale_y_continuous(labels = scales::comma_format())
#-----
multiplot(p1, p2, cols = 2)
```


### By Site Type  

```{r}
p1 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  ggplot(data = .,
         aes(x = pc_crh_per_1k_total_pc)) +
  geom_histogram(color = "black", fill = "dodgerblue") +
  labs(x = "Penetration Rate",
       y = "Observations") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~s_abbr) +
  scale_x_continuous(labels = scales::comma_format())
#
p2 <- pen_rate %>% inner_join(., dates) %>%
  filter(sta5a %in% sta5as_to_include$sta5a) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  ggplot(data = .,
         aes(x = s_abbr, y = pc_crh_per_1k_total_pc)) +
  geom_boxplot(color = "black", 
               fill = "aquamarine3") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(y = "Penetration Rate") +
  theme(axis.title.x = element_blank())
#
multiplot(p1, p2, cols = 2)
```

## By Gap Metric Category  

```{r}
pen_rate %>% inner_join(., dates) %>%
  left_join(., gap_metric) %>%
  filter(sta5a %in% sta5as_to_include$sta5a
         & crh_encounter_count > 0
         & is.na(gap_metric_cat) == F) %>%
  ggplot(data = .,
         aes(x = pc_crh_per_1k_total_pc)) +
  geom_histogram(color = "black",
                 fill = "blueviolet") +
  facet_wrap(~gap_metric_cat) +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "Penetration Rate",
       y = "Observations",
       caption = "*Only sta5as with at least 1 CRH encounter that month")
#
pen_rate %>% inner_join(., dates) %>%
  left_join(., gap_metric) %>%
  filter(sta5a %in% sta5as_to_include$sta5a
         & crh_encounter_count > 0
         & is.na(gap_metric_cat) == F) %>%
  ggplot(data = .,
         aes(y = pc_crh_per_1k_total_pc,
             x = gap_metric_cat)) +
  geom_boxplot(color = "black",
                 fill = "cadetblue4") +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(y = "Penetration Rate",
       x = "Gap Metric",
       caption = "*Only sta5as with at least 1 CRH encounter that month")
```