---
title: "Graphical Display of PC Gap and CRH Utilization Over Time"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0),
         s_abbr2 = case_when(s_abbr %in% c("PCCBOC", "MSCBOC") ~ "CBOC",
                             s_abbr %in% c("VAMC", "HCC") ~ "VAMC/HCC",
                             s_abbr == "OOS" ~ "OOS")) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv")) %>%
  rename(treated_ever = treated_num)
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care) %>%
  inner_join(., dates) %>%
  mutate(panel_fullness_pct = panel_fullness * 100,
         panel_fullness_cat = factor(case_when(panel_fullness_pct < 80 ~ "<80%",
                                        panel_fullness_pct > 105 ~ ">105%",
                                        panel_fullness_pct >= 80 & panel_fullness_pct <= 105 ~ "80-105%"),
                                     ordered = TRUE,
                                     levels = c("<80%", "80-105%", ">105%")))
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>% 
  rename(sta5a = Sta6a, vssc_month = visitMonth)  %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness) %>%
  inner_join(., dates) %>%
  mutate(panel_fullness_pct = panel_fullness * 100,
         panel_fullness_cat = factor(case_when(panel_fullness_pct < 80 ~ "<80%",
                                        panel_fullness_pct > 105 ~ ">105%",
                                        panel_fullness_pct >= 80 & panel_fullness_pct <= 105 ~ "80-105%")))
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_metric_cat = factor(case_when(gap_metric >= 1.2 ~ "> 1.2",
                                    gap_metric < 1 ~ "< 1.0",
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ "1.0-1.2"),
                                 ordered = T,
                                 levels = c("< 1.0", "1.0-1.2", "> 1.2"))) %>%
  inner_join(., dates)
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month),
         treated_month = if_else(crh_encounter_count > 9, 1, 0)) %>%
  inner_join(., dates)
```


```{r time_varying_treated}
treated_sta5a <- ps_matched %>%
  filter(treated_ever == 1) %>%
  select(sta5a)
#
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    ((last_mo_mt9_pc_crh == 1 | is.na(last_mo_mt9_pc_crh)) 
                                     | (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh))),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit_both = meets_inc_crit,
         meets_inc_crit_fwd = if_else(this_mo_mt9_pc_crh == TRUE & (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh)), 1, 0)
         ) %>%
  filter(sta5a %in% treated_sta5a$sta5a) %>%
  right_join(., dates %>%
               select(vssc_month) %>%
               cross_join(., treated_sta5a)) %>%
  mutate(meets_inc_crit_both = replace_na(meets_inc_crit_both, 0),
         meets_inc_crit_fwd = replace_na(meets_inc_crit_fwd, 0),
         crh_enc_count_na = crh_encounter_count,
         crh_encounter_count = replace_na(crh_encounter_count, 0))
```


```{r}
sta5as_to_include <- vast %>%
  left_join(., scrssn_count) %>%
  filter(s_abbr %in% c("PCCBOC", "MSCBOC", "OOS", "VAMC", "HCC")
         & scrssn_count_cat != "< 450") %>%
  select(sta5a) %>%
  left_join(., ps_matched) %>%
  mutate(treated_ever = replace_na(treated_ever, 0))
```


# Front Matter  

## Description of this report  

* This report is to address GANTT section 1.5  


# Gap Metric  

## National  
```{r}
gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  group_by(vssc_month) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = ., 
         aes(x = vssc_month, y = gap_metric)) +
  geom_line() +
  scale_y_continuous(limits = c(0.75, NA)) +
  labs(x = "Month",
       y = "Gap Metric") +
  geom_hline(yintercept = 1.0, lty = 2) +
  geom_hline(yintercept = 1.2, lty = 3)
#--
p1 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  group_by(vssc_month) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(x = gap_metric)) +
  geom_histogram(color = "black",
                 fill = "aquamarine",
                 bins = 20) +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = "Gap Metric",
       y = "Observations/Months")
#
p2 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  group_by(vssc_month) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(x = "a", y = gap_metric)) +
  geom_boxplot(color = "black",
               fill = "dodgerblue") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Gap Metric")
#
multiplot(p1, p2, cols = 2)
```

## VISN    
```{r}
gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = ., 
         aes(x = vssc_month, y = gap_metric, color = parent_visn)) +
  geom_line() +
  scale_y_continuous(limits = c(0.75, NA)) +
  labs(x = "Month",
       y = "Gap Metric") +
  geom_hline(yintercept = 1.0, lty = 2) +
  geom_hline(yintercept = 1.2, lty = 3) +
  facet_wrap(~parent_visn) +
  theme(legend.position = "none")
#--
p1 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(x = gap_metric, fill = parent_visn)) +
  geom_histogram(color = "black",
                 bins = 20) +
  scale_y_continuous(breaks = seq(0, 10, 2)) +
  labs(x = "Gap Metric",
       y = "Observations/Months") +
  facet_wrap(~parent_visn) +
  theme(legend.position = "none")
#
p2 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(x = "a", y = gap_metric, fill = parent_visn)) +
  geom_boxplot(color = "black") +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none") +
  labs(y = "Gap Metric") +
  facet_wrap(~parent_visn)
#
multiplot(p1, p2, cols = 2)
#----
gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  group_by(parent_visn) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            sd_gap = sd(gap_metric, na.rm = T)) %>%
  ggplot(data = .,
         aes(y = mean_gap,
             ymin = mean_gap - sd_gap,
             ymax = mean_gap + sd_gap,
             x = reorder(parent_visn, mean_gap))) +
  geom_point() +
  geom_errorbar(width = 0.75) +
  scale_y_continuous(limits = c(0.85, NA)) +
  geom_hline(yintercept = 1.0, lty = 2) +
  geom_hline(yintercept = 1.2, lty = 3) +
  labs(y = "Mean Gap +/- SD(Gap)",
       x = "VISN")
```

## Site Type  

```{r}
p1 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  group_by(vssc_month, s_abbr) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = gap_metric, color = s_abbr)) +
  geom_line() +
  scale_y_continuous(limits = c(0.85, NA)) +
  geom_hline(yintercept = 1.0, lty = 2) +
  geom_hline(yintercept = 1.2, lty = 3) +
  labs(x = "Month",
       y = "Gap Metric")

p2 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, s_abbr2)) %>%
  group_by(vssc_month, s_abbr2) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = gap_metric, color = s_abbr2)) +
  geom_line() +
  scale_y_continuous(limits = c(0.85, NA)) +
  geom_hline(yintercept = 1.0, lty = 2) +
  geom_hline(yintercept = 1.2, lty = 3) +
  labs(x = "Month",
       y = "Gap Metric")
#--
multiplot(p1, p2)
```

```{r}
p1 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, s_abbr2)) %>%
  group_by(vssc_month, s_abbr2) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(x = gap_metric, fill = s_abbr2)) +
  geom_histogram(color = "black") +
  facet_wrap(~s_abbr2) +
  theme(legend.position = "none") +
  labs(x = "Gap Metric",
       y = "Observations/Months")
#
p2 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, s_abbr2)) %>%
  group_by(vssc_month, s_abbr2) %>%
  summarise(observed_ps_tot = sum(observed_ps_tot, na.rm = T),
            expected_ps_tot = sum(expected_ps_tot, na.rm = T)) %>%
  mutate(gap_metric = expected_ps_tot / observed_ps_tot) %>%
  ggplot(data = .,
         aes(y = gap_metric, fill = s_abbr2)) +
  geom_boxplot(color = "black") +
  facet_wrap(~s_abbr2) +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Gap Metric")
#
multiplot(p1, p2, cols = 2)
```

## Sta5a  

```{r}
gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  summarise(obs = n(),
            obs_na = sum(is.na(gap_metric)),
            mean_gap = mean(gap_metric, na.rm = T),
            sd_gap = sd(gap_metric, na.rm = T),
            qtl_5 = quantile(gap_metric, 0.05, na.rm = T),
            qtl_95 = quantile(gap_metric, 0.95, na.rm = T),
            qtl_1 = quantile(gap_metric, 0.01, na.rm = T),
            qtl_99 = quantile(gap_metric, 0.99, na.rm = T)) %>%
  mutate(foo = "foo", 
         across(c(3:8), ~comma(.x, accuracy = 0.01)),
         across(c(1:2), ~comma(.x, accuracy = 1)),
         mean_sd = paste0(mean_gap, " (", sd_gap, ")"),
         qtls_05_95 = paste0("[", qtl_5, ", ", qtl_95, "]"),
         qtls_01_99 = paste0("[", qtl_1, ", ", qtl_99, "]")) %>%
  select(obs, obs_na, mean_sd, qtls_05_95, qtls_01_99) %>%
  kbl(col.names = c("Observations", "Missing", "Mean (SD)", "[5th %ile, 95th %ile]", "[1st %ile, 99th %ile]"),
      align = rep("r", 5)) %>%
  kable_classic(full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  filter(gap_metric < 3) %>%
  ggplot(data = .,
         aes(y = gap_metric, x = vssc_month, group = sta5a)) +
  geom_hline(yintercept = 1.0, lty = 2, color = "red") +
  geom_hline(yintercept = 1.2, lty = 3, color = "red") +
  geom_line(alpha = 0.1) +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "Gap Metric",
       caption = "*Removed obs. > 3")
#--
gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  filter(gap_metric < 3) %>%
  ggplot(data = .,
         aes(x = gap_metric)) +
  geom_histogram(color = "black",
                 fill = "darkorchid") +
  labs(x = "Gap Metric",
       y = "Observations/Months",
       caption = "*Removed obs. > 3") +
  scale_y_continuous(labels = scales::comma_format())
```

```{r}
gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  filter(gap_metric < 3) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(y = gap_metric, x = vssc_month, group = sta5a)) +
  geom_hline(yintercept = 1.0, lty = 2, color = "red") +
  geom_hline(yintercept = 1.2, lty = 3, color = "red") +
  geom_line(alpha = 0.2) +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "Gap Metric",
       caption = "*Removed obs. > 3") +
  facet_wrap(~parent_visn)
#--
p1 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  filter(gap_metric < 3) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(x = gap_metric, fill = parent_visn)) +
  geom_histogram(color = "black") +
  facet_wrap(~parent_visn) +
  theme(legend.position = "none") +
  labs(y = "Observations/Months",
       x = "Gap Metric")
#
p2 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  filter(gap_metric < 3) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(y = gap_metric, fill = parent_visn)) +
  geom_boxplot(color = "black") +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  facet_wrap(~parent_visn) +
  labs(y = "Gap Metric")
#
multiplot(p1, p2, cols = 2)
```

```{r}
qtl_05 <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  summarise(qtl_95 = quantile(gap_metric, 0.05, na.rm = T)) %>%
  pull
#
outlier_sta5as <- gap_metric %>%
  inner_join(., sta5as_to_include) %>%
  mutate(lt_5th_pctle = if_else(gap_metric < qtl_05, 1, 0)) %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(outlier = if_else(lt_5th_pctle == 1
                           & lead(lt_5th_pctle, n = 1) == 1
                           & lead(lt_5th_pctle, n = 2) == 1
                           & lead(lt_5th_pctle, n = 3) == 1, 1, 0)) %>%
  filter(outlier == 1) %>%
  select(sta5a) %>%
  distinct
#--
gap_metric %>%
  filter(sta5a %in% outlier_sta5as$sta5a) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = gap_metric, group = sta5a)) +
  geom_line(alpha = 0.3) +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "Gap Metric")
#
gap_stats <- gap_metric %>%
  filter(sta5a %in% outlier_sta5as$sta5a) %>%
  summarise(nobs = n(),
            months_below_qtl_05 = sum(if_else(gap_metric < qtl_05, 1, 0), na.rm = T))
```

* There are `r nrow(outlier_sta5as)` sta5as that have at least 4 consecutive months with a gap metric < `r comma(qtl_05, accuracy = 0.01)`, the 5th percentile of gap metric
* These `r nrow(outlier_sta5as)` sta5as all contribute 36 months of observation, giving us a total of $\text{127}\times\text{36}=\text{4,572}$ observations
* Out of these $\text{4,572}$ observations, $\text{1,524}$ (`r percent(gap_stats$months_below_qtl_05 / gap_stats$nobs, accuracy = 0.1)`) have a gap metric less than the 5th percentile of all gap metric observations in our study period

```{r}
gap_chisq <- gap_metric %>%
  filter(sta5a %in% outlier_sta5as$sta5a) %>%
  left_join(., ps_matched %>% select(sta5a, treated)) %>%
  mutate(treated = replace_na(treated, "Control")) %>%
  filter(is.na(gap_metric_cat) == F) %>%
  tabyl(gap_metric_cat, treated) %>%
  chisq.test()
#--
gap_chisq$observed %>%
  tibble %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 1))) %>%
  kbl(col.names = c("Gap Metric Category", "Control", "Treated", "Total"),
      align = c("l", rep("r", 3)),
      caption = "<b>Observed</b>") %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(c(0, 4), bold = T)
#--
gap_chisq$expected %>%
  tibble %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("Gap Metric Category", "Control", "Treated", "Total"),
      align = c("l", rep("r", 3)),
      caption = "<b>Expected</b>") %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(c(0, 4), bold = T)
#
gap_chisq
```

# Panel Fullness  





## Sta5a  

```{r}
access_metrics %>%
  inner_join(., sta5as_to_include) %>%
  summarise(obs = n(),
            obs_na = sum(is.na(panel_fullness)),
            mean_gap = mean(panel_fullness, na.rm = T),
            sd_gap = sd(panel_fullness, na.rm = T),
            qtl_5 = quantile(panel_fullness, 0.05, na.rm = T),
            qtl_95 = quantile(panel_fullness, 0.95, na.rm = T),
            qtl_1 = quantile(panel_fullness, 0.01, na.rm = T),
            qtl_99 = quantile(panel_fullness, 0.99, na.rm = T)) %>%
  mutate(foo = "foo", 
         across(c(3:8), ~percent(.x, accuracy = 0.1)),
         across(c(1:2), ~comma(.x, accuracy = 1)),
         mean_sd = paste0(mean_gap, " (", sd_gap, ")"),
         qtls_05_95 = paste0("[", qtl_5, ", ", qtl_95, "]"),
         qtls_01_99 = paste0("[", qtl_1, ", ", qtl_99, "]")) %>%
  select(obs, obs_na, mean_sd, qtls_05_95, qtls_01_99) %>%
  kbl(col.names = c("Observations", "Missing", "Mean (SD)", "[5th %ile, 95th %ile]", "[1st %ile, 99th %ile]"),
      align = rep("r", 5)) %>%
  kable_classic(full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
access_metrics %>%
  inner_join(., sta5as_to_include) %>%
  ggplot(data = .,
         aes(y = panel_fullness, x = vssc_month, group = sta5a)) +
  geom_hline(yintercept = 0.88, lty = 3, color = "blue") +
  geom_line(alpha = 0.1) +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "Panel Fullness") +
  scale_y_continuous(limits = c(0, 1.5),
                     labels = scales::percent_format(accuracy = 1))
#--
access_metrics %>%
  inner_join(., sta5as_to_include) %>%
  filter(panel_fullness < 1.5) %>%
  ggplot(data = .,
         aes(x = panel_fullness)) +
  geom_histogram(color = "black",
                 fill = "darkorchid") +
  labs(x = "Panel Fullness",
       y = "Observations/Months",
       caption = "*Removed obs. > 150%") +
  scale_y_continuous(labels = scales::comma_format()) +
  scale_x_continuous(labels = scales::percent_format())
```

```{r}
access_metrics %>%
  inner_join(., sta5as_to_include) %>%
  filter(panel_fullness < 1.5) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(y = panel_fullness, x = vssc_month, group = sta5a)) +
  geom_line(alpha = 0.2) +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "Panel Fullness",
       caption = "*Removed obs. > 150%") +
  facet_wrap(~parent_visn) +
  scale_y_continuous(labels = scales::percent_format())
#--
p1 <- access_metrics %>%
  inner_join(., sta5as_to_include) %>%
  filter(panel_fullness < 1.5) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(x = panel_fullness, fill = parent_visn)) +
  geom_histogram(color = "black") +
  facet_wrap(~parent_visn) +
  theme(legend.position = "none") +
  labs(y = "Observations/Months",
       x = "Panel Fullness") +
  scale_x_continuous(labels = scales::percent_format())
#
p2 <- access_metrics %>%
  inner_join(., sta5as_to_include) %>%
  filter(panel_fullness < 1.5) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(y = panel_fullness, fill = parent_visn)) +
  geom_boxplot(color = "black") +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  facet_wrap(~parent_visn) +
  labs(y = "Panel Fullness") +
  scale_y_continuous(labels = scales::percent_format())
#
multiplot(p1, p2, cols = 2)
```

```{r}
qtl_95_pf <- access_metrics %>%
  inner_join(., sta5as_to_include) %>%
  summarise(qtl_95 = quantile(panel_fullness, 0.95, na.rm = T)) %>%
  pull
#
outlier_sta5as_pf <- access_metrics %>%
  select(sta5a, vssc_month, panel_fullness) %>%
  inner_join(., sta5as_to_include) %>%
  mutate(lt_5th_pctle = if_else(panel_fullness > qtl_95_pf, 1, 0)) %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(outlier = if_else(lt_5th_pctle == 1
                           & lead(lt_5th_pctle, n = 1) == 1
                           & lead(lt_5th_pctle, n = 2) == 1
                           & lead(lt_5th_pctle, n = 3) == 1, 1, 0)) %>%
  filter(outlier == 1) %>%
  select(sta5a) %>%
  distinct
#--
access_metrics %>%
  filter(sta5a %in% outlier_sta5as_pf$sta5a) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = panel_fullness, group = sta5a)) +
  geom_line(alpha = 0.3) +
  theme(legend.position = "none") +
  labs(x = "Month",
       y = "Panel Fullness") +
  scale_y_continuous(labels = scales::percent_format())
#
pf_stats <- outlier_sta5as_pf %>%
  cross_join(., dates %>%
               select(vssc_month)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, panel_fullness)) %>%
  ungroup %>%
  summarise(nobs = n(),
            months_above_qtl_95 = sum(if_else(panel_fullness > qtl_95_pf, 1, 0), na.rm = T))
```

* There are `r nrow(outlier_sta5as_pf)` sta5as that have at least 4 consecutive months with a panel fullness > `r percent(qtl_95_pf / 100, accuracy = 0.1)`, the 95th percentile of panel fullness
* These `r nrow(outlier_sta5as_pf)` sta5as all contribute 36 months of observation, giving us a total of $\text{127}\times\text{36}=\text{4,572}$ observations
* Out of these $\text{4,572}$ observations, $\text{1,488}$ (`r percent(pf_stats$months_above_qtl_95 / pf_stats$nobs, accuracy = 0.1)`) have panel fullness greater than the 5th percentile of all panel fullness observations in our study period

```{r}
pf_chisq <- access_metrics %>%
  filter(sta5a %in% outlier_sta5as$sta5a) %>%
  left_join(., ps_matched %>% select(sta5a, treated)) %>%
  mutate(treated = replace_na(treated, "Control")) %>%
  filter(is.na(panel_fullness_cat) == F) %>%
  tabyl(panel_fullness_cat, treated) %>%
  chisq.test()
#--
pf_chisq$observed %>%
  tibble %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 1))) %>%
  kbl(col.names = c("Panel Fullness Category", "Control", "Treated", "Total"),
      align = c("l", rep("r", 3)),
      caption = "<b>Observed</b>") %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(c(0, 4), bold = T)
#--
pf_chisq$expected %>%
  tibble %>%
  adorn_totals("both") %>%
  mutate(across(where(is.numeric), ~comma(.x, accuracy = 0.1))) %>%
  kbl(col.names = c("Panel Fullness Category", "Control", "Treated", "Total"),
      align = c("l", rep("r", 3)),
      caption = "<b>Expected</b>") %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(c(0, 4), bold = T)
#
gap_chisq
```


# CRH Utilization  


```{r}
pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  group_by(vssc_month) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = crh_encounter_count)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "Total PC CRH Encounters",
       caption = "We have been assured the drop is normal")
```


```{r}
pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = crh_encounter_count, color = parent_visn)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "Total PC CRH Encounters") +
  facet_wrap(~parent_visn) +
  theme(legend.position = "none")
#--
p1 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count, fill = parent_visn)) +
  geom_histogram(color = "black") +
  scale_x_continuous(labels = scales::comma_format()) +
  facet_wrap(~parent_visn) +
  labs(x = "PC CRH Encounters",
       y = "Observations/Months") +
  theme(legend.position = "none")
#--
p2 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(y = crh_encounter_count, fill = parent_visn)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~parent_visn) +
  labs(y = "PC CRH Encounters per Month") +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
#
multiplot(p1, p2, cols = 2)
```


```{r}
p1 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn, s_abbr)) %>%
  group_by(vssc_month, s_abbr) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = crh_encounter_count, color = s_abbr)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(y = "Total PC CRH Encounters") +
  theme(axis.title.x = element_blank())
#---
p2 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn, s_abbr2)) %>%
  group_by(vssc_month, s_abbr2) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = crh_encounter_count, color = s_abbr2)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(y = "Total PC CRH Encounters") +
  theme(axis.title.x = element_blank())
#-
multiplot(p1, p2, cols = 1)
#--==--
p1 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast) %>%
  group_by(vssc_month, s_abbr) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count, fill = s_abbr)) +
  geom_histogram(color = "black") +
  scale_x_continuous(labels = scales::comma_format()) +
  facet_wrap(~s_abbr) +
  labs(x = "PC CRH Encounters",
       y = "Observations/Months") +
  theme(legend.position = "none")
#--
p2 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast) %>%
  group_by(vssc_month, s_abbr) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(y = crh_encounter_count, fill = s_abbr)) +
  geom_boxplot(color = "black") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~s_abbr) +
  labs(y = "PC CRH Encounters per Month") +
  theme(legend.position = "none",
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())
#
multiplot(p1, p2)
```

### Sta5a  
```{r}
p1 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black") +
  labs(x = "PC CRH Encounters",
       y = "Observations/Sta5a-Months") +
  scale_y_continuous(labels = scales::comma_format())
#--
p2 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  ggplot(data = .,
         aes(y = crh_encounter_count)) +
  geom_boxplot(color = "black",
               fill = "chartreuse") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "PC CRH Encounters per Month")
#
multiplot(p1, p2, cols = 2) 
#--
pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  filter(crh_encounter_count < 31)  %>%
  ggplot(data = .,
         aes(x = crh_encounter_count)) +
  geom_histogram(color = "black") +
  labs(x = "PC CRH Encounters",
       y = "Observations/Sta5a-Months",
       caption = "*Restricted to the first 30 integers") +
  scale_y_continuous(labels = scales::comma_format())
```

```{r}
p1 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count, fill = parent_visn)) +
  geom_histogram(color = "black") +
  labs(x = "PC CRH Encounters",
       y = "Observations/Sta5a-Months") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~parent_visn) +
  theme(legend.position  = "none")
#--
p2 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  ggplot(data = .,
         aes(y = crh_encounter_count, fill = parent_visn)) +
  geom_boxplot(color = "black") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "PC CRH Encounters per Month") +
  facet_wrap(~parent_visn) +
  theme(legend.position  = "none")
#
multiplot(p1, p2, cols = 2) 
```

```{r}
p1 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, s_abbr2)) %>%
  ggplot(data = .,
         aes(x = crh_encounter_count, fill = s_abbr2)) +
  geom_histogram(color = "black") +
  labs(x = "PC CRH Encounters",
       y = "Observations/Sta5a-Months") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~s_abbr2) +
  theme(legend.position  = "none")
#--
p2 <- pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, s_abbr2)) %>%
  ggplot(data = .,
         aes(y = crh_encounter_count, fill = s_abbr2)) +
  geom_boxplot(color = "black") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "PC CRH Encounters per Month") +
  facet_wrap(~s_abbr2) +
  theme(legend.position  = "none")
#
multiplot(p1, p2, cols = 2) 
```

## Meaningful Use Definition  
* The meaningful use definition of PC CRH engagement is two consecutive months with at least 10 PC CRH Encounters

```{r}
pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  filter(treated_ever == 1) %>%
  group_by(vssc_month) %>%
  summarise(treated_month = sum(treated_month, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = treated_month)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "Sta5as meeting Meaningful Use")
```

```{r}
pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  filter(treated_ever == 1) %>%
  left_join(., vast) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(treated_month = sum(treated_month, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = treated_month, color = parent_visn)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = scales::comma_format()) +
  labs(x = "Month",
       y = "Sta5as meeting Meaningful Use") +
  facet_wrap(~parent_visn) +
  theme(legend.position = "none")
```




## Continuous Pentration Rate  

```{r}
pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  group_by(vssc_month) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T),
            pc_encounter_total = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(pc_crh_per_1k_total_pc = crh_encounter_count / pc_encounter_total * 1000) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = pc_crh_per_1k_total_pc)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Month",
       y = "PC CRH per 1,000 total PC")
```


```{r}
pen_rate %>%
  inner_join(., sta5as_to_include) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  group_by(vssc_month, parent_visn) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T),
            pc_encounter_total = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(pc_crh_per_1k_total_pc = crh_encounter_count / pc_encounter_total * 1000) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = pc_crh_per_1k_total_pc, color = parent_visn)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Month",
       y = "PC CRH per 1,000 total PC") +
  theme(legend.position = "none") +
  facet_wrap(~parent_visn)
```



