---
title: "D-i-D - Not matched, no covariates"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, echo = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v3_1.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01") & vssc_month > ymd("2018-09-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
  #1: must have Access metrics
  #2: must be in VAST
  #3: no missing scrssn_count_cat
  #4: CBOCs only
  #5: must have scrssn_count_avg_fy18 >= 450
sta5as_to_include <- access_metrics %>%#1: must have Access metrics
  select(sta5a) %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, "PC CRH", "No PC CRH")) %>%#making the crh_flag
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F #3: no missing scrssn_count_cat
         & str_detect(s_abbr, "CBOC")#4: CBOCs only
           & scrssn_count_cat != "< 450")#5: must have scrssn_count_avg_fy18 >= 450
#this little table is for the functions i wrote for outputting tables, and I don't want to have to look for it later
# not strictly necissary
# scrssn_cat_count <- sta5as_to_include %>%
#   group_by(crh_flag, scrssn_count_cat) %>%
#   summarise(count = n()) %>%
#   mutate(count = as.character(count)) %>%
#   pivot_wider(names_from = scrssn_count_cat, values_from = count)
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
      left_join(., crh_flag %>% select(sta5a, first_mo_w_mt9_pc_crh)) %>%
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "No PC CRH")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup()
#
tx_pre <- analytic_df %>%
  filter(tx_fe == 1 & post_fe == 0)
#
tx_post <- analytic_df %>%
  filter(tx_fe == 1 & post_fe == 1)
#
noTx_pre <- analytic_df %>%
  filter(tx_fe == 0 & post_fe == 0)
#
noTx_post <- analytic_df %>%
  filter(tx_fe == 0 & post_fe == 1)
```

# Front Matter  

## Description of this report  

* This is a Difference-in-Differences analysis of 3 outcomes by whether or not the sta5a met our PC CRH inclusion criteria before March, 2020  
    + Because, according to Hallberg et al. CITS = DiD, I am not going to estimate the DiD by regression but rather just by the grouped mean

## Decision Points  

* This is analysis __1Ai__ from the Project Face Sheet
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
    + Each row is a sta5a-month
    
    
* Description of _Propensity Score_ matching
    + There is no matching in this analysis 

* Description of analyses    
    + I am analyzing our 3 primary outcomes: New and Established patient wait time, and Third-next available
* DiD analysis is reasonably straight-forward:
    1. Estimate 4 mean outcome values
      + Treated, pre intervention
      + Treated, post intervention
      + Not treated, pre intervention
      + Not treated, post intervention
    2. Take difference of differences to estimate the Average Treatment Effect Among the Treated (ATT)
      + $(Treated_{post}-Treated_{pre})-(Not Treated_{post}-Not Treated_{pre})$
      + $(Treated_{post}-NotTreated_{post})-(Treated_{pre}-NotTreated_{pre})$


# New Patient Wait Time   
```{r}
newPtWt_tx_pre <- tx_pre %>%
  summarise(avg_val = mean(new_pc_pt_wt, na.rm = T))
#
newPtWt_tx_post <- tx_post %>%
  summarise(avg_val = mean(new_pc_pt_wt, na.rm = T))
#
newPtWt_noTx_pre <- noTx_pre %>%
  summarise(avg_val = mean(new_pc_pt_wt, na.rm = T))
#
newPtWt_noTx_post <- noTx_post %>%
  summarise(avg_val = mean(new_pc_pt_wt, na.rm = T))
#---
did_1 <- (newPtWt_tx_post$avg_val - newPtWt_tx_pre$avg_val) - (newPtWt_noTx_post$avg_val - newPtWt_noTx_pre$avg_val)
#---
did_2 <- (newPtWt_tx_post$avg_val - newPtWt_noTx_post$avg_val) - (newPtWt_tx_pre$avg_val - newPtWt_noTx_pre$avg_val)
#---
cf_value_at_start <- newPtWt_tx_pre$avg_val
cf_value_at_end <- newPtWt_tx_post$avg_val - did_1
#--
plot_df <- tibble(
  group = c("PC CRH", "PC CRH",
            "No PC CRH", "No PC CRH",
            "Counterfactual", "Counterfactual"),
  time = factor(rep(c("Pre", "Post"), 3),
                ordered = TRUE,
                levels = c("Pre", "Post")),
  value = c(newPtWt_tx_pre$avg_val, newPtWt_tx_post$avg_val,
            newPtWt_noTx_pre$avg_val, newPtWt_noTx_post$avg_val,
            cf_value_at_start, cf_value_at_end)
)
```

* The difference in differences is __0.65 days__ (`r round(did_2, 4)`)  

```{r}
ggplot(plot_df,
       aes(x = time, y = value, group = group, color = group)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Time", y = "Avg. New Patient Wait Time (days)")
  
```


# Established Patient Wait Time   
```{r}
estPtWt_tx_pre <- tx_pre %>%
  summarise(avg_val = mean(est_pc_pt_wt, na.rm = T))
#
estPtWt_tx_post <- tx_post %>%
  summarise(avg_val = mean(est_pc_pt_wt, na.rm = T))
#
estPtWt_noTx_pre <- noTx_pre %>%
  summarise(avg_val = mean(est_pc_pt_wt, na.rm = T))
#
estPtWt_noTx_post <- noTx_post %>%
  summarise(avg_val = mean(est_pc_pt_wt, na.rm = T))
#---
did_1 <- (estPtWt_tx_post$avg_val - estPtWt_tx_pre$avg_val) - (estPtWt_noTx_post$avg_val - estPtWt_noTx_pre$avg_val)
#---
did_2 <- (estPtWt_tx_post$avg_val - estPtWt_noTx_post$avg_val) - (estPtWt_tx_pre$avg_val - estPtWt_noTx_pre$avg_val)
#---
cf_value_at_start <- estPtWt_tx_pre$avg_val
cf_value_at_end <- estPtWt_tx_post$avg_val - did_1
#--
plot_df <- tibble(
  group = c("PC CRH", "PC CRH",
            "No PC CRH", "No PC CRH",
            "Counterfactual", "Counterfactual"),
  time = factor(rep(c("Pre", "Post"), 3),
                ordered = TRUE,
                levels = c("Pre", "Post")),
  value = c(estPtWt_tx_pre$avg_val, estPtWt_tx_post$avg_val,
            estPtWt_noTx_pre$avg_val, estPtWt_noTx_post$avg_val,
            cf_value_at_start, cf_value_at_end)
)
```

* The difference in differences is __-0.66 days__ (`r round(did_2, 4)`)  

```{r}
ggplot(plot_df,
       aes(x = time, y = value, group = group, color = group)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Time", y = "Avg. Established Patient Wait Time (days)")
  
```


# Third Next Available     
```{r}
tna_tx_pre <- tx_pre %>%
  summarise(avg_val = mean(third_next_avail, na.rm = T))
#
tna_tx_post <- tx_post %>%
  summarise(avg_val = mean(third_next_avail, na.rm = T))
#
tna_noTx_pre <- noTx_pre %>%
  summarise(avg_val = mean(third_next_avail, na.rm = T))
#
tna_noTx_post <- noTx_post %>%
  summarise(avg_val = mean(third_next_avail, na.rm = T))
#---
did_1 <- (tna_tx_post$avg_val - tna_tx_pre$avg_val) - (tna_noTx_post$avg_val - tna_noTx_pre$avg_val)
#---
did_2 <- (tna_tx_post$avg_val - tna_noTx_post$avg_val) - (tna_tx_pre$avg_val - tna_noTx_pre$avg_val)
#---
cf_value_at_start <- tna_tx_pre$avg_val
cf_value_at_end <- tna_tx_post$avg_val - did_1
#--
plot_df <- tibble(
  group = c("PC CRH", "PC CRH",
            "No PC CRH", "No PC CRH",
            "Counterfactual", "Counterfactual"),
  time = factor(rep(c("Pre", "Post"), 3),
                ordered = TRUE,
                levels = c("Pre", "Post")),
  value = c(tna_tx_pre$avg_val, tna_tx_post$avg_val,
            tna_noTx_pre$avg_val, tna_noTx_post$avg_val,
            cf_value_at_start, cf_value_at_end)
)
```

* The difference in differences is __-0.69 days__ (`r round(did_2, 4)`)  

```{r}
ggplot(plot_df,
       aes(x = time, y = value, group = group, color = group)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(x = "Time", y = "Avg. Third-Next Available (days)")
  
```
