---
title: "PC CRH Analysis: Difference-in-Difference"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
pactcc_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "PACT_CC",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         initiated_pc_crh_b4_march_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-03-01"), TRUE, FALSE),
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
pilot_sites <- dbGetQuery(pactcc_con,
                          "select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY20_working 
                          UNION
                          select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY21_working ") %>%
  filter(vimpact_pilot == 1) %>%
  select(sta5a = spoke_sta5a)
#
ps_matched <- read_csv(here::here("Input", "Data", "ps_matched_sta5as.csv"))
#==
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month))
```

# 1A: All Sta5as that met PC CRH inclusion criteria before February, 2020  
```{r}
included_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag)
#----------------------------------------------------------
new_pt_wt <- access_metrics %>%
  select(sta5a, vssc_month, new_pc_pt_wt) %>%
  inner_join(., included_sta5as) %>%
  filter(vssc_month %in% c(ymd("2019-09-01"), ymd("2020-02-01"))) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH")))
```

* There were `r nrow(included_sta5as) / 2` sta5as that met inclusion criteria before February, 2020  

## Distribution of New Patient Wait Times    
```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 25) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "September, 2019") +
  theme(legend.title = element_blank())
#--
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 25) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "February, 2020") +
  theme(legend.title = element_blank())
#
multiplot(p1, p2, cols = 2)
```

```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "September, 2019")
#
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "February, 2020")
#
multiplot(p1, p2, cols = 2)
```


```{r}
differences <- new_pt_wt %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(new_pc_pt_wt = mean(new_pc_pt_wt, na.rm = T)) %>%
  mutate(vssc_month = format(vssc_month, "%b, %Y"))
#
crh_sep <- differences[3,3] %>% pull
crh_feb <- differences[4,3] %>% pull
noCrh_sep <- differences[1,3] %>% pull
noCrh_feb <- differences[2,3] %>% pull
#
foo <- tibble(
  crh_flag = rep("PC CRH (counterfactual)", 2),
  vssc_month = c(format(ymd("2019-09-01"), "%b, %Y"),
                 format(ymd("2020-02-01"), "%b, %Y")),
  new_pc_pt_wt = c(crh_sep, (crh_sep + (noCrh_feb - noCrh_sep)))
)
#
differences %>%
  bind_rows(., foo) %>%
  mutate(new_pc_pt_wt = round(new_pc_pt_wt, 1)) %>%
  kbl(col.names = c("CRH Flag", "Month", "Average New Pat. WT")) %>%
  kable_classic("striped",
      full_width = FALSE, font_size = 16) %>%
  row_spec(0, bold = TRUE)
```

## DiD Plot  

```{r}
did_plot_df <- tibble(
  label_name = c("No PC CRH", "PC CRH", "PC CRH (Counterfactual)",
                 "No PC CRH", "PC CRH", "PC CRH (Counterfactual)"),
  timepoint = c("September, 2019", "September, 2019", "September, 2019",
                "February, 2020", "February, 2020", "February, 2020"),
  value = c(noCrh_sep, crh_sep, crh_sep,
            noCrh_feb, crh_feb, 
              (crh_sep + (noCrh_feb - noCrh_sep)))) %>%
  mutate(timepoint = factor(timepoint,
                            ordered = TRUE,
                            levels = c("September, 2019", "February, 2020")))
#
ggplot(data = did_plot_df,
       aes(x = timepoint, y = value, group = label_name, color = label_name)) +
  geom_line(size = 1.5) +
  scale_y_continuous(limits = c(plyr::round_any(min(did_plot_df$value), 5, floor), 
                                plyr::round_any(max(did_plot_df$value), 5, ceiling)),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.position = "right",
        axis.title.x = element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  geom_segment(aes(x = 2.02, xend = 2.02,
                   y = (crh_sep + (noCrh_feb - noCrh_sep)), 
                   yend = crh_feb),
               color = "black",
               arrow = arrow(angle = 90, ends = "both", length = unit(0.125, "cm"))) +
  geom_curve(aes(x = 2.3, xend = 2.05,
                 y = (crh_sep + (noCrh_feb - noCrh_sep)) - 0.85,
                 yend = (crh_sep + (noCrh_feb - noCrh_sep)) + (crh_feb - (crh_sep + (noCrh_feb - noCrh_sep)))/2),
             color = "black",
             arrow = arrow(type = "closed", length = unit(0.25, "cm"))) +
  annotate("text",
           x = 2.125, y = (crh_sep + (noCrh_feb - noCrh_sep)) - 1,
           label = "{Difference-in-Differences}") +
  labs(y = "New Patient Wait Time (days)")
```

## Regression  

```{r}
foo <- new_pt_wt %>%
  mutate(february2020 = if_else(vssc_month == ymd("2020-02-01"), 1, 0),
         did = february2020 * at_least_10_pc_crh_flag)
#
didreg = lm(new_pc_pt_wt ~ at_least_10_pc_crh_flag*february2020, data = foo)
summary(didreg)
```

# 1B: No pilot sites, all Sta5as that met PC CRH inclusion criteria before February, 2020  
```{r}
included_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE
         & sta5a %ni% pilot_sites$sta5a) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag)
#----------------------------------------------------------
new_pt_wt <- access_metrics %>%
  select(sta5a, vssc_month, new_pc_pt_wt) %>%
  inner_join(., included_sta5as) %>%
  filter(vssc_month %in% c(ymd("2019-09-01"), ymd("2020-02-01"))) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH")))
```

* There were `r nrow(included_sta5as) / 2` non-pilot sta5as that met inclusion criteria before February, 2020  

## Distribution of New Patient Wait Times    
```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 25) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "September, 2019") +
  theme(legend.title = element_blank())
#--
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 25) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "February, 2020") +
  theme(legend.title = element_blank())
#
multiplot(p1, p2, cols = 2)
```

```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "September, 2019")
#
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "February, 2020")
#
multiplot(p1, p2, cols = 2)
```


```{r}
differences <- new_pt_wt %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(new_pc_pt_wt = mean(new_pc_pt_wt, na.rm = T)) %>%
  mutate(vssc_month = format(vssc_month, "%b, %Y"))
#
crh_sep <- differences[3,3] %>% pull
crh_feb <- differences[4,3] %>% pull
noCrh_sep <- differences[1,3] %>% pull
noCrh_feb <- differences[2,3] %>% pull
#
foo <- tibble(
  crh_flag = rep("PC CRH (counterfactual)", 2),
  vssc_month = c(format(ymd("2019-09-01"), "%b, %Y"),
                 format(ymd("2020-02-01"), "%b, %Y")),
  new_pc_pt_wt = c(crh_sep, (crh_sep + (noCrh_feb - noCrh_sep)))
)
#
differences %>%
  bind_rows(., foo) %>%
  mutate(new_pc_pt_wt = round(new_pc_pt_wt, 1)) %>%
  kbl(col.names = c("CRH Flag", "Month", "Average New Pat. WT")) %>%
  kable_classic("striped",
      full_width = FALSE, font_size = 16) %>%
  row_spec(0, bold = TRUE)
```

## DiD Plot  

```{r}
did_plot_df <- tibble(
  label_name = c("No PC CRH", "PC CRH", "PC CRH (Counterfactual)",
                 "No PC CRH", "PC CRH", "PC CRH (Counterfactual)"),
  timepoint = c("September, 2019", "September, 2019", "September, 2019",
                "February, 2020", "February, 2020", "February, 2020"),
  value = c(noCrh_sep, crh_sep, crh_sep,
            noCrh_feb, crh_feb, 
              (crh_sep + (noCrh_feb - noCrh_sep)))) %>%
  mutate(timepoint = factor(timepoint,
                            ordered = TRUE,
                            levels = c("September, 2019", "February, 2020")))
#
ggplot(data = did_plot_df,
       aes(x = timepoint, y = value, group = label_name, color = label_name)) +
  geom_line(size = 1.5) +
  scale_y_continuous(limits = c(plyr::round_any(min(did_plot_df$value), 5, floor), 
                                plyr::round_any(max(did_plot_df$value), 5, ceiling)),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.position = "right",
        axis.title.x = element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  geom_segment(aes(x = 2.02, xend = 2.02,
                   y = (crh_sep + (noCrh_feb - noCrh_sep)), 
                   yend = crh_feb),
               color = "black",
               arrow = arrow(angle = 90, ends = "both", length = unit(0.125, "cm"))) +
  geom_curve(aes(x = 2.3, xend = 2.05,
                 y = (crh_sep + (noCrh_feb - noCrh_sep)) - 0.85,
                 yend = (crh_sep + (noCrh_feb - noCrh_sep)) + (crh_feb - (crh_sep + (noCrh_feb - noCrh_sep)))/2),
             color = "black",
             arrow = arrow(type = "closed", length = unit(0.25, "cm"))) +
  annotate("text",
           x = 2.125, y = (crh_sep + (noCrh_feb - noCrh_sep)) - 1,
           label = "{Difference-in-Differences}") +
  labs(y = "New Patient Wait Time (days)")
```

## Regression  

```{r}
foo <- new_pt_wt %>%
  mutate(february2020 = if_else(vssc_month == ymd("2020-02-01"), 1, 0),
         did = february2020 * at_least_10_pc_crh_flag)
#
didreg = lm(new_pc_pt_wt ~ at_least_10_pc_crh_flag*february2020, data = foo)
summary(didreg)
```


# 2A: All Sta5as meeting inclusion criteria for all first 6 months of FY20   
```{r}
included_sta5as <- crh_flag %>%
  filter(first_6_mos_w_10_flag == TRUE) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag)
#----------------------------------------------------------
new_pt_wt <- access_metrics %>%
  select(sta5a, vssc_month, new_pc_pt_wt) %>%
  inner_join(., included_sta5as) %>%
  filter(vssc_month %in% c(ymd("2019-09-01"), ymd("2020-02-01"))) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH")))
```

* There were `r nrow(included_sta5as) / 2` sta5as that met inclusion criteria for all first 6 months of FY20  

## Distribution of New Patient Wait Times    
```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 25) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "September, 2019") +
  theme(legend.title = element_blank())
#--
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 25) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "February, 2020") +
  theme(legend.title = element_blank())
#
multiplot(p1, p2, cols = 2)
```

```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "September, 2019")
#
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "February, 2020")
#
multiplot(p1, p2, cols = 2)
```


```{r}
differences <- new_pt_wt %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(new_pc_pt_wt = mean(new_pc_pt_wt, na.rm = T)) %>%
  mutate(vssc_month = format(vssc_month, "%b, %Y"))
#
crh_sep <- differences[3,3] %>% pull
crh_feb <- differences[4,3] %>% pull
noCrh_sep <- differences[1,3] %>% pull
noCrh_feb <- differences[2,3] %>% pull
#
foo <- tibble(
  crh_flag = rep("PC CRH (counterfactual)", 2),
  vssc_month = c(format(ymd("2019-09-01"), "%b, %Y"),
                 format(ymd("2020-02-01"), "%b, %Y")),
  new_pc_pt_wt = c(crh_sep, (crh_sep + (noCrh_feb - noCrh_sep)))
)
#
differences %>%
  bind_rows(., foo) %>%
  mutate(new_pc_pt_wt = round(new_pc_pt_wt, 1)) %>%
  kbl(col.names = c("CRH Flag", "Month", "Average New Pat. WT")) %>%
  kable_classic("striped",
      full_width = FALSE, font_size = 16) %>%
  row_spec(0, bold = TRUE)
```

## DiD Plot  

```{r}
did_plot_df <- tibble(
  label_name = c("No PC CRH", "PC CRH", "PC CRH (Counterfactual)",
                 "No PC CRH", "PC CRH", "PC CRH (Counterfactual)"),
  timepoint = c("September, 2019", "September, 2019", "September, 2019",
                "February, 2020", "February, 2020", "February, 2020"),
  value = c(noCrh_sep, crh_sep, crh_sep,
            noCrh_feb, crh_feb, 
              (crh_sep + (noCrh_feb - noCrh_sep)))) %>%
  mutate(timepoint = factor(timepoint,
                            ordered = TRUE,
                            levels = c("September, 2019", "February, 2020")))
#
ggplot(data = did_plot_df,
       aes(x = timepoint, y = value, group = label_name, color = label_name)) +
  geom_line(size = 1.5) +
  scale_y_continuous(limits = c(plyr::round_any(min(did_plot_df$value), 5, floor), 
                                plyr::round_any(max(did_plot_df$value), 5, ceiling)),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.position = "right",
        axis.title.x = element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  geom_segment(aes(x = 2.02, xend = 2.02,
                   y = (crh_sep + (noCrh_feb - noCrh_sep)), 
                   yend = crh_feb),
               color = "black",
               arrow = arrow(angle = 90, ends = "both", length = unit(0.125, "cm"))) +
  geom_curve(aes(x = 2.3, xend = 2.05,
                 y = (crh_sep + (noCrh_feb - noCrh_sep)) - 0.85,
                 yend = (crh_sep + (noCrh_feb - noCrh_sep)) + (crh_feb - (crh_sep + (noCrh_feb - noCrh_sep)))/2),
             color = "black",
             arrow = arrow(type = "closed", length = unit(0.25, "cm"))) +
  annotate("text",
           x = 2.125, y = (crh_sep + (noCrh_feb - noCrh_sep)) - 1,
           label = "{Difference-in-Differences}") +
  labs(y = "New Patient Wait Time (days)")
```


## Regression  

```{r}
foo <- new_pt_wt %>%
  mutate(february2020 = if_else(vssc_month == ymd("2020-02-01"), 1, 0),
         did = february2020 * at_least_10_pc_crh_flag)
#
didreg = lm(new_pc_pt_wt ~ at_least_10_pc_crh_flag*february2020, data = foo)
summary(didreg)
```


# 2B: No pilot sites, all Sta5as meeting inclusion criteria for all first 6 months of FY20   
```{r}
included_sta5as <- crh_flag %>%
  filter(first_6_mos_w_10_flag == TRUE
         & sta5a %ni% pilot_sites$sta5a) %>%
  select(sta5a) %>%
  inner_join(., ps_matched) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag)
#----------------------------------------------------------
new_pt_wt <- access_metrics %>%
  select(sta5a, vssc_month, new_pc_pt_wt) %>%
  inner_join(., included_sta5as) %>%
  filter(vssc_month %in% c(ymd("2019-09-01"), ymd("2020-02-01"))) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH")))
```

* There were `r nrow(included_sta5as) / 2` non-pilot sta5as that met inclusion criteria for all first 6 months of FY20  

## Distribution of New Patient Wait Times    

```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 22) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "September, 2019") +
  theme(legend.title = element_blank())
#--
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(x = new_pc_pt_wt, 
             fill = crh_flag, 
             group = crh_flag)) +
  geom_histogram(aes(y=c(..count..[..group..==1]/sum(..count..[..group..==1]),
                         ..count..[..group..==2]/sum(..count..[..group..==2]))),
                 position = "dodge",
                 bins = 22) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, NA)) +
  scale_x_continuous(limits = c(0, 75)) +
  labs(x = "New Patient Wait Time",
       y = "Proportion of Sta5as",
       title = "February, 2020") +
  theme(legend.title = element_blank())
#
multiplot(p1, p2, cols = 2)
```

```{r}
p1 <- new_pt_wt %>%
  filter(vssc_month == ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "September, 2019")
#
p2 <- new_pt_wt %>%
  filter(vssc_month != ymd("2019-09-01")) %>%
  ggplot(data = .,
         aes(y = new_pc_pt_wt, 
             fill = crh_flag, 
             x = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_nejm() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time",
       title = "February, 2020")
#
multiplot(p1, p2, cols = 2)
```


```{r}
differences <- new_pt_wt %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(new_pc_pt_wt = mean(new_pc_pt_wt, na.rm = T)) %>%
  mutate(vssc_month = format(vssc_month, "%b, %Y"))
#
crh_sep <- differences[3,3] %>% pull
crh_feb <- differences[4,3] %>% pull
noCrh_sep <- differences[1,3] %>% pull
noCrh_feb <- differences[2,3] %>% pull
#
foo <- tibble(
  crh_flag = rep("PC CRH (counterfactual)", 2),
  vssc_month = c(format(ymd("2019-09-01"), "%b, %Y"),
                 format(ymd("2020-02-01"), "%b, %Y")),
  new_pc_pt_wt = c(crh_sep, (crh_sep + (noCrh_feb - noCrh_sep)))
)
#
differences %>%
  bind_rows(., foo) %>%
  mutate(new_pc_pt_wt = round(new_pc_pt_wt, 1)) %>%
  kbl(col.names = c("CRH Flag", "Month", "Average New Pat. WT")) %>%
  kable_classic("striped",
      full_width = FALSE, font_size = 16) %>%
  row_spec(0, bold = TRUE)
```

## DiD Plot  

```{r}
did_plot_df <- tibble(
  label_name = c("No PC CRH", "PC CRH", "PC CRH (Counterfactual)",
                 "No PC CRH", "PC CRH", "PC CRH (Counterfactual)"),
  timepoint = c("September, 2019", "September, 2019", "September, 2019",
                "February, 2020", "February, 2020", "February, 2020"),
  value = c(noCrh_sep, crh_sep, crh_sep,
            noCrh_feb, crh_feb, 
              (crh_sep + (noCrh_feb - noCrh_sep)))) %>%
  mutate(timepoint = factor(timepoint,
                            ordered = TRUE,
                            levels = c("September, 2019", "February, 2020")))
#
ggplot(data = did_plot_df,
       aes(x = timepoint, y = value, group = label_name, color = label_name)) +
  geom_line(size = 1.5) +
  scale_y_continuous(limits = c(plyr::round_any(min(did_plot_df$value), 5, floor), 
                                plyr::round_any(max(did_plot_df$value), 5, ceiling)),
                     labels = scales::comma_format(accuracy = 1)) +
  theme(legend.position = "right",
        axis.title.x = element_blank()) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  geom_segment(aes(x = 2.02, xend = 2.02,
                   y = (crh_sep + (noCrh_feb - noCrh_sep)), 
                   yend = crh_feb),
               color = "black",
               arrow = arrow(angle = 90, ends = "both", length = unit(0.125, "cm"))) +
  geom_curve(aes(x = 2.3, xend = 2.05,
                 y = (crh_sep + (noCrh_feb - noCrh_sep)) - 4.85,
                 yend = (crh_sep + (noCrh_feb - noCrh_sep)) + (crh_feb - (crh_sep + (noCrh_feb - noCrh_sep)))/2),
             color = "black",
             arrow = arrow(type = "closed", length = unit(0.25, "cm"))) +
  annotate("text",
           x = 2.125, y = (crh_sep + (noCrh_feb - noCrh_sep)) - 5,
           label = "{Difference-in-Differences}") +
  labs(y = "New Patient Wait Time (days)")
```


## Regression  

```{r}
foo <- new_pt_wt %>%
  mutate(february2020 = if_else(vssc_month == ymd("2020-02-01"), 1, 0),
         did = february2020 * at_least_10_pc_crh_flag)
#
didreg = lm(new_pc_pt_wt ~ at_least_10_pc_crh_flag*february2020, data = foo)
summary(didreg)
```