---
title: "Consults for Primary Care: intra-VHA vs. community"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```
```{r}
t.test2 <- function(m1, m2, s1, s2, n1, n2, m0=0, equal.variances = FALSE){
  if(equal.variances == FALSE)
  {
    se <- round(sqrt((s1 ^ 2 / n1) + (s2^2 / n2)), 8)
    #welch-satterwaithe df
    df <- ((s1^2 / n1 + s2 ^ 2 / n2) ^2 ) / ((s1 ^ 2 / n1) ^ 2 / (n1 - 1) + (s2 ^ 2 / n2) ^ 2 / (n2 - 1))
  }
  else
  {
    se <- sqrt((1 / n1 + 1/ n2) * ((n1 - 1) * s1^2 +(n2-1) * s2^2) / (n1 + n2 - 2))
    df <- n1 + n2 - 2
  }
  t <- round((m1 - m2 - m0)/ se, 4)
  se <- round(se, 4)
  mean_diff <- round((m1 - m2), 4)
  pval <- if_else(2*pt(-abs(t), df) < 0.00001, "<0.00001", as.character(2*pt(-abs(t), df)))
  dat <- c(mean_diff, se, t, pval)
  names(dat) <- c("difference_of_means", "std_Error", "t", "p_value")
  return(dat)
}
```



```{r cdw_cc_refs}
cc_refs_cdw <- dbGetQuery(oabi_con,
                          "--
select count(*) as referral_count
	, actyMonth, non_va, stopCode_group
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
group by actyMonth, non_va, stopCode_group") %>%
  mutate(actyMonth = ymd(actyMonth),
         fy = if_else(month(actyMonth) > 9, year(actyMonth) + 1, year(actyMonth))) %>%
  filter(actyMonth < ymd("2021-10-01")
         & actyMonth > ymd("2017-12-01"))
#
non_va_cc_refs <- cc_refs_cdw %>%
  filter(non_va == 1) %>%
  rename(non_va_referral_count = referral_count) %>%
  select(-non_va)
#
yes_va_cc_refs <- cc_refs_cdw %>%
  filter(non_va == 0) %>%
  rename(yes_va_referral_count = referral_count) %>%
  select(-non_va)
#--
analytic_df <- non_va_cc_refs %>%
  left_join(., yes_va_cc_refs) %>%
  mutate(total_referrals = yes_va_referral_count + non_va_referral_count,
         non_va_as_prop_of_total = non_va_referral_count / total_referrals) %>%
  filter(str_detect(stopCode_group, "Primary") == T)
```

# Front Matter  

## Description of this report  

* This report is written in response for feedback on the "Referrals for Primary Care in the Veterans Health Administration (VHA)" abstract 
    + It focuses on PC only (i.e., eliminates urology, heme/onc, and cardio)
    + It changes the focus from rural to rural

    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$actyMonth)`
    + The last observation in the data occurs on `r max(analytic_df$actyMonth)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + Each row is a month

* Description of analyses 
    + Outcome
    + Technique
    + Link function, if applicable
    
    
## Primary Care  
```{r pc_total_referrals}
total_refs_by_nonVA <- dbGetQuery(oabi_con,
           "select count(*) as referral_count, stopCode_group, non_va
           from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
           where fy < 2022
           group by stopCode_group, non_va") %>%
  arrange(stopCode_group, non_va)
#
pc_refs_total <- total_refs_by_nonVA %>%
  filter(stopCode_group == "Primary care")
#
pc_total_refs_table <- tibble(
  name = "Total Referrals",
  yes_va = comma(pc_refs_total[[1]][1], accuracy = 1),
  non_va = comma(pc_refs_total[[1]][2], accuracy = 1),
  p_val = "N/A"
)
#####
uniques_by_nonVA <- dbGetQuery(oabi_con,
           "select count(distinct scrssn) as referral_count, stopCode_group, non_va
           from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
           where fy < 2022
           group by stopCode_group, non_va") %>%
  arrange(stopCode_group, non_va)
#
uniques_pc <- uniques_by_nonVA %>%
  filter(stopCode_group == "Primary care")
# 
pc_uniques_table <- tibble(
  name = "Uniques Receiving Referrals",
  yes_va = comma(uniques_pc[[1]][1], accuracy = 1),
  non_va = comma(uniques_pc[[1]][2], accuracy = 1),
  p_val = "N/A"
)
#####
refs_by_urh <- dbGetQuery(oabi_con,
           "with CTE as(
	select *, rural_flag = case when urh <> 'U' AND urh IS NOT NULL then 1 else 0 end
	from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
           where fy < 2022
	)
select AVG(cast(rural_flag as float)) as avg_rural
	, STDEV(rural_flag) as sd_rural
	, sum(rural_flag) as sum_rural
	, non_va, stopCode_group
from CTE
group by non_va, stopCode_group
") %>%
  arrange(stopCode_group, non_va)
#
pc_refs_urh1 <- refs_by_urh %>%
  filter(stopCode_group == "Primary care")
#
urh_pc_ttest <- t.test2(pc_refs_urh1[[1]][1], pc_refs_urh1[[1]][2],
                        pc_refs_urh1[[2]][1], pc_refs_urh1[[2]][2],
                        pc_refs_urh1[[3]][1], pc_refs_urh1[[3]][2])
#
pc_refs_urh <- pc_refs_urh1  %>%
  mutate_at(c(1, 2), ~percent(., accuracy = 0.1))
#
pc_urh_table <- tibble(
  name = "Rural Patients % (SD)",
  yes_va = paste0(pc_refs_urh[[1]][1], " (", pc_refs_urh[[2]][1], ")"),
  non_va = paste0(pc_refs_urh[[1]][2], " (", pc_refs_urh[[2]][2], ")"),
  p_val = urh_pc_ttest[4]
)
#####
refs_by_dta <- dbGetQuery(oabi_con,
                          "
  select AVG(cast(dta as float)) as avg_dta
	, STDEV(dta) as sd_dta
	, count(*) as sum_dta
	, non_va, stopCode_group
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where fy < 2022
group by non_va, stopCode_group") %>%
  arrange(stopCode_group, non_va)
#
pc_refs_dta <- refs_by_dta %>%
  filter(stopCode_group == "Primary care")
#
dta_pc_ttest <- t.test2(pc_refs_dta[[1]][1], pc_refs_dta[[1]][2],
                        pc_refs_dta[[2]][1], pc_refs_dta[[2]][2],
                        pc_refs_dta[[3]][1], pc_refs_dta[[3]][2])
#
pc_dta_table <- tibble(
  name = "Days to Approved (SD)",
  yes_va = paste0(comma(pc_refs_dta[[1]][1], accuracy = 0.1), " (", comma(pc_refs_dta[[2]][1], accuracy = 0.1), ")"),
  non_va = paste0(comma(pc_refs_dta[[1]][2], accuracy = 0.1), " (", comma(pc_refs_dta[[2]][2], accuracy = 0.1), ")"),
  p_val = dta_pc_ttest[4]
)
#####
refs_by_dts <- dbGetQuery(oabi_con,
                          "
  select AVG(cast(dts as float)) as avg_dts
	, STDEV(dts) as sd_dts
	, count(*) as sum_dts
	, non_va, stopCode_group
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where fy < 2022
group by non_va, stopCode_group") %>%
  arrange(stopCode_group, non_va)
#
pc_refs_dts <- refs_by_dts %>%
  filter(stopCode_group == "Primary care")
#
dts_pc_ttest <- t.test2(pc_refs_dts[[1]][1], pc_refs_dts[[1]][2],
                        pc_refs_dts[[2]][1], pc_refs_dts[[2]][2],
                        pc_refs_dts[[3]][1], pc_refs_dts[[3]][2])
#
pc_dts_table <- tibble(
  name = "Days to Scheduled (SD)",
  yes_va = paste0(comma(pc_refs_dts[[1]][1], accuracy = 0.1), " (", comma(pc_refs_dts[[2]][1], accuracy = 0.1), ")"),
  non_va = paste0(comma(pc_refs_dts[[1]][2], accuracy = 0.1), " (", comma(pc_refs_dts[[2]][2], accuracy = 0.1), ")"),
  p_val = dts_pc_ttest[4]
)

#####
refs_by_dtc <- dbGetQuery(oabi_con,
                          "
  select AVG(cast(dtc as float)) as avg_dtc
	, STDEV(dtc) as sd_dtc
	, count(*) as sum_dtc
	, non_va, stopCode_group
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where fy < 2022
group by non_va, stopCode_group") %>%
  arrange(stopCode_group, non_va)
#
pc_refs_dtc <- refs_by_dtc %>%
  filter(stopCode_group == "Primary care")
#
dtc_pc_ttest <- t.test2(pc_refs_dtc[[1]][1], pc_refs_dtc[[1]][2],
                        pc_refs_dtc[[2]][1], pc_refs_dtc[[2]][2],
                        pc_refs_dtc[[3]][1], pc_refs_dtc[[3]][2])
#
pc_dtc_table <- tibble(
  name = "Days to Completed (SD)",
  yes_va = paste0(comma(pc_refs_dtc[[1]][1], accuracy = 0.1), " (", comma(pc_refs_dtc[[2]][1], accuracy = 0.1), ")"),
  non_va = paste0(comma(pc_refs_dtc[[1]][2], accuracy = 0.1), " (", comma(pc_refs_dtc[[2]][2], accuracy = 0.1), ")"),
  p_val = dtc_pc_ttest[4]
)

#####
foo <- ls(pattern = "_table")
do.call(bind_rows, mget(foo)) %>%
  mutate(name = factor(name, 
                       ordered = TRUE,
                       levels = c("Total Referrals", "Uniques Receiving Referrals",
                                  "Rural Patients % (SD)", "Days to Approved (SD)", 
                                  "Days to Scheduled (SD)", "Days to Completed (SD)"))) %>%
  arrange(name) %>%
  kbl(col.names = c("", "Yes VA", "Non-VA", "p-value"),
      align = c("l", "r", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```
