---
title: "Community Referrals"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
pactcc_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "PACT_CC",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r}
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
# setting flag for initiated_pc_crh_b4_feb_2020
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         initiated_pc_crh_b4_march_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-03-01"), TRUE, FALSE),
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#identifying sta5as that had at least 10 PC CRH encounters per month from October, 2019 through March, 2020
sta5as_w_gt9 <- crh_flag %>%
  filter(first_6_mos_w_10_flag == 1) %>%
  select(sta5a) %>% pull
# identifying sta5as that initiated PC CRH before February, 2020
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
# identifying pilot sta5as
pilot_sites <- dbGetQuery(pactcc_con,
                          "select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY20_working 
                          UNION
                          select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY21_working ") %>%
  filter(vimpact_pilot == 1) %>%
  select(sta5a = spoke_sta5a)
# propensity score-matched sta5as
ps_matched <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/ps_matched_sta5as.csv")
# identifying ps-matched sta5as 
ps_groups_w_gt9 <- ps_matched %>%
  filter(at_least_10_pc_crh_flag == 1
         & sta5a %in% sta5as_w_gt9) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a) %>%
  pull
# timely care success rate
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#VSSC access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#make dataframe of all dates and a column for time
dates <- access_metrics %>%
  filter(vssc_month <= ymd("2020-02-01")) %>%#this is where we DO NOT drop October, 2019
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#Uniques in PCMM, categorized
scrssn_count <- dbGetQuery(pactcc_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2019
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy19, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy19 < 450 ~ "< 450",
    scrssn_count_avg_fy19 >= 450 & scrssn_count_avg_fy19 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy19 >= 2400 & scrssn_count_avg_fy19 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy19 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#x intercept at October, 2019
vline_xint <- as.numeric(ymd("2019-10-01"))
#####
# Community care referrals for Primary Care
pc_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_PC_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")
#
pc_summary_month <- pc_referrals %>%
  group_by(vssc_month) %>%
  summarise(pc_referrals = sum(`Referral Count`, na.rm = T))
#
pc_summary_qtr <- pc_referrals %>%
  group_by(fy_qtr) %>%
  summarise(pc_referrals = sum(`Referral Count`, na.rm = T))
# Community care referrals, total
total_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_total_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")

# Community care referrals, ED
ed_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_ED_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")
#

#
ed_summary_month <- ed_referrals %>%
  group_by(vssc_month) %>%
  summarise(ed_referrals = sum(`Referral Count`, na.rm = T))
#
ed_summary_qtr <- ed_referrals %>%
  group_by(fy_qtr) %>%
  summarise(ed_referrals = sum(`Referral Count`, na.rm = T))
# Community care referrals, dialysis
dialysis_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_dialysis_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")

#
dialysis_summary_month <- dialysis_referrals %>%
  group_by(vssc_month) %>%
  summarise(dialysis_referrals = sum(`Referral Count`, na.rm = T))
#
dialysis_summary_qtr <- dialysis_referrals %>%
  group_by(fy_qtr) %>%
  summarise(dialysis_referrals = sum(`Referral Count`, na.rm = T))
# Community care referrals, mental healht
mh_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_MH_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")

#
mh_summary_month <- mh_referrals %>%
  group_by(vssc_month) %>%
  summarise(mh_referrals = sum(`Referral Count`, na.rm = T))
#
mh_summary_qtr <- mh_referrals %>%
  group_by(fy_qtr) %>%
  summarise(mh_referrals = sum(`Referral Count`, na.rm = T))
# Community care referrals, pain management
pain_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_painMngmt_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")

#
pain_summary_month <- pain_referrals %>%
  group_by(vssc_month) %>%
  summarise(pain_referrals = sum(`Referral Count`, na.rm = T))
#
pain_summary_qtr <- pain_referrals %>%
  group_by(fy_qtr) %>%
  summarise(pain_referrals = sum(`Referral Count`, na.rm = T))
# Community care referrals, urology
urology_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_urology_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")

#
urology_summary_month <- urology_referrals %>%
  group_by(vssc_month) %>%
  summarise(urology_referrals = sum(`Referral Count`, na.rm = T))
#
urology_summary_qtr <- urology_referrals %>%
  group_by(fy_qtr) %>%
  summarise(urology_referrals = sum(`Referral Count`, na.rm = T))
# Community care referrals, cardiology
cardiology_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_cardiology_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")

#
cardiology_summary_month <- cardiology_referrals %>%
  group_by(vssc_month) %>%
  summarise(cardiology_referrals = sum(`Referral Count`, na.rm = T))
#
cardiology_summary_qtr <- cardiology_referrals %>%
  group_by(fy_qtr) %>%
  summarise(cardiology_referrals = sum(`Referral Count`, na.rm = T))
# Community care referrals, chiropractic
chiropractic_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_chiropractic_sta5a_month.csv") %>%
  mutate(parent_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4")

#
chiropractic_summary_month <- chiropractic_referrals %>%
  group_by(vssc_month) %>%
  summarise(chiropractic_referrals = sum(`Referral Count`, na.rm = T))
#
chiropractic_summary_qtr <- chiropractic_referrals %>%
  group_by(fy_qtr) %>%
  summarise(chiropractic_referrals = sum(`Referral Count`, na.rm = T))
```

```{r pcccrf}
parent_to_sta5a_crosswalk <- vast %>%
  select(sta5a, parent_station_sta5a) %>%
  distinct
#--
pc_refs_limited <- pc_referrals %>%
  select(parent_sta5a, fy_qtr, "pc_referral_count" = `Referral Count`)
#--
pcccrf <- pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., parent_to_sta5a_crosswalk) %>%
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_avg_fy19) == F)
#--
pcmm_by_parent <- scrssn_count %>%
  left_join(., parent_to_sta5a_crosswalk) %>%
  group_by(parent_station_sta5a) %>%
  summarise(scrssn_count = sum(scrssn_count_avg_fy19))
```

# Community Referrals - Total  
 
```{r}
total_referrals %>%
  group_by(fy_qtr) %>%
  summarise(referrals = sum(`Referral Count`, na.rm = T)) %>%
  left_join(., pc_summary_qtr) %>%
  mutate(not_pc_referrals = referrals - pc_referrals) %>%
  select(-referrals) %>%
  pivot_longer(-fy_qtr) %>%
  mutate(name_lab = if_else(name == "pc_referrals", "Primary Care", "Not Primary Care"))  %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  ggsci::scale_color_aaas() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```


# Community Referrals for Primary Care  

```{r}
pc_referrals %>%
  group_by(fy_qtr) %>%
  summarise(referrals = sum(`Referral Count`, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = referrals, group = "A")) +
  geom_line(color = "red") +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals for Primary Care",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

# Community Referrals - Additional Examples  
     
```{r}
pc_summary_qtr %>%
  left_join(., dialysis_summary_qtr) %>%
  left_join(., ed_summary_qtr) %>%
  left_join(., mh_summary_qtr) %>%
  left_join(., pain_summary_qtr) %>%
  left_join(., urology_summary_qtr) %>%
  left_join(., chiropractic_summary_qtr) %>%
  left_join(., cardiology_summary_qtr) %>%
  pivot_longer(-fy_qtr) %>%
  mutate(name_lab = case_when(name == "pc_referrals" ~ "Primary Care",
                              str_detect(name, "dialysis") ~ "Dialysis",
                              str_detect(name, "ed_") ~ "ED",
                              str_detect(name, "mh") ~ "Mental Health",
                              str_detect(name, "pain") ~ "Pain Management",
                              str_detect(name, "urology") ~ "Urology",
                              str_detect(name, "chiro") ~ "Chiropractic",
                              str_detect(name, "cardio") ~ "Cardiology"),
         name_lab = fct_reorder(name_lab, value, tail, n = 1, .desc = TRUE))%>%
  ggplot(data = .,
         aes(x = fy_qtr, y = value, group = name_lab, color = name_lab)) +
  geom_line(size = 1) +
  ggsci::scale_color_aaas() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```


# The Problem  

* Unfortunately the deepest I can dive into the origin of the Primary Care referrals seems to be the parent station; when I select "Division" I get the 139 sta5as we generally associate with parent stations

* I suspect that this isn't an error per-se, since there are `r ed_referrals %>% select(Division) %>% n_distinct()` distinct sta5as with ED referrals, `r chiropractic_referrals %>% select(Division) %>% n_distinct()` distinct sta5as with Chiropractic referrals, and `r cardiology_referrals %>% select(Division) %>% n_distinct()` with Cardiology referrals, for example

## A solution?  
* One potential solution is to simply assign the parent-station value for a "PC Community Care Referral Load" (PCCCRL) to each of the child sta5as:

$$ \text{Primary Care Community Care Referral Load}_{\text{ Sta5a}}=\frac{\text{Number Of PC Referrals}_{\text{ At Parent}}}{\text{Number in PCMM}_{\text{ At Sta5a}}}\times10,000 $$

* So, let's look at that


# PCCCRL - National  

```{r}
pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  group_by(fy_qtr) %>%
  summarise(pc_referral_count = sum(pc_referral_count),
            scrssn_count = sum(scrssn_count, na.rm = T)) %>%
  mutate(refs_per_10k_pcmm = (pc_referral_count / scrssn_count) * 10000) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = "A")) +
  geom_line() +
  geom_line(size = 1) +
  ggsci::scale_color_nejm() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For PC\nper 10,000 in PCMM",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

# PCCCRL - By VISN  

```{r}
parent_visns <- vast %>% select(parent_visn) %>% distinct %>% arrange(parent_visn) %>% pull
#
pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(pc_referral_count = sum(pc_referral_count),
            scrssn_count = sum(scrssn_count)) %>%
  ungroup() %>%
  mutate(refs_per_10k_pcmm = (pc_referral_count / scrssn_count) * 10000,,
         parent_visn = fct_reorder(parent_visn, refs_per_10k_pcmm, tail, n = 1, .desc = TRUE)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = parent_visn, color = parent_visn)) +
  geom_line() +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For PC\nper 10,000 in PCMM",
       x = "FY-Qtr",
       color = "VISN") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

## PCCCRL - By VISN I  

```{r}
pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(pc_referral_count = sum(pc_referral_count),
            scrssn_count = sum(scrssn_count)) %>%
  ungroup() %>%
  mutate(refs_per_10k_pcmm = (pc_referral_count / scrssn_count) * 10000,
         parent_visn = fct_reorder(parent_visn, refs_per_10k_pcmm, tail, n = 1, .desc = TRUE)) %>%
  filter(parent_visn %in% parent_visns[1:6]) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = parent_visn, color = parent_visn)) +
  geom_line() +
  geom_line(size = 1) +
  ggsci::scale_color_nejm() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For PC\nper 10,000 in PCMM",
       x = "FY-Qtr",
       color = "VISN") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

## PCCCRL - By VISN II  

```{r}
pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(pc_referral_count = sum(pc_referral_count),
            scrssn_count = sum(scrssn_count)) %>%
  ungroup() %>%
  mutate(refs_per_10k_pcmm = (pc_referral_count / scrssn_count) * 10000,
         parent_visn = fct_reorder(parent_visn, refs_per_10k_pcmm, tail, n = 1, .desc = TRUE)) %>%
  filter(parent_visn %in% parent_visns[7:12]) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = parent_visn, color = parent_visn)) +
  geom_line() +
  geom_line(size = 1) +
  ggsci::scale_color_aaas() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For PC\nper 10,000 in PCMM",
       x = "FY-Qtr",
       color = "VISN") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

## PCCCRL - By VISN III  
* VISN 20!

```{r}
pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(pc_referral_count = sum(pc_referral_count),
            scrssn_count = sum(scrssn_count)) %>%
  ungroup() %>%
  mutate(refs_per_10k_pcmm = (pc_referral_count / scrssn_count) * 10000,
         parent_visn = fct_reorder(parent_visn, refs_per_10k_pcmm, tail, n = 1, .desc = TRUE)) %>%
  filter(parent_visn %in% parent_visns[13:18]) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = parent_visn, color = parent_visn)) +
  geom_line() +
  geom_line(size = 1) +
  ggsci::scale_color_jco() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For PC\nper 10,000 in PCMM",
       x = "FY-Qtr",
       color = "VISN") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

# VISN 20  
## How Different?  
* VISN 20 is significantly different from the other VISNs in terms of PCCCRF:

```{r}
visn_df_for_ttest <- pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(pc_referral_count = sum(pc_referral_count),
            scrssn_count = sum(scrssn_count)) %>%
  mutate(refs_per_10k_pcmm = (pc_referral_count / scrssn_count) * 10000,
         visn_20_flag = if_else(parent_visn == "20", 1, 0))
#
t.test(refs_per_10k_pcmm ~ visn_20_flag, data = visn_df_for_ttest)
```

* VISN 20 is significantly different from the other VISNs in terms of total PC referrals as well:

```{r}
visn_df_for_ttest <- pc_refs_limited %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(pc_referral_count = sum(pc_referral_count),
            scrssn_count = sum(scrssn_count)) %>%
  mutate(refs_per_10k_pcmm = (pc_referral_count / scrssn_count) * 10000,
         visn_20_flag = if_else(parent_visn == "20", 1, 0))
#
t.test(pc_referral_count ~ visn_20_flag, data = visn_df_for_ttest)
```

## What About Other Care Types?  

### Emergency  
```{r}
ed_referrals %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(ed_referral_count = sum(`Referral Count`),
            scrssn_count = sum(scrssn_count)) %>%
  ungroup() %>%
  mutate(refs_per_10k_pcmm = (ed_referral_count / scrssn_count) * 10000,
         parent_visn = fct_reorder(parent_visn, refs_per_10k_pcmm, tail, n = 1, .desc = TRUE)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = parent_visn, color = parent_visn)) +
  geom_line() +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For ED\nper 10,000 in PCMM",
       x = "FY-Qtr",
       color = "VISN") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

### Cardiology     
```{r}
cardiology_referrals %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(ed_referral_count = sum(`Referral Count`),
            scrssn_count = sum(scrssn_count)) %>%
  ungroup() %>%
  mutate(refs_per_10k_pcmm = (ed_referral_count / scrssn_count) * 10000,
         parent_visn = fct_reorder(parent_visn, refs_per_10k_pcmm, tail, n = 1, .desc = TRUE)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = parent_visn, color = parent_visn)) +
  geom_line() +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For Cardiology\nper 10,000 in PCMM",
       x = "FY-Qtr",
       color = "VISN") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

### Chiropractic     
```{r}
chiropractic_referrals %>%
  rename(parent_station_sta5a = parent_sta5a) %>%
  left_join(., pcmm_by_parent) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct) %>%
  filter(is.na(parent_visn) == F) %>%
  group_by(fy_qtr, parent_visn) %>%
  summarise(ed_referral_count = sum(`Referral Count`),
            scrssn_count = sum(scrssn_count)) %>%
  ungroup() %>%
  mutate(refs_per_10k_pcmm = (ed_referral_count / scrssn_count) * 10000,
         parent_visn = fct_reorder(parent_visn, refs_per_10k_pcmm, tail, n = 1, .desc = TRUE)) %>%
  ggplot(data = .,
         aes(x = fy_qtr, y = refs_per_10k_pcmm, group = parent_visn, color = parent_visn)) +
  geom_line() +
  geom_line(size = 1) +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(y = "Community Care Referrals For Chiropractic\nper 10,000 in PCMM",
       x = "FY-Qtr",
       color = "VISN") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```


# Comparing PC CRH to No PC CRH  

## All Sta5as  
* Note that the metric is now per 1,000 in PCMM, rather than per 10,000:

$$ \text{Primary Care Community Care Referral Load}_{\text{ Sta5a}}=\frac{\text{Number Of PC Referrals}_{\text{ At Parent}}}{\text{Number in PCMM}_{\text{ At Sta5a}}}\times1,000 $$


```{r}
pcccrf %>%
  left_join(., crh_flag %>% select(sta5a, crh_10_flag)) %>%
  mutate(crh_flag = if_else(is.na(crh_10_flag), 0, 1),
         refs_per_1k_pcmm = (pc_referral_count / scrssn_count_avg_fy19) * 1000) %>%
  t.test(refs_per_1k_pcmm ~ crh_flag, data = .)
```

```{r}
pcccrf %>%
  left_join(., crh_flag %>% select(sta5a, crh_10_flag)) %>%
  mutate(crh_flag = factor(if_else(is.na(crh_10_flag), "No PC CRH", "PC CRH")),
         refs_per_1k_pcmm = (pc_referral_count / scrssn_count_avg_fy19) * 1000) %>%
  filter(refs_per_1k_pcmm < 100) %>%
  ggplot(data = .,
         aes(group = crh_flag, y = refs_per_1k_pcmm, x = crh_flag, fill = crh_flag)) +
  geom_boxplot() +
  labs(y = "Referrals per 1,000 in PCMM") +
  theme(legend.position = "none",
        axis.title.x = element_blank())
```


## Without VISN 20    
* Note that the metric is now per 1,000 in PCMM, rather than per 10,000

```{r}
pcccrf %>%
  left_join(., crh_flag %>% select(sta5a, crh_10_flag)) %>%
  left_join(., vast %>% select(sta5a, parent_visn)) %>%
  filter(parent_visn != "20" & is.na(parent_visn) == F) %>%
  mutate(crh_flag = if_else(is.na(crh_10_flag), 0, 1),
         refs_per_1k_pcmm = (pc_referral_count / scrssn_count_avg_fy19) * 1000) %>%
  t.test(refs_per_1k_pcmm ~ crh_flag, data = .)
```


## CBOCs Only      
* Note that the metric is now per 1,000 in PCMM, rather than per 10,000

```{r}
pcccrf %>%
  left_join(., crh_flag %>% select(sta5a, crh_10_flag)) %>%
  left_join(., vast %>% select(sta5a, s_abbr, parent_visn)) %>%
  filter(str_detect(s_abbr, "CBOC") & parent_visn != "20") %>%
  mutate(crh_flag = if_else(is.na(crh_10_flag), 0, 1),
         refs_per_1k_pcmm = (pc_referral_count / scrssn_count_avg_fy19) * 1000) %>%
  t.test(refs_per_1k_pcmm ~ crh_flag, data = .)
```

## Propensity Score Matched Only        
* Note that the metric is now per 1,000 in PCMM, rather than per 10,000

```{r}
pcccrf %>%
  inner_join(., ps_matched) %>%
  mutate(refs_per_1k_pcmm = (pc_referral_count / scrssn_count_avg_fy19) * 1000) %>%
  t.test(refs_per_1k_pcmm ~ at_least_10_pc_crh_flag, data = .)
```