---
title: "VSSC PC Community Care Referrals"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
pactcc_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "PACT_CC",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#
every_nth = function(n) {
  return(function(x) {x[c(TRUE, rep(FALSE, n - 1))]})
}
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r}
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
# setting flag for initiated_pc_crh_b4_feb_2020
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         initiated_pc_crh_b4_march_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-03-01"), TRUE, FALSE),
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#identifying sta5as that had at least 10 PC CRH encounters per month from October, 2019 through March, 2020
sta5as_w_gt9 <- crh_flag %>%
  filter(first_6_mos_w_10_flag == 1) %>%
  select(sta5a) %>% pull
# identifying sta5as that initiated PC CRH before February, 2020
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
# identifying pilot sta5as
pilot_sites <- dbGetQuery(pactcc_con,
                          "select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY20_working 
                          UNION
                          select distinct spoke_sta5a, vimpact_pilot
                          from PACT_CC.CRH.CRH_sites_FY21_working ") %>%
  filter(vimpact_pilot == 1) %>%
  select(sta5a = spoke_sta5a)
# propensity score-matched sta5as
ps_matched <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/ps_matched_sta5as.csv")
# identifying ps-matched sta5as 
ps_groups_w_gt9 <- ps_matched %>%
  filter(at_least_10_pc_crh_flag == 1
         & sta5a %in% sta5as_w_gt9) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a) %>%
  pull
# timely care success rate
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#VSSC access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#make dataframe of all dates and a column for time
dates <- access_metrics %>%
  filter(vssc_month <= ymd("2020-02-01")) %>%#this is where we DO NOT drop October, 2019
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#Uniques in PCMM, categorized
scrssn_count <- dbGetQuery(pactcc_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2019
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy19, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy19 < 450 ~ "< 450",
    scrssn_count_avg_fy19 >= 450 & scrssn_count_avg_fy19 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy19 >= 2400 & scrssn_count_avg_fy19 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy19 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#scrssn count at parent-sta5a
pcmm_parent_sta5a <- dbGetQuery(pactcc_con,
                                "with CTE as(
                                	select a.*, b.parent_station_sta5a
                                	from [PACT_CC].[econ].PatientPCP as a
                                	inner join [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as b
                                	on a.Sta5a = b.sta5a
                                	where fy > 2018
                                	)
                                select count(distinct ScrSSN_num) as scrssn_count, parent_station_sta5a, fy, qtr
                                from CTE
                                group by parent_station_sta5a, fy, qtr")
#x intercept at October, 2019
vline_xint <- as.numeric(ymd("2019-10-01"))
#####
```


```{r vssc_community_refs}
# VSSC Community care referrals for Primary Care
pc_referrals <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/community_referrals_PC_sta5a_month.csv") %>%
  mutate(parent_station_sta5a = if_else(str_sub(Division, start = 11, end = 11) == ")",
                         str_sub(Division, start = 8, end = 10),
                         str_sub(Division, start = 8, end = 12)),
         visn = str_sub(Division, start = 3, end = 4),
         month_c = str_to_title(str_sub(`Referral From Date`, end = 3)),
         month_n = match(month_c, month.abb),
         qtr = case_when(month_n %in% c(10, 11, 12) ~ 1,
                         month_n %in% c(1, 2, 3) ~ 2,
                         month_n %in% c(4, 5, 6) ~ 3,
                         month_n %in% c(7, 8, 9) ~ 4),
         fy = as.numeric(str_c("20", str_sub(`Referral From Date`, start = -2))),
         cy = if_else(month_n > 9, fy - 1, fy),
         vssc_month = ymd(str_c(cy, month_n, "01", sep = "-")),
         fy_qtr = str_c(fy, qtr, sep = "-")) %>%
  filter(fy_qtr != "2022-4") %>%
  inner_join(., vast %>% select(parent_station_sta5a, parent_visn) %>% distinct()) %>%
  rename(referral_count = `Referral Count`) %>%
  distinct()
#
pc_referrals_qtr <- pc_referrals %>%
  group_by(parent_station_sta5a, fy_qtr, fy, qtr) %>%
  summarise(referral_count = sum(referral_count, na.rm = T))
```

# Community Care Referrals from VSSC     

## Primary Care Community Care Referrals per 10,000 in PCMM - Parent Station     
* There are `r nrow(pc_referrals_qtr) %>% comma(accuracy = 1)` Parent-Station-Quarter combinations  
* Out of those observations `r sum(pc_referrals_qtr$referral_count == 1)` (`r (sum(pc_referrals_qtr$referral_count == 1) / nrow(pc_referrals_qtr)) %>% percent(accuracy = 0.1)`) have exactly 1 PC Community Care Referral, while `r sum(pc_referrals_qtr$referral_count < 11)` (`r (sum(pc_referrals_qtr$referral_count < 11) / nrow(pc_referrals_qtr)) %>% percent(accuracy = 0.1)`) have 10 or less

```{r}
pc_cc_refs_per_10k_parent_sta5a <- pc_referrals_qtr %>%
  inner_join(., pcmm_parent_sta5a) %>%
  left_join(., vast %>% select(parent_station_sta5a, parent_visn)) %>%
  mutate(pc_cc_refs_per_10k = referral_count / scrssn_count * 10000)
#
ggplot(data = pc_cc_refs_per_10k_parent_sta5a,
       aes(y = pc_cc_refs_per_10k)) +
  geom_boxplot(fill = "red") +
  labs(y = "PC CC Referrals per 10,000 in PCMM") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  scale_y_continuous(labels = comma_format(accuracy = 1))
#--
ggplot(data = pc_cc_refs_per_10k_parent_sta5a,
       aes(y = pc_cc_refs_per_10k, x = fy_qtr, group = parent_station_sta5a)) +
  geom_line() +
  labs(y = "PC CC Referrals per 10,000 in PCMM",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

## Without VISN 20       

```{r}
ggplot(data = subset(pc_cc_refs_per_10k_parent_sta5a, parent_visn != "20"),
       aes(y = pc_cc_refs_per_10k)) +
  geom_boxplot(fill = "red") +
  labs(y = "PC CC Referrals per 10,000 in PCMM") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  scale_y_continuous(labels = comma_format(accuracy = 1))
#
ggplot(data = subset(pc_cc_refs_per_10k_parent_sta5a, parent_visn %in% 
                       c("06", "09", "12", "15", "16", "17", "21", "19", "23")),
       aes(y = pc_cc_refs_per_10k)) +
  geom_boxplot(fill = "red") +
  labs(y = "PC CC Referrals per 10,000 in PCMM") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  facet_wrap(~parent_visn)
#==
ggplot(data = subset(pc_cc_refs_per_10k_parent_sta5a, parent_visn %ni% 
                       c("06", "09", "12", "15", "16", "17", "20", "21", "19", "23")),
       aes(y = pc_cc_refs_per_10k)) +
  geom_boxplot(fill = "blue") +
  labs(y = "PC CC Referrals per 10,000 in PCMM") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  facet_wrap(~parent_visn)
```


```{r}
ggplot(data = subset(pc_cc_refs_per_10k_parent_sta5a, parent_visn != "20"),
       aes(y = pc_cc_refs_per_10k, x = fy_qtr, group = parent_station_sta5a)) +
  geom_line() +
  labs(y = "PC CC Referrals per 10,000 in PCMM",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
#
ggplot(data = subset(pc_cc_refs_per_10k_parent_sta5a, parent_visn %in% 
                       c("06", "09", "12", "15", "16", "17", "21", "19", "23")),
       aes(y = pc_cc_refs_per_10k, x = fy_qtr, group = parent_station_sta5a)) +
  geom_line() +
  labs(y = "PC CC Referrals per 10,000 in PCMM",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
#
ggplot(data = subset(pc_cc_refs_per_10k_parent_sta5a, parent_visn %ni% 
                       c("06", "09", "12", "15", "16", "17","20", "21", "19", "23")),
       aes(y = pc_cc_refs_per_10k, x = fy_qtr, group = parent_station_sta5a)) +
  geom_line() +
  labs(y = "PC CC Referrals per 10,000 in PCMM",
       x = "FY-Qtr") +
  theme(axis.text.x = element_text(angle = 270,
                                   vjust = 0.4))
```

## Distributing to All Child Sta5as  

$$ \text{Primary Care Community Care Referral Load}_{\text{ Sta5a}}=\frac{\text{Number Of PC Referrals}_{\text{ At Parent}}}{\text{Uniques in PCMM}_{\text{ At Parent}}}\times10,000 $$


```{r}
vast %>%
  select(sta5a, parent_station_sta5a) %>%
  distinct %>%
  left_join(., pc_cc_refs_per_10k_parent_sta5a %>% ungroup %>%
              select(parent_station_sta5a, fy_qtr, referral_count, scrssn_count, parent_visn, pc_cc_refs_per_10k) %>%
              distinct) %>%
  left_join(., crh_flag %>%
              select(sta5a, crh_10_flag)) %>%
  mutate(crh_flag = if_else(is.na(crh_10_flag), "No PC CRH", "PC CRH")) %>%
  select(sta5a, parent_station_sta5a, fy_qtr, parent_visn, pc_cc_refs_per_10k, crh_flag) %>%
  ggplot(data = .,
         aes(x = crh_flag, y = pc_cc_refs_per_10k, group = crh_flag,
             fill = crh_flag)) +
  geom_boxplot() +
  ggsci::scale_fill_aaas() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  labs(y = "PC CC Referrals per 10,000 in PCMM")
```


```{r}
vast %>%
  select(sta5a, parent_station_sta5a) %>%
  distinct %>%
  left_join(., pc_cc_refs_per_10k_parent_sta5a %>% ungroup %>%
              select(parent_station_sta5a, fy_qtr, referral_count, scrssn_count, parent_visn, pc_cc_refs_per_10k) %>%
              distinct) %>%
  left_join(., crh_flag %>%
              select(sta5a, crh_10_flag)) %>%
  mutate(crh_flag = if_else(is.na(crh_10_flag), "No PC CRH", "PC CRH")) %>%
  select(sta5a, parent_station_sta5a, fy_qtr, parent_visn, pc_cc_refs_per_10k, crh_flag) %>%
  t.test(pc_cc_refs_per_10k ~ crh_flag, data = .)
```


