---
title: "Outcomes by Period and CRH, Matching vs. Not"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/ps_matched_sta5as_v3_1.csv")
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#
ps_matched_initiated_before_feb_20 <- ps_matched %>%
  filter(sta5a %in% crh_sta5as) %>%
  select(-at_least_10_pc_crh_flag) %>%
  inner_join(., ps_matched, by = "subclass") %>%
  select(sta5a = sta5a.y) %>%
  pull
  
  
#this is where exclusion criteria are applied:
  #1: must have Access metrics
  #2: must be in VAST
  #3: no missing scrssn_count_cat
  #4: CBOCs only
  #5: must have scrssn_count_avg_fy18 >= 450
sta5as_to_include <- access_metrics %>%#1: must have Access metrics
  select(sta5a) %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, "PC CRH", "No PC CRH")) %>%#making the crh_flag
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F #3: no missing scrssn_count_cat
         & str_detect(s_abbr, "CBOC")#4: CBOCs only
           & scrssn_count_cat != "< 450")
#this little table is for the functions i wrote for outputting tables, and I don't want to have to look for it later
# not strictly necissary
# scrssn_cat_count <- sta5as_to_include %>%
#   group_by(crh_flag, scrssn_count_cat) %>%
#   summarise(count = n()) %>%
#   mutate(count = as.character(count)) %>%
#   pivot_wider(names_from = scrssn_count_cat, values_from = count)
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  filter(sta5a %in% ps_matched_initiated_before_feb_20)
#making the analytic dataset without the PS matching restriction for comparison
analytic_df2 <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") & vssc_month > ymd("2018-09-01") & third_next_avail < 100) %>%#restrict to our timeframe
      left_join(., dates)
```

# Front Matter  

## Description of this report  

* This report does 2 things:
    1. It allows visual comparison of outcome slopes between CRH and non-CRH sites over 3 periods
    2. Acts as an example of the .html template I have in mind moving forward
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
    + Each row is a sta5a-month
    + This uses the naive PS matching scheme 
    + What else?
    
* Description of _Propensity Score_ matching
    + The current PS matching scheme version 3.1 (i.e., 3 sta5a-specific FY19 average outcomes are included)
    + This PS matching scheme includes `r n_distinct(ps_matched$subclass)` pairs of sta5a (i.e., `r nrow(ps_matched)` sta5as)
    + I could add a hyperlink here to the "official" PS Matching report, when we have one
    + Could also get fancy and output more model info from the PS match and include that here in a table, maybe?
  

* Description of plots  
    + The y-axes (i.e., outcomes) are: __New Patient Wait Time__, __Established Patient Wait Time__, and __Third Next Available__
    + The x-axis is time in months
    + The black lines are individual sta5as' monthly values
    + The regression lines are OLS regressions, stratified by PC CRH: $$y_{outcome}=x_{time}$$
    + The plots __without matching__ include all `r analytic_df2 %>% select(sta5a) %>% n_distinct()` sta5as, while the plots __with matching__ include the `r n_distinct(ps_matched$subclass)` sta5as (and their PS matches) that met our inclusion criteria before March, 2020


# New Patient Wait Time (plots omit values > 75)  
## Without Matching  
```{r}
ggplot(data = subset(analytic_df2, new_pc_pt_wt < 75),
       aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  labs(y = "New Patient Wait Time (days)") +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  geom_smooth(size = 1.5, data = subset(analytic_df2, vssc_month > ymd("2018-09-01") & vssc_month < ymd("2019-10-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F) +
  geom_smooth(size = 1.5, data = subset(analytic_df2, vssc_month > ymd("2019-09-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F)
```

 
## With Matching  
```{r}
ggplot(data = subset(analytic_df, new_pc_pt_wt < 75),
       aes(x = vssc_month, y = new_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  labs(y = "New Patient Wait Time (days)") +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  geom_smooth(size = 1.5, data = subset(analytic_df, vssc_month > ymd("2018-09-01") & vssc_month < ymd("2019-10-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F) +
  geom_smooth(size = 1.5, data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F)
```


# Established Patient Wait Time   
## Without Matching  
```{r}
ggplot(data = analytic_df2,
       aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  labs(y = "Established Patient Wait Time (days)") +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  geom_smooth(size = 1.5, data = subset(analytic_df2, vssc_month > ymd("2018-09-01") & vssc_month < ymd("2019-10-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F) +
  geom_smooth(size = 1.5, data = subset(analytic_df2, vssc_month > ymd("2019-09-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F)
```

 
## With Matching  
```{r}
ggplot(data = analytic_df,
       aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  labs(y = "Established Patient Wait Time (days)") +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  geom_smooth(size = 1.5, data = subset(analytic_df, vssc_month < ymd("2018-10-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F) +
  geom_smooth(size = 1.5, data = subset(analytic_df, vssc_month > ymd("2018-09-01") & vssc_month < ymd("2019-10-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F) +
  geom_smooth(size = 1.5, data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F)
```

# Third Next Available Appointment     
## Without Matching (plots omit values > 60)    
```{r}
ggplot(data = subset(analytic_df2, third_next_avail < 60),
       aes(x = vssc_month, y = third_next_avail, group = sta5a)) +
  geom_line(alpha = 0.3) +
  labs(y = "Third Next Available Appointment (days)") +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  geom_smooth(size = 1.5, data = subset(analytic_df2, vssc_month > ymd("2018-09-01") & vssc_month < ymd("2019-10-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F) +
  geom_smooth(size = 1.5, data = subset(analytic_df2, vssc_month > ymd("2019-09-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F)
```

 
## With Matching  
```{r}
ggplot(data = subset(analytic_df, third_next_avail < 60),
       aes(x = vssc_month, y = third_next_avail, group = sta5a)) +
  geom_line(alpha = 0.3) +
  labs(y = "Third Next Available Appointment (days)") +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  geom_smooth(size = 1.5, data = subset(analytic_df, vssc_month > ymd("2018-09-01") & vssc_month < ymd("2019-10-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F) +
  geom_smooth(size = 1.5, data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
              aes(group = crh_flag, color = crh_flag), 
              method = "lm", se = F)
```

# An aside about period of PC CRH Initiation  

```{r}
crh_flag %>%
  mutate(period_initiating_crh = factor(period_initiating_crh,
                                        ordered = T,
                                        levels = c("Initiated PC CRH Before 9/2019",
                                                   "Initiated PC CRH Between 10/2019 and 2/2020",
                                                   "Initiated PC CHR Between 3/2020 and 2/2021",
                                                   "Initiated PC CRH After 2/2021"))) %>%
  filter(is.na(period_initiating_crh) == F) %>%
  group_by(period_initiating_crh) %>%
  summarise(count = n()) %>%
  kbl(col.names = c("Period Meeting Inclusion Criteria", "Number of Sta5as")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```

```{r}
crh_flag %>%
  group_by(first_mo_w_mt9_pc_crh) %>%
  summarise(count = n()) %>%
  kbl(col.names = c("First Month Meeting Inclusion Criteria", "Number of Sta5as")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```
