---
title: "PC CRH Analysis: Final PS Matching Model v3.0"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```



```{r reading_in}
sta5a_demog <- dbGetQuery(oabi_con,
                          "select a.sta5a, a.nosos_3mo_avg, a.obs_exp_panel_ratio_3mo_avg, a.team_pcp_ap_fte_total_3mo_avg
	, b.pcmm_scrssn_count
	, c.est_pc_pt_wt_avg, c.new_pc_pt_wt_avg, c.third_next_avail_avg, c.tc_success_prop_avg, c.tc_pc_success_prop_avg
	, d.adi_natRnk_avg
	, e.avg_non_va_cons, e.avg_tot_cons, e.cons_rate_avg, e.non_va_cons_rate_per_10k_pcmm
	, f.rural_prop
	, at_least_10_pc_crh_flag = case	
		when crh_flag.crh_10_flag = 1 then 1
		else 0 end
	, vast.parent_visn, vast.s_abbr
from [OABI_MyVAAccess].[crh_eval].F1_3_vssc_3mo_avg as a
left join [OABI_MyVAAccess].[crh_eval].F2_pcmm_scrssn_count as b
	on a.sta5a = b.sta5a
left join [OABI_MyVAAccess].[crh_eval].F3_access_metrics_3mo_avg as c
	on a.sta5a = c.sta5a
left join [OABI_MyVAAccess].[crh_eval].F4_adi as d
	on a.sta5a = d.sta5a
left join [OABI_MyVAAccess].[crh_eval].F5_avg_pc_cons as e
	on a.sta5a = e.sta6a
left join [OABI_MyVAAccess].[crh_eval].F6_urh_white_female_prop as f
	on a.sta5a = f.sta5a
left join [OABI_MyVAAccess].[crh_eval].C1_crh_flag as crh_flag
	on a.sta5a = crh_flag.sta5a
left join [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as vast
	on a.sta5a = vast.sta5a") %>%
  mutate(avg_tot_cons = replace_na(avg_tot_cons, 0),
         non_va_cons_rate_per_10k_pcmm = replace_na(non_va_cons_rate_per_10k_pcmm, 0),
         parent_visn = factor(parent_visn),
         adi_cat = case_when(adi_natRnk_avg < 25 ~ "0-24",
                             adi_natRnk_avg >= 25 & adi_natRnk_avg < 50 ~ "25-49",
                             adi_natRnk_avg >= 50 & adi_natRnk_avg < 75 ~ "50-74",
                             adi_natRnk_avg >= 75 ~ "75-100"),
         treat = if_else(at_least_10_pc_crh_flag == 1, 0, 1),
         s_abbr2 = case_when(s_abbr %in% c("MSCBOC", "PCCBOC") ~ "CBOC",
                             s_abbr %in% c("HCC", "VAMC") ~ "VAMC/HCC",
                             TRUE ~ s_abbr)) %>%
  mutate(pilot_visn_flag = if_else(parent_visn %in% c("06", "16", "19", "20"), "Pilot VISN", "Not a Pilot VISN")) %>%
  select(pcmm_scrssn_count
         , nosos_3mo_avg
         , obs_exp_panel_ratio_3mo_avg
         , team_pcp_ap_fte_total_3mo_avg
         , adi_natRnk_avg
         , rural_prop
         , non_va_cons_rate_per_10k_pcmm, sta5a, at_least_10_pc_crh_flag, pilot_visn_flag,
         est_pc_pt_wt_avg, new_pc_pt_wt_avg, third_next_avail_avg, s_abbr2) %>%
  drop_na()
#
sta5a_demog_no_missing <- sta5a_demog %>%
  filter(pcmm_scrssn_count > 450 & nosos_3mo_avg < 2 & non_va_cons_rate_per_10k_pcmm < 50
         & third_next_avail_avg < 60
         & s_abbr2 == "CBOC"
         & obs_exp_panel_ratio_3mo_avg < 5)
```



```{r PS_matching_pcmm}
opt_match_pcmm <- matchit(at_least_10_pc_crh_flag ~  
                       pilot_visn_flag
                      + pcmm_scrssn_count
                     + nosos_3mo_avg
                     + obs_exp_panel_ratio_3mo_avg
                     + team_pcp_ap_fte_total_3mo_avg
                     + adi_natRnk_avg
                     + rural_prop
                     + non_va_cons_rate_per_10k_pcmm
                     + third_next_avail_avg
                     + new_pc_pt_wt_avg
                     + est_pc_pt_wt_avg,
                     data = sta5a_demog_no_missing,
                     method = "optimal",
                     distance = "glm",
                     link = "logit",
                     exact = ~pilot_visn_flag)
#--
opt_matches_pcmm <- match.data(opt_match_pcmm)
```


# Dropped stations  
* From a starting set of `r sta5a_demog %>% nrow()` candidate sta5as, we drop  `r sta5a_demog %>% nrow() - sta5a_demog_no_missing %>% nrow()` sta5as that:
    + Are not CBOCs (`r sta5a_demog %>% drop_na() %>% filter(s_abbr2 != "CBOC") %>% nrow()`)
    + Have fewer than 450 uniques in PCMM (`r sta5a_demog %>% drop_na() %>% filter(pcmm_scrssn_count <= 450) %>% nrow()`)
    + Have an average NOSOS score > 2 (`r sta5a_demog %>% drop_na() %>% filter(nosos_3mo_avg > 2) %>% nrow()`)
    + Have more than 50 PC CCs per 10,000 Uniques in PCMM (`r sta5a_demog %>% drop_na() %>% filter(non_va_cons_rate_per_10k_pcmm > 50) %>% nrow()`)
    + Have third Next available > 60 days (`r sta5a_demog %>% drop_na() %>% filter(third_next_avail_avg > 60) %>% nrow()`)
    + Have Observed:Expected Panel Size > 5 (`r sta5a_demog %>% drop_na() %>% filter(obs_exp_panel_ratio_3mo_avg > 5) %>% nrow()`)
* This leaves `r nrow(sta5a_demog_no_missing)` sta5as   

# Propensity Score "Optimal" Matching


## Final Model    

-   Using [Optimal Matching](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html#optimal-pair-matching-method-optimal) we get `r nrow(opt_matches_pcmm) / 2` pairs\

-   Model: Treatment (i.e., at least two consecutive months with \>9 PC CRH encounters) =

    -   Pilot VISN (Exact)
    -   NOSOS (FY18 Q4 Avg)
    -   Observed:Expected PC Panel Size (FY18 Q4 Avg)
    -   Team PCP/AP FTE (FY18 Q4 Avg)
    -   Uniques in PCMM (FY18 Q4)
    -   ADI (FY18 Q4)
    -   Proportion rural (FY18 Q4)
    -   (Non-VA PCCC Consults / Total PCCC Consults) X (uniques in PCMM) X 10,000 (FY18 Q4 Avg)
    -   Third Next Available PC Appointment (FY18 Q4 Avg)
    -   Established Patient Waittime (FY18 Q4 Avg)
    -   New Patient Waittime (FY18 Q4 Avg)

-   We estimate the propensity score with logistic regression (i.e., GLM and logit link)
- [Absolute standardized mean difference:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm)$sum.matched[1,3], 3)` 
- [Variance ratio:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm)$sum.matched[1,4], 3)`
- [Empirical CDF:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) 
    - Mean: `r round(summary(opt_match_pcmm)$sum.matched[1,5], 2)`
    - Max: `r round(summary(opt_match_pcmm)$sum.matched[1,6], 2)`

```{r}
plot(opt_match_pcmm, type = "jitter", interactive = FALSE)
```

### QQ Plots    
```{r}
plot(opt_match_pcmm, type = "qq", interactive = FALSE,
     which.xs = c('pcmm_scrssn_count'
                     , 'nosos_3mo_avg'
                     , 'obs_exp_panel_ratio_3mo_avg'
                     , 'team_pcp_ap_fte_total_3mo_avg'
                     , 'adi_natRnk_avg'
                     , 'rural_prop'
                     , 'non_va_cons_rate_per_10k_pcmm'
                    , 'third_next_avail_avg'))
```

### eCDF Plots  
```{r}
plot(opt_match_pcmm, type = "ecdf", interactive = FALSE,
     which.xs = c('pcmm_scrssn_count'
                     , 'nosos_3mo_avg'
                     , 'obs_exp_panel_ratio_3mo_avg'
                     , 'team_pcp_ap_fte_total_3mo_avg'
                     , 'adi_natRnk_avg'
                     , 'rural_prop'
                     , 'non_va_cons_rate_per_10k_pcmm'
                    , 'third_next_avail_avg'))
```

```{r}
ps_plot_df_pcmm <- tibble(
  covariate = attributes(summary(opt_match_pcmm)$sum.all)$dimnames[[1]], 
  smd_matched = summary(opt_match_pcmm)$sum.matched[,3], 
  smd_preMatch = summary(opt_match_pcmm)$sum.all[,3]) %>%
  mutate(covariate = str_remove(covariate, "s_abbr2|census_division|pilot_visn_flag"),
         covariate = str_replace(covariate, "parent_visn", "V"),
         covar_lab = factor(case_when(
           covariate == "distance" ~ "Distance",
           str_detect(covariate, "nosos") == TRUE ~ "NOSOS",
           str_detect(covariate, "obs_exp") == TRUE ~ "Obs:Exp",
           str_detect(covariate, "team") == TRUE ~ "PCP/AP FTE",
           str_detect(covariate, "pcmm_") == TRUE ~ "PCMM ScrSSN Count",
           str_detect(covariate, "est_") == TRUE ~ "Established Patient WT",
           str_detect(covariate, "new_") == TRUE ~ "New Patient WT",
           str_detect(covariate, "third_") == TRUE ~ "Third-Next Available",
           str_detect(covariate, "adi") == TRUE ~ "ADI, Avg",
           str_detect(covariate, "age") == TRUE ~ "Age, Avg",
           str_detect(covariate, "male") == TRUE ~ "Male %",
           str_detect(covariate, "white") == TRUE ~ "White %",
           str_detect(covariate, "rural") == TRUE ~ "Rural %",
           str_detect(covariate, "gap") == TRUE ~ "Gap Metric",
           str_detect(covariate, "non_va") == TRUE ~ "Non-VA Consults per 10,000 in PCMM",
           TRUE ~ covariate
         ), ordered = TRUE, levels = rev(c("Distance","Not a Pilot VISN",
                                       "Pilot VISN","NOSOS","Obs:Exp","PCP/AP FTE",
                                       "PCMM ScrSSN Count", "Rural %", "ADI, Avg",
                                       "Non-VA Consults per 10,000 in PCMM",
                                       "Third-Next Available", "New Patient WT", "Established Patient WT")))) %>%
  select(-covariate) %>%
  pivot_longer(-covar_lab) %>%
  mutate(abs_smd = abs(value),
         name_lab = if_else(name == "smd_matched", "Matched", "Un-Matched"))
#
ggplot(data = ps_plot_df_pcmm,
       aes(x = abs_smd, y = covar_lab, group = name_lab, fill = name_lab)) +
  geom_point(shape = 21,
             size = 2.25) +
  scale_fill_manual(values = c(
    "Matched" = "black",
    "Un-Matched" = "white"
  )) +
  labs(x = "Absolute Standardized Mean Difference") +
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept = 0, lty = 1) +
  geom_vline(xintercept = 0.05, lty = 2) +
  geom_vline(xintercept = 0.1, lty = 1)
```


