---
title: "PC CRH Analysis: PS Matching & Naive Analysis"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
knitr::knit_hooks$set(inline = function(x){
  prettyNum(x, big.mark = ",")
})
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(DT)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading_in}
gap_join_dates <- dbGetQuery(oabi_con,
                             "with cte as(
select sta5a, dateadd(MONTH, -1, first_mo_w_mt9_pc_crh) as month_for_joining
from [OABI_MyVAAccess].[crh_eval].C1_crh_flag
where crh_10_flag = 1)
select cte.sta5a
	, cte.month_for_joining
from cte as cte
UNION
select sta5a
	, cast('2019-09-01' as date) as month_for_joining
from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06
where sta5a NOT IN (select sta5a from [OABI_MyVAAccess].[crh_eval].C1_crh_flag where crh_10_flag = 1)") %>%
  mutate(month_for_joining = ymd(month_for_joining),
         month_minus_2 = month_for_joining - months(2))
#=====
gap_metric <- read_csv("//vhacdwdwhapp15.vha.med.va.gov/PACT_CC/CRH/Documentation/Gap Metric/GapData_Jan2022.csv") %>%
  rename_all(tolower) %>%
  mutate(moyear = ymd(moyear))
#-----
gap_avg <- gap_join_dates %>%
  left_join(., gap_metric, by = c("sta5a" = "sta6a")) %>%
  filter(moyear >= month_minus_2 & moyear <= month_for_joining) %>%
  group_by(sta5a) %>%
  summarise(gap_3mo_avg = mean(gap, na.rm = T))
#===
sta5a_demog <- dbGetQuery(oabi_con,
                          "select vast.sta5a
	, at_least_10_pc_crh_flag = case	
		when crh_flag.crh_10_flag = 1 then 1
		else 0 end
	, vast.parent_visn
	, urh = case 
		when vast.urh_vast = 'U' then 'U'
		when vast.urh_vast <> 'U' then 'R'
		end
	, vast.census_division
	, vast.s_abbr
	, vssc.nosos_3mo_avg
	, vssc.obs_exp_panel_ratio_3mo_avg
	, vssc.team_pcp_ap_fte_total_3mo_avg
	, pcmm.pcmm_scrssn_count
	, access.est_pc_pt_wt_3mo_avg
	, access.new_pc_pt_wt_3mo_avg
	, access.third_next_avail_3mo_avg
	, adi.adi_natRnk_avg
	, age.avg_age_oct1_2020
	, prop_male = cast(demog.male_count as float) / cast(demog.scrssn_count as float)
	, prop_white = cast(demog.race_white_count as float) / cast(demog.scrssn_count as float)
	, prop_rural = cast(demog.urh_rural_count as float) / cast(demog.scrssn_count as float)
from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as vast
left join [OABI_MyVAAccess].[crh_eval].C1_crh_flag as crh_flag
	on vast.sta5a = crh_flag.sta5a
left join [OABI_MyVAAccess].[crh_eval].F1_3_vssc_3mo_avg as vssc
	on vast.sta5a = vssc.sta5a
left join [OABI_MyVAAccess].[crh_eval].F2_pcmm_scrssn_count_avg as pcmm
	on vast.sta5a = pcmm.sta5a
left join [OABI_MyVAAccess].[crh_eval].F3_access_metrics_3mo_avg as access
	on vast.sta5a = access.sta5a
left join [OABI_MyVAAccess].[crh_eval].F4_adi_avg as adi
	on vast.sta5a = adi.sta5a
left join [OABI_MyVAAccess].[crh_eval].D1_age_sta5a_qtr as age
	on vast.sta5a = age.Sta5a
left join [OABI_MyVAAccess].[crh_eval].D2_race_gender_urh_count as demog
	on vast.sta5a = demog.Sta5a
where age.FY = 2020 AND age.QTR = 1
	AND demog.fy = 2020 AND demog.qtr = 1") %>%
  mutate(parent_visn = factor(parent_visn),
         adi_cat = case_when(adi_natRnk_avg < 25 ~ "0-24",
                             adi_natRnk_avg >= 25 & adi_natRnk_avg < 50 ~ "25-49",
                             adi_natRnk_avg >= 50 & adi_natRnk_avg < 75 ~ "50-74",
                             adi_natRnk_avg >= 75 ~ "75-100"),
         treat = if_else(at_least_10_pc_crh_flag == 1, 0, 1),
         s_abbr2 = case_when(s_abbr %in% c("MSCBOC", "PCCBOC") ~ "CBOC",
                             s_abbr %in% c("HCC", "VAMC") ~ "VAMC/HCC",
                             TRUE ~ s_abbr)) %>%
  left_join(., gap_avg)
#
sta5a_demog_no_missing <- sta5a_demog %>%
  drop_na() %>%
  mutate(pilot_visn_flag = if_else(parent_visn %in% c("06", "16", "19", "20"), "Pilot VISN", "Not a Pilot VISN"))
```

```{r PS_matching}
opt_match <- matchit(at_least_10_pc_crh_flag ~ 
                       parent_visn 
                     + pilot_visn_flag
                     + census_division 
                     + s_abbr2
                     + nosos_3mo_avg
                     + obs_exp_panel_ratio_3mo_avg
                     + team_pcp_ap_fte_total_3mo_avg
                     + pcmm_scrssn_count
                     + est_pc_pt_wt_3mo_avg
                     + new_pc_pt_wt_3mo_avg
                     + third_next_avail_3mo_avg
                     + adi_natRnk_avg
                     + avg_age_oct1_2020
                     + prop_male 
                     + prop_white
                     + prop_rural
                     + gap_3mo_avg,
                     data = sta5a_demog_no_missing,
                     method = "optimal",
                     distance = "glm",
                     link = "logit",
                     exact = ~pilot_visn_flag)
#--
opt_matches <- match.data(opt_match)
```

# Propensity Score "Optimal" Matching  
* Using [Optimal Matching](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html#optimal-pair-matching-method-optimal) we get `r nrow(opt_matches) / 2` pairs  
* This means that we are unable to match `r sum(sta5a_demog_no_missing$at_least_10_pc_crh_flag) - sum(opt_matches$at_least_10_pc_crh_flag)` PC CRH sites  
* Model: Treatment (i.e., at least two consecutive months with >9 PC CRH encounters) = 
    + Parent VISN (Exact)
    + Pilot VISN (Yes/No)
    + Census Division
    + NOSOS (3 month average)
    + Observed:Expected PC Panel Size (3 month average)
    + Team PCP/AP FTE (3 month average)
    + Uniques in PCMM (2 quarter average)
    + Established patient wait time (3 month average)
    + New patient wait time (3 month average)
    + Third next available (3 month average)
    + ADI (3 month average)
    + Average age October 1st, 2020
    + Proportion male (Q1, FY20)
    + Proportion white (Q1, FY20)
    + Proportion rural (Q1, FY20)
    + Gap Metric (3 month average)
* We estimate the propensity score with logistic regression (i.e., GLM and logit link) 

```{r}
plot(opt_match, type = "jitter", interactive = FALSE)
```


```{r}
plot(summary(opt_match), position = NULL)
```

# Naive Analysis  

* To "get around" the problem of all CRH sites being engaged at different times, I am choosing outcomes in the first month after our observation period (i.e., January, 2022) 
* For convenience I am using new and established PC patient wait times, and third-next available appointment from the VSSC's PACT Cube

```{r}
vssc_jan_fy22 <- dbGetQuery(oabi_con,
                            "SELECT [sta5a]
      ,[est_pc_pt_wt] as est_pc_pt_wt_jan
      ,[new_pc_pt_wt] as new_pc_pt_wt_jan
      ,[third_next_avail] as third_next_avail_jan
  FROM [OABI_MyVAAccess].[crh_eval].[E2_VSSC_access_metrics]
  where vssc_month = '2022-01-01'")
#--====
opt_matches_df <- opt_matches %>%
  left_join(., vssc_jan_fy22) %>%
  mutate(at_least_10_pc_crh_flag = factor(at_least_10_pc_crh_flag),
         crh_flag = relevel(as.factor(if_else(at_least_10_pc_crh_flag == 1, "CRH", "No CRH")),
                            ref = "No CRH"))
#--
```

## Established patient wait time  
### Un-Matched Analysis  
```{r}
unmatched_df <- sta5a_demog_no_missing %>%
  left_join(., vssc_jan_fy22) %>%
  mutate(at_least_10_pc_crh_flag = factor(at_least_10_pc_crh_flag),
         crh_flag = relevel(as.factor(if_else(at_least_10_pc_crh_flag == 1, "CRH", "No CRH")),
                            ref = "No CRH"))
#--
ggplot(data = unmatched_df,
         aes(x = crh_flag, y = est_pc_pt_wt_jan, fill = crh_flag)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time January, 2022")
#
est_pt_opt_noMatch_res <- lm(est_pc_pt_wt_jan ~ crh_flag,
   data = unmatched_df)
#
summary(est_pt_opt_noMatch_res)
```
  
### Matched Analysis  
```{r}
opt_matches_df %>%
  ggplot(data = .,
         aes(x = crh_flag, y = est_pc_pt_wt_jan, fill = crh_flag)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Established Patient Wait Time January, 2022")
#
est_pt_opt_match_res <- lm(est_pc_pt_wt_jan ~ crh_flag,
   data = opt_matches_df,
   weights = weights)
#
summary(est_pt_opt_match_res)
```

### Sandwich estimator    
```{r}
lmtest::coeftest(est_pt_opt_match_res,
                 vcov. = sandwich::vcovCL(est_pt_opt_match_res),
                 cluster = ~subclass)
```

## New Patient Wait Time  
### Un-Matched Analysis  
```{r}
ggplot(data = unmatched_df,
         aes(x = crh_flag, y = new_pc_pt_wt_jan, fill = crh_flag)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time January, 2022")
#
new_pt_opt_noMatch_res <- lm(new_pc_pt_wt_jan ~ crh_flag,
   data = unmatched_df)
#
summary(new_pt_opt_noMatch_res)
```
  
### Matched Analysis 
```{r}
opt_matches_df %>%
  ggplot(data = .,
         aes(x = crh_flag, y = new_pc_pt_wt_jan, fill = crh_flag)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "New Patient Wait Time January, 2022")
#
new_pt_opt_match_res <- lm(new_pc_pt_wt_jan ~ crh_flag,
                           data = opt_matches_df,
                           weights = weights)
#
summary(new_pt_opt_match_res)
```

### Sandwich estimator  
```{r}
lmtest::coeftest(new_pt_opt_match_res,
                 vcov. = sandwich::vcovCL(new_pt_opt_match_res),
                 cluster = ~subclass)
```

## Third-Next Available   
### Un-Matched Analysis  
```{r}
ggplot(data = unmatched_df,
         aes(x = crh_flag, y = third_next_avail_jan, fill = crh_flag)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Third-Next AVailable Appointment January, 2022")
#
tna_opt_noMatch_res <- lm(third_next_avail_jan ~ crh_flag,
   data = unmatched_df)
#
summary(tna_opt_noMatch_res)
```
  
### Matched Analysis 
```{r}
opt_matches_df %>%
  ggplot(data = .,
         aes(x = crh_flag, y = third_next_avail_jan, fill = crh_flag)) +
  geom_boxplot() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  labs(y = "Third-Next AVailable Appointment January, 2022")
tna_opt_match_res <- lm(third_next_avail_jan ~ crh_flag,
                           data = opt_matches_df,
                           weights = weights)
#
summary(tna_opt_match_res)
```

### Sandwich estimator  
```{r}
lmtest::coeftest(tna_opt_match_res,
                 vcov. = sandwich::vcovCL(tna_opt_match_res),
                 cluster = ~subclass)
```