---
title: "Access Metrics by Rurality of Sta5a"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(lmerTest)
library(sjPlot)
library(cowplot)
library(stargazer)
library(starpolishr)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#--
theme_update(axis.title = element_text(size = 25),
             legend.text = element_text(size = 20))
```


```{r reading-in}
starting_df = dbGetQuery(oabi_con,
                         "select *
                         from [OABI_myVAAccess].[pccrh_eng].Z_analytic_df") %>%
  filter(always_missing_gap == F & always_missing_pf == F) %>%
  mutate(vssc_month = ymd(vssc_month),
         gap_cat = factor(case_when(
           gap_metric < 1.0 ~ "< 1.0",
           gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
           gap_metric > 1.2 ~ "> 1.2",
           TRUE ~ NA
         )),
         pf_cat = factor(case_when(
           panel_fullness > 1.0 ~ "> 100%",
           panel_fullness >= 0.8 & panel_fullness <= 1.0 ~ "80% - 100%",
           panel_fullness < 0.8 ~ "< 80%",
           TRUE ~ NA
         )),
         pf_cat_85 = factor(case_when(
           panel_fullness > 1.05 ~ "> 105%",
           panel_fullness >= 0.85 & panel_fullness <= 1.05 ~ "85% - 105%",
           panel_fullness < 0.85 ~ "< 85%",
           TRUE ~ NA
         )),
         joint_def = fct_drop(factor(
           case_when(panel_fullness > 1.0 | gap_metric < 1.0 ~ 
                       "Worst Group",
                     panel_fullness < 0.8 | gap_metric > 1.2 ~
                       "Best Group",
                     (panel_fullness >= 0.8 & panel_fullness <= 1.0) | 
                       (gap_metric <= 1.2 & gap_metric >= 1.0) ~
                       "Middle Group",
                     TRUE ~ NA)
         )),
         joint_def2 = fct_drop(factor(
           case_when(panel_fullness > 1.05 | gap_metric < 1.0 ~ 
                       "Worst Group",
                     panel_fullness < 0.85 | gap_metric > 1.2 ~
                       "Best Group",
                     (panel_fullness >= 0.85 & panel_fullness <= 1.05) | 
                       (gap_metric <= 1.2 & gap_metric >= 1.0) ~
                       "Middle Group",
                     TRUE ~ NA)
         )),
         period_initiating_crh = relevel(factor(period_initiating_crh,
                                                ordered = FALSE,
                                                levels = c("Before March 2020", 
                                                           "March to September 2020",
                                                           "After September 2020")),
                                         ref = "Before March 2020"))
#============
pen_rate = dbGetQuery(oabi_con,
                      "select a.* 
                      from [OABI_MyVAAccess].[crh_eval].[B1_crh_penRate] as a
                      left join [OABI_MyVAAccess].pccrh_eng.G_crh_flag as b
                      	on a.sta5a = b.sta5a
                      where crh_encounter_count > 9
                      	and a.crh_month >= b.first_mo_w_mt9_pc_crh") %>%
  mutate(this_month_crh = 1,
         vssc_month = ymd(crh_month)) %>%
  select(sta5a, vssc_month, this_month_crh)
#============
tot_crh_fte_visn = starting_df %>%
  group_by(vssc_month, visn) %>%
  summarise(tot_crh_fte = sum(pcp_fte_crh, na.rm = T))
#
tot_crh_fte_nat = starting_df %>%
  group_by(vssc_month) %>%
  summarise(tot_crh_fte = sum(pcp_fte_crh, na.rm = T))
#------------
prop_crh_fte_in_worst_pf = starting_df %>% 
  filter(is.na(pf_cat_85) == F) %>%
  group_by(vssc_month, visn, pf_cat_85) %>%
  summarise(crh_fte_in_group = sum(pcp_fte_crh, na.rm = T)) %>%
  left_join(., tot_crh_fte_visn) %>%
  mutate(prop_crh_fte_in_worst_pf = crh_fte_in_group / tot_crh_fte) %>%
  filter(pf_cat_85 == "> 105%") %>%
  select(vssc_month, visn, prop_crh_fte_in_worst_pf)
#------------
prop_crh_fte_in_worst_gap = starting_df %>% 
  filter(is.na(gap_cat) == F) %>%
  group_by(vssc_month, visn, gap_cat) %>%
  summarise(crh_fte_in_group = sum(pcp_fte_crh, na.rm = T)) %>%
  left_join(., tot_crh_fte_visn) %>%
  mutate(prop_crh_fte_in_worst_gap = crh_fte_in_group / tot_crh_fte) %>%
  filter(gap_cat == "< 1.0") %>%
  select(vssc_month, visn, prop_crh_fte_in_worst_gap)
#------------
prop_crh_fte_in_worst_joint = starting_df %>% 
  filter(is.na(joint_def2) == F) %>%
  group_by(vssc_month, visn, joint_def2) %>%
  summarise(crh_fte_in_group = sum(pcp_fte_crh, na.rm = T)) %>%
  left_join(., tot_crh_fte_visn) %>%
  mutate(prop_crh_fte_in_worst_joint = crh_fte_in_group / tot_crh_fte) %>%
  filter(joint_def2 == "Worst Group") %>%
  select(vssc_month, visn, prop_crh_fte_in_worst_joint)
#============
treated_after_sep2020 <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month),
         treated_month = if_else(crh_encounter_count > 9, 1, 0)) %>%
  filter(vssc_month > ymd("2020-09-01")) %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    ((last_mo_mt9_pc_crh == 1 | is.na(last_mo_mt9_pc_crh)) 
                                     | (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh))),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit_both = meets_inc_crit,
         meets_inc_crit_fwd = if_else(this_mo_mt9_pc_crh == TRUE & (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh)), 1, 0)
  ) %>%
  filter(meets_inc_crit == 1) %>%
  select(sta5a) %>%
  distinct
#=-==========
vast = DBI::dbGetQuery(oabi_con,
                       "select distinct sta5a = stationno, parent_station = par_sta_no, visn = newvisn, city, st, stationname, urh, s_abbr
from [PACT_CC].[Dim].VAST
where extractdate = '8-16-2022'
	AND s_abbr IN('HCC', 'VAMC', 'MSCBOC', 'PCCBOC', 'OOS')
	AND stationname NOT LIKE '%Mobile Clinic%'
	AND stationno IN(select distinct sta6aid from PACT_CC.Dim.VAST_Historic where snapshotDate = '2022-07-01')") %>%
  mutate(visn = str_pad(visn, width = 2, side = "left", pad = "0"),
         urh_vast = if_else(urh %in% c("R", "H", "I"), "Rural", "Urban"))
#------------
analytic_df = starting_df %>%
  left_join(., vast %>%
              select(sta5a, urh_vast)) %>%
  left_join(., pen_rate) %>%
  left_join(., tot_crh_fte_visn) %>%
  left_join(., prop_crh_fte_in_worst_gap) %>%
  left_join(., prop_crh_fte_in_worst_pf) %>%
  left_join(., prop_crh_fte_in_worst_joint) %>%
  mutate(pc_cc_refs_per_1k_tot_pc = replace_na(pc_cc_refs_per_1k_tot_pc, 0),
         joint_def2 = relevel(joint_def2, ref = "Best Group"),
         pf_cat = relevel(pf_cat, ref = "< 80%"),
         gap_cat = relevel(gap_cat, ref = "> 1.2"),
         tc_pc_success_pct = tc_pc_success_prop * 100,
         crh_flag = relevel(factor(crh_flag), ref = "0"),
         scrssn_count_cat = relevel(factor(scrssn_count_cat, ordered = FALSE), ref = "450-2,399"),
         male_pct = prop_male * 100,
         #visn = relevel(factor(visn), ref = "06"),
         cHosp_90d_gt90_pct = cHosp_90d_gt90_prop * 100,
         this_month_crh = replace_na(this_month_crh, 0),
         this_month_crh = relevel(factor(this_month_crh), ref = "0"),
         period_initiating_crh = relevel(factor(
           if_else(is.na(period_initiating_crh), "Never Initiated CRH", period_initiating_crh)),
           ref = "Never Initiated CRH"),
         crh_fte_prop = pcp_fte_crh / tot_crh_fte,
         crh_fte_pct = crh_fte_prop * 100,
         treated_ever = if_else(sta5a %in% treated_after_sep2020$sta5a, 1, 0))
#
est_99 = quantile(analytic_df$est_pt_wt_pid, 0.99, na.rm = T)
new_99 = quantile(analytic_df$new_pt_wt, 0.99, na.rm = T)
tna_99 = quantile(analytic_df$tna, 0.99, na.rm = T)
```

# Established Patient Wait Time    
## Takeaways  

* __Urban__ wait times are generally __longer__
* __Urban__ wait times are __growing longer__ compared to rural sites

```{r}
analytic_df %>%
  filter(fy == 2024
         & est_pt_wt_pid < est_99) %>%
  ggplot(data = .,
         aes(x = urh_vast, y = est_pt_wt_pid, fill = urh_vast)) +
  geom_boxplot() +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "Established Patient Wait Time (days)") +
  facet_wrap(~visn)
```

```{r}
analytic_df %>%
  filter(est_pt_wt_pid < est_99) %>%
ggplot(data = .,
       aes(x = vssc_month, y = est_pt_wt_pid, group = sta5a)) +
  geom_line(alpha = 0.3) +
  geom_smooth(method = "lm",
              aes(group = urh_vast, color = urh_vast)) +
  labs(x = "Month",
       y = "Established Patient Wait Time") +
  theme(legend.title = element_blank())
```

# New Patient Wait Time  
## Takeaways  
* __Urban__ wait times are __longer__
* Both __Rural__ and __Urban__ wait times are __growing__
* __Urban__ wait times are __growing faster__

```{r}
analytic_df %>%
  filter(fy == 2024
         & new_pt_wt < new_99) %>%
  ggplot(data = .,
         aes(x = urh_vast, y = new_pt_wt, fill = urh_vast)) +
  geom_boxplot() +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "New Patient Wait Time (days)") +
  facet_wrap(~visn)
```

```{r}
analytic_df %>%
  filter(new_pt_wt < new_99) %>%
  ggplot(data = .,
       aes(x = vssc_month, y = new_pt_wt, group = sta5a)) +
  geom_line(alpha = 0.3) +
  geom_smooth(method = "lm",
              aes(group = urh_vast, color = urh_vast)) +
  labs(x = "Month",
       y = "New Patient Wait Time") +
  theme(legend.title = element_blank())
```

# Third Next Available    
## Takeaways  
* __Urban__ wait times are __longer__
* __Urban__ wait times are __growing__
* __Rural__ wait times are __decreasing__

```{r}
analytic_df %>%
  filter(fy == 2024
         & tna < tna_99) %>%
  ggplot(data = .,
         aes(x = urh_vast, y = tna, fill = urh_vast)) +
  geom_boxplot() +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "Third Next Available (days)") +
  facet_wrap(~visn)
```

```{r}
analytic_df %>%
  filter(tna < tna_99) %>%
  ggplot(data = .,
       aes(x = vssc_month, y = tna, group = sta5a)) +
  geom_line(alpha = 0.3) +
  geom_smooth(method = "lm",
              aes(group = urh_vast, color = urh_vast)) +
  labs(x = "Month",
       y = "Third Next Available") +
  theme(legend.title = element_blank())
```

# Gap Metric      
## Takeaways  
* __Rural__ sites have a __higher__ gap metric than __Urban__ sites
* The gap metric has __decreased__ over time


```{r}
analytic_df %>%
  filter(fy == 2024
         & gap_metric < 3) %>%
  ggplot(data = .,
         aes(x = urh_vast, y = gap_metric, fill = urh_vast)) +
  geom_boxplot() +
  geom_hline(yintercept = 1,
             lty = 3) +
  theme(legend.title = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank()) +
  labs(y = "Gap Metric") +
  facet_wrap(~visn)
```

```{r}
analytic_df %>%
  filter(gap_metric < 3) %>%
  ggplot(data = .,
       aes(x = vssc_month, y = gap_metric, group = sta5a)) +
  geom_hline(yintercept = 1,
             lty = 3) +
  geom_line(alpha = 0.3) +
  geom_smooth(method = "lm",
              aes(group = urh_vast, color = urh_vast)) +
  labs(x = "Month",
       y = "Gap Metric") +
  theme(legend.title = element_blank())
```