---
title: "Pre-COVID Analysis: Contrasting 3 models"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_noCRH_among_controls.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(vssc_month = seq.Date(ymd("2018-10-01"), ymd("2020-02-01"), "1 month")) %>%
  rowid_to_column(., var = "time") %>%
  mutate(time2 = time - 13)
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>% 
  filter(sta5a %in% crh_sta5as) %>%
  select(subclass) %>%
  inner_join(., ps_matched) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
analytic_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df$treat <- relevel(analytic_df$treat, ref = 'Control')
```

```{r}
#propensity score matched sta5as if being used
ps_matched2 <- read_csv(here("Input","Data", "ps_matched_sta5as_v5.csv"))
#
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include2 <- ps_matched2 %>% 
  filter(sta5a %in% crh_sta5as) %>%
  select(subclass) %>%
  inner_join(., ps_matched2) %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df2 <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include2) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
analytic_df2$post <- relevel(analytic_df2$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df2$treat <- relevel(analytic_df2$treat, ref = 'Control')
```


# Front Matter  

## Description of this report  

* This is a comparison of 3 pre-COVID analyses: the original analysis and two sensitivity analyses

## Decision Points  

* Per our discussion on 5/4 I have generated a document to contrast the three pre-COVID analyses we have been discussing:
    + The original analysis with two 2-way interactions
    + A restricted analysis with two 2-way interactions
    + A restricted analysis with a 3-way interaction
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + There are two analytic datasets 
    + The original dataset has `r analytic_df2 %>% select(sta5a) %>% n_distinct` sta5as
        + I am not sure where or when I lost 6 sta5as
    + The restricted dataset has `r analytic_df %>% select(sta5a) %>% n_distinct` sta5as
    
* Description of _Propensity Score_ matching
    + This report uses two varieties of __Propensity Score v5.0__
    + The original PS model v5.0 consists of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact
    + The restricted version restricts the pool of potential controls to those sta5as that have never had a PC CRH encounter


# Established Patient Wait Time, 3-Ways  

```{r}
bline_trend_est <- lmer(est_pc_pt_wt ~ treat * post    
                     + time2 * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df2,
                     REML = TRUE)
#
bline_trend_est2 <- lmer(est_pc_pt_wt ~ treat * post    
                     + time2 * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
bline_trend_est3 <- lmer(est_pc_pt_wt ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
```

```{r}
est1_pred <- ggeffects::ggpredict(bline_trend_est,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Original")
#
est2_pred <- ggeffects::ggpredict(bline_trend_est2,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Restricted")
#
est3_pred <- ggeffects::ggpredict(bline_trend_est3,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Restricted, 3-way")
#--
pred_est <- est1_pred %>%
  bind_rows(., est2_pred) %>%
  bind_rows(., est3_pred)
#--
ggplot(data = pred_est,
         aes(x = vssc_month, y = predicted, group = facet, color = facet)) +
  geom_line(data = subset(pred_est, vssc_month < ymd("2019-10-01") & group == "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  geom_line(data = subset(pred_est, vssc_month > ymd("2019-09-01") & group != "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title = element_blank()) +
  labs(y = "Predicted Value") +
  facet_wrap(~analysis)
```

```{r}
tab_model(bline_trend_est, bline_trend_est2, bline_trend_est3,
          dv.labels = c("Original", "Restricted", "Restricted, 3-way"),
          show.se = TRUE,
          show.ci = FALSE)
```


# New Patient Wait Time, 3-Ways  

```{r}
bline_trend_new <- lmer(new_pc_pt_wt ~ treat * post    
                     + time2 * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df2,
                     REML = TRUE)
#
bline_trend_new2 <- lmer(new_pc_pt_wt ~ treat * post    
                     + time2 * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
bline_trend_new3 <- lmer(new_pc_pt_wt ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
```

```{r}
new1_pred <- ggeffects::ggpredict(bline_trend_new,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Original")
#
new2_pred <- ggeffects::ggpredict(bline_trend_new2,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Restricted")
#
new3_pred <- ggeffects::ggpredict(bline_trend_new3,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Restricted, 3-way")
#--
pred_new <- new1_pred %>%
  bind_rows(., new2_pred) %>%
  bind_rows(., new3_pred)
#--
ggplot(data = pred_new,
         aes(x = vssc_month, y = predicted, group = facet, color = facet)) +
  geom_line(data = subset(pred_new, vssc_month < ymd("2019-10-01") & group == "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  geom_line(data = subset(pred_new, vssc_month > ymd("2019-09-01") & group != "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title = element_blank()) +
  labs(y = "Predicted Value") +
  facet_wrap(~analysis)
```

```{r}
tab_model(bline_trend_new, bline_trend_new2, bline_trend_new3,
          dv.labels = c("Original", "Restricted", "Restricted, 3-way"),
          show.se = TRUE,
          show.ci = FALSE)
```

# Third Next Available, 3-Ways  

```{r}
bline_trend_tna <- lmer(third_next_avail ~ treat * post    
                     + time2 * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df2,
                     REML = TRUE)
#
bline_trend_tna2 <- lmer(third_next_avail ~ treat * post    
                     + time2 * treat 
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
bline_trend_tna3 <- lmer(third_next_avail ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
```

```{r}
tna1_pred <- ggeffects::ggpredict(bline_trend_tna,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Original")
#
tna2_pred <- ggeffects::ggpredict(bline_trend_tna2,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Restricted")
#
tna3_pred <- ggeffects::ggpredict(bline_trend_tna3,
                                  terms = c("time2 [-12:5]", "post", "treat")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2")) %>%
  mutate(analysis = "Restricted, 3-way")
#--
pred_tna <- tna1_pred %>%
  bind_rows(., tna2_pred) %>%
  bind_rows(., tna3_pred)
#--
ggplot(data = pred_tna,
         aes(x = vssc_month, y = predicted, group = facet, color = facet)) +
  geom_line(data = subset(pred_tna, vssc_month < ymd("2019-10-01") & group == "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  geom_line(data = subset(pred_tna, vssc_month > ymd("2019-09-01") & group != "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "bottom",
        axis.title = element_blank()) +
  labs(y = "Predicted Value") +
  facet_wrap(~analysis)
```

```{r}
tab_model(bline_trend_tna, bline_trend_tna2, bline_trend_tna3,
          dv.labels = c("Original", "Restricted", "Restricted, 3-way"),
          show.se = TRUE,
          show.ci = FALSE)
```