---
title: "PC CRH - Pre-COVID Analysis"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_1_noCRH_among_controls.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(vssc_month = seq.Date(ymd("2018-10-01"), ymd("2020-02-01"), "1 month")) %>%
  rowid_to_column(., var = "time") %>%
  mutate(time2 = time - 12)
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#
analytic_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df$treat <- relevel(analytic_df$treat, ref = 'Control')
```

# Front Matter  

## Description of this report  

* This is an abbreviated description of the three pre-COVID analyses

## Decision Points  

* Per our discussion on Wednesday (5/3) this is a sensitivity analysis of PC CRH data, pre-COVID, with a triple interaction between $\text{time}$, $\text{treat}$, and $\text{post}$
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This report uses a variation of __Propensity Score v5.1__
    + PS model v5.1 consists of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Removed ADI and NOSOS
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact
    + __This version restricted the pool of potential controls to those sta5as that have never had a PC CRH encounter__

* Description of analyses  
    + This analysis is a Comparative Interrupted Time Series with covariates
    + We will use a mixed-effects model __with REML__ 
    + We will allow random intercepts for sta5a
    + On the LHS of the model we have New Patient Wait Time, Established Patient Wait Time, and Third Next Available 
    + In addition to the various combinations of _treat_, _time_, and _post_, all models have the following covariates:
        + Observed:Expected PC Panel Size 
        + Proportion male 
        + Proportion rural 

## Covariate description  

```{r}
analytic_df %>% 
  select(obs_exp_panel_ratio, pct_male, pct_rural) %>%
  rownames_to_column() %>%
  pivot_longer(-rowname) %>%
  group_by(name) %>%
  summarise(mean_val = mean(value, na.rm = T),
            med_val = median(value, na.rm = T),
            sd_val = sd(value, na.rm = T),
            qtl_25 = quantile(value, probs = 0.25, na.rm = T),
            qtl_75 = quantile(value, probs = 0.75, na.rm = T)) %>%
  mutate(
    name2 = case_when(
      name == "obs_exp_panel_ratio" ~ "Obs:Exp",
      name == "pct_male" ~ "% male",
      name == "pct_rural" ~ "% rural"),
    mean_val2 = if_else(name == "obs_exp_panel_ratio",
                          paste0(round(mean_val, 2), " (", round(sd_val, 2), ")"),
                        paste0(percent(mean_val / 100, accuracy = 0.1), 
                               " (", round(sd_val, 1), ")")),
    med_val2 = if_else(name == "obs_exp_panel_ratio",
                       as.character(round(med_val, 2)),
                       percent(med_val / 100, accuracy = 0.1)),
    qtls = if_else(name == "obs_exp_panel_ratio",
                   paste0(round(qtl_25, 2), ", ", round(qtl_75, 2)),
                   paste0(round(qtl_25, 1), "%, ", round(qtl_75, 1), "%"))) %>%
  select(7:10) %>%
  kbl(col.names = c("", "Mean (SD)", "Median", "25th, 75th %-iles"),
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped", full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
plot_fxn <- function(outcome, outcome_c){
  ylab <- if(outcome_c == "est_pc_pt_wt"){
    "Established Patient Wait Time (days)"
  }
  else if(outcome_c == "new_pc_pt_wt"){
    "New Patient Wait Time (days)"
  }
  else{
    "Third Next Available (days)"
  }

  ggplot(data = analytic_df,
         aes(x = vssc_month, y = {{outcome}}, group = sta5a)) +
    geom_smooth(linewidth = 1.25, data = subset(analytic_df, vssc_month < ymd("2019-10-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    geom_smooth(linewidth = 1.25, data = subset(analytic_df, vssc_month > ymd("2019-09-01")),
                aes(x = vssc_month, y = {{outcome}}, group = treat, color = treat),
                inherit.aes = F,
                method = lm, se = F) +
    ggthemes::scale_color_colorblind() +
    theme(axis.title.x = element_blank()) +
    labs(y = ylab) +
    scale_y_continuous(limits = c(0, NA))
}
#
```

# Baseline Linear Trend  

* This model includes _time_ (i.e., months) as well as an interaction between _time_ and _treat_, an interaction between _treat_ and _post_, as well as a 3-way interaction between _time_, _treat_, and _post_:

$$Y_{jt}=\beta_{0} +\beta_1Z_{jt}+ \beta_{2}time_{t} +  \beta_{3}post_{t}+\beta_{4}treat_{j}+\beta_{5}time_{t}treat_{j}+\beta_{6}post_{t}treat_{j} + \beta_{7}time_{t}post_{t}treat_{j} +v_{j}+u_{jt}$$

# Dates  
```{r}
dates
```

# Established Patient Wait Time  

## Trend Over Time: PC CRH vs. no PC CRH  


```{r}
bline_trend1 <- lmer(est_pc_pt_wt ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_1 <- ggeffects::ggpredict(bline_trend1, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2"))
#--
ggplot(data = pred_1,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_1, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  geom_line(data = subset(pred_1, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "right",
        axis.title = element_blank()) +
  labs("Predicted Value")
```

#### Bootstrapped Confidence Intervals  
```{r}
confint(bline_trend1, method = "boot", oldNames = F, nsim = 500)
```


#### Model Estimates    
```{r}
tab_model(bline_trend1,
          dv.labels = c("Established Patient Wait Time"))
```

# New Patient Wait Time  

## Trend Over Time: PC CRH vs. no PC CRH  



```{r}
bline_trend2 <- lmer(new_pc_pt_wt ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_2 <- ggeffects::ggpredict(bline_trend2, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2"))
#--
ggplot(data = pred_2,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_2, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  geom_line(data = subset(pred_2, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  scale_y_continuous(limits = c(0, NA)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "right",
        axis.title = element_blank()) +
  labs("Predicted Value")
```

#### Bootstrapped Confidence Intervals  
```{r}
confint(bline_trend2, method = "boot", oldNames = F, nsim = 500)
```

#### Model Estimates    
```{r}
tab_model(bline_trend2,
          dv.labels = c("New Patient Wait Time"))
```

# Third Next Available    

## Trend Over Time: PC CRH vs. no PC CRH  



```{r}
bline_trend3 <- lmer(third_next_avail ~ treat * post * time2  
                     + obs_exp_panel_ratio
                     + pct_male
                     + pct_rural
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
pred_3 <- ggeffects::ggpredict(bline_trend3, terms = c("time2 [-12:5]", "treat", "post")) %>%
  tibble() %>%
  left_join(., dates, by = c("x" = "time2"))
#--
ggplot(data = pred_3,
       aes(x = vssc_month, y = predicted, group = group, color = group)) +
  geom_line(data = subset(pred_3, vssc_month < ymd("2019-10-01") & facet == "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  geom_line(data = subset(pred_3, vssc_month > ymd("2019-09-01") & facet != "Pre-Intervention (i.e., FY19)"),
            size = 1) +
  scale_y_continuous(limits = c(0, 15)) +
  ggthemes::scale_color_colorblind() +
  theme(legend.position = "right",
        axis.title = element_blank()) +
  labs("Predicted Value")
```

#### Bootstrapped Confidence Intervals  
```{r}
confint(bline_trend3, method = "boot", oldNames = F, nsim = 500)
```

#### Model Estimates    
```{r}
tab_model(bline_trend3,
          dv.labels = c("Third Next Available"))
```


# All Together  

```{r}
tab_model(bline_trend1, bline_trend2, bline_trend3,
          dv.labels = c("Established Pt WT", "New Pt WT", "3rd Next Available"),
          show.se = TRUE)
```