---
title: "Post-COVID PC CRH Analysis"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             plot.title = element_text(size = 24),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0),
         s_abbr2 = case_when(str_detect(s_abbr, "CBOC") ~ "CBOC",
                             str_detect(s_abbr, "VAMC|HCC") ~ "VAMC/HCC",
                             s_abbr == "OOS" ~ "OOS")) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well as 
  #flags for treated/control
  #PS matching weights
  #flags for meeting inclusion criteria in 3 periods
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv")) %>%
  rename(treated_ever = treated_num)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(tna_new_source = as.numeric(tna_new_source))
#making a time/date dataset
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time") %>%
  mutate(fy = if_else(month(vssc_month) > 9, year(vssc_month) + 1, year(vssc_month)),
         qtr = case_when(month(vssc_month) %in% c(10, 11, 12) ~ 1,
                         month(vssc_month) %in% c(1, 2, 3) ~ 2,
                         month(vssc_month) %in% c(4, 5, 6) ~ 3,
                         month(vssc_month) %in% c(7, 8, 9) ~ 4,
                         TRUE ~ 99))
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
#average age on october 1st 2022
age_sta5a_qtr <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].D1_age_sta5a_qtr")
#sta5a-fy-specific counts of gender, race, and urh, as well as total uniques
race_gender_urh <- dbGetQuery(oabi_con,
                              "select * from [OABI_MyVAAccess].[crh_eval].D2_race_gender_urh_count") %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100)
#sta5a-fy_qtr-specific average ADI and quartile counts, as well as total
adi_sta5a_fy <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].D3_adi_sta5a_fy")
#sta5a-month-specific average Nosos, Obs:Exp, and Team PCP/AP FTE
nosos_obs_exp_team_fte <- dbGetQuery(oabi_con,
                                     "select * from [OABI_MyVAAccess].[crh_eval].F1_2_vssc_covars") %>%
  mutate(vssc_month = ymd(vssc_month))
#sta5a-fy-specific average drive distance and time to closest PC site
drive_time <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].D4_avg_drive_time")
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#sta5a-month-specific timely care success rate
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#sta5a-month-specific PC CRH penetration rate and it's components
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month),
         treated_month = if_else(crh_encounter_count > 9, 1, 0))#time-varying treated
```

```{r time_varying_treated}
treated_sta5a <- ps_matched %>%
  filter(treated_ever == 1) %>%
  select(sta5a)
#
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    ((last_mo_mt9_pc_crh == 1 | is.na(last_mo_mt9_pc_crh)) 
                                     | (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh))),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit_both = meets_inc_crit,
         meets_inc_crit_fwd = if_else(this_mo_mt9_pc_crh == TRUE & (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh)), 1, 0)
         ) %>%
  filter(sta5a %in% treated_sta5a$sta5a) %>%
  right_join(., dates %>%
               select(vssc_month) %>%
               cross_join(., treated_sta5a)) %>%
  mutate(meets_inc_crit_both = replace_na(meets_inc_crit_both, 0),
         meets_inc_crit_fwd = replace_na(meets_inc_crit_fwd, 0),
         crh_enc_count_na = crh_encounter_count,
         crh_encounter_count = replace_na(crh_encounter_count, 0))
```

```{r}
#making the analytic dataset
analytic_df_match <- ps_matched %>%
  select(sta5a, treated, treated_ever, weights, starts_with("period")) %>%
  mutate(period_flag = case_when(period1_inc == 1 ~ "Period 1",
                                 period1_inc == 0 & period2_inc == 1 ~ "Period 2",
                                 TRUE ~ "Period 3")) %>%
  cross_join(., dates) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source, new_0_20_days_create, panel_fullness)) %>%
  left_join(., adi_sta5a_fy %>%
              select(sta5a = Sta5a, fy, adi_natRnk_avg)) %>%
  left_join(., age_sta5a_qtr %>%
              select(sta5a = Sta5a, fy = FY, qtr = QTR, avg_age_oct1_2022)) %>%
  left_join(., drive_time %>%
              select(sta5a = CLOSESTPCSITE, fy, avg_driveTime) %>%
              bind_rows(., drive_time %>%
                          filter(fy == 2022) %>%
                          select(sta5a = CLOSESTPCSITE, fy, avg_driveTime) %>%
                          mutate(fy = 2023))) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  left_join(., nosos_obs_exp_team_fte) %>%
  left_join(., race_gender_urh %>%
              select(sta5a = Sta5a, fy = FY, pct_male, pct_white, pct_rural)) %>%
  left_join(., vast %>%
              select(sta5a, s_abbr, s_abbr2, parent_visn)) %>%
  left_join(., pen_rate) %>%
  left_join(., scrssn_count) %>%
  mutate(treated_ever = relevel(as.factor(treated_ever), ref = "0"),
         new_0_20_days_create_pct = new_0_20_days_create * 100,
         treated = relevel(as.factor(treated), ref = "Control"),
         treated_month = relevel(as.factor(replace_na(treated_month, 0)), ref = "0"),
         tc_pc_success_pct = tc_pc_success_prop * 100,
         time_t = time,
         gap_metric_cat = factor(case_when(gap_metric >= 1.2 ~ "> 1.2",
                                    gap_metric < 1 ~ "< 1.0",
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ "1.0-1.2")),
         gap_metric_num = case_when(gap_metric >= 1.2 ~ 3,
                                    gap_metric < 1 ~ 1,
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ 2),
         new_0_20_binary_success = if_else(new_0_20_days_create_pct >= 80, 1, 0),
         panel_fullness_pct = panel_fullness * 100,
         panel_fullness_cat = factor(case_when(panel_fullness_pct < 80 ~ "<80%",
                                        panel_fullness_pct > 105 ~ ">105%",
                                        panel_fullness_pct >= 80 & panel_fullness_pct <= 105 ~ "80-105%")))
#--
analytic_panel_match <- analytic_df_match %>%
  panelr::panel_data(.,
                     id = sta5a,
                     wave = time)
```


```{r unmatched_analytic_df}
treated_after_sep2020 <- pen_rate %>%
  filter(vssc_month > ymd("2020-09-01")) %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    ((last_mo_mt9_pc_crh == 1 | is.na(last_mo_mt9_pc_crh)) 
                                     | (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh))),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit_both = meets_inc_crit,
         meets_inc_crit_fwd = if_else(this_mo_mt9_pc_crh == TRUE & (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh)), 1, 0)
  ) %>%
  filter(meets_inc_crit == 1) %>%
  select(sta5a) %>%
  distinct
#--
analytic_df_noMatch <- vast %>%
  filter(str_detect(s_abbr, "CBOC|VAMC|HCC|OOS") == T) %>%
  select(sta5a) %>%
  inner_join(., scrssn_count %>%
               filter(is.na(scrssn_count_cat) == F
                      & scrssn_count_cat != "< 450") %>%
               select(sta5a)) %>%
  mutate(treated_ever = if_else(sta5a %in% treated_after_sep2020$sta5a, 1, 0)) %>%
  cross_join(., dates) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source, new_0_20_days_create, panel_fullness)) %>%
  left_join(., adi_sta5a_fy %>%
              select(sta5a = Sta5a, fy, adi_natRnk_avg)) %>%
  left_join(., age_sta5a_qtr %>%
              select(sta5a = Sta5a, fy = FY, qtr = QTR, avg_age_oct1_2022)) %>%
  left_join(., drive_time %>%
              select(sta5a = CLOSESTPCSITE, fy, avg_driveTime) %>%
              bind_rows(., drive_time %>%
                          filter(fy == 2022) %>%
                          select(sta5a = CLOSESTPCSITE, fy, avg_driveTime) %>%
                          mutate(fy = 2023))) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  left_join(., nosos_obs_exp_team_fte) %>%
  left_join(., race_gender_urh %>%
              select(sta5a = Sta5a, fy = FY, pct_male, pct_white, pct_rural)) %>%
  left_join(., vast %>%
              select(sta5a, s_abbr, s_abbr2, parent_visn)) %>%
  left_join(., pen_rate) %>%
  left_join(., scrssn_count) %>%
  mutate(treated_ever = relevel(as.factor(treated_ever), ref = "0"),
         new_0_20_days_create_pct = new_0_20_days_create * 100,
         #treated = relevel(as.factor(treated), ref = "Control"),
         treated_month = relevel(as.factor(replace_na(treated_month, 0)), ref = "0"),
         tc_pc_success_pct = tc_pc_success_prop * 100,
         time_t = time,
         gap_metric_cat = factor(case_when(gap_metric >= 1.2 ~ "> 1.2",
                                    gap_metric < 1 ~ "< 1.0",
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ "1.0-1.2")),
         gap_metric_num = case_when(gap_metric >= 1.2 ~ 3,
                                    gap_metric < 1 ~ 1,
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ 2),
         new_0_20_binary_success = if_else(new_0_20_days_create_pct >= 80, 1, 0),
         panel_fullness_pct = panel_fullness * 100,
         panel_fullness_cat = factor(case_when(panel_fullness_pct < 80 ~ "<80%",
                                        panel_fullness_pct > 105 ~ ">105%",
                                        panel_fullness_pct >= 80 & panel_fullness_pct <= 105 ~ "80-105%")),
         gap_lt_1 = if_else(gap_metric_cat == "< 1.0", 1, 0),
         gap_1_12 = if_else(gap_metric_cat == "1.0-1.2", 1, 0),
         gap_gt_12 = if_else(gap_metric_cat == "> 1.2", 1, 0),
         scrssn_450_2399 = if_else(scrssn_count_cat == "450 - 2,399", 1, 0),
         scrssn_2400_9999 = if_else(scrssn_count_cat == "2,400 - 9,999", 1, 0),
         scrssn_ge_10k = if_else(scrssn_count_cat == "10,000+", 1, 0)) %>%
  fastDummies::dummy_cols(., select_columns = c("parent_visn", "s_abbr"))
#--
analytic_panel_noMatch <- analytic_df_noMatch %>%
  panelr::panel_data(.,
                     id = sta5a,
                     wave = time)
```




# Front Matter  

## Description of this report  

* This report is a comparison of out GLMM models vs. W-B models using the matched and un-matched datasets


    
## Analytic details  

    
* Description of the __unmatched__ cohort 
    + The first observation in the data occurs on `r min(analytic_df_noMatch$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df_noMatch$vssc_month)`
    + There are `r nrow(analytic_df_noMatch) %>% comma()` rows in the data
    + These rows come from `r analytic_df_noMatch %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df_noMatch %>% select(sta5a, treated_ever) %>% distinct() %>% summarise(tot = sum(if_else(treated_ever == "1", 1, 0)))` of these met our criteria for PC CRH 
      + `r analytic_df_noMatch %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df_noMatch %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df_noMatch %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of the __matched__ cohort 
    + The first observation in the data occurs on `r min(analytic_df_match$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df_match$vssc_month)`
    + There are `r nrow(analytic_df_match) %>% comma()` rows in the data
    + These rows come from `r analytic_df_match %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df_match %>% select(sta5a, treated_ever) %>% distinct() %>% summarise(tot = sum(if_else(treated_ever == "1", 1, 0)))` of these met our criteria for PC CRH 
      + `r analytic_df_match %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df_match %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df_match %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
 

```{r set_ref_levs2, class.source = 'fold-show'}
analytic_df_noMatch$panel_fullness_cat <- relevel(analytic_df_noMatch$panel_fullness_cat, ref = ">105%")
analytic_df_noMatch$treated_month <- relevel(analytic_df_noMatch$treated_month, ref = "0")
analytic_df_noMatch$gap_metric_cat <- relevel(analytic_df_noMatch$gap_metric_cat, ref = "< 1.0")
analytic_df_noMatch$scrssn_count_cat <- relevel(factor(analytic_df_noMatch$scrssn_count_cat, ordered = F), ref = "450 - 2,399")
analytic_df_noMatch$new_0_20_binary_success <- relevel(factor(analytic_df_noMatch$new_0_20_binary_success, ordered = F), ref = "0")
analytic_df_noMatch$treated_ever <- relevel(factor(analytic_df_noMatch$treated_ever, ordered = F), ref = "0")
analytic_df_noMatch$s_abbr2 <- relevel(factor(analytic_df_noMatch$s_abbr2, ordered = F), ref = "CBOC")
#--
analytic_df_match$panel_fullness_cat <- relevel(analytic_df_match$panel_fullness_cat, ref = ">105%")
analytic_df_match$treated_month <- relevel(analytic_df_match$treated_month, ref = "0")
analytic_df_match$gap_metric_cat <- relevel(analytic_df_match$gap_metric_cat, ref = "< 1.0")
analytic_df_match$scrssn_count_cat <- relevel(factor(analytic_df_match$scrssn_count_cat, ordered = F), ref = "450 - 2,399")
analytic_df_match$new_0_20_binary_success <- relevel(factor(analytic_df_match$new_0_20_binary_success, ordered = F), ref = "0")
analytic_df_match$treated_ever <- relevel(factor(analytic_df_match$treated_ever, ordered = F), ref = "0")
analytic_df_match$s_abbr2 <- relevel(factor(analytic_df_match$s_abbr2, ordered = F), ref = "CBOC")
#--
analytic_panel_noMatch$panel_fullness_cat <- relevel(analytic_panel_noMatch$panel_fullness_cat, ref = ">105%")
analytic_panel_noMatch$treated_month <- relevel(analytic_panel_noMatch$treated_month, ref = "0")
analytic_panel_noMatch$gap_metric_cat <- relevel(analytic_panel_noMatch$gap_metric_cat, ref = "< 1.0")
analytic_panel_noMatch$scrssn_count_cat <- relevel(factor(analytic_panel_noMatch$scrssn_count_cat, ordered = F), ref = "450 - 2,399")
analytic_panel_noMatch$new_0_20_binary_success <- relevel(factor(analytic_panel_noMatch$new_0_20_binary_success, ordered = F), ref = "0")
analytic_panel_noMatch$treated_ever <- relevel(factor(analytic_panel_noMatch$treated_ever, ordered = F), ref = "0")
analytic_panel_noMatch$s_abbr2 <- relevel(factor(analytic_panel_noMatch$s_abbr2, ordered = F), ref = "CBOC")
#--
analytic_panel_match$panel_fullness_cat <- relevel(analytic_panel_match$panel_fullness_cat, ref = ">105%")
analytic_panel_match$treated_month <- relevel(analytic_panel_match$treated_month, ref = "0")
analytic_panel_match$gap_metric_cat <- relevel(analytic_panel_match$gap_metric_cat, ref = "< 1.0")
analytic_panel_match$scrssn_count_cat <- relevel(factor(analytic_panel_match$scrssn_count_cat, ordered = F), ref = "450 - 2,399")
analytic_panel_match$new_0_20_binary_success <- relevel(factor(analytic_panel_match$new_0_20_binary_success, ordered = F), ref = "0")
analytic_panel_match$treated_ever <- relevel(factor(analytic_panel_match$treated_ever, ordered = F), ref = "0")
analytic_panel_match$s_abbr2 <- relevel(factor(analytic_panel_match$s_abbr2, ordered = F), ref = "CBOC")
```


```{r}
contrast_fxn <- function(outcome){
  wb_fmla <- as.formula(paste0(outcome, " ~ treated_month + time_t ", 
                               "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                               "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + scrssn_count_cat", 
                               "| treated_ever", 
                               "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                               "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + s_abbr2 + scrssn_count_cat + parent_visn", 
                               " | (1|sta5a)"))
  glm_fmla <- as.formula(paste0(outcome, " ~ treated_month + treated_ever + time_t ", 
                                "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score ",
                                "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + scrssn_count_cat",
                                "+ s_abbr2 + parent_visn + (1|sta5a)"))
  #
  wb_mod_noMatch <- panelr::wbm(wb_fmla,
                                data = analytic_panel_noMatch)
  wb_noMatch_summ <- summary(wb_mod_noMatch,
                             digits = 3)
  #-
  wb_mod_match <- panelr::wbm(wb_fmla,
                              data = analytic_panel_match,
                              weights = weights)
  wb_match_summ <- summary(wb_mod_match,
                           digits = 3)
  #--
  glm_mod_noMatch <- lmerTest::lmer(glm_fmla,
                                    data = analytic_df_noMatch)
  glm_noMatch_summ <- summary(glm_mod_noMatch)
  #--
  glm_mod_match <- lmerTest::lmer(glm_fmla,
                                  data = analytic_df_match,
                                  weights = weights)
  glm_match_summ <- summary(glm_mod_match)
  #
  aic_bic_table <- tibble(col_1 = c("AIC", "BIC"),
                          col_glm_noMatch = c(comma(AIC(glm_mod_noMatch), accuracy = 0.1), comma(BIC(glm_mod_noMatch), accuracy = 0.1)),
                          col_wbm_noMatch = c(comma(AIC(wb_mod_noMatch), accuracy = 0.1), comma(BIC(wb_mod_noMatch), accuracy = 0.1)),
                          col_glm_match = c(comma(AIC(glm_mod_match), accuracy = 0.1), comma(BIC(glm_mod_match), accuracy = 0.1)),
                          col_wbm_match = c(comma(AIC(wb_mod_match), accuracy = 0.1), comma(BIC(wb_mod_match), accuracy = 0.1))) %>%
    kbl(col.names = c("", "GLMM", "WBM", "GLMM", "WBM"),
        align = c("l", rep("r", 4))) %>%
    kable_classic("striped",
                  full_width = F) %>%
    row_spec(0, bold = T) %>%
    column_spec(1, bold = TRUE) %>%
    column_spec(3, border_right = TRUE) %>%
    add_header_above(c("", "No Match" = 2, "Matched" = 2),
                     bold = TRUE)
  #--
  contrast_table <- glm_noMatch_summ$coefficients %>% 
    as.data.frame() %>% 
    rownames_to_column() %>% 
    select(rowname) %>%
    bind_rows(., wb_noMatch_summ$between_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname) %>%
                mutate(rowname = if_else(str_detect(rowname, "treated_e|s_abbr"), str_c(rowname, "between", sep = "_"), rowname))) %>%
    bind_rows(., wb_noMatch_summ$within_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname)) %>%
    distinct %>%
    left_join(., glm_noMatch_summ$coefficients %>%
                as.data.frame() %>%
                rownames_to_column() %>%
                select(rowname, Estimate, "Pr(>|t|)")) %>%
    left_join(., wb_noMatch_summ$within_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname, Est., p) %>%
                bind_rows(., wb_noMatch_summ$between_table %>% 
                            as.data.frame() %>% 
                            rownames_to_column() %>% 
                            select(rowname, Est., p) %>%
                            mutate(rowname = if_else(str_detect(rowname, "treated_e|s_abbr"), 
                                                     str_c(rowname, "between", sep = "_"), rowname))),
              by = "rowname") %>%
    left_join(., glm_match_summ$coefficients %>%
                as.data.frame() %>%
                rownames_to_column() %>%
                select(rowname, Estimate, "Pr(>|t|)"),
              by = "rowname") %>%
    left_join(., wb_match_summ$within_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname, Est., p) %>%
                bind_rows(., wb_match_summ$between_table %>% 
                            as.data.frame() %>% 
                            rownames_to_column() %>% 
                            select(rowname, Est., p) %>%
                            mutate(rowname = if_else(str_detect(rowname, "treated_e|s_abbr"), 
                                                     str_c(rowname, "between", sep = "_"), rowname))),
              by = "rowname") %>%
    mutate(across(contains("Est"), ~comma(.x, accuracy = 0.01)),
           across(contains("p"), ~comma(.x, accuracy = 0.01)),
           across(contains("p"), ~if_else(as.numeric(.x) < 0.05, 
                         cell_spec(.x, background = "skyblue"), cell_spec(.x, background = "white")))) %>%
    kbl(col.names = c("", rep(c("Estimate", "p"), 4)),
        align = c("l", rep("r", 8)),
        escape = F) %>%
    column_spec(5, border_right = TRUE) %>%
    kable_classic("striped") %>%
    add_header_above(c("", "GLMM, No Match" = 2, "WBM, No Match" = 2, "GLMM, Matched" = 2, "WBM, Matched" = 2),
                     bold = TRUE)
  #--
  return(list(slot_1 = aic_bic_table, slot_2 = contrast_table))
}
```

# Established Patient Wait Time  

```{r}
est_list <- contrast_fxn("est_pc_pt_wt_pid")
#
est_list$slot_1
#
est_list$slot_2
```

# New Patient Wait Time  

```{r}
new_list <- contrast_fxn("new_pc_pt_wt_create")
#
new_list$slot_1
#
new_list$slot_2
```

# Third Next Available  

```{r}
tna_list <- contrast_fxn("tna_new_source")
#
tna_list$slot_1
#
tna_list$slot_2
```

# Timely Care  

```{r}
timely_list <- contrast_fxn("tc_pc_success_pct")
#
timely_list$slot_1
#
timely_list$slot_2
```

```{r}
tictoc::tic()
contrast_bin_fxn <- function(outcome){
  wb_fmla <- as.formula(paste0(outcome, " ~ treated_month + time_t ", 
                               "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                               "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + scrssn_count_cat", 
                               "| treated_ever", 
                               "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                               "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + s_abbr2 + scrssn_count_cat + parent_visn", 
                               " | (1|sta5a)"))
  glm_fmla <- as.formula(paste0(outcome, " ~ treated_month + treated_ever + time_t ", 
                                "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score ",
                                "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + scrssn_count_cat",
                                "+ s_abbr2 + parent_visn + (1|sta5a)"))
  #
  wb_mod_noMatch <- panelr::wbm(wb_fmla,
                                data = analytic_panel_noMatch, 
                                family = "binomial",
                                pvals = T,
                                pR2 = F,
                                control = glmerControl(calc.derivs = FALSE))
  wb_noMatch_summ <- summary(wb_mod_noMatch,
                             digits = 3)
  #-
  wb_mod_match <- panelr::wbm(wb_fmla,
                              data = analytic_panel_match,
                              weights = weights, 
                              family = "binomial",
                              pvals = T,
                              pR2 = F,
                              control = glmerControl(calc.derivs = FALSE))
  wb_match_summ <- summary(wb_mod_match,
                           digits = 3)
  #--
  glm_mod_noMatch <- glmer(glm_fmla,
                           data = analytic_df_noMatch,
                           family = "binomial",
                           control = glmerControl(calc.derivs = FALSE))
  glm_noMatch_summ <- summary(glm_mod_noMatch)
  #--
  glm_mod_match <- glmer(glm_fmla,
                         data = analytic_df_match,
                         weights = weights,
                         family = "binomial",
                         control = glmerControl(calc.derivs = FALSE))
  glm_match_summ <- summary(glm_mod_match)
  #
  aic_bic_table <- tibble(col_1 = c("AIC", "BIC"),
                          col_glm_noMatch = c(comma(AIC(glm_mod_noMatch), accuracy = 0.1), comma(BIC(glm_mod_noMatch), accuracy = 0.1)),
                          col_wbm_noMatch = c(comma(AIC(wb_mod_noMatch), accuracy = 0.1), comma(BIC(wb_mod_noMatch), accuracy = 0.1)),
                          col_glm_match = c(comma(AIC(glm_mod_match), accuracy = 0.1), comma(BIC(glm_mod_match), accuracy = 0.1)),
                          col_wbm_match = c(comma(AIC(wb_mod_match), accuracy = 0.1), comma(BIC(wb_mod_match), accuracy = 0.1))) %>%
    kbl(col.names = c("", "GLMM", "WBM", "GLMM", "WBM"),
        align = c("l", rep("r", 4))) %>%
    kable_classic("striped",
                  full_width = F) %>%
    row_spec(0, bold = T) %>%
    column_spec(1, bold = TRUE) %>%
    column_spec(3, border_right = TRUE) %>%
    add_header_above(c("", "No Match" = 2, "Matched" = 2),
                     bold = TRUE)
  #--
  contrast_table <- glm_noMatch_summ$coefficients %>% 
    as.data.frame() %>% 
    rownames_to_column() %>% 
    select(rowname) %>%
    bind_rows(., wb_noMatch_summ$between_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname) %>%
                mutate(rowname = if_else(str_detect(rowname, "treated_e|s_abbr"), str_c(rowname, "between", sep = "_"), rowname))) %>%
    bind_rows(., wb_noMatch_summ$within_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname)) %>%
    distinct %>%
    left_join(., glm_noMatch_summ$coefficients %>%
                as.data.frame() %>%
                rownames_to_column() %>%
                select(rowname, Estimate, "Pr(>|z|)")) %>%
    left_join(., wb_noMatch_summ$within_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname, Est., p) %>%
                bind_rows(., wb_noMatch_summ$between_table %>% 
                            as.data.frame() %>% 
                            rownames_to_column() %>% 
                            select(rowname, Est., p) %>%
                            mutate(rowname = if_else(str_detect(rowname, "treated_e|s_abbr"), 
                                                     str_c(rowname, "between", sep = "_"), rowname))),
              by = "rowname") %>%
    left_join(., glm_match_summ$coefficients %>%
                as.data.frame() %>%
                rownames_to_column() %>%
                select(rowname, Estimate, "Pr(>|z|)"),
              by = "rowname") %>%
    left_join(., wb_match_summ$within_table %>% 
                as.data.frame() %>% 
                rownames_to_column() %>% 
                select(rowname, Est., p) %>%
                bind_rows(., wb_match_summ$between_table %>% 
                            as.data.frame() %>% 
                            rownames_to_column() %>% 
                            select(rowname, Est., p) %>%
                            mutate(rowname = if_else(str_detect(rowname, "treated_e|s_abbr"), 
                                                     str_c(rowname, "between", sep = "_"), rowname))),
              by = "rowname") %>%
    mutate(across(contains("Est"), ~comma(exp(.x), accuracy = 0.01)),
           across(contains("p"), ~comma(.x, accuracy = 0.01)),
           across(contains("p"), ~if_else(as.numeric(.x) < 0.05, 
                         cell_spec(.x, background = "skyblue"), cell_spec(.x, background = "white")))) %>%
    kbl(col.names = c("", rep(c("Estimate", "p"), 4)),
        align = c("l", rep("r", 8)),
        escape = F) %>%
    column_spec(5, border_right = TRUE) %>%
    kable_classic("striped") %>%
    add_header_above(c("", "GLMM, No Match" = 2, "WBM, No Match" = 2, "GLMM, Matched" = 2, "WBM, Matched" = 2),
                     bold = TRUE)
  #--
  return(list(slot_1 = aic_bic_table, slot_2 = contrast_table))
}
```

# New Patients Seen in 0-20 Days   

```{r binomial_wbm}
new_0_20_list <- contrast_bin_fxn("new_0_20_binary_success")
#
new_0_20_list$slot_1
#
new_0_20_list$slot_2
tictoc::toc()
```