---
title: "Association Between CRH Penetration and Gap Metric"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 12, fig.height = 12)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             plot.title = element_text(size = 22),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PCS_PCAT].[econ].PatientPCP_2020_2024
#                             	where fy = 2020
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- ps_matched %>%
  filter(treated_num == 1) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  inner_join(., vast %>% select(sta5a, s_abbr, parent_visn)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, 
                            "PC CRH", "No PC CRH"))
#=================
#making the analytic dataset
analytic_df <- sta5as_to_include %>%
  select(sta5a) %>%
  cross_join(., dates %>%
              select(vssc_month)) %>%
  left_join(., sta5as_to_include) %>%
  select(sta5a, vssc_month, treated_num, treated, s_abbr, parent_visn) %>%
  left_join(., gap_metric %>% 
              select(sta5a, vssc_month, gap_metric)) %>%
  left_join(., pen_rate %>%
              select(sta5a, vssc_month, pc_crh_per_1k_total_pc)) %>%
  mutate(pen_rate_w_0 = replace_na(pc_crh_per_1k_total_pc, 0),
         s_abbr2 = case_when(str_detect(s_abbr, "CBOC") ~ "CBOC",
                             str_detect(s_abbr, "HCC|VAMC") ~ "HCC/VAMC",
                             s_abbr == "OOS" ~ "OOS"),
         gap_cap_3 = if_else(gap_metric >= 3, 3, gap_metric))
```

# Front Matter  

## Description of this report  

* This report examines the relationship between the Gap Metric and our PC CRH Penetration Rate

## Decision Points  

* Per our discussion on April 25th I am making a report that examines the relationship between the Gap Metric and our PC CRH Penetration Rate

$$
\text{PC CRH Penetration Rate}=\frac{\text{PC CRH Encounters}}{\text{PC Encounters}+\text{PC CRH Encounters}}\times 1,000
$$
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, treated_num) %>% distinct() %>% summarise(tot = sum(treated_num))` of these met our criteria for PC CRH 
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    
* Description of _Propensity Score_ matching
    + This PS model consists of 
        + Covariates matched on their average values over Q4 FY20
        + Outcomes matched on their average values over Q4 FY20
        + Site type (CBOC, VAMC/HCC, OOS) - Exact

* The penetration rate plots below only include data from the `r length(crh_sta5as)` sta5as that met our meaningful use criteria
* The plots below have observations with a gap metric > 3 set to 3
      + There are `r sum(analytic_df$gap_metric > 3, na.rm = T)` observations with a gap metric > 3

# Gap Metric    


```{r, fig.asp = 0.8}
nat_gap <- dates %>%
  select(vssc_month) %>%
  left_join(., gap_metric %>%
              select(vssc_month, expected_ps_tot, observed_ps_tot, sta5a)) %>%
  group_by(vssc_month) %>%
  summarise(exp_tot = sum(expected_ps_tot),
            obs_tot = sum(observed_ps_tot)) %>%
  mutate(gap_metric = exp_tot / obs_tot)
#-----
# p1 <- ggplot(data = nat_gap,
#        aes(x = vssc_month, y = gap_metric)) +
#   geom_line() +
#   scale_y_continuous(limits = c(0, 3)) +
#   labs(x = "Month",
#        y = "Gap Metric")
#
mean_gap <- analytic_df %>%
  group_by(treated) %>%
  summarise(mean_val = mean(gap_metric, na.rm = T))
#
analytic_df %>%
  ggplot(data = .,
         aes(x = vssc_month, y = gap_cap_3, group = sta5a)) +
  geom_line(alpha = 0.2) +
  labs(x = "Month", 
       y = "Gap Metric") +
  facet_wrap(~treated) +
  geom_hline(data = mean_gap,
             aes(yintercept = mean_val, group = treated, color = treated),
             linewidth = 1.25) +
  theme(legend.position = "none")
#======
# p1 <- ggplot(data = nat_gap,
#        aes(y = gap_metric)) +
#   geom_boxplot() +
#   scale_y_continuous(limits = c(0, 3)) +
#   labs(y = "Gap Metric") +
#   theme(axis.text.x = element_blank(),
#         axis.ticks.x = element_blank())
#
analytic_df %>%
  ggplot(data = .,
         aes(y = gap_cap_3,
             fill = treated)) +
  geom_boxplot() +
  labs(y = "Gap Metric") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none") +
  facet_wrap(~treated)
#-------
# p1 <- ggplot(data = nat_gap,
#        aes(x = gap_metric)) +
#   geom_histogram(bins = 20,
#                  color = "black") +
#   labs(x = "Gap Metric",
#        y = "Observations")
#
analytic_df %>%
  ggplot(data = .,
         aes(x = gap_cap_3, fill = treated)) +
  geom_histogram(color = "black",
                 position = "identity",
                 alpha = 0.4,
                 bins = 50) +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "Gap Metric",
       y = "Observations") +
  theme(legend.position = "right")
```

# Penetration Rate   


```{r}
pen_rate_nat <- dates %>%
  select(vssc_month) %>%
  left_join(., pen_rate) %>%
  filter(sta5a %in% crh_sta5as) %>%
  group_by(vssc_month) %>%
  summarise(crh_tot = sum(crh_encounter_count, na.rm = T),
            pc_tot = sum(pc_encounter_total, na.rm = T)) %>%
  mutate(pen_rate = crh_tot / pc_tot * 1000)
#------
# p1 <- pen_rate_nat %>%
#   ggplot(data = .,
#          aes(x = vssc_month, y = pen_rate)) +
#   geom_line() +
#   scale_y_continuous(limits = c(0, NA)) +
#   labs(y = "PC CRH Penetration Rate",
#        x = "Month")
#
analytic_df %>%
  ggplot(data = .,
         aes(x = vssc_month, y = pc_crh_per_1k_total_pc, group = sta5a)) +
  geom_line(alpha = 0.3) +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "Month",
       y = "PC CRH Penetration Rate") +
  facet_wrap(~treated)
```

```{r}
analytic_df %>%
  ggplot(data = .,
         aes(y = pc_crh_per_1k_total_pc,
             fill = treated))  +
  geom_boxplot(color = "black") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "PC CRH Penetration Rate") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~treated)
```

```{r}
analytic_df %>%
  ggplot(data = .,
         aes(x = pc_crh_per_1k_total_pc, fill = treated)) +
  geom_histogram(color = "black",
                 position = "identity",
                 alpha = 0.4,
                 bins = 50) +
  scale_y_continuous(labels = scales::comma_format()) +
  labs(x = "PC CRH Penetration Rate",
       y = "Observations") +
  theme(legend.position = "right")
```


# Penetration Rate X Gap Metric  



```{r, fig.asp = 0.66}
analytic_df %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 8) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate")
#--
analytic_df %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 8) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate") +
  facet_wrap(~treated)
#--
# p2 <- analytic_df %>%
#   filter(gap_metric < 3) %>%
#   ggplot(data = .,
#        aes(x = gap_metric, y = pen_rate_w_0)) +
#   geom_point() +
#   ggpubr::stat_cor(color = "red") +
#   scale_y_continuous(labels = scales::comma_format()) +
#   geom_smooth(method = "lm",
#               se = F) +
#   labs(x = "Gap Metric",
#        y = "PC CRH Penetration Rate",
#        title = "Zeroes")
# #
# cowplot::plot_grid(p1, p2,
#                    ncol = 2)
```

## By VISN  

```{r, fig.asp = 0.8}
analytic_df %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 5) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate") +
  facet_wrap(~parent_visn)
#--
analytic_df %>%
  filter(treated == "Treated") %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 5) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate",
       title = "Treated") +
  facet_wrap(~parent_visn)
#
analytic_df %>%
  filter(treated != "Treated") %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 5) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate",
       title = "Control") +
  facet_wrap(~parent_visn)
#
# p2 <- analytic_df %>%
#   filter(gap_metric < 3) %>%
#   ggplot(data = .,
#        aes(x = gap_metric, y = pen_rate_w_0)) +
#   geom_point() +
#   ggpubr::stat_cor(color = "red") +
#   scale_y_continuous(labels = scales::comma_format()) +
#   geom_smooth(method = "lm",
#               se = F) +
#   labs(x = "Gap Metric",
#        y = "PC CRH Penetration Rate",
#        title = "Zeroes") +
#   facet_wrap(~parent_visn)
# #

```


## By Site Type    

```{r, fig.asp = 0.8}
analytic_df %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 8) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate") +
  facet_wrap(~s_abbr2)
# #
analytic_df %>%
  filter(treated == "Treated") %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 8) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate",
       title = "Treated") +
  facet_wrap(~s_abbr2)
#
analytic_df %>%
  filter(treated != "Treated") %>%
  ggplot(data = .,
       aes(x = gap_cap_3, y = pc_crh_per_1k_total_pc)) +
  geom_point() +
  ggpubr::stat_cor(color = "red",
                   size = 8) +
  scale_y_continuous(labels = scales::comma_format()) +
  geom_smooth(method = "lm",
              se = F) +
  labs(x = "Gap Metric",
       y = "PC CRH Penetration Rate",
       title = "Control") +
  facet_wrap(~s_abbr2)
```

# Categorical Mean Gap Metric  

```{r}
mean_gap <- analytic_df %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T),
            obs_n = n()) %>%
  mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "< 1.0",
                                    mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0 - 1.2",
                                    mean_gap > 1.2 ~ "> 1.2"),
                          ordered = TRUE,
                          levels = c("< 1.0", "1.0 - 1.2", "> 1.2")))
```

```{r}
analytic_df %>%
  left_join(., mean_gap %>%
              select(sta5a, gap_cat)) %>%
  filter(is.na(gap_cat) == F
         & is.na(pc_crh_per_1k_total_pc) == F) %>%
  group_by(gap_cat) %>%
  summarise(n_obs = comma(n()),
            mean_val = mean(pc_crh_per_1k_total_pc),
            med_val = comma(median(pc_crh_per_1k_total_pc), accuracy = 0.1),
            sd_val = sd(pc_crh_per_1k_total_pc),
            qtl_25 = quantile(pc_crh_per_1k_total_pc, 0.25),
            qtl_75 = quantile(pc_crh_per_1k_total_pc, 0.75),
            qtl_975 = quantile(pc_crh_per_1k_total_pc, 0.975),
            qtl_025 = quantile(pc_crh_per_1k_total_pc, 0.025)) %>%
  mutate(across(contains("qtl_"), ~comma(.x, accuracy = 0.01)),
         mean_sd = paste0(comma(mean_val, accuracy = 0.1), " (", comma(sd_val, accuracy = 0.01), ")"),
         qtl_25_75 = paste0("[", qtl_25, ", ", qtl_75, "]"),
         qtl_2 = paste0("[", qtl_025, ", ", qtl_975, "]")) %>%
  select(gap_cat, n_obs, mean_sd, med_val, qtl_25_75, qtl_2) %>%
  kbl(col.names = c("Mean Gap Metric", "Observations", "Mean Penetration Rate (SD)", "Median", "[25th %ile, 75th %ile]",
                    "[2.5th %ile, 97.5th %ile]"),
      align = c("l", rep("r", 5))) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
analytic_df %>%
  left_join(., mean_gap) %>%
  filter(is.na(gap_cat) == F
         & is.na(pc_crh_per_1k_total_pc) == F) %>%
  ggplot(data = .,
         aes(x = gap_cat, y = pc_crh_per_1k_total_pc,
             fill = gap_cat)) +
  geom_boxplot(color = "black") +
  theme(legend.position = "none") +
  labs(x = "Mean Gap Metric", 
       y = "PC CRH Penetration Rate") +
  scale_y_continuous(labels = scales::comma_format()) +
  stat_summary(fun = mean, geom = "point", color = "red")
```

## By Site Type  

```{r}
analytic_df %>%
  left_join(., mean_gap %>%
              select(sta5a, gap_cat)) %>%
  filter(is.na(gap_cat) == F
         & is.na(pc_crh_per_1k_total_pc) == F) %>%
  group_by(s_abbr2, gap_cat) %>%
  summarise(n_obs = comma(n()),
            mean_val = mean(pc_crh_per_1k_total_pc),
            sd_val = sd(pc_crh_per_1k_total_pc),
            med_val = comma(median(pc_crh_per_1k_total_pc), accuracy = 0.1),
            qtl_25 = quantile(pc_crh_per_1k_total_pc, 0.25),
            qtl_75 = quantile(pc_crh_per_1k_total_pc, 0.75),
            qtl_975 = quantile(pc_crh_per_1k_total_pc, 0.975),
            qtl_025 = quantile(pc_crh_per_1k_total_pc, 0.025)) %>%
  mutate(across(contains("qtl_"), ~comma(.x, accuracy = 0.01)),
         mean_sd = paste0(comma(mean_val, accuracy = 0.1), " (", comma(sd_val, accuracy = 0.01), ")"),
         qtl_25_75 = paste0("[", qtl_25, ", ", qtl_75, "]"),
         qtl_2 = paste0("[", qtl_025, ", ", qtl_975, "]")) %>%
  select(gap_cat, s_abbr2, n_obs, mean_sd, med_val, qtl_25_75, qtl_2) %>%
  kbl(col.names = c("Site Type", "Mean Gap Metric", "Observations", "Mean Penetration Rate (SD)", 
                    "Median", "[25th %ile, 75th %ile]",
                    "[2.5th %ile, 97.5th %ile]"),
      align = c("l", "l", rep("r", 5))) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T) %>%
  row_spec(c(3, 6), extra_css = "border-bottom: 1px solid;")
```

```{r}
analytic_df %>%
  left_join(., mean_gap) %>%
  filter(is.na(gap_cat) == F) %>%
  ggplot(data = .,
         aes(x = gap_cat, y = pc_crh_per_1k_total_pc,
             fill = gap_cat)) +
  geom_boxplot(color = "black") +
  theme(legend.position = "none") +
  labs(x = "Mean Gap Metric", 
       y = "PC CRH Penetration Rate") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~s_abbr2) +
  stat_summary(fun = mean, geom = "point", color = "red")
```

## By VISN  

```{r}
analytic_df %>%
  left_join(., mean_gap %>%
              select(sta5a, gap_cat)) %>%
  filter(is.na(gap_cat) == F
         & is.na(pc_crh_per_1k_total_pc) == F) %>%
  group_by(parent_visn, gap_cat) %>%
  summarise(n_obs = comma(n()),
            n_sta5a = n_distinct(sta5a),
            mean_val = mean(pc_crh_per_1k_total_pc),
            med_val = comma(median(pc_crh_per_1k_total_pc), accuracy = 0.1),
            sd_val = sd(pc_crh_per_1k_total_pc),
            qtl_25 = quantile(pc_crh_per_1k_total_pc, 0.25),
            qtl_75 = quantile(pc_crh_per_1k_total_pc, 0.75),
            qtl_975 = quantile(pc_crh_per_1k_total_pc, 0.975),
            qtl_025 = quantile(pc_crh_per_1k_total_pc, 0.025)) %>%
  arrange(parent_visn, gap_cat) %>%
  mutate(across(contains("qtl_"), ~comma(.x, accuracy = 0.01)),
         mean_sd = paste0(comma(mean_val, accuracy = 0.1), " (", comma(sd_val, accuracy = 0.01), ")"),
         qtl_25_75 = paste0("[", qtl_25, ", ", qtl_75, "]"),
         qtl_2 = paste0("[", qtl_025, ", ", qtl_975, "]")) %>%
  select(parent_visn, gap_cat, n_obs, n_sta5a, mean_sd, med_val, qtl_25_75, qtl_2) %>%
  kbl(col.names = c("VISN", "Mean Gap Metric", "Observations", "Sta5as", "Mean Penetration Rate (SD)", "Median", "[25th %ile, 75th %ile]",
                    "[2.5th %ile, 97.5th %ile]"),
      align = c("l", "l", rep("r", 6))) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T) %>%
  row_spec(c(2, 4, 7, 9, 11, 14, 17, 19, 22, 25, 27, 30, 32, 35, 37, 39, 42), extra_css = "border-bottom: 1px solid;")
```

```{r}
analytic_df %>%
  left_join(., mean_gap) %>%
  filter(is.na(gap_cat) == F) %>%
  ggplot(data = .,
         aes(x = gap_cat, y = pc_crh_per_1k_total_pc,
             fill = gap_cat)) +
  geom_boxplot(color = "black") +
  theme(legend.position = "none") +
  labs(x = "Mean Gap Metric", 
       y = "PC CRH Penetration Rate") +
  scale_y_continuous(labels = scales::comma_format()) +
  facet_wrap(~parent_visn) +
  stat_summary(fun = mean, geom = "point", color = "red")
```