---
title: "SAG Abstract Tables"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
#
dates3 <- tibble(
  vssc_month = seq.Date(ymd("2020-07-01"), ymd("2020-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#----
pc_encounters <- dbGetQuery(oabi_con, 
                            "select *
                            from [OABI_MyVAAccess].[crh_eval].A1_pc_enc_scrssn_count") %>%
  mutate(vssc_month = ymd(visitMonth),
         sta5a = Sta6a)
```

```{r}
analytic_df <- ps_matched %>%
  select(sta5a, treated, treated_num, weights, starts_with("period")) %>%
  mutate(period_flag = case_when(period1_inc == 1 ~ "Period 1",
                                 period1_inc == 0 & period2_inc == 1 ~ "Period 2",
                                 period1_inc == 0 & period2_inc == 0 & period3_inc == 1  ~ "Period 3",
                                 TRUE ~ "Control")) %>%
  left_join(., scrssn_count %>% select(sta5a, scrssn_count_avg_fy20, scrssn_count_cat)) %>%
  left_join(., vast %>% select(sta5a, s_abbr, urh_vast, parent_visn) %>%
              mutate(urh_vast = if_else(urh_vast == "U", "Urban", "Rural"))) %>%
  mutate(s_abbr2 = case_when(s_abbr %in% c("PCCBOC", "MSCBOC") ~ "CBOC",
                             s_abbr == "VAMC" ~ "VAMC",
                             s_abbr == "HCC" ~ "HCC",
                             s_abbr == "OOS" ~ "OOS",
                             TRUE ~ NA),
         treated = factor(treated,
                          ordered = T,
                          levels = c("Treated", "Control")))
```

# Front Matter  

## Description of this report  

* This is a document for creating the plots and tables we need for the SAG CRH abstract

    
## Analytic details  

    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v6.0__
    + PS model v6.0 consists of 
        + Covariates matched on their average values in FY21 Q2
        + Outcomes matched on their average values over October 2020 - March 2021
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact


# Table 1  

```{r}
analytic_df %>% droplevels %>% tabyl(scrssn_count_cat, treated) %>%
  rename(var = 1) %>%
  adorn_percentages("col") %>% 
  adorn_pct_formatting(rounding = "half up", digits = 1) %>%
  adorn_ns(position = "front") %>%
  bind_rows(., analytic_df %>%
              droplevels %>%
              tabyl(urh_vast, treated) %>%
              rename(var = 1) %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front")) %>%
  bind_rows(., analytic_df %>%
              droplevels %>%
              tabyl(s_abbr2, treated) %>%
              rename(var = 1) %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front")) %>%
  bind_rows(., analytic_df %>%
              droplevels %>%
              tabyl(period_flag, treated) %>%
              rename(var = 1) %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front")) %>%
  bind_rows(., analytic_df %>%
              droplevels %>%
              tabyl(parent_visn, treated) %>%
              rename(var = 1) %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front")) %>%
  kbl(col.names = c("", "Treated N (Col %)", "Control N (Col %)"),
      align = c("l", "c", "c")) %>%
  kable_classic("striped", 
                full_width = F) %>%
  row_spec(0, bold = T) %>%
  row_spec(3, extra_css = "border-bottom: 1px solid") %>%
  row_spec(5, extra_css = "border-bottom: 1px solid") %>%
  row_spec(9, extra_css = "border-bottom: 1px solid") %>%
  row_spec(13, extra_css = "border-bottom: 1px solid")
```

```{r}
pval_fxn <- function(covariate) {
  foo <- analytic_df %>%
    droplevels() %>%
    tabyl({{covariate}}, treated) %>%
    chisq.test()
  #
  foo$p.value
}
#
tibble(col_1 = c(
  "scrssn_count_cat",
  "urh_vast", 
  "s_abbr",
  "period_flag",
  "parent_visn"
),
col_2 = c(
  pval_fxn(scrssn_count_cat),
  pval_fxn(urh_vast),
  pval_fxn(s_abbr),
  pval_fxn(period_flag),
  pval_fxn(parent_visn)
)) %>%
  kbl(col.names = c("covariate", "p-value")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```


# Table 2  

```{r}
pc_encounters %>%
  inner_join(dates3) %>%
  inner_join(., analytic_df) %>%
  filter(is.na(treated) == F) %>%
  group_by(treated) %>%
  summarise(unique_sta5a = n_distinct(sta5a),
            sum_pc = comma(sum(pc_encounter_total, na.rm = T)),
            mean_pc = comma(mean(pc_encounter_total, na.rm = T), accuracy = 0.1),
            sd_pc = comma(sd(pc_encounter_total, na.rm = T), accuracy = 0.1), 
            count_ = comma(n())) %>%
  mutate(mean_sd_count_pc = paste0(mean_pc, " (N= ", count_, ", SD= ", sd_pc, ")")) %>%
  select(treated, sum_pc, mean_sd_count_pc) %>%
  pivot_longer(-treated) %>%
  pivot_wider(values_from = value, names_from = treated) %>%
  kbl(col.names = c("", "Treated", "Control")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
#-
analytic_df %>%
  tabyl(s_abbr2, treated) %>%
  adorn_percentages("col") %>% 
  adorn_pct_formatting(rounding = "half up", digits = 1) %>%
  adorn_ns(position = "front") %>%
  kbl(col.names = c("s_abbr", "Treated", "Control")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

```{r}
outcomes_df <- analytic_df %>%
  select(sta5a, treated) %>%
  cross_join(., dates3 %>%
               select(-time)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source, 
                     new_0_20_days_create, panel_fullness)) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  left_join(., covariates %>% 
              select(sta5a, vssc_month, pcmm_count_fy_qtr, team_pcp_ap_fte_total, pc_crh_per_1k_total_pc, pct_rural,
                     pct_white, pct_male, nosos_risk_score, adi_natRnk_avg, avg_age_oct1_2022, shep_access_metric)) %>%
  mutate(tna_new_source = as.numeric(tna_new_source))
#--
covars_fxn <- function(covar_char, covar, covar_name){
  fmla <- as.formula(paste0({{covar_char}}, " ~ treated"))
  foo <- outcomes_df %>% t.test(fmla, data = .)
  sd_vals <- outcomes_df %>%
    group_by(treated) %>% summarise(sd_val = sd({{covar}}, na.rm = T))
  #
  tibble(col_1 = {{covar_name}},
         treated_col = paste0(comma(foo$estimate[1], accuracy = 0.01), " (", comma(sd_vals[[1,2]], accuracy = 0.01), ")"),
         control_col = paste0(comma(foo$estimate[2], accuracy = 0.01), " (", comma(sd_vals[[2,2]], accuracy = 0.01), ")"),
         confint_col = paste0(comma(foo$conf.int[1], accuracy = 0.1), "-", comma(foo$conf.int[2], accuracy = 0.1)),
         pval_col = comma(foo$p.value, accuracy = 0.01))
}
#
covars_fxn("panel_fullness", panel_fullness, "Panel Fullness") %>%
  bind_rows(covars_fxn("team_pcp_ap_fte_total", team_pcp_ap_fte_total, "Team PCP/AP FTE")) %>%
  bind_rows(covars_fxn("pcmm_count_fy_qtr", pcmm_count_fy_qtr, "Uniques in PCMM")) %>%
  bind_rows(covars_fxn("pc_crh_per_1k_total_pc", pc_crh_per_1k_total_pc, "Community Care Referral Rate")) %>%
  bind_rows(covars_fxn("pct_rural", pct_rural, "Rural %")) %>%
  bind_rows(covars_fxn("pct_male", pct_male, "Male %")) %>%
  bind_rows(covars_fxn("pct_white", pct_white, "White %")) %>%
  bind_rows(covars_fxn("nosos_risk_score", nosos_risk_score, "Nosos")) %>%
  bind_rows(covars_fxn("adi_natRnk_avg", adi_natRnk_avg, "ADI")) %>%
  bind_rows(covars_fxn("avg_age_oct1_2022", avg_age_oct1_2022, "Age")) %>%
  bind_rows(covars_fxn("shep_access_metric", shep_access_metric, "SHEP")) %>%
  bind_rows(covars_fxn("est_pc_pt_wt_pid", est_pc_pt_wt_pid, "Established"))  %>%
  bind_rows(covars_fxn("new_pc_pt_wt_create", new_pc_pt_wt_create, "New")) %>%
  bind_rows(covars_fxn("tna_new_source", tna_new_source, "TNA")) %>%
  bind_rows(covars_fxn("tc_pc_success_prop", tc_pc_success_prop, "Timely Care")) %>%
  kbl(col.names = c("", "Treated Mean (SD)", "Control Mean (SD)", "95% CI", "p-value"),
      full_width = F) %>%
  kable_classic("striped")
```

# Slide 7  

```{r}
uniques_count <- dbGetQuery(oabi_con,
                            "select count(distinct ScrSSN_char) as scrssn_count
                              	, sta5a
                              from [PCS_PCAT].[econ].PatientPCP_2020_2024 
                              where fy IN(2021, 2022, 2023)
                              group by sta5a")
#
sta5as_to_include <- vast %>%
  left_join(., scrssn_count) %>%
  filter(scrssn_count_cat != "< 450"
         & is.na(scrssn_count_cat) == F) %>%
  select(sta5a) 
#
mean_gap <- sta5as_to_include %>%
  cross_join(., dates %>%
               select(vssc_month)) %>%
  left_join(., gap_metric) %>%
  group_by(sta5a) %>%
  summarise(mean_gap = mean(gap_metric, na.rm = T)) %>%
  mutate(gap_cat = factor(case_when(mean_gap < 1.0 ~ "< 1.0",
                             mean_gap >= 1.0 & mean_gap <= 1.2 ~ "1.0 - 1.2",
                             mean_gap > 1.2 ~ "> 1.2"),
                          ordered = T,
                          levels = c("< 1.0", "1.0 - 1.2", "> 1.2")))
#--
uniques_crh <- dbGetQuery(oabi_con,
                          "select count(distinct scrssn) as scrssn_count_crh
from [pact_cc].CRH.C_crh_utilization_final
where visitdate > cast('2020-09-30' as date)
	and visitdate < cast('2023-10-01' as date)
	and care_type = 'Primary Care'")
#
slide_7_df <- sta5as_to_include %>%
  cross_join(., dates %>%
               select(vssc_month)) %>%
  left_join(., pen_rate %>%
              select(sta5a, vssc_month, crh_encounter_count)) %>%
  left_join(., pc_encounters %>%
              mutate(vssc_month = ymd(visitMonth)) %>%
              select(sta5a = Sta6a, vssc_month, pc_encounter_total)) %>%
  left_join(., gap_metric) %>%
  left_join(., ps_matched %>%
              select(sta5a, treated_num)) %>%
  mutate(treated_num = replace_na(treated_num, 0))
#
col_1 <- slide_7_df %>%
  filter(treated_num == 1) %>%
  group_by(sta5a) %>%
  summarise(crh_encounter_count = sum(crh_encounter_count, na.rm = T),
            mean_gap = mean(gap_metric, na.rm = T)) %>%
  left_join(., uniques_count) %>%
  summarise(viz_sum = sum(crh_encounter_count, na.rm = T),
            uniques_sum = uniques_crh[[1]],
            sites = n()) %>%
  mutate(foo = "foo",
         viz_per_unique = comma(viz_sum / uniques_sum, accuracy = 0.01),
         across(starts_with("gap_"),
                ~paste0(.x, " (", percent(.x / 338, accuracy = 0.1), ")")),
         across(where(is.numeric), ~comma(.x, accuracy = 1))) %>%
  select(1, 2, 5, 3, 4) %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  bind_rows(., mean_gap %>%
              filter(is.na(gap_cat) == F) %>%
              left_join(., slide_7_df) %>%
              filter(treated_num == 1) %>%
              group_by(gap_cat) %>%
              summarise(value = sum(crh_encounter_count, na.rm = T)) %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front") %>%
              rename(name = gap_cat))
#
col_2 <- slide_7_df %>%
  filter(treated_num == 1) %>%
  group_by(sta5a) %>%
  summarise(encounter_count = sum(pc_encounter_total, na.rm = T),
            mean_gap = mean(gap_metric, na.rm = T)) %>%
  left_join(., uniques_count) %>%
  summarise(viz_sum = sum(encounter_count, na.rm = T),
            uniques_sum = sum(scrssn_count, na.rm = T),
            sites = n()) %>%
  mutate(foo = "foo",
         viz_per_unique = comma(viz_sum / uniques_sum, accuracy = 0.01),
         across(starts_with("gap_"),
                ~paste0(.x, " (", percent(.x / 338, accuracy = 0.1), ")")),
         across(where(is.numeric), ~comma(.x, accuracy = 1))) %>%
  select(1, 2, 5, 3, 4) %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  bind_rows(., mean_gap %>%
              filter(is.na(gap_cat) == F) %>%
              left_join(., slide_7_df) %>%
              filter(treated_num == 1) %>%
              group_by(gap_cat) %>%
              summarise(value = sum(pc_encounter_total, na.rm = T)) %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front") %>%
              rename(name = gap_cat))
#
col_3 <- slide_7_df %>%
  filter(treated_num == 0) %>%
  group_by(sta5a) %>%
  summarise(encounter_count = sum(pc_encounter_total, na.rm = T),
            mean_gap = mean(gap_metric, na.rm = T)) %>%
  left_join(., uniques_count) %>%
  summarise(viz_sum = sum(encounter_count, na.rm = T),
            uniques_sum = sum(scrssn_count, na.rm = T),
            sites = n()) %>%
  mutate(foo = "foo",
         viz_per_unique = comma(viz_sum / uniques_sum, accuracy = 0.01),
         across(starts_with("gap_"),
                ~paste0(.x, " (", percent(.x / 638, accuracy = 0.1), ")")),
         across(where(is.numeric), ~comma(.x, accuracy = 1))) %>%
  select(1, 2, 5, 3, 4) %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  bind_rows(., mean_gap %>%
              filter(is.na(gap_cat) == F) %>%
              left_join(., slide_7_df) %>%
              filter(treated_num == 0) %>%
              group_by(gap_cat) %>%
              summarise(value = sum(pc_encounter_total, na.rm = T)) %>%
              adorn_percentages("col") %>% 
              adorn_pct_formatting(rounding = "half up", digits = 1) %>%
              adorn_ns(position = "front") %>%
              rename(name = gap_cat))
#=======
col_1 %>%
  left_join(., col_2, by = "name") %>%
  left_join(., col_3, by = "name") %>%
  kbl(col.names = c("", "PC CRH Encounters - Treated", "PC Visits - Treated", "PC Visits - Control"),
      full_width = F,
      align = c("l", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

# Slide 8  

```{r}
analytic_df <- ps_matched %>%
  select(sta5a) %>%
  cross_join(., dates %>% 
               select(vssc_month)) %>%
  left_join(., ps_matched %>% 
              select(sta5a, treated_num)) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source) %>%
              mutate(tna_new_source = as.numeric(tna_new_source))) %>%
  left_join(., pen_rate %>%
              select(sta5a, vssc_month, crh_encounter_count)) %>%
  left_join(., timely_care %>%
              mutate(tc_pc_success_pct = tc_pc_success_prop * 100) %>%
              select(sta5a, vssc_month, tc_pc_success_pct)) %>%
  mutate(gap_cat = factor(case_when(gap_metric < 1.0 ~ "< 1.0",
                             gap_metric >= 1.0 & gap_metric <= 1.2 ~ "1.0 - 1.2",
                             gap_metric > 1.2 ~ "> 1.2")))
#---
analytic_df$treated_num <- relevel(as.factor(analytic_df$treated_num),
                                   ref = "0")
#
analytic_df$gap_cat <- relevel(as.factor(analytic_df$gap_cat),
                                   ref = "> 1.2")
#
glm_fxn <- function(outcome, exposure, reference_cat){
  fmla <- as.formula(paste0({{outcome}},
                            " ~ ",
                            {{exposure}},
                            " + (1|sta5a)"))
  #
  model <- lmer(fmla,
                data = analytic_df)
  #
  estimate <- if({{reference_cat}} == "gap_cat1.0 - 1.2"){fixef(model)[3]} 
    else {fixef(model)[2]}
  #
  confint_est <- if({{reference_cat}} == "treated_num1"){confint(model, "treated_num1", method = "profile")}
    else if({{reference_cat}} == "gap_cat< 1.0"){confint(model, "gap_cat< 1.0", method = "profile")}
    else {confint(model, "gap_cat1.0 - 1.2", method = "profile")}
      
  #
  paste0(comma(estimate, accuracy = 0.01), 
         " (",
         comma(confint_est[1], accuracy = 0.01),
         ", ",
         comma(confint_est[2], accuracy = 0.01),
         ")")
}
tibble(
  col_1 = c("Meaningful use (vs. No)",
            "Gap < 1.0 (vs. > 1.2)",
            "Gap 1.0 - 1.2 (vs. > 1.2)"),
  col_2 = c(glm_fxn("est_pc_pt_wt_pid", "treated_num", "treated_num1"),
            glm_fxn("est_pc_pt_wt_pid", "gap_cat", "gap_cat< 1.0"),
            glm_fxn("est_pc_pt_wt_pid", "gap_cat", "gap_cat1.0 - 1.2")),
  col_3 = c(glm_fxn("new_pc_pt_wt_create", "treated_num", "treated_num1"),
            glm_fxn("new_pc_pt_wt_create", "gap_cat", "gap_cat< 1.0"),
            glm_fxn("new_pc_pt_wt_create", "gap_cat", "gap_cat1.0 - 1.2")),
  col_4 = c(glm_fxn("tna_new_source", "treated_num", "treated_num1"),
            glm_fxn("tna_new_source", "gap_cat", "gap_cat< 1.0"),
            glm_fxn("tna_new_source", "gap_cat", "gap_cat1.0 - 1.2")),
  col_5 = c(glm_fxn("tc_pc_success_pct", "treated_num", "treated_num1"),
            glm_fxn("tc_pc_success_pct", "gap_cat", "gap_cat< 1.0"),
            glm_fxn("tc_pc_success_pct", "gap_cat", "gap_cat1.0 - 1.2"))
) %>%
  kbl(col.names = c("", "EPWT", "NPWT", "TNA", "Timely Care"),
      align = c("l", rep("r", 4))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```