---
title: "Post-COVID PC CRH Analysis: Continuous Gap vs. Panel Fullness"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             plot.title = element_text(size = 24),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0),
         s_abbr2 = case_when(str_detect(s_abbr, "CBOC") ~ "CBOC",
                             str_detect(s_abbr, "VAMC|HCC") ~ "VAMC/HCC",
                             s_abbr == "OOS" ~ "OOS")) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well as 
  #flags for treated/control
  #PS matching weights
  #flags for meeting inclusion criteria in 3 periods
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv")) %>%
  rename(treated_ever = treated_num)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(tna_new_source = as.numeric(tna_new_source))
#making a time/date dataset
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time") %>%
  mutate(fy = if_else(month(vssc_month) > 9, year(vssc_month) + 1, year(vssc_month)),
         qtr = case_when(month(vssc_month) %in% c(10, 11, 12) ~ 1,
                         month(vssc_month) %in% c(1, 2, 3) ~ 2,
                         month(vssc_month) %in% c(4, 5, 6) ~ 3,
                         month(vssc_month) %in% c(7, 8, 9) ~ 4,
                         TRUE ~ 99))
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
#average age on october 1st 2022
age_sta5a_qtr <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].D1_age_sta5a_qtr")
#sta5a-fy-specific counts of gender, race, and urh, as well as total uniques
race_gender_urh <- dbGetQuery(oabi_con,
                              "select * from [OABI_MyVAAccess].[crh_eval].D2_race_gender_urh_count") %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100)
#sta5a-fy_qtr-specific average ADI and quartile counts, as well as total
adi_sta5a_fy <- dbGetQuery(oabi_con,
                            "select * from [OABI_MyVAAccess].[crh_eval].D3_adi_sta5a_fy")
#sta5a-month-specific average Nosos, Obs:Exp, and Team PCP/AP FTE
nosos_obs_exp_team_fte <- dbGetQuery(oabi_con,
                                     "select * from [OABI_MyVAAccess].[crh_eval].F1_2_vssc_covars") %>%
  mutate(vssc_month = ymd(vssc_month))
#sta5a-fy-specific average drive distance and time to closest PC site
drive_time <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].D4_avg_drive_time")
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#sta5a-month-specific timely care success rate
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#sta5a-month-specific PC CRH penetration rate and it's components
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month),
         treated_month = if_else(crh_encounter_count > 9, 1, 0))#time-varying treated
```

```{r time_varying_treated}
treated_sta5a <- ps_matched %>%
  filter(treated_ever == 1) %>%
  select(sta5a)
#
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    ((last_mo_mt9_pc_crh == 1 | is.na(last_mo_mt9_pc_crh)) 
                                     | (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh))),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit_both = meets_inc_crit,
         meets_inc_crit_fwd = if_else(this_mo_mt9_pc_crh == TRUE & (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh)), 1, 0)
         ) %>%
  filter(sta5a %in% treated_sta5a$sta5a) %>%
  right_join(., dates %>%
               select(vssc_month) %>%
               cross_join(., treated_sta5a)) %>%
  mutate(meets_inc_crit_both = replace_na(meets_inc_crit_both, 0),
         meets_inc_crit_fwd = replace_na(meets_inc_crit_fwd, 0),
         crh_enc_count_na = crh_encounter_count,
         crh_encounter_count = replace_na(crh_encounter_count, 0))
```




```{r unmatched_analytic_df}
treated_after_sep2020 <- pen_rate %>%
  filter(vssc_month > ymd("2020-09-01")) %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    ((last_mo_mt9_pc_crh == 1 | is.na(last_mo_mt9_pc_crh)) 
                                     | (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh))),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit_both = meets_inc_crit,
         meets_inc_crit_fwd = if_else(this_mo_mt9_pc_crh == TRUE & (next_mo_mt9_pc_crh == 1 | is.na(next_mo_mt9_pc_crh)), 1, 0)
  ) %>%
  filter(meets_inc_crit == 1) %>%
  select(sta5a) %>%
  distinct
#--
analytic_df2 <- vast %>%
  filter(str_detect(s_abbr, "CBOC|VAMC|HCC|OOS") == T) %>%
  select(sta5a) %>%
  inner_join(., scrssn_count %>%
               filter(is.na(scrssn_count_cat) == F
                      & scrssn_count_cat != "< 450") %>%
               select(sta5a)) %>%
  mutate(treated_ever = if_else(sta5a %in% treated_after_sep2020$sta5a, 1, 0)) %>%
  cross_join(., dates) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source, new_0_20_days_create, panel_fullness)) %>%
  left_join(., adi_sta5a_fy %>%
              select(sta5a = Sta5a, fy, adi_natRnk_avg)) %>%
  left_join(., age_sta5a_qtr %>%
              select(sta5a = Sta5a, fy = FY, qtr = QTR, avg_age_oct1_2022)) %>%
  left_join(., drive_time %>%
              select(sta5a = CLOSESTPCSITE, fy, avg_driveTime) %>%
              bind_rows(., drive_time %>%
                          filter(fy == 2022) %>%
                          select(sta5a = CLOSESTPCSITE, fy, avg_driveTime) %>%
                          mutate(fy = 2023))) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  left_join(., nosos_obs_exp_team_fte) %>%
  left_join(., race_gender_urh %>%
              select(sta5a = Sta5a, fy = FY, pct_male, pct_white, pct_rural)) %>%
  left_join(., vast %>%
              select(sta5a, s_abbr, s_abbr2, parent_visn)) %>%
  left_join(., pen_rate) %>%
  left_join(., scrssn_count) %>%
  mutate(treated_ever = relevel(as.factor(treated_ever), ref = "0"),
         new_0_20_days_create_pct = new_0_20_days_create * 100,
         #treated = relevel(as.factor(treated), ref = "Control"),
         treated_month = relevel(as.factor(replace_na(treated_month, 0)), ref = "0"),
         tc_pc_success_pct = tc_pc_success_prop * 100,
         time_t = time,
         gap_metric_cat = factor(case_when(gap_metric >= 1.2 ~ "> 1.2",
                                    gap_metric < 1 ~ "< 1.0",
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ "1.0-1.2")),
         gap_metric_num = case_when(gap_metric >= 1.2 ~ 3,
                                    gap_metric < 1 ~ 1,
                                    gap_metric < 1.2 & gap_metric >= 1.0 ~ 2),
         gap_x_10 = gap_metric * 10,
         new_0_20_binary_success = if_else(new_0_20_days_create_pct >= 80, 1, 0),
         panel_fullness_capped = if_else(panel_fullness > 5, 5, panel_fullness),
         panel_fullness_pct = panel_fullness_capped * 100,
         pf_pct_div_10 = panel_fullness_pct / 10,
         panel_fullness_cat = factor(case_when(panel_fullness_pct < 80 ~ "<80%",
                                        panel_fullness_pct > 105 ~ ">105%",
                                        panel_fullness_pct >= 80 & panel_fullness_pct <= 105 ~ "80-105%")),
         gap_lt_1 = if_else(gap_metric_cat == "< 1.0", 1, 0),
         gap_1_12 = if_else(gap_metric_cat == "1.0-1.2", 1, 0),
         gap_gt_12 = if_else(gap_metric_cat == "> 1.2", 1, 0),
         scrssn_450_2399 = if_else(scrssn_count_cat == "450 - 2,399", 1, 0),
         scrssn_2400_9999 = if_else(scrssn_count_cat == "2,400 - 9,999", 1, 0),
         scrssn_ge_10k = if_else(scrssn_count_cat == "10,000+", 1, 0)) %>%
  fastDummies::dummy_cols(., select_columns = c("parent_visn", "s_abbr"))
#--
analytic_panel_noMatch <- analytic_df2 %>%
  panelr::panel_data(.,
                     id = sta5a,
                     wave = time)
```




# Front Matter  

## Description of this report  

* This is an iteration of the _post-COVID_ analysis

## Decision Points  

* This is a sensitivity analysis contrasting __continuous__ gap metric vs panel fullness


    
## Analytic details  

    
* Description of the unmatched cohort for the W-B model 
    + The first observation in the data occurs on `r min(analytic_df2$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df2$vssc_month)`
    + There are `r nrow(analytic_df2) %>% comma()` rows in the data
    + These rows come from `r analytic_df2 %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df2 %>% select(sta5a, treated_ever) %>% distinct() %>% summarise(tot = sum(if_else(treated_ever == "1", 1, 0)))` of these met our criteria for PC CRH 
      + `r analytic_df2 %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df2 %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df2 %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    

```{r set_ref_levs2, class.source = 'fold-show'}
analytic_panel_noMatch$panel_fullness_cat <- relevel(analytic_panel_noMatch$panel_fullness_cat, ref = ">105%")
analytic_panel_noMatch$treated_month <- relevel(analytic_panel_noMatch$treated_month, ref = "0")
analytic_panel_noMatch$gap_metric_cat <- relevel(analytic_panel_noMatch$gap_metric_cat, ref = "< 1.0")
analytic_panel_noMatch$scrssn_count_cat <- relevel(factor(analytic_panel_noMatch$scrssn_count_cat, ordered = F), ref = "450 - 2,399")
analytic_panel_noMatch$new_0_20_binary_success <- relevel(factor(analytic_panel_noMatch$new_0_20_binary_success, ordered = F), ref = "0")
analytic_panel_noMatch$treated_ever <- relevel(factor(analytic_panel_noMatch$treated_ever, ordered = F), ref = "0")
analytic_panel_noMatch$s_abbr2 <- relevel(factor(analytic_panel_noMatch$s_abbr2, ordered = F), ref = "CBOC")
```


```{r fxns}
wbm_fxn <- function(outcome){
  fmla_og <- as.formula(paste0(outcome, " ~ treated_month + time_t ", 
                               "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                               "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + scrssn_count_cat", 
                               "| treated_ever", 
                               "+ gap_metric_cat + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                               "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + s_abbr2 + scrssn_count_cat + parent_visn", 
                               " | (1|sta5a)"))
  wb_fmla_gap <- as.formula(paste0(outcome, " ~ treated_month + time_t ", 
                                   "+ gap_x_10 + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                                   "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + scrssn_count_cat", 
                                   "| treated_ever", 
                                   "+ gap_x_10 + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                                   "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + s_abbr2 + scrssn_count_cat + parent_visn", 
                                   " | (1|sta5a)"))
  wb_fmla_pf <- as.formula(paste0(outcome, " ~ treated_month + time_t ", 
                                  "+ pf_pct_div_10 + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                                  "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + scrssn_count_cat", 
                                  "| treated_ever", 
                                  "+ pf_pct_div_10 + adi_natRnk_avg + avg_age_oct1_2022 + avg_driveTime + nosos_risk_score",
                                  "+ team_pcp_ap_fte_total + pct_male + pct_white + pct_rural + s_abbr2 + scrssn_count_cat + parent_visn", 
                                  " | (1|sta5a)"))
  #
  mod_og <- 
    if({{outcome}} == "new_0_20_binary_success")
    {panelr::wbm(fmla_og,
                 data = analytic_panel_noMatch,
                 family = "binomial",
                 pvals = T,
                 pR2 = F,
                 control = glmerControl(calc.derivs = FALSE)) %>%
        summary()}
  else
  {panelr::wbm(fmla_og, 
               data = analytic_panel_noMatch) %>%
      summary()}
  #--
  mod_gap <- 
    if({{outcome}} == "new_0_20_binary_success")
    {panelr::wbm(wb_fmla_gap,
                 data = analytic_panel_noMatch,
                 family = "binomial",
                 pvals = T,
                 pR2 = F,
                 control = glmerControl(calc.derivs = FALSE)) %>%
        summary()}
  else
  {panelr::wbm(wb_fmla_gap, 
               data = analytic_panel_noMatch) %>%
      summary()}
  #--
  mod_pf <- 
    if({{outcome}} == "new_0_20_binary_success")
    {panelr::wbm(wb_fmla_pf,
                 data = analytic_panel_noMatch,
                 family = "binomial",
                 pvals = T,
                 pR2 = F,
                 control = glmerControl(calc.derivs = FALSE)) %>%
        summary()}
  else
  {panelr::wbm(wb_fmla_pf, 
               data = analytic_panel_noMatch) %>%
      summary()}
  #=====
  col_name <- if({{outcome}} == "new_0_20_binary_success"){"Odds Ratio"}
  else{"Estimate"}
  #=====
  within_og_sum <- if({{outcome}} == "new_0_20_binary_success"){mod_og$within_table %>%
      rownames_to_column() %>%
      mutate(`Est.` = exp(`Est.`))}
  else {mod_og$within_table %>%
      rownames_to_column()}
  #
  between_og_sum <- if({{outcome}} == "new_0_20_binary_success"){mod_og$between_table %>%
      rownames_to_column() %>%
      mutate(`Est.` = exp(`Est.`))}
  else {mod_og$between_table %>%
      rownames_to_column()}
  #
  within_gap_sum <- if({{outcome}} == "new_0_20_binary_success"){mod_gap$within_table %>%
      rownames_to_column() %>%
      mutate(`Est.` = exp(`Est.`))}
  else {mod_gap$within_table %>%
      rownames_to_column()}
  #
  between_gap_sum <- if({{outcome}} == "new_0_20_binary_success"){mod_gap$between_table %>%
      rownames_to_column() %>%
      mutate(`Est.` = exp(`Est.`))}
  else {mod_gap$between_table %>%
      rownames_to_column()}
  #
  within_pf_sum <- if({{outcome}} == "new_0_20_binary_success"){mod_pf$within_table %>%
      rownames_to_column() %>%
      mutate(`Est.` = exp(`Est.`))}
  else {mod_pf$within_table %>%
      rownames_to_column()}
  #
  between_pf_sum <- if({{outcome}} == "new_0_20_binary_success"){mod_pf$between_table %>%
      rownames_to_column() %>%
      mutate(`Est.` = exp(`Est.`))}
  else {mod_pf$between_table %>%
      rownames_to_column()}
  #----
  within_table <- within_og_sum %>%
    full_join(., within_gap_sum,
              by = "rowname") %>%
    full_join(., within_pf_sum,
              by = "rowname") %>%
    select(rowname, 
           Est..x, p.x, Est..y, p.y, Est., p) %>%
    mutate(across(contains("Est"), ~comma(.x, accuracy = 0.001)),
           across(contains("p"), ~if_else(.x < 0.001, "< 0.001", comma(.x, accuracy = 0.001)))) %>%
    kbl(col.names = c("Covariate", col_name, "p-value", col_name, "p-value", col_name, "p-value"),
        align = c("l", rep("r", 6)),
        caption = "<span style='font-size:22px'><b>Within</b></span>") %>%
    kable_classic("striped",
                  full_width = F) %>%
    row_spec(0, bold = TRUE) %>%
    column_spec(c(3, 5), border_right = TRUE) %>%
    add_header_above(c(" ", "Original Analysis" = 2, "Gap Metric" = 2, "Panel Fullness" = 2),
                     bold = T,
                     font_size = 18)
  #=======
  between_table <-  between_og_sum %>%
    full_join(., between_gap_sum,
              by = "rowname") %>%
    full_join(., between_pf_sum,
              by = "rowname") %>%
    select(rowname, 
           Est..x, p.x, Est..y, p.y, Est., p) %>%
    mutate(across(contains("Est"), ~comma(.x, accuracy = 0.001)),
           across(contains("p"), ~if_else(.x < 0.001, "< 0.001", comma(.x, accuracy = 0.001)))) %>%
    kbl(col.names = c("Covariate", col_name, "p-value", col_name, "p-value", col_name, "p-value"),
        align = c("l", rep("r", 6)),
        caption = "<span style='font-size:22px'><b>Within</b></span>") %>%
    kable_classic("striped",
                  full_width = F) %>%
    row_spec(0, bold = TRUE) %>%
    column_spec(c(3, 5), border_right = TRUE) %>%
    add_header_above(c(" ", "Original Analysis" = 2, "Gap Metric" = 2, "Panel Fullness" = 2),
                     bold = T,
                     font_size = 18)
  
  #
  return(list(slot_1 = within_table, slot_2 = between_table))
}
```

```{r}
pf_1 <- analytic_df2 %>%
  filter(panel_fullness < 2) %>% 
  ggplot(data = .,
       aes(x = panel_fullness)) +
  scale_x_continuous(labels = percent_format()) +
  scale_y_continuous(labels = comma_format()) +
  geom_histogram(color = "black",
                 fill = "darkorchid") +
  labs(y = "Observations",
       x = "Panel Fullness")
#
pf_2 <- analytic_df2 %>%
  filter(panel_fullness < 2) %>%
  ggplot(data = .,
         aes(x = "a",
             y = panel_fullness)) +
  geom_boxplot(fill = "darkorchid") +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="red", fill="red") +
  labs(y = "Panel Fullness")
#-
cowplot::plot_grid(pf_1, pf_2, ncol = 2)
#--
gap_1 <- analytic_df2 %>%
  filter(gap_metric < 2) %>% 
  ggplot(data = .,
       aes(x = gap_metric)) +
  scale_x_continuous(labels = comma_format()) +
  scale_y_continuous(labels = comma_format()) +
  geom_histogram(color = "black",
                 fill = "dodgerblue") +
  labs(y = "Observations",
       x = "Gap Metric")
#
gap_2 <- analytic_df2 %>%
  filter(gap_metric < 2) %>%
  ggplot(data = .,
         aes(x = "a",
             y = gap_metric)) +
  geom_boxplot(fill = "dodgerblue") +
  scale_y_continuous(labels = comma_format()) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  stat_summary(fun = mean, geom="point", shape=20, size=3, color="red", fill="red") +
  labs(y = "Gap Metric")
#-
cowplot::plot_grid(gap_1, gap_2, ncol = 2)
```


# Established Patient Wait Time  
 
```{r}
est_list <- wbm_fxn("est_pc_pt_wt_pid")
#
est_list$slot_1
#
est_list$slot_2
```

# New Patient Wait Time  
  
```{r}
new_list <- wbm_fxn("new_pc_pt_wt_create")
#
new_list$slot_1
#
new_list$slot_2
```


# Third Next Available    
  
```{r}
tna_list <- wbm_fxn("tna_new_source")
#
tna_list$slot_1
#
tna_list$slot_2
```


# Timely Care    
 
```{r}
tc_list <- wbm_fxn("tc_pc_success_pct")
#
tc_list$slot_1
#
tc_list$slot_2
```


# New Patients Seen in 0-20 days > 80%  

```{r wb_model}
tictoc::tic()
bin_list <- wbm_fxn("new_0_20_binary_success")
#
bin_list$slot_1
#
bin_list$slot_2
tictoc::toc()
```


