---
title: "A Better Self-Check of FY23 CRH Encounters"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
library(plotly)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```


```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#crh encounters
crh_encounters <- dbGetQuery(oabi_con,
                             "select *
                             from [PACT_CC].[CRH].C_crh_utilization_final") %>%
  rename(sta5a = spoke_sta5a_combined_cdw) %>%
  mutate(visitdate = ymd(visitdate))
#
totals_by_sta5a <- crh_encounters %>%
  group_by(sta5a) %>%
  summarise(crh_encounters_total = n())
#
totals_by_type_and_sta5a <- crh_encounters %>%
  group_by(sta5a, care_type) %>%
  summarise(crh_encounters_type = n())
#
sta5a_to_keep <- totals_by_sta5a %>%
  filter(crh_encounters_total > 25) %>%
  select(sta5a) %>%
  pull
#---
analytic_df <- crh_encounters %>%
  filter(sta5a %in% sta5a_to_keep)
#
unique_sta5a <- analytic_df %>%
  select(sta5a) %>%
  distinct %>%
  left_join(., vast)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

# Front Matter  

## Description of this report  

* This is a __better__ self-check of the FY2023 CRH Encounters table(s)
    + The one I use here is _[PACT_CC].[CRH].C_crh_utilization_final_, but _[PACT_CC].[CRH].crh_utilization_fy23_ contains the same data, restricted to FY2023

## Decision Points  

* There is a drop-off in CRH encounters from September to October 2022, and this report hopes to shed some light on where and (maybe) why that happens
    

# Encounters By Fiscal Year  

## Total Encounters  
* In the tables below I am restricting to the `r totals_by_sta5a %>% filter(crh_encounters_total > 25) %>% nrow` sta5as that had __more than 25 CRH encounters__ over these 5 years of data 

```{r}
tot_col <- analytic_df %>%
  filter(fy != 2018) %>%
  group_by(fy) %>%
  summarise(count_tot = n(),
            count_sta5a_tot = n_distinct(sta5a)) %>%
  mutate(fy = as.character(fy),
         count_sta5a_tot = as.character(count_sta5a_tot))
#---
mh_col <- analytic_df %>%
  filter(fy != 2018 & care_type == "Mental Health") %>%
  group_by(fy) %>%
  summarise(count_mh = n(),
            count_sta5a_mh = n_distinct(sta5a)) %>%
  mutate(fy = as.character(fy),
         count_sta5a_mh = as.character(count_sta5a_mh))
#--
pc_col <- analytic_df %>%
  filter(fy != 2018 & care_type == "Primary Care") %>%
  group_by(fy) %>%
  summarise(count_pc = n(),
            count_sta5a_pc = n_distinct(sta5a)) %>%
  mutate(fy = as.character(fy),
         count_sta5a_pc = as.character(count_sta5a_pc))
#--
ph_col <- analytic_df %>%
  filter(fy != 2018 & care_type == "Pharmacy") %>%
  group_by(fy) %>%
  summarise(count_ph = n(),
            count_sta5a_ph = n_distinct(sta5a)) %>%
  mutate(fy = as.character(fy),
         count_sta5a_ph = as.character(count_sta5a_ph)) 
#--
pcmhi_col <- analytic_df %>%
  filter(fy != 2018 & care_type == "PCMHI") %>%
  group_by(fy) %>%
  summarise(count_pcmhi = n(),
            count_sta5a_pcmhi = n_distinct(sta5a)) %>%
  mutate(fy = as.character(fy),
         count_sta5a_pcmhi = as.character(count_sta5a_pcmhi))
#--
spec_col <- analytic_df %>%
  filter(fy != 2018 & care_type == "Specialty") %>%
  group_by(fy) %>%
  summarise(count = n(),
            count_sta5a_spec = n_distinct(sta5a)) %>%
  mutate(fy = as.character(fy),
         count_sta5a_spec = as.character(count_sta5a_spec))
#==--==--
mh_col %>%
  left_join(., pc_col) %>%
  left_join(., ph_col) %>%
  left_join(., pcmhi_col) %>%
  left_join(., spec_col) %>%
  adorn_totals("both") %>%
  right_join(., tot_col %>%
               adorn_totals()) %>%
  select(1, 13, 14, 2:12) %>%
  mutate(across(where(is.numeric), ~comma(.x))) %>%
  kbl(col.names = c("FY", rep(c("Encounters", "Unique Stations"), 6), "Total"),
      align = rep("r", 14)) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T, font_size = 14) %>%
  add_header_above(c("", 
                     "Total" = 2,
                     "Mental Health" = 2,
                     "Primary Care" = 2,
                     "Pharmacy" = 2,
                     "PCMHI" = 2,
                     "Specialty" = 2,
                     ""),
                   font_size = 22,
                   bold = TRUE)
```


# The Problem   

## CRH Encounters Drop-Off From September to October 2022     
* The plots below include all sta5as 

```{r}
pen_rate %>% 
  filter(vssc_month > ymd("2018-09-01")) %>%
  group_by(vssc_month) %>%
  summarise(tot_crh = sum(crh_encounter_count, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = tot_crh)) +
  geom_line() +
  scale_y_continuous(limits = c(0, NA),
                     labels = comma_format(accuracy = 1)) +
  labs(x = "Month",
       y = "Total PC CRH")
```

### By Type   
```{r}
all_encounters_by_type <- dbGetQuery(oabi_con,
                                     "with CTE as (
	select *,
		vizMonth = DATEFROMPARTS(year(visitdate), month(visitdate), '01')
	from [PACT_CC].[CRH].C_crh_utilization_final
)
select vizMonth, care_type, count(*) as encounter_count
from CTE
group by vizMonth, care_type") %>%
  mutate(vizMonth = as.Date(vizMonth)) %>%
  filter(vizMonth > ymd("2018-09-01"))
#----
ggplot(data = all_encounters_by_type,
       aes(x = vizMonth, y = encounter_count, color = care_type, group = care_type)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters") +
  theme(legend.position = "right")
```

# By VISN  
```{r}
all_encounters_type_visn <- dbGetQuery(oabi_con,
                                       "with CTE as (
	select *,
		vizMonth = DATEFROMPARTS(year(visitdate), month(visitdate), '01')
	from [PACT_CC].[CRH].C_crh_utilization_final
)
select vizMonth, care_type, count(*) as encounter_count, b.parent_visn
from CTE as a
left join [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as b
on a.spoke_sta5a_combined_cdw = b.sta5a
group by vizMonth, care_type, parent_visn") %>%
  mutate(vizMonth = as.Date(vizMonth)) %>%
  filter(vizMonth > ymd("2018-09-01"))
```

## All Encounters  
```{r}

all_encounters_type_visn %>% 
  group_by(vizMonth, parent_visn) %>%
  summarise(encounter_count = sum(encounter_count, na.rm = T)) %>%
  filter(is.na(parent_visn) == F) %>%
  ggplot(data = .,
       aes(x = vizMonth, y = encounter_count, color = parent_visn, group = parent_visn)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters") +
  theme(legend.position = "none") +
  facet_wrap(~parent_visn) +
  geom_vline(xintercept = as.Date("2022-10-01"),
             lty = 2)
```

## Mental Health  
```{r}
all_encounters_type_visn %>%
  filter(is.na(parent_visn) == F
         & care_type == "Mental Health") %>%
  ggplot(data = .,
       aes(x = vizMonth, y = encounter_count, color = parent_visn, group = parent_visn)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters") +
  theme(legend.position = "none") +
  facet_wrap(~parent_visn) +
  geom_vline(xintercept = as.Date("2022-10-01"),
             lty = 2)
```

## Primary Care    
```{r}
all_encounters_type_visn %>%
  filter(is.na(parent_visn) == F
         & care_type == "Primary Care") %>%
  ggplot(data = .,
       aes(x = vizMonth, y = encounter_count, color = parent_visn, group = parent_visn)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters") +
  theme(legend.position = "none") +
  facet_wrap(~parent_visn) +
  geom_vline(xintercept = as.Date("2022-10-01"),
             lty = 2)
```

## PCMHI, Pharmacy, & Specialty      
```{r}
all_encounters_type_visn %>%
  filter(is.na(parent_visn) == F
         & care_type %ni% c("Mental Health", "Primary Care")) %>%
  ggplot(data = .,
       aes(x = vizMonth, y = encounter_count, color = care_type, group = care_type)) + 
  geom_line(linewidth = 1) +
  scale_y_continuous(labels = comma_format()) +
  scale_x_date(date_breaks = "6 months",
               date_labels = "%b-%y") +
  labs(x = "Month",
       y = "CRH Encounters") +
  theme(legend.position = "bottom") +
  facet_wrap(~parent_visn) +
  geom_vline(xintercept = as.Date("2022-10-01"),
             lty = 2)
```