---
title: "Gap Metric: Self-check"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  left_join(., scrssn_count) %>%
  filter(scrssn_count_cat != "< 450"
         & is.na(scrssn_count_cat) == F
         & is.na(s_abbr) == F)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
# ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
# #pulling vssc access metrics
# access_metrics <- dbGetQuery(oabi_con,
#                              "select * from [crh_eval].E2_VSSC_access_metrics") %>%
#   mutate(vssc_month = ymd(vssc_month)) %>%
#   left_join(timely_care)
# #making a time column
# dates <- tibble(
#   vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
#   arrange(vssc_month) %>%
#   rowid_to_column(., var = "time")
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#========
gap_metric_1 <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  inner_join(., vast) %>%
  mutate(obs_only_zero = if_else(observed_ps_tot == 0 & expected_ps_tot != 0, 1, 0),
         exp_only_zero = if_else(expected_ps_tot == 0 & observed_ps_tot != 0, 1, 0),
         both_zero = if_else(observed_ps_tot == 0 & expected_ps_tot == 0, 1, 0),
         either_zero = if_else(observed_ps_tot == 0 | expected_ps_tot == 0, 1, 0),
         vssc_month = ymd(vssc_month))
#
gap_nas <- gap_metric_1 %>% filter(is.na(gap_metric))
#
gap_metric <- gap_metric_1 %>%
  filter(gap_metric < 10
         & gap_metric > 0)
```



# Front Matter  

## Description of this report  

* This is a self-check of my downloading and processing of the __Gap Metric__ data

## Decision Points  

* In moving forward with the __post-COVID analysis__ we have discussed including several new metrics, including the gap metric
* The gap metric data was updated through September 2022, and when we last discussed the end of our post-COVID study period we had decided that December 2022 would be our final month
* I followed the directions from Amy's .pdf and produced the data described here
* What that means is I: 
    1. Downloaded 2 versions each of the observed and expected panel sizes, the first I select "All Teams" while for the second I only select "CRH Teams"
    2. I join these two datasets on sta5a and month
    3. I subtract CRH values from All Teams values
* The Gap Metric is then the sta5a-month ratio of observed to expected panel size, with the CRH contribution removed:

$$
\text{Gap Metric}=\frac{Expected Panel Size}{Observed Panel Size}
$$

   
## Description of the data    

+ The first observation in the data occurs on `r min(gap_metric$vssc_month)`
+ The last observation in the data occurs on `r max(gap_metric$vssc_month)`
+ There are `r nrow(gap_metric) %>% comma()` rows in the data
+ These rows come from `r gap_metric %>% select(sta5a) %>% n_distinct() %>% comma()` sta5as 
    + `r gap_metric %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
    + `r gap_metric %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
    + `r gap_metric %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
+ In the plot below I dropped `r nrow(gap_metric_1) - nrow(gap_metric)` observations:
    + `r sum(is.na(gap_metric_1$gap_metric))` (`r (sum(is.na(gap_metric_1$gap_metric)) / (nrow(gap_metric_1) - nrow(gap_metric))) %>% percent(accuracy = 0.1)`) of these have missing values
    + `r sum(gap_metric_1$gap_metric >= 10, na.rm = T)` (`r (sum(gap_metric_1$gap_metric >= 10, na.rm = T)/ (nrow(gap_metric_1) - nrow(gap_metric))) %>% percent(accuracy = 0.1)`) have values greater or equal to 10
    + `r sum(gap_metric_1$gap_metric <= 0, na.rm = T)` (`r (sum(gap_metric_1$gap_metric <= 0, na.rm = T)/ (nrow(gap_metric_1) - nrow(gap_metric))) %>% percent(accuracy = 0.1)`). I want to note that `r sum(gap_metric_1$gap_metric == 0, na.rm = T)` of these are exactly zero
    

```{r}
gap_summary <- gap_metric %>%
  group_by(sta5a) %>%
  summarise(avg_val = mean(gap_metric, na.rm = T),
            sd_val = sd(gap_metric, na.rm = T),
            n_obs = n(),
            avg_obsr = mean(observed_panel_size, na.rm = T),
            sd_obsr = sd(observed_panel_size, na.rm = T),
            avg_exp = mean(expected_panel_size, na.rm = T),
            sd_exp = sd(expected_panel_size, na.rm = T))
#--
ggplot(data = gap_summary,
         aes(x = reorder(sta5a, avg_val), 
             y = avg_val,
             ymin = avg_val - sd_val,
             ymax = avg_val + sd_val)) +
  geom_point() +
  geom_hline(yintercept = 1,
             lty = 2) +
  geom_errorbar(alpha = 0.5) +
  ggthemes::theme_clean() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(x = "Sta5a",
       y = "Average Gap Metric +/- SD")
```


# Top 25     

```{r}
top_25 <- gap_summary %>%
  arrange(desc(avg_val)) %>%
  slice_head(., n = 25) %>%
  left_join(., vast) %>%
  mutate(
    disp_val = paste0(
      comma(avg_val, accuracy = 0.1), " (",
      comma(sd_val, accuracy = 0.1), ")"
    ),
    disp_val_obs = paste0(
      comma(avg_obsr, accuracy = 0.1), " (",
      comma(sd_obsr, accuracy = 0.1), ")"
    ),
    disp_val_exp = paste0(
      comma(avg_exp, accuracy = 0.1), " (",
      comma(sd_exp, accuracy = 0.1), ")"
    ),
    disp_name = paste0(
      "(", sta5a, ") ",
      short_name
    )) %>%
  select(parent_visn, disp_name, s_abbr, disp_val, n_obs, disp_val_obs, disp_val_exp)
#
top_25 %>%
  kbl(col.names = c("VISN", "(Sta5a) Division Name", "Site Type in VAST", "Average Gap Metric (SD)",
                    "Observations (i.e., months)", "Average Observed Panel Size (SD)", "Average Expected Panel Size (SD)"),
      align = c("c", "l", "c", rep("r", 4))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

# Just the top 5  

```{r}
gap_metric %>%
  filter(sta5a %in% c("605", "619", "528G8", "598", "603")) %>%
  select(sta5a, vssc_month, observed_ps_tot, expected_ps_tot) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  ggplot(data = .,
         aes(x = vssc_month, y = value, group = name, color = name)) +
  geom_line() +
  facet_wrap(~sta5a) +
  scale_x_date(breaks = "6 months") +
  theme(axis.text.x = element_text(angle = 270))
```



# Bottom 15       

```{r}
bottom_15 <- gap_summary %>%
  arrange(desc(avg_val)) %>%
  slice_tail(., n = 15) %>%
  left_join(., vast) %>%
  mutate(
    disp_val = paste0(
      comma(avg_val, accuracy = 0.1), " (",
      comma(sd_val, accuracy = 0.1), ")"
    ),
    disp_val_obs = paste0(
      comma(avg_obsr, accuracy = 0.1), " (",
      comma(sd_obsr, accuracy = 0.1), ")"
    ),
    disp_val_exp = paste0(
      comma(avg_exp, accuracy = 0.1), " (",
      comma(sd_exp, accuracy = 0.1), ")"
    ),
    disp_name = paste0(
      "(", sta5a, ") ",
      short_name
    )) %>%
  select(parent_visn, disp_name, s_abbr, disp_val, n_obs, disp_val_obs, disp_val_exp)
#
bottom_15 %>%
  kbl(col.names = c("VISN", "(Sta5a) Division Name", "Site Type in VAST", "Average Gap Metric (SD)",
                    "Observations (i.e., months)", "Average Observed Panel Size (SD)", "Average Expected Panel Size (SD)"),
      align = c("c", "l", "c", rep("r", 4))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```