---
title: "A Quick Look at MH Access Metrics"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2023-10-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PCS_PCAT].[econ].PatientPCP_2020_2024
#                             	where fy = 2020
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
mh_metrics_filepath <- "R:\\HSRD\\HSRD_General\\Kaboli Access Team\\CRH Evaluation\\Bjarni\\MH Access Metrics"
mh_access_dirs <- list.dirs(path = mh_metrics_filepath, full.names = TRUE)
```


# Front Matter  

## Description of this report  

* This is a sanity check of the MH Access metrics I have downloaded



# CONT3  
```{r}
cont3 <- read_csv(list.files(mh_access_dirs[2], full.names = TRUE, pattern = "_all"))
#
cont3_national <- cont3 %>%
  filter(location == "National") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
cont3_visn <- cont3 %>%
  filter(str_sub(location, start = 1, end = 1) == "V") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
cont3_parent <- cont3 %>%
  filter(str_sub(location, start = 1, end = 1) == "(") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
```

* This is available quarterly at the national level:
```{r}
ggplot(data = cont3_national,
       aes(x = name, y = value, group = 1)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  labs(y = "CONT3")
```

* As well as the VISN level:
```{r}
ggplot(data = cont3_visn,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "right") +
  labs(y = "CONT3")
```

* And the parent station level:
```{r}
ggplot(data = cont3_parent,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "CONT3")
```

# MH13  
* This is available monthly at the sta5a level: 
* The actual metric we want (i.e., proportion of appointments in 30 days or less) isn't directly reported, which means I had to do some math to get the answer  

```{r}
#------
mh13 <- read_csv(list.files(mh_access_dirs[5], full.names = TRUE, pattern = "_all"))
#==
mh13 %>% left_join(., vast %>% select(sta5a, parent_visn)) %>%
  filter(is.na(parent_visn) == F) %>%
  ggplot(data = .,
         aes(x = month, y = prop_le_30, group = sta5a, color = sta5a)) +
  geom_line() +
  scale_y_continuous(limits = c(NA, 1.0),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "MH13") +
  facet_wrap(~parent_visn)
```

# MH17  
* This is available monthly at the sta5a level: 
* The actual metric we want (i.e., proportion of appointments in 30 days or less) isn't directly reported, which means I had to do some math to get the answer  

```{r}
mh17 <- read_csv(list.files(mh_access_dirs[6], full.names = TRUE, pattern = "_all"))
#==
mh17 %>% left_join(., vast %>% select(sta5a, parent_visn)) %>%
  filter(is.na(parent_visn) == F) %>%
  ggplot(data = .,
         aes(x = month, y = prop_le_30, group = sta5a, color = sta5a)) +
  geom_line() +
  scale_y_continuous(limits = c(NA, 1.0),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "MH17") +
  facet_wrap(~parent_visn)
```

# MHPA1  

```{r}
#------
mhpa1 <- read_csv(list.files(mh_access_dirs[7], full.names = TRUE, pattern = "_all"))
#
mhpa1_national <- mhpa1 %>%
  filter(location == "National") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
mhpa1_visn <- mhpa1 %>%
  filter(str_sub(location, start = 1, end = 1) == "V") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
mhpa1_parent <- mhpa1 %>%
  filter(str_sub(location, start = 1, end = 1) == "(") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
```

* This is available quarterly at the national level:
```{r}
ggplot(data = mhpa1_national,
       aes(x = name, y = value, group = 1)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  labs(y = "MHPA1")
```

* As well as the VISN level:
```{r}
ggplot(data = mhpa1_visn,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "right") +
  labs(y = "MHPA1")
```

* And the parent station level:
```{r}
ggplot(data = mhpa1_parent,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "MHPA1")
```

# PCMHI7  

```{r}
#------
pcmhi7 <- read_csv(list.files(mh_access_dirs[8], full.names = TRUE, pattern = "_all"))
#
pcmhi7_national <- pcmhi7 %>%
  filter(location == "National") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"),
         value = as.numeric(str_remove(value, "%")) / 100)
#
pcmhi7_visn <- pcmhi7 %>%
  filter(str_sub(location, start = 1, end = 1) == "V") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"),
         value = as.numeric(str_remove(value, "%")) / 100)
#
pcmhi7_parent <- pcmhi7 %>%
  filter(str_sub(location, start = 1, end = 1) == "(") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"),
         value = as.numeric(str_remove(value, "%")) / 100)
```

* This is available quarterly at the national level:
```{r}
ggplot(data = pcmhi7_national,
       aes(x = name, y = value, group = 1)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 0.5),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  labs(y = "PCMHI7")
```

* As well as the VISN level:
```{r}
ggplot(data = pcmhi7_visn,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous(limits = c(0, 0.6),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "right") +
  labs(y = "PCMHI7")
```

* And the parent station level:
```{r}
ggplot(data = pcmhi7_parent,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous(limits = c(NA, 1.0),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "PCMHI7")
```

# PCOV2  

```{r}
#------
pcov2 <- read_csv(list.files(mh_access_dirs[9], full.names = TRUE, pattern = "_all"))
#
pcov2_national <- pcov2 %>%
  filter(location == "National") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
pcov2_visn <- pcov2 %>%
  filter(str_sub(location, start = 1, end = 1) == "V") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
pcov2_parent <- pcov2 %>%
  filter(str_sub(location, start = 1, end = 1) == "(") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
```

* This is available quarterly at the national level:
```{r}
ggplot(data = pcov2_national,
       aes(x = name, y = value, group = 1)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  labs(y = "PCOV2")
```

* As well as the VISN level:
```{r}
ggplot(data = pcov2_visn,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "right") +
  labs(y = "PCOV2")
```

* And the parent station level:
```{r}
ggplot(data = pcov2_parent,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "PCOV2")
```

# PDE1  

```{r}
#------
pde1 <- read_csv(list.files(mh_access_dirs[10], full.names = TRUE, pattern = "_all"))
#
pde1_national <- pde1 %>%
  filter(location == "National") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"),
         value = as.numeric(str_remove(value, "%")) / 100)
#
pde1_visn <- pde1 %>%
  filter(str_sub(location, start = 1, end = 1) == "V") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"),
         value = as.numeric(str_remove(value, "%")) / 100)
#
pde1_parent <- pde1 %>%
  filter(str_sub(location, start = 1, end = 1) == "(") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"),
         value = as.numeric(str_remove(value, "%")) / 100)
```

* This is available quarterly at the national level:
```{r}
ggplot(data = pde1_national,
       aes(x = name, y = value, group = 1)) +
  geom_line() +
  scale_y_continuous(limits = c(0.5, 1),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  labs(y = "PDE1")
```

* As well as the VISN level:
```{r}
ggplot(data = pde1_visn,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous(limits = c(0.5, 1),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "right") +
  labs(y = "PDE1")
```

* And the parent station level:
```{r}
ggplot(data = pde1_parent,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous(limits = c(NA, 1.0),
                     labels = percent_format(accuracy = 1)) +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "PDE1")
```

# VSAA1  

```{r}
#------
vsaa1 <- read_csv(list.files(mh_access_dirs[11], full.names = TRUE, pattern = "_all"))
#
vsaa1_national <- vsaa1 %>%
  filter(location == "National") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
vsaa1_visn <- vsaa1 %>%
  filter(str_sub(location, start = 1, end = 1) == "V") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
vsaa1_parent <- vsaa1 %>%
  filter(str_sub(location, start = 1, end = 1) == "(") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
```

* This is available quarterly at the national level:
```{r}
ggplot(data = vsaa1_national,
       aes(x = name, y = value, group = 1)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  labs(y = "VSAA1")
```

* As well as the VISN level:
```{r}
ggplot(data = vsaa1_visn,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "right") +
  labs(y = "VSAA1")
```

* And the parent station level:
```{r}
ggplot(data = vsaa1_parent,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "VSAA1")
```

# VSPC2  

```{r}
#------
vspc2 <- read_csv(list.files(mh_access_dirs[12], full.names = TRUE, pattern = "_all"))
#
vspc2_national <- vspc2 %>%
  filter(location == "National") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
vspc2_visn <- vspc2 %>%
  filter(str_sub(location, start = 1, end = 1) == "V") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
#
vspc2_parent <- vspc2 %>%
  filter(str_sub(location, start = 1, end = 1) == "(") %>%
  select(-contains("std")) %>%
  pivot_longer(-location) %>%
  mutate(name = str_remove(name, "score_"))
```

* This is available quarterly at the national level:
```{r}
ggplot(data = vspc2_national,
       aes(x = name, y = value, group = 1)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank()) +
  labs(y = "VSPC2")
```

* As well as the VISN level:
```{r}
ggplot(data = vspc2_visn,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "right") +
  labs(y = "VSPC2")
```

* And the parent station level:
```{r}
ggplot(data = vspc2_parent,
       aes(x = name, y = value, group = location, color = location)) +
  geom_line() +
  scale_y_continuous() +
  theme(axis.text.x = element_text(angle = 270, vjust = 0.3),
        axis.title.x = element_blank(),
        legend.position = "none") +
  labs(y = "VSPC2")
```

