---
title: "Bootstrap Self-Check"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
#library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_pre_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(vssc_month = seq.Date(ymd("2018-10-01"), ymd("2020-02-01"), "1 month")) %>%
  rowid_to_column(., var = "time") %>%
  mutate(time2 = time - 12)
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PACT_CC].[econ].PatientPCP
#                             	where fy = 2018
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- ps_matched %>%
  select(sta5a, at_least_10_pc_crh_flag) %>%
  mutate(crh_flag = factor(if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "No PC CRH"),
                           ordered = TRUE,
                           levels = c("PC CRH", "No PC CRH")))
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01") 
             & vssc_month > ymd("2018-09-01")) %>%#restrict to our timeframe
      left_join(., dates) %>%#add time column
  group_by(sta5a) %>%
  mutate(treat = factor(case_when(
    sta5a %in% crh_sta5as ~ "PC CRH",
    TRUE ~ "Control")),
         post = factor(if_else(vssc_month > ymd("2019-09-01"), 
                               "Post Intervention (i.e., FY20)",
                               "Pre-Intervention (i.e., FY19)")),
    tx_fe = if_else(treat == "PC CRH", 1, 0),
    post_fe = if_else(post == "Post Intervention (i.e., FY20)", 1, 0)) %>%
  ungroup %>%
  left_join(., covariates) %>%
  left_join(., vast %>% select(sta5a, s_abbr)) %>%
  mutate(nosos_x_10 = nosos_risk_score * 10,
         panel_ratio_x_10 = obs_exp_panel_ratio * 10,
         adi_div_10 = adi_natRnk_avg / 10)
#
analytic_df$post <- relevel(analytic_df$post, ref = "Pre-Intervention (i.e., FY19)")
analytic_df$treat <- relevel(analytic_df$treat, ref = 'Control')
```

# Front Matter  

## Description of this report  

* This is a self-check of the bootstrapping I did of the estimates (and their standard errors) of our interaction terms   

## Decision Points  

* Since this is my first "official" boostrap, I thought I should conduct a self-check of my methods
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    + Propensity score matching restrictions (i.e., pairs, weights, none)
    + What else?
    
* Description of _Propensity Score_ matching
    + This report uses a variation of __Propensity Score v5.1__
    + PS model v5.1 consists of 
        + Covariates matched on their average values in FY18 Q4
        + Outcomes matched on their average values over FY19
        + Removed ADI and NOSOS
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact
    + __This version restricted the pool of potential controls to those sta5as that have never had a PC CRH encounter__



# Established Patient Wait Time  

```{r}
bline_trend1 <- lmer(est_pc_pt_wt_pid ~ 
                       treat * post * time2
                     + panel_ratio_x_10
                     + pct_male
                     + pct_rural
                     + nosos_x_10
                     + adi_div_10
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#
bline_trend1_confints <- confint(bline_trend1)
#--
b_time <- summary(bline_trend1)$coefficients[4,1]
ci_time <- paste0("(", 
                  comma(bline_trend1_confints[6,1], accuracy = 0.0001), ", ",
                  comma(bline_trend1_confints[6,2], accuracy = 0.0001), ")")
b_post <- summary(bline_trend1)$coefficients[3,1]
ci_post <- paste0("(", 
                  comma(bline_trend1_confints[5,1], accuracy = 0.0001), ", ",
                  comma(bline_trend1_confints[5,2], accuracy = 0.0001), ")")
b_treat <- summary(bline_trend1)$coefficients[2,1]
ci_treat <- paste0("(", 
                  comma(bline_trend1_confints[4,1], accuracy = 0.0001), ", ",
                  comma(bline_trend1_confints[4,2], accuracy = 0.0001), ")")
b_treat_x_time <- summary(bline_trend1)$coefficients[11,1]
ci_treat_x_time <- paste0("(", 
                  comma(bline_trend1_confints[13,1], accuracy = 0.0001), ", ",
                  comma(bline_trend1_confints[13,2], accuracy = 0.0001), ")")
b_post_x_time <- summary(bline_trend1)$coefficients[12,1]
ci_post_x_time <- paste0("(", 
                  comma(bline_trend1_confints[14,1], accuracy = 0.001), ", ",
                  comma(bline_trend1_confints[14,2], accuracy = 0.001), ")")
b_post_x_time_x_treat <- summary(bline_trend1)$coefficients[13,1]
ci_post_x_time_x_treat <- paste0("(", 
                  comma(bline_trend1_confints[15,1], accuracy = 0.001), ", ",
                  comma(bline_trend1_confints[15,2], accuracy = 0.001), ")")
#-----
est_boot <- read_csv(here("Input", "Bootstrap", "est_pc_pt_wt_boot.csv"))
#
b_time_diff <- b_time - mean(est_boot$b_time)
b_post_diff <- b_post - mean(est_boot$b_post)
b_treat_diff <- b_treat - mean(est_boot$b_treat)
b_treat_x_time_diff <- b_treat_x_time - mean(est_boot$b_treat_x_time)
b_post_x_time_diff <- b_post_x_time - mean(est_boot$b_post_x_time)
b_post_x_time_x_treat_diff <- b_post_x_time_x_treat - mean(est_boot$b_post_x_time_x_treat)
#-----
beta_paste_fxn <- function(input_b, input_ci){
  paste0(comma({{input_b}}, accuracy = 0.001), " ", {{input_ci}})
}
#--
boot_paste_fxn <- function(df_name, var_name){
  paste0(
    comma(mean(df_name[[var_name]]), accuracy = 0.0001), " (", 
    comma(quantile(df_name[[var_name]], probs = 0.025), accuracy = 0.0001), ", ",
    comma(quantile(df_name[[var_name]], probs = 0.975), accuracy = 0.0001), ")")
}
boot_paste_fxn(est_boot, "b_time")

#
tibble(
  col_1 = c("$\\beta_{time}$",
            "$\\beta_{post}$",
            "$\\beta_{treat}$",
            "$\\beta_{time\\times treat}$",
            "$\\beta_{time\\times post}$",
            "$\\beta_{time\\times treat\\times post}$"),
  col_2 = c(beta_paste_fxn(b_time, ci_time),
            beta_paste_fxn(b_post, ci_post),
            beta_paste_fxn(b_treat, ci_treat),
            beta_paste_fxn(b_treat_x_time, ci_treat_x_time),
            beta_paste_fxn(b_post_x_time, ci_post_x_time),
            beta_paste_fxn(b_post_x_time_x_treat, ci_post_x_time_x_treat)),
  col_3 = c(boot_paste_fxn(est_boot, "b_time"),
            boot_paste_fxn(est_boot, 'b_post'),
            boot_paste_fxn(est_boot, 'b_treat'),
            boot_paste_fxn(est_boot, 'b_treat_x_time'),
            boot_paste_fxn(est_boot, 'b_post_x_time'),
            boot_paste_fxn(est_boot, 'b_post_x_time_x_treat')),
  col_4 = c(comma(b_time_diff, accuracy = 0.0001),
            comma(b_post_diff, accuracy = 0.0001),
            comma(b_treat_diff, accuracy = 0.0001),
            comma(b_treat_x_time_diff, accuracy = 0.0001),
            comma(b_post_x_time_diff, accuracy = 0.0001),
            comma(b_post_x_time_x_treat_diff, accuracy = 0.0001)),
  col_5 = c(percent(b_time_diff / b_time, accuracy = 0.1),
            percent(b_post_diff / b_post, accuracy = 0.1),
            percent(b_treat_diff / b_treat, accuracy = 0.1),
            percent(b_treat_x_time_diff / b_treat_x_time, accuracy = 0.1),
            percent(b_post_x_time_diff / b_post_x_time, accuracy = 0.1),
            percent(b_post_x_time_x_treat_diff / b_post_x_time_x_treat, accuracy = 0.1))
) %>%
  kbl(escape = F,
      col.names = c("", "Estimates - Full Dataset", "Estimates - Bootstrap",
                    "Difference", "Difference as Proportion of Full Dataset"),
      align = c("l", rep("r", 4))) %>%
  kable_classic("striped")
```

* Assuming we are ok with these results, I'll move on to Table 3

## Table 3  



```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(paste0("$\\beta_{time}=", 
                   comma(mean(est_boot$b_time), accuracy = 0.001), "$"), 
            paste0("$\\beta_{time} + \\beta_{treat\\times time}=", 
                   comma(mean(est_boot$b_time + est_boot$b_treat_x_time), accuracy = 0.001), "$"), 
            paste0("$\\beta_{treat\\times time}=", 
                   comma(mean(est_boot$b_treat_x_time), accuracy = 0.001), "$")),
  col_3 = c(paste0("$\\beta_{time}+\\beta_{post\\times time}=",
                   comma(mean(est_boot$b_time + est_boot$b_post_x_time), accuracy = 0.001), "$"),
            paste0("$\\beta_{time}+\\beta_{post\\times time} +$ \n  $\\beta_{post\\times time\\times treat}=",
                   comma(mean(est_boot$b_time + est_boot$b_post_x_time + est_boot$b_post_x_time_x_treat), accuracy = 0.001), "$"),
            paste0("$\\beta_{post\\times time\\times treat}=",
                   comma(mean(est_boot$b_post_x_time_x_treat), accuracy = 0.001), "$")),
  col_4 = c(paste0("$\\beta_{post\\times time}=",
                   comma(mean(est_boot$b_post_x_time), accuracy = 0.001), "$"),
            paste0("$\\beta_{post\\times time} +$ \n $\\beta_{post\\times time\\times treat} -$\n$\\beta_{treat\\times time}=",
                   comma(mean(est_boot$b_post_x_time + est_boot$b_post_x_time_x_treat - est_boot$b_treat_x_time), accuracy = 0.001), "$"),
            "")
) %>%
  kbl(escape = F,
      col.names = c("", "Pre Slope", "Post Slope", "Post - Pre"),
      align = c("l", rep("c", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

# New Patient Wait Time  

```{r}
bline_trend2 <- lmer(new_pc_pt_wt ~ 
                       treat * post * time2
                     + panel_ratio_x_10
                     + pct_male
                     + pct_rural
                     + nosos_x_10
                     + adi_div_10
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#--
b_time <- summary(bline_trend2)$coefficients[4,1]
b_post <- summary(bline_trend2)$coefficients[3,1]
b_treat <- summary(bline_trend2)$coefficients[2,1]
b_treat_x_time <- summary(bline_trend2)$coefficients[11,1]
b_post_x_time <- summary(bline_trend2)$coefficients[12,1]
b_post_x_time_x_treat <- summary(bline_trend2)$coefficients[13,1]
#-----
new_boot <- read_csv(here("Input", "Bootstrap", "new_pc_pt_wt_boot.csv"))
#
b_time_diff <- b_time - mean(new_boot$b_time)
b_post_diff <- b_post - mean(new_boot$b_post)
b_treat_diff <- b_treat - mean(new_boot$b_treat)
b_treat_x_time_diff <- b_treat_x_time - mean(new_boot$b_treat_x_time)
b_post_x_time_diff <- b_post_x_time - mean(new_boot$b_post_x_time)
b_post_x_time_x_treat_diff <- b_post_x_time_x_treat - mean(new_boot$b_post_x_time_x_treat)
#-----
tibble(
  col_1 = c("$\\beta_{time}$",
            "$\\beta_{post}$",
            "$\\beta_{treat}$",
            "$\\beta_{time\\times treat}$",
            "$\\beta_{time\\times post}$",
            "$\\beta_{time\\times treat\\times post}$"),
  col_2 = c(comma(b_time, accuracy = 0.001),
            comma(b_post, accuracy = 0.001),
            comma(b_treat, accuracy = 0.001),
            comma(b_treat_x_time, accuracy = 0.001),
            comma(b_post_x_time, accuracy = 0.001),
            comma(b_post_x_time_x_treat, accuracy = 0.001)),
  col_3 = c(comma(mean(new_boot$b_time), accuracy = 0.001),
            comma(mean(new_boot$b_post), accuracy = 0.001),
            comma(mean(new_boot$b_treat), accuracy = 0.001),
            comma(mean(new_boot$b_treat_x_time), accuracy = 0.001),
            comma(mean(new_boot$b_post_x_time), accuracy = 0.001),
            comma(mean(new_boot$b_post_x_time_x_treat), accuracy = 0.001)),
  col_4 = c(comma(b_time_diff, accuracy = 0.0001),
            comma(b_post_diff, accuracy = 0.0001),
            comma(b_treat_diff, accuracy = 0.0001),
            comma(b_treat_x_time_diff, accuracy = 0.0001),
            comma(b_post_x_time_diff, accuracy = 0.0001),
            comma(b_post_x_time_x_treat_diff, accuracy = 0.0001)),
  col_5 = c(percent(b_time_diff / b_time, accuracy = 0.1),
            percent(b_post_diff / b_post, accuracy = 0.1),
            percent(b_treat_diff / b_treat, accuracy = 0.1),
            percent(b_treat_x_time_diff / b_treat_x_time, accuracy = 0.1),
            percent(b_post_x_time_diff / b_post_x_time, accuracy = 0.1),
            percent(b_post_x_time_x_treat_diff / b_post_x_time_x_treat, accuracy = 0.1))
) %>%
  kbl(escape = F,
      col.names = c("", "Estimates - Full Dataset", "Estimates - Bootstrap",
                    "Difference", "Difference as Proportion of Full Dataset"),
      align = c("l", rep("r", 4))) %>%
  kable_classic("striped")
```

* Assuming we are ok with these results, I'll move on to Table 3

## Table 3  



```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(paste0("$\\beta_{time}=", 
                   comma(mean(new_boot$b_time), accuracy = 0.001), "$"), 
            paste0("$\\beta_{time} + \\beta_{treat\\times time}=", 
                   comma(mean(new_boot$b_time + new_boot$b_treat_x_time), accuracy = 0.001), "$"), 
            paste0("$\\beta_{treat\\times time}=", 
                   comma(mean(new_boot$b_treat_x_time), accuracy = 0.001), "$")),
  col_3 = c(paste0("$\\beta_{time}+\\beta_{post\\times time}=",
                   comma(mean(new_boot$b_time + new_boot$b_post_x_time), accuracy = 0.001), "$"),
            paste0("$\\beta_{time}+\\beta_{post\\times time} +$ \n  $\\beta_{post\\times time\\times treat}=",
                   comma(mean(new_boot$b_time + new_boot$b_post_x_time + new_boot$b_post_x_time_x_treat), accuracy = 0.001), "$"),
            paste0("$\\beta_{post\\times time\\times treat}=",
                   comma(mean(new_boot$b_post_x_time_x_treat), accuracy = 0.001), "$")),
  col_4 = c(paste0("$\\beta_{post\\times time}=",
                   comma(mean(new_boot$b_post_x_time), accuracy = 0.001), "$"),
            paste0("$\\beta_{post\\times time} +$ \n $\\beta_{post\\times time\\times treat} -$\n$\\beta_{treat\\times time}=",
                   comma(mean(new_boot$b_post_x_time + new_boot$b_post_x_time_x_treat - new_boot$b_treat_x_time), accuracy = 0.001), "$"),
            "")
) %>%
  kbl(escape = F,
      col.names = c("", "Pre Slope", "Post Slope", "Post - Pre"),
      align = c("l", rep("c", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```


# Third Next Available    

```{r}
bline_trend3 <- lmer(third_next_avail ~ 
                       treat * post * time2
                     + panel_ratio_x_10
                     + pct_male
                     + pct_rural
                     + nosos_x_10
                     + adi_div_10
                     + (1|sta5a),
                     data = analytic_df,
                     REML = TRUE)
#--
b_time <- summary(bline_trend3)$coefficients[4,1]
b_post <- summary(bline_trend3)$coefficients[3,1]
b_treat <- summary(bline_trend3)$coefficients[2,1]
b_treat_x_time <- summary(bline_trend3)$coefficients[11,1]
b_post_x_time <- summary(bline_trend3)$coefficients[12,1]
b_post_x_time_x_treat <- summary(bline_trend3)$coefficients[13,1]
#-----
tna_boot <- read_csv(here("Input", "Bootstrap", "third_next_avail_boot.csv"))
#
b_time_diff <- b_time - mean(tna_boot$b_time)
b_post_diff <- b_post - mean(tna_boot$b_post)
b_treat_diff <- b_treat - mean(tna_boot$b_treat)
b_treat_x_time_diff <- b_treat_x_time - mean(tna_boot$b_treat_x_time)
b_post_x_time_diff <- b_post_x_time - mean(tna_boot$b_post_x_time)
b_post_x_time_x_treat_diff <- b_post_x_time_x_treat - mean(tna_boot$b_post_x_time_x_treat)
#-----
tibble(
  col_1 = c("$\\beta_{time}$",
            "$\\beta_{post}$",
            "$\\beta_{treat}$",
            "$\\beta_{time\\times treat}$",
            "$\\beta_{time\\times post}$",
            "$\\beta_{time\\times treat\\times post}$"),
  col_2 = c(comma(b_time, accuracy = 0.001),
            comma(b_post, accuracy = 0.001),
            comma(b_treat, accuracy = 0.001),
            comma(b_treat_x_time, accuracy = 0.001),
            comma(b_post_x_time, accuracy = 0.001),
            comma(b_post_x_time_x_treat, accuracy = 0.001)),
  col_3 = c(comma(mean(tna_boot$b_time), accuracy = 0.001),
            comma(mean(tna_boot$b_post), accuracy = 0.001),
            comma(mean(tna_boot$b_treat), accuracy = 0.001),
            comma(mean(tna_boot$b_treat_x_time), accuracy = 0.001),
            comma(mean(tna_boot$b_post_x_time), accuracy = 0.001),
            comma(mean(tna_boot$b_post_x_time_x_treat), accuracy = 0.001)),
  col_4 = c(comma(b_time_diff, accuracy = 0.0001),
            comma(b_post_diff, accuracy = 0.0001),
            comma(b_treat_diff, accuracy = 0.0001),
            comma(b_treat_x_time_diff, accuracy = 0.0001),
            comma(b_post_x_time_diff, accuracy = 0.0001),
            comma(b_post_x_time_x_treat_diff, accuracy = 0.0001)),
  col_5 = c(percent(b_time_diff / b_time, accuracy = 0.1),
            percent(b_post_diff / b_post, accuracy = 0.1),
            percent(b_treat_diff / b_treat, accuracy = 0.1),
            percent(b_treat_x_time_diff / b_treat_x_time, accuracy = 0.1),
            percent(b_post_x_time_diff / b_post_x_time, accuracy = 0.1),
            percent(b_post_x_time_x_treat_diff / b_post_x_time_x_treat, accuracy = 0.1))
) %>%
  kbl(escape = F,
      col.names = c("", "Estimates - Full Dataset", "Estimates - Bootstrap",
                    "Difference", "Difference as Proportion of Full Dataset"),
      align = c("l", rep("r", 4))) %>%
  kable_classic("striped")
```

* Assuming we are ok with these results, I'll move on to Table 3

## Table 3  



```{r}
tibble(
  col_1 = c("Control", "Treated", "Treated - Control"),
  col_2 = c(paste0("$\\beta_{time}=", 
                   comma(mean(tna_boot$b_time), accuracy = 0.001), "$"), 
            paste0("$\\beta_{time} + \\beta_{treat\\times time}=", 
                   comma(mean(tna_boot$b_time + tna_boot$b_treat_x_time), accuracy = 0.001), "$"), 
            paste0("$\\beta_{treat\\times time}=", 
                   comma(mean(tna_boot$b_treat_x_time), accuracy = 0.001), "$")),
  col_3 = c(paste0("$\\beta_{time}+\\beta_{post\\times time}=",
                   comma(mean(tna_boot$b_time + tna_boot$b_post_x_time), accuracy = 0.001), "$"),
            paste0("$\\beta_{time}+\\beta_{post\\times time} +$ \n  $\\beta_{post\\times time\\times treat}=",
                   comma(mean(tna_boot$b_time + tna_boot$b_post_x_time + tna_boot$b_post_x_time_x_treat), accuracy = 0.001), "$"),
            paste0("$\\beta_{post\\times time\\times treat}=",
                   comma(mean(tna_boot$b_post_x_time_x_treat), accuracy = 0.001), "$")),
  col_4 = c(paste0("$\\beta_{post\\times time}=",
                   comma(mean(tna_boot$b_post_x_time), accuracy = 0.001), "$"),
            paste0("$\\beta_{post\\times time} +$ \n $\\beta_{post\\times time\\times treat} -$\n$\\beta_{treat\\times time}=",
                   comma(mean(tna_boot$b_post_x_time + tna_boot$b_post_x_time_x_treat - tna_boot$b_treat_x_time), accuracy = 0.001), "$"),
            "")
) %>%
  kbl(escape = F,
      col.names = c("", "Pre Slope", "Post Slope", "Post - Pre"),
      align = c("l", rep("c", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```
