---
title: "Timely Care: Self-check"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(DBI)
library(here)
library(scales)
library(janitor)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
# ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  inner_join(., vast)
# #pulling vssc access metrics
# access_metrics <- dbGetQuery(oabi_con,
#                              "select * from [crh_eval].E2_VSSC_access_metrics") %>%
#   mutate(vssc_month = ymd(vssc_month)) %>%
#   left_join(timely_care)
# #making a time column
# dates <- tibble(
#   vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
#   arrange(vssc_month) %>%
#   rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PACT_CC].[econ].PatientPCP
#                             	where fy = 2018
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
# covariates <- dbGetQuery(oabi_con,
#                          "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
#   rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
#   mutate(vssc_month = ymd(vssc_month)) %>%
#   mutate(pct_male = male_count / scrssn_count * 100,
#          pct_white = race_white_count / scrssn_count * 100,
#          pct_rural = urh_rural_count / scrssn_count * 100) %>%
#   select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
#          avg_age_oct1_2022, sta5a, vssc_month, 
#          parent_visn, census_division,
#          nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
#          pcmm_count_fy_qtr,
#          adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
#          shep_access_metric)
#========
# gap_metric_1 <- dbGetQuery(oabi_con,
#                          "select * from [crh_eval].H_gap_metric") %>%
#   inner_join(., vast) %>%
#   mutate(obs_only_zero = if_else(observed_ps_tot == 0 & expected_ps_tot != 0, 1, 0),
#          exp_only_zero = if_else(expected_ps_tot == 0 & observed_ps_tot != 0, 1, 0),
#          both_zero = if_else(observed_ps_tot == 0 & expected_ps_tot == 0, 1, 0),
#          either_zero = if_else(observed_ps_tot == 0 | expected_ps_tot == 0, 1, 0))
# #
# gap_nas <- gap_metric_1 %>% filter(is.na(gap_metric))
# #
# gap_metric <- gap_metric_1 %>%
#   filter(gap_metric < 10
#          & gap_metric > 0)
```

```{r}
tc_summary <- timely_care %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum) %>%
  group_by(sta5a) %>%
  summarise(avg_val = mean(tc_pc_success_prop, na.rm = T),
            sd_val = sd(tc_pc_success_prop, na.rm = T),
            n_obs = n(),
            avg_reqs = mean(tc_requests_sum, na.rm = T),
            tot_reqs = sum(tc_requests_sum, na.rm = T)) %>%
  left_join(., vast)
```

# Front Matter  

## Description of this report  

* This is a self-check of the __Timely Care__ data  
* A brief refresher on what the Timely Care metric _is_:
    + A Timely Care $Request$ is when a patient requests an appointment to primary care as either a walk-in or a first next available
    + The denominator of the metric is the number of Timely Care $Requests$ made to primary care during a particular sta5a-month
    + And the numerator is the number of those that were seen __in primary care__ (i.e., $Successes$)
    + Putting these together we get the Timely Care metric:
    
$$
\text{Timely Care Success Rate} = \frac{\sum{Successes}}{\sum{Requests}}
$$

## Decision Points  

* In moving forward with the __post-COVID analysis__ we have discussed including several new metrics, including Timely Care
    
## Description of the data    

+ The first observation in the data occurs on `r min(timely_care$vssc_month)`
+ The last observation in the data occurs on `r max(timely_care$vssc_month)`
+ There are `r nrow(timely_care) %>% comma()` rows in the data
+ These rows come from `r timely_care %>% select(sta5a) %>% n_distinct() %>% comma()` sta5as 
    + `r timely_care %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
    + `r timely_care %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
    + `r timely_care %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS

    

```{r}

#---
ggplot(data = tc_summary,
         aes(x = reorder(sta5a, avg_val), 
             y = avg_val,
             ymin = avg_val - sd_val,
             ymax = avg_val + sd_val)) +
  geom_point() +
  geom_hline(yintercept = 1,
             lty = 2) +
  geom_errorbar(alpha = 0.5) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
  ggthemes::theme_clean() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(x = "Sta5a",
       y = "Average Timely Care Success +/- SD")
```

# Top 25     

```{r}
top_25 <- tc_summary %>%
  arrange(desc(avg_val)) %>%
  slice_head(., n = 25) %>%
  mutate(
    disp_val = paste0(
      percent(avg_val, accuracy = 0.1), " (",
      percent(sd_val, accuracy = 0.1), ")"
    ),
    disp_name = paste0(
      "(", sta5a, ") ",
      short_name
    ),
    avg_reqs = comma(avg_reqs, accuracy = 0.1),
    tot_reqs = comma(tot_reqs, accuracy = 1)) %>%
  select(parent_visn, disp_name, s_abbr, disp_val, n_obs, avg_reqs, tot_reqs)
#
top_25 %>%
  kbl(col.names = c("VISN", "(Sta5a) Division Name", "Site Type in VAST", "Average Timely Care PC Success % (SD)",
                    "Observations (i.e., months)", "Average TC Requests", "Total TC Requests"),
      align = c("c", "l", "c", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

# Bottom 15  

```{r}
bottom_15 <- tc_summary %>%
  arrange(desc(avg_val)) %>%
  slice_tail(., n = 15) %>%
  left_join(., vast) %>%
  mutate(
    disp_val = paste0(
      percent(avg_val, accuracy = 0.1), " (",
      percent(sd_val, accuracy = 0.1), ")"
    ),
    disp_name = paste0(
      "(", sta5a, ") ",
      short_name
    ),
    avg_reqs = comma(avg_reqs, accuracy = 0.1),
    tot_reqs = comma(tot_reqs, accuracy = 1)) %>%
  select(parent_visn, disp_name, s_abbr, disp_val, n_obs, avg_reqs, tot_reqs)
#
bottom_15 %>%
  kbl(col.names = c("VISN", "(Sta5a) Division Name", "Site Type in VAST", "Average Timely Care PC Success % (SD)",
                    "Observations (i.e., months)", "Average TC Requests", "Total TC Requests"),
      align = c("c", "l", "c", rep("r", 3))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```