---
title: "Missingness in PC CRH PS Matching Data"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month),
         tna_new_source = as.numeric(tna_new_source))
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-04-01"), ymd("2020-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
dates3 <- tibble(
  vssc_month = seq.Date(ymd("2020-07-01"), ymd("2020-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
#--
pc_community_care <- dbGetQuery(oabi_con,
                                 "select *
                                 from [OABI_MyVAAccess].[crh_eval].F5_avg_pc_cons_post_COVID")
```

```{r}
# a vector of sta5as that:
    #1. have at least 451 average unique scrssns in pcmm FY20
    #2. are a CBOC, OOS, VAMC, or HCC
sta5as_to_start_with <- vast %>%
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F
         & scrssn_count_cat != "< 450"
         & s_abbr %in% c("PCCBOC", "MSCBOC", "VAMC", "OOS", "HCC")) %>%
  select(sta5a, s_abbr, scrssn_count_cat)
#-----
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    (last_mo_mt9_pc_crh == 1 | next_mo_mt9_pc_crh == 1),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit = replace_na(meets_inc_crit, 0)) %>%#replacing NA with 0
  mutate(
    period_meeting_citeria = factor(case_when(
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month < ymd("2020-03-01") #AND month < march 2020
      ~ "Before March 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month >= ymd("2020-03-01")#AND month between March 2020
      & vssc_month <= ymd("2020-09-01") #AND September 2020
      ~ "Between March and September 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month > ymd("2020-09-01") #AND month > Setember 2020
      ~ "After September 2020",#label
      TRUE ~ "Not Enough PC CRH"),#ELSE
      ordered = TRUE,
      levels = c("Before March 2020", 
                 "Between March and September 2020",
                 "After September 2020",
                 "Not Enough PC CRH")))
#--
sta5a_month_inc <- months_meeting_inclusion_criteria %>%
  group_by(sta5a, period_meeting_citeria) %>%
  summarise(count = n()) %>%
  filter(period_meeting_citeria != "Not Enough PC CRH") %>%
  group_by(sta5a) %>%
  summarise(period1_inc = sum(if_else(period_meeting_citeria == "Before March 2020" & count > 1, 1, 0)),
            period2_inc = sum(if_else(period_meeting_citeria == "Between March and September 2020" & count > 1, 1, 0)),
            period3_inc = sum(if_else(period_meeting_citeria == "After September 2020" & count > 1, 1, 0)))
#--
cases_controls <- sta5as_to_start_with %>%
  left_join(., sta5a_month_inc) %>%
  mutate(across(contains("period"), ~replace_na(.x, 0)),
         not_enough_crh = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0 & sta5a %in% pen_rate$sta5a, 
                                  1, 0),
         potential_control = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0 & not_enough_crh == 0, 1, 0),
         ever_met_criteria = if_else(period1_inc == 1 | period2_inc == 1 | period3_inc == 1, 1, 0),
         treated = factor(case_when(period3_inc == 1 ~ "Treated",
                             potential_control == 1 ~ "Control",
                             TRUE ~ "Drop me!"),
                          ordered = T, 
                          levels = c("Treated", "Control", "Drop me!"))) %>%
  filter(treated != "Drop me!")
#--average values of outcomes over April through September
outcomes_df <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates %>%
               select(-time)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source, 
                     new_0_20_days_create, panel_fullness)) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  summarise(avg_val = mean(value, na.rm = T)) %>%
  pivot_wider(names_from = name, values_from = avg_val)
#--average values of covariates over July, August, September
covars_df <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates3 %>%
               select(-time)) %>%
  left_join(., covariates) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  select(-parent_visn, -census_division, -pc_crh_per_1k_total_pc) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  summarise(avg_val = mean(value, na.rm = T)) %>%
  pivot_wider(names_from = name, values_from = avg_val) %>%
  left_join(., vast %>%
              select(sta5a, parent_visn, s_abbr, census_division)) %>%
  left_join(., cases_controls %>%
              select(sta5a, treated)) %>%
  mutate(across(contains("pct_"), ~.x / 100))
#=====
analytic_df <- outcomes_df %>%
  left_join(., covars_df) %>%
  left_join(., pc_community_care %>%
              rename(sta5a = sta6a) %>%
              select(sta5a, non_va_cons_rate_per_10k_pcmm))
```

# Front Matter  

## Description of this report  

* This is a look at the missingness and combinations of missingness in the Propensity Score Matching data
* I also make a detour to discuss alternative ideas for a PC Community Care covariate 

## Decision Points  

* Per our discussion on November 21st I am investigating what column(s), or combination of columns, in our Propensity Score matching data are responsible for the most missingness

    
## Analytic details  


* Description of the data:
    + The first observation in the data occurs on `r min(dates$vssc_month)`
    + The last observation in the data occurs on `r max(dates$vssc_month)`
    + Outcome values are averaged over all 6 months
    + All other covariates are averaged over the 4th quarter of FY2020 (i.e., July, August, and September of CY2020)
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + There are `r analytic_df %>% select(sta5a) %>% n_distinct()` unique sta5as
      + `r sum(analytic_df$treated == "Treated")` of these met our criteria for PC CRH at least once after September 2020  
      + `r sum(str_detect(analytic_df$s_abbr, "CBOC") == T)` of these are CBOCs
      + `r sum(str_detect(analytic_df$s_abbr, "HCC|VAMC") == T)` of these are HCCs or VAMCs
      + `r sum(str_detect(analytic_df$s_abbr, "OOS") == T)` of these are OOS    
    + Treated sta5as are the `r sum(analytic_df$treated == "Treated")` sta5as that __met our inclusion criteria after September 2020__ 
    + Control sta5as are the `r sum(analytic_df$treated != "Treated")` sta5as that have __never had a PC CRH encounter__




# Missingness  

```{r}
naniar::gg_miss_upset(analytic_df)
```

<!-- ## Without PC Consult Rate   -->

<!-- ```{r} -->
<!-- analytic_df %>% select(-non_va_cons_rate_per_10k_pcmm) %>% naniar::gg_miss_upset(.) -->
<!-- ``` -->

# Complete Data For Summary?  
* It occurrred to me to investigate how any sta5as have complete data for the summary data. I.e., what proportion of sta5as had 6 months of non-missing data for outcomes and 3 months of non-missing data for all other covariates

```{r}
outcomes_no_summary <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates %>%
               select(-time)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source, 
                     new_0_20_days_create, panel_fullness)) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  pivot_longer(-c(sta5a, vssc_month))
#
outcomes_no_summary %>% group_by(sta5a, name) %>%
  summarise(missing_count = sum(is.na(value))) %>%
  ggplot(data = .,
         aes(x = missing_count)) +
  geom_histogram(bins = 7) +
  facet_wrap(~name) +
  labs(x = "Number of Months Without Data",
       y = "Number of Sta5as in Column")
```

```{r alternative_cc}
community_care_no_summary <- cases_controls %>%
  cross_join(dates3) %>%
  select(sta5a, vssc_month) %>%
  left_join(., dbGetQuery(oabi_con,
                          "select sum(non_va) as non_va_cons, sta5a = sta6a
	, vssc_month = DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01')
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where stopCode_group = 'Primary Care'
	AND MONTH(activityDateTime) IN(7, 8, 9)
	AND year(activityDateTime) = 2020
group by Sta6a, DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01')") %>%
  mutate(vssc_month = ymd(vssc_month))) %>%
  mutate(non_va_cons_na = non_va_cons,
         non_va_cons = replace_na(non_va_cons, 0))
```

```{r}
covariates_no_summary <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates3 %>%
               select(-time)) %>%
  left_join(., covariates) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  select(-parent_visn, -census_division, -pc_crh_per_1k_total_pc) %>%
  left_join(., community_care_no_summary %>%
              select(sta5a, vssc_month, non_va_cons_na)) %>%
  pivot_longer(-c(sta5a, vssc_month))
#--
covariates_no_summary %>% group_by(sta5a, name) %>%
  summarise(missing_count = sum(is.na(value))) %>%
  ggplot(data = .,
         aes(x = missing_count)) +
  geom_histogram(bins = 7) +
  facet_wrap(~name) +
  labs(x = "Number of Months Without Data",
       y = "Number of Sta5as in Column")
```

# Alternative Community Care Covariate   
* Out of a total of `r nrow(community_care_no_summary) %>% comma()` observations/sta5a-months, there are `r community_care_no_summary %>% filter(non_va_cons >0) %>% nrow()` (`r ((community_care_no_summary %>% filter(non_va_cons >0) %>% nrow()) / nrow(community_care_no_summary)) %>% percent(accuracy = 0.1)`) that have at least 1 non-VA PC consult
* The average number of consults is `r mean(community_care_no_summary$non_va_cons) %>% comma(accuracy = 0.1)`
* The average number of consults __without zeroes__ is `r mean(community_care_no_summary$non_va_cons_na, na.rm = T) %>% comma(accuracy = 0.1)`


```{r}
bp_all <- community_care_no_summary %>%
  ggplot(data = .,
         aes(y = non_va_cons)) +
  geom_boxplot(fill = "dodgerblue") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Consults per Sta5a-Month")
#--
bp_no0 <- community_care_no_summary %>%
  filter(non_va_cons > 0) %>%
  ggplot(data = .,
         aes(y = non_va_cons)) +
  geom_boxplot(fill = "darkorchid") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Consults per Sta5a-Month (no 0)")
#--
hp_all <- community_care_no_summary %>%
  ggplot(data = .,
         aes(x = non_va_cons)) +
  geom_histogram(fill = "dodgerblue",
                 color = "black",
                 bins = 50) +
  labs(x = "Consults per sta5a-month",
       y = "Observations") +
  scale_y_continuous(labels = comma_format())
#--
hp_no0 <- community_care_no_summary %>%
  filter(non_va_cons > 0) %>%
  ggplot(data = .,
         aes(x = non_va_cons)) +
  geom_histogram(fill = "darkorchid",
                 color = "black",
                 bins = 50) +
  labs(x = "Consults per sta5a-month (no 0)",
       y = "Observations") +
  scale_y_continuous(labels = comma_format())
#==
multiplot(bp_all, bp_no0, hp_all, hp_no0, cols = 2)

```

```{r}
bp_all <- community_care_no_summary %>%
  ggplot(data = .,
         aes(y = non_va_cons)) +
  geom_boxplot(fill = "dodgerblue") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Consults per Sta5a-Month") +
  scale_y_continuous(limits = c(0, 50))
#--
bp_no0 <- community_care_no_summary %>%
  filter(non_va_cons > 0) %>%
  ggplot(data = .,
         aes(y = non_va_cons)) +
  geom_boxplot(fill = "darkorchid") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(y = "Consults per Sta5a-Month (no 0)") +
  scale_y_continuous(limits = c(0, 50))
#--
hp_all <- community_care_no_summary %>%
  ggplot(data = .,
         aes(x = non_va_cons)) +
  geom_histogram(fill = "dodgerblue",
                 color = "black",
                 bins = 50) +
  labs(x = "Consults per sta5a-month",
       y = "Observations") +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(limits = c(-1, 50))
#--
hp_no0 <- community_care_no_summary %>%
  filter(non_va_cons > 0) %>%
  ggplot(data = .,
         aes(x = non_va_cons)) +
  geom_histogram(fill = "darkorchid",
                 color = "black",
                 bins = 50) +
  labs(x = "Consults per sta5a-month (no 0)",
       y = "Observations") +
  scale_y_continuous(labels = comma_format()) +
  scale_x_continuous(limits = c(0, 50))
#==
multiplot(bp_all, bp_no0, hp_all, hp_no0, cols = 2)
```

## Making Cutoffs at 0, 5, and 10 Consults per month  

```{r}
categorical_community_care <- community_care_no_summary %>%
  mutate(mt_0 = if_else(non_va_cons > 0, 1, 0),
         mt_4 = if_else(non_va_cons > 4, 1, 0),
         mt_9 = if_else(non_va_cons > 9, 1, 0)) %>%
  group_by(sta5a) %>%
  summarise(mt_0 = sum(mt_0),
            mt_4 = sum(mt_4),
            mt_9 = sum(mt_9))
```



### At least 1  
* There are `r sum(categorical_community_care$mt_0 != 0)` sta5as that have at least 1 month with 1 or more PC community care consults


```{r}
ggplot(data = categorical_community_care,
         aes(x = mt_0)) +
  geom_histogram(bins = 4,
                 color = "black") +
  scale_x_continuous(breaks = c(0, 1, 2, 3)) +
  labs(x = "Months with > 0 Community Care Consults",
       y = "Sta5as in Column")
```


### At least 5   
* There are `r sum(categorical_community_care$mt_4 != 0)` sta5as that have at least 1 month with 5 or more PC community care consults
```{r}
ggplot(data = categorical_community_care,
         aes(x = mt_4)) +
  geom_histogram(bins = 4,
                 color = "black") +
  scale_x_continuous(breaks = c(0, 1, 2, 3)) +
  labs(x = "Months with > 4 Community Care Consults",
       y = "Sta5as in Column")
```

### At least 10   
* There are `r sum(categorical_community_care$mt_9 != 0)` sta5as that have at least 1 month with 10 or more PC community care consults
```{r}
ggplot(data = categorical_community_care,
         aes(x = mt_9)) +
  geom_histogram(bins = 4,
                 color = "black") +
  scale_x_continuous(breaks = c(0, 1, 2, 3)) +
  labs(x = "Months with > 9 Community Care Consults",
       y = "Sta5as in Column")
```