---
title: "A \"first look\" at propensity-score matching in post-COVID"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 15, fig.height = 15)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 10),
             strip.text = element_text(size = 10),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month),
         tna_new_source = as.numeric(tna_new_source)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(this_mo_mt9_pcCRH = if_else(crh_encounter_count > 9, 1, 0),
         next_mo_mt9_pcCRH = if_else(lead(crh_encounter_count, 1) > 9, 1, 0),
         meets_inclusion_criteria = if_else(this_mo_mt9_pcCRH == 1
                                            & next_mo_mt9_pcCRH == 1, 1, 0)) %>%
  filter(meets_inclusion_criteria == 1) %>%
  complete(vssc_month = seq(min(vssc_month), ymd("2022-12-01"), by = "month")) %>%
  mutate(rowNum = row_number()) %>%
  select(sta5a, vssc_month, crh_encounter_count, meets_inclusion_criteria, rowNum)
#---
all_crh_sta5a <- months_meeting_inclusion_criteria %>% 
  filter(meets_inclusion_criteria == 1) %>%
  select(sta5a) %>%
  distinct
#
met_criteria_after_sept_20 <- months_meeting_inclusion_criteria %>%
  filter(vssc_month > ymd("2020-09-01")
         & meets_inclusion_criteria == 1) %>%
  select(sta5a) %>%
  distinct()
#
any_pc_crh <- pen_rate %>%
  filter(is.na(crh_encounter_count) == F) %>%
  select(sta5a) %>%
  distinct
#
not_enough_crh <- any_pc_crh %>%
  filter(sta5a %ni% met_criteria_after_sept_20$sta5a)
```

```{r analytic_df}
outcomes_avg <- access_metrics %>%
  select(-starts_with("tc_")) %>%
  left_join(., timely_care) %>%
  filter(vssc_month >= ymd("2020-04-01")
         & vssc_month <= ymd("2020-09-01")) %>%
  select(sta5a, 
         est_pc_pt_wt_pid,
         new_pc_pt_wt_create,
         tna_new_source,
         tc_pc_success_prop,
         new_0_20_days_create) %>%
  group_by(sta5a) %>%
  summarise(across(where(is.numeric), ~mean(.x, na.rm = T)))
#======
covariates_avg <- covariates %>%
  filter(vssc_month >= ymd("2020-07-01")
         & vssc_month <= ymd("2020-09-01")) %>%
  select(sta5a,
         nosos_risk_score,
         obs_exp_panel_ratio,
         team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg,
         avg_age_oct1_2022,
         pct_male,
         pct_white,
         pct_rural) %>%
  group_by(sta5a) %>%
  summarise(across(where(is.numeric), ~mean(.x, na.rm = T)))
#=======
sta5as_to_include <- vast %>%
  left_join(., scrssn_count) %>%
  filter(scrssn_count_cat != "< 450"
         & is.na(scrssn_count_cat) == F)
#========
analytic_df <- sta5as_to_include %>%
  left_join(., outcomes_avg) %>%
  left_join(., covariates_avg)
```




# What Covariates have we considered?  

* The longest list of potential covariates I found in my archive includes 17 items:
    -   Parent VISN
    -   Pilot VISN 
    -   Census Division
    -   Site Type
    -   NOSOS 
    -   Observed:Expected PC Panel Size 
    -   Team PCP/AP FTE 
    -   Uniques in PCMM 
    -   Established patient wait time  (__outcome__)
    -   New patient wait time (__outcome__)
    -   Third next available (__outcome__)
    -   ADI 
    -   Average age October 1st, 2022
    -   Proportion male 
    -   Proportion white 
    -   Proportion rural 
    -   Gap Metric (__effect modifier__)

* We are also adding 2 outcomes to the list:
    -   Timely Care 
    -   0/1 at least 80% of new patients seen in 0-20 days
    
* We have also discussed adding __PC Panel Fullness__


# What timeframes for matching have considered?  

* Last we discussed this I made the document _crh_sta5as_when_and_how_much.html_
* In that document I presented 3 periods of interest:
    + Before March 2020
    + Between March 2020 and September 2020 (inclusive)
    + After September 2020
    
* Per our Pre-COVID analysis, we would like:
    + A 6-month window for matching outcomes (i.e., average each outcome for each sta5a during those 6 months and match on that value)
    + A 3-month window for matching everything else

# Correlations between continuous variables     

```{r}
foo_plot <- GGally::ggpairs(analytic_df %>% select(-c(1:11, 13)))
#
foo_plot
```