---
title: "PS Matching version 5.2: 0 CRH Encounters Among Controls"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
#Input\Analytic df\F2_propensity_score_matching\propensity_score_matching_v3_1.R"

source(here("Input", "Analytic df", "F2_propensity_score_matching","propensity_score_matching_v5_2_tna_only.R"))
#---
pilot_sites <- dbGetQuery(oabi_con,
                          "select distinct spoke_sta5a as sta5a
                            from [PACT_CC].[CRH].[CRH_sites_FY20_working]
                          where vimpact_pilot = 1") %>%
  pull
#--
sta5a_demog_no_missing <- sta5a_demog_no_missing %>%
  mutate(pilot_site = if_else(sta5a %in% pilot_sites, 1, 0))
```




# Dropped stations  
* From a starting set of `r sta5a_demog %>% nrow() %>% comma()` candidate sta5as, we drop  `r sta5a_demog %>% nrow() - sta5a_demog_no_missing %>% nrow()` sta5as that:
    + Have fewer than 450 uniques in PCMM (`r sta5a_demog %>% drop_na() %>% filter(pcmm_scrssn_count <= 450) %>% nrow()`)
    + Had more than 0 PC CRH encounters before March 2020 but not enough to meet our inclusion criteria (`r sta5a_demog %>% drop_na() %>% filter(not_enough_crh_before_march_20 == 1) %>% nrow()`)

# Overlap With PS v5.1  

```{r}
ps_match_5_1 <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_1_noCRH_among_controls.csv")) %>%
  filter(at_least_10_pc_crh_flag == 0)
ps_match_5_2 <- read_csv(here("Input","Data", "ps_matched_sta5as_v5_2.csv")) %>%
  filter(at_least_10_pc_crh_flag == 0)
#=====
```

* Only `r sum(ps_match_5_1$sta5a %in% ps_match_5_2$sta5a)` out of `r nrow(ps_match_5_1)` (`r (sum(ps_match_5_1$sta5a %in% ps_match_5_2$sta5a) / nrow(ps_match_5_1)) %>% percent(accuracy = 0.1)`) control sta5as in this PS match are the same as in version 5.1  

# Propensity Score "Optimal" Matching


## Final Model    

-   Using [Optimal Matching](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html#optimal-pair-matching-method-optimal) we get `r nrow(opt_matches_pcmm_wVISN) / 2` pairs from a starting set of `r sum(sta5a_demog_no_missing$at_least_10_pc_crh_flag)` __Treated__ sta5as
    - `r sum(sta5a_demog_no_missing$pilot_site == 1 & sta5a_demog_no_missing$at_least_10_pc_crh_flag == 1)` of these are pilot sites
    - Controls are those sta5as that had 0 CRH encounters by March 2020

-   Model: Treatment (i.e., at least two consecutive months with \>9 PC CRH encounters) =

    -   ~~NOSOS (FY18 Q4 Avg)~~
    -   Observed:Expected PC Panel Size (FY18 Q4 Avg)
    -   Team PCP/AP FTE (FY18 Q4 Avg)
    -   Uniques in PCMM (FY18 Q4)
    -   ~~ADI (FY18 Q4)~~
    -   Proportion rural (FY18 Q4)
    -   (Non-VA PCCC Consults / Total PCCC Consults) X (uniques in PCMM) X 10,000 (FY18 Q4 Avg)
    -   Third Next Available PC Appointment (FY19 Avg)
    -   ~~Established Patient Waittime (FY19 Avg)~~
    -   ~~New Patient Waittime (FY19 Avg)~~
    -   VISN (Exact)
    -   Site Type (i.e., CBOC, VAMC/HCC, or OOS) - (Exact)

-   We estimate the propensity score with logistic regression (i.e., GLM and logit link)
- [Absolute standardized mean difference:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,3], 3)` 
- [Variance ratio:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,4], 3)`
- [Empirical CDF:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) 
    - Mean: `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,5], 2)`
    - Max: `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,6], 2)`

```{r}
plot(opt_match_pcmm_wVISN, type = "jitter", interactive = FALSE)
```


```{r}
ps_plot_df_pcmm <- tibble(
  covariate = attributes(summary(opt_match_pcmm_wVISN)$sum.all)$dimnames[[1]], 
  smd_matched = summary(opt_match_pcmm_wVISN)$sum.matched[,3], 
  smd_preMatch = summary(opt_match_pcmm_wVISN)$sum.all[,3]) %>%
  mutate(covariate = str_remove(covariate, "s_abbr2|census_division|pilot_visn_flag"),
         covariate = str_replace(covariate, "parent_visn", "V"),
         covar_lab = factor(case_when(
           covariate == "distance" ~ "Distance",
           #str_detect(covariate, "PCCBOC") == TRUE ~ "PCCBOC",
           str_detect(covariate, "HCC") == TRUE ~ "VAMC/HCC",
           #str_detect(covariate, "VAMC") == TRUE ~ "VAMC",
           #str_detect(covariate, "MSCBOC") == TRUE ~ "MSCBOC",
           str_detect(covariate, "CBOC") == TRUE ~ "CBOC",
           str_detect(covariate, "OOS") == TRUE ~ "OOS",
           str_detect(covariate, "nosos") == TRUE ~ "NOSOS",
           str_detect(covariate, "obs_exp") == TRUE ~ "Obs:Exp",
           str_detect(covariate, "team") == TRUE ~ "PCP/AP FTE",
           str_detect(covariate, "pcmm_") == TRUE ~ "PCMM ScrSSN Count",
           str_detect(covariate, "est_") == TRUE ~ "Established Patient WT",
           str_detect(covariate, "new_") == TRUE ~ "New Patient WT",
           str_detect(covariate, "third_") == TRUE ~ "Third-Next Available",
           str_detect(covariate, "adi") == TRUE ~ "ADI, Avg",
           str_detect(covariate, "age") == TRUE ~ "Age, Avg",
           str_detect(covariate, "male") == TRUE ~ "Male %",
           str_detect(covariate, "white") == TRUE ~ "White %",
           str_detect(covariate, "rural") == TRUE ~ "Rural %",
           str_detect(covariate, "gap") == TRUE ~ "Gap Metric",
           str_detect(covariate, "non_va") == TRUE ~ "Non-VA Consults per 10,000 in PCMM",
           TRUE ~ covariate
         ), ordered = TRUE, levels = rev(c("Distance","Not a Pilot VISN",
                                       "Pilot VISN","NOSOS","Obs:Exp","PCP/AP FTE",
                                       "PCMM ScrSSN Count", "Rural %", "ADI, Avg",
                                       "Non-VA Consults per 10,000 in PCMM",
                                       "Third-Next Available", "New Patient WT", 
                                       "Established Patient WT", "VAMC/HCC", "CBOC",
                                       "HCC", "VAMC", "OOS",
                                       "MSCBOC", "PCCBOC", "V01", "V02", "V04", "V05",
                                       "V06", "V07", "V08", "V09", "V10", "V12", "V15",
                                       "V16", "V17", "V19", "V20", "V21", "V22", "V23")))) %>%
  select(-covariate) %>%
  pivot_longer(-covar_lab) %>%
  mutate(abs_smd = abs(value),
         name_lab = if_else(name == "smd_matched", "Matched", "Un-Matched"))
#
ggplot(data = ps_plot_df_pcmm,
       aes(x = abs_smd, y = covar_lab, group = name_lab, fill = name_lab)) +
  geom_point(shape = 21,
             size = 2.25) +
  scale_fill_manual(values = c(
    "Matched" = "black",
    "Un-Matched" = "white"
  )) +
  labs(x = "Absolute Standardized Mean Difference") +
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept = 0, lty = 1) +
  geom_vline(xintercept = 0.05, lty = 2) +
  geom_vline(xintercept = 0.1, lty = 1)
```



```{r}
dates <- tibble(
  vssc_month = seq.Date(ymd("2018-10-01"),
                  ymd("2020-02-01"),
                  "1 month")) %>%
  rownames_to_column(var = "time") %>%
  mutate(time = str_pad(time,
                        side = "left",
                        pad = "0",
                        width = 2))

```

# Let's look at outcomes  

```{r}
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  filter(vssc_month >= ymd("2018-10-01")
         & vssc_month <= ymd("2020-02-01")) %>%
  inner_join(., opt_matches_pcmm_wVISN) %>%
  mutate(crh_flag = if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "Control"))
```




## Third Next Available    
```{r}
access_metrics %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(mean_val = mean(third_next_avail, na.rm = T),
            sd_val = sd(third_next_avail, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, group = crh_flag, color = crh_flag,
             y = mean_val,
             ymin = mean_val - sd_val,
             ymax = mean_val + sd_val)) +
  geom_point(position = position_dodge(width = 1)) +
  geom_line() +
  geom_errorbar(position = position_dodge(width = 1)) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Mean +/- SD")
```

```{r}
access_metrics %>%
  select(vssc_month, third_next_avail, crh_flag) %>% 
  left_join(dates) %>%
  ggplot(data = .,
         aes(x = time, y = third_next_avail, fill = crh_flag)) +
  geom_boxplot(position = position_dodge()) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = "Third Next Available (days)",
       x = "Month",
       caption = "*Removed 9 observations with values > 100")
```