---
title: "PS Match: Post COVID"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month),
         tna_new_source = as.numeric(tna_new_source))
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-04-01"), ymd("2020-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
dates3 <- tibble(
  vssc_month = seq.Date(ymd("2020-07-01"), ymd("2020-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
# a vector of sta5as that:
    #1. have at least 451 average unique scrssns in pcmm FY20
    #2. are a CBOC, OOS, VAMC, or HCC
sta5as_to_start_with <- vast %>%
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F
         & scrssn_count_cat != "< 450"
         & s_abbr %in% c("PCCBOC", "MSCBOC", "VAMC", "OOS", "HCC")) %>%
  select(sta5a, s_abbr, scrssn_count_cat)
#-----
months_meeting_inclusion_criteria <- pen_rate %>%
  arrange(sta5a, vssc_month) %>%#ordering by station and month
  group_by(sta5a) %>%#grouping by station
  mutate(this_mo_mt9_pc_crh = if_else(crh_encounter_count > 9, 1, 0),#flag for this month meeting criteria 
         last_mo_mt9_pc_crh = if_else(lag(crh_encounter_count) > 9, 1, 0),#flag for last month
         next_mo_mt9_pc_crh = if_else(lead(crh_encounter_count) > 9, 1, 0),#flag for next month
         meets_inc_crit = if_else(this_mo_mt9_pc_crh == 1 & # IF this month meets criteria
                                    (last_mo_mt9_pc_crh == 1 | next_mo_mt9_pc_crh == 1),#AND either this or last month
                                  1, 0),#THEN 1, ELSE 0
         meets_inc_crit = replace_na(meets_inc_crit, 0)) %>%#replacing NA with 0
  mutate(
    period_meeting_citeria = factor(case_when(
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month < ymd("2020-03-01") #AND month < march 2020
      ~ "Before March 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month >= ymd("2020-03-01")#AND month between March 2020
      & vssc_month <= ymd("2020-09-01") #AND September 2020
      ~ "Between March and September 2020",#label
      meets_inc_crit == 1 #IF meets criteria
      & vssc_month > ymd("2020-09-01") #AND month > Setember 2020
      ~ "After September 2020",#label
      TRUE ~ "Not Enough PC CRH"),#ELSE
      ordered = TRUE,
      levels = c("Before March 2020", 
                 "Between March and September 2020",
                 "After September 2020",
                 "Not Enough PC CRH")))
#--
sta5a_month_inc <- months_meeting_inclusion_criteria %>%
  group_by(sta5a, period_meeting_citeria) %>%
  summarise(count = n()) %>%
  filter(period_meeting_citeria != "Not Enough PC CRH") %>%
  group_by(sta5a) %>%
  summarise(period1_inc = sum(if_else(period_meeting_citeria == "Before March 2020" & count > 1, 1, 0)),
            period2_inc = sum(if_else(period_meeting_citeria == "Between March and September 2020" & count > 1, 1, 0)),
            period3_inc = sum(if_else(period_meeting_citeria == "After September 2020" & count > 1, 1, 0)))
#--
cases_controls <- sta5as_to_start_with %>%
  left_join(., sta5a_month_inc) %>%
  mutate(across(contains("period"), ~replace_na(.x, 0)),
         not_enough_crh = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0 & sta5a %in% pen_rate$sta5a, 
                                  1, 0),
         potential_control = if_else(period1_inc == 0 & period2_inc == 0 & period3_inc == 0, 1, 0),#CHANGE ME!
         ever_met_criteria = if_else(period1_inc == 1 | period2_inc == 1 | period3_inc == 1, 1, 0),
         treated = factor(case_when(period3_inc == 1 ~ "Treated",
                             potential_control == 1 ~ "Control",
                             TRUE ~ "Drop me!"),
                          ordered = T, 
                          levels = c("Treated", "Control", "Drop me!"))) %>%
  filter(treated != "Drop me!")
#--
community_care_no_summary <- cases_controls %>%
  cross_join(dates3) %>%
  select(sta5a, vssc_month) %>%
  left_join(., dbGetQuery(oabi_con,
                          "select sum(non_va) as non_va_cons, sta5a = sta6a
	, vssc_month = DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01')
from [OABI_MyVAAccess].[crh_eval].G_communityCare_referrals
where stopCode_group = 'Primary Care'
	AND MONTH(activityDateTime) IN(7, 8, 9)
	AND year(activityDateTime) = 2020
group by Sta6a, DATEFROMPARTS(year(activityDateTime), month(activityDateTime), '01')") %>%
  mutate(vssc_month = ymd(vssc_month))) %>%
  mutate(non_va_cons_na = non_va_cons,
         non_va_cons = replace_na(non_va_cons, 0),
         mt_4_flag = if_else(non_va_cons > 4, 1, 0)) %>%
  group_by(sta5a) %>%
  summarise(mt_4_pc_cc_flag = if_else(sum(mt_4_flag) > 0, 1, 0))
#--average values of outcomes over July, August, September
outcomes_df <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates3 %>%
               select(-time)) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source, 
                     new_0_20_days_create, panel_fullness)) %>%
  left_join(., timely_care %>%
              select(sta5a, vssc_month, tc_pc_success_prop)) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  summarise(avg_val = mean(value, na.rm = T)) %>%
  pivot_wider(names_from = name, values_from = avg_val)
#--average values of covariates over July, August, September
covars_df <- cases_controls %>%
  select(sta5a) %>%
  cross_join(., dates3 %>%
               select(-time)) %>%
  left_join(., covariates) %>%
  left_join(., gap_metric %>%
              select(sta5a, vssc_month, gap_metric)) %>%
  select(-parent_visn, -census_division, -pc_crh_per_1k_total_pc) %>%
  pivot_longer(-c(sta5a, vssc_month)) %>%
  group_by(sta5a, name) %>%
  summarise(avg_val = mean(value, na.rm = T)) %>%
  pivot_wider(names_from = name, values_from = avg_val) %>%
  left_join(., vast %>%
              select(sta5a, parent_visn, s_abbr, census_division)) %>%
  left_join(., cases_controls %>%
              select(sta5a, treated)) %>%
  mutate(across(contains("pct_"), ~.x / 100))
#=====
analytic_df <- outcomes_df %>%
  left_join(., covars_df) %>%
  left_join(., community_care_no_summary) %>%
  select(-avg_driveDist,
         -new_0_20_days_create,
         -obs_exp_panel_ratio,
         -gap_metric,
         -pcmm_count_fy_qtr) %>%
  left_join(., scrssn_count %>%
              select(sta5a, scrssn_count_cat)) %>%
  mutate(s_abbr2 = if_else(str_detect(s_abbr, "CBOC"), "CBOC", s_abbr))
#--
analytic_df_no_missing <- analytic_df %>%
  drop_na() %>%
  mutate(treated_num = if_else(treated == "Treated", 1, 0))
```

# Front Matter  

## Description of this report  

* This is fourth iteration of the __Post-COVID Propensity Score Match__

## Decision Points

* Per our discussion on December 12th I am presenting propensity score model #1

    
## Analytic details  


* Description of the data:
    + The first observation in the data occurs on `r min(dates3$vssc_month)`
    + The last observation in the data occurs on `r max(dates3$vssc_month)`
    + Outcome values are averaged over the 4th quarter of FY2020 (i.e., July, August, and September of CY2020)
    + Covariate values are averaged over the 4th quarter of FY2020 (i.e., July, August, and September of CY2020)
    + There are `r nrow(analytic_df_no_missing) %>% comma()` rows in the data
    + The `r nrow(analytic_df) - nrow(analytic_df_no_missing)` fewer sta5as comes from missing covariate values
    + There are `r analytic_df_no_missing %>% select(sta5a) %>% n_distinct()` unique sta5as
      + `r sum(analytic_df_no_missing$treated == "Treated")` of these met our criteria for PC CRH after September 2020  
      + `r sum(str_detect(analytic_df_no_missing$s_abbr, "CBOC") == T)` of these are CBOCs
      + `r sum(str_detect(analytic_df_no_missing$s_abbr, "HCC|VAMC") == T)` of these are HCCs or VAMCs
      + `r sum(str_detect(analytic_df_no_missing$s_abbr, "OOS") == T)` of these are OOS    
    + Treated sta5as are the `r sum(analytic_df_no_missing$treated == "Treated")` sta5as that __met our inclusion criteria after September 2020__ 
    + Control sta5as are the `r sum(analytic_df_no_missing$treated != "Treated")` sta5as that have __never met our inclusion criteria__



```{r}
ps_match <- matchit(treated_num ~ 
                      est_pc_pt_wt_pid
                    + new_pc_pt_wt_create
                    + tc_pc_success_prop
                    + tna_new_source
                    + panel_fullness
                    + adi_natRnk_avg
                    + avg_age_oct1_2022
                    + nosos_risk_score
                    + scrssn_count_cat 
                    + pct_male
                    + pct_rural
                    + pct_white
                    + shep_access_metric
                    + team_pcp_ap_fte_total
                    + parent_visn
                    + s_abbr2
                    + mt_4_pc_cc_flag
                      ,
                    data = analytic_df_no_missing,
                    exact = ~s_abbr2,
                    method = "nearest",
                    replace = TRUE,
                    distance = "glm",
                    link = "logit",
                    ratio = 3)
#=====
ps_matched_sites <- match.data(ps_match) %>%
  select(sta5a, treated_num, weights, distance) %>%
  left_join(., analytic_df %>%
              select(sta5a, treated)) %>%
  left_join(., cases_controls %>%
              select(sta5a, period1_inc, period2_inc, period3_inc))
```

## Writing The Match & Weights to a .csv  
```{r class.source = 'fold-show'}
#--outputting .csv with sta5a, treated, and weights
write_csv(ps_matched_sites,
          here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
```

# Propensity Score Match      

-   Using [Nearest Neighbor](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html#nearest-neighbor-matching-method-nearest) we matched all `r sum(ps_matched_sites$treated == "Treated")` __Treated__ sta5as 
    - I asked for 3:1 matching __with replacement__
    - `r sum(ps_matched_sites$treated != "Treated")` control sites were matched 

-   Model: Treatment (i.e., at least two consecutive months with \>9 PC CRH encounters after September 2020) =

    -   Established Patient Wait Time (PID)
    -   New Patient Wait Time (Create)
    -   Timely Care
    -   Third Next Available
    -   Panel Fullness
    -   ADI
    -   Average Age
    -   Nosos
    -   Uniques in PCMM (categorical)
    -   Male %
    -   Rural %
    -   White %
    -   SHEP Access Composite
    -   Team PCP/AP FTE
    -   VISN 
    -   Site Type (exact)
    -   At least one month in Q4FY20 with > 4 PC Community Care Referrals

-   We estimate the propensity score with logistic regression (i.e., GLM and logit link)
- [Absolute standardized mean difference:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(ps_match)$sum.matched[1,3], 3)` 
- [Variance ratio:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(ps_match)$sum.matched[1,4], 3)`
- [Empirical CDF:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) 
    - Mean: `r round(summary(ps_match)$sum.matched[1,5], 2)`
    - Max: `r round(summary(ps_match)$sum.matched[1,6], 2)`

```{r}
plot(ps_match, type = "jitter", interactive = FALSE)
```

```{r}
tibble(
  covariate = attributes(summary(ps_match)$sum.all)$dimnames[[1]], 
  smd_matched = summary(ps_match)$sum.matched[,3], 
  smd_preMatch = summary(ps_match)$sum.all[,3]) %>%
  mutate(covar_lab = 
           case_when(
             covariate == "distance" ~ "Distance",
             covariate == "est_pc_pt_wt_pid" ~ "Established Pt WT",
             covariate == "new_pc_pt_wt_create" ~ "New Pt WT",
             covariate == "tc_pc_success_prop" ~ "Timely Care",
             covariate == "tna_new_source" ~ "Third Next Available",
             covariate == "panel_fullness" ~ "Panel Fullness",
             covariate == "adi_natRnk_avg" ~ "ADI",
             covariate == "avg_age_oct1_2022" ~ "Average Age",
             covariate == "gap_metric" ~ "Gap Metric",
             covariate == "nosos_risk_score" ~ "Nosos",
             covariate == "pcmm_count_fy_qtr" ~ "Uniques in PCMM",
             covariate == "pct_male" ~ "Male %",
             covariate == "pct_rural" ~ "Rural %",
             covariate == "pct_white" ~ "White %",
             covariate == "shep_access_metric" ~ "SHEP Access Composite",
             covariate == "team_pcp_ap_fte_total" ~ "Team PCP/AP FTE",
             covariate == "mt_4_pc_cc_flag" ~ "PC Community Care",
             covariate == "s_abbr2CBOC" ~ "CBOC",
             covariate == "s_abbr2HCC" ~ "HCC",
             covariate == "s_abbr2OOS" ~ "OOS",
             covariate == "s_abbr2VAMC" ~ "VAMC",
             covariate == "scrssn_count_cat450 - 2,399" ~ "450 - 2,399",
             covariate == "scrssn_count_cat2,400 - 9,999" ~ "2,400 - 9,999",
             covariate == "scrssn_count_cat10,000+" ~ "10,000+",
             str_detect(covariate, "parent_visn") == T ~ str_c("V", str_remove(covariate, "parent_visn"), sep = "")
           ),
         covar_lab = factor(covar_lab,
                             ordered = TRUE,
                             levels = rev(c("Distance",
                                        "Established Pt WT",
                                        "New Pt WT",
                                        "Timely Care",
                                        "Third Next Available",
                                        "Panel Fullness",
                                        "ADI",
                                        "Average Age",
                                        "Gap Metric",
                                        "Nosos",
                                        "Uniques in PCMM",
                                        "Male %",
                                        "Rural %",
                                        "White %",
                                        "SHEP Access Composite",
                                        "Team PCP/AP FTE",
                                        "PC Community Care",
                                        "450 - 2,399", "2,400 - 9,999", "10,000+",
                                        "CBOC", "HCC", "OOS", "VAMC",
                                        "V01","V02","V04", "V05", "V06", "V07", "V08", "V09", "V10",
                                        "V12", "V15", "V16", "V17", "V19", "V20", "V21", "V22", "V23")))) %>%
  select(-covariate) %>%
  pivot_longer(-covar_lab) %>%
  mutate(abs_val = abs(value),
         name_lab = if_else(name == "smd_matched", "Matched", "Un-Matched")) %>%
  ggplot(data = .,
         aes(x = abs_val,
             y = covar_lab,
             fill = name_lab,
             group = name_lab)) +
  geom_point(shape = 21,
             size = 2.25) +
  scale_fill_manual(values = c(
    "Matched" = "black",
    "Un-Matched" = "white"
  )) +
  labs(x = "Absolute Standardized Mean Difference") +
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept = 0, lty = 1) +
  geom_vline(xintercept = 0.05, lty = 2) +
  geom_vline(xintercept = 0.1, lty = 1)
```


```{r}
cobalt::bal.tab(ps_match, un = TRUE)$Observations %>%
  as.data.frame %>%
  kbl(col.names = c("Control", "Treated")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```


```{r}
ps_match2 <- matchit(treated_num ~ 
                      est_pc_pt_wt_pid
                    + new_pc_pt_wt_create
                    + tc_pc_success_prop
                    + tna_new_source
                    + panel_fullness
                    + adi_natRnk_avg
                    + avg_age_oct1_2022
                    + nosos_risk_score
                    + scrssn_count_cat 
                    + pct_male
                    + pct_rural
                    + pct_white
                    + shep_access_metric
                    + team_pcp_ap_fte_total
                    + parent_visn
                    + s_abbr2
                    + mt_4_pc_cc_flag
                      ,
                    data = analytic_df_no_missing,
                    exact = ~s_abbr2,
                    method = "full",
                    distance = "glm",
                    link = "logit")
#=====
ps_matched_sites2 <- match.data(ps_match2) %>%
  select(sta5a, treated_num, weights, distance) %>%
  left_join(., analytic_df %>%
              select(sta5a, treated))
```


