---
title: "PS Matching: Pre-COVID"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 8, fig.height = 8)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
#Input\Analytic df\F2_propensity_score_matching\propensity_score_matching_v3_1.R"

source(here("Input", "Analytic df", "F2_propensity_score_matching","ps_match_pre_covid.R"))
#---
pilot_sites <- dbGetQuery(oabi_con,
                          "select distinct spoke_sta5a as sta5a
                            from [PACT_CC].[CRH].[CRH_sites_FY20_working]
                          where vimpact_pilot = 1") %>%
  pull
#--
sta5a_demog_no_missing <- sta5a_demog_no_missing %>%
  mutate(pilot_site = if_else(sta5a %in% pilot_sites, 1, 0))
```




# Dropped stations  
* From a starting set of `r sta5a_demog %>% nrow() %>% comma()` candidate sta5as, we drop  `r sta5a_demog %>% nrow() - sta5a_demog_no_missing %>% nrow()` sta5as that:
    + Have fewer than 450 uniques in PCMM (`r sta5a_demog %>% drop_na() %>% filter(pcmm_scrssn_count <= 450) %>% nrow()`)
    + Had more than 0 PC CRH encounters before March 2020 but not enough to meet our inclusion criteria (`r sta5a_demog %>% drop_na() %>% filter(not_enough_crh_before_march_20 == 1) %>% nrow()`)
    + Were classified as OOS, but had the word "Mobile" in their official site name (`r sta5a_demog %>% drop_na() %>% filter(mobile_flag == 1) %>% nrow()`)

# Propensity Score "Optimal" Matching


## Final Model    

-   Using [Optimal Matching](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html#optimal-pair-matching-method-optimal) we get `r nrow(opt_matches_pcmm_wVISN) / 2` pairs from a starting set of `r sum(sta5a_demog_no_missing$at_least_10_pc_crh_flag)` __Treated__ sta5as
    - `r sum(sta5a_demog_no_missing$pilot_site == 1 & sta5a_demog_no_missing$at_least_10_pc_crh_flag == 1)` of these are pilot sites
    - Controls are those sta5as that had 0 CRH encounters by March 2020

-   Model: Treatment (i.e., at least two consecutive months with \>9 PC CRH encounters) =

    -   ~~NOSOS (FY18 Q4 Avg)~~
    -   Observed:Expected PC Panel Size (FY18 Q4 Avg)
    -   ~~Team PCP/AP FTE (FY18 Q4 Avg)~~
    -   Uniques in PCMM (FY18 Q4)
    -   ~~ADI (FY18 Q4)~~
    -   Proportion rural (FY18 Q4)
    -   (Non-VA PCCC Consults / Total PCCC Consults) X (uniques in PCMM) X 10,000 (FY18 Q4 Avg)
    -   Third Next Available PC Appointment (FY19 Avg)
    -   Established Patient Waittime from PID (FY19 Avg)
    -   New Patient Waittime (FY19 Avg)
    -   VISN (Exact)
    -   Site Type (i.e., CBOC, VAMC/HCC, or OOS) - (Exact)

-   We estimate the propensity score with logistic regression (i.e., GLM and logit link)
- [Absolute standardized mean difference:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,3], 3)` 
- [Variance ratio:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,4], 3)`
- [Empirical CDF:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) 
    - Mean: `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,5], 2)`
    - Max: `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,6], 2)`

```{r}
plot(opt_match_pcmm_wVISN, type = "jitter", interactive = FALSE)
```


```{r}
ps_plot_df_pcmm <- tibble(
  covariate = attributes(summary(opt_match_pcmm_wVISN)$sum.all)$dimnames[[1]], 
  smd_matched = summary(opt_match_pcmm_wVISN)$sum.matched[,3], 
  smd_preMatch = summary(opt_match_pcmm_wVISN)$sum.all[,3]) %>%
  mutate(covariate = str_remove(covariate, "s_abbr2|census_division|pilot_visn_flag"),
         covariate = str_replace(covariate, "parent_visn", "VISN "),
         covar_lab = factor(case_when(
           covariate == "distance" ~ "Distance",
           #str_detect(covariate, "PCCBOC") == TRUE ~ "PCCBOC",
           str_detect(covariate, "HCC") == TRUE ~ "VAMC/HCC",
           #str_detect(covariate, "VAMC") == TRUE ~ "VAMC",
           #str_detect(covariate, "MSCBOC") == TRUE ~ "MSCBOC",
           str_detect(covariate, "CBOC") == TRUE ~ "Community-Based Outpatient Clinic",
           str_detect(covariate, "OOS") == TRUE ~ "Other Outpatient Services",
           str_detect(covariate, "nosos") == TRUE ~ "NOSOS",
           str_detect(covariate, "obs_exp") == TRUE ~ "Observed:Expected Panel Size Ratio",
           str_detect(covariate, "team") == TRUE ~ "Primary Care Provider FTE",
           str_detect(covariate, "pcmm_") == TRUE ~ "Clinic Size",
           str_detect(covariate, "est_") == TRUE ~ "Established Patient Wait Time",
           str_detect(covariate, "new_") == TRUE ~ "New Patient Wait Time",
           str_detect(covariate, "third_") == TRUE ~ "Third-Next Available",
           str_detect(covariate, "adi") == TRUE ~ "ADI, Avg",
           str_detect(covariate, "age") == TRUE ~ "Age, Avg",
           str_detect(covariate, "male") == TRUE ~ "Male %",
           str_detect(covariate, "white") == TRUE ~ "White %",
           str_detect(covariate, "rural") == TRUE ~ "Rural Residing (%)",
           str_detect(covariate, "gap") == TRUE ~ "Gap Metric",
           str_detect(covariate, "non_va") == TRUE ~ "Community Care Referral Rate",
           TRUE ~ covariate
         ), ordered = TRUE, levels = rev(c("Distance","Not a Pilot VISN",
                                       "Pilot VISN","NOSOS","Observed:Expected Panel Size Ratio","Primary Care Provider FTE",
                                       "Clinic Size", "Rural Residing (%)", "ADI, Avg",
                                       "Community Care Referral Rate",
                                       "Third-Next Available", "New Patient Wait Time", 
                                       "Established Patient Wait Time", "VAMC/HCC", "Community-Based Outpatient Clinic",
                                       "HCC", "VAMC", "Other Outpatient Services",
                                       "MSCBOC", "PCCBOC", "VISN 01", "VISN 02", "VISN 04", "VISN 05",
                                       "VISN 06", "VISN 07", "VISN 08", "VISN 09", "VISN 10", "VISN 12", "VISN 15",
                                       "VISN 16", "VISN 17", "VISN 19", "VISN 20", "VISN 21", "VISN 22", "VISN 23")))) %>%
  select(-covariate) %>%
  pivot_longer(-covar_lab) %>%
  mutate(abs_smd = abs(value),
         name_lab = if_else(name == "smd_matched", "Matched", "Un-Matched"))
#
ggplot(data = ps_plot_df_pcmm,
       aes(x = abs_smd, y = covar_lab, group = name_lab, fill = name_lab)) +
  geom_point(shape = 21,
             size = 2.25) +
  scale_fill_manual(values = c(
    "Matched" = "black",
    "Un-Matched" = "white"
  )) +
  labs(x = "Absolute Standardized Mean Difference") +
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept = 0, lty = 1) +
  geom_vline(xintercept = 0.05, lty = 2) +
  geom_vline(xintercept = 0.1, lty = 1)
```




# Let's look at outcomes  

```{r}
dates <- tibble(
  vssc_month = seq.Date(ymd("2018-10-01"),
                        ymd("2020-02-01"),
                        "1 month")
) %>%
  rownames_to_column(var = "time")
#--
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  filter(vssc_month >= ymd("2018-10-01")
         & vssc_month <= ymd("2020-02-01")) %>%
  inner_join(., opt_matches_pcmm_wVISN) %>%
  mutate(crh_flag = if_else(at_least_10_pc_crh_flag == 1, "PC CRH", "Control"))
```

## New Patient Wait Time  
```{r}
access_metrics %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(mean_val = mean(new_pc_pt_wt, na.rm = T),
            sd_val = sd(new_pc_pt_wt, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, group = crh_flag, color = crh_flag,
             y = mean_val,
             ymin = mean_val - sd_val,
             ymax = mean_val + sd_val)) +
  geom_point(position = position_dodge(width = 1)) +
  geom_line() +
  geom_errorbar(position = position_dodge(width = 1)) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Mean +/- SD")
```

```{r}
access_metrics %>%
  select(vssc_month, new_pc_pt_wt, crh_flag) %>% 
  left_join(dates) %>%
  ggplot(data = .,
         aes(x = time, y = new_pc_pt_wt, fill = crh_flag)) +
  geom_boxplot(position = position_dodge()) +
  scale_y_continuous(limits = c(0, 100)) +
  labs(y = "New Patient Wait Time (days)",
       x = "Month",
       caption = "*Removed 3 observations with values > 100")
```

## Established Patient Wait Time from PID  
```{r}
access_metrics %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(mean_val = mean(est_pc_pt_wt_pid, na.rm = T),
            sd_val = sd(est_pc_pt_wt_pid, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, group = crh_flag, color = crh_flag,
             y = mean_val,
             ymin = mean_val - sd_val,
             ymax = mean_val + sd_val)) +
  geom_point(position = position_dodge(width = 1)) +
  geom_line() +
  geom_errorbar(position = position_dodge(width = 1)) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Mean +/- SD")
```

```{r}
access_metrics %>%
  select(vssc_month, est_pc_pt_wt_pid, crh_flag) %>% 
  left_join(dates) %>%
  ggplot(data = .,
         aes(x = time, y = est_pc_pt_wt_pid, fill = crh_flag)) +
  geom_boxplot(position = position_dodge()) +
  scale_y_continuous(limits = c(0, 35)) +
  labs(y = "Established Patient Wait Time from PID (days)",
       x = "Month",
       caption = "*Removed 1 observation with a value > 40")
```


## Third Next Available    
```{r}
access_metrics %>%
  group_by(crh_flag, vssc_month) %>%
  summarise(mean_val = mean(third_next_avail, na.rm = T),
            sd_val = sd(third_next_avail, na.rm = T)) %>%
  ggplot(data = .,
         aes(x = vssc_month, group = crh_flag, color = crh_flag,
             y = mean_val,
             ymin = mean_val - sd_val,
             ymax = mean_val + sd_val)) +
  geom_point(position = position_dodge(width = 1)) +
  geom_line() +
  geom_errorbar(position = position_dodge(width = 1)) +
  theme(axis.title.x = element_blank()) +
  labs(y = "Mean +/- SD")
```

```{r}
access_metrics %>%
  select(vssc_month, third_next_avail, crh_flag) %>% 
  left_join(dates) %>%
  ggplot(data = .,
         aes(x = time, y = third_next_avail, fill = crh_flag)) +
  geom_boxplot(position = position_dodge()) +
  scale_y_continuous(limits = c(0, NA)) +
  labs(y = "Third Next Available (days)",
       x = "Month")
```