---
title: "PS Matching post-COVID"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12))
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
#Input\Analytic df\F2_propensity_score_matching\propensity_score_matching_v3_1.R"

source(here("Input", "Analytic df",
            "F2_propensity_score_matching","propensity_score_matching_v6_postCOVID.R"))
```




# Dropped stations  
* From a starting set of `r sta5a_demog %>% nrow() %>% comma()` candidate sta5as, we drop  `r sta5a_demog %>% nrow() - sta5a_demog_no_missing %>% nrow()` sta5as that:
    + Have fewer than 450 uniques in PCMM (`r sta5a_demog %>% drop_na() %>% filter(pcmm_scrssn_count <= 450) %>% nrow()`)
    + Had more than 0 PC CRH encounters before October 2021 but not enough to meet our inclusion criteria (`r sta5a_demog %>% drop_na() %>% filter(not_enough_crh_before_oct_21 == 1) %>% nrow()`)

# Propensity Score "Optimal" Matching


## Final Model    

-   Using [Optimal Matching](https://cran.r-project.org/web/packages/MatchIt/vignettes/matching-methods.html#optimal-pair-matching-method-optimal) we get `r nrow(opt_matches_pcmm_wVISN) / 2` pairs from a starting set of `r sum(sta5a_demog_no_missing$pc_crh_criteria_met_after_sept_21)` __Treated__ sta5as (`r ((nrow(opt_matches_pcmm_wVISN) / 2) / sum(sta5a_demog_no_missing$pc_crh_criteria_met_after_sept_21)) %>% percent(accuracy = 0.1)`)

-   Model: Treatment (i.e., at least two consecutive months after September 2021 with \>9 PC CRH encounters) =

    -   NOSOS (FY21 Q2 Avg)
    -   Observed:Expected PC Panel Size (FY21 Q2 Avg)
    -   Team PCP/AP FTE (FY21 Q2 Avg)
    -   Uniques in PCMM (FY21 Avg)
    -   ADI (FY21 Q2)
    -   Proportion rural (FY21 Q2)
    -   (Non-VA PCCC Consults / Total PCCC Consults) X (uniques in PCMM) X 10,000 (FY21 Q2 Avg)
    -   Third Next Available PC Appointment (October 2020 - March 2021 Avg)
    -   Established Patient Waittime __from PID__ (October 2020 - March 2021 Avg)
    -   New Patient Waittime __from create__ (October 2020 - March 2021 Avg)
    -   Site Type (i.e., CBOC, VAMC/HCC, or OOS) - (Exact)
    -   VISN (Exact)

```{r fig.width = 16.18, fig.height = 10}
tibble(
  month_outcomes = c(
    ymd("2020-10-01"), ymd("2021-01-01"), ymd("2021-03-01")
  ),
  `Outcomes` = rep(1.5, 3),
  `Covariates` = c(NA_real_, 0.5, 0.5)
) %>%
  pivot_longer(-month_outcomes) %>%
  mutate(name = factor(name, ordered = T, levels = c("Outcomes", "Covariates"))) %>%
  ggplot(data = .,
         aes(y = value, x = month_outcomes, group = name, color = name)) +
  geom_line(linewidth = 2) +
  scale_y_continuous(limits = c(0, 2)) +
  scale_x_date(date_labels = "%b-%Y") +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size = 20),
        axis.text.x = element_text(size = 18)) +
  ggsci::scale_color_jama()
```

-   We estimate the propensity score with logistic regression (i.e., GLM and logit link)
- [Absolute standardized mean difference:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,3], 3)` 
- [Variance ratio:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,4], 3)`
- [Empirical CDF:](https://cran.r-project.org/web/packages/MatchIt/vignettes/assessing-balance.html#recommendations-for-balance-assessment) 
    - Mean: `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,5], 2)`
    - Max: `r round(summary(opt_match_pcmm_wVISN)$sum.matched[1,6], 2)`

```{r}
plot(opt_match_pcmm_wVISN, type = "jitter", interactive = FALSE)
```



```{r}
ps_plot_df_pcmm <- tibble(
  covariate = attributes(summary(opt_match_pcmm_wVISN)$sum.all)$dimnames[[1]], 
  smd_matched = summary(opt_match_pcmm_wVISN)$sum.matched[,3], 
  smd_preMatch = summary(opt_match_pcmm_wVISN)$sum.all[,3]) %>%
  mutate(covariate = str_remove(covariate, "s_abbr2|census_division|pilot_visn_flag"),
         covariate = str_replace(covariate, "parent_visn", "V"),
         covar_lab = factor(case_when(
           covariate == "distance" ~ "Distance",
           #str_detect(covariate, "PCCBOC") == TRUE ~ "PCCBOC",
           str_detect(covariate, "HCC") == TRUE ~ "VAMC/HCC",
           #str_detect(covariate, "VAMC") == TRUE ~ "VAMC",
           #str_detect(covariate, "MSCBOC") == TRUE ~ "MSCBOC",
           str_detect(covariate, "CBOC") == TRUE ~ "CBOC",
           str_detect(covariate, "OOS") == TRUE ~ "OOS",
           str_detect(covariate, "nosos") == TRUE ~ "NOSOS",
           str_detect(covariate, "obs_exp") == TRUE ~ "Obs:Exp",
           str_detect(covariate, "team") == TRUE ~ "PCP/AP FTE",
           str_detect(covariate, "pcmm_") == TRUE ~ "PCMM ScrSSN Count",
           str_detect(covariate, "est_") == TRUE ~ "Established Patient WT",
           str_detect(covariate, "new_") == TRUE ~ "New Patient WT",
           str_detect(covariate, "third_") == TRUE ~ "Third-Next Available",
           str_detect(covariate, "adi") == TRUE ~ "ADI, Avg",
           str_detect(covariate, "age") == TRUE ~ "Age, Avg",
           str_detect(covariate, "male") == TRUE ~ "Male %",
           str_detect(covariate, "white") == TRUE ~ "White %",
           str_detect(covariate, "rural") == TRUE ~ "Rural %",
           str_detect(covariate, "gap") == TRUE ~ "Gap Metric",
           str_detect(covariate, "non_va") == TRUE ~ "Non-VA Consults per 10,000 in PCMM",
           TRUE ~ covariate
         ), ordered = TRUE, levels = rev(c("Distance","Not a Pilot VISN",
                                       "Pilot VISN","NOSOS","Obs:Exp","PCP/AP FTE",
                                       "PCMM ScrSSN Count", "Rural %", "ADI, Avg",
                                       "Non-VA Consults per 10,000 in PCMM",
                                       "Third-Next Available", "New Patient WT", 
                                       "Established Patient WT", "VAMC/HCC", "CBOC",
                                       "HCC", "VAMC", "OOS",
                                       "MSCBOC", "PCCBOC")))) %>%
  select(-covariate) %>%
  pivot_longer(-covar_lab) %>%
  mutate(abs_smd = abs(value),
         name_lab = if_else(name == "smd_matched", "Matched", "Un-Matched")) %>%
  filter(is.na(covar_lab) == F)
#
ggplot(data = ps_plot_df_pcmm,
       aes(x = abs_smd, y = covar_lab, group = name_lab, fill = name_lab)) +
  geom_point(shape = 21,
             size = 2.25) +
  scale_fill_manual(values = c(
    "Matched" = "black",
    "Un-Matched" = "white"
  )) +
  labs(x = "Absolute Standardized Mean Difference") +
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept = 0, lty = 1) +
  geom_vline(xintercept = 0.05, lty = 2) +
  geom_vline(xintercept = 0.1, lty = 1)
```

## Including VISN  


```{r}
ps_plot_df_pcmm <- tibble(
  covariate = attributes(summary(opt_match_pcmm_wVISN)$sum.all)$dimnames[[1]], 
  smd_matched = summary(opt_match_pcmm_wVISN)$sum.matched[,3], 
  smd_preMatch = summary(opt_match_pcmm_wVISN)$sum.all[,3]) %>%
  mutate(covariate = str_remove(covariate, "s_abbr2|census_division|pilot_visn_flag"),
         covariate = str_replace(covariate, "parent_visn", "V"),
         covar_lab = factor(case_when(
           covariate == "distance" ~ "Distance",
           #str_detect(covariate, "PCCBOC") == TRUE ~ "PCCBOC",
           str_detect(covariate, "HCC") == TRUE ~ "VAMC/HCC",
           #str_detect(covariate, "VAMC") == TRUE ~ "VAMC",
           #str_detect(covariate, "MSCBOC") == TRUE ~ "MSCBOC",
           str_detect(covariate, "CBOC") == TRUE ~ "CBOC",
           str_detect(covariate, "OOS") == TRUE ~ "OOS",
           str_detect(covariate, "nosos") == TRUE ~ "NOSOS",
           str_detect(covariate, "obs_exp") == TRUE ~ "Obs:Exp",
           str_detect(covariate, "team") == TRUE ~ "PCP/AP FTE",
           str_detect(covariate, "pcmm_") == TRUE ~ "PCMM ScrSSN Count",
           str_detect(covariate, "est_") == TRUE ~ "Established Patient WT",
           str_detect(covariate, "new_") == TRUE ~ "New Patient WT",
           str_detect(covariate, "third_") == TRUE ~ "Third-Next Available",
           str_detect(covariate, "adi") == TRUE ~ "ADI, Avg",
           str_detect(covariate, "age") == TRUE ~ "Age, Avg",
           str_detect(covariate, "male") == TRUE ~ "Male %",
           str_detect(covariate, "white") == TRUE ~ "White %",
           str_detect(covariate, "rural") == TRUE ~ "Rural %",
           str_detect(covariate, "gap") == TRUE ~ "Gap Metric",
           str_detect(covariate, "non_va") == TRUE ~ "Non-VA Consults per 10,000 in PCMM",
           TRUE ~ covariate
         ), ordered = TRUE, levels = rev(c("Distance","Not a Pilot VISN",
                                       "Pilot VISN","NOSOS","Obs:Exp","PCP/AP FTE",
                                       "PCMM ScrSSN Count", "Rural %", "ADI, Avg",
                                       "Non-VA Consults per 10,000 in PCMM",
                                       "Third-Next Available", "New Patient WT", 
                                       "Established Patient WT", "VAMC/HCC", "CBOC",
                                       "HCC", "VAMC", "OOS",
                                       "MSCBOC", "PCCBOC", "V01", "V02", "V04", "V05",
                                       "V06", "V07", "V08", "V09", "V10", "V12", "V15",
                                       "V16", "V17", "V19", "V20", "V21", "V22", "V23")))) %>%
  select(-covariate) %>%
  pivot_longer(-covar_lab) %>%
  mutate(abs_smd = abs(value),
         name_lab = if_else(name == "smd_matched", "Matched", "Un-Matched"))
#
ggplot(data = ps_plot_df_pcmm,
       aes(x = abs_smd, y = covar_lab, group = name_lab, fill = name_lab)) +
  geom_point(shape = 21,
             size = 2.25) +
  scale_fill_manual(values = c(
    "Matched" = "black",
    "Un-Matched" = "white"
  )) +
  labs(x = "Absolute Standardized Mean Difference") +
  theme(axis.title.y = element_blank()) +
  geom_vline(xintercept = 0, lty = 1) +
  geom_vline(xintercept = 0.05, lty = 2) +
  geom_vline(xintercept = 0.1, lty = 1)
```

# Un-Matched Sta5as  

```{r}
unmatched_sta5as <- sta5a_demog_no_missing %>%
  filter(sta5a %ni% opt_matches_pcmm_wVISN$sta5a
         & pc_crh_criteria_met_after_sept_21 == T)
#
matches <- sta5a_demog_no_missing %>%
  filter(sta5a %ni% unmatched_sta5as$sta5a)
```

* There are `r nrow(unmatched_sta5as)` sta5as that met our inclusion criteria, but were not matched to a control site

## Meaningful Differences  

### Non-Matched Treated vs. All Sta5as    

```{r}
matches %>%
  mutate(grouping = "match") %>%
  bind_rows(., unmatched_sta5as %>% mutate(grouping = "noMatch")) %>%
  select(-c(s_abbr2, parent_visn, not_enough_crh_before_oct_21, had_pccrh_after_sep_21,
            pc_crh_criteria_met_after_sept_21)) %>%
  pivot_longer(-c(sta5a, grouping)) %>%
  group_by(grouping, name) %>%
  nest() %>%
  spread(key = grouping, value = data) %>%
  mutate(t_test = map2(match, noMatch, ~{t.test(.x$value, .y$value) %>% broom::tidy()}),
         match = map(match, nrow),
         noMatch = map(noMatch, nrow)) %>%
  unnest(cols = c(match, noMatch, t_test)) %>%
  mutate(name2 = case_when(
    name == "adi_natRnk_avg" ~ "ADI",
    name == "est_pid_avg" ~ "Established Pt WT (PID)",
    name == "new_create_avg" ~ "New Pt WT (Create)",
    name == "non_va_cons_rate_per_10k_pcmm" ~ "Non-VA PC Consults per 10k in PCMM",
    name == "obs_exp_panel_ratio_3mo_avg" ~ "Observed:Expected Panel Ratio",
    name == "pcmm_scrssn_count" ~ "PCMM ScrSSN",
    name == "rural_prop" ~ "Rural %",
    name == "team_pcp_ap_fte_total_3mo_avg" ~ "Team PCP/AP FTE",
    name == "third_next_avail_avg" ~ "Third-Next Available"
  )) %>%
  ungroup() %>%
  select(name2, match, noMatch, estimate1, estimate2, estimate, p.value) %>%
  mutate(across(contains("estimate"), ~comma(.x, accuracy = 0.1))) %>%
  mutate(p.value = if_else(p.value < 0.001, "<0.001",
                           comma(p.value, accuracy = 0.001))) %>%
  kbl(col.names = c("", "N Matched", "N Un-Matched", 
                    "Avg. Among Matched", "Avg. Among Un-Matched", "Difference", "p-value"),
      align = c("l", rep("r", 6))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

### Is VISN a Clue?  

```{r}
matches %>%
  group_by(parent_visn) %>%
  summarise(count = n()) %>%
  mutate(prop = percent(count / nrow(matches), accuracy = 0.1)) %>%
  left_join(., by = "parent_visn",
            unmatched_sta5as %>%
              group_by(parent_visn) %>%
              summarise(count = n()) %>%
              mutate(count = replace_na(count, 0),
                     prop = percent(count / nrow(unmatched_sta5as), accuracy = 0.1))) %>%
  mutate(count.y = replace_na(count.y, 0),
         prop.y = replace_na(prop.y, "0%"),
         matched_val = paste0(count.x, " (", prop.x, ")"),
         unMatched_val = paste0(count.y, " (", prop.y, ")")) %>%
  select(parent_visn, contains("_val")) %>%
  kbl(col.names = c("VISN", "N (%) Matched", "N (%) Un-Matched"),
      align = c("c", "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```

* How many potential sta5as are there in VISNs 4, 10, and 20?

```{r}
sta5a_demog_no_missing %>%
  filter(parent_visn %in% c("04", "10", "20")
         & pc_crh_criteria_met_after_sept_21 == F) %>%
  group_by(parent_visn) %>% 
  summarise(count = n())
```


### Non-Matched Treated vs. Control Sta5as    

```{r}
matches %>%
  mutate(grouping = "match") %>%
  filter(pc_crh_criteria_met_after_sept_21 == 0) %>%
  bind_rows(., unmatched_sta5as %>% mutate(grouping = "noMatch")) %>%
  select(-c(s_abbr2, parent_visn, not_enough_crh_before_oct_21, had_pccrh_after_sep_21,
            pc_crh_criteria_met_after_sept_21)) %>%
  pivot_longer(-c(sta5a, grouping)) %>%
  group_by(grouping, name) %>%
  nest() %>%
  spread(key = grouping, value = data) %>%
  mutate(t_test = map2(match, noMatch, ~{t.test(.x$value, .y$value) %>% broom::tidy()}),
         match = map(match, nrow),
         noMatch = map(noMatch, nrow)) %>%
  unnest(cols = c(match, noMatch, t_test)) %>%
  mutate(name2 = case_when(
    name == "adi_natRnk_avg" ~ "ADI",
    name == "est_pid_avg" ~ "Established Pt WT (PID)",
    name == "new_create_avg" ~ "New Pt WT (Create)",
    name == "non_va_cons_rate_per_10k_pcmm" ~ "Non-VA PC Consults per 10k in PCMM",
    name == "obs_exp_panel_ratio_3mo_avg" ~ "Observed:Expected Panel Ratio",
    name == "pcmm_scrssn_count" ~ "PCMM ScrSSN",
    name == "rural_prop" ~ "Rural %",
    name == "team_pcp_ap_fte_total_3mo_avg" ~ "Team PCP/AP FTE",
    name == "third_next_avail_avg" ~ "Third-Next Available"
  )) %>%
  ungroup() %>%
  select(name2, match, noMatch, estimate1, estimate2, estimate, p.value) %>%
  mutate(across(contains("estimate"), ~comma(.x, accuracy = 0.1))) %>%
  mutate(p.value = if_else(p.value < 0.001, "<0.001",
                           comma(p.value, accuracy = 0.001))) %>%
  kbl(col.names = c("", "N Matched", "N Un-Matched", 
                    "Avg. Among Matched", "Avg. Among Un-Matched", "Difference", "p-value"),
      align = c("l", rep("r", 6))) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = T)
```