---
title: "TITLE"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv("H:/HSRD_General/Kaboli Access Team/CRH Evaluation/Bjarni/CRH_r_project/Input/Data/ps_matched_sta5as_v2.csv")
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(initiated_pc_crh_b4_feb_2020 == TRUE) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
  #1: must have Access metrics
  #2: must be in VAST
  #3: no missing scrssn_count_cat
  #4: CBOCs only
  #5: must have scrssn_count_avg_fy18 >= 450
sta5as_to_include <- access_metrics %>%#1: must have Access metrics
  select(sta5a) %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, "PC CRH", "No PC CRH")) %>%#making the crh_flag
  left_join(., scrssn_count) %>%
  filter(is.na(scrssn_count_cat) == F #3: no missing scrssn_count_cat
         & str_detect(s_abbr, "CBOC")#4: CBOCs only
           & scrssn_count_cat != "< 450")#5: must have scrssn_count_avg_fy18 >= 450
#this little table is for the functions i wrote for outputting tables, and I don't want to have to look for it later
# not strictly necissary
scrssn_cat_count <- sta5as_to_include %>%
  group_by(crh_flag, scrssn_count_cat) %>%
  summarise(count = n()) %>%
  mutate(count = as.character(count)) %>%
  pivot_wider(names_from = scrssn_count_cat, values_from = count)
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
      filter(vssc_month < ymd("2020-03-01")) %>%#restrict to our timeframe
      left_join(., dates)#add time column
```

# Front Matter  

## Description of this report  

* This should be a description of what this report/analysis attempts to address/answer  
    + It should be succinct 
    
## Analytic details  


* Description of the "cohort" (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, crh_flag) %>% distinct() %>% summarise(tot = sum(crh_flag == "PC CRH"))` of these met our criteria for PC CRH before March, 2020
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
    + Each row is a sta5a-month
    + Propensity score matching restrictions (i.e., pairs, weights, none)
    + What else?
    
* Description of _Propensity Score_ matching, if any
    + Number of sta5as included as a result
    + Which PS model
    + Included covariates
    + Timeframe of PS covariates

* Description of analyses, if any  
    + Outcome
    + Technique
    + Link function, if applicable


```{r functions}
table_fxn <- function(access_metric, scrssn_cat){
  access_metric_var <- ensym(access_metric)
  #
  y_axis_lab <- if (str_detect(access_metric, "est") == T){
    "Established Patient Wait Time"
  }
  else if (str_detect(access_metric, "new") == T){
    "New Patient Wait Time"
  }
  else if (str_detect(access_metric, "third") == T){
    "Third Next Available"
  }
  else if (str_detect(access_metric, "tc_success_prop") == T){
    "Timely Care Success Rate"
  }
  #-----
  scrssn_cat_count <- if(missing(scrssn_cat)){
    sta5as_to_include %>%
      group_by(crh_flag, scrssn_count_cat) %>%
      summarise(count = n()) %>%
      mutate(count = as.character(count)) %>%
      pivot_wider(names_from = scrssn_count_cat, values_from = count)
  }
  else{
    sta5as_to_include %>%
      filter(scrssn_count_cat == !!scrssn_cat) %>%
      group_by(crh_flag, scrssn_count_cat) %>%
      summarise(count = n()) %>%
      mutate(count = as.character(count)) %>%
      pivot_wider(names_from = scrssn_count_cat, values_from = count)
  }
  #--
  if(missing(scrssn_cat)){
    ttest_uniques <- t.test(scrssn_count_avg_fy18 ~ crh_flag, data = analytic_df)
    uniques_pval <- if_else(ttest_uniques$p.value < 0.001, "<0.001", comma(ttest_uniques$p.value, accuracy = 0.001))
    #
    ttest_value <- if (str_detect(access_metric, "est") == T){
      t.test(est_pc_pt_wt ~ crh_flag, data = analytic_df)
    }
    else if (str_detect(access_metric, "new") == T){
      t.test(new_pc_pt_wt ~ crh_flag, data = analytic_df)
    }
    else if (str_detect(access_metric, "third") == T){
      t.test(third_next_avail ~ crh_flag, data = analytic_df)
    }
    else if (str_detect(access_metric, "tc_success_prop") == T){
      t.test(tc_success_prop ~ crh_flag, data = analytic_df)
    }
    value_pval <- if_else(ttest_value$p.value < 0.001, "<0.001", comma(ttest_value$p.value, accuracy = 0.001))
    #
    ttest_df <- tibble(
      table_labs = c("Average Uniques in PCMM (SD)",
                     paste0("Average ", y_axis_lab, " (SD)"),
                     paste0("Median ", y_axis_lab),
                     "25th and 75th percentiles",
                     "Sta5as with 450 - 2,399 Uniques",
                     "Sta5as with 2,400 - 9,999 Uniques",
                     "Sta5as with > 10,000 Uniques"),
      pvals = c(uniques_pval,
                value_pval,
                "-", "-","-", "-", "-")
    )
    #
    analytic_df %>%
      group_by(crh_flag) %>%
      summarise(avg_pcmm = mean(scrssn_count_avg_fy18, na.rm = T),
                sd_pcmm = sd(scrssn_count_avg_fy18, na.rm = T),
                pcmm_lab = paste0(comma(avg_pcmm, accuracy = 1), 
                                  " (", comma(sd_pcmm, accuracy = 0.1), ")"),
                avg_val = mean(!!access_metric_var, na.rm = T),
                sd_val = sd(!!access_metric_var, na.rm = T),
                val_lab = paste0(comma(avg_val, accuracy = 0.1),
                                 " (", comma(sd_val, accuracy = 0.1), ")"),
                median_lab = comma(median(!!access_metric_var, na.rm = T), accuracy = 0.1),
                qtl_25 = quantile(!!access_metric_var, 0.25, na.rm = T),
                qtl_75 = quantile(!!access_metric_var, 0.75, na.rm = T),
                qtl_lab = paste0("[", comma(qtl_25, accuracy = 0.1), ", ",
                                 comma(qtl_75, accuracy = 0.1), "]")) %>%
      select(crh_flag, ends_with("_lab")) %>%
      left_join(., scrssn_cat_count) %>%
      pivot_longer(-crh_flag) %>%
      pivot_wider(names_from = crh_flag, values_from = value) %>%
      mutate(table_labs = case_when(
        name == "pcmm_lab" ~ "Average Uniques in PCMM (SD)",
        name == "val_lab" ~ paste0("Average ", y_axis_lab, " (SD)"),
        name == "median_lab" ~ paste0("Median ", y_axis_lab),
        name == "qtl_lab" ~ "25th and 75th percentiles",
        name == "450 - 2,399" ~ "Sta5as with 450 - 2,399 Uniques",
        name == "2,400 - 9,999" ~ "Sta5as with 2,400 - 9,999 Uniques",
        name == "10,000+" ~ "Sta5as with > 10,000 Uniques")) %>%
      select(4, 2, 3) %>%
      left_join(., ttest_df) %>%
      kbl(col.names = c("", "No PC CRH", "PC CRH", "p-value"),
          align = c("l", "r", "r", "r")) %>%
      kable_classic("striped") %>%
      row_spec(0, bold = TRUE)
  }
  else{
    analytic_df <- analytic_df %>%
      filter(scrssn_count_cat == !!scrssn_cat)
    #
    ttest_uniques <- t.test(scrssn_count_avg_fy18 ~ crh_flag, data = analytic_df)
    uniques_pval <- if_else(ttest_uniques$p.value < 0.001, "<0.001", comma(ttest_uniques$p.value, accuracy = 0.001))
    #
    ttest_value <- if (str_detect(access_metric, "est") == T){
      t.test(est_pc_pt_wt ~ crh_flag, data = analytic_df)
    }
    else if (str_detect(access_metric, "new") == T){
      t.test(new_pc_pt_wt ~ crh_flag, data = analytic_df)
    }
    else if (str_detect(access_metric, "third") == T){
      t.test(third_next_avail ~ crh_flag, data = analytic_df)
    }
    else if (str_detect(access_metric, "tc_success_prop") == T){
      t.test(tc_success_prop ~ crh_flag, data = analytic_df)
    }
    value_pval <- if_else(ttest_value$p.value < 0.001, "<0.001", comma(ttest_value$p.value, accuracy = 0.001))
    #
    ttest_df <- tibble(
      table_labs = c("Average Uniques in PCMM (SD)",
                     paste0("Average ", y_axis_lab, " (SD)"),
                     paste0("Median ", y_axis_lab),
                     "25th and 75th percentiles",
                     "Sta5as with 450 - 2,399 Uniques",
                     "Sta5as with 2,400 - 9,999 Uniques",
                     "Sta5as with > 10,000 Uniques"),
      pvals = c(uniques_pval,
                value_pval,
                "-", "-","-", "-", "-")
    )
    #
    if(str_detect(access_metric, "tc_success") != T){
      crh_lm <- analytic_df %>% 
        filter(crh_flag == "PC CRH") %>%
        select(time, metric = !!access_metric_var) %>%
        lm(metric ~ time, data = .)
      #
      pred_crh_df <- tibble(
        crh_flag = c("PC CRH", "PC CRH"),
        time = c(18, 29)
      )
      #
      noCrh_lm <- analytic_df %>% 
        filter(crh_flag == "No PC CRH") %>%
        select(time, metric = !!access_metric_var) %>%
        lm(metric ~ time, data = .)
      #
      pred_noCrh_df <- tibble(
        crh_flag = c("No PC CRH", "No PC CRH"),
        time = c(18, 29)
      )
      #--
      value_t1 <- tibble(
        table_labs = paste0("Predicted ", y_axis_lab, " in March, 2019"),
        "No PC CRH" = comma(predict.lm(noCrh_lm, pred_noCrh_df)[1], accuracy = 0.1),
        "PC CRH" = comma(predict.lm(crh_lm, pred_crh_df)[1], accuracy = 0.1),
        pvals = "-"
      )
      #--
      value_t17 <- tibble(
        table_labs = paste0("Predicted ", y_axis_lab, " in February, 2020"),
        "No PC CRH" = comma(predict.lm(noCrh_lm, pred_noCrh_df)[2], accuracy = 0.1),
        "PC CRH" = comma(predict.lm(crh_lm, pred_crh_df)[2], accuracy = 0.1),
        pvals = "-"
      )
      #
      analytic_df  %>%
        group_by(crh_flag) %>%
        summarise(avg_pcmm = mean(scrssn_count_avg_fy18, na.rm = T),
                  sd_pcmm = sd(scrssn_count_avg_fy18, na.rm = T),
                  pcmm_lab = paste0(comma(avg_pcmm, accuracy = 1), 
                                    " (", comma(sd_pcmm, accuracy = 0.1), ")"),
                  avg_val = mean(!!access_metric_var, na.rm = T),
                  sd_val = sd(!!access_metric_var, na.rm = T),
                  val_lab = paste0(comma(avg_val, accuracy = 0.1),
                                   " (", comma(sd_val, accuracy = 0.1), ")"),
                  median_lab = comma(median(!!access_metric_var, na.rm = T), accuracy = 0.1),
                  qtl_25 = quantile(!!access_metric_var, 0.25, na.rm = T),
                  qtl_75 = quantile(!!access_metric_var, 0.75, na.rm = T),
                  qtl_lab = paste0("[", comma(qtl_25, accuracy = 0.1), ", ",
                                   comma(qtl_75, accuracy = 0.1), "]")) %>%
        select(crh_flag, ends_with("_lab")) %>%
        left_join(., scrssn_cat_count) %>%
        pivot_longer(-crh_flag) %>%
        pivot_wider(names_from = crh_flag, values_from = value) %>%
        mutate(table_labs = case_when(
          name == "pcmm_lab" ~ "Average Uniques in PCMM (SD)",
          name == "val_lab" ~ paste0("Average ", y_axis_lab, " (SD)"),
          name == "median_lab" ~ paste0("Median ", y_axis_lab),
          name == "qtl_lab" ~ "25th and 75th percentiles",
          name == "450 - 2,399" ~ "Sta5as with 450 - 2,399 Uniques",
          name == "2,400 - 9,999" ~ "Sta5as with 2,400 - 9,999 Uniques",
          name == "10,000+" ~ "Sta5as with > 10,000 Uniques")) %>%
        select(4, 2, 3) %>%
        left_join(., ttest_df) %>%
        bind_rows(., value_t1) %>%
        bind_rows(., value_t17) %>%
        kbl(col.names = c("", "No PC CRH", "PC CRH", "p-value"),
            align = c("l", "r", "r", "r")) %>%
        kable_classic("striped") %>%
        row_spec(0, bold = TRUE)
    }
    else{
      crh_lm <- analytic_df %>% 
        filter(crh_flag == "PC CRH") %>%
        lm(tc_success_prop ~ time, data = .)
      #
      pred_crh_df <- tibble(
        crh_flag = c("PC CRH", "PC CRH"),
        time = c(18, 29)
      )
      #
      noCrh_lm <- analytic_df %>% 
        filter(crh_flag == "No PC CRH") %>%
        lm(tc_success_prop ~ time, data = .)
      pred_noCrh_df <- tibble(
        crh_flag = c("No PC CRH", "No PC CRH"),
        time = c(18, 29)
      )
      #--
      value_t1 <- tibble(
        table_labs = paste0("Predicted ", y_axis_lab, " in March, 2019"),
        "No PC CRH" = percent(predict.lm(noCrh_lm, pred_noCrh_df)[1], accuracy = 0.1),
        "PC CRH" = percent(predict.lm(crh_lm, pred_crh_df)[1], accuracy = 0.1),
        pvals = "-"
      )
      #--
      value_t17 <- tibble(
        table_labs = paste0("Predicted ", y_axis_lab, " in February, 2020"),
        "No PC CRH" = percent(predict.lm(noCrh_lm, pred_noCrh_df)[2], accuracy = 0.1),
        "PC CRH" = percent(predict.lm(crh_lm, pred_crh_df)[2], accuracy = 0.1),
        pvals = "-"
      )
      #
      analytic_df  %>%
        group_by(crh_flag) %>%
        summarise(avg_pcmm = mean(scrssn_count_avg_fy18, na.rm = T),
                  sd_pcmm = sd(scrssn_count_avg_fy18, na.rm = T),
                  pcmm_lab = paste0(comma(avg_pcmm, accuracy = 1), 
                                    " (", comma(sd_pcmm, accuracy = 0.1), ")"),
                  avg_val = mean(!!access_metric_var, na.rm = T),
                  sd_val = sd(!!access_metric_var, na.rm = T),
                  val_lab = paste0(percent(avg_val, accuracy = 0.1),
                                   " (", percent(sd_val, accuracy = 0.1), ")"),
                  median_lab = percent(median(!!access_metric_var, na.rm = T), accuracy = 0.1),
                  qtl_25 = quantile(!!access_metric_var, 0.25, na.rm = T),
                  qtl_75 = quantile(!!access_metric_var, 0.75, na.rm = T),
                  qtl_lab = paste0("[", percent(qtl_25, accuracy = 0.1), ", ",
                                   percent(qtl_75, accuracy = 0.1), "]")) %>%
        select(crh_flag, ends_with("_lab")) %>%
        left_join(., scrssn_cat_count) %>%
        pivot_longer(-crh_flag) %>%
        pivot_wider(names_from = crh_flag, values_from = value) %>%
        mutate(table_labs = case_when(
          name == "pcmm_lab" ~ "Average Uniques in PCMM (SD)",
          name == "val_lab" ~ paste0("Average ", y_axis_lab, " (SD)"),
          name == "median_lab" ~ paste0("Median ", y_axis_lab),
          name == "qtl_lab" ~ "25th and 75th percentiles",
          name == "450 - 2,399" ~ "Sta5as with 450 - 2,399 Uniques",
          name == "2,400 - 9,999" ~ "Sta5as with 2,400 - 9,999 Uniques",
          name == "10,000+" ~ "Sta5as with > 10,000 Uniques")) %>%
        select(4, 2, 3) %>%
        left_join(., ttest_df) %>%
        bind_rows(., value_t1) %>%
        bind_rows(., value_t17) %>%
        kbl(col.names = c("", "No PC CRH", "PC CRH", "p-value"),
            align = c("l", "r", "r", "r")) %>%
        kable_classic("striped") %>%
        row_spec(0, bold = TRUE)
    }
  }
}

#===============================
plot_fxn <- function(access_metric, pcmm_cat){
  access_metric_var <- ensym(access_metric)
  #
  y_axis_lab <- if (str_detect(access_metric, "est") == T){
    "Established Patient Wait Time"
  }
  else if (str_detect(access_metric, "new") == T){
    "New Patient Wait Time"
  }
  else if (str_detect(access_metric, "third") == T){
    "Third Next Available"
  }
  else if (str_detect(access_metric, "tc_success_prop") == T){
    "Timely Care Success Rate"
  }
  #-----
  analytic_df <- if (str_detect(access_metric, "third") != T){access_metrics %>%
                    select(sta5a, vssc_month, access_metric_var) %>%
                    inner_join(., sta5as_to_include) %>%
                    filter(vssc_month < ymd("2020-03-01")) %>%
                    left_join(., dates) %>%
                    left_join(., crh_flag %>% select(sta5a, first_6_mos_w_10_flag)) %>%
                    filter(scrssn_count_cat == !!pcmm_cat)}
              else{access_metrics %>%
                    select(sta5a, vssc_month, access_metric_var) %>%
                    inner_join(., sta5as_to_include) %>%
                    filter(vssc_month < ymd("2020-03-01")) %>%
                    left_join(., dates) %>%
                    filter(third_next_avail < 100) %>%
                    filter(scrssn_count_cat == !!pcmm_cat)}
  #--
  p2 <- ggplot(data = analytic_df,
               aes(x = vssc_month, y = !!access_metric_var, group = sta5a)) +
    geom_vline(xintercept = vline_xint,
               lty = 3) +
    scale_x_date() +
    geom_line(alpha = 0.35) +
    geom_smooth(aes(x = vssc_month, y = !!access_metric_var, group = crh_flag, lty = crh_flag),
                color = "red",
                inherit.aes = FALSE,
                se = TRUE,
                method = "lm") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    ggsci::scale_color_d3() +
    guides(color = guide_legend(override.aes = list(size = 2))) +
    labs(y = y_axis_lab)
  #==========================
  if (str_detect(access_metric, "tc_") == T){
    print(p2 + scale_y_continuous(labels = percent_format(accuracy = 1)))
  }
  else {
    print(p2)
  }
}
#------------------------
regression_fxn <- function(access_metric, pcmm_cat){
   reg_label <- if (str_detect(access_metric, "est") == T){
    "Established Patient Wait Time"
  }
  else if (str_detect(access_metric, "new") == T){
    "New Patient Wait Time"
  }
  else if (str_detect(access_metric, "third") == T){
    "Third Next Available"
  }
  else if (str_detect(access_metric, "tc_success_prop") == T){
    "Timely Care Success Rate"
  }
  #==
  reg_df_crh <- if(missing(pcmm_cat)){analytic_df}
  else {analytic_df %>%
    filter(scrssn_count_cat == !!pcmm_cat)}
  #==
  lm_crh <- if (str_detect(access_metric, "est") == T){
    lm(est_pc_pt_wt ~ time*crh_flag, data = reg_df_crh)
  }
  else if (str_detect(access_metric, "new") == T){
    lm(new_pc_pt_wt ~ time*crh_flag, data = reg_df_crh)
  }
  else if (str_detect(access_metric, "third") == T){
    lm(third_next_avail ~ time*crh_flag, data = reg_df_crh)
  }
  else if (str_detect(access_metric, "tc_success_prop") == T){
    lm(tc_success_prop ~ time*crh_flag, data = reg_df_crh)
  }
  tab_model(lm_crh,
            show.se = TRUE,
            dv.labels = reg_label,
            pred.labels = c(
              "Intercept", "Time",
              "PC CRH (vs. No PC CRH)",
              "Time X PC CRH"
            ))
}
#=============
regression_table_fxn <- function(access_metric, pcmm_cat){
  reg_label <- if (str_detect(access_metric, "est") == T){
    "Established Patient Wait Time"
  }
  else if (str_detect(access_metric, "new") == T){
    "New Patient Wait Time"
  }
  else if (str_detect(access_metric, "third") == T){
    "Third Next Available"
  }
  else if (str_detect(access_metric, "tc_success_prop") == T){
    "Timely Care Success Rate"
  }
  #==
  reg_df_crh <- if(missing(pcmm_cat)){analytic_df %>%
    filter(crh_flag == "PC CRH")}
  else {analytic_df %>%
    filter(scrssn_count_cat == !!pcmm_cat 
           & crh_flag == "PC CRH")}
  #==
  lm_crh <- if (str_detect(access_metric, "est") == T){
    lm(est_pc_pt_wt ~ time, data = reg_df_crh)
  }
  else if (str_detect(access_metric, "new") == T){
    lm(new_pc_pt_wt ~ time, data = reg_df_crh)
  }
  else if (str_detect(access_metric, "third") == T){
    lm(third_next_avail ~ time, data = reg_df_crh)
  }
  else if (str_detect(access_metric, "tc_success_prop") == T){
    lm(tc_success_prop ~ time, data = reg_df_crh)
  }
  #--
  reg_df_noCrh <- if(missing(pcmm_cat)){analytic_df %>%
    filter(crh_flag == "No PC CRH")}
  else {analytic_df %>%
    filter(scrssn_count_cat == !!pcmm_cat 
           & crh_flag == "No PC CRH")}
  #==
  lm_noCrh <- if (str_detect(access_metric, "est") == T){
    lm(est_pc_pt_wt ~ time, data = reg_df_noCrh)
  }
  else if (str_detect(access_metric, "new") == T){
    lm(new_pc_pt_wt ~ time, data = reg_df_noCrh)
  }
  else if (str_detect(access_metric, "third") == T){
    lm(third_next_avail ~ time, data = reg_df_noCrh)
  }
  else if (str_detect(access_metric, "tc_success_prop") == T){
    lm(tc_success_prop ~ time, data = reg_df_noCrh)
  }
  tab_model(lm_crh, lm_noCrh,
            show.se = TRUE,
            pred.labels = c("Intercept", "Time (month)"),
            dv.labels = c("PC CRH", "No PC CRH"))
}
```

# Established Patient Wait Time    

## Overall   

```{r}
#
vline_xint <- as.numeric(ymd("2019-10-01"))
#
ggplot(data = analytic_df,
               aes(x = vssc_month, y = est_pc_pt_wt, group = sta5a)) +
    geom_vline(xintercept = vline_xint,
               lty = 3) +
    scale_x_date() +
    geom_line(alpha = 0.35) +
    geom_smooth(aes(x = vssc_month, y = est_pc_pt_wt, group = crh_flag, lty = crh_flag),
                color = "red",
                inherit.aes = FALSE,
                se = TRUE,
                method = "lm") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(angle = 270, vjust = 0.3)) +
    ggsci::scale_color_d3() +
    guides(color = guide_legend(override.aes = list(size = 2))) +
    labs(y = "Established Patient Wait Time")
```
 
```{r, results = 'asis'}
table_fxn("est_pc_pt_wt")
```

```{r}
regression_fxn("est_pc_pt_wt")
```

## 450 - 2,399 Uniques in PCMM  

```{r est_table1, results = 'asis'}
table_fxn("est_pc_pt_wt", "450 - 2,399")
```


```{r est_plot1}
plot_fxn("est_pc_pt_wt", "450 - 2,399")
```

```{r est_reg1}
regression_fxn("est_pc_pt_wt", "450 - 2,399")
```


## 2,400 - 9,999 Uniques in PCMM  
```{r est_table2, results = 'asis'}
table_fxn("est_pc_pt_wt", "2,400 - 9,999")
```

```{r est_plot2}
plot_fxn("est_pc_pt_wt", "2,400 - 9,999")
```

```{r est_reg2}
regression_fxn("est_pc_pt_wt", "2,400 - 9,999")
```


## 10,000+ Uniques in PCMM  
```{r est_table3, results = 'asis'}
table_fxn("est_pc_pt_wt", "10,000+")
```

```{r est_plot3}
plot_fxn("est_pc_pt_wt", "10,000+")
```

```{r est_reg3}
regression_fxn("est_pc_pt_wt", "10,000+")
```
