---
title: "PC FTE Needed: July 2023"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v6_post_COVID.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-02-01"), ymd("2022-12-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PCS_PCAT].[econ].PatientPCP_2020_2024
                            	where fy = 2020
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
analytic_df <- gap_metric %>%
  inner_join(., vast) %>%
  left_join(., scrssn_count) %>%
  filter(s_abbr %in% c("PCCBOC", "MSCBOC", "HCC", "VAMC", "OOS")
         & scrssn_count_cat != "< 450"
         & vssc_month == ymd("2021-03-01")
         & is.na(gap_metric) == F) %>%
  mutate(gap_level = case_when(
    gap_metric >= 1 & gap_metric < 1.2 ~ "Marginally Staffed (1-1.2)",
    gap_metric >= 1.2 ~ "Fully Staffed (>= 1.2)",
    gap_metric < 1 ~ "Not Fully Staffed (< 1)"
  ),
  gap_diff = 1.2 - gap_metric,
  dr_fte_diff = (gap_diff * observed_ps_tot) / 1200,
  np_fte_diff = (gap_diff * observed_ps_tot) / 900,
  #
  dr_fte_diff_up = ceiling((gap_diff * observed_ps_tot) / 1200),
  np_fte_diff_up = ceiling((gap_diff * observed_ps_tot) / 900),
  #
  excess_gap = if_else(gap_metric > 1.2, gap_metric - 1.2, NA_integer_),
  #
  excess_dr = (excess_gap * observed_ps_tot) / 1200,
  excess_app = (excess_gap * observed_ps_tot) / 900,
  #
  patient_diff = (gap_diff * observed_ps_tot),
  #
  status = if_else(gap_metric >= 1.2, "No Gap", "Gap"),
  #
  np_need = case_when(np_fte_diff >= 0.5 ~ 1,
                      is.na(np_fte_diff) & np_fte_diff < 0.5 ~ 0,
                      TRUE ~ 99))
#--
analytic_df2 <- gap_metric %>%
  inner_join(., vast) %>%
  left_join(., scrssn_count) %>%
  filter(s_abbr %in% c("PCCBOC", "MSCBOC", "HCC", "VAMC", "OOS")
         & scrssn_count_cat != "< 450"
         & vssc_month == ymd("2023-07-01")
         & is.na(gap_metric) == F) %>%
  mutate(gap_level = case_when(
    gap_metric >= 1 & gap_metric < 1.2 ~ "Marginally Staffed (1-1.2)",
    gap_metric >= 1.2 ~ "Fully Staffed (>= 1.2)",
    gap_metric < 1 ~ "Not Fully Staffed (< 1)"
  ),
  gap_diff = 1.2 - gap_metric,
  dr_fte_diff = (gap_diff * observed_ps_tot) / 1200,
  np_fte_diff = (gap_diff * observed_ps_tot) / 900,
  #
  dr_fte_diff_up = ceiling((gap_diff * observed_ps_tot) / 1200),
  np_fte_diff_up = ceiling((gap_diff * observed_ps_tot) / 900),
  #
  excess_gap = if_else(gap_metric > 1.2, gap_metric - 1.2, NA_integer_),
  #
  excess_dr = (excess_gap * observed_ps_tot) / 1200,
  excess_app = (excess_gap * observed_ps_tot) / 900,
  #
  patient_diff = (gap_diff * observed_ps_tot),
  #
  status = if_else(gap_metric >= 1.2, "No Gap", "Gap"),
  #
  np_need = case_when(np_fte_diff >= 0.5 ~ 1,
                      is.na(np_fte_diff) & np_fte_diff < 0.5 ~ 0,
                      TRUE ~ 99))
```

# Front Matter  

## Description of this report  

* This is a response to the rapid request for PCP FTE needed to be fully staffed


    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`
    + There are `r nrow(analytic_df) %>% comma()` rows in the data
    + These rows come from `r analytic_df %>% select(sta5a) %>% n_distinct()` sta5as
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "CBOC") == T))` of these are CBOCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "HCC|VAMC") == T))` of these are HCCs or VAMCs
      + `r analytic_df %>% select(sta5a, s_abbr) %>% distinct() %>% summarise(tot = sum(str_detect(s_abbr, "OOS") == T))` of these are OOS
    + Each row is a sta5a-month
    

# March 2021    

## FTE Needed  

```{r}
analytic_df %>%
  filter(status == "Gap") %>%
  summarise("MD FTE Needed" = sum(dr_fte_diff, na.rm = T),
            "MD FTE Needed, Ceiling" = sum(dr_fte_diff_up, na.rm = T),
            "APP FTE Needed" = sum(np_fte_diff, na.rm = T),
            "APP FTE Needed, Ceiling" = sum(np_fte_diff_up, na.rm = T)) %>%
  mutate(foo = "foo") %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  mutate(value = comma(value, accuracy = 0.1)) %>%
  kbl(col.names = c("", "FTE")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

## Number of under-staffed, marginally staffed, and over-staffed sta5as  

```{r}
analytic_df %>%
  tabyl(gap_level) %>%
  adorn_totals("row") %>%
  mutate(n = comma(n, accuracy = 1)) %>%
  adorn_pct_formatting() %>%
  kbl(col.names = c("Gap Category", "Count", "%")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```



# July 2023  

## FTE Needed  

```{r}
analytic_df2 %>%
  filter(status == "Gap") %>%
  summarise("MD FTE Needed" = sum(dr_fte_diff, na.rm = T),
            "MD FTE Needed, Ceiling" = sum(dr_fte_diff_up, na.rm = T),
            "APP FTE Needed" = sum(np_fte_diff, na.rm = T),
            "APP FTE Needed, Ceiling" = sum(np_fte_diff_up, na.rm = T)) %>%
  mutate(foo = "foo") %>%
  pivot_longer(-foo) %>%
  select(-foo) %>%
  mutate(value = comma(value, accuracy = 0.1)) %>%
  kbl(col.names = c("", "FTE")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```

## Number of under-staffed, marginally staffed, and over-staffed sta5as  

```{r}
analytic_df2 %>%
  tabyl(gap_level) %>%
  adorn_totals("row") %>%
  mutate(n = comma(n, accuracy = 1)) %>%
  adorn_pct_formatting() %>%
  kbl(col.names = c("Gap Category", "Count", "%")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = T)
```


```{r}
analytic_df %>%
  rename(gap_level_march_21 = gap_level) %>%
  select(sta5a, gap_level_march_21) %>%
  left_join(., analytic_df2 %>%
              select(sta5a, gap_level_july_23 = gap_level)) %>%
  tabyl(gap_level_march_21, gap_level_july_23) %>%
  select(-NA_) %>%
  kbl(col.names = c("", "Fully Staffed (>= 1.2)", "Marginally Staffed (1-1.2)", "Not Fully Staffed (< 1)"),
      full_width = F) %>%
  kable_classic("striped") %>%
  add_header_above(c("", "<b>July 2023</b>" = 3))
```