---
title: "CRH Urgent Request for USH"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
set.seed(1234)
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06") %>%
  mutate(drop_flag = if_else(str_detect(short_name, "Mobile") & state != "AL", 1, 0)) %>%
  filter(drop_flag == 0) %>%
  select(-drop_flag)
#propensity score matched sta5as, as well 
ps_matched <- read_csv(here("Input","Post-COVID", "ps_matched_sites_post_covid.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- tibble(
  vssc_month = seq.Date(ymd("2020-10-01"), ymd("2023-09-01"), "1 month")) %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2020 by sta5a and making a categorical variable
  # that we use for exclusion
# scrssn_count <- dbGetQuery(oabi_con,
#                            "with CTE as(
#                             	select count(distinct ScrSSN_num) as scrssn_count
#                             		, sta5a, fy, qtr
#                             	from [PCS_PCAT].[econ].PatientPCP_2020_2024
#                             	where fy = 2020
#                             	group by Sta5a, fy, QTR
#                             	)
#                             select AVG(scrssn_count) as scrssn_count_avg_fy20, sta5a
#                             from CTE
#                             group by Sta5a") %>%
#   mutate(scrssn_count_cat = factor(case_when(
#     scrssn_count_avg_fy20 < 450 ~ "< 450",# exclusion criteria
#     scrssn_count_avg_fy20 >= 450 & scrssn_count_avg_fy20 < 2400 ~ "450 - 2,399",
#     scrssn_count_avg_fy20 >= 2400 & scrssn_count_avg_fy20 < 10000 ~ "2,400 - 9,999",
#     scrssn_count_avg_fy20 >= 10000 ~ "10,000+"
#   ), ordered = TRUE,
#   levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, #pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric, panel_fullness)
#--
gap_metric <- dbGetQuery(oabi_con,
                         "select * from [crh_eval].H_gap_metric") %>%
  mutate(vssc_month = ymd(vssc_month))
#--
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month) %>%
  mutate(tc_pc_success_prop = tc_pc_success_sum / tc_requests_sum)
#--
pen_rate <- dbGetQuery(oabi_con, 
                       "select *
                       from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  rename(vssc_month = crh_month) %>%
  mutate(vssc_month = ymd(vssc_month))
```

```{r}
analytic_df <- ps_matched %>%
  select(sta5a, treated, weights) %>%
  cross_join(., dates) %>%
  left_join(., access_metrics %>%
              select(sta5a, vssc_month, est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source)) %>%
  mutate(tna_new_source = as.numeric(tna_new_source))
#
difference_df <- analytic_df %>%
  filter(vssc_month == ymd("2022-09-01")) %>%
  rename_at(vars(c(est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source)), paste0, "_2022") %>%
  select(-weights, -time, -vssc_month) %>%
  left_join(., analytic_df %>%
              filter(vssc_month == ymd("2023-09-01")) %>%
              rename_at(vars(c(est_pc_pt_wt_pid, new_pc_pt_wt_create, tna_new_source)), paste0, "_2023")) %>%
  select(-weights, -time, -vssc_month) %>%
  mutate(est_diff = est_pc_pt_wt_pid_2023 - est_pc_pt_wt_pid_2022,
         new_diff = new_pc_pt_wt_create_2023 - new_pc_pt_wt_create_2022,
         tna_diff = tna_new_source_2023 - tna_new_source_2022)
```

# Front Matter  

## Description of this report  

* This document contains analyses for the rapid request for CRH information by the USH

    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs on `r min(analytic_df$vssc_month)`
    + The last observation in the data occurs on `r max(analytic_df$vssc_month)`

    
* Description of _Propensity Score_ matching
    + This report uses __Propensity Score v6.0__
    + PS model v6.0 consists of 
        + Covariates matched on their average values in FY21 Q2
        + Outcomes matched on their average values over October 2020 - March 2021
        + Site type (CBOC, VAMC/HCC, OOS) - Exact
        + VISN - Exact

# Linear Regression  
## Established Patient Wait Time  

```{r}
est_model <- lmer(est_pc_pt_wt_pid ~ treated + (1|sta5a),
                  weights = weights,
     data = analytic_df)
#
tab_model(est_model)
```

## New Patient Wait Time  

```{r}
new_model <- lmer(new_pc_pt_wt_create ~ treated + (1|sta5a),
                  weights = weights,
     data = analytic_df)
#
tab_model(new_model)
```

## Third Next Available    

```{r}
tna_model <- lmer(tna_new_source ~ treated + (1|sta5a),
                  weights = weights,
     data = analytic_df)
#
tab_model(tna_model)
```


# Average Wait Times September 2023  
## Established Patient Wait Time  

```{r}
analytic_df %>%
  filter(vssc_month == ymd("2023-09-01")) %>%
  t.test(est_pc_pt_wt_pid ~ treated, data = .)
```

## New Patient Wait Time  
```{r}
analytic_df %>%
  filter(vssc_month == ymd("2023-09-01")) %>%
  t.test(new_pc_pt_wt_create ~ treated, data = .)
```

## Third Next Available    
```{r}
analytic_df %>%
  filter(vssc_month == ymd("2023-09-01")) %>%
  t.test(tna_new_source ~ treated, data = .)
```

# Change in Wait Times from September 2022 to September 2023  
## Established  
```{r}
difference_df %>%
  t.test(est_diff ~ treated, data = .)
```

## New  
```{r}
difference_df %>%
  t.test(new_diff ~ treated, data = .)
```

## TNA  
```{r}
difference_df %>%
  t.test(tna_diff ~ treated, data = .)
```

# Subtracting Previous Month's Value  
## Established  

* This model is singular  
```{r}
lagged_df <- analytic_df %>%
  arrange(sta5a, vssc_month) %>%
  group_by(sta5a) %>%
  mutate(est_diff = est_pc_pt_wt_pid - lag(est_pc_pt_wt_pid),
         new_diff = new_pc_pt_wt_create - lag(new_pc_pt_wt_create),
         tna_diff = tna_new_source - lag(tna_new_source))
#
lmer(est_diff ~ treated + (1 | sta5a),
     data = lagged_df) %>%
  tab_model()
```

## New  
* This model is also singular  
```{r}
lmer(new_diff ~ treated + (1 | sta5a),
     data = lagged_df) %>%
  tab_model()
```

## TNA    
* This model is also singular  
```{r}
lmer(tna_diff ~ treated + (1 | sta5a),
     data = lagged_df) %>%
  tab_model()
```