---
title: "Sta5as with CRH pre-COVID, but not after March 2020"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    code_folding: hide
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v5.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month > ymd("2020-02-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, pcccr_per_10k_uniques,
         avg_age_oct1_2022, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
# a vector of sta5as meeting our pc crh criteria
crh_sta5as <- crh_flag %>%
  filter(crh_10_flag == 1) %>%
  select(sta5a) %>%
  pull
#this is where exclusion criteria are applied:
sta5as_to_include <- access_metrics %>%#1: must have Access metrics
  select(sta5a) %>%
  inner_join(ps_matched) %>%
  inner_join(., vast %>% select(sta5a, s_abbr)) %>%#2: must be in VAST
  distinct %>%
  mutate(crh_flag = if_else(sta5a %in% crh_sta5as, 
                            "PC CRH", "No PC CRH")) %>%#making the crh_flag
  left_join(., scrssn_count) %>%
  filter(scrssn_count_cat != "< 450")#3: must have scrssn_count_avg_fy18 >= 450
#=================
#making the analytic dataset
analytic_df <- access_metrics %>%# start with access metrics
      inner_join(., sta5as_to_include) %>%#restrict to our table from above
     # filter(vssc_month > ymd("2019-09-01")) %>%#restrict to our timeframe
      left_join(., dates)
```

# Front Matter  

## Description of this report  

* This is a report on the `r crh_flag %>% filter(crh_10_flag == 1 & had_pcCRH_after_march20 == 0) %>% nrow()` sta5as that met PC CRH inclusion criteria before March 2020, but didn't meet those criteria after March 2020

## Decision Points  

* As part of our effort to move forward with the post-COVID analysis I am asking whether we should re-visit our propensity score matching scheme
    
# Which sta5as are these?  


```{r}
sta5as_didnt_have_pccrh_after_march20 <-crh_flag %>% 
  filter(crh_10_flag == 1 & had_pcCRH_after_march20 == 0) %>%
  select(sta5a) %>%
  pull
#
pen_rate_month <- dbGetQuery(oabi_con,
                             "select * from [OABI_MyVAAccess].[crh_eval].B1_crh_penRate") %>%
  mutate(crh_month = ymd(crh_month)) %>%
  filter(sta5a %in% sta5as_didnt_have_pccrh_after_march20)
#--
total_after <- pen_rate_month %>%
  group_by(sta5a) %>%
  filter(crh_month > ymd("2020-03-01")) %>%
  summarise(total_crh_after = sum(crh_encounter_count, na.rm = T))
#--
total_before <- pen_rate_month %>%
  group_by(sta5a) %>%
  filter(crh_month <= ymd("2020-03-01")) %>%
  summarise(total_crh_before = sum(crh_encounter_count, na.rm = T))
#---
pen_rate_month %>%
  select(sta5a) %>%
  distinct %>%
  left_join(., total_before) %>%
  left_join(., total_after) %>%
  left_join(., vast %>% select(sta5a, short_name, state, parent_visn, s_abbr)) %>%
  left_join(., crh_flag %>% select(sta5a, first_mo_w_mt9_pc_crh)) %>%
  select(parent_visn, sta5a, short_name, state, s_abbr, first_mo_w_mt9_pc_crh, starts_with("total")) %>%
  mutate(total_crh_before = comma(total_crh_before),
         short_name = str_remove(short_name, ", Iowa")) %>%
  kbl(col.names = c("VISN", "Sta5a", "Name", "State", "Type", 
                    "First month meeting inclusion", "Total PC CRH before 3/20", 
                    "Total PC CRH After 3/20"),
      align = c(rep("l", 6), "r", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
  
```


