---
title: "CRH Encounters by Site Type"
date: "`r Sys.Date()`"
author: "Bjarni Haraldsson"
output: 
  html_document:
    toc_float: true
    toc: true
    toc_depth: 3
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE, cache = FALSE, fig.width = 10, fig.height = 10)
#
# knitr::knit_hooks$set(inline = function(x){
#   prettyNum(x, big.mark = ",")
# })
#
options(scipen = 999, knitr.kable.NA = ' ')
#
library(tidyverse)
library(lubridate)
library(gt)
library(kableExtra)
library(readxl)
library(DBI)
library(here)
library(scales)
library(janitor)
library(MatchIt)
library(lme4)
library(sjPlot)
#
##---------- Connection to SQL13
oabi_con <- dbConnect(odbc::odbc(),
                      Driver = "SQL Server",
                      Server = "vhacdwsql13.vha.med.va.gov",
                      Database = "OABI_MyVAAccess",
                      Trusted_Connection = "true")
#
`%ni%` <- negate(`%in%`)
#---------
theme_update(axis.title = element_text(size = 20),
             axis.text = element_text(size = 16),
             strip.text = element_text(size = 14),
             legend.text = element_text(size = 18),
             legend.title = element_blank(),
             plot.caption = element_text(size = 12),
             legend.position = "bottom")
#===========
#source(here("input", "Functions", "multiplot_05jan21.R"))
```

```{r reading-in}
#vast file for s_abbr and others
vast <- dbGetQuery(oabi_con,
                   "select * from [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06")
#making PC CRH criteria for this analysis
crh_flag <- dbGetQuery(oabi_con,
                       "select * from [crh_eval].C1_crh_flag") %>%
  mutate(first_mo_w_mt9_pc_crh = ymd(first_mo_w_mt9_pc_crh),
         #initiated before february to account for needing two consecutive months with > 9
         initiated_pc_crh_b4_feb_2020 = if_else(first_mo_w_mt9_pc_crh < ymd("2020-02-01"), TRUE, FALSE)) %>%
  left_join(., vast %>% select(sta5a, s_abbr))
#propensity score matched sta5as if being used
ps_matched <- read_csv(here("Input","Data", "ps_matched_sta5as_v3_1.csv"))
#pulling timely care
timely_care <- dbGetQuery(oabi_con,
                          "select *
                          from [OABI_MyVAAccess].[crh_eval].[E3_daysDV_month_sta5a]") %>%
  mutate(viz_month = ymd(viz_month)) %>%
  rename(sta5a = req_sta5a,
         vssc_month = viz_month)
#pulling vssc access metrics
access_metrics <- dbGetQuery(oabi_con,
                             "select * from [crh_eval].E2_VSSC_access_metrics") %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
  left_join(timely_care)
#making a time column
dates <- access_metrics %>%
  filter(vssc_month < ymd("2020-03-01") & vssc_month > ymd("2018-09-01")) %>%
  select(vssc_month) %>%
  distinct %>%
  arrange(vssc_month) %>%
  rowid_to_column(., var = "time")
#counting average # of unique scrssns in FY2018 by sta5a and making a categorical variable
  # that we use for exclusion
scrssn_count <- dbGetQuery(oabi_con,
                           "with CTE as(
                            	select count(distinct ScrSSN_num) as scrssn_count
                            		, sta5a, fy, qtr
                            	from [PACT_CC].[econ].PatientPCP
                            	where fy = 2018
                            	group by Sta5a, fy, QTR
                            	)
                            select AVG(scrssn_count) as scrssn_count_avg_fy18, sta5a
                            from CTE
                            group by Sta5a") %>%
  mutate(scrssn_count_cat = factor(case_when(
    scrssn_count_avg_fy18 < 450 ~ "< 450",# exclusion criteria
    scrssn_count_avg_fy18 >= 450 & scrssn_count_avg_fy18 < 2400 ~ "450 - 2,399",
    scrssn_count_avg_fy18 >= 2400 & scrssn_count_avg_fy18 < 10000 ~ "2,400 - 9,999",
    scrssn_count_avg_fy18 >= 10000 ~ "10,000+"
  ), ordered = TRUE,
  levels = c("< 450", "450 - 2,399", "2,400 - 9,999", "10,000+")))
#---------------
covariates <- dbGetQuery(oabi_con,
                         "select * from [OABI_MyVAAccess].[crh_eval].Z_analytic_df") %>%
  rename(sta5a = Sta6a, vssc_month = visitMonth) %>%
  mutate(vssc_month = ymd(vssc_month)) %>%
      filter(vssc_month < ymd("2020-03-01") & vssc_month > ymd("2018-09-01")) %>%
  mutate(pct_male = male_count / scrssn_count * 100,
         pct_white = race_white_count / scrssn_count * 100,
         pct_rural = urh_rural_count / scrssn_count * 100) %>%
  select(pc_crh_per_1k_total_pc, pcccr_per_10k_uniques,
         avg_age_oct1_2020, sta5a, vssc_month, 
         parent_visn, census_division,
         nosos_risk_score, obs_exp_panel_ratio, team_pcp_ap_fte_total,
         pcmm_count_fy_qtr,
         adi_natRnk_avg, pct_male, pct_white, pct_rural, avg_driveDist,
         shep_access_metric)
```

```{r}
analytic_df <- dbGetQuery(oabi_con,
                          "with CTE as (
	select count(*) as crh_encounter_count, spoke_sta5a_combined_cdw as sta5a
	from [PACT_CC].[CRH].C_crh_utilization_final
	where care_type = 'Primary Care'
		AND visitdate < cast('2020-03-01' as date)
		AND visitdate > cast('2018-09-30' as date)
	group by spoke_sta5a_combined_cdw
	),
cte2 as (
	select *
		, initiated_b4_feb2020 = case when first_mo_w_mt9_pc_crh < cast('2020-02-01' as date) then 1 else 0 end
	from [OABI_MyVAAccess].[crh_eval].C1_crh_flag
	)
select a.*, b.initiated_b4_feb2020, c.s_abbr
from CTE as a
left join cte2 as b
	on a.sta5a = b.sta5a
left join [OABI_MyVAAccess].[crh_eval].C2_vast_from_a06 as c
	on a.sta5a = c.sta5a
") %>%
  filter(initiated_b4_feb2020 == 1)
```

# Front Matter  

## Description of this report  

* This report produces tables of __PC CRH Encounter Counts__ by __Site Type (e.g., PCCBOC)__

## Decision Points  

* This was the lowest-hanging fruit from our meeting with Matt, Ashok, and Chelle on 12/7/2022
    
## Analytic details  


* Description of the cohort (i.e., __analytic\_df__)
    + The first observation in the data occurs in October, 2018
    + The last observation in the data occurs in February, 2020
    + These are the `r nrow(analytic_df)` sta5as that met our inclusion criteria before February, 2020
    
* Description of _Propensity Score_ matching
    + There is __No PS Matching__ applied 


## As a Table  
```{r}
analytic_df %>%
  group_by(s_abbr) %>%
  summarise(sum_crh_encounter_count = sum(crh_encounter_count),
            sta5a_count = n()) %>%
  mutate(sum_prop = sum_crh_encounter_count / sum(sum_crh_encounter_count),
         count_prop = sta5a_count / sum(sta5a_count)) %>%
  adorn_totals() %>%
  mutate(across(c(4, 5), ~percent(.x,accuracy = 0.1))) %>%
  mutate(across(c(2, 3), ~comma(.x, accuracy = 1))) %>%
  mutate(sum_val = paste0(sum_crh_encounter_count, " (", sum_prop, ")"),
         count_val = paste0(sta5a_count, " (", count_prop, ")")) %>%
  select(1, 6, 7) %>%
  kbl(col.names = c("Site Type", "PC CRH Encounters", "Sta5as"),
      align = c("l", "r", "r")) %>%
  kable_classic("striped",
                full_width = F) %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(6, bold = TRUE)

```

## As Boxplots  
```{r}
analytic_df %>%
  ggplot(data = .,
         aes(x = s_abbr, y = crh_encounter_count,
             fill = s_abbr)) +
  geom_boxplot() +
  theme(legend.position = "none", 
        axis.title.x = element_blank()) +
  scale_y_continuous(labels = comma_format(accuracy = 1)) +
  labs(y = "Total PC CRH Encounters Before March 2020")
```

## Looking closer at OOS and HCC sites    

```{r}
oos_hcc_sites <- analytic_df %>%
  filter(s_abbr %in% c("HCC", "OOS")) %>%
  left_join(., vast %>% select(sta5a, urh_vast, short_name, parent_visn, city, state)) %>%
  select(sta5a, s_abbr, crh_encounter_count, urh_vast, city, state) %>%
  arrange(s_abbr) %>%
  mutate(crh_encounter_count = comma(crh_encounter_count, accuracy = 1))
#
pcmm_count_avg_fy19 <- covariates %>%
  filter(sta5a %in% oos_hcc_sites$sta5a
         & vssc_month > ymd("2018-09-01")
         & vssc_month < ymd("2020-03-01")) %>%
  group_by(sta5a) %>%
  summarise(avg_pcmm_count = comma(mean(pcmm_count_fy_qtr, na.rm = T), accuracy = 0.1))
#
oos_hcc_sites %>%
  left_join(., pcmm_count_avg_fy19) %>%
  kbl(col.names = c("Sta5a", "Site Type", "PC CRH Encounters", "URH (VAST)",
                    "City", "State", "Average Uniques in PCMM, FY19"),
      align = c("l", "l", "r", "l", "l", "l", "r")) %>%
  kable_classic("striped") %>%
  row_spec(0, bold = TRUE)
```